### 2021-01-12 markdown/fees_fines_to.Rmd
first build out (asa abstract)

---
title: "Turnout and Amendment 4: Mobilizing Eligible Voters Close to Formerly Incarcerated Floridians"
subtitle: ""
thanks: Prepared for the 2021 Annual Meeting of the SPSA. Draft --- please do not circulate without permission. The author thanks Myrna Pérez, Patrick Berry, and Peter Miller for their comments on this project. All errors are my responsibility.
author: Kevin Morris^[Researcher, Brennan Center for Justice at NYU School of Law, 120 Broadway Ste 1750, New York, NY 10271 (kevin.morris@nyu.edu)]
institute: "Brennan Center for Justice"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  bookdown::pdf_document2:
    toc: no
    fig_caption: yes
    latex_engine: xelatex
    keep_tex: true
link-citations: yes
fontsize: 12pt
header-includes:
    - \usepackage{rotating}
    - \usepackage{setspace}
    - \usepackage{lineno}
    - \linenumbers
abstract: ""
---
\pagenumbering{gobble}
\pagebreak
```{r setup, echo = F, message = F, warning = F}
knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf")
library(systemfit)
library(kevostools)
library(AER)
library(sandwich)
library(lmtest)
library(scales)
library(ggpubr)
library(tidyverse)
library(extrafont)
library(kableExtra)
library(data.table)
library(stargazer)
loadfonts()
```
\pagenumbering{arabic}
\doublespacing

```{r, figures-side, fig.show="hold", out.width="50%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:marg1}Dollars per Resident and 2018 Turnout"}
p1 <- readRDS("./temp/simple_scat.rds")
load("./temp/mef_to.rdata")
print(p1)
print(p2)
```

```{r, fig.show="hold", out.width="50%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:marg1}Dollars per Resident and 2018 Turnout Gap"}
p3 <- readRDS("./temp/simple_scat_gap.rds")
load("./temp/mef_gap.rdata")
print(p3)
print(p4)
```

### 2021-01-12 markdown/fees_fines_to.tex
first build out (asa abstract)

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Turnout and Amendment 4: Mobilizing Eligible Voters Close to Formerly Incarcerated Floridians},
  pdfauthor={Kevin Morris},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{lineno}
\linenumbers
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\title{Turnout and Amendment 4: Mobilizing Eligible Voters Close to Formerly Incarcerated Floridians\thanks{Prepared for the 2021 Annual Meeting of the SPSA. Draft --- please do not circulate without permission. The author thanks Myrna Pérez, Patrick Berry, and Peter Miller for their comments on this project. All errors are my responsibility.}}
\author{Kevin Morris\footnote{Researcher, Brennan Center for Justice at NYU School of Law, 120 Broadway Ste 1750, New York, NY 10271 (\href{mailto:kevin.morris@nyu.edu}{\nolinkurl{kevin.morris@nyu.edu}})}}
\date{January 12, 2021}

\begin{document}
\maketitle

\pagenumbering{gobble}
\pagebreak

\pagenumbering{arabic}
\doublespacing

\begin{figure}
\includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/figures-side-1} \includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/figures-side-2} \caption{\label{fig:marg1}Dollars per Resident and 2018 Turnout}\label{fig:figures-side}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/unnamed-chunk-1-1} \includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/unnamed-chunk-1-2} \caption{\label{fig:marg1}Dollars per Resident and 2018 Turnout Gap}\label{fig:unnamed-chunk-1}
\end{figure}

\end{document}

### 2021-01-12 code/00_initialize.R

@@ -1,0 +1,16 @@
+library(miceadds)
+library(ggeffects)
+library(scales)
+library(extrafont)
+library(data.table)
+library(stargazer)
+library(tidyverse)
+library(kevostools)
+
+save <- c("db", "cleanup", "theme_bc", "save", "weighted.ttest.ci")
+
+
+cleanup <- function(...){
+  save2 <- c(save, ...)
+  rm(list=ls(envir = .GlobalEnv)[! ls(envir = .GlobalEnv) %in% save2], envir = .GlobalEnv)
+}

### 2021-01-12 code/01_cog.R

@@ -1,0 +1,65 @@
+d <- read_fwf("raw_data/2017_individual_unit_file/2017FinEstDAT_09102020modp_pu.txt",
+              col_positions = fwf_widths(c(14, 3, 12, 4, 1),
+                                         col_names = c("place_id",
+                                                       "item_code",
+                                                       "amount",
+                                                       "year",
+                                                       "imputation")),
+              col_types = "ccccc")
+
+
+police <- d %>% 
+  filter(item_code %in% c("E62", "F62", "G62", "I62", "L62", "M62", "N62", "O62", "P62", "R62",
+                          "E25", "I25", "F25", "G25", "K25")) %>% 
+  filter(as.numeric(amount) > 0)
+
+
+info <- read_fwf("raw_data/2017_individual_unit_file/Fin_GID_2017.txt",
+                 col_positions = fwf_widths(c(14, 64, 35, 2, 3, 5, 9, 2, 7, 2, 2, 2, 4, 2)),
+                 col_types = "cccccccccccccc")
+
+d <- left_join(d, select(info,
+                         X1,
+                         population = X7,
+                         fips = X6,
+                         state = X4,
+                         name = X2), by = c("place_id" = "X1")) %>% 
+  rename(pop_cog = population)
+
+# 
+# c <- get_basic_census_stats("place", 2018)
+# 
+# sd <- rbindlist(lapply(unique(filter(fips_codes, as.integer(state_code) < 60)$state_code), function(s){
+#   if(!file.exists(paste0("temp/census_sub_", s, ".rds"))){
+#     j <- get_basic_census_stats("county subdivision", 2018, state = s)
+#     saveRDS(j, paste0("temp/census_sub_", s, ".rds"))
+#   }else{
+#     j <- readRDS(paste0("temp/census_sub_", s, ".rds"))
+#   }
+#   return(j)
+# })) %>% 
+#   mutate(GEOID = paste0(substring(GEOID, 1, 2), substring(GEOID, 6)))
+# 
+# c2 <- rbind(c, sd)
+# 
+# saveRDS(c2, "temp/census_data.rds")
+
+c2 <- readRDS("temp/census_data.rds")
+
+cities <- inner_join(mutate(d, GEOID = paste0(state, fips)), c2, by = "GEOID") %>% 
+  filter(item_code == "U30",
+         place_id %in% police$place_id,
+         as.integer(pop_cog) > 2500) %>% 
[…]

### 2021-01-12 code/02_find_places.R

@@ -1,0 +1,75 @@
+library(data.table)
+library(tidyverse)
+library(rgdal)
+
+fc <- fread("raw_data/fips_codes.csv") %>%
+  mutate(state_code = str_pad(as.character(state_code), side = "left", width = 2, pad = "0"))
+
+nat <- readRDS("./temp/national_merged.rds")
+
+nat <- left_join(nat, fc) %>%
+  select(-state) %>%
+  rename(state = state_code)
+
+nat <- rename(nat, lat = Residence_Addresses_Latitude, long = Residence_Addresses_Longitude) %>%
+  mutate(lat = as.numeric(lat),
+         long = as.numeric(long)) %>%
+  ungroup()
+
+
+print(nrow(nat))
+
+for(s in unique(nat$state)){
+  print(s)
+  if(s != "00"){
+    if(!file.exists(paste0("temp/subs_places_", s, ".rds"))){
+      if(file.exists(paste0("raw_data/tl_2018_", s, "_cousub/tl_2018_", s, "_cousub.shp"))){
+        s <- str_pad(as.character(s), width = 2, side = "left", pad = "0")
+        r <- filter(nat, state == s, !is.na(lat), !is.na(long))
+        
+        places <- readOGR(paste0("raw_data/tl_2018_", s, "_place"),
+                          paste0("tl_2018_", s, "_place"))
+        
+        pings  <- SpatialPoints(select(r, long, lat), proj4string = places@proj4string)
+        
+        r$place<- over(pings, places)$GEOID
+        
+        
+        subs <- readOGR(paste0("raw_data/tl_2018_", s, "_cousub"),
+                        paste0("tl_2018_", s, "_cousub"))
+        
+        pings  <- SpatialPoints(select(r, long, lat), proj4string = subs@proj4string)
+        
+        r$county_s<- over(pings, subs)$GEOID
+        
+        saveRDS(select(r, LALVOTERID, place, county_s), paste0("temp/subs_places_", s, ".rds"))
+      }
+    }
+  }
+}
+
+###########################
+locs <- rbindlist(lapply(list.files("temp", full.names = T, pattern = "subs_places"), readRDS))
+
+nat <- left_join(nat, locs)
+
+saveRDS(nat, "temp/nat_with_places.rds")
+
+# nat <- readRDS("temp/nat_with_places.rds")
+
+cities <- readRDS("temp/cog_cities.rds")
+
+nat <- nat %>% 
[…]

### 2021-01-12 code/03_merge.R

@@ -1,0 +1,50 @@
+library(data.table)
+library(tidyverse)
+library(kevostools)
+library(rgdal)
+
+nat <- readRDS("./temp/national_merged.rds")
+
+locs <- rbindlist(lapply(list.files("temp", full.names = T, pattern = "subs_places"), readRDS))
+
+nat <- left_join(nat, locs)
+
+saveRDS(nat, "temp/nat_with_places.rds")
+
+cities <- readRDS("temp/cog_cities.rds")
+
+nat <- nat %>% 
+  mutate_at(vars(place, county_s), as.character) %>% 
+  mutate(plasub = ifelse(place %in% cities$GEOID, place,
+                         ifelse(county_s %in% cities$GEOID, county_s, NA)))
+
+
+ll <- nat %>% 
+  group_by(EthnicGroups_EthnicGroup1Desc, plasub, state) %>% 
+  summarize(count = n(),
+            to = mean(General_2018_11_06),
+            to_old = mean(General_2016_11_08))
+
+ll2 <- nat %>% 
+  group_by(plasub, state) %>% 
+  summarize(count = n(),
+            to = mean(General_2018_11_06),
+            to_old = mean(General_2016_11_08)) %>% 
+  mutate(EthnicGroups_EthnicGroup1Desc = "overall")
+
+ll3 <- nat %>% 
+  filter(EthnicGroups_EthnicGroup1Desc != "European") %>% 
+  group_by(plasub, state) %>% 
+  summarize(count = n(),
+            to = mean(General_2018_11_06),
+            to_old = mean(General_2016_11_08)) %>% 
+  mutate(EthnicGroups_EthnicGroup1Desc = "nonwhite")
+
+ll <- bind_rows(ll, ll2, ll3)
+
+ll <- pivot_wider(ll, id_cols = plasub, names_from = "EthnicGroups_EthnicGroup1Desc",
+                  values_from = c("count", "to", "to_old"))
+
+colnames(ll) <- clean_names(ll)
+
+saveRDS(ll, "temp/city_to.rds")

### 2021-01-12 code/03_regs.R

@@ -1,0 +1,133 @@
+
+
+cog <- readRDS("temp/cog_cities.rds") %>% 
+  mutate(state = as.factor(state))
+
+to <- readRDS("temp/city_to.rds") %>% 
+  group_by(plasub) %>% 
+  summarize(to_18 = weighted.mean(to, count),
+            to_16 = weighted.mean(to_old, count))
+
+full_set <- inner_join(cog, to, by = c("GEOID" = "plasub"))
+
+p1 <- ggplot(full_set, aes(x = lndper, y = to_18)) + geom_point(shape = 1) + geom_smooth(method = "lm") +
+  xlab("Dollars per Resident") +
+  ylab("Turnout in 2018") + scale_x_continuous(breaks = c(log(2), log(11), log(101), log(1001)),
+                                                                           labels = c("$1", "$10", "$100", "$1,000")) +
+  scale_y_continuous(labels = percent) +
+  theme_bw() + theme(plot.caption = element_text(hjust = 0),
+                     text = element_text(family = "LM Roman 10")) +
+  coord_cartesian(xlim = c(-.3, log(1001))) +
+  labs(caption = "
+       
+       ")
+
+m1 <- lm.cluster(to_18 ~ lndper + nh_white + nh_black + latino +
+           median_income + some_college + median_age + share_over_64 +
+           state, data = full_set, cluster = full_set$state)
+
+m2 <- lm(to_18 ~ lndper + nh_white +  + latino +
+           median_income + some_college + median_age + share_over_64 +
+           state, full_set)
+
+stargazer(m1, m2, type = "text", omit = c("state"))
+
+
+marg <- ggeffect(m2, "lndper [all]", vcov.fun = "vcovCR", vcov.type = "CR0", 
+                 vcov.args = list(cluster = full_set$state))
+
+
+p2 <- ggplot() + 
+  geom_histogram(aes(x = lndper, y = ..count../5000), position="identity", linetype=1,
+                 fill="gray60", data = full_set, alpha=0.5, bins = 30) + 
+  geom_line(aes(x = x, y = predicted), data = marg, color = "black") +
+  geom_ribbon(aes(x = x, ymin = conf.low, ymax = conf.high), fill= "black", alpha=0.25, data = marg) +
+  xlab("Dollars per Resident") +
+  ylab("Turnout in 2018") + scale_x_continuous(breaks = c(log(2), log(11), log(101), log(1001)),
[…]

### 2021-01-12 markdown/fees_fines_to.Rmd
asa abstract

@@
 ---
-title: "Turnout and Amendment 4: Mobilizing Eligible Voters Close to Formerly Incarcerated Floridians"
+title: "Policing for profit undermines democracy: Fines, Fees, and Voter Turnout"
 subtitle: ""
-thanks: Prepared for the 2021 Annual Meeting of the SPSA.
-Draft --- please do not circulate without permission.
-The author thanks Myrna Pérez, Patrick Berry, and Peter Miller for their comments on this project.
-All errors are my responsibility.
-author: Kevin Morris^[Researcher, Brennan Center for Justice at NYU School of Law, 120 Broadway Ste 1750, New York, NY 10271 (kevin.morris@nyu.edu)]
-institute: "Brennan Center for Justice"
+thanks: 
+author:
+- Jonathan Ben-Menachem^[PhD Student, Columbia University, Department of Sociology (jbenmenachem@gmail.com)]
+- Kevin Morris^[Researcher, Brennan Center for Justice at NYU School of Law (kevin.morris@nyu.edu)]
 date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
     - \usepackage{setspace}
-    - \usepackage{lineno}
-    - \linenumbers
 abstract: ""
@@
 \pagenumbering{arabic}
-\doublespacing
+Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities’ alienation from government.
+After Michael Brown was killed by the Ferguson Police Department in 2014, a US Department of Justice investigation into the city’s police and courts demonstrated that the municipality was engaged in a practice that advocates now refer to as “policing for profit.” The city’s reliance on fines and fees to fund government functions grew from 13 to 23 percent of the total budget between fiscal years 2012 and 2015 (United States Department of Justice 2015).
+Although a body of literature developed over the past decade indicates that criminalization chills political participation, no work has directly investigated the relationship between fines and fees revenue collection and voter turnout.
+This project intends to fill that gap.
 
-```{r, figures-side, fig.show="hold", out.width="50%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:marg1}Dollars per Resident and 2018 Turnout"}
+It wasn’t just a Ferguson problem, or even a Missouri problem.
+American cities’ reliance on fines and fees revenue increased significantly following the 2008 recession—as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (Singla, Kirschner, and Stone 2019, Mughan 2020, Kirk, Fernandes, and Friedman 2020, Martin 2018).
+
+Fines and fees practices disproportionately target Black Americans: city government reliance on fines and fees revenue is associated with larger Black populations, racial stereotypes affect the imposition of fines and fees, and Black defendants face more severe penalties related to monetary sanctions (United States Commission on Civil Rights 2017, Harris, Evans, and Beckett 2011, Edwards and Harris 2020).
+The relationship between cities’ reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator, however (Sances and You 2017).
+This could suggest that higher reliance on fines and fees results from government officials targeting individuals who hold less political power (Makowsky and Stratmann 2009).
+
+Fines and fees legally disenfranchise Americans: 48 states and the District of Columbia authorize some form of wealth-based penal disenfranchisement (Colgan 2019).
+More specifically, many states require payment of fees as a condition of criminal legal supervision or the payment of all legal financial obligations as a condition of completing a sentence, and failure to comply with supervision conditions or sentence completion conditions can be a barrier to voting rights restoration.
+A recent report from the Sentencing Project estimates that more than 5 million Americans are legally barred from voting due to a felony conviction (Uggen et al 2020).
+
+Recent work from scholars in sociology and political science, however, indicates that many more voters are indirectly disenfranchised due to over-incarceration and the politically chilling effects of the carceral state.
+Policing and incarceration shape political socialization: personal contact with police or incarceration is associated with a reduced likelihood of political participation, and that alienating effect extends even to people who have incarcerated family members or who simply reside in affected communities (Lee, Porter, and Comfort 2014, Weaver and Lerman 2010; Morris 2020).
+This relationship may be more complicated, however.
+In New York City, concentrated policing was associated with reduced turnout in Congressional elections and increased turnout in the 2008 Presidential election as well as the local mayoral election in 2013 (Laniyonu 2019).
+It may also be the case that proximal contact differs from personal contact with the criminal legal system—whereas direct experience with criminalization (and incarceration in particular) reduces the likelihood of voting, proximal or indirect experience produces more mixed results.
+Hannah Walker suggests that police contact that does not lead to a criminal conviction may even mobilize voters—but her survey questions specifically excluded “minor traffic stops,” a primary site of police ticketing (Walker 2014).
+
+However, one of the most routine interactions Americans have with the police has gone largely unstudied: namely, ticketing for low-level offenses.
+Police ticketing practices may discourage potential voters without directly disenfranchising them, and ticketing affects more Americans than legal disenfranchisement.
+In 2018, more than 24 million people experienced police contact in the context of a traffic stop; by contrast, about 5.17 million people are disenfranchised as a result of a felony conviction (Harrell and Davis 2020, Uggen et al 2020).
+
+Ticketing practices may be related to distrust of government and reduced political participation.
+In a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government more broadly (Carpenter, Sweetland, and McDonald 2019).
+Lerman and Weaver have argued that residents’ perceptions of law enforcement may affect their perceptions of government as a whole (Lerman and Weaver 2013).
+As one man told them, “I feel like if I contact a senator or governor, they’ll probably want to put me in jail and leave me as a troublemaker… I try to basically stay away from government” (Lerman and Weaver 2014).
+In their study of descriptive representation, Sances and You explicitly suggested that “fines may make descriptive representation less likely by depressing minority turnout,” and called for further research regarding voter turnout and the imposition of fines (Sances and You 2017).
+In this paper, we clarify that relationship.
+
+We begin by picking up where Sances, and You (2017) left off.
+By tying data from the Census of Governments to a national geocoded voter file we test whether municipalities with more fees and fines collected per resident saw lower turnout in the 2014, 2016, and 2018 general elections.
+We expect to find that municipalities where more revenue is raised per resident saw lower turnout, other things being equal.
+Because the American criminal legal system falls disproportionately on minorities, we also expect that the racial turnout gap (Fraga 2019 [NEED TO ADD CITE]) will be larger in municipalities that rely more heavily on fines and fees.
+
+Of course, fines and fees imposition may be related to turnout without necessarily indicating a causal relationship.
+To estimate the causal effect, we explore whether turnout increases or decreases in the wake of changes in city revenue collection policy.
+We explore this at the national level using the Census of Governments data, and also how turnout changed in [Buffalo] in the years following a dramatic increase in ticketing in that city.
+
+### Data and Design {-}
+
+In order to ascertain whether fines and fees practices affect voter turnout, we exploit data from the 2013 and 2017 Census of Governments and national voter file data.
+The COG, a project of the US Census Bureau, collects budget data for all local governments every five years, and the most recent survey was in 2017.
+The COG asks cities how much revenue they collect from “penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation .
+.
+.
+and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).” As indicated by previous researchers, these data serve as a useful proxy for the prevalence of police ticketing (Goldstein, Sances, and You 2018, Sances and You 2017).
+
+Unfortunately, the COG data does not include voter turnout, and turnout data is not generally available at this level.
+Therefore, in order to determine municipality-level turnout, we employ a national, geocoded voter file.
+This voter file is provided by L2 Political, and includes a host of information about each voter, including age, party affiliation, racial estimates, and historical turnout.
+By using the latitude and longitude of every registered voter in the country and shapefiles provided by the Census Bureau, we map each voter to their home municipality using the same definitions as the COG.
+We then aggregate these individual-level records up to the municipality level to determine municipal turnout, measured as a share of registered voters.
+The full study will include other turnout denominators to avoid biased estimates arising from differential registration rates.
+
+Because the L2 national voter file includes estimates of each voter’s racioethnic identity, we can also use these data to determine the racial turnout gap in each municipality.
+These records are just estimates, and may be imprecise at the individual level.
+However, we assume that this presents less of a problem when aggregating to the municipality-level.
+
+In order to control for potential confounders, we also control for a host of other information from the 5-year American Community Survey.
+
+Although we do not present these results in this abstract, we also intend to incorporate causal estimates in the full version of this study.
+We will begin by modelling changes in fees and fines reliance between the 2013 and 2017 COGs, and turnout in the 2014 and 2018 elections.
+We will also compare the turnout of voters in [Buffalo, New York] to voters in surrounding municipalities between [20XX] and [20XX].
+[Buffalo] increased its reliance on fees and fines dramatically in this period, allowing us to directly observe whether a decrease in turnout followed this change.
+
+### Results {-}
+
+Figure 1 makes clear that there is a relationship between the fees and fines collected by a municipality and its turnout.The left hand panel shows the simple bivariate relationship between the two quantities.
+In the right hand panel, we present the marginal effects plot in lieu of a regression table due to space constraints.
+The second panel shows that, even after controlling for a municipality’s racial composition, median income, collegiate education, age, and state fixed effects, there is a statistically significant, negative relationship between fees and fines and turnout in 2018.
+In these models, the dependent variable is municipal turnout in 2018 and the independent variable of interest is the natural log of the dollars in fees and fines per resident plus 1.
+
+```{r, figures-side, fig.show="hold", out.width="50%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:marg1}Dollars per Resident and 2018 Turnout", fig.pos = "H"}
 p1 <- readRDS("./temp/simple_scat.rds")
@@
 
-```{r, fig.show="hold", out.width="50%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:marg1}Dollars per Resident and 2018 Turnout Gap"}
+A 10 percent increase in the dollars of fees and fines raised per resident is associated with a reduction in turnout of 0.06 percentage points, and the relationship is significant at the 99 percent confidence level.
+Although this may seem small, Figure 1 shows that the range of fees and fines raised is large.
+The figure marks the 10th and 90th percentiles for revenue collected in fees and fines, and predicted turnout drops by 1.6 percentage points over this range.
+
+Figure 2 presents the results of preliminary analyses investigating the relationship between fees and fines collection and the racial turnout gap.
+Because the bivariate regression is not significant and the R2 is very small (<0.001) we refrain from including the line of best fit in the first panel.
+Our initial analysis indicates, however, that the relationship between fees and fines collection and the racial turnout gap in a municipality is moderated by its racial composition.
+The second panel of Figure 2 indicates the racial turnout gap is much larger in minority-white cities that collect no fees and fines than in whiter cities that also do not collect fees and fines.
+As fees and fines collections increase in less-white cities the turnout gap drops, though we see no such pattern in municipalities that are predominantly white.
+
+```{r, fig.show="hold", out.width="50%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:marg1}Dollars per Resident and 2018 Turnout Gap", fig.pos = "H"}
 p3 <- readRDS("./temp/simple_scat_gap.rds")
@@
 ```
+
+### Discussion {-}
+
+The significant negative association in our analysis provides some support for our hypothesis: though our preliminary analyses cannot establish causality, they are consistent with a causal story that links fines and fees practices with lower political participation among those who are subjected to them.
+On the other hand, officials in municipalities with lower turnout may feel more free to rely on fees and fines for revenue collection because they have less fear of electoral repercussions.
+Our full study will explore these causal relationships directly by supplementing our initial analysis with an analysis of voter turnout and revenue reliance change over time.
+
+That the racial turnout gap is more sensitive to fees and fines collection in municipalities with a smaller white share of the population is somewhat surprising.
+This could reflect racially disparate policing in cities with large nonwhite populations.
+It is possible that cities with many nonwhite residents and low fees and fines collections disproportionately penalize nonwhite residents; as fees and fines collections increase, however, a larger share of the population - and, thus, more white voters - may be swept into these programs, thereby reducing racial disparities and consequently discrepancies in the racial turnout gap.
+
+Our full study will also include an analysis of racial disparities in voter turnout using data from states where race is included in the voter file (North Carolina, Georgia, or Florida).
+In other words, is Black voter turnout more depressed in cities with greater fines and fees reliance?
+
+Future research could include a more narrow analysis of turnout in jurisdictions that dramatically increased or decreased ticketing over a comparatively short period of time.
+For instance, a Florida Times-Union investigation revealed that police in four counties disproportionately issued tickets to Black pedestrians (Sanders and Conarck 2017).
+In Tampa, police issued thousands of tickets to Black cyclists between 2012 and 2015—after journalists reported on the problem, the city began to issue fewer than 100 citations each year as of 2018 (Zayas 2015, Frago 2019).
+Systematically conducting such an analysis would likely require collecting and organizing new data, as city-level police ticketing data is inconsistent and not always public information.

### 2021-01-12 markdown/fees_fines_to.tex
asa abstract

@@
 \hypersetup{
-  pdftitle={Turnout and Amendment 4: Mobilizing Eligible Voters Close to Formerly Incarcerated Floridians},
-  pdfauthor={Kevin Morris},
+  pdftitle={Policing for profit undermines democracy: Fines, Fees, and Voter Turnout},
+  pdfauthor={Jonathan Ben-Menachem; Kevin Morris},
   hidelinks,
@@
 \usepackage{setspace}
-\usepackage{lineno}
-\linenumbers
 \usepackage{booktabs}
@@
 
-\title{Turnout and Amendment 4: Mobilizing Eligible Voters Close to Formerly Incarcerated Floridians\thanks{Prepared for the 2021 Annual Meeting of the SPSA.
-Draft --- please do not circulate without permission.
-The author thanks Myrna Pérez, Patrick Berry, and Peter Miller for their comments on this project.
-All errors are my responsibility.}}
-\author{Kevin Morris\footnote{Researcher, Brennan Center for Justice at NYU School of Law, 120 Broadway Ste 1750, New York, NY 10271 (\href{mailto:kevin.morris@nyu.edu}{\nolinkurl{kevin.morris@nyu.edu}})}}
+\title{Policing for profit undermines democracy: Fines, Fees, and Voter Turnout}
+\author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jbenmenachem@gmail.com}{\nolinkurl{jbenmenachem@gmail.com}})} \and Kevin Morris\footnote{Researcher, Brennan Center for Justice at NYU School of Law (\href{mailto:kevin.morris@nyu.edu}{\nolinkurl{kevin.morris@nyu.edu}})}}
 \date{January 12, 2021}
@@
 \pagenumbering{arabic}
-\doublespacing
 
-\begin{figure}
+Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities' alienation from government.
+After Michael Brown was killed by the Ferguson Police Department in 2014, a US Department of Justice investigation into the city's police and courts demonstrated that the municipality was engaged in a practice that advocates now refer to as ``policing for profit.'' The city's reliance on fines and fees to fund government functions grew from 13 to 23 percent of the total budget between fiscal years 2012 and 2015 (United States Department of Justice 2015).
+Although a body of literature developed over the past decade indicates that criminalization chills political participation, no work has directly investigated the relationship between fines and fees revenue collection and voter turnout.
+This project intends to fill that gap.
+
+It wasn't just a Ferguson problem, or even a Missouri problem.
+American cities' reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (Singla, Kirschner, and Stone 2019, Mughan 2020, Kirk, Fernandes, and Friedman 2020, Martin 2018).
+
+Fines and fees practices disproportionately target Black Americans: city government reliance on fines and fees revenue is associated with larger Black populations, racial stereotypes affect the imposition of fines and fees, and Black defendants face more severe penalties related to monetary sanctions (United States Commission on Civil Rights 2017, Harris, Evans, and Beckett 2011, Edwards and Harris 2020).
+The relationship between cities' reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator, however (Sances and You 2017).
+This could suggest that higher reliance on fines and fees results from government officials targeting individuals who hold less political power (Makowsky and Stratmann 2009).
+
+Fines and fees legally disenfranchise Americans: 48 states and the District of Columbia authorize some form of wealth-based penal disenfranchisement (Colgan 2019).
+More specifically, many states require payment of fees as a condition of criminal legal supervision or the payment of all legal financial obligations as a condition of completing a sentence, and failure to comply with supervision conditions or sentence completion conditions can be a barrier to voting rights restoration.
+A recent report from the Sentencing Project estimates that more than 5 million Americans are legally barred from voting due to a felony conviction (Uggen et al 2020).
+
+Recent work from scholars in sociology and political science, however, indicates that many more voters are indirectly disenfranchised due to over-incarceration and the politically chilling effects of the carceral state.
+Policing and incarceration shape political socialization: personal contact with police or incarceration is associated with a reduced likelihood of political participation, and that alienating effect extends even to people who have incarcerated family members or who simply reside in affected communities (Lee, Porter, and Comfort 2014, Weaver and Lerman 2010; Morris 2020).
+This relationship may be more complicated, however.
+In New York City, concentrated policing was associated with reduced turnout in Congressional elections and increased turnout in the 2008 Presidential election as well as the local mayoral election in 2013 (Laniyonu 2019).
+It may also be the case that proximal contact differs from personal contact with the criminal legal system---whereas direct experience with criminalization (and incarceration in particular) reduces the likelihood of voting, proximal or indirect experience produces more mixed results.
+Hannah Walker suggests that police contact that does not lead to a criminal conviction may even mobilize voters---but her survey questions specifically excluded ``minor traffic stops,'' a primary site of police ticketing (Walker 2014).
+
+However, one of the most routine interactions Americans have with the police has gone largely unstudied: namely, ticketing for low-level offenses.
+Police ticketing practices may discourage potential voters without directly disenfranchising them, and ticketing affects more Americans than legal disenfranchisement.
+In 2018, more than 24 million people experienced police contact in the context of a traffic stop; by contrast, about 5.17 million people are disenfranchised as a result of a felony conviction (Harrell and Davis 2020, Uggen et al 2020).
+
+Ticketing practices may be related to distrust of government and reduced political participation.
+In a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government more broadly (Carpenter, Sweetland, and McDonald 2019).
+Lerman and Weaver have argued that residents' perceptions of law enforcement may affect their perceptions of government as a whole (Lerman and Weaver 2013).
+As one man told them, ``I feel like if I contact a senator or governor, they'll probably want to put me in jail and leave me as a troublemaker\ldots{} I try to basically stay away from government'' (Lerman and Weaver 2014).
+In their study of descriptive representation, Sances and You explicitly suggested that ``fines may make descriptive representation less likely by depressing minority turnout,'' and called for further research regarding voter turnout and the imposition of fines (Sances and You 2017).
+In this paper, we clarify that relationship.
+
+We begin by picking up where Sances, and You (2017) left off.
+By tying data from the Census of Governments to a national geocoded voter file we test whether municipalities with more fees and fines collected per resident saw lower turnout in the 2014, 2016, and 2018 general elections.
+We expect to find that municipalities where more revenue is raised per resident saw lower turnout, other things being equal.
+Because the American criminal legal system falls disproportionately on minorities, we also expect that the racial turnout gap (Fraga 2019 {[}NEED TO ADD CITE{]}) will be larger in municipalities that rely more heavily on fines and fees.
+
+Of course, fines and fees imposition may be related to turnout without necessarily indicating a causal relationship.
+To estimate the causal effect, we explore whether turnout increases or decreases in the wake of changes in city revenue collection policy.
+We explore this at the national level using the Census of Governments data, and also how turnout changed in {[}Buffalo{]} in the years following a dramatic increase in ticketing in that city.
+
+\hypertarget{data-and-design}{%
+\subsubsection*{Data and Design}\label{data-and-design}}
+\addcontentsline{toc}{subsubsection}{Data and Design}
+
+In order to ascertain whether fines and fees practices affect voter turnout, we exploit data from the 2013 and 2017 Census of Governments and national voter file data.
+The COG, a project of the US Census Bureau, collects budget data for all local governments every five years, and the most recent survey was in 2017.
+The COG asks cities how much revenue they collect from ``penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation .
+.
+.
+and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).'' As indicated by previous researchers, these data serve as a useful proxy for the prevalence of police ticketing (Goldstein, Sances, and You 2018, Sances and You 2017).
+
+Unfortunately, the COG data does not include voter turnout, and turnout data is not generally available at this level.
+Therefore, in order to determine municipality-level turnout, we employ a national, geocoded voter file.
+This voter file is provided by L2 Political, and includes a host of information about each voter, including age, party affiliation, racial estimates, and historical turnout.
+By using the latitude and longitude of every registered voter in the country and shapefiles provided by the Census Bureau, we map each voter to their home municipality using the same definitions as the COG.
+We then aggregate these individual-level records up to the municipality level to determine municipal turnout, measured as a share of registered voters.
+The full study will include other turnout denominators to avoid biased estimates arising from differential registration rates.
+
+Because the L2 national voter file includes estimates of each voter's racioethnic identity, we can also use these data to determine the racial turnout gap in each municipality.
+These records are just estimates, and may be imprecise at the individual level.
+However, we assume that this presents less of a problem when aggregating to the municipality-level.
+
+In order to control for potential confounders, we also control for a host of other information from the 5-year American Community Survey.
+
+Although we do not present these results in this abstract, we also intend to incorporate causal estimates in the full version of this study.
+We will begin by modelling changes in fees and fines reliance between the 2013 and 2017 COGs, and turnout in the 2014 and 2018 elections.
+We will also compare the turnout of voters in {[}Buffalo, New York{]} to voters in surrounding municipalities between {[}20XX{]} and {[}20XX{]}.
+{[}Buffalo{]} increased its reliance on fees and fines dramatically in this period, allowing us to directly observe whether a decrease in turnout followed this change.
+
+\hypertarget{results}{%
+\subsubsection*{Results}\label{results}}
+\addcontentsline{toc}{subsubsection}{Results}
+
+Figure 1 makes clear that there is a relationship between the fees and fines collected by a municipality and its turnout.The left hand panel shows the simple bivariate relationship between the two quantities.
+In the right hand panel, we present the marginal effects plot in lieu of a regression table due to space constraints.
+The second panel shows that, even after controlling for a municipality's racial composition, median income, collegiate education, age, and state fixed effects, there is a statistically significant, negative relationship between fees and fines and turnout in 2018.
+In these models, the dependent variable is municipal turnout in 2018 and the independent variable of interest is the natural log of the dollars in fees and fines per resident plus 1.
+
+\begin{figure}[H]
 \includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/figures-side-1} \includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/figures-side-2} \caption{\label{fig:marg1}Dollars per Resident and 2018 Turnout}\label{fig:figures-side}
@@
 
-\begin{figure}
+A 10 percent increase in the dollars of fees and fines raised per resident is associated with a reduction in turnout of 0.06 percentage points, and the relationship is significant at the 99 percent confidence level.
+Although this may seem small, Figure 1 shows that the range of fees and fines raised is large.
+The figure marks the 10th and 90th percentiles for revenue collected in fees and fines, and predicted turnout drops by 1.6 percentage points over this range.
+
+Figure 2 presents the results of preliminary analyses investigating the relationship between fees and fines collection and the racial turnout gap.
+Because the bivariate regression is not significant and the R2 is very small (\textless0.001) we refrain from including the line of best fit in the first panel.
+Our initial analysis indicates, however, that the relationship between fees and fines collection and the racial turnout gap in a municipality is moderated by its racial composition.
+The second panel of Figure 2 indicates the racial turnout gap is much larger in minority-white cities that collect no fees and fines than in whiter cities that also do not collect fees and fines.
+As fees and fines collections increase in less-white cities the turnout gap drops, though we see no such pattern in municipalities that are predominantly white.
+
+\begin{figure}[H]
 \includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/unnamed-chunk-1-1} \includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/unnamed-chunk-1-2} \caption{\label{fig:marg1}Dollars per Resident and 2018 Turnout Gap}\label{fig:unnamed-chunk-1}
@@
 
+\hypertarget{discussion}{%
+\subsubsection*{Discussion}\label{discussion}}
+\addcontentsline{toc}{subsubsection}{Discussion}
+
+The significant negative association in our analysis provides some support for our hypothesis: though our preliminary analyses cannot establish causality, they are consistent with a causal story that links fines and fees practices with lower political participation among those who are subjected to them.
+On the other hand, officials in municipalities with lower turnout may feel more free to rely on fees and fines for revenue collection because they have less fear of electoral repercussions.
+Our full study will explore these causal relationships directly by supplementing our initial analysis with an analysis of voter turnout and revenue reliance change over time.
+
+That the racial turnout gap is more sensitive to fees and fines collection in municipalities with a smaller white share of the population is somewhat surprising.
+This could reflect racially disparate policing in cities with large nonwhite populations.
+It is possible that cities with many nonwhite residents and low fees and fines collections disproportionately penalize nonwhite residents; as fees and fines collections increase, however, a larger share of the population - and, thus, more white voters - may be swept into these programs, thereby reducing racial disparities and consequently discrepancies in the racial turnout gap.
+
+Our full study will also include an analysis of racial disparities in voter turnout using data from states where race is included in the voter file (North Carolina, Georgia, or Florida).
+In other words, is Black voter turnout more depressed in cities with greater fines and fees reliance?
+
+Future research could include a more narrow analysis of turnout in jurisdictions that dramatically increased or decreased ticketing over a comparatively short period of time.
+For instance, a Florida Times-Union investigation revealed that police in four counties disproportionately issued tickets to Black pedestrians (Sanders and Conarck 2017).
+In Tampa, police issued thousands of tickets to Black cyclists between 2012 and 2015---after journalists reported on the problem, the city began to issue fewer than 100 citations each year as of 2018 (Zayas 2015, Frago 2019).
+Systematically conducting such an analysis would likely require collecting and organizing new data, as city-level police ticketing data is inconsistent and not always public information.
+
 \end{document}

### 2021-01-12 markdown/fees_fines_to.Rmd
asa abstract

@@
 subtitle: ""
-thanks: 
+thanks: The authors thank XX for their feedback and support. All errors are our responsibility. 
 author:
@@
     - \usepackage{setspace}
-abstract: ""
+abstract: "This is an abstract."
 ---

### 2021-01-13 code/03_regs.R
change figures

@@ -12,21 +12,21 @@ full_set <- inner_join(cog, to, by = c("GEOID" = "plasub"))
 
 p1 <- ggplot(full_set, aes(x = lndper, y = to_18)) + geom_point(shape = 1) + geom_smooth(method = "lm") +
   xlab("Dollars per Resident") +
-  ylab("Turnout in 2018") + scale_x_continuous(breaks = c(log(2), log(11), log(101), log(1001)),
-                                                                           labels = c("$1", "$10", "$100", "$1,000")) +
+  ylab("Turnout in 2018") + scale_x_continuous(breaks = c(log(1), log(2), log(11), log(101), log(201)),
+                                                                           labels = c("$0", "$1", "$10", "$100", "$200")) +
   scale_y_continuous(labels = percent) +
   theme_bw() + theme(plot.caption = element_text(hjust = 0),
                      text = element_text(family = "LM Roman 10")) +
-  coord_cartesian(xlim = c(-.3, log(1001))) +
+  coord_cartesian(xlim = c(0, log(201))) +
   labs(caption = "
        
        ")
-
+p1
 m1 <- lm.cluster(to_18 ~ lndper + nh_white + nh_black + latino +
            median_income + some_college + median_age + share_over_64 +
            state, data = full_set, cluster = full_set$state)
 
-m2 <- lm(to_18 ~ lndper + nh_white +  + latino +
+m2 <- lm(to_18 ~ lndper + nh_white + nh_black + latino +
            median_income + some_college + median_age + share_over_64 +
            state, full_set)
 
@@ -37,35 +37,49 @@ marg <- ggeffect(m2, "lndper [all]", vcov.fun = "vcovCR", vcov.type = "CR0",
                  vcov.args = list(cluster = full_set$state))
 
 
+bars <- data.frame(x = c(quantile(full_set$lndper, 0.1),
+                         quantile(full_set$lndper, 0.9)),
+                   y = c(
+                     filter(marg,
+                            x == round(quantile(full_set$lndper, 0.1), digits = 3)) %>% 
+                       select(predicted) %>% 
+                       pull(),
+                     filter(marg,
+                            x == round(quantile(full_set$lndper, 0.9), digits = 3)) %>% 
+                       select(predicted) %>% 
[…]

### 2021-01-13 markdown/fees_fines_to.Rmd
write (asa abstract)

--- 2021-01-12 markdown/fees_fines_to.Rmd
@@
 ---
-title: "Turnout and Amendment 4: Mobilizing Eligible Voters Close to Formerly Incarcerated Floridians"
-subtitle: ""
-thanks: Prepared for the 2021 Annual Meeting of the SPSA.
-Draft --- please do not circulate without permission.
-The author thanks Myrna Pérez, Patrick Berry, and Peter Miller for their comments on this project.
-All errors are my responsibility.
-author: Kevin Morris^[Researcher, Brennan Center for Justice at NYU School of Law, 120 Broadway Ste 1750, New York, NY 10271 (kevin.morris@nyu.edu)]
-institute: "Brennan Center for Justice"
+title: "Policing for Profit and the Undermining of Democracy"
+subtitle: "Fines, Fees, and Turnout"
+thanks: The authors thank XX for their feedback and support. All errors are our responsibility. 
+author:
+- Jonathan Ben-Menachem^[PhD Student, Columbia University, Department of Sociology (jbenmenachem@gmail.com)]
+- Kevin Morris^[Researcher, Brennan Center for Justice at NYU School of Law (kevin.morris@nyu.edu)]
 date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
     keep_tex: true
+bibliography: "policing_turnout.bib"
 link-citations: yes
@@
     - \usepackage{setspace}
-    - \usepackage{lineno}
-    - \linenumbers
-abstract: ""
+abstract: "This is an abstract."
 ---
@@
 \pagenumbering{arabic}
-\doublespacing
+\begin{center}
+Policing for Profit and the Undermining of Democracy: Fines, Fees, and Turnout \\
+Jonathan Ben-Menachem and Kevin Morris
+\end{center}
 
-```{r, figures-side, fig.show="hold", out.width="50%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:marg1}Dollars per Resident and 2018 Turnout"}
+Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities’ alienation from government.
+After Michael Brown was killed by the Ferguson Police Department in 2014, a US Department of Justice investigation into the city’s police and courts demonstrated that the municipality was engaged in a practice that advocates now refer to as “policing for profit.” The city’s reliance on fines and fees to fund government functions grew from 13 to 23 percent of the total budget between fiscal years 2012 and 2015 [@UnitedStatesDepartmentofJusticeCivilRightsDivision2015].
+Although a body of literature developed over the past decade indicates that criminalization chills political participation, no work has directly investigated the relationship between fines and fees revenue collection and voter turnout.
+This project intends to fill that gap.
+
+It wasn’t just a Ferguson problem, or even a Missouri problem.
+American cities’ reliance on fines and fees revenue increased significantly following the 2008 recession—as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services [@Singla2020; @Mughan2020; @Kirk2020; @Martin2018].
+
+Fines and fees practices disproportionately target Black Americans: city government reliance on fines and fees revenue is associated with larger Black populations, racial stereotypes affect the imposition of fines and fees, and Black defendants face more severe penalties related to monetary sanctions [@UnitedStatesCommissiononCivilRights2017; @Harris2011; @Edwards2020].
+The relationship between cities’ reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator, however [@Sances2017].
+This could suggest that higher reliance on fines and fees results from government officials targeting individuals who hold less political power [@Makowsky2009].
+
+Fines and fees legally disenfranchise Americans: 48 states and the District of Columbia authorize some form of wealth-based penal disenfranchisement [@Colgan2019].
+More specifically, many states require payment of fees as a condition of criminal legal supervision or the payment of all legal financial obligations as a condition of completing a sentence, and failure to comply with supervision conditions or sentence completion conditions can be a barrier to voting rights restoration.
+A recent report from the Sentencing Project estimates that more than 5 million Americans are legally barred from voting due to a felony conviction [@Uggen2020], and the role of fees and fines in the context of felony disenfranchisement has taken on greater significance in the past year.
+After Floridians voted to restore voting rights to individuals with felony convictions, Florida legislators passed legislation requiring these individuals to pay off the fees and fines associated with their original sentence.
+Because Florida does not maintain good records on who owes how much, this has proved a major hurdle for would-be voters.
+
+Recent work from scholars in sociology and political science, however, indicates that many more voters are *indirectly* disenfranchised due to over-incarceration and the politically chilling effects of the carceral state.
+Policing and incarceration shape political socialization: personal contact with police or incarceration is associated with a reduced likelihood of political participation, and that alienating effect extends even to people who have incarcerated family members or who simply reside in affected communities [@Lee2014; @Weaver2010; @Morris2020].
+This relationship may be more complicated, however.
+In New York City, concentrated policing was associated with reduced turnout in Congressional elections and increased turnout in the 2008 Presidential election as well as the local mayoral election in 2013 [@Laniyonu2019].
+It may also be the case that proximal contact differs from personal contact with the criminal legal system—whereas direct experience with criminalization (and incarceration in particular) reduces the likelihood of voting, proximal or indirect experience produces more mixed results.
+Hannah Walker suggests that police contact that does not lead to a criminal conviction may even mobilize voters—but her survey questions specifically excluded “minor traffic stops,” a primary site of police ticketing [@Walker2014].
+
+However, one of the most routine interactions Americans have with the police has gone largely unstudied: namely, ticketing for low-level offenses.
+Police ticketing practices may discourage potential voters without directly disenfranchising them, and ticketing affects more Americans than legal disenfranchisement.
+In 2018, more than 24 million people experienced police contact in the context of a traffic stop; by contrast, about 5.17 million people are disenfranchised as a result of a felony conviction [@Harrell2020; @Uggen2020].
+
+Ticketing practices may be related to distrust of government and reduced political participation.
+In a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government more broadly [@CarpenterII2019].
+Lerman and Weaver have argued that residents’ perceptions of law enforcement may affect their perceptions of government as a whole.
+As one man told them, “I feel like if I contact a senator or governor, they’ll probably want to put me in jail and leave me as a troublemaker...
+I try to basically stay away from government” [-@Lerman2014].
+In their study of descriptive representation, Sances and You [-@Sances2017] explicitly suggested that “fines may make descriptive representation less likely by depressing minority turnout,” and called for further research regarding voter turnout and the imposition of fines.
+In this paper, we clarify that relationship.
+
+We begin by picking up where @Sances2017 left off.
+By tying data from the Census of Governments to a national geocoded voter file we test whether municipalities with more fees and fines collected per resident saw lower turnout in the 2014, 2016, and 2018 general elections.
+We expect to find that municipalities where more revenue is raised per resident saw lower turnout, other things being equal.
+Because the American criminal legal system falls disproportionately on minorities, we also expect that the racial turnout gap [@Fraga2018] will be larger in municipalities that rely more heavily on fines and fees.
+
+Of course, fines and fees imposition may be related to turnout without necessarily indicating a causal relationship.
+To estimate the causal effect, we will explore whether turnout increases or decreases in the wake of changes in city revenue collection policy.
+
+### Data and Design {-}
+
+In order to ascertain whether fines and fees practices affect voter turnout, we exploit data from the 2013 and 2017 Census of Governments (COG) and national voter file data.
+The COG, a project of the US Census Bureau, collects budget data for all local governments every five years, and the most recent survey was in 2017.
+The COG asks cities how much revenue they collect from “penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation...
+and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).” As indicated by previous researchers, these data serve as a useful proxy for the prevalence of police ticketing [@Goldstein2020; @Sances2017].
+
+Unfortunately, the COG data does not include voter turnout, and turnout data is not generally available at this level.
+Therefore, in order to determine municipality-level turnout, we employ a national, geocoded voter file.
+This voter file is provided by L2 Political, and includes a host of information about each voter, including age, party affiliation, racial estimates, and historical turnout.
+By using the latitude and longitude of every registered voter in the country and shapefiles provided by the Census Bureau, we map each voter to their home municipality using the same definitions as the COG.^[Although the registered voter file includes the name of the city in which the voter is registered, these do not always map neatly to the municipalities defined in the COG data.
+The use of these shapefiles ensures an apples-to-apples comparison.] We then aggregate these individual-level records up to the municipality level to determine municipal turnout, measured as a share of registered voters.
+The full study will include other turnout denominators to avoid biased estimates arising from differential registration rates.
+
+Because the L2 national voter file includes estimates of each voter’s racioethnic identity, we can also use these data to determine the *racial turnout gap* in each municipality.
+These records are just estimates, and may be imprecise at the individual level.
+However, we assume that this presents less of a problem when aggregating to the municipality-level.
+In order to control for potential confounders, we also control for a host of other information from the 5-year American Community Survey.
+
+Although we do not present these results in this abstract, we also intend to incorporate causal estimates in the full version of this study by using changes in fees and fines reliance between the 2013 and 2017 COGs, and turnout in the 2014 and 2018 elections.
+
+### Results {-}
+
+Figure \ref{fig:marg1} makes clear that there is a relationship between the fees and fines collected by a municipality and its turnout.
+The left hand panel shows the simple bivariate relationship between the two quantities.
+In the right hand panel, we present the marginal effects plot in lieu of a regression table due to space constraints.
+The second panel shows that, even after controlling for a municipality’s racial composition, median income, collegiate education, age, and state fixed effects, there is a statistically significant, negative relationship between fees and fines and turnout in 2018.
+In these models, the dependent variable is municipal turnout in 2018 and the independent variable of interest is the natural log of the dollars in fees and fines per resident plus 1.
+
+```{r, figures-side, fig.show="hold", out.width="50%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:marg1}Dollars per Resident and 2018 Turnout", fig.pos = "H"}
 p1 <- readRDS("./temp/simple_scat.rds")
@@
 
-```{r, fig.show="hold", out.width="50%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:marg1}Dollars per Resident and 2018 Turnout Gap"}
+All else equal, a 10 percent increase in the dollars of fees and fines raised per resident is associated with a reduction in turnout of 0.06 percentage points, and the relationship is significant at the 99 percent confidence level.
+Although this may seem small, Figure \ref{fig:marg1} shows that the range of fees and fines raised is large.
+The figure marks the 10th and 90th percentiles for revenue collected in fees and fines, and predicted turnout drops by 1.8 percentage points over this range.
+
+Figure \ref{fig:marg2} presents the results of preliminary analyses investigating the relationship between fees and fines collection and the racial turnout gap.^[Because we are interested in the racial turnout gap, we include only cities where the population is less than 90 percent non-Hispanic white.] Because the bivariate regression is not statistically significant and the *R^2^* is very small (<0.001) we refrain from including the line of best fit in the first panel.
+Our initial analysis indicates, however, that the relationship between fees and fines collection and the racial turnout gap in a municipality is moderated by its racial composition.
+The second panel of Figure \ref{fig:marg2} indicates the racial turnout gap is much larger in minority-white cities that collect no fees and fines than in whiter cities that also do not collect fees and fines.
+As fees and fines collections increase in less-white cities the turnout gap drops, though we see no such pattern in municipalities that are predominantly white.
+As in Figure \ref{fig:marg1}, we mark the 10th and 90th percentiles.
+
+```{r, fig.show="hold", out.width="50%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:marg2}Dollars per Resident and 2018 Turnout Gap", fig.pos = "H"}
 p3 <- readRDS("./temp/simple_scat_gap.rds")
@@
 ```
+
+### Discussion {-}
+
+The significant negative association in our analysis provides some support for our hypothesis: though our preliminary analyses cannot establish causality, they are consistent with a causal story that links fines and fees practices with lower political participation among those who are subjected to them.
+On the other hand, officials in municipalities with lower turnout may feel more free to rely on fees and fines for revenue collection because they have less fear of electoral repercussions.
+Our full study will explore these causal relationships directly by supplementing our initial analysis with an analysis of voter turnout and revenue reliance change over time.
+
+That the racial turnout gap is more sensitive to fees and fines collection in municipalities with a smaller white share of the population is somewhat surprising.
+This could reflect racially disparate policing in cities with large nonwhite populations.
+It is possible that cities with many nonwhite residents and *low* fees and fines collections disproportionately penalize nonwhite residents; as fees and fines collections increase, however, a larger share of the population - and, thus, more white voters - may be swept into these programs, thereby *reducing* racial disparities and consequently discrepancies in the racial turnout gap.
+
+Our full study will include a more narrow analysis of turnout in jurisdictions that dramatically increased or decreased ticketing over a comparatively short period of time.
+For instance, a Florida Times-Union investigation revealed that police in four counties disproportionately issued tickets to Black pedestrians [@Sanders2017].
+In Tampa, police issued thousands of tickets to Black cyclists between 2012 and 2015—after journalists reported on the problem, the city began to issue fewer than 100 citations each year as of 2018 [@Zayas2015; @Frago2019].
+Systematically conducting such an analysis would likely require collecting and organizing new data, as city-level police ticketing data is inconsistent and not always public information.
+
+\newpage
+### Bibliography

### 2021-01-13 markdown/fees_fines_to.tex
asa abstract
write (asa abstract)

--- 2021-01-12 markdown/fees_fines_to.tex
@@
 \hypersetup{
-  pdftitle={Turnout and Amendment 4: Mobilizing Eligible Voters Close to Formerly Incarcerated Floridians},
-  pdfauthor={Kevin Morris},
+  pdftitle={Policing for Profit and the Undermining of Democracy},
+  pdfauthor={Jonathan Ben-Menachem; Kevin Morris},
   hidelinks,
@@
 \usepackage{xcolor}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newenvironment{cslreferences}%
+  {\setlength{\parindent}{0pt}%
+  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
+  {\par}
 
-\title{Turnout and Amendment 4: Mobilizing Eligible Voters Close to Formerly Incarcerated Floridians\thanks{Prepared for the 2021 Annual Meeting of the SPSA.
-Draft --- please do not circulate without permission.
-The author thanks Myrna Pérez, Patrick Berry, and Peter Miller for their comments on this project.
-All errors are my responsibility.}}
-\author{Kevin Morris\footnote{Researcher, Brennan Center for Justice at NYU School of Law, 120 Broadway Ste 1750, New York, NY 10271 (\href{mailto:kevin.morris@nyu.edu}{\nolinkurl{kevin.morris@nyu.edu}})}}
-\date{January 12, 2021}
+\title{Policing for Profit and the Undermining of Democracy\thanks{The authors thank XX for their feedback and support. All errors are our responsibility.}}
+\usepackage{etoolbox}
+\makeatletter
+\providecommand{\subtitle}[1]{% add subtitle to \maketitle
+  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
+}
+\makeatother
+\subtitle{Fines, Fees, and Turnout}
+\author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jbenmenachem@gmail.com}{\nolinkurl{jbenmenachem@gmail.com}})} \and Kevin Morris\footnote{Researcher, Brennan Center for Justice at NYU School of Law (\href{mailto:kevin.morris@nyu.edu}{\nolinkurl{kevin.morris@nyu.edu}})}}
+\date{January 13, 2021}
 
@@
 \maketitle
+\begin{abstract}
+This is an abstract.
+\end{abstract}
 
@@
 \pagenumbering{arabic}
-\doublespacing
+\begin{center}
+Policing for Profit and the Undermining of Democracy: Fines, Fees, and Turnout \\
+Jonathan Ben-Menachem and Kevin Morris
+\end{center}
 
-\begin{figure}
+Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities' alienation from government.
+After Michael Brown was killed by the Ferguson Police Department in 2014, a US Department of Justice investigation into the city's police and courts demonstrated that the municipality was engaged in a practice that advocates now refer to as ``policing for profit.'' The city's reliance on fines and fees to fund government functions grew from 13 to 23 percent of the total budget between fiscal years 2012 and 2015 (United States Department of Justice Civil Rights Division \protect\hyperlink{ref-UnitedStatesDepartmentofJusticeCivilRightsDivision2015}{2015}).
+Although a body of literature developed over the past decade indicates that criminalization chills political participation, no work has directly investigated the relationship between fines and fees revenue collection and voter turnout.
+This project intends to fill that gap.
+
+It wasn't just a Ferguson problem, or even a Missouri problem.
+American cities' reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (Singla, Kirschner, and Stone \protect\hyperlink{ref-Singla2020}{2020}; Mughan \protect\hyperlink{ref-Mughan2020}{2020}; Kirk, Fernandes, and Friedman \protect\hyperlink{ref-Kirk2020}{2020}; Martin \protect\hyperlink{ref-Martin2018}{2018}).
+
+Fines and fees practices disproportionately target Black Americans: city government reliance on fines and fees revenue is associated with larger Black populations, racial stereotypes affect the imposition of fines and fees, and Black defendants face more severe penalties related to monetary sanctions (United States Commission on Civil Rights \protect\hyperlink{ref-UnitedStatesCommissiononCivilRights2017}{2017}; Harris, Evans, and Beckett \protect\hyperlink{ref-Harris2011}{2011}; Edwards and Harris \protect\hyperlink{ref-Edwards2020}{n.d.}).
+The relationship between cities' reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator, however (Sances and You \protect\hyperlink{ref-Sances2017}{2017}).
+This could suggest that higher reliance on fines and fees results from government officials targeting individuals who hold less political power (Makowsky and Stratmann \protect\hyperlink{ref-Makowsky2009}{2009}).
+
+Fines and fees legally disenfranchise Americans: 48 states and the District of Columbia authorize some form of wealth-based penal disenfranchisement (Colgan \protect\hyperlink{ref-Colgan2019}{2019}).
+More specifically, many states require payment of fees as a condition of criminal legal supervision or the payment of all legal financial obligations as a condition of completing a sentence, and failure to comply with supervision conditions or sentence completion conditions can be a barrier to voting rights restoration.
+A recent report from the Sentencing Project estimates that more than 5 million Americans are legally barred from voting due to a felony conviction (Uggen et al.
+\protect\hyperlink{ref-Uggen2020}{2020}), and the role of fees and fines in the context of felony disenfranchisement has taken on greater significance in the past year.
+After Floridians voted to restore voting rights to individuals with felony convictions, Florida legislators passed legislation requiring these individuals to pay off the fees and fines associated with their original sentence.
+Because Florida does not maintain good records on who owes how much, this has proved a major hurdle for would-be voters.
+
+Recent work from scholars in sociology and political science, however, indicates that many more voters are \emph{indirectly} disenfranchised due to over-incarceration and the politically chilling effects of the carceral state.
+Policing and incarceration shape political socialization: personal contact with police or incarceration is associated with a reduced likelihood of political participation, and that alienating effect extends even to people who have incarcerated family members or who simply reside in affected communities (Lee, Porter, and Comfort \protect\hyperlink{ref-Lee2014}{2014}; Weaver and Lerman \protect\hyperlink{ref-Weaver2010}{2010}; Morris \protect\hyperlink{ref-Morris2020}{2020}).
+This relationship may be more complicated, however.
+In New York City, concentrated policing was associated with reduced turnout in Congressional elections and increased turnout in the 2008 Presidential election as well as the local mayoral election in 2013 (Laniyonu \protect\hyperlink{ref-Laniyonu2019}{2019}).
+It may also be the case that proximal contact differs from personal contact with the criminal legal system---whereas direct experience with criminalization (and incarceration in particular) reduces the likelihood of voting, proximal or indirect experience produces more mixed results.
+Hannah Walker suggests that police contact that does not lead to a criminal conviction may even mobilize voters---but her survey questions specifically excluded ``minor traffic stops,'' a primary site of police ticketing (Walker \protect\hyperlink{ref-Walker2014}{2014}).
+
+However, one of the most routine interactions Americans have with the police has gone largely unstudied: namely, ticketing for low-level offenses.
+Police ticketing practices may discourage potential voters without directly disenfranchising them, and ticketing affects more Americans than legal disenfranchisement.
+In 2018, more than 24 million people experienced police contact in the context of a traffic stop; by contrast, about 5.17 million people are disenfranchised as a result of a felony conviction (Harrell and Davis \protect\hyperlink{ref-Harrell2020}{2020}; Uggen et al.
+\protect\hyperlink{ref-Uggen2020}{2020}).
+
+Ticketing practices may be related to distrust of government and reduced political participation.
+In a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government more broadly (Carpenter II, Sweetland, and McDonald \protect\hyperlink{ref-CarpenterII2019}{2019}).
+Lerman and Weaver have argued that residents' perceptions of law enforcement may affect their perceptions of government as a whole.
+As one man told them, ``I feel like if I contact a senator or governor, they'll probably want to put me in jail and leave me as a troublemaker\ldots{} I try to basically stay away from government'' (\protect\hyperlink{ref-Lerman2014}{2014}).
+In their study of descriptive representation, Sances and You (\protect\hyperlink{ref-Sances2017}{2017}) explicitly suggested that ``fines may make descriptive representation less likely by depressing minority turnout,'' and called for further research regarding voter turnout and the imposition of fines.
+In this paper, we clarify that relationship.
+
+We begin by picking up where Sances and You (\protect\hyperlink{ref-Sances2017}{2017}) left off.
+By tying data from the Census of Governments to a national geocoded voter file we test whether municipalities with more fees and fines collected per resident saw lower turnout in the 2014, 2016, and 2018 general elections.
+We expect to find that municipalities where more revenue is raised per resident saw lower turnout, other things being equal.
+Because the American criminal legal system falls disproportionately on minorities, we also expect that the racial turnout gap (Fraga \protect\hyperlink{ref-Fraga2018}{2018}) will be larger in municipalities that rely more heavily on fines and fees.
+
+Of course, fines and fees imposition may be related to turnout without necessarily indicating a causal relationship.
+To estimate the causal effect, we will explore whether turnout increases or decreases in the wake of changes in city revenue collection policy.
+
+\hypertarget{data-and-design}{%
+\subsubsection*{Data and Design}\label{data-and-design}}
+\addcontentsline{toc}{subsubsection}{Data and Design}
+
+In order to ascertain whether fines and fees practices affect voter turnout, we exploit data from the 2013 and 2017 Census of Governments (COG) and national voter file data.
+The COG, a project of the US Census Bureau, collects budget data for all local governments every five years, and the most recent survey was in 2017.
+The COG asks cities how much revenue they collect from ``penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation\ldots{} and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).'' As indicated by previous researchers, these data serve as a useful proxy for the prevalence of police ticketing (Goldstein, Sances, and You \protect\hyperlink{ref-Goldstein2020}{2020}; Sances and You \protect\hyperlink{ref-Sances2017}{2017}).
+
+Unfortunately, the COG data does not include voter turnout, and turnout data is not generally available at this level.
+Therefore, in order to determine municipality-level turnout, we employ a national, geocoded voter file.
+This voter file is provided by L2 Political, and includes a host of information about each voter, including age, party affiliation, racial estimates, and historical turnout.
+By using the latitude and longitude of every registered voter in the country and shapefiles provided by the Census Bureau, we map each voter to their home municipality using the same definitions as the COG.\footnote{Although the registered voter file includes the name of the city in which the voter is registered, these do not always map neatly to the municipalities defined in the COG data.
+The use of these shapefiles ensures an apples-to-apples comparison.} We then aggregate these individual-level records up to the municipality level to determine municipal turnout, measured as a share of registered voters.
+The full study will include other turnout denominators to avoid biased estimates arising from differential registration rates.
+
+Because the L2 national voter file includes estimates of each voter's racioethnic identity, we can also use these data to determine the \emph{racial turnout gap} in each municipality.
+These records are just estimates, and may be imprecise at the individual level.
+However, we assume that this presents less of a problem when aggregating to the municipality-level.
+In order to control for potential confounders, we also control for a host of other information from the 5-year American Community Survey.
+
+Although we do not present these results in this abstract, we also intend to incorporate causal estimates in the full version of this study by using changes in fees and fines reliance between the 2013 and 2017 COGs, and turnout in the 2014 and 2018 elections.
+
+\hypertarget{results}{%
+\subsubsection*{Results}\label{results}}
+\addcontentsline{toc}{subsubsection}{Results}
+
+Figure \ref{fig:marg1} makes clear that there is a relationship between the fees and fines collected by a municipality and its turnout.
+The left hand panel shows the simple bivariate relationship between the two quantities.
+In the right hand panel, we present the marginal effects plot in lieu of a regression table due to space constraints.
+The second panel shows that, even after controlling for a municipality's racial composition, median income, collegiate education, age, and state fixed effects, there is a statistically significant, negative relationship between fees and fines and turnout in 2018.
+In these models, the dependent variable is municipal turnout in 2018 and the independent variable of interest is the natural log of the dollars in fees and fines per resident plus 1.
+
+\begin{figure}[H]
 \includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/figures-side-1} \includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/figures-side-2} \caption{\label{fig:marg1}Dollars per Resident and 2018 Turnout}\label{fig:figures-side}
@@
 
-\begin{figure}
-\includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/unnamed-chunk-1-1} \includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/unnamed-chunk-1-2} \caption{\label{fig:marg1}Dollars per Resident and 2018 Turnout Gap}\label{fig:unnamed-chunk-1}
+All else equal, a 10 percent increase in the dollars of fees and fines raised per resident is associated with a reduction in turnout of 0.06 percentage points, and the relationship is significant at the 99 percent confidence level.
+Although this may seem small, Figure \ref{fig:marg1} shows that the range of fees and fines raised is large.
+The figure marks the 10th and 90th percentiles for revenue collected in fees and fines, and predicted turnout drops by 1.8 percentage points over this range.
+
+Figure \ref{fig:marg2} presents the results of preliminary analyses investigating the relationship between fees and fines collection and the racial turnout gap.\footnote{Because we are interested in the racial turnout gap, we include only cities where the population is less than 90 percent non-Hispanic white.} Because the bivariate regression is not statistically significant and the \emph{R\textsuperscript{2}} is very small (\textless0.001) we refrain from including the line of best fit in the first panel.
+Our initial analysis indicates, however, that the relationship between fees and fines collection and the racial turnout gap in a municipality is moderated by its racial composition.
+The second panel of Figure \ref{fig:marg2} indicates the racial turnout gap is much larger in minority-white cities that collect no fees and fines than in whiter cities that also do not collect fees and fines.
+As fees and fines collections increase in less-white cities the turnout gap drops, though we see no such pattern in municipalities that are predominantly white.
+As in Figure \ref{fig:marg1}, we mark the 10th and 90th percentiles.
+
+\begin{figure}[H]
+\includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/unnamed-chunk-1-1} \includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/unnamed-chunk-1-2} \caption{\label{fig:marg2}Dollars per Resident and 2018 Turnout Gap}\label{fig:unnamed-chunk-1}
 \end{figure}
 
+\hypertarget{discussion}{%
+\subsubsection*{Discussion}\label{discussion}}
+\addcontentsline{toc}{subsubsection}{Discussion}
+
+The significant negative association in our analysis provides some support for our hypothesis: though our preliminary analyses cannot establish causality, they are consistent with a causal story that links fines and fees practices with lower political participation among those who are subjected to them.
+On the other hand, officials in municipalities with lower turnout may feel more free to rely on fees and fines for revenue collection because they have less fear of electoral repercussions.
+Our full study will explore these causal relationships directly by supplementing our initial analysis with an analysis of voter turnout and revenue reliance change over time.
+
+That the racial turnout gap is more sensitive to fees and fines collection in municipalities with a smaller white share of the population is somewhat surprising.
+This could reflect racially disparate policing in cities with large nonwhite populations.
+It is possible that cities with many nonwhite residents and \emph{low} fees and fines collections disproportionately penalize nonwhite residents; as fees and fines collections increase, however, a larger share of the population - and, thus, more white voters - may be swept into these programs, thereby \emph{reducing} racial disparities and consequently discrepancies in the racial turnout gap.
+
+Our full study will include a more narrow analysis of turnout in jurisdictions that dramatically increased or decreased ticketing over a comparatively short period of time.
+For instance, a Florida Times-Union investigation revealed that police in four counties disproportionately issued tickets to Black pedestrians (Sanders and Conark \protect\hyperlink{ref-Sanders2017}{2017}).
+In Tampa, police issued thousands of tickets to Black cyclists between 2012 and 2015---after journalists reported on the problem, the city began to issue fewer than 100 citations each year as of 2018 (Zayas \protect\hyperlink{ref-Zayas2015}{2015}; Frago \protect\hyperlink{ref-Frago2019}{2019}).
+Systematically conducting such an analysis would likely require collecting and organizing new data, as city-level police ticketing data is inconsistent and not always public information.
+
+\newpage
+
+\hypertarget{bibliography}{%
+\subsubsection*{Bibliography}\label{bibliography}}
+\addcontentsline{toc}{subsubsection}{Bibliography}
+
+\hypertarget{refs}{}
+\begin{cslreferences}
+\leavevmode\hypertarget{ref-CarpenterII2019}{}%
+Carpenter II, Dick M, Kyle Sweetland, and Jennifer McDonald.
+2019.
+``The Price of Taxation by Citation: Case Studies of Three Georgia Cities That Rely Heavily on Fines and Fees.'' Institute for Justice.
+
+\leavevmode\hypertarget{ref-Colgan2019}{}%
+Colgan, Beth A. 2019. ``Wealth-Based Penal Disenfranchisement.'' \emph{Vanderbilt Law Review} 72 (1:55). \url{https://papers.ssrn.com/abstract=3312439}.
+
+\leavevmode\hypertarget{ref-Edwards2020}{}%
+Edwards, Frank, and Alexes Harris.
+n.d.
+``An Analysis of Court Imposed Monetary Sanctions in Seattle Municipal Courts, 2000-2017.'' Accessed January 13, 2021.
+\url{https://doi.org/10.31235/osf.io/ajpqc}.
+
+\leavevmode\hypertarget{ref-Fraga2018}{}%
+Fraga, Bernard L. 2018. \emph{The Turnout Gap: Race, Ethnicity, and Political Inequality in a Diversifying America}. 1st ed. Cambridge University Press. \url{https://doi.org/10.1017/9781108566483}.
+
+\leavevmode\hypertarget{ref-Frago2019}{}%
+Frago, Charlie.
+2019.
+``Tampa Police Have `Evolved' on Biking While Black, Chief Says.'' \emph{Tampa Bay Times}, October 24, 2019.
+\url{https://www.tampabay.com/news/tampa/2019/10/24/tampa-police-have-evolved-on-biking-while-black-chief-says/}.
+
+\leavevmode\hypertarget{ref-Goldstein2020}{}%
+Goldstein, Rebecca, Michael W.
+Sances, and Hye Young You.
+2020.
+``Exploitative Revenues, Law Enforcement, and the Quality of Government Service.'' \emph{Urban Affairs Review} 56 (1): 5--31.
+\url{https://doi.org/10.1177/1078087418791775}.
+
+\leavevmode\hypertarget{ref-Harrell2020}{}%
+Harrell, Erika, and Elizabeth Davis.
+2020.
+``Contacts Between Police and the Public, 2018 - Statistical Tables.'' Bureau of Justice Statistics.
+\url{https://www.bjs.gov/index.cfm?ty=pbdetail\&iid=7167}.
+
+\leavevmode\hypertarget{ref-Harris2011}{}%
+Harris, Alexes, Heather Evans, and Katherine Beckett.
+2011.
+``Courtesy Stigma and Monetary Sanctions: Toward a Socio-Cultural Theory of Punishment.'' \emph{American Sociological Review} 76 (2): 234--64.
+\url{https://doi.org/10.1177/0003122411400054}.
+
+\leavevmode\hypertarget{ref-Kirk2020}{}%
+Kirk, Gabriela, April Fernandes, and Brittany Friedman.
+2020.
+``Who Pays for the Welfare State?
+Austerity Politics and the Origin of Pay-to-Stay Fees as Revenue Generation.'' \emph{Sociological Perspectives} 63 (6): 921--38.
+\url{https://doi.org/10.1177/0731121420967037}.
+
+\leavevmode\hypertarget{ref-Laniyonu2019}{}%
+Laniyonu, Ayobami. 2019. ``The Political Consequences of Policing: Evidence from New York City.'' \emph{Political Behavior} 41 (2): 527--58. \url{https://doi.org/10.1007/s11109-018-9461-9}.
+
+\leavevmode\hypertarget{ref-Lee2014}{}%
+Lee, Hedwig, Lauren C.
+Porter, and Megan Comfort.
+2014.
+``Consequences of Family Member Incarceration: Impacts on Civic Participation and Perceptions of the Legitimacy and Fairness of Government.'' \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 44--73.
+\url{https://doi.org/10.1177/0002716213502920}.
+
+\leavevmode\hypertarget{ref-Lerman2014}{}%
+Lerman, Amy E., and Vesla M.
+Weaver.
+2014.
+\emph{Arresting Citizenship: The Democratic Consequences of American Crime Control}.
+Chicago Studies in American Politics.
+Chicago ; London: The University of Chicago Press.
+
+\leavevmode\hypertarget{ref-Makowsky2009}{}%
+Makowsky, Michael D., and Thomas Stratmann.
+2009.
+``Political Economy at Any Speed: What Determines Traffic Citations?'' \emph{The American Economic Review} 99 (1): 509--27.
+\url{http://www.jstor.org/stable/29730194}.
+
+\leavevmode\hypertarget{ref-Martin2018}{}%
+Martin, Karin D.
+2018.
+``Monetary Myopia: An Examination of Institutional Response to Revenue from Monetary Sanctions for Misdemeanors.'' \emph{Criminal Justice Policy Review} 29 (6-7): 630--62.
+\url{https://doi.org/10.1177/0887403418761099}.
+
+\leavevmode\hypertarget{ref-Morris2020}{}%
+Morris, Kevin. 2020. ``Neighborhoods and Felony Disenfranchisement: The Case of New York City.'' \emph{Urban Affairs Review}, May, 1078087420921522. \url{https://doi.org/10.1177/1078087420921522}.
+
+\leavevmode\hypertarget{ref-Mughan2020}{}%
+Mughan, Siân.
+2020.
+``Municipal Reliance on Fine and Fee Revenues: How Local Courts Contribute to Extractive Revenue Practices in U.S.
+Cities.'' \emph{Public Budgeting \& Finance}, December.
+\url{https://doi.org/10.1111/pbaf.12277}.
+
+\leavevmode\hypertarget{ref-Sances2017}{}%
+Sances, Michael W., and Hye Young You.
+2017.
+``Who Pays for Government?
+Descriptive Representation and Exploitative Revenue Sources.'' \emph{The Journal of Politics} 79 (3): 1090--4.
+\url{https://doi.org/10.1086/691354}.
+
+\leavevmode\hypertarget{ref-Sanders2017}{}%
+Sanders, Topher, and Benjamin Conark.
+2017.
+``Florida Police Issue Hundreds of Bad Pedestrian Tickets Every Year Because They Don't Seem to Know the Law.'' \emph{ProPublica}, December 20, 2017.
+\url{https://www.propublica.org/article/florida-police-issue-hundreds-of-bad-pedestrian-tickets-every-year-because-they-dont-seem-to-know-the-law?token=CpfrqXaMuR8UnJ5-FryRkVwuKl3C98Ae}.
+
+\leavevmode\hypertarget{ref-Singla2020}{}%
+Singla, Akheil, Charlotte Kirschner, and Samuel B.
+Stone.
+2020.
+``Race, Representation, and Revenue: Reliance on Fines and Forfeitures in City Governments.'' \emph{Urban Affairs Review} 56 (4): 1132--67.
+\url{https://doi.org/10.1177/1078087419834632}.
+
+\leavevmode\hypertarget{ref-Uggen2020}{}%
+Uggen, Christopher, Ryan Larson, Sarah Shannon, and Arleth Pulido-Nava.
+2020.
+``Locked Out 2020: Estimates of People Denied Voting Rights Due to a Felony Conviction.'' Research report.
+The Sentencing Project.
+\url{https://www.sentencingproject.org/wp-content/uploads/2020/10/Locked-Out-2020.pdf}.
+
+\leavevmode\hypertarget{ref-UnitedStatesCommissiononCivilRights2017}{}%
+United States Commission on Civil Rights. 2017. ``Targeted Fines and Fees Against Communities of Color.'' \url{https://www.usccr.gov/pubs/2017/Statutory_Enforcement_Report2017.pdf}.
+
+\leavevmode\hypertarget{ref-UnitedStatesDepartmentofJusticeCivilRightsDivision2015}{}%
+United States Department of Justice Civil Rights Division.
+2015.
+``Investigation of the Ferguson Police Department.'' \url{https://www.justice.gov/sites/default/files/opa/press-releases/attachments/2015/03/04/ferguson_police_department_report.pdf}.
+
+\leavevmode\hypertarget{ref-Walker2014}{}%
+Walker, Hannah L.
+2014.
+``Extending the Effects of the Carceral State: Proximal Contact, Political Participation, and Race.'' \emph{Political Research Quarterly}, July.
+\url{https://doi.org/10.1177/1065912914542522}.
+
+\leavevmode\hypertarget{ref-Weaver2010}{}%
+Weaver, Vesla M., and Amy E. Lerman. 2010. ``Political Consequences of the Carceral State.'' \emph{American Political Science Review} 104 (4): 817--33. \url{https://doi.org/10.1017/S0003055410000456}.
+
+\leavevmode\hypertarget{ref-Zayas2015}{}%
+Zayas, Alexandra.
+2015.
+``How Riding Your Bike Can Land You in Trouble with the Cops --- If You're Black.'' \emph{Tampa Bay Times}, April 15, 2015.
+\url{https://www.tampabay.com/news/publicsafety/how-riding-your-bike-can-land-you-in-trouble-with-the-cops---if-youre-black/2225966/}.
+\end{cslreferences}
+
 \end{document}

### 2021-01-20 markdown/fees_fines_to.Rmd
keep going

@@
 After Michael Brown was killed by the Ferguson Police Department in 2014, a US Department of Justice investigation into the city’s police and courts demonstrated that the municipality was engaged in a practice that advocates now refer to as “policing for profit.” The city’s reliance on fines and fees to fund government functions grew from 13 to 23 percent of the total budget between fiscal years 2012 and 2015 [@UnitedStatesDepartmentofJusticeCivilRightsDivision2015].
-Although a body of literature developed over the past decade indicates that criminalization chills political participation, no work has directly investigated the relationship between fines and fees revenue collection and voter turnout.
-This project intends to fill that gap.
 
@@
 American cities’ reliance on fines and fees revenue increased significantly following the 2008 recession—as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services [@Singla2020; @Mughan2020; @Kirk2020; @Martin2018].
+Although a body of literature developed over the past decade indicates that criminalization chills political participation, no work has directly investigated the relationship between fines and fees revenue collection and voter turnout.
+This project intends to fill that gap.
 
@@
 
-Recent work from scholars in sociology and political science, however, indicates that many more voters are *indirectly* disenfranchised due to over-incarceration and the politically chilling effects of the carceral state.
+Recent work from scholars in sociology and political science, however, indicates that many more voters are also *indirectly* disenfranchised due to over-incarceration and the politically chilling effects of the carceral state.
 Policing and incarceration shape political socialization: personal contact with police or incarceration is associated with a reduced likelihood of political participation, and that alienating effect extends even to people who have incarcerated family members or who simply reside in affected communities [@Lee2014; @Weaver2010; @Morris2020].
-This relationship may be more complicated, however.
-In New York City, concentrated policing was associated with reduced turnout in Congressional elections and increased turnout in the 2008 Presidential election as well as the local mayoral election in 2013 [@Laniyonu2019].
+This relationship is complicated, however.
+In New York City, concentrated stop-and-frisk activity was associated with *reduced* turnout in Congressional elections, but *increased* turnout in the 2008 presidential election as well as the local mayoral election in 2013 [@Laniyonu2019].
 It may also be the case that proximal contact differs from personal contact with the criminal legal system—whereas direct experience with criminalization (and incarceration in particular) reduces the likelihood of voting, proximal or indirect experience produces more mixed results.
@@
 
-However, one of the most routine interactions Americans have with the police has gone largely unstudied: namely, ticketing for low-level offenses.
+Despite this burgeoning literature, one of the most routine interactions Americans have with the police has gone largely unstudied: namely, ticketing for low-level offenses.
 Police ticketing practices may discourage potential voters without directly disenfranchising them, and ticketing affects more Americans than legal disenfranchisement.
@@
 As one man told them, “I feel like if I contact a senator or governor, they’ll probably want to put me in jail and leave me as a troublemaker...
-I try to basically stay away from government” [-@Lerman2014].
+I try to basically stay away from government” [-@Lerman2014, p.
+210].
 In their study of descriptive representation, Sances and You [-@Sances2017] explicitly suggested that “fines may make descriptive representation less likely by depressing minority turnout,” and called for further research regarding voter turnout and the imposition of fines.
@@
 By using the latitude and longitude of every registered voter in the country and shapefiles provided by the Census Bureau, we map each voter to their home municipality using the same definitions as the COG.^[Although the registered voter file includes the name of the city in which the voter is registered, these do not always map neatly to the municipalities defined in the COG data.
-The use of these shapefiles ensures an apples-to-apples comparison.] We then aggregate these individual-level records up to the municipality level to determine municipal turnout, measured as a share of registered voters.
-The full study will include other turnout denominators to avoid biased estimates arising from differential registration rates.
+The use of these shapefiles ensures an apples-to-apples comparison.] We then aggregate these individual-level records up to the municipality level to determine the number of ballots cast in each municipality.
+TUrnout is calculated by dividing this number by the city’s citizen voting age population (CVAP) from the Census Bureau.
 
@@
 
-### Results {-}
+### Preliminary Results {-}
 
 Figure \ref{fig:marg1} makes clear that there is a relationship between the fees and fines collected by a municipality and its turnout.
-The left hand panel shows the simple bivariate relationship between the two quantities.
-In the right hand panel, we present the marginal effects plot in lieu of a regression table due to space constraints.
+The left-hand panel shows the simple bivariate relationship between the two quantities.
+In the right-hand panel, we present the marginal effects plot in lieu of a regression table due to space constraints.
 The second panel shows that, even after controlling for a municipality’s racial composition, median income, collegiate education, age, and state fixed effects, there is a statistically significant, negative relationship between fees and fines and turnout in 2018.
@@
 
-All else equal, a 10 percent increase in the dollars of fees and fines raised per resident is associated with a reduction in turnout of 0.06 percentage points, and the relationship is significant at the 99 percent confidence level.
+All else equal, a 1 percent increase in the dollars of fees and fines raised per resident is associated with a reduction in turnout of 0.003 percentage points, and the relationship is significant at the 99 percent confidence level.
 Although this may seem small, Figure \ref{fig:marg1} shows that the range of fees and fines raised is large.
-The figure marks the 10th and 90th percentiles for revenue collected in fees and fines, and predicted turnout drops by 1.8 percentage points over this range.
+The figure marks the 10th and 90th percentiles for revenue collected in fees and fines, and predicted turnout drops by 0.8 percentage points over this range.
 
-Figure \ref{fig:marg2} presents the results of preliminary analyses investigating the relationship between fees and fines collection and the racial turnout gap.^[Because we are interested in the racial turnout gap, we include only cities where the population is less than 90 percent non-Hispanic white.] Because the bivariate regression is not statistically significant and the *R^2^* is very small (<0.001) we refrain from including the line of best fit in the first panel.
-Our initial analysis indicates, however, that the relationship between fees and fines collection and the racial turnout gap in a municipality is moderated by its racial composition.
-The second panel of Figure \ref{fig:marg2} indicates the racial turnout gap is much larger in minority-white cities that collect no fees and fines than in whiter cities that also do not collect fees and fines.
-As fees and fines collections increase in less-white cities the turnout gap drops, though we see no such pattern in municipalities that are predominantly white.
-As in Figure \ref{fig:marg1}, we mark the 10th and 90th percentiles.
+Figure \ref{fig:marg2} presents the results of preliminary analyses investigating the relationship between fees and fines collection and the white-Black turnout gap.
+Racial turnout figures are calculated by using the number of ballots cast by members of each racial group according to L2 divided by the CVAP estimates for that group in each municipality.
+Our initial analysis indicates that the white-Black turnout gap in a municipality is strongly associated with the level of fees and fines it imposes.
+Figure \ref{fig:marg2} shows that the racial turnout gap is much larger in cities where there are fewer fees and fines imposed.
+Moving from the 10th to 90th percentile of fees and fines per capita is associated with a 9 percentage point drop in the white-Black turnout gap.
 
 ```{r, fig.show="hold", out.width="50%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:marg2}Dollars per Resident and 2018 Turnout Gap", fig.pos = "H"}
-p3 <- readRDS("./temp/simple_scat_gap.rds")
-load("./temp/mef_gap.rdata")
-print(p3)
-print(p4)
+p5 <- readRDS("./temp/simple_scat_gap_bw.rds")
+load("./temp/mef_gap_bw.rdata")
+print(p5)
+print(p6)
 ```
@@
 
-The significant negative association in our analysis provides some support for our hypothesis: though our preliminary analyses cannot establish causality, they are consistent with a causal story that links fines and fees practices with lower political participation among those who are subjected to them.
+The significant negative association in our analysis provides some support for our first hypothesis: though our preliminary analyses cannot establish causality, they are consistent with a causal story that links fines and fees practices with lower political participation among those who are subjected to them.
 On the other hand, officials in municipalities with lower turnout may feel more free to rely on fees and fines for revenue collection because they have less fear of electoral repercussions.
@@
 
-That the racial turnout gap is more sensitive to fees and fines collection in municipalities with a smaller white share of the population is somewhat surprising.
-This could reflect racially disparate policing in cities with large nonwhite populations.
-It is possible that cities with many nonwhite residents and *low* fees and fines collections disproportionately penalize nonwhite residents; as fees and fines collections increase, however, a larger share of the population - and, thus, more white voters - may be swept into these programs, thereby *reducing* racial disparities and consequently discrepancies in the racial turnout gap.
+That the racial turnout gap is smaller in cities with more fees and fines is surprising, and the opposite of what we expected to find.
+This could reflect racially disparate policing in cities with low fee collection.
+It is possible that cities with *low* fees and fines collections disproportionately penalize nonwhite residents; as fees and fines collections increase, however, a larger share of the population --- and, thus, more white voters --- may have a negative interaction with a police officer, thereby *reducing* racial disparities and consequently discrepancies in the racial turnout gap.
 

### 2021-01-20 markdown/fees_fines_to.tex
keep going

@@
 \author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jbenmenachem@gmail.com}{\nolinkurl{jbenmenachem@gmail.com}})} \and Kevin Morris\footnote{Researcher, Brennan Center for Justice at NYU School of Law (\href{mailto:kevin.morris@nyu.edu}{\nolinkurl{kevin.morris@nyu.edu}})}}
-\date{January 13, 2021}
+\date{January 14, 2021}
 
@@
 After Michael Brown was killed by the Ferguson Police Department in 2014, a US Department of Justice investigation into the city's police and courts demonstrated that the municipality was engaged in a practice that advocates now refer to as ``policing for profit.'' The city's reliance on fines and fees to fund government functions grew from 13 to 23 percent of the total budget between fiscal years 2012 and 2015 (United States Department of Justice Civil Rights Division \protect\hyperlink{ref-UnitedStatesDepartmentofJusticeCivilRightsDivision2015}{2015}).
+
+It wasn't just a Ferguson problem, or even a Missouri problem.
+American cities' reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (Singla, Kirschner, and Stone \protect\hyperlink{ref-Singla2020}{2020}; Mughan \protect\hyperlink{ref-Mughan2020}{2020}; Kirk, Fernandes, and Friedman \protect\hyperlink{ref-Kirk2020}{2020}; Martin \protect\hyperlink{ref-Martin2018}{2018}).
 Although a body of literature developed over the past decade indicates that criminalization chills political participation, no work has directly investigated the relationship between fines and fees revenue collection and voter turnout.
@@
 
-It wasn't just a Ferguson problem, or even a Missouri problem.
-American cities' reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (Singla, Kirschner, and Stone \protect\hyperlink{ref-Singla2020}{2020}; Mughan \protect\hyperlink{ref-Mughan2020}{2020}; Kirk, Fernandes, and Friedman \protect\hyperlink{ref-Kirk2020}{2020}; Martin \protect\hyperlink{ref-Martin2018}{2018}).
-
-Fines and fees practices disproportionately target Black Americans: city government reliance on fines and fees revenue is associated with larger Black populations, racial stereotypes affect the imposition of fines and fees, and Black defendants face more severe penalties related to monetary sanctions (United States Commission on Civil Rights \protect\hyperlink{ref-UnitedStatesCommissiononCivilRights2017}{2017}; Harris, Evans, and Beckett \protect\hyperlink{ref-Harris2011}{2011}; Edwards and Harris \protect\hyperlink{ref-Edwards2020}{n.d.}).
+Fines and fees practices disproportionately target Black Americans: city government reliance on fines and fees revenue is associated with larger Black populations, racial stereotypes affect the imposition of fines and fees, and Black defendants face more severe penalties related to monetary sanctions (United States Commission on Civil Rights \protect\hyperlink{ref-UnitedStatesCommissiononCivilRights2017}{2017}; Harris, Evans, and Beckett \protect\hyperlink{ref-Harris2011}{2011}; Edwards and Harris \protect\hyperlink{ref-Edwards2020}{2020}).
 The relationship between cities' reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator, however (Sances and You \protect\hyperlink{ref-Sances2017}{2017}).
@@
 
-Recent work from scholars in sociology and political science, however, indicates that many more voters are \emph{indirectly} disenfranchised due to over-incarceration and the politically chilling effects of the carceral state.
+Recent work from scholars in sociology and political science, however, indicates that many more voters are also \emph{indirectly} disenfranchised due to over-incarceration and the politically chilling effects of the carceral state.
 Policing and incarceration shape political socialization: personal contact with police or incarceration is associated with a reduced likelihood of political participation, and that alienating effect extends even to people who have incarcerated family members or who simply reside in affected communities (Lee, Porter, and Comfort \protect\hyperlink{ref-Lee2014}{2014}; Weaver and Lerman \protect\hyperlink{ref-Weaver2010}{2010}; Morris \protect\hyperlink{ref-Morris2020}{2020}).
-This relationship may be more complicated, however.
-In New York City, concentrated policing was associated with reduced turnout in Congressional elections and increased turnout in the 2008 Presidential election as well as the local mayoral election in 2013 (Laniyonu \protect\hyperlink{ref-Laniyonu2019}{2019}).
+This relationship is complicated, however.
+In New York City, concentrated stop-and-frisk activity was associated with \emph{reduced} turnout in Congressional elections, but \emph{increased} turnout in the 2008 presidential election as well as the local mayoral election in 2013 (Laniyonu \protect\hyperlink{ref-Laniyonu2019}{2019}).
 It may also be the case that proximal contact differs from personal contact with the criminal legal system---whereas direct experience with criminalization (and incarceration in particular) reduces the likelihood of voting, proximal or indirect experience produces more mixed results.
@@
 Lerman and Weaver have argued that residents' perceptions of law enforcement may affect their perceptions of government as a whole.
-As one man told them, ``I feel like if I contact a senator or governor, they'll probably want to put me in jail and leave me as a troublemaker\ldots{} I try to basically stay away from government'' (\protect\hyperlink{ref-Lerman2014}{2014}).
+As one man told them, ``I feel like if I contact a senator or governor, they'll probably want to put me in jail and leave me as a troublemaker\ldots{} I try to basically stay away from government'' (\protect\hyperlink{ref-Lerman2014}{2014}, 210).
 In their study of descriptive representation, Sances and You (\protect\hyperlink{ref-Sances2017}{2017}) explicitly suggested that ``fines may make descriptive representation less likely by depressing minority turnout,'' and called for further research regarding voter turnout and the imposition of fines.
@@
 By using the latitude and longitude of every registered voter in the country and shapefiles provided by the Census Bureau, we map each voter to their home municipality using the same definitions as the COG.\footnote{Although the registered voter file includes the name of the city in which the voter is registered, these do not always map neatly to the municipalities defined in the COG data.
-The use of these shapefiles ensures an apples-to-apples comparison.} We then aggregate these individual-level records up to the municipality level to determine municipal turnout, measured as a share of registered voters.
-The full study will include other turnout denominators to avoid biased estimates arising from differential registration rates.
+The use of these shapefiles ensures an apples-to-apples comparison.} We then aggregate these individual-level records up to the municipality level to determine the number of ballots cast in each municipality.
+TUrnout is calculated by dividing this number by the city's citizen voting age population (CVAP) from the Census Bureau.
 
@@
 
-\hypertarget{results}{%
-\subsubsection*{Results}\label{results}}
-\addcontentsline{toc}{subsubsection}{Results}
+\hypertarget{preliminary-results}{%
+\subsubsection*{Preliminary Results}\label{preliminary-results}}
+\addcontentsline{toc}{subsubsection}{Preliminary Results}
 
 Figure \ref{fig:marg1} makes clear that there is a relationship between the fees and fines collected by a municipality and its turnout.
-The left hand panel shows the simple bivariate relationship between the two quantities.
-In the right hand panel, we present the marginal effects plot in lieu of a regression table due to space constraints.
+The left-hand panel shows the simple bivariate relationship between the two quantities.
+In the right-hand panel, we present the marginal effects plot in lieu of a regression table due to space constraints.
 The second panel shows that, even after controlling for a municipality's racial composition, median income, collegiate education, age, and state fixed effects, there is a statistically significant, negative relationship between fees and fines and turnout in 2018.
@@
 
-All else equal, a 10 percent increase in the dollars of fees and fines raised per resident is associated with a reduction in turnout of 0.06 percentage points, and the relationship is significant at the 99 percent confidence level.
+All else equal, a 1 percent increase in the dollars of fees and fines raised per resident is associated with a reduction in turnout of 0.003 percentage points, and the relationship is significant at the 99 percent confidence level.
 Although this may seem small, Figure \ref{fig:marg1} shows that the range of fees and fines raised is large.
-The figure marks the 10th and 90th percentiles for revenue collected in fees and fines, and predicted turnout drops by 1.8 percentage points over this range.
+The figure marks the 10th and 90th percentiles for revenue collected in fees and fines, and predicted turnout drops by 0.8 percentage points over this range.
 
-Figure \ref{fig:marg2} presents the results of preliminary analyses investigating the relationship between fees and fines collection and the racial turnout gap.\footnote{Because we are interested in the racial turnout gap, we include only cities where the population is less than 90 percent non-Hispanic white.} Because the bivariate regression is not statistically significant and the \emph{R\textsuperscript{2}} is very small (\textless0.001) we refrain from including the line of best fit in the first panel.
-Our initial analysis indicates, however, that the relationship between fees and fines collection and the racial turnout gap in a municipality is moderated by its racial composition.
-The second panel of Figure \ref{fig:marg2} indicates the racial turnout gap is much larger in minority-white cities that collect no fees and fines than in whiter cities that also do not collect fees and fines.
-As fees and fines collections increase in less-white cities the turnout gap drops, though we see no such pattern in municipalities that are predominantly white.
-As in Figure \ref{fig:marg1}, we mark the 10th and 90th percentiles.
+Figure \ref{fig:marg2} presents the results of preliminary analyses investigating the relationship between fees and fines collection and the white-Black turnout gap.
+Racial turnout figures are calculated by using the number of ballots cast by members of each racial group according to L2 divided by the CVAP estimates for that group in each municipality.
+Our initial analysis indicates that the white-Black turnout gap in a municipality is strongly associated with the level of fees and fines it imposes.
+Figure \ref{fig:marg2} shows that the racial turnout gap is much larger in cities where there are fewer fees and fines imposed.
+Moving from the 10th to 90th percentile of fees and fines per capita is associated with a 9 percentage point drop in the white-Black turnout gap.
 
@@
 
-That the racial turnout gap is more sensitive to fees and fines collection in municipalities with a smaller white share of the population is somewhat surprising.
-This could reflect racially disparate policing in cities with large nonwhite populations.
-It is possible that cities with many nonwhite residents and \emph{low} fees and fines collections disproportionately penalize nonwhite residents; as fees and fines collections increase, however, a larger share of the population - and, thus, more white voters - may be swept into these programs, thereby \emph{reducing} racial disparities and consequently discrepancies in the racial turnout gap.
+That the racial turnout gap is smaller in cities with more fees and fines is surprising, and the opposite of what we expected to find.
+This could reflect racially disparate policing in cities with low fee collection.
+It is possible that cities with \emph{low} fees and fines collections disproportionately penalize nonwhite residents; as fees and fines collections increase, however, a larger share of the population --- and, thus, more white voters --- may have a negative interaction with a police officer, thereby \emph{reducing} racial disparities and consequently discrepancies in the racial turnout gap.
 
 Our full study will include a more narrow analysis of turnout in jurisdictions that dramatically increased or decreased ticketing over a comparatively short period of time.
-For instance, a Florida Times-Union investigation revealed that police in four counties disproportionately issued tickets to Black pedestrians (Sanders and Conark \protect\hyperlink{ref-Sanders2017}{2017}).
+For instance, a Florida Times-Union investigation revealed that police in four counties disproportionately issued tickets to Black pedestrians (Sanders and Conarck \protect\hyperlink{ref-Sanders2017}{2017}).
 In Tampa, police issued thousands of tickets to Black cyclists between 2012 and 2015---after journalists reported on the problem, the city began to issue fewer than 100 citations each year as of 2018 (Zayas \protect\hyperlink{ref-Zayas2015}{2015}; Frago \protect\hyperlink{ref-Frago2019}{2019}).
@@
 \leavevmode\hypertarget{ref-Edwards2020}{}%
-Edwards, Frank, and Alexes Harris.
-n.d.
-``An Analysis of Court Imposed Monetary Sanctions in Seattle Municipal Courts, 2000-2017.'' Accessed January 13, 2021.
-\url{https://doi.org/10.31235/osf.io/ajpqc}.
+Edwards, Frank, and Alexes Harris. 2020. ``An Analysis of Court Imposed Monetary Sanctions in Seattle Municipal Courts, 2000-2017.'' August. \url{https://doi.org/10.31235/osf.io/ajpqc}.
 
@@
 \leavevmode\hypertarget{ref-Sanders2017}{}%
-Sanders, Topher, and Benjamin Conark.
+Sanders, Topher, and Benjamin Conarck.
 2017.

### 2021-01-20 code/00_initialize.R

@@ -1,4 +1,5 @@
 library(miceadds)
+library(Matching)
 library(ggeffects)
 library(scales)
 library(extrafont)

### 2021-01-20 code/01_cog.R

@@ -26,28 +26,128 @@ d <- left_join(d, select(info,
                          name = X2), by = c("place_id" = "X1")) %>% 
   rename(pop_cog = population)
 
+############################# NOW DO 2012
+d12 <- read_fwf("raw_data/2012_individual_unit_file/2012FinEstDAT_10162019modp_pu.txt",
+              col_positions = fwf_widths(c(14, 3, 12, 4, 1),
+                                         col_names = c("place_id",
+                                                       "item_code",
+                                                       "amount",
+                                                       "year",
+                                                       "imputation")),
+              col_types = "ccccc")
+
+
+police12 <- d12 %>% 
+  filter(item_code %in% c("E62", "F62", "G62", "I62", "L62", "M62", "N62", "O62", "P62", "R62",
+                          "E25", "I25", "F25", "G25", "K25")) %>% 
+  filter(as.numeric(amount) > 0)
+
+
+info12 <- read_fwf("raw_data/2012_individual_unit_file/Fin_GID_2012.txt",
+                 col_positions = fwf_widths(c(14, 64, 35, 2, 3, 5, 9, 2, 7, 2, 2, 2, 4, 2)),
+                 col_types = "cccccccccccccc")
+
+d12 <- left_join(d12, select(info12,
+                             X1,
+                             population = X7,
+                             fips = X6,
+                             state = X4,
+                             name = X2), by = c("place_id" = "X1")) %>% 
+  filter(item_code == "U30",
+       place_id %in% police12$place_id) %>% 
+  mutate(dper12 = as.numeric(amount)*1000 / as.numeric(population),
+         GEOID = paste0(state, fips)) %>% 
+  select(GEOID, dper12)
+rm(info12, police12)
+##################################
+
+
+# c <- get_basic_census_stats("place", 2018) %>%
+#   select(-NAME)
 # 
-# c <- get_basic_census_stats("place", 2018)
+# ptime <- get_acs("place", variables = c("B08013_001", "B08006_001"), year = 2018, output = "wide") %>% 
+#   mutate(travel_time = B08013_001E/ B08006_001E) %>% 
+#   select(GEOID, travel_time)
+# 
[…]

### 2021-01-20 code/03_regs.R

@@ -4,20 +4,29 @@ cog <- readRDS("temp/cog_cities.rds") %>%
   mutate(state = as.factor(state))
 
 to <- readRDS("temp/city_to.rds") %>% 
-  group_by(plasub) %>% 
-  summarize(to_18 = weighted.mean(to, count),
-            to_16 = weighted.mean(to_old, count))
+  group_by(plasub) %>%
+  mutate(votes_18 = count * to_18,
+         votes_16 = count * to_16,
+         votes_10 = count * to_10) %>% 
+  summarize(to_18 = sum(votes_18) / sum(count),
+            to_16 = sum(votes_16) / sum(count),
+            votes_18 = sum(votes_18),
+            votes_16 = sum(votes_16),
+            votes_10 = sum(votes_10))
 
-full_set <- inner_join(cog, to, by = c("GEOID" = "plasub"))
+full_set <- inner_join(cog, to, by = c("GEOID" = "plasub")) %>% 
+  mutate(vap_to_18 = votes_18 / cvap,
+         vap_to_10 = votes_10 / cvap)
 
-p1 <- ggplot(full_set, aes(x = lndper, y = to_18)) + geom_point(shape = 1) + geom_smooth(method = "lm") +
+p1 <- ggplot(full_set, aes(x = lndper, y = vap_to_18)) + geom_point(shape = 1) + geom_smooth(method = "lm") +
   xlab("Dollars per Resident") +
   ylab("Turnout in 2018") + scale_x_continuous(breaks = c(log(1), log(2), log(11), log(101), log(201)),
                                                                            labels = c("$0", "$1", "$10", "$100", "$200")) +
   scale_y_continuous(labels = percent) +
   theme_bw() + theme(plot.caption = element_text(hjust = 0),
                      text = element_text(family = "LM Roman 10")) +
-  coord_cartesian(xlim = c(0, log(201))) +
+  coord_cartesian(xlim = c(0, log(201)),
+                  ylim = c(0, .825)) +
   labs(caption = "
        
        ")
@@ -26,11 +35,15 @@ m1 <- lm.cluster(to_18 ~ lndper + nh_white + nh_black + latino +
            median_income + some_college + median_age + share_over_64 +
            state, data = full_set, cluster = full_set$state)
 
-m2 <- lm(to_18 ~ lndper + nh_white + nh_black + latino +
[…]

### 2021-01-20 code/04_did.R

@@ -1,0 +1,179 @@
+#######
+
+cities <- readRDS("temp/cog_cities.rds") %>% 
+  mutate(pct_change = dper / dper12,
+         q = ntile(pct_change, 10)) %>% 
+  filter(q %in% c(1:7, 10)) %>% 
+  mutate(treated = q == 10) %>% 
+  dplyr::select(place_id, treated, population, asian, latino, nh_black, nh_white,
+         median_income, some_college, median_age,
+         share_no_car, GEOID)
+
+cities <- cities[complete.cases(cities), ]
+
+match_data <- cities %>% 
+  dplyr::select(-place_id, -treated, -GEOID)
+
+# genout <- GenMatch(Tr = cities$treated, X = match_data, replace = T, pop.size = 1000)
+# saveRDS(genout, "temp/genout_pct.rds")
+
+genout <- readRDS("temp/genout_pct.rds")
+
+mout <- Match(Tr = cities$treated, X = match_data,
+              estimand = "ATT", Weight.matrix = genout, M = 2)
+##################################
+
+varnames <- c("population", "asian", "latino", "nh_black", "nh_white",
+              "median_income", "some_college", "median_age",
+              "share_no_car")
+
+balance <- MatchBalance(treated ~ population + asian + latino + nh_black + nh_white +
+                  median_income + some_college + median_age +
+                  share_no_car, data = cities, match.out = mout)
+TrMean <- c()
+PreMean <- c()
+PreQQmed <- c()
+PreQQmean <- c()
+PreQQmax <- c()
+PostMean <- c()
+PostQQmed <- c()
+PostQQmean <- c()
+PostQQmax <- c()
+
+for(i in c(1:length(balance$BeforeMatching))){
+  TrMean <- unlist(c(TrMean, balance$BeforeMatching[[i]][3][1]))
+  PreMean <- unlist(c(PreMean, balance$BeforeMatching[[i]][4][1]))
+  PreQQmed <- unlist(c(PreQQmed, balance$BeforeMatching[[i]]$qqsummary[2]))
+  PreQQmean <- unlist(c(PreQQmean, balance$BeforeMatching[[i]]$qqsummary[1]))
+  PreQQmax <- unlist(c(PreQQmax, balance$BeforeMatching[[i]]$qqsummary[3]))
+  
+  PostMean <- unlist(c(PostMean, balance$AfterMatching[[i]][4][1]))
[…]

### 2021-01-27 markdown/fees_fines_to.Rmd
add 2way fes

@@
 author:
-- Jonathan Ben-Menachem^[PhD Student, Columbia University, Department of Sociology (jbenmenachem@gmail.com)]
+- Jonathan Ben-Menachem^[PhD Student, Columbia University, Department of Sociology (jb4487@columbia.edu)]
 - Kevin Morris^[Researcher, Brennan Center for Justice at NYU School of Law (kevin.morris@nyu.edu)]
@@
 Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities’ alienation from government.
-After Michael Brown was killed by the Ferguson Police Department in 2014, a US Department of Justice investigation into the city’s police and courts demonstrated that the municipality was engaged in a practice that advocates now refer to as “policing for profit.” The city’s reliance on fines and fees to fund government functions grew from 13 to 23 percent of the total budget between fiscal years 2012 and 2015 [@UnitedStatesDepartmentofJusticeCivilRightsDivision2015].
-
-It wasn’t just a Ferguson problem, or even a Missouri problem.
 American cities’ reliance on fines and fees revenue increased significantly following the 2008 recession—as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services [@Singla2020; @Mughan2020; @Kirk2020; @Martin2018].
 Although a body of literature developed over the past decade indicates that criminalization chills political participation, no work has directly investigated the relationship between fines and fees revenue collection and voter turnout.
-This project intends to fill that gap.
+This project intends to fill that gap by testing whether fines and fees at the municipal level influence voter turnout.
 
@@
 This could suggest that higher reliance on fines and fees results from government officials targeting individuals who hold less political power [@Makowsky2009].
+
+Additionally, Sances and You [-@Sances2017] explicitly suggested that “fines may make descriptive representation less likely by depressing minority turnout,” and called for further research regarding voter turnout and the imposition of fines.
+In this paper, we clarify that relationship by picking up where @Sances2017 left off.
+By tying data from the 2012 and 2017 Census of Governments to a national geocoded voter file we test whether municipalities with more fees and fines collected per resident saw lower turnout in the 2014 and 2018 general elections.
+We expect to find that municipalities where more revenue is raised per resident saw lower turnout, other things being equal.
+Because the American criminal legal system falls disproportionately on minorities, we also expect that the racial turnout gap [@Fraga2018] will be larger in municipalities that rely more heavily on fines and fees.
+Of course, fines and fees imposition may be related to turnout without necessarily indicating a causal relationship.
+For this reason we leverage data on fines collections and turnout from multiple time periods to investigate the causal relationship.
 
@@
 
-Ticketing practices may be related to distrust of government and reduced political participation.
+Public perceptions of abusive police practices, such as high-profile incidents of police violence or racially discriminatory street stops, can reduce willingness to report crimes or cooperate with law enforcement [@Desmond2016; @Tyler2014).
+Legitimacy studies have largely focused on police violence or police street stops, but new evidence related to fines and fees has recently emerged.
 In a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government more broadly [@CarpenterII2019].
-Lerman and Weaver have argued that residents’ perceptions of law enforcement may affect their perceptions of government as a whole.
-As one man told them, “I feel like if I contact a senator or governor, they’ll probably want to put me in jail and leave me as a troublemaker...
-I try to basically stay away from government” [-@Lerman2014, p.
-210].
-In their study of descriptive representation, Sances and You [-@Sances2017] explicitly suggested that “fines may make descriptive representation less likely by depressing minority turnout,” and called for further research regarding voter turnout and the imposition of fines.
-In this paper, we clarify that relationship.
 
-We begin by picking up where @Sances2017 left off.
-By tying data from the Census of Governments to a national geocoded voter file we test whether municipalities with more fees and fines collected per resident saw lower turnout in the 2014, 2016, and 2018 general elections.
-We expect to find that municipalities where more revenue is raised per resident saw lower turnout, other things being equal.
-Because the American criminal legal system falls disproportionately on minorities, we also expect that the racial turnout gap [@Fraga2018] will be larger in municipalities that rely more heavily on fines and fees.
-
-Of course, fines and fees imposition may be related to turnout without necessarily indicating a causal relationship.
-To estimate the causal effect, we will explore whether turnout increases or decreases in the wake of changes in city revenue collection policy.
+Although the conceptual framework for police legitimacy has been fruitfully critiqued—Monica @Bell2017 points to legal estrangement and structural exclusion in order to shift the theoretical focus from perceptions of unfairness to substantively unjust practices—the empirical literature on legitimacy is useful to demonstrate how police practices can alienate those subjected to them.
+The alienating effect of criminal legal exposure has also been tied to institutional avoidance [see, for instance, @Brayne2014].
+.
 
@@
 
-In order to ascertain whether fines and fees practices affect voter turnout, we exploit data from the 2013 and 2017 Census of Governments (COG) and national voter file data.
+In order to ascertain whether fines and fees practices affect voter turnout, we exploit data from the 2012 and 2017 Census of Governments (COG) and national voter file data.
 The COG, a project of the US Census Bureau, collects budget data for all local governments every five years, and the most recent survey was in 2017.
@@
 By using the latitude and longitude of every registered voter in the country and shapefiles provided by the Census Bureau, we map each voter to their home municipality using the same definitions as the COG.^[Although the registered voter file includes the name of the city in which the voter is registered, these do not always map neatly to the municipalities defined in the COG data.
-The use of these shapefiles ensures an apples-to-apples comparison.] We then aggregate these individual-level records up to the municipality level to determine the number of ballots cast in each municipality.
-TUrnout is calculated by dividing this number by the city’s citizen voting age population (CVAP) from the Census Bureau.
+The use of these shapefiles ensures an apples-to-apples comparison.] We then aggregate these individual-level records up to the municipality level to determine each municipality’s turnout.
 
@@
 However, we assume that this presents less of a problem when aggregating to the municipality-level.
-In order to control for potential confounders, we also control for a host of other information from the 5-year American Community Survey.
-
-Although we do not present these results in this abstract, we also intend to incorporate causal estimates in the full version of this study by using changes in fees and fines reliance between the 2013 and 2017 COGs, and turnout in the 2014 and 2018 elections.
+In order to control for potential confounders, we also control for a host of other information from the 5-year American Community Survey and the COG.
 
@@
 
-Figure \ref{fig:marg1} makes clear that there is a relationship between the fees and fines collected by a municipality and its turnout.
-The left-hand panel shows the simple bivariate relationship between the two quantities.
-In the right-hand panel, we present the marginal effects plot in lieu of a regression table due to space constraints.
-The second panel shows that, even after controlling for a municipality’s racial composition, median income, collegiate education, age, and state fixed effects, there is a statistically significant, negative relationship between fees and fines and turnout in 2018.
-In these models, the dependent variable is municipal turnout in 2018 and the independent variable of interest is the natural log of the dollars in fees and fines per resident plus 1.
+Figure \ref{fig:marg1} makes clear that higher fees and fines collections lead to lower turnout.
+The left-hand panel shows the simple bivariate relationship between turnout among registered voters in 2018 and fees and fines collection.
+The right-hand panel shows the bivariate relationship between the 2018 white-Black turnout gap and fines collections.
+The turnout gap is calculated by dividing the number of ballots cast by each racial group according to L2 by the estimated 2018 citizen voting age population (CVAP) from the Census Bureau to account for possible registration differences between groups.
 
@@
 p1 <- readRDS("./temp/simple_scat.rds")
-load("./temp/mef_to.rdata")
+p2 <- readRDS("./temp/simple_scat_gap_bw.rds")
 print(p1)
@@
 
-All else equal, a 1 percent increase in the dollars of fees and fines raised per resident is associated with a reduction in turnout of 0.003 percentage points, and the relationship is significant at the 99 percent confidence level.
-Although this may seem small, Figure \ref{fig:marg1} shows that the range of fees and fines raised is large.
-The figure marks the 10th and 90th percentiles for revenue collected in fees and fines, and predicted turnout drops by 0.8 percentage points over this range.
+Although Figure \ref{fig:marg1} shows that there is a relationship between collections and turnout and the turnout gap, the simple scatter plots cannot demonstrate a causal relationship.
+To investigate whether there is such a relationship, we employ two-way fixed effect models.
+In these models, each municipality is observed twice: their first observation includes their (logged + 1) fees and fines per capita from the 2012 COG, their turnout and turnout gap in 2014, and their sociodemographic characteristics from the ACS 5-year estimates from 2012.
+The second observation includes their (logged + 1) fees and fines from the 2017 COG, their 2018 turnout (gap), and their 2018 5-year ACS demographics.
+In each case, turnout is measured only among the individuals who were registered in a given municipality in both 2014 and 2018 to control for changes in registration rates, and in Model 2 the turnout gap is calculated using CVAP.
+Table \ref{tab:tab1} presents the results of these models.
 
-Figure \ref{fig:marg2} presents the results of preliminary analyses investigating the relationship between fees and fines collection and the white-Black turnout gap.
-Racial turnout figures are calculated by using the number of ballots cast by members of each racial group according to L2 divided by the CVAP estimates for that group in each municipality.
-Our initial analysis indicates that the white-Black turnout gap in a municipality is strongly associated with the level of fees and fines it imposes.
-Figure \ref{fig:marg2} shows that the racial turnout gap is much larger in cities where there are fewer fees and fines imposed.
-Moving from the 10th to 90th percentile of fees and fines per capita is associated with a 9 percentage point drop in the white-Black turnout gap.
-
-```{r, fig.show="hold", out.width="50%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:marg2}Dollars per Resident and 2018 Turnout Gap", fig.pos = "H"}
-p5 <- readRDS("./temp/simple_scat_gap_bw.rds")
-load("./temp/mef_gap_bw.rdata")
-print(p5)
-print(p6)
-```
+\begin{singlespace}
+\input{"../temp/2wfe_reg_clean.tex"}
+\end{singlespace}
 

### 2021-01-27 markdown/fees_fines_to.tex
add 2way fes

@@
 \subtitle{Fines, Fees, and Turnout}
-\author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jbenmenachem@gmail.com}{\nolinkurl{jbenmenachem@gmail.com}})} \and Kevin Morris\footnote{Researcher, Brennan Center for Justice at NYU School of Law (\href{mailto:kevin.morris@nyu.edu}{\nolinkurl{kevin.morris@nyu.edu}})}}
-\date{January 14, 2021}
+\author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{Researcher, Brennan Center for Justice at NYU School of Law (\href{mailto:kevin.morris@nyu.edu}{\nolinkurl{kevin.morris@nyu.edu}})}}
+\date{January 27, 2021}
 
@@
 Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities' alienation from government.
-After Michael Brown was killed by the Ferguson Police Department in 2014, a US Department of Justice investigation into the city's police and courts demonstrated that the municipality was engaged in a practice that advocates now refer to as ``policing for profit.'' The city's reliance on fines and fees to fund government functions grew from 13 to 23 percent of the total budget between fiscal years 2012 and 2015 (United States Department of Justice Civil Rights Division \protect\hyperlink{ref-UnitedStatesDepartmentofJusticeCivilRightsDivision2015}{2015}).
-
-It wasn't just a Ferguson problem, or even a Missouri problem.
 American cities' reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (Singla, Kirschner, and Stone \protect\hyperlink{ref-Singla2020}{2020}; Mughan \protect\hyperlink{ref-Mughan2020}{2020}; Kirk, Fernandes, and Friedman \protect\hyperlink{ref-Kirk2020}{2020}; Martin \protect\hyperlink{ref-Martin2018}{2018}).
 Although a body of literature developed over the past decade indicates that criminalization chills political participation, no work has directly investigated the relationship between fines and fees revenue collection and voter turnout.
-This project intends to fill that gap.
+This project intends to fill that gap by testing whether fines and fees at the municipal level influence voter turnout.
 
@@
 This could suggest that higher reliance on fines and fees results from government officials targeting individuals who hold less political power (Makowsky and Stratmann \protect\hyperlink{ref-Makowsky2009}{2009}).
+
+Additionally, Sances and You (\protect\hyperlink{ref-Sances2017}{2017}) explicitly suggested that ``fines may make descriptive representation less likely by depressing minority turnout,'' and called for further research regarding voter turnout and the imposition of fines.
+In this paper, we clarify that relationship by picking up where Sances and You (\protect\hyperlink{ref-Sances2017}{2017}) left off.
+By tying data from the 2012 and 2017 Census of Governments to a national geocoded voter file we test whether municipalities with more fees and fines collected per resident saw lower turnout in the 2014 and 2018 general elections.
+We expect to find that municipalities where more revenue is raised per resident saw lower turnout, other things being equal.
+Because the American criminal legal system falls disproportionately on minorities, we also expect that the racial turnout gap (Fraga \protect\hyperlink{ref-Fraga2018}{2018}) will be larger in municipalities that rely more heavily on fines and fees.
+Of course, fines and fees imposition may be related to turnout without necessarily indicating a causal relationship.
+For this reason we leverage data on fines collections and turnout from multiple time periods to investigate the causal relationship.
 
@@
 
-Ticketing practices may be related to distrust of government and reduced political participation.
+Public perceptions of abusive police practices, such as high-profile incidents of police violence or racially discriminatory street stops, can reduce willingness to report crimes or cooperate with law enforcement {[}Desmond, Papachristos, and Kirk (\protect\hyperlink{ref-Desmond2016}{2016}); Tyler, Fagan, and Geller (\protect\hyperlink{ref-Tyler2014}{2014})).
+Legitimacy studies have largely focused on police violence or police street stops, but new evidence related to fines and fees has recently emerged.
 In a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government more broadly (Carpenter II, Sweetland, and McDonald \protect\hyperlink{ref-CarpenterII2019}{2019}).
-Lerman and Weaver have argued that residents' perceptions of law enforcement may affect their perceptions of government as a whole.
-As one man told them, ``I feel like if I contact a senator or governor, they'll probably want to put me in jail and leave me as a troublemaker\ldots{} I try to basically stay away from government'' (\protect\hyperlink{ref-Lerman2014}{2014}, 210).
-In their study of descriptive representation, Sances and You (\protect\hyperlink{ref-Sances2017}{2017}) explicitly suggested that ``fines may make descriptive representation less likely by depressing minority turnout,'' and called for further research regarding voter turnout and the imposition of fines.
-In this paper, we clarify that relationship.
 
-We begin by picking up where Sances and You (\protect\hyperlink{ref-Sances2017}{2017}) left off.
-By tying data from the Census of Governments to a national geocoded voter file we test whether municipalities with more fees and fines collected per resident saw lower turnout in the 2014, 2016, and 2018 general elections.
-We expect to find that municipalities where more revenue is raised per resident saw lower turnout, other things being equal.
-Because the American criminal legal system falls disproportionately on minorities, we also expect that the racial turnout gap (Fraga \protect\hyperlink{ref-Fraga2018}{2018}) will be larger in municipalities that rely more heavily on fines and fees.
-
-Of course, fines and fees imposition may be related to turnout without necessarily indicating a causal relationship.
-To estimate the causal effect, we will explore whether turnout increases or decreases in the wake of changes in city revenue collection policy.
+Although the conceptual framework for police legitimacy has been fruitfully critiqued---Monica Bell (\protect\hyperlink{ref-Bell2017}{2017}) points to legal estrangement and structural exclusion in order to shift the theoretical focus from perceptions of unfairness to substantively unjust practices---the empirical literature on legitimacy is useful to demonstrate how police practices can alienate those subjected to them.
+The alienating effect of criminal legal exposure has also been tied to institutional avoidance (see, for instance, Brayne \protect\hyperlink{ref-Brayne2014}{2014}).
+.
 
@@
 By using the latitude and longitude of every registered voter in the country and shapefiles provided by the Census Bureau, we map each voter to their home municipality using the same definitions as the COG.\footnote{Although the registered voter file includes the name of the city in which the voter is registered, these do not always map neatly to the municipalities defined in the COG data.
-The use of these shapefiles ensures an apples-to-apples comparison.} We then aggregate these individual-level records up to the municipality level to determine the number of ballots cast in each municipality.
-TUrnout is calculated by dividing this number by the city's citizen voting age population (CVAP) from the Census Bureau.
+The use of these shapefiles ensures an apples-to-apples comparison.} We then aggregate these individual-level records up to the municipality level to determine each municipality's turnout.
 
@@
 
-Figure \ref{fig:marg1} makes clear that there is a relationship between the fees and fines collected by a municipality and its turnout.
-The left-hand panel shows the simple bivariate relationship between the two quantities.
-In the right-hand panel, we present the marginal effects plot in lieu of a regression table due to space constraints.
-The second panel shows that, even after controlling for a municipality's racial composition, median income, collegiate education, age, and state fixed effects, there is a statistically significant, negative relationship between fees and fines and turnout in 2018.
-In these models, the dependent variable is municipal turnout in 2018 and the independent variable of interest is the natural log of the dollars in fees and fines per resident plus 1.
+Figure \ref{fig:marg1} makes clear that higher fees and fines collections lead to lower turnout.
+The left-hand panel shows the simple bivariate relationship between turnout among registered voters in 2018 and fees and fines collection.
+The right-hand panel shows the bivariate relationship between the 2018 white-Black turnout gap and fines collections.
+The turnout gap is calculated by dividing the number of ballots cast by each racial group according to L2 by the estimated 2018 citizen voting age population (CVAP) from the Census Bureau to account for possible registration differences between groups.
 
@@
 
-All else equal, a 1 percent increase in the dollars of fees and fines raised per resident is associated with a reduction in turnout of 0.003 percentage points, and the relationship is significant at the 99 percent confidence level.
-Although this may seem small, Figure \ref{fig:marg1} shows that the range of fees and fines raised is large.
-The figure marks the 10th and 90th percentiles for revenue collected in fees and fines, and predicted turnout drops by 0.8 percentage points over this range.
+Although Figure \ref{fig:marg1} shows that there is a relationship between collections and turnout and the turnout gap, the simple scatter plots cannot demonstrate a causal relationship.
+To investigate whether there is such a relationship, we employ two-way fixed effect models.
+In these models, each municipality is observed twice: their first observation includes their (logged + 1) fees and fines per capita from the 2012 COG, their turnout and turnout gap in 2014, and their sociodemographic characteristics from the ACS 5-year estimates from 2012.
+The second observation includes their (logged + 1) fees and fines from the 2017 COG, their 2018 turnout (gap), and their 2018 5-year ACS demographics.
+In each case, turnout is measured only among the individuals who were registered in a given municipality in both 2014 and 2018 to control for changes in registration rates, and in Model 2 the turnout gap is calculated using CVAP.
+Table \ref{tab:tab1} presents the results of these models.
 
-Figure \ref{fig:marg2} presents the results of preliminary analyses investigating the relationship between fees and fines collection and the white-Black turnout gap.
-Racial turnout figures are calculated by using the number of ballots cast by members of each racial group according to L2 divided by the CVAP estimates for that group in each municipality.
-Our initial analysis indicates that the white-Black turnout gap in a municipality is strongly associated with the level of fees and fines it imposes.
-Figure \ref{fig:marg2} shows that the racial turnout gap is much larger in cities where there are fewer fees and fines imposed.
-Moving from the 10th to 90th percentile of fees and fines per capita is associated with a 9 percentage point drop in the white-Black turnout gap.
-
-\begin{figure}[H]
-\includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/unnamed-chunk-1-1} \includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/unnamed-chunk-1-2} \caption{\label{fig:marg2}Dollars per Resident and 2018 Turnout Gap}\label{fig:unnamed-chunk-1}
-\end{figure}
+\begin{singlespace}
+\input{"../temp/2wfe_reg_clean.tex"}
+\end{singlespace}
 
@@
 \begin{cslreferences}
+\leavevmode\hypertarget{ref-Bell2017}{}%
+Bell, Monica C. 2017. ``Police Reform and the Dismantling of Legal Estrangement.'' \emph{The Yale Law Journal} 126 (7): 2054--2150. \url{http://www.jstor.org/stable/45222555}.
+
+\leavevmode\hypertarget{ref-Brayne2014}{}%
+Brayne, Sarah.
+2014.
+``Surveillance and System Avoidance: Criminal Justice Contact and Institutional Attachment.'' \emph{American Sociological Review} 79 (3): 367--91.
+\url{https://doi.org/10.1177/0003122414530398}.
+
 \leavevmode\hypertarget{ref-CarpenterII2019}{}%
@@
 Colgan, Beth A. 2019. ``Wealth-Based Penal Disenfranchisement.'' \emph{Vanderbilt Law Review} 72 (1:55). \url{https://papers.ssrn.com/abstract=3312439}.
+
+\leavevmode\hypertarget{ref-Desmond2016}{}%
+Desmond, Matthew, Andrew V.
+Papachristos, and David S.
+Kirk.
+2016.
+``Police Violence and Citizen Crime Reporting in the Black Community.'' \emph{American Sociological Review} 81 (5): 857--76.
+\url{https://doi.org/10.1177/0003122416663494}.
 
@@
 
-\leavevmode\hypertarget{ref-Lerman2014}{}%
-Lerman, Amy E., and Vesla M.
-Weaver.
-2014.
-\emph{Arresting Citizenship: The Democratic Consequences of American Crime Control}.
-Chicago Studies in American Politics.
-Chicago ; London: The University of Chicago Press.
-
 \leavevmode\hypertarget{ref-Makowsky2009}{}%
@@
 
+\leavevmode\hypertarget{ref-Tyler2014}{}%
+Tyler, Tom R., Jeffrey Fagan, and Amanda Geller.
+2014.
+``Street Stops and Police Legitimacy: Teachable Moments in Young Urban Men's Legal Socialization.'' \emph{Journal of Empirical Legal Studies} 11 (4): 751--85.
+\url{https://doi.org/10.1111/jels.12055}.
+
 \leavevmode\hypertarget{ref-Uggen2020}{}%
@@
 United States Commission on Civil Rights. 2017. ``Targeted Fines and Fees Against Communities of Color.'' \url{https://www.usccr.gov/pubs/2017/Statutory_Enforcement_Report2017.pdf}.
-
-\leavevmode\hypertarget{ref-UnitedStatesDepartmentofJusticeCivilRightsDivision2015}{}%
-United States Department of Justice Civil Rights Division.
-2015.
-``Investigation of the Ferguson Police Department.'' \url{https://www.justice.gov/sites/default/files/opa/press-releases/attachments/2015/03/04/ferguson_police_department_report.pdf}.
 

### 2021-01-27 code/00_initialize.R

@@ -1,5 +1,6 @@
 library(miceadds)
 library(Matching)
+library(plm)
 library(ggeffects)
 library(scales)
 library(extrafont)

### 2021-01-27 code/01_cog.R

@@ -24,17 +24,33 @@ d <- left_join(d, select(info,
                          fips = X6,
                          state = X4,
                          name = X2), by = c("place_id" = "X1")) %>% 
-  rename(pop_cog = population)
+  rename(pop_cog = population) %>% 
+  mutate(dper = as.numeric(amount)*1000 / as.numeric(pop_cog),
+         lndper = log(dper + 1))
+
+rev <- d %>% 
+  filter(substring(item_code, 1, 1) %in% c("T", "B", "C", "D", "A", "U")) %>% 
+  mutate(amount = as.numeric(amount),
+         state_fed = amount * substring(item_code, 1, 1) %in% c("B", "C"),
+         taxes = amount * substring(item_code, 1, 1) %in% c("T")) %>% 
+  group_by(place_id) %>% 
+  summarize(total_revenue = sum(amount),
+            rev_state_fed = sum(state_fed),
+            taxes = sum(taxes)) %>% 
+  mutate(share_state_fed = rev_state_fed / total_revenue,
+         share_taxes = taxes / total_revenue) %>% 
+  select(-rev_state_fed, -taxes) %>% 
+  ungroup()
 
 ############################# NOW DO 2012
 d12 <- read_fwf("raw_data/2012_individual_unit_file/2012FinEstDAT_10162019modp_pu.txt",
-              col_positions = fwf_widths(c(14, 3, 12, 4, 1),
-                                         col_names = c("place_id",
-                                                       "item_code",
-                                                       "amount",
-                                                       "year",
-                                                       "imputation")),
-              col_types = "ccccc")
+                col_positions = fwf_widths(c(14, 3, 12, 4, 1),
+                                           col_names = c("place_id",
+                                                         "item_code",
+                                                         "amount",
+                                                         "year",
+                                                         "imputation")),
+                col_types = "ccccc")
 
 
 police12 <- d12 %>% 
@@ -44,8 +60,8 @@ police12 <- d12 %>%
 
 
[…]

### 2021-01-27 code/03_regs.R

@@ -1,7 +1,8 @@
 
 
 cog <- readRDS("temp/cog_cities.rds") %>% 
-  mutate(state = as.factor(state))
+  mutate(state = as.factor(state),
+         fines_rev = dper / total_revenue)
 
 to <- readRDS("temp/city_to.rds") %>% 
   group_by(plasub) %>%
@@ -31,17 +32,30 @@ p1 <- ggplot(full_set, aes(x = lndper, y = vap_to_18)) + geom_point(shape = 1) +
        
        ")
 p1
-m1 <- lm.cluster(to_18 ~ lndper + nh_white + nh_black + latino +
+p1b <- ggplot(full_set, aes(x = log(fines_rev), y = vap_to_18)) + geom_point(shape = 1) + geom_smooth(method = "lm") +
+  xlab("Share of Municipal Revenue from Fees and Fines") +
+  ylab("Turnout in 2018") + scale_x_continuous(breaks = c(log(0.00005), log(0.001), log(0.0075)),
+                                               labels = c("0.005%", "0.1%", "0.75%")) +
+  scale_y_continuous(labels = percent) +
+  theme_bw() + theme(plot.caption = element_text(hjust = 0),
+                     text = element_text(family = "LM Roman 10")) +
+  coord_cartesian(xlim = c(log(0.000005), log(0.04)),
+                  ylim = c(0, 1)) +
+  labs(caption = "
+       
+       ")
+p1b
+m1 <- lm.cluster(to_18 ~ lndper + nh_white + nh_black + latino + pop_dens + 
            median_income + some_college + median_age + share_over_64 +
-           state, data = full_set, cluster = full_set$state)
+           state + total_revenue + share_taxes + share_state_fed, data = full_set, cluster = full_set$state)
 
-m2 <- lm(vap_to_18 ~ lndper + nh_white + nh_black + latino +
+m2 <- lm(vap_to_18 ~ lndper + nh_white + nh_black + latino + pop_dens +
            median_income + some_college + median_age + share_over_64 +
-           state, data = filter(full_set, vap_to_18 <= 1))
+           state + total_revenue + share_taxes + share_state_fed, data = filter(full_set, vap_to_18 <= 1))
 
 m3 <- lm(vap_to_18 ~ lndper + nh_white + nh_black + latino +
            median_income + some_college + median_age + share_over_64 +
-           state, data = filter(full_set, vap_to_18 <= 1))
[…]

### 2021-01-27 code/04_did_gap.R

@@ -1,21 +1,22 @@
-#######
-set.seed(38913)
+to <- readRDS("temp/city_to_early_reg.rds") %>%
+  filter(EthnicGroups_EthnicGroup1Desc %in% c("European",
+                                              "Likely African-American")) %>%
+  pivot_wider(id_cols = c("plasub", "state"), names_from = "EthnicGroups_EthnicGroup1Desc",
+              values_from = c("count", "to_18", "to_16", "to_14", "to_12", "to_10"))
+to <- to[complete.cases(to), ] %>%
+  select(plasub) %>% 
+  pull()
 
+#######
 cities <- readRDS("temp/cog_cities.rds") %>% 
+  filter(GEOID %in% to) %>% 
   mutate(pct_change = dper / dper12,
          q = ntile(pct_change, 10)) %>% 
   filter(q %in% c(1:7, 10)) %>% 
   mutate(treated = q == 10) %>% 
-  dplyr::select(place_id, treated, GEOID)
-
-pot_con <- filter(cities, !treated)
-
-census <- readRDS("temp/census_12.rds") %>% 
-  select(population, asian, latino, nh_black, nh_white,
-         median_income, some_college, median_age,
-         share_no_car, GEOID)
-
-cities <- left_join(cities, census)
+  dplyr::select(place_id, treated, population, asian, latino, nh_black, nh_white,
+                median_income, some_college, median_age,
+                share_no_car, GEOID)
 
 cities <- cities[complete.cases(cities), ]
 
@@ -23,9 +24,9 @@ match_data <- cities %>%
   dplyr::select(-place_id, -treated, -GEOID)
 
 # genout <- GenMatch(Tr = cities$treated, X = match_data, replace = T, pop.size = 1000)
-# saveRDS(genout, "temp/genout_pct.rds")
+# saveRDS(genout, "temp/genout_pct_gap.rds")
 
-genout <- readRDS("temp/genout_pct.rds")
+genout <- readRDS("temp/genout_pct_gap.rds")
 
 mout <- Match(Tr = cities$treated, X = match_data,
               estimand = "ATT", Weight.matrix = genout, M = 2)
@@ -36,8 +37,8 @@ varnames <- c("population", "asian", "latino", "nh_black", "nh_white",
               "share_no_car")
 
 balance <- MatchBalance(treated ~ population + asian + latino + nh_black + nh_white +
-                  median_income + some_college + median_age +
[…]

### 2021-01-27 code/05_2wayfe.R

@@ -1,0 +1,163 @@
+
+cities1 <- readRDS("temp/cog_cities.rds") %>% 
+  select(GEOID, lndper, total_revenue, share_state_fed, share_taxes, place_id) %>% 
+  mutate(year = 2017)
+
+
+cities2 <- inner_join(select(cities1, place_id, GEOID),
+                      readRDS("temp/cog_12.rds")) %>% 
+  select(GEOID, lndper, total_revenue, share_state_fed, share_taxes) %>% 
+  mutate(year = 2012)
+
+cities <- bind_rows(cities1, cities2) %>% 
+  select(-place_id)
+
+census <- bind_rows(
+  readRDS("temp/census_12.rds") %>% 
+    mutate(year = 2012),
+  readRDS("temp/census_data.rds") %>% 
+    mutate(year = 2017)
+)
+
+cities <- left_join(cities, census)
+
+to <- readRDS("temp/city_to_14_reg.rds") %>% 
+  group_by(plasub, state) %>%
+  summarize_at(vars(to_18, to_16, to_14, to_12, to_10),
+               ~ weighted.mean(., count)) %>% 
+  select(GEOID = plasub, state, to_18, to_14) %>% 
+  pivot_longer(cols = starts_with("to_"), names_to = "year", values_to = "to") %>% 
+  mutate(year = as.integer(gsub("to_", "20", year)),
+         year = ifelse(year == 2018, 2017, 2012))
+
+to2 <- readRDS("temp/city_to_14_reg.rds") %>% 
+  filter(EthnicGroups_EthnicGroup1Desc %in% c("European", "Likely African-American")) %>% 
+  mutate(race = ifelse(EthnicGroups_EthnicGroup1Desc == "European", "White", "Nonwhite")) %>% 
+  group_by(plasub, state, race) %>%
+  summarize_at(vars(to_18, to_16, to_14, to_12, to_10),
+               ~ sum(. * count)) %>% 
+  select(GEOID = plasub, race, state, to_18, to_14) %>% 
+  pivot_longer(cols = starts_with("to_"), names_to = "year", values_to = "to") %>% 
+  mutate(year = as.integer(gsub("to_", "20", year)),
+         year = ifelse(year == 2018, 2017, 2012)) %>% 
+  pivot_wider(id_cols = c("GEOID", "year", "state"), names_from = "race", values_from = "to")
+
+
+cities1 <- left_join(cities, to)
+
[…]

### 2021-01-27 code/misc/census_12.R

@@ -1,0 +1,83 @@
+c <- get_basic_census_stats("place", 2012) %>%
+  select(-NAME)
+
+ptime <- get_acs("place", variables = c("B08013_001", "B08006_001"), year = 2012, output = "wide") %>%
+  mutate(travel_time = B08013_001E/ B08006_001E) %>%
+  select(GEOID, travel_time)
+
+c <- full_join(c, ptime)
+
+sd <- rbindlist(lapply(unique(filter(fips_codes, as.integer(state_code) < 60)$state_code), function(s){
+  if(!file.exists(paste0("temp/census_sub_", s, "_12.rds"))){
+    j <- get_basic_census_stats("county subdivision", 2012, state = s)
+    t <- get_acs("county subdivision", variables = c("B08013_001", "B08006_001"),
+                 output = "wide", year = 2012, state = s) %>%
+      mutate(travel_time = B08013_001E/ B08006_001E) %>%
+      select(GEOID, travel_time)
+
+    j <- full_join(j, t)
+
+    saveRDS(j, paste0("temp/census_sub_", s, "_12.rds"))
+  }else{
+    j <- readRDS(paste0("temp/census_sub_", s, "_12.rds"))
+  }
+  return(j)
+})) %>%
+  mutate(GEOID = paste0(substring(GEOID, 1, 2), substring(GEOID, 6))) %>%
+  filter(!GEOID %in% c$GEOID)
+
+sd1 <- sd %>%
+  group_by(GEOID) %>%
+  summarize_at(vars(asian, hawaiian_pac_island, latino, latino_black,
+                    native_american, nh_black, nh_white, median_income,
+                    some_college, unem, median_age, share_non_citizen, travel_time,
+                    share_moved, share_no_car, share_over_64, share_under40, pop_dens),
+               ~ weighted.mean(., population, na.rm = T))
+
+sd2 <- sd %>%
+  group_by(GEOID) %>%
+  summarize(population = sum(population, na.rm = T),
+            vap = sum(vap, na.rm = T))
+
+sd <- inner_join(sd1, sd2)
+
+c2 <- bind_rows(c, sd)
+
+pcvap <- fread("../regular_data/CVAP_2008-2012_ACS_csv_files/Place.csv") %>%
+  mutate(GEOID = substring(GEOID, 8),
+         LNTITLE = ifelse(LNTITLE == "Total", "total",
[…]

### 2021-01-27 markdown/fees_fines_to.Rmd
keep writing

@@
 Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities’ alienation from government.
-American cities’ reliance on fines and fees revenue increased significantly following the 2008 recession—as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services [@Singla2020; @Mughan2020; @Kirk2020; @Martin2018].
+American cities’ reliance on fines and fees revenue increased significantly following the 2008 recession --- as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services [@Singla2020; @Mughan2020; @Kirk2020; @Martin2018].
 Although a body of literature developed over the past decade indicates that criminalization chills political participation, no work has directly investigated the relationship between fines and fees revenue collection and voter turnout.
@@
 In New York City, concentrated stop-and-frisk activity was associated with *reduced* turnout in Congressional elections, but *increased* turnout in the 2008 presidential election as well as the local mayoral election in 2013 [@Laniyonu2019].
-It may also be the case that proximal contact differs from personal contact with the criminal legal system—whereas direct experience with criminalization (and incarceration in particular) reduces the likelihood of voting, proximal or indirect experience produces more mixed results.
-Hannah Walker suggests that police contact that does not lead to a criminal conviction may even mobilize voters—but her survey questions specifically excluded “minor traffic stops,” a primary site of police ticketing [@Walker2014].
+It may also be the case that proximal contact differs from personal contact with the criminal legal system --- whereas direct experience with criminalization (and incarceration in particular) reduces the likelihood of voting, proximal or indirect experience produces more mixed results.
+Hannah Walker suggests that police contact that does not lead to a criminal conviction may even mobilize voters --- but her survey questions specifically excluded “minor traffic stops,” a primary site of police ticketing [@Walker2014].
 
@@
 
-Public perceptions of abusive police practices, such as high-profile incidents of police violence or racially discriminatory street stops, can reduce willingness to report crimes or cooperate with law enforcement [@Desmond2016; @Tyler2014).
+Public perceptions of abusive police practices, such as high-profile incidents of police violence or racially discriminatory street stops, can reduce willingness to report crimes or cooperate with law enforcement [@Desmond2016; @Tyler2014].
 Legitimacy studies have largely focused on police violence or police street stops, but new evidence related to fines and fees has recently emerged.
@@
 
-Although the conceptual framework for police legitimacy has been fruitfully critiqued—Monica @Bell2017 points to legal estrangement and structural exclusion in order to shift the theoretical focus from perceptions of unfairness to substantively unjust practices—the empirical literature on legitimacy is useful to demonstrate how police practices can alienate those subjected to them.
+Although the conceptual framework for police legitimacy has been fruitfully critiqued --- Monica @Bell2017 points to legal estrangement and structural exclusion in order to shift the theoretical focus from perceptions of unfairness to substantively unjust practices --- the empirical literature on legitimacy is useful to demonstrate how police practices can alienate those subjected to them.
 The alienating effect of criminal legal exposure has also been tied to institutional avoidance [see, for instance, @Brayne2014].
@@
 
-Figure \ref{fig:marg1} makes clear that higher fees and fines collections lead to lower turnout.
-The left-hand panel shows the simple bivariate relationship between turnout among registered voters in 2018 and fees and fines collection.
-The right-hand panel shows the bivariate relationship between the 2018 white-Black turnout gap and fines collections.
-The turnout gap is calculated by dividing the number of ballots cast by each racial group according to L2 by the estimated 2018 citizen voting age population (CVAP) from the Census Bureau to account for possible registration differences between groups.
+Figures \ref{fig:to} and \ref{fig:to-gap} make clear that higher fees and fines collections are associated with lower turnout *and* a lower turnout gap.
+Figure \ref{fig:to} plots the simple bivariate relationship between turnout among registered voters in 2018 and fees and fines collection, while Figure \ref{fig:to-gap} shows the bivariate relationship between the 2018 white-Black turnout gap and fines collections.
+The turnout gap is calculated by dividing the number of ballots cast by each racial group according to L2 by the estimated 2018 citizen voting age population (CVAP) for that group from the Census Bureau to account for possible registration differences between groups.
 
-```{r, figures-side, fig.show="hold", out.width="50%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:marg1}Dollars per Resident and 2018 Turnout", fig.pos = "H"}
-p1 <- readRDS("./temp/simple_scat.rds")
-p2 <- readRDS("./temp/simple_scat_gap_bw.rds")
-print(p1)
-print(p2)
-```
-
-Although Figure \ref{fig:marg1} shows that there is a relationship between collections and turnout and the turnout gap, the simple scatter plots cannot demonstrate a causal relationship.
+Figures \ref{fig:to} and \ref{fig:to-gap} cannot demonstrate a causal relationship.
 To investigate whether there is such a relationship, we employ two-way fixed effect models.
@@
 The second observation includes their (logged + 1) fees and fines from the 2017 COG, their 2018 turnout (gap), and their 2018 5-year ACS demographics.
-In each case, turnout is measured only among the individuals who were registered in a given municipality in both 2014 and 2018 to control for changes in registration rates, and in Model 2 the turnout gap is calculated using CVAP.
+In each case, turnout is measured only among the individuals who were registered in a given municipality in both 2014 and 2018 to control for changes in registration rates, and in Model 2 the turnout gap is calculated using CVAP in each year.
 Table \ref{tab:tab1} presents the results of these models.
+Table \ref{tab:tab1} demonstrates that fees and fines collections likely have a causal effect on voter turnout and the turnout gap.
+A 10 percent increase in collections is associated with a roughly 3.3 percentage point decrease in turnout, and a 1.8 percentage point decrease in the racial turnout gap.
+
+### Discussion {-}
+
+Our preliminary results with respect to turnout are not particularly surprising: prior literature led us to expect that, as municipalities increased their fees and fines, voters would become alienated from their government and opt out of democratic participation.
+Nevertheless, these are substantive impacts.
+
+That increased collections reduce the racial turnout gap is surprising, and the opposite of what we expected to find.
+This could reflect racially disparate policing in cities with low fee collection.
+It is possible that as fees and fines collections increase a larger share of the population --- and, thus, more white voters --- may have a negative interaction with a police officer, thereby reducing racial disparities in fines and fees and, consequently, discrepancies in the racial turnout gap.
+
+Our full study will include a more narrow analysis of turnout in jurisdictions that dramatically increased or decreased ticketing over a comparatively short period of time.
+For instance, a Florida Times-Union investigation revealed that police in four counties disproportionately issued tickets to Black pedestrians [@Sanders2017].
+In Tampa, police issued thousands of tickets to Black cyclists between 2012 and 2015 --- after journalists reported on the problem, the city began to issue fewer than 100 citations each year as of 2018 [@Zayas2015; @Frago2019].
+Systematically conducting such an analysis would likely require collecting and organizing new data, as city-level police ticketing data is inconsistent and not always public information.
+
+\newpage
+### Bibliography {-}
+<div id="refs"></div>
+
+\newpage
+\pagenumbering{gobble}
+\pagenumbering{arabic}
+## Appendix A {-}
+
+```{r, figures-side, fig.show="hold", out.height="40%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:to}Dollars per Resident and 2018 Turnout", fig.pos = "H", fig.align = "center"}
+p1 <- readRDS("./temp/simple_scat.rds")
+print(p1)
+```
+
+```{r, fig.show="hold", out.height="40%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:to-gap}Dollars per Resident and 2018 Turnout Gap", fig.pos = "H", fig.align = "center"}
+p1 <- readRDS("./temp/simple_scat_gap_bw.rds")
+print(p1)
+```
 
@@
 \end{singlespace}
-
-### Discussion {-}
-
-The significant negative association in our analysis provides some support for our first hypothesis: though our preliminary analyses cannot establish causality, they are consistent with a causal story that links fines and fees practices with lower political participation among those who are subjected to them.
-On the other hand, officials in municipalities with lower turnout may feel more free to rely on fees and fines for revenue collection because they have less fear of electoral repercussions.
-Our full study will explore these causal relationships directly by supplementing our initial analysis with an analysis of voter turnout and revenue reliance change over time.
-
-That the racial turnout gap is smaller in cities with more fees and fines is surprising, and the opposite of what we expected to find.
-This could reflect racially disparate policing in cities with low fee collection.
-It is possible that cities with *low* fees and fines collections disproportionately penalize nonwhite residents; as fees and fines collections increase, however, a larger share of the population --- and, thus, more white voters --- may have a negative interaction with a police officer, thereby *reducing* racial disparities and consequently discrepancies in the racial turnout gap.
-
-Our full study will include a more narrow analysis of turnout in jurisdictions that dramatically increased or decreased ticketing over a comparatively short period of time.
-For instance, a Florida Times-Union investigation revealed that police in four counties disproportionately issued tickets to Black pedestrians [@Sanders2017].
-In Tampa, police issued thousands of tickets to Black cyclists between 2012 and 2015—after journalists reported on the problem, the city began to issue fewer than 100 citations each year as of 2018 [@Zayas2015; @Frago2019].
-Systematically conducting such an analysis would likely require collecting and organizing new data, as city-level police ticketing data is inconsistent and not always public information.
-
-\newpage
-### Bibliography

### 2021-01-27 markdown/fees_fines_to.tex
keep writing

@@
 Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities' alienation from government.
-American cities' reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (Singla, Kirschner, and Stone \protect\hyperlink{ref-Singla2020}{2020}; Mughan \protect\hyperlink{ref-Mughan2020}{2020}; Kirk, Fernandes, and Friedman \protect\hyperlink{ref-Kirk2020}{2020}; Martin \protect\hyperlink{ref-Martin2018}{2018}).
+American cities' reliance on fines and fees revenue increased significantly following the 2008 recession --- as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (Singla, Kirschner, and Stone \protect\hyperlink{ref-Singla2020}{2020}; Mughan \protect\hyperlink{ref-Mughan2020}{2020}; Kirk, Fernandes, and Friedman \protect\hyperlink{ref-Kirk2020}{2020}; Martin \protect\hyperlink{ref-Martin2018}{2018}).
 Although a body of literature developed over the past decade indicates that criminalization chills political participation, no work has directly investigated the relationship between fines and fees revenue collection and voter turnout.
@@
 In New York City, concentrated stop-and-frisk activity was associated with \emph{reduced} turnout in Congressional elections, but \emph{increased} turnout in the 2008 presidential election as well as the local mayoral election in 2013 (Laniyonu \protect\hyperlink{ref-Laniyonu2019}{2019}).
-It may also be the case that proximal contact differs from personal contact with the criminal legal system---whereas direct experience with criminalization (and incarceration in particular) reduces the likelihood of voting, proximal or indirect experience produces more mixed results.
-Hannah Walker suggests that police contact that does not lead to a criminal conviction may even mobilize voters---but her survey questions specifically excluded ``minor traffic stops,'' a primary site of police ticketing (Walker \protect\hyperlink{ref-Walker2014}{2014}).
+It may also be the case that proximal contact differs from personal contact with the criminal legal system --- whereas direct experience with criminalization (and incarceration in particular) reduces the likelihood of voting, proximal or indirect experience produces more mixed results.
+Hannah Walker suggests that police contact that does not lead to a criminal conviction may even mobilize voters --- but her survey questions specifically excluded ``minor traffic stops,'' a primary site of police ticketing (Walker \protect\hyperlink{ref-Walker2014}{2014}).
 
@@
 
-Public perceptions of abusive police practices, such as high-profile incidents of police violence or racially discriminatory street stops, can reduce willingness to report crimes or cooperate with law enforcement {[}Desmond, Papachristos, and Kirk (\protect\hyperlink{ref-Desmond2016}{2016}); Tyler, Fagan, and Geller (\protect\hyperlink{ref-Tyler2014}{2014})).
+Public perceptions of abusive police practices, such as high-profile incidents of police violence or racially discriminatory street stops, can reduce willingness to report crimes or cooperate with law enforcement (Desmond, Papachristos, and Kirk \protect\hyperlink{ref-Desmond2016}{2016}; Tyler, Fagan, and Geller \protect\hyperlink{ref-Tyler2014}{2014}).
 Legitimacy studies have largely focused on police violence or police street stops, but new evidence related to fines and fees has recently emerged.
@@
 
-Although the conceptual framework for police legitimacy has been fruitfully critiqued---Monica Bell (\protect\hyperlink{ref-Bell2017}{2017}) points to legal estrangement and structural exclusion in order to shift the theoretical focus from perceptions of unfairness to substantively unjust practices---the empirical literature on legitimacy is useful to demonstrate how police practices can alienate those subjected to them.
+Although the conceptual framework for police legitimacy has been fruitfully critiqued --- Monica Bell (\protect\hyperlink{ref-Bell2017}{2017}) points to legal estrangement and structural exclusion in order to shift the theoretical focus from perceptions of unfairness to substantively unjust practices --- the empirical literature on legitimacy is useful to demonstrate how police practices can alienate those subjected to them.
 The alienating effect of criminal legal exposure has also been tied to institutional avoidance (see, for instance, Brayne \protect\hyperlink{ref-Brayne2014}{2014}).
@@
 
-Figure \ref{fig:marg1} makes clear that higher fees and fines collections lead to lower turnout.
-The left-hand panel shows the simple bivariate relationship between turnout among registered voters in 2018 and fees and fines collection.
-The right-hand panel shows the bivariate relationship between the 2018 white-Black turnout gap and fines collections.
-The turnout gap is calculated by dividing the number of ballots cast by each racial group according to L2 by the estimated 2018 citizen voting age population (CVAP) from the Census Bureau to account for possible registration differences between groups.
+Figures \ref{fig:to} and \ref{fig:to-gap} make clear that higher fees and fines collections are associated with lower turnout \emph{and} a lower turnout gap.
+Figure \ref{fig:to} plots the simple bivariate relationship between turnout among registered voters in 2018 and fees and fines collection, while Figure \ref{fig:to-gap} shows the bivariate relationship between the 2018 white-Black turnout gap and fines collections.
+The turnout gap is calculated by dividing the number of ballots cast by each racial group according to L2 by the estimated 2018 citizen voting age population (CVAP) for that group from the Census Bureau to account for possible registration differences between groups.
 
-\begin{figure}[H]
-\includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/figures-side-1} \includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/figures-side-2} \caption{\label{fig:marg1}Dollars per Resident and 2018 Turnout}\label{fig:figures-side}
-\end{figure}
-
-Although Figure \ref{fig:marg1} shows that there is a relationship between collections and turnout and the turnout gap, the simple scatter plots cannot demonstrate a causal relationship.
+Figures \ref{fig:to} and \ref{fig:to-gap} cannot demonstrate a causal relationship.
 To investigate whether there is such a relationship, we employ two-way fixed effect models.
@@
 The second observation includes their (logged + 1) fees and fines from the 2017 COG, their 2018 turnout (gap), and their 2018 5-year ACS demographics.
-In each case, turnout is measured only among the individuals who were registered in a given municipality in both 2014 and 2018 to control for changes in registration rates, and in Model 2 the turnout gap is calculated using CVAP.
+In each case, turnout is measured only among the individuals who were registered in a given municipality in both 2014 and 2018 to control for changes in registration rates, and in Model 2 the turnout gap is calculated using CVAP in each year.
 Table \ref{tab:tab1} presents the results of these models.
-
-\begin{singlespace}
-\input{"../temp/2wfe_reg_clean.tex"}
-\end{singlespace}
+Table \ref{tab:tab1} demonstrates that fees and fines collections likely have a causal effect on voter turnout and the turnout gap.
+A 10 percent increase in collections is associated with a roughly 3.3 percentage point decrease in turnout, and a 1.8 percentage point decrease in the racial turnout gap.
 
@@
 
-The significant negative association in our analysis provides some support for our first hypothesis: though our preliminary analyses cannot establish causality, they are consistent with a causal story that links fines and fees practices with lower political participation among those who are subjected to them.
-On the other hand, officials in municipalities with lower turnout may feel more free to rely on fees and fines for revenue collection because they have less fear of electoral repercussions.
-Our full study will explore these causal relationships directly by supplementing our initial analysis with an analysis of voter turnout and revenue reliance change over time.
+Our preliminary results with respect to turnout are not particularly surprising: prior literature led us to expect that, as municipalities increased their fees and fines, voters would become alienated from their government and opt out of democratic participation.
+Nevertheless, these are substantive impacts.
 
-That the racial turnout gap is smaller in cities with more fees and fines is surprising, and the opposite of what we expected to find.
+That increased collections reduce the racial turnout gap is surprising, and the opposite of what we expected to find.
 This could reflect racially disparate policing in cities with low fee collection.
-It is possible that cities with \emph{low} fees and fines collections disproportionately penalize nonwhite residents; as fees and fines collections increase, however, a larger share of the population --- and, thus, more white voters --- may have a negative interaction with a police officer, thereby \emph{reducing} racial disparities and consequently discrepancies in the racial turnout gap.
+It is possible that as fees and fines collections increase a larger share of the population --- and, thus, more white voters --- may have a negative interaction with a police officer, thereby reducing racial disparities in fines and fees and, consequently, discrepancies in the racial turnout gap.
 
@@
 For instance, a Florida Times-Union investigation revealed that police in four counties disproportionately issued tickets to Black pedestrians (Sanders and Conarck \protect\hyperlink{ref-Sanders2017}{2017}).
-In Tampa, police issued thousands of tickets to Black cyclists between 2012 and 2015---after journalists reported on the problem, the city began to issue fewer than 100 citations each year as of 2018 (Zayas \protect\hyperlink{ref-Zayas2015}{2015}; Frago \protect\hyperlink{ref-Frago2019}{2019}).
+In Tampa, police issued thousands of tickets to Black cyclists between 2012 and 2015 --- after journalists reported on the problem, the city began to issue fewer than 100 citations each year as of 2018 (Zayas \protect\hyperlink{ref-Zayas2015}{2015}; Frago \protect\hyperlink{ref-Frago2019}{2019}).
 Systematically conducting such an analysis would likely require collecting and organizing new data, as city-level police ticketing data is inconsistent and not always public information.
@@
 
+\newpage
+\pagenumbering{gobble}
+\pagenumbering{arabic}
+
+\hypertarget{appendix-a}{%
+\subsection*{Appendix A}\label{appendix-a}}
+\addcontentsline{toc}{subsection}{Appendix A}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[height=0.4\textheight]{fees_fines_to_files/figure-latex/figures-side-1}
+
+}
+
+\caption{\label{fig:to}Dollars per Resident and 2018 Turnout}\label{fig:figures-side}
+\end{figure}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[height=0.4\textheight]{fees_fines_to_files/figure-latex/unnamed-chunk-1-1}
+
+}
+
+\caption{\label{fig:to-gap}Dollars per Resident and 2018 Turnout Gap}\label{fig:unnamed-chunk-1}
+\end{figure}
+
+\begin{singlespace}
+\input{"../temp/2wfe_reg_clean.tex"}
+\end{singlespace}
+
 \end{document}

### 2021-01-28 markdown/fees_fines_to.Rmd
final (maybe?) for asa submission

@@
 subtitle: "Fines, Fees, and Turnout"
-thanks: The authors thank XX for their feedback and support. All errors are our responsibility. 
+thanks: Prepared in preparation for the 2021 Annual Meeting of the American Sociological Association. Please do not circulate without permission. 
 author:
@@
     - \usepackage{setspace}
-abstract: "This is an abstract."
+abstract: |
+  In recent years, scholars have documented the effects of criminalization on citizens’ relationship with their government.
+The American criminal legal system is an important site of political socialization, and its structural inequities have alienated affected communities.
+Sociologists have observed that this results in *system* or *institutional avoidance*, while political scientists have measured the effects of police stops, incarceration, and felony disenfranchisement on political participation --- particularly in the voter booth.
+
+  Despite this increase in research, relatively little work has explored the effects of one of the most routine interactions Americans have with police: namely, ticketing for low-level offenses.
+In the aftermath of the 2008 financial crisis, cash-strapped municipalities increasingly turned to fees and fines collections to fund local services.
+The democratic effects of this change, however, have gone largely unstudied.
+Using data from the Census of Governments and the national voter file, we fill this hole in the literature.
+Our preliminary analyses indicate that municipalities with higher fees and fines collections have lower turnout, and that this relationship is likely causal.
+Moreover, we find that municipalities with higher fees and fines have a *lower* racial turnout gap.
+Taken together, our project raises important questions about the (racial) representational effects of policing for profit.
 ---
@@
 \pagenumbering{arabic}
-\begin{center}
-Policing for Profit and the Undermining of Democracy: Fines, Fees, and Turnout \\
-Jonathan Ben-Menachem and Kevin Morris
-\end{center}
+### Introduction {-}
 
@@
 Although a body of literature developed over the past decade indicates that criminalization chills political participation, no work has directly investigated the relationship between fines and fees revenue collection and voter turnout.
-This project intends to fill that gap by testing whether fines and fees at the municipal level influence voter turnout.
+This project intends to fill that gap by testing this relationship at the local level.
 
@@
 We expect to find that municipalities where more revenue is raised per resident saw lower turnout, other things being equal.
-Because the American criminal legal system falls disproportionately on minorities, we also expect that the racial turnout gap [@Fraga2018] will be larger in municipalities that rely more heavily on fines and fees.
+Because the American criminal legal system disproportionately punishes minorities, we also expect that the racial turnout gap [@Fraga2018] will be larger in municipalities that rely more heavily on fines and fees.
 Of course, fines and fees imposition may be related to turnout without necessarily indicating a causal relationship.
-For this reason we leverage data on fines collections and turnout from multiple time periods to investigate the causal relationship.
+To investigate the causal relationship we leverage data on fines collections and turnout from multiple time periods.
+
+### The Chilling Effect of Fines and Fees {-}
 
@@
 More specifically, many states require payment of fees as a condition of criminal legal supervision or the payment of all legal financial obligations as a condition of completing a sentence, and failure to comply with supervision conditions or sentence completion conditions can be a barrier to voting rights restoration.
-A recent report from the Sentencing Project estimates that more than 5 million Americans are legally barred from voting due to a felony conviction [@Uggen2020], and the role of fees and fines in the context of felony disenfranchisement has taken on greater significance in the past year.
-After Floridians voted to restore voting rights to individuals with felony convictions, Florida legislators passed legislation requiring these individuals to pay off the fees and fines associated with their original sentence.
+A recent report from the Sentencing Project estimates that more than 5 million Americans are legally barred from voting due to a felony conviction [@Uggen2020], and the role of fees and fines in the context of felony disenfranchisement has taken on greater significance in the past two years.
+After Floridians voted to restore voting rights to individuals with felony convictions in 2018, Florida legislators passed legislation requiring these individuals to pay off the fees and fines associated with their original sentence.
 Because Florida does not maintain good records on who owes how much, this has proved a major hurdle for would-be voters.
@@
 The alienating effect of criminal legal exposure has also been tied to institutional avoidance [see, for instance, @Brayne2014].
-.
 
@@
 
-In order to ascertain whether fines and fees practices affect voter turnout, we exploit data from the 2012 and 2017 Census of Governments (COG) and national voter file data.
-The COG, a project of the US Census Bureau, collects budget data for all local governments every five years, and the most recent survey was in 2017.
+In order to ascertain whether fines and fees practices affect voter turnout, we exploit data from the 2012 and 2017 Census of Governments (COG) and the national voter file data.
+The COG, a project of the US Census Bureau, collects budget data for all local governments every five years.
 The COG asks cities how much revenue they collect from “penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation...
@@
 
-Unfortunately, the COG data does not include voter turnout, and turnout data is not generally available at this level.
+The COG data does not include voter turnout, and turnout data is not generally available at this level.
 Therefore, in order to determine municipality-level turnout, we employ a national, geocoded voter file.
@@
 Because the L2 national voter file includes estimates of each voter’s racioethnic identity, we can also use these data to determine the *racial turnout gap* in each municipality.
-These records are just estimates, and may be imprecise at the individual level.
+These records are just estimates, and may be imprecise at the individual-level.
 However, we assume that this presents less of a problem when aggregating to the municipality-level.
@@
 
-Figures \ref{fig:to} and \ref{fig:to-gap} make clear that higher fees and fines collections are associated with lower turnout *and* a lower turnout gap.
+Figures \ref{fig:to} and \ref{fig:to-gap} (see the appendix) make clear that higher fees and fines collections are associated with lower turnout *and* a lower turnout gap.
 Figure \ref{fig:to} plots the simple bivariate relationship between turnout among registered voters in 2018 and fees and fines collection, while Figure \ref{fig:to-gap} shows the bivariate relationship between the 2018 white-Black turnout gap and fines collections.
@@
 Nevertheless, these are substantive impacts.
+Our full paper will explore this causal relationship in greater depth using alternative estimation strategies.
 
@@
 It is possible that as fees and fines collections increase a larger share of the population --- and, thus, more white voters --- may have a negative interaction with a police officer, thereby reducing racial disparities in fines and fees and, consequently, discrepancies in the racial turnout gap.
-
-Our full study will include a more narrow analysis of turnout in jurisdictions that dramatically increased or decreased ticketing over a comparatively short period of time.
-For instance, a Florida Times-Union investigation revealed that police in four counties disproportionately issued tickets to Black pedestrians [@Sanders2017].
-In Tampa, police issued thousands of tickets to Black cyclists between 2012 and 2015 --- after journalists reported on the problem, the city began to issue fewer than 100 citations each year as of 2018 [@Zayas2015; @Frago2019].
-Systematically conducting such an analysis would likely require collecting and organizing new data, as city-level police ticketing data is inconsistent and not always public information.
+Additionally, it’s possible that the effect of fines and fees practices on voter turnout is not uniformly distributed across racioethnic groups; @Walker2014 found that proximal criminal legal contact mobilizes nonwhite voters to a greater extent than white voters.
+It could also be the case that Black voters are aware of the effect of descriptive representation on fines and fees practices, which would be compatible with the mobilization hypothesis.
 

### 2021-01-28 markdown/fees_fines_to.tex
final (maybe?) for asa submission

@@
 
-\title{Policing for Profit and the Undermining of Democracy\thanks{The authors thank XX for their feedback and support. All errors are our responsibility.}}
+\title{Policing for Profit and the Undermining of Democracy\thanks{Prepared in preparation for the 2021 Annual Meeting of the American Sociological Association.
+Please do not circulate without permission.}}
 \usepackage{etoolbox}
@@
 \author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{Researcher, Brennan Center for Justice at NYU School of Law (\href{mailto:kevin.morris@nyu.edu}{\nolinkurl{kevin.morris@nyu.edu}})}}
-\date{January 27, 2021}
+\date{January 28, 2021}
 
@@
 \begin{abstract}
-This is an abstract.
+In recent years, scholars have documented the effects of criminalization on citizens' relationship with their government.
+The American criminal legal system is an important site of political socialization, and its structural inequities have alienated affected communities.
+Sociologists have observed that this results in \emph{system} or \emph{institutional avoidance}, while political scientists have measured the effects of police stops, incarceration, and felony disenfranchisement on political participation --- particularly in the voter booth.
+
+Despite this increase in research, relatively little work has explored the effects of one of the most routine interactions Americans have with police: namely, ticketing for low-level offenses.
+In the aftermath of the 2008 financial crisis, cash-strapped municipalities increasingly turned to fees and fines collections to fund local services.
+The democratic effects of this change, however, have gone largely unstudied.
+Using data from the Census of Governments and the national voter file, we fill this hole in the literature.
+Our preliminary analyses indicate that municipalities with higher fees and fines collections have lower turnout, and that this relationship is likely causal.
+Moreover, we find that municipalities with higher fees and fines have a \emph{lower} racial turnout gap.
+Taken together, our project raises important questions about the (racial) representational effects of policing for profit.
 \end{abstract}
@@
 \pagenumbering{arabic}
-\begin{center}
-Policing for Profit and the Undermining of Democracy: Fines, Fees, and Turnout \\
-Jonathan Ben-Menachem and Kevin Morris
-\end{center}
+
+\hypertarget{introduction}{%
+\subsubsection*{Introduction}\label{introduction}}
+\addcontentsline{toc}{subsubsection}{Introduction}
 
@@
 We expect to find that municipalities where more revenue is raised per resident saw lower turnout, other things being equal.
-Because the American criminal legal system falls disproportionately on minorities, we also expect that the racial turnout gap (Fraga \protect\hyperlink{ref-Fraga2018}{2018}) will be larger in municipalities that rely more heavily on fines and fees.
+Because the American criminal legal system disproportionately punishes minorities, we also expect that the racial turnout gap (Fraga \protect\hyperlink{ref-Fraga2018}{2018}) will be larger in municipalities that rely more heavily on fines and fees.
 Of course, fines and fees imposition may be related to turnout without necessarily indicating a causal relationship.
-For this reason we leverage data on fines collections and turnout from multiple time periods to investigate the causal relationship.
+To investigate the causal relationship we leverage data on fines collections and turnout from multiple time periods.
+
+\hypertarget{the-chilling-effect-of-fines-and-fees}{%
+\subsubsection*{The Chilling Effect of Fines and Fees}\label{the-chilling-effect-of-fines-and-fees}}
+\addcontentsline{toc}{subsubsection}{The Chilling Effect of Fines and Fees}
 
@@
 A recent report from the Sentencing Project estimates that more than 5 million Americans are legally barred from voting due to a felony conviction (Uggen et al.
-\protect\hyperlink{ref-Uggen2020}{2020}), and the role of fees and fines in the context of felony disenfranchisement has taken on greater significance in the past year.
-After Floridians voted to restore voting rights to individuals with felony convictions, Florida legislators passed legislation requiring these individuals to pay off the fees and fines associated with their original sentence.
+\protect\hyperlink{ref-Uggen2020}{2020}), and the role of fees and fines in the context of felony disenfranchisement has taken on greater significance in the past two years.
+After Floridians voted to restore voting rights to individuals with felony convictions in 2018, Florida legislators passed legislation requiring these individuals to pay off the fees and fines associated with their original sentence.
 Because Florida does not maintain good records on who owes how much, this has proved a major hurdle for would-be voters.
@@
 The alienating effect of criminal legal exposure has also been tied to institutional avoidance (see, for instance, Brayne \protect\hyperlink{ref-Brayne2014}{2014}).
-.
 
@@
 
-In order to ascertain whether fines and fees practices affect voter turnout, we exploit data from the 2012 and 2017 Census of Governments (COG) and national voter file data.
-The COG, a project of the US Census Bureau, collects budget data for all local governments every five years, and the most recent survey was in 2017.
+In order to ascertain whether fines and fees practices affect voter turnout, we exploit data from the 2012 and 2017 Census of Governments (COG) and the national voter file data.
+The COG, a project of the US Census Bureau, collects budget data for all local governments every five years.
 The COG asks cities how much revenue they collect from ``penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation\ldots{} and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).'' As indicated by previous researchers, these data serve as a useful proxy for the prevalence of police ticketing (Goldstein, Sances, and You \protect\hyperlink{ref-Goldstein2020}{2020}; Sances and You \protect\hyperlink{ref-Sances2017}{2017}).
 
-Unfortunately, the COG data does not include voter turnout, and turnout data is not generally available at this level.
+The COG data does not include voter turnout, and turnout data is not generally available at this level.
 Therefore, in order to determine municipality-level turnout, we employ a national, geocoded voter file.
@@
 Because the L2 national voter file includes estimates of each voter's racioethnic identity, we can also use these data to determine the \emph{racial turnout gap} in each municipality.
-These records are just estimates, and may be imprecise at the individual level.
+These records are just estimates, and may be imprecise at the individual-level.
 However, we assume that this presents less of a problem when aggregating to the municipality-level.
@@
 
-Figures \ref{fig:to} and \ref{fig:to-gap} make clear that higher fees and fines collections are associated with lower turnout \emph{and} a lower turnout gap.
+Figures \ref{fig:to} and \ref{fig:to-gap} (see the appendix) make clear that higher fees and fines collections are associated with lower turnout \emph{and} a lower turnout gap.
 Figure \ref{fig:to} plots the simple bivariate relationship between turnout among registered voters in 2018 and fees and fines collection, while Figure \ref{fig:to-gap} shows the bivariate relationship between the 2018 white-Black turnout gap and fines collections.
@@
 It is possible that as fees and fines collections increase a larger share of the population --- and, thus, more white voters --- may have a negative interaction with a police officer, thereby reducing racial disparities in fines and fees and, consequently, discrepancies in the racial turnout gap.
-
-Our full study will include a more narrow analysis of turnout in jurisdictions that dramatically increased or decreased ticketing over a comparatively short period of time.
-For instance, a Florida Times-Union investigation revealed that police in four counties disproportionately issued tickets to Black pedestrians (Sanders and Conarck \protect\hyperlink{ref-Sanders2017}{2017}).
-In Tampa, police issued thousands of tickets to Black cyclists between 2012 and 2015 --- after journalists reported on the problem, the city began to issue fewer than 100 citations each year as of 2018 (Zayas \protect\hyperlink{ref-Zayas2015}{2015}; Frago \protect\hyperlink{ref-Frago2019}{2019}).
-Systematically conducting such an analysis would likely require collecting and organizing new data, as city-level police ticketing data is inconsistent and not always public information.
+Additionally, it's possible that the effect of fines and fees practices on voter turnout is not uniformly distributed across racioethnic groups; Walker (\protect\hyperlink{ref-Walker2014}{2014}) found that proximal criminal legal contact mobilizes nonwhite voters to a greater extent than white voters.
+It could also be the case that Black voters are aware of the effect of descriptive representation on fines and fees practices, which would be compatible with the mobilization hypothesis.
 
@@
 Fraga, Bernard L. 2018. \emph{The Turnout Gap: Race, Ethnicity, and Political Inequality in a Diversifying America}. 1st ed. Cambridge University Press. \url{https://doi.org/10.1017/9781108566483}.
-
-\leavevmode\hypertarget{ref-Frago2019}{}%
-Frago, Charlie.
-2019.
-``Tampa Police Have `Evolved' on Biking While Black, Chief Says.'' \emph{Tampa Bay Times}, October 24, 2019.
-\url{https://www.tampabay.com/news/tampa/2019/10/24/tampa-police-have-evolved-on-biking-while-black-chief-says/}.
 
@@
 
-\leavevmode\hypertarget{ref-Sanders2017}{}%
-Sanders, Topher, and Benjamin Conarck.
-2017.
-``Florida Police Issue Hundreds of Bad Pedestrian Tickets Every Year Because They Don't Seem to Know the Law.'' \emph{ProPublica}, December 20, 2017.
-\url{https://www.propublica.org/article/florida-police-issue-hundreds-of-bad-pedestrian-tickets-every-year-because-they-dont-seem-to-know-the-law?token=CpfrqXaMuR8UnJ5-FryRkVwuKl3C98Ae}.
-
 \leavevmode\hypertarget{ref-Singla2020}{}%
@@
 Weaver, Vesla M., and Amy E. Lerman. 2010. ``Political Consequences of the Carceral State.'' \emph{American Political Science Review} 104 (4): 817--33. \url{https://doi.org/10.1017/S0003055410000456}.
-
-\leavevmode\hypertarget{ref-Zayas2015}{}%
-Zayas, Alexandra.
-2015.
-``How Riding Your Bike Can Land You in Trouble with the Cops --- If You're Black.'' \emph{Tampa Bay Times}, April 15, 2015.
-\url{https://www.tampabay.com/news/publicsafety/how-riding-your-bike-can-land-you-in-trouble-with-the-cops---if-youre-black/2225966/}.
 \end{cslreferences}

### 2021-01-28 code/01_cog.R

@@ -191,9 +191,7 @@ cities <- inner_join(mutate(d, GEOID = paste0(state, fips)), c2, by = "GEOID") %
   mutate(lnbl = log(nh_black + 1))
 
 cities <- left_join(cities, select(d12_good,
-                                   place_id, lndper12 = lndper))
-
-cities <- left_join(cities, cvap)
+                                   place_id, lndper12 = lndper, dper_12 = dper))
 
 cities <- left_join(cities, rev)
 

### 2021-01-28 code/04_did_gap.R

@@ -10,13 +10,18 @@ to <- to[complete.cases(to), ] %>%
 #######
 cities <- readRDS("temp/cog_cities.rds") %>% 
   filter(GEOID %in% to) %>% 
-  mutate(pct_change = dper / dper12,
+  mutate(pct_change = dper / dper_12,
          q = ntile(pct_change, 10)) %>% 
   filter(q %in% c(1:7, 10)) %>% 
   mutate(treated = q == 10) %>% 
-  dplyr::select(place_id, treated, population, asian, latino, nh_black, nh_white,
-                median_income, some_college, median_age,
-                share_no_car, GEOID)
+  dplyr::select(place_id, treated, GEOID)
+
+census <- readRDS("temp/census_12.rds") %>% 
+  select(population, asian, latino, nh_black, nh_white,
+         median_income, some_college, median_age,
+         share_no_car, GEOID)
+
+cities <- left_join(cities, census)
 
 cities <- cities[complete.cases(cities), ]
 
@@ -117,8 +122,8 @@ cities <- left_join(
   mutate(weight = ifelse(is.na(weight), 0, weight))
 ##############################
 dper <- readRDS("temp/cog_cities.rds") %>% 
-  select(GEOID, dper, dper12) %>% 
-  pivot_longer(cols = c("dper", "dper12"), names_to = "year") %>% 
+  select(GEOID, dper, dper_12) %>% 
+  pivot_longer(cols = c("dper", "dper_12"), names_to = "year") %>% 
   mutate(year = ifelse(year == "dper", "2017", "2012"))
 
 change <- left_join(cities, dper) %>% 

### 2021-01-28 code/05_2wayfe.R

@@ -112,7 +112,7 @@ j <- j %>%
          V1 = ifelse(grepl("\\\\#tab", V1), gsub("\\\\#", "", V1), V1)) %>%
   filter(!grepl("Note:", V1))
 
-insert1 <- "\\resizebox{!}{.5\\textheight}{%"
+insert1 <- "\\resizebox{1\\textwidth}{.5\\textheight}{%"
 insert2 <- "}"
 
 j <- bind_rows(j, data.frame(V1 = c(insert1, insert2), n = c(5.1, nrow(j) + 1 - 0.01))) %>%

### 2021-01-28 markdown/fees_fines_to.Rmd
post "concentrated criminalization" change

@@
 Using data from the Census of Governments and the national voter file, we fill this hole in the literature.
-Our preliminary analyses indicate that municipalities with higher fees and fines collections have lower turnout, and that this relationship is likely causal.
+Our preliminary analyses indicate that municipalities with higher per-capita fees and fines collections have lower turnout, and that this relationship is likely causal.
 Moreover, we find that municipalities with higher fees and fines have a *lower* racial turnout gap.
@@
 
-Recent work from scholars in sociology and political science, however, indicates that many more voters are also *indirectly* disenfranchised due to over-incarceration and the politically chilling effects of the carceral state.
+Recent work from scholars in sociology and political science, however, indicates that many more voters are also *indirectly* disenfranchised due to concentrated criminalization and the politically chilling effects of the carceral state.
 Policing and incarceration shape political socialization: personal contact with police or incarceration is associated with a reduced likelihood of political participation, and that alienating effect extends even to people who have incarcerated family members or who simply reside in affected communities [@Lee2014; @Weaver2010; @Morris2020].

### 2021-01-28 markdown/fees_fines_to.tex
post "concentrated criminalization" change

@@
 Using data from the Census of Governments and the national voter file, we fill this hole in the literature.
-Our preliminary analyses indicate that municipalities with higher fees and fines collections have lower turnout, and that this relationship is likely causal.
+Our preliminary analyses indicate that municipalities with higher per-capita fees and fines collections have lower turnout, and that this relationship is likely causal.
 Moreover, we find that municipalities with higher fees and fines have a \emph{lower} racial turnout gap.
@@
 
-Recent work from scholars in sociology and political science, however, indicates that many more voters are also \emph{indirectly} disenfranchised due to over-incarceration and the politically chilling effects of the carceral state.
+Recent work from scholars in sociology and political science, however, indicates that many more voters are also \emph{indirectly} disenfranchised due to concentrated criminalization and the politically chilling effects of the carceral state.
 Policing and incarceration shape political socialization: personal contact with police or incarceration is associated with a reduced likelihood of political participation, and that alienating effect extends even to people who have incarcerated family members or who simply reside in affected communities (Lee, Porter, and Comfort \protect\hyperlink{ref-Lee2014}{2014}; Weaver and Lerman \protect\hyperlink{ref-Weaver2010}{2010}; Morris \protect\hyperlink{ref-Morris2020}{2020}).

### 2021-03-16 markdown/draft_paper.Rmd
draft paper

---
title: "Policing for Profit and the Mobilization of Black Voters"
subtitle: "Fines, Fees, and Turnout"
author:
- Jonathan Ben-Menachem^[PhD Student, Columbia University, Department of Sociology (jb4487@columbia.edu)]
- Kevin Morris^[PhD Student, CUNY Graduate Center, Department of Sociology (kmorris@gradcenter.cuny.edu)]
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  bookdown::pdf_document2:
    toc: no
    fig_caption: yes
    latex_engine: xelatex
    keep_tex: true
bibliography: "policing_turnout.bib"
link-citations: yes
fontsize: 12pt
header-includes:
    - \usepackage{rotating}
    - \usepackage{setspace}
abstract: |
  The American criminal legal system is an important site of political socialization: sociologists show how the alienating effect of criminalization manifests as systems avoidance, and political scientists have measured the effects of policing and incarceration on political participation. Despite this burgeoning literature, no research has directly investigated how ticketing for low-level offenses affects political participation. Using data from the Census of Governments and the national voter file, we conduct the first quasi-experimental analysis of the causal effect of fines and fees practices on American voting behavior at the city level. Additionally, we exploit individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019. We find that municipal fines and fees practices mobilize Black voters. Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 3.3 percentage point decrease in 2018 federal turnout, and a 1.8 percentage point decrease in the Black-white turnout gap. In Tampa, Florida, we estimate that Black voters who were ticketed in the 90-day period preceding a federal election were 3 percentage points more likely to turn out in federal elections. 
---
\pagenumbering{gobble}
\pagebreak
```{r setup, echo = F, message = F, warning = F}
knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf")
library(systemfit)
library(kevostools)
library(AER)
library(sandwich)
library(lmtest)
library(scales)
library(ggpubr)
library(tidyverse)
library(extrafont)
library(kableExtra)
library(data.table)
library(stargazer)
loadfonts()
```
\pagenumbering{arabic}
\doublespacing
Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities’ alienation from government. After Michael Brown was killed by the Ferguson Police Department in 2014, a US Department of Justice investigation into the city’s police and courts demonstrated that the municipality was engaged in a practice that advocates now refer to as “policing for profit.” The city’s reliance on fines and fees to fund government functions grew from 13 to 23 percent of the total budget between fiscal years 2012 and 2015. From 2012 to 2014, the Department of Justice found that 85 percent of vehicle stops, 90 percent of citations, and 93 percent of arrests targeted Black people. By contrast, just two-thirds of Ferguson’s residents are Black [@UnitedStatesDepartmentofJusticeCivilRightsDivision2015].

It wasn’t just a Ferguson problem, or even a Missouri problem. American cities’ reliance on fines and fees revenue increased significantly following the 2008 recession --- as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services [@Singla2020; @Harris2017].

Work exploring how criminalization directly and indirectly influences political participation has exploded in recent years. This work, however, has largely focused on the effects of highly consequential contact with the criminal legal system such as incarceration and felony convictions [@Burch2014; @Lee2014]. Although some work has leveraged survey data and qualitative approaches to interrogate lower-level police interactions --- such as ticketing --- our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior. We begin by joining fees and fines data from XX municipalities around the country in 2012 and 2017 with a novel data set estimating racial turnout for each municipality in the country. We find that higher fees and fines collections are associated with lower turnout for white Americans, but higher turnout for Black Americans --- and that this relationship is likely causal.

After exploring national data, we use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were ticketed between the 2012 and 2018 elections. By matching individuals who were ticketed to other, similar voters who were not ticketed and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout. Using self-reported race from the Florida registered voter file, we identify a modest, negative effect for non-Black voters, and a modest positive effect for Black voters. These individual-level analyses corroborate our municipal-level analyses from around the country.

We demonstrate that police ticketing practices --- the most widespread form of police contact in America --- influence the political behavior of Americans, with distinct effects for white and Black voters. This finding extends and supports Hannah Walker’s theory of criminal legal contact mobilizing nonwhite political participation [@Walker2020; @Walker2014]. On an individual level, we also find that Black voters who were ticketed turn out at higher rates in subsequent elections. This finding complicates Vesla Weaver and Amy Lerman’s theory of low-level criminal legal contact discouraging political participation [@Weaver2010]. Our findings are relevant for interdisciplinary scholars of crime, race, politics, political economy, social movements, and policing.

# Literature Review {-}

Sociologists have incorporated contemporary fines and fees practices into a broader empirical-historical theory of racialized punishment policy [@Harris2010; @Friedman2020]. Additionally, an emerging political science literature directly investigates the relationship between criminalization and political behavior.

In order to theorize how fines and fees affect political behavior, we consider (1) how criminalization directly shapes the electorate, (2) the influence of criminalization on political socialization, and (3) how contemporary ticketing practices are tied to a longer legacy of racist exploitation.

## Criminalization and the American electorate {-}

The American criminal legal system directly shapes the American electorate and excludes Black voters. Today, more than five million Americans are legally barred from voting due to a felony conviction, and one in every sixteen Black Americans of voting age is disenfranchised [@Uggen2020]. Following the implementation of the Fifteenth Amendment in 1870, over a dozen U.S. states passed laws denying voting rights to people who were convicted of felonies. In their analysis of how racial threat catalyzes felon disenfranchisement, Behrens, Uggen, and Manza found that increases in a state’s nonwhite prison population drastically increase the likelihood of legislation permanently disenfranchising people convicted of felonies [@Behrens2003].

Notably, fines and fees legally disenfranchise Americans: 48 states and the District of Columbia authorize some form of wealth-based penal disenfranchisement [@Colgan2019]. More specifically, many states require payment of fees as a condition of criminal legal supervision or the payment of all legal financial obligations as a condition of completing a sentence, and failure to comply with supervision or sentence completion conditions can be a barrier to voting rights restoration. These political barriers also disproportionately affect Black people. In Alabama, for example, Black people with felony convictions applying to have their voting rights restored were 26 percentage points more likely to have their application denied over outstanding fines and fees [@Meredith2017].

Another process by which criminalization shapes the electorate is “prison gerrymandering,” or the practice of counting incarcerated people as residing in the district where their prison is located for the purposes of creating electoral districts. This practice inflates the voting power of rural and white voters while diminishing the power of urban, Black, and Latino voters [@Remster2018].

## Criminalization and political socialization {-}

Beyond direct disenfranchisement, the spatial and racial concentration of criminalization significantly influences affected communities’ perceptions of government. Monica Bell calls this process “legal estrangement,” a conceptual framework meant to capture those perceptions and cultural attitudes (“legal cynicism”) as well as the historical-structural conditions that produced them [@Bell2017]. Research on legal cynicism has found that public perceptions of abusive police practices can reduce willingness to report crimes or cooperate with law enforcement [@Desmond2016; @Tyler2014]. Because police are the most visible agents of the state, perceptions of unfairness in policing can translate to a recognition of actual group-level structural exclusion from public institutions [@Bell2017]. New evidence related to ticketing and legal estrangement has recently emerged: in a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government compared to residents who were not ticketed [@CarpenterII2019].

In addition to influencing perceptions of government, recent scholarship indicates that criminalization influences political behavior. Several studies indicate that potential voters are discouraged from voting due to personal or proximal contact with the criminal legal system, and this chilling effect is most salient for what we consider “high-intensity” criminal legal involvement, such as being convicted of a crime or being incarcerated.

Using existing national survey data and new extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) [@Weaver2010]. Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective racial political consciousness, or a “linked fate” of all Black Americans. Their interview data lead them to conclude that “a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing” --- and interview respondents who had been incarcerated reported that withdrawal from public institutions constituted a form of self-preservation [@Lerman2014].

Sarah Brayne calls this phenomenon “system avoidance,” and she found similar results in her analysis of survey data: as the intensity of criminal legal contact escalates, people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions [@Brayne2014]. Brayne’s analysis demonstrates how lower-intensity criminal legal contact can be theorized as a mechanism for discouraging Americans’ participation in public institutions.

It may be the case that Black and non-Black Americans employ different self-preservation strategies, however. Ariel White’s analysis of how short jail sentences affect voting in Harris County, Texas found that Black defendant turnout in subsequent elections dropped by 13 percentage points --- but the effect on white turnout was not statistically significant [@White2019].

Proximal exposure to criminalization --- “having a loved one who is a custodial citizen without yourself having had contact” [@Walker2017] --- also influences Americans’ perceptions of government and political behavior, and the emerging literature has produced mixed findings. Using survey and ethnographic interview data, @Lee2014 found that adult children of incarcerated parents are less likely to vote, report lower trust in government, and are less likely to engage in other prosocial behaviors like community service [@Lee2014]. @Sugie2015 used survey data to show that partners of formerly incarcerated men are less likely to vote, but not less likely to participate in religious or civic institutions [@Sugie2015].

Although geographic or spatial analyses of how criminalization affects political socialization technically move beyond proximal contact as an extant conceptual framework, we argue that geographic proximity should work similarly to social network proximity --- if one neighborhood is heavily policed, people who live in that neighborhood are more likely to have social ties who have experienced policing. Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level [@Burch2014]. KEVIN WRITE A SENTENCE ABOUT YOUR PAPER HERE. [@Morris2020].

White also conducted a proximal contact analysis using Harris County administrative data regarding households wherein one member was charged with a misdemeanor offense and arrested, convicted, or jailed [@White2019]. She found that a household member who was charged but not convicted in the 30 day period preceding an election increased voter turnout by 3 percentage points, whereas “convicted but not jailed” decreased turnout by 6 percentage points and “convicted and jailed” decreased turnout by 12 percentage points. This provides further support for the theory that increasing intensity of criminalization could change the direction of the effect of criminalization on political behavior.

This chilling effect does not appear uniformly across all studies. In New York City, geographically concentrated stop-and-frisk activity was associated with *reduced* turnout in Congressional elections, but *increased* turnout in the 2008 presidential election as well as the local mayoral election in 2013 [@Laniyonu2019]. If proximal contact mobilizes, then, mobilized voters are likely targeting officials who they perceive as holding the power to change police practices. To the extent that descriptive representation mitigates exploitative fines and fees practices [-@Sances2017], this could constitute an effective political strategy.

Hannah Walker’s research specifically tests differences between the effects of proximal and personal criminal legal contact on political behavior, and her findings underscore how a “linked fate” political analysis could catalyze distinct political behavior among Black voters [@Walker2014]. Using data from a 2012 survey of Washington state residents, she found that as the degree of an individual’s proximity to a criminalized person increases, so does their likelihood of participating in political activities (such as voting, signing a petition, volunteering, donating to politicians, etc.). Importantly, Walker found that nonwhite people who had experienced *either* proximal or personal contact *at any level of intensity*, including being stopped and questioned by police, were politically mobilized --- and the same held true for whites, but with a much smaller effect size. Walker theorizes that this finding suggests that nonwhite people view criminalization “as a form of systemic political threat,” an analysis comparable to “linked fate.” Notably, Walker’s survey questions excluded “minor traffic stops,” the primary focus of this paper.

Over the past few years, scientific understanding of the political effects of more serious interactions with the criminal legal system has grown by leaps and bounds. The following table summarizes our understanding of the literature.

```{r lit-table, echo = F, warning = F}
t <- fread("./raw_data/lit_table.csv")
j <- knitr::kable(t, booktabs = T, caption = "\\label{tab:lit-table} Summary of Literature", linesep = "",
                  align = c("l", "l", "l"), "latex") %>%
  kable_styling(latex_options = c("HOLD_position"),
                full_width = F) %>% 
  column_spec(1, width = "10em") %>% 
  column_spec(2, width = "10em") %>% 
  column_spec(3, width = "10em")
write(j, "./temp/tab_lit.tex")
```
\begin{singlespace}
\input{"../temp/tab_lit.tex"}
\end{singlespace}

Researchers have used administrative data linked with registered voter files to explore the effects of stops, arrests, conviction, and incarceration on political behavior. We can say, with some reservations, that such contact likely reduces participation at the ballot box. To date, however, no work has leveraged administrative data to test the effect of police ticketing routine police stops on political behavior, and relatively little work has investigated the effects of police stops. Some qualitative research [@Weaver2010] indicates that these low-level stops are demobilizing; Laniyou, on the other hand, finds that neighborhoods with many police stops can turnout at higher rates, and survey data analyzed by Walker similarly shows that police stops can mobilize. By identifying all individuals subjected to a traffic stop in Hillsborough County, this project pushes us forward along the lines of other work using administrative data.

Most of the aforementioned studies were conducted using data collected before the rise of the Black Lives Matter movement in 2013, which could be construed as a significant development for the political socialization of Black Americans with respect to policing and incarceration. The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious. Though racist police violence was and is a focal point for many Black Lives Matter actions, local chapters frequently use policing as an entry point into a wider set of demands regarding the material security of Black Americans and their marginalization in American politics --- and these demands affect police practices. One recent study found that census places that saw Black Lives Matter protests experienced a 15 to 20 percent decrease in police killings over the following five year period [@Campbell2021]. It’s possible that any potentially mobilizing effects of criminal legal contact became stronger in the 2010s --- in other words, Black Lives Matter could have facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis. That said, -@Laniyonu2019 did demonstrate mobilization in Black neighborhoods before the beginning of the Black Lives Matter movement.

## Race and fines and fees practices {-}

Apart from the fact that no prior work has directly investigated the relationship between police ticketing practices and political behavior, we argue that fines and fees invoke a distinct historical legacy of racist exploitation that merits further study.

Cedric Robinson’s articulation of racial capitalism offers a useful theoretical framework for interpreting the trajectory of American anti-Black political economy [@Robinson2005]. Brittany Friedman theorizes fines and fees as a “progression of racial capitalism penology,” emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices [@Friedman2020, page 177]. Robinson argues that European industrial capitalism continued a longer political-economic trend of differentiating racial groups in order to dispossess them and exploit their labor. Indeed, early American agrarian and mercantile economies relied on the labor-power of enslaved Black people, and the slave patrols created to terrorize and discipline enslaved laborers are the earliest antecedents of contemporary American police departments [@DuBois1935; @Hadden2003].

Following the Civil War and the rise of global industrial capitalism, slave patrols were replaced by more formal police forces and vigilante lynch mobs [@EqualJusticeInitiative2017; @Hinton2021]. The implementation of the Black Codes, convict leasing, and sharecropping systems marked a transition to a new stage of racial capitalism, wherein criminalization provided an easily-exploited labor supply that offset costs that the state incurred by coercing their labor [@Lichtenstein1996; @Mancini1978]. Criminal legal debt has also been directly compared to sharecropping because both structures share “a long-term pattern of financial exploitation based on race… that limits the life-choices of the affected population” [@Blessett2016, page 113].

In the 20th century, residential segregation simultaneously fueled the racial wealth gap and ensured that criminalization was both spatially and racially concentrated [@Rothstein2017; @Hinton2021]. At the level of federal policy, racial threat and whites’ attribution of criminality to Blackness [@Muhammad2010] prompted a shift “from the War on Poverty to the War on Crime” wherein Black communities’ demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration [@Hinton2016; @Vargas2016]. Ruth Wilson Gilmore explains how mid to late 20th-century whites “demanded that the state become leaner and meaner, except when directed to do otherwise” --- in other words, Keynesian welfare guarantees were undermined by the racist myth of “welfare queens” and supplanted by expanded police power [@Gilmore2007, page 53].

The 2008 financial crisis solidified the connection between fiscal austerity and policing, prompting a decline in tax revenues that devastated state and local governments --- but law enforcement agencies were largely spared from cuts. At the local level, this means that police budgets today constitute about thirty percent of city budgets nationwide, and cities where residents have lower median incomes dedicate a larger proportion of spending to policing [@Friedman2020]. In municipalities with substantial Black populations, then, people who are most heavily affected by criminalization are expected to foot the bill for their own mistreatment.

Today, fines and fees primarily target Black Americans: traffic stops and searches disproportionately affect Black motorists nationwide [@Pierson2020], and a host of local analyses confirm this finding [@Dunn2009; @Goncalves2020; @Mughan2020]. In criminal court proceedings, Black defendants tend to face more severe monetary sanctions [@Edwards2020; @Harris2011].

In 2020, a Federal Reserve survey found that five percent of white respondents reported “unpaid legal expenses, fines, or court costs,” whereas twelve percent of Black respondents reported such debt [@BoardofGovernorsoftheFederalReserveSystem2020]. Across the country, city government reliance on fines and fees revenue is associated with larger Black populations [@UnitedStatesCommissiononCivilRights2017]. Although major urban centers collect high dollar amounts of fines and fees, some of the most egregious ticketing practices measured on a per-capita basis are concentrated in suburbs or smaller cities with municipal courts --- Ferguson being a prominent example [@UnitedStatesDepartmentofJusticeCivilRightsDivision2015; @Mughan2020]. The positive association between cities’ reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator, however [@Sances2017].

Racial capitalist political economy imposes fiscal constraints regardless of city officials’ intentions. In their study of fines and fees reliance in Chicago suburbs, Josh Pacewicz and John Robinson, III show how the racialization of municipal opportunity structures prevents majority-Black suburban governments from acquiring sufficient revenue from “good” sources such as sales taxes or property taxes, catalyzing a reliance on fines and fees to fund essential government services [@Pacewicz2020]. Importantly, Pacewicz and Robinson III note that these racialized municipal opportunity structures are tied to the political-historical processes of neoliberalism and fiscal austerity, an observation that aligns with recent scholarship detailing the origins of fees paid by incarcerated people [@Kirk2020]. The late 20th century “property tax revolt” most significantly benefited white homeowners [@Martin2015], and without property tax hikes as a revenue-raising option, smaller cities and towns have few choices.

Research regarding police stops and searches in response to local fiscal crisis shows how decreasing local revenues affect racist police practices. One study of all U.S. city governments found that local fiscal stress was related to increased “revenue-generating arrests” (e.g. arrests involving civil asset forfeiture) and that Black and Hispanic people were arrested at higher rates [@Makowsky2009]. A study of four million North Carolina traffic stops found that fiscal stress caused a decrease in the probability of white drivers being searched, but no decrease for Black drivers [Shoub2020]. This suggests that higher reliance on fines and fees results in government officials and police targeting individuals who hold less political power --- whether those individuals are out-of-state motorists or members of local marginalized communities [@Makowsky2009].

With this history in mind, we argue that Black Americans can situate exploitative ticketing practices in a longer historical legacy of collective disparate treatment and violence at the hands of the state, which may facilitate a stronger collective political analysis when police ticketing practices become more extreme.  We expect that Black voters’ political behavior in response to police ticketing will be distinct from the political behavior of white voters.

# Data and Design {-}

We explore the effect of fees and fines collections on voter turnout by looking at two different levels: the municipal and the individual. Such an approach gives us both breadth and depth: our municipal-level analysis allows us to broadly understand the relationship between fees and fines across the entire United States, while the individual-level analyses allow us to interrogate the specific causal mechanisms at play.

## City-level relationship between voter turnout and fines and fees {-}

We begin with our nationwide analysis in which we observe the turnout and fees and fines collections of cities from around the country. Our data come from two primary sources: the US Census Bureau’s Census of Governments Data (COG), and registered voter files from L2 Political.

**Census of Governments**: Every five years, the US Census Bureau collects data from governmental bodies around the country. We use two snapshots of the COG: one that covers the years 2008 - 2012, and another that covers 2013 - 2017. The COG includes a host of information about state and municipal finances. The COG asks municipalities to report how much revenue they collect from “penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation... and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).” This data has been used as a proxy for the amount of tickets issued at the local level in scholarly research [see, for instance, @Goldstein2020; @Sances2017].

The COG data are useful to isolate ticketing practices because other fines and fees (e.g. fines imposed at sentencing in state court, probation fees, conviction fees, public defender fees) are typically collected by county or state governments. The COG data only include local revenues, which means the share of fines revenue corresponds more directly to local police practices.

**Registered Voter Files**: The COG data do not include estimates of turnout at the local level. To estimate local turnout, we leverage registered voter files provided by data vendor L2. Voters in Washington, DC, and every state in the country (with the exception of North Dakota) requires voters to register to vote prior to participating. These files are considered public record, and in most states contain information about each voter’s age, residential address, political affiliation, and participation history. L2 collects these voter files from around the country and merges them with proprietary data that estimates other voter- and household-level characteristics such as race and education. L2 also geocodes voters’ residential addresses. L2 does not collect all states’ voter file on the same date; the date of the “raw” voter file from each state from which the L2 data are modelled can be found in Appendix A.

We merge these geocoded voter files with “place” and “county subdivision” shapefiles published by the US Census Bureau. By aggregating these individual-level records to the municipal level, we are able to estimate the number of registered voters and the number of ballots cast in every city in the country. By using the racial estimates provided by L2, we can estimate the number of ballots cast by voters of each race in each city. Although each voters’ race is modeled based on L2’s algorithms --- not self-reported --- it is possibly incorrect for some voters. We assume this does not present a problem when records are aggregated to the municipal level.

Although turnout could be calculated as a share of *registered voters* who participated, such an approach could be biased. If fees and fines collection impact the number of individuals who register to vote, but not the share of registered voters who participate, our estimates will be compromised. We therefore calculate turnout by dividing the number of ballots cast according to L2 by the 5-year estimate of each municipality’s citizen voting-age population (CVAP) from the US Census Bureau. These estimates are available for individual racial groups.

**Estimation Strategy**: We begin by merging each municipality’s fees and fines per capita from the 2012 COG to its turnout from the 2014 midterm election, and the 2017 COG to its 2018 turnout. Because this measure is highly right-skewed, we use the natural log of fees and fines per capita plus one. We also control for other municipal and state characteristics. These include racial composition, population density, median income, collegiate education, median age, and share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality’s revenue that comes from the state or federal government in the 2012 and 2017 COGs. We retain only municipalities whose data is reported to the COG in both 2012 and 2017. We then run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.

Unfortunately, the 5-year cycle of the COG does not neatly line up with the general 4-year cycle typical of American elections. The timing of the COG and midterm elections mean that our analytical strategy is conservative. If municipalities shift their fees and fines collections dramatically over the 2013 - 2017 period, this shift may influence their 2014 turnout. However, we assume that turnout in 2014 will still be influenced by the policing practices of the 2008 -- 2012 period, while 2018 turnout will be largely influenced by the practices of the 2013 -- 2017 period.

Our national two-way fixed effect model allows us to test our first two hypotheses:

*Hypothesis 1: Increased reliance on fines and fees revenue at the city level affects voter turnout at the city level.*

*Hypothesis 2: The effect of the city-level relationship between fines and voter turnout is distinct for Black voters --- i.e. more pronounced than or in the opposite direction of the effect of fines on turnout for white voters.*

## Individual-Level Effects of Ticketing {-}

Our national test of the relationship between municipal fees and fines collection and turnout offers novel insight into the political socialization of low-level police contact. It cannot, however, directly observe the causal mechanism we argue is at play: namely, that personal or proximal contact with the criminal legal system influences turnout. Our national analysis suffers from what is called the ecological fallacy: it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.

To test whether a ticket directly influences the turnout voters we turn to individual-level data from Hillsborough County, Florida (home to Tampa). Hillsborough County is interesting for theoretical reasons: Tampa is in the top decile of municipalities in terms of fees and fines increase between the 2012 and 2017 COGs, and its population puts it in the top 1 percent of cities nationwide. It also has a relatively large Black population, allowing us to test for racial differences in the turnout effect of ticketing.

Further, the Tampa Police Department was scrutinized by the Tampa Bay Times in 2015 for its relentless ticketing of Black bicyclists [@Zayas2015]. This investigation catalyzed a U.S. Department of Justice investigation and report, requested by Tampa’s mayor and police chief. In other words, there’s strong evidence suggesting both racist targeting of tickets and potential publicity to catalyze distinct Black voter responses to the abusive behavior during the same time frame as our national analysis. Ticketing has also been expressly politicized in Tampa: Jane Castor, who was elected mayor in 2019, was Tampa’s police chief until 2015 and publicly defended her department’s disproportionate ticketing of Black bicyclists before retracting her defense during her mayoral campaign [CITE]. Her opponent, banker and philanthropist David Straz, campaigned against red-light cameras and focused his outreach in Tampa’s Black communities.

Perhaps more prosaically, Hillsborough County also makes a unique set of data publicly available. The county clerk makes information available about every traffic stop in the county going back to 2003. This data includes the name and date of birth of the individual stopped; the date of the offense; and the amount the individual paid for a ticket. We retain only the records where the individual paid money.

To test the effect of ticketing on individual-level turnout, we match the first and last names and dates of birth against the Hillsborough County registered voter file from L2. To improve the quality of the match between the two datasets, we remove all punctuation from all names and convert all names to lower-case. This means that a “Jonathan O’Shea” in one file would match a “jonathan oshea” in the other. @Meredith2014 develops a test for assessing the prevalence of false-positives in administrative record matching. We present the results of that test in Appendix B, but we likely have a false-positive match of around 0.03 percent.

By matching these records, we identify all voters who were ticketed between the 2012 and 2018 general elections. Voters are considered “treated” for every general election following their first ticket. This means that a voter who was ticketed in early 2014 was considered treated”= for the 2014, 2016, and 2018 elections. A voter treated in 2017, on the other hand, is only considered treated in the 2018 election.

These voters are then matched to one control voter using what methodologists call a “genetic” process [@Sekhon2011]. The pool of potential control voters are the individuals who are never stopped during the 2012 -- 2018 period, regardless of whether they paid a fine. We match voters on individual-level characteristics (race / ethnicity; gender; party affiliation; age; registration date; number of traffic stops between 2003 and the 2012 election) and block group-level characteristics from the 2012 5-year ACS estimates (median income; share of the population with some college; unemployment rate).

We also match treated and control voters on their 2010 and 2012 general election turnout, as well as any other even-yeared general election turnout in the pre-treatment period. In other words, a voter ticketed in 2013 is matched to controls based on turnout in 2010 and 2012, while a voter ticketed in 2017 is matched to their control using 2010, 2012, 2014, and 2016 turnout. Because voters treated in later periods are matched to their controls along more covariates, we run three separate matches: one for voters stopped between the 2012 and 2014 elections; for voters stopped between the 2014 and 2016 elections; and for those stopped between the 2016 and 2018 elections.

*Hypothesis 3: Among individuals who were ticketed (“treated”) in Tampa, their likelihood of turning out in a subsequent election roughly matches the racioethnic distribution apparent in the national city-level data. If fines uniquely mobilize Black voters nationally, they should also uniquely mobilize Black voters in Tampa.*

Because Tampa holds off-year local elections, we are able to test whether mobilized voters target officials who are able to change local police practices. @Laniyonu2019 gives us reason to believe that the effect should be stronger for local elections.

*Hypothesis 4: Any potential mobilizing turnout effect in Tampa is stronger for local (mayoral) elections, since those elections directly affect police practices.*

That said, Laniyonu found that heavily policed, majority-Black New York City neighborhoods tended to vote for William Thompson, a Black candidate who opposed police reform --- which could suggest that Black voters prioritized descriptive representation over outward-facing policy messaging. In Tampa, however, both leading candidates were white, and Castor was the police chief during the city’s racist ticketing scandal. Thus, the racioethnic identity of the candidates in 2019 should not affect ticketed Black voters’ responses to candidates’ policy messaging in the same way.

One novel feature of our analysis is that we are able to assess the political effects of both proximal and personal criminal legal contact during the same time frame. The COG data likely capture the voting behavior of people who were not personally ticketed, but know one or several people who were; and the Tampa data capture the voting behavior of people who were themselves ticketed.

Additionally, our analysis eliminates measurement problems that potentially affected past research and accounts for the temporal features of the relationship between criminal legal contact and voting. Several prior studies regarding criminalization and political behavior [@Walker2014; @Weaver2010] involve surveys where the measure of police contact is self-reported intensity of contact --- “have you ever been stopped by police? Arrested? Incarcerated?” Respondents were then asked to indicate how likely they might be to vote. Our analysis allows us to assess the actual voting behavior of people who we verify were ticketed and gauge the strength of the treatment effect over time by comparing each individual’s participation in subsequent elections. It is also advantageous that we are able to capture actual voting behavior within a few months or weeks of treatment application --- only Walker and White conduct individual-level analyses consistent with voter file data, and Laniyonu conducts a neighborhood-level analysis using voter file data. This feature of our data also helps us avoid measurement issues with survey instruments used in prior studies --- for example, Lerman and Weaver are careful to note that people who have been arrested or incarcerated sometimes misreport their political behavior in survey research. Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to police ticketing.

# Results {-}

Before testing the causal effect of fees and fines collections, we begin with a cross-sectional analysis of the relationship between fees and fines and turnout. Here, we regress municipality-level turnout in 2018 against fees and fines collections as reported in the 2017 COG, as well as a number of other covariates. In Figure \ref{fig:mef-2018} we present the marginal effect of fees and fines on municipal-level turnout. The plot shows the results from two separate models: one in which the dependent variable is Black turnout (as a share of CVAP), and a second in which the dependent variable is non-Black turnout. The figure also marks the interdecile range. The full regression table can be found in Appendix XX.

```{r cross-18, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:mef-2018}Marginal Effect of per-capita Fees and Fines on Turnout, 2018", fig.pos = "H", fig.align = "center"}
load("temp/mef_to.rdata")
print(p2)
```

As Figure \ref{fig:mef-2018} makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 1 percentage point over the interdecile range, after controlling for the other covariates. The opposite is true for Black voters: over the same range, Black turnout *increases* by roughly 2.5 percentage points. Both of these relationships are statistically significant at the 95 confidence level. To be sure, this does not prove that higher fees and fines increase Black turnout; these cross-sectional regressions cannot establish causality. Nevertheless, Figure \ref{fig:mef-2018} is consistent with this story.

We turn now to our two-way fixed effects model. As discussed above, we retain each municipality that reported their fees and fines data to the COG in both 2012 and 2017 (and met the other criteria discussed in the *Data and Design* section). The dependent variable in each model is calculated by dividing the number of ballots cast in 2014 and 2018 by the 5-year CVAP estimate from the same year. We run the two-way fixed effects on overall turnout, Black turnout, and non-Black turnout. The results of these models can be found in Table \ref{tab:twfe}.

\begin{singlespace}
\input{"../temp/2wfe_reg_clean.tex"}
\end{singlespace}

The results of the two-way fixed effects model are slightly different than what we saw in the 2018 cross-sectional approach; namely, while Table \ref{tab:twfe} indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not impact Black turnout. The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.06 percentage points. Moreover, because of the relative stability in fees and fines collections at the municipal level over this time period (the mean increase in per-capita fees and fines collections was just 6 percent, and the median municipality decreased by about 1.5 percent), it is not clear how informative this approach is.

In Table \ref{tab:coarser}, we re-estimate the model from Table \ref{tab:twfe} but coarsen the data. Here, we test whether turnout changed for municipalities who increased their fees and fines collections differently than municipalities where collections stayed the same or decreased. Municipalities that increased their per-capita fees and fines are considered “treated.”

The coefficient on *Treated × 2018* indicates that non-Black turnout dropped by about 0.5 percentage points in municipalities where fees and fines collections increased relative to other municipalities. While this coefficient is also negative for Black voters, it is not statistically significantly different from 0. In other words, both Tables \ref{tab:twfe} and \ref{tab:coarser} indicate that increased fees and fines collections decrease non-Black turnout but have no impact on Black turnout.

## Individual-Level Results {-}

Thus far, we have shown that the turnout effects of fees and fines collection impact municipal-level turnout, and that the effects are different for Black and non-Black Americans. We argue that this relationship is causal: increased fees and fines collections means that more residents have direct interactions with the criminal legal system. Based on prior literature, we assume there are indirect effects as well, as more residents know a family or community member who has been ticketed. While the national analysis gives us great breadth and an increased understanding of how this plays out across the country, municipal-level data leaves us unable to directly observe the causal mechanisms at play.

To directly observe the effect of being ticketed on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida. As discussed above, we match [@Sekhon2011] individuals who were stopped and assessed a fine between the 2012 and 2018 elections to individuals who were not stopped during this time period.^[Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights. The full sample is used in the actual matching process.]  Matching is done with replacement and ties are not broken, meaning some treated voters may have more than XX controls; the regression weights reflect this possibility. In Table \ref{tab:balance} we present the results of the matching algorithm. We manage to reduce between treated and control voters substantially along all observed characteristics with the exception of 2012 turnout. However, this is not likely a problem: the turnout of all potential and actual controls were both within 0.1 percentage points of the treatment group’s turnout that year.

\begin{singlespace}
\input{"../temp/coarser_reg_clean.tex"}
\end{singlespace}

## Individual-Level Results {-}

Thus far, we have shown that the turnout effects of fees and fines collection impact municipal-level turnout, and that the effects are different for Black and non-Black Americans. We argue that this relationship is causal: increased fees and fines collections means that more residents have direct interactions with the criminal legal system. Based on prior literature, we assume there are indirect effects as well, as more residents know a family or community member who has been ticketed. While the national analysis gives us great breadth and an increased understanding of how this plays out across the country, municipal-level data leaves us unable to directly observe the causal mechanisms at play.

To directly observe the effect of being ticketed on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida. As discussed above, we match [@Sekhon2011] individuals who were stopped and assessed a fine between the 2012 and 2018 elections to individuals who were not stopped during this time period.^[Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights. The full sample is used in the actual matching process.]  Matching is done with replacement and ties are not broken, meaning some treated voters may have more than XX controls; the regression weights reflect this possibility. In Table \ref{tab:balance} we present the results of the matching algorithm. We manage to reduce between treated and control voters substantially along all observed characteristics with the exception of 2012 turnout. However, this is not likely a problem: the turnout of all potential and actual controls were both within 0.1 percentage points of the treatment group’s turnout that year.

INSERT BALANCE TABLE

It is worth noting that voters who were stopped between 2012 and 2018 were far more likely to be Black, males, and registered Democrats than the general electorate, and live in Census block groups with moderately lower incomes. Unsurprisingly, they were also stopped at higher rates in the pre-treatment period than those never stopped between 2012 and 2018.

While Table \ref{tab:balance} indicates that our treatment voters and their matches are substantially similar to their matches, the validity of the difference-in-differences design requires that the treatment and control voters turned out at comparable rates in the baseline period. In Figure \ref{fig:did1}, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped. The first election following a treated voter’s stop is denoted as *t = 0*; subsequent elections take higher positive numbers, while the years in which *t* is less than zero are the periods prior to the stop. This means that for someone stopped in 2013, *t* is 0 in 2014, while *t* is equal to 0 in 2018 for an individual stopped between the 2016 and 2018 elections.

```{r did1, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/stopped_any_time.rds")
print(p2)
```

Figure \ref{fig:did1} makes a number of things immediately apparent. First, we can see that for both Black and non-Black voters the parallel trends assumption is satisfied. Because we matched treated and control voters based on turnout prior to the ticket, this is unsurprising. The visual results of the post-treatment trend corroborate what we found nationwide using the municipal-level data; namely, ticketing has a different effect for Black voters than for others..

Figure \ref{fig:did2} makes this effect even clearer. Here, we limit the analysis to voters who were stopped within the 90 days prior to an election (and their controls). We expected that the ticket would be more salient for individuals stopped shortly before the election. This appears to be the case --- *especially for Black voters.*

```{r did2, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:did-2}Effect of Being Ticketed Within 90 Days of Election on Turnout", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/within90days.rds")
print(p2)
```

Table \ref{tab:dind-table} formalizes Figures ref{fig:did1} and ref{fig:did2} into an ordinary least squares regression. Models 1 and 2 present the causal estimates of being stopped at any point in the two years prior to an election; Models 3 and 4 re-estimate the effect of being stopped within 90 days of an election. Models 1 and 3 show our overall causal effect, while Models 2 and 4 allow for the possibility that a ticket differentially mobilizes Black voters. The coefficients of note are *Treated X Post Treatment* and *Treated X Post Treatment X Black*. In models 1 and 3, *Treated X Post Treatment* measures the overall treatment effect, and in models 2 and 4 it measures the treatment effect for non-Black voters. *Treated X Post Treatment X Black* measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.

\begin{singlespace}
\input{"../temp/dind_reg.tex"}
\end{singlespace}

\newpage
# References {-}

### 2021-03-16 markdown/draft_paper.tex
draft paper

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
  \usepackage{amssymb}
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Policing for Profit and the Mobilization of Black Voters},
  pdfauthor={Jonathan Ben-Menachem; Kevin Morris},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Policing for Profit and the Mobilization of Black Voters}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Fines, Fees, and Turnout}
\author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
\date{March 16, 2021}

\begin{document}
\maketitle
\begin{abstract}
The American criminal legal system is an important site of political socialization: sociologists show how the alienating effect of criminalization manifests as systems avoidance, and political scientists have measured the effects of policing and incarceration on political participation. Despite this burgeoning literature, no research has directly investigated how ticketing for low-level offenses affects political participation. Using data from the Census of Governments and the national voter file, we conduct the first quasi-experimental analysis of the causal effect of fines and fees practices on American voting behavior at the city level. Additionally, we exploit individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019. We find that municipal fines and fees practices mobilize Black voters. Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 3.3 percentage point decrease in 2018 federal turnout, and a 1.8 percentage point decrease in the Black-white turnout gap. In Tampa, Florida, we estimate that Black voters who were ticketed in the 90-day period preceding a federal election were 3 percentage points more likely to turn out in federal elections.
\end{abstract}

\pagenumbering{gobble}
\pagebreak

\pagenumbering{arabic}
\doublespacing

Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities' alienation from government. After Michael Brown was killed by the Ferguson Police Department in 2014, a US Department of Justice investigation into the city's police and courts demonstrated that the municipality was engaged in a practice that advocates now refer to as ``policing for profit.'' The city's reliance on fines and fees to fund government functions grew from 13 to 23 percent of the total budget between fiscal years 2012 and 2015. From 2012 to 2014, the Department of Justice found that 85 percent of vehicle stops, 90 percent of citations, and 93 percent of arrests targeted Black people. By contrast, just two-thirds of Ferguson's residents are Black (\protect\hyperlink{ref-UnitedStatesDepartmentofJusticeCivilRightsDivision2015}{United States Department of Justice Civil Rights Division 2015}).

It wasn't just a Ferguson problem, or even a Missouri problem. American cities' reliance on fines and fees revenue increased significantly following the 2008 recession --- as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (\protect\hyperlink{ref-Singla2020}{Singla, Kirschner, and Stone 2020}; \protect\hyperlink{ref-Harris2017}{Harris et al. 2017}).

Work exploring how criminalization directly and indirectly influences political participation has exploded in recent years. This work, however, has largely focused on the effects of highly consequential contact with the criminal legal system such as incarceration and felony convictions (\protect\hyperlink{ref-Burch2014}{Burch 2014}; \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}). Although some work has leveraged survey data and qualitative approaches to interrogate lower-level police interactions --- such as ticketing --- our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior. We begin by joining fees and fines data from XX municipalities around the country in 2012 and 2017 with a novel data set estimating racial turnout for each municipality in the country. We find that higher fees and fines collections are associated with lower turnout for white Americans, but higher turnout for Black Americans --- and that this relationship is likely causal.

After exploring national data, we use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were ticketed between the 2012 and 2018 elections. By matching individuals who were ticketed to other, similar voters who were not ticketed and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout. Using self-reported race from the Florida registered voter file, we identify a modest, negative effect for non-Black voters, and a modest positive effect for Black voters. These individual-level analyses corroborate our municipal-level analyses from around the country.

We demonstrate that police ticketing practices --- the most widespread form of police contact in America --- influence the political behavior of Americans, with distinct effects for white and Black voters. This finding extends and supports Hannah Walker's theory of criminal legal contact mobilizing nonwhite political participation (\protect\hyperlink{ref-Walker2020}{Walker 2020}, \protect\hyperlink{ref-Walker2014}{2014}). On an individual level, we also find that Black voters who were ticketed turn out at higher rates in subsequent elections. This finding complicates Vesla Weaver and Amy Lerman's theory of low-level criminal legal contact discouraging political participation (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}). Our findings are relevant for interdisciplinary scholars of crime, race, politics, political economy, social movements, and policing.

\hypertarget{literature-review}{%
\section*{Literature Review}\label{literature-review}}
\addcontentsline{toc}{section}{Literature Review}

Sociologists have incorporated contemporary fines and fees practices into a broader empirical-historical theory of racialized punishment policy (\protect\hyperlink{ref-Harris2010}{Harris, Evans, and Beckett 2010}; \protect\hyperlink{ref-Friedman2020}{Friedman 2020}). Additionally, an emerging political science literature directly investigates the relationship between criminalization and political behavior.

In order to theorize how fines and fees affect political behavior, we consider (1) how criminalization directly shapes the electorate, (2) the influence of criminalization on political socialization, and (3) how contemporary ticketing practices are tied to a longer legacy of racist exploitation.

\hypertarget{criminalization-and-the-american-electorate}{%
\subsection*{Criminalization and the American electorate}\label{criminalization-and-the-american-electorate}}
\addcontentsline{toc}{subsection}{Criminalization and the American electorate}

The American criminal legal system directly shapes the American electorate and excludes Black voters. Today, more than five million Americans are legally barred from voting due to a felony conviction, and one in every sixteen Black Americans of voting age is disenfranchised (\protect\hyperlink{ref-Uggen2020}{Uggen et al. 2020}). Following the implementation of the Fifteenth Amendment in 1870, over a dozen U.S. states passed laws denying voting rights to people who were convicted of felonies. In their analysis of how racial threat catalyzes felon disenfranchisement, Behrens, Uggen, and Manza found that increases in a state's nonwhite prison population drastically increase the likelihood of legislation permanently disenfranchising people convicted of felonies (\protect\hyperlink{ref-Behrens2003}{Behrens, Uggen, and Manza 2003}).

Notably, fines and fees legally disenfranchise Americans: 48 states and the District of Columbia authorize some form of wealth-based penal disenfranchisement (\protect\hyperlink{ref-Colgan2019}{Colgan 2019}). More specifically, many states require payment of fees as a condition of criminal legal supervision or the payment of all legal financial obligations as a condition of completing a sentence, and failure to comply with supervision or sentence completion conditions can be a barrier to voting rights restoration. These political barriers also disproportionately affect Black people. In Alabama, for example, Black people with felony convictions applying to have their voting rights restored were 26 percentage points more likely to have their application denied over outstanding fines and fees (\protect\hyperlink{ref-Meredith2017}{Meredith and Morse 2017}).

Another process by which criminalization shapes the electorate is ``prison gerrymandering,'' or the practice of counting incarcerated people as residing in the district where their prison is located for the purposes of creating electoral districts. This practice inflates the voting power of rural and white voters while diminishing the power of urban, Black, and Latino voters (\protect\hyperlink{ref-Remster2018}{Remster and Kramer 2018/ed}).

\hypertarget{criminalization-and-political-socialization}{%
\subsection*{Criminalization and political socialization}\label{criminalization-and-political-socialization}}
\addcontentsline{toc}{subsection}{Criminalization and political socialization}

Beyond direct disenfranchisement, the spatial and racial concentration of criminalization significantly influences affected communities' perceptions of government. Monica Bell calls this process ``legal estrangement,'' a conceptual framework meant to capture those perceptions and cultural attitudes (``legal cynicism'') as well as the historical-structural conditions that produced them (\protect\hyperlink{ref-Bell2017}{Bell 2017}). Research on legal cynicism has found that public perceptions of abusive police practices can reduce willingness to report crimes or cooperate with law enforcement (\protect\hyperlink{ref-Desmond2016}{Desmond, Papachristos, and Kirk 2016}; \protect\hyperlink{ref-Tyler2014}{Tyler, Fagan, and Geller 2014}). Because police are the most visible agents of the state, perceptions of unfairness in policing can translate to a recognition of actual group-level structural exclusion from public institutions (\protect\hyperlink{ref-Bell2017}{Bell 2017}). New evidence related to ticketing and legal estrangement has recently emerged: in a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government compared to residents who were not ticketed (\protect\hyperlink{ref-CarpenterII2019}{Carpenter II, Sweetland, and McDonald 2019}).

In addition to influencing perceptions of government, recent scholarship indicates that criminalization influences political behavior. Several studies indicate that potential voters are discouraged from voting due to personal or proximal contact with the criminal legal system, and this chilling effect is most salient for what we consider ``high-intensity'' criminal legal involvement, such as being convicted of a crime or being incarcerated.

Using existing national survey data and new extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}). Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective racial political consciousness, or a ``linked fate'' of all Black Americans. Their interview data lead them to conclude that ``a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing'' --- and interview respondents who had been incarcerated reported that withdrawal from public institutions constituted a form of self-preservation (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}).

Sarah Brayne calls this phenomenon ``system avoidance,'' and she found similar results in her analysis of survey data: as the intensity of criminal legal contact escalates, people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions (\protect\hyperlink{ref-Brayne2014}{Brayne 2014}). Brayne's analysis demonstrates how lower-intensity criminal legal contact can be theorized as a mechanism for discouraging Americans' participation in public institutions.

It may be the case that Black and non-Black Americans employ different self-preservation strategies, however. Ariel White's analysis of how short jail sentences affect voting in Harris County, Texas found that Black defendant turnout in subsequent elections dropped by 13 percentage points --- but the effect on white turnout was not statistically significant (\protect\hyperlink{ref-White2019}{White 2019}).

Proximal exposure to criminalization --- ``having a loved one who is a custodial citizen without yourself having had contact'' (\protect\hyperlink{ref-Walker2017}{Walker and García-Castañon 2017}) --- also influences Americans' perceptions of government and political behavior, and the emerging literature has produced mixed findings. Using survey and ethnographic interview data, \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort} (\protect\hyperlink{ref-Lee2014}{2014}) found that adult children of incarcerated parents are less likely to vote, report lower trust in government, and are less likely to engage in other prosocial behaviors like community service (\protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}). \protect\hyperlink{ref-Sugie2015}{Sugie} (\protect\hyperlink{ref-Sugie2015}{2015}) used survey data to show that partners of formerly incarcerated men are less likely to vote, but not less likely to participate in religious or civic institutions (\protect\hyperlink{ref-Sugie2015}{Sugie 2015}).

Although geographic or spatial analyses of how criminalization affects political socialization technically move beyond proximal contact as an extant conceptual framework, we argue that geographic proximity should work similarly to social network proximity --- if one neighborhood is heavily policed, people who live in that neighborhood are more likely to have social ties who have experienced policing. Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level (\protect\hyperlink{ref-Burch2014}{Burch 2014}). KEVIN WRITE A SENTENCE ABOUT YOUR PAPER HERE. (\protect\hyperlink{ref-Morris2020}{Morris 2020}).

White also conducted a proximal contact analysis using Harris County administrative data regarding households wherein one member was charged with a misdemeanor offense and arrested, convicted, or jailed (\protect\hyperlink{ref-White2019}{White 2019}). She found that a household member who was charged but not convicted in the 30 day period preceding an election increased voter turnout by 3 percentage points, whereas ``convicted but not jailed'' decreased turnout by 6 percentage points and ``convicted and jailed'' decreased turnout by 12 percentage points. This provides further support for the theory that increasing intensity of criminalization could change the direction of the effect of criminalization on political behavior.

This chilling effect does not appear uniformly across all studies. In New York City, geographically concentrated stop-and-frisk activity was associated with \emph{reduced} turnout in Congressional elections, but \emph{increased} turnout in the 2008 presidential election as well as the local mayoral election in 2013 (\protect\hyperlink{ref-Laniyonu2019}{Laniyonu 2019}). If proximal contact mobilizes, then, mobilized voters are likely targeting officials who they perceive as holding the power to change police practices. To the extent that descriptive representation mitigates exploitative fines and fees practices (\protect\hyperlink{ref-Sances2017}{2017}), this could constitute an effective political strategy.

Hannah Walker's research specifically tests differences between the effects of proximal and personal criminal legal contact on political behavior, and her findings underscore how a ``linked fate'' political analysis could catalyze distinct political behavior among Black voters (\protect\hyperlink{ref-Walker2014}{Walker 2014}). Using data from a 2012 survey of Washington state residents, she found that as the degree of an individual's proximity to a criminalized person increases, so does their likelihood of participating in political activities (such as voting, signing a petition, volunteering, donating to politicians, etc.). Importantly, Walker found that nonwhite people who had experienced \emph{either} proximal or personal contact \emph{at any level of intensity}, including being stopped and questioned by police, were politically mobilized --- and the same held true for whites, but with a much smaller effect size. Walker theorizes that this finding suggests that nonwhite people view criminalization ``as a form of systemic political threat,'' an analysis comparable to ``linked fate.'' Notably, Walker's survey questions excluded ``minor traffic stops,'' the primary focus of this paper.

Over the past few years, scientific understanding of the political effects of more serious interactions with the criminal legal system has grown by leaps and bounds. The following table summarizes our understanding of the literature.

\begin{singlespace}
\input{"../temp/tab_lit.tex"}
\end{singlespace}

Researchers have used administrative data linked with registered voter files to explore the effects of stops, arrests, conviction, and incarceration on political behavior. We can say, with some reservations, that such contact likely reduces participation at the ballot box. To date, however, no work has leveraged administrative data to test the effect of police ticketing routine police stops on political behavior, and relatively little work has investigated the effects of police stops. Some qualitative research (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}) indicates that these low-level stops are demobilizing; Laniyou, on the other hand, finds that neighborhoods with many police stops can turnout at higher rates, and survey data analyzed by Walker similarly shows that police stops can mobilize. By identifying all individuals subjected to a traffic stop in Hillsborough County, this project pushes us forward along the lines of other work using administrative data.

Most of the aforementioned studies were conducted using data collected before the rise of the Black Lives Matter movement in 2013, which could be construed as a significant development for the political socialization of Black Americans with respect to policing and incarceration. The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious. Though racist police violence was and is a focal point for many Black Lives Matter actions, local chapters frequently use policing as an entry point into a wider set of demands regarding the material security of Black Americans and their marginalization in American politics --- and these demands affect police practices. One recent study found that census places that saw Black Lives Matter protests experienced a 15 to 20 percent decrease in police killings over the following five year period (\protect\hyperlink{ref-Campbell2021}{Campbell 2021}). It's possible that any potentially mobilizing effects of criminal legal contact became stronger in the 2010s --- in other words, Black Lives Matter could have facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis. That said, (\protect\hyperlink{ref-Laniyonu2019}{2019}) did demonstrate mobilization in Black neighborhoods before the beginning of the Black Lives Matter movement.

\hypertarget{race-and-fines-and-fees-practices}{%
\subsection*{Race and fines and fees practices}\label{race-and-fines-and-fees-practices}}
\addcontentsline{toc}{subsection}{Race and fines and fees practices}

Apart from the fact that no prior work has directly investigated the relationship between police ticketing practices and political behavior, we argue that fines and fees invoke a distinct historical legacy of racist exploitation that merits further study.

Cedric Robinson's articulation of racial capitalism offers a useful theoretical framework for interpreting the trajectory of American anti-Black political economy (\protect\hyperlink{ref-Robinson2005}{\textbf{Robinson2005?}}). Brittany Friedman theorizes fines and fees as a ``progression of racial capitalism penology,'' emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices (\protect\hyperlink{ref-Friedman2020}{Friedman 2020, 177}). Robinson argues that European industrial capitalism continued a longer political-economic trend of differentiating racial groups in order to dispossess them and exploit their labor. Indeed, early American agrarian and mercantile economies relied on the labor-power of enslaved Black people, and the slave patrols created to terrorize and discipline enslaved laborers are the earliest antecedents of contemporary American police departments (\protect\hyperlink{ref-DuBois1935}{Du Bois 1935}; \protect\hyperlink{ref-Hadden2003}{Hadden 2003}).

Following the Civil War and the rise of global industrial capitalism, slave patrols were replaced by more formal police forces and vigilante lynch mobs (\protect\hyperlink{ref-EqualJusticeInitiative2017}{Initiative 2017}; \protect\hyperlink{ref-Hinton2021}{Hinton and Cook 2021}). The implementation of the Black Codes, convict leasing, and sharecropping systems marked a transition to a new stage of racial capitalism, wherein criminalization provided an easily-exploited labor supply that offset costs that the state incurred by coercing their labor (\protect\hyperlink{ref-Lichtenstein1996}{Lichtenstein 1996}; \protect\hyperlink{ref-Mancini1978}{Mancini 1978}). Criminal legal debt has also been directly compared to sharecropping because both structures share ``a long-term pattern of financial exploitation based on race\ldots{} that limits the life-choices of the affected population'' (\protect\hyperlink{ref-Blessett2016}{Blessett and Box 2016, 113}).

In the 20th century, residential segregation simultaneously fueled the racial wealth gap and ensured that criminalization was both spatially and racially concentrated (\protect\hyperlink{ref-Rothstein2017}{Rothstein 2017}; \protect\hyperlink{ref-Hinton2021}{Hinton and Cook 2021}). At the level of federal policy, racial threat and whites' attribution of criminality to Blackness (\protect\hyperlink{ref-Muhammad2010}{Muhammad 2010}) prompted a shift ``from the War on Poverty to the War on Crime'' wherein Black communities' demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration (\protect\hyperlink{ref-Hinton2016}{\textbf{Hinton2016?}}; \protect\hyperlink{ref-Vargas2016}{\textbf{Vargas2016?}}). Ruth Wilson Gilmore explains how mid to late 20th-century whites ``demanded that the state become leaner and meaner, except when directed to do otherwise'' --- in other words, Keynesian welfare guarantees were undermined by the racist myth of ``welfare queens'' and supplanted by expanded police power (\protect\hyperlink{ref-Gilmore2007}{\textbf{Gilmore2007?}}).

The 2008 financial crisis solidified the connection between fiscal austerity and policing, prompting a decline in tax revenues that devastated state and local governments --- but law enforcement agencies were largely spared from cuts. At the local level, this means that police budgets today constitute about thirty percent of city budgets nationwide, and cities where residents have lower median incomes dedicate a larger proportion of spending to policing (\protect\hyperlink{ref-Friedman2020}{Friedman 2020}). In municipalities with substantial Black populations, then, people who are most heavily affected by criminalization are expected to foot the bill for their own mistreatment.

Today, fines and fees primarily target Black Americans: traffic stops and searches disproportionately affect Black motorists nationwide (\protect\hyperlink{ref-Pierson2020}{\textbf{Pierson2020?}}), and a host of local analyses confirm this finding (\protect\hyperlink{ref-Dunn2009}{Dunn 2009}; \protect\hyperlink{ref-Goncalves2020}{Goncalves and Mello 2020}; \protect\hyperlink{ref-Mughan2020}{Mughan 2020}). In criminal court proceedings, Black defendants tend to face more severe monetary sanctions (\protect\hyperlink{ref-Edwards2020}{Edwards and Harris 2020}; \protect\hyperlink{ref-Harris2011}{Harris, Evans, and Beckett 2011}).

In 2020, a Federal Reserve survey found that five percent of white respondents reported ``unpaid legal expenses, fines, or court costs,'' whereas twelve percent of Black respondents reported such debt (\protect\hyperlink{ref-BoardofGovernorsoftheFederalReserveSystem2020}{Governors of the Federal Reserve System 2020}). Across the country, city government reliance on fines and fees revenue is associated with larger Black populations (\protect\hyperlink{ref-UnitedStatesCommissiononCivilRights2017}{United States Commission on Civil Rights 2017}). Although major urban centers collect high dollar amounts of fines and fees, some of the most egregious ticketing practices measured on a per-capita basis are concentrated in suburbs or smaller cities with municipal courts --- Ferguson being a prominent example (\protect\hyperlink{ref-UnitedStatesDepartmentofJusticeCivilRightsDivision2015}{United States Department of Justice Civil Rights Division 2015}; \protect\hyperlink{ref-Mughan2020}{Mughan 2020}). The positive association between cities' reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator, however (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}).

Racial capitalist political economy imposes fiscal constraints regardless of city officials' intentions. In their study of fines and fees reliance in Chicago suburbs, Josh Pacewicz and John Robinson, III show how the racialization of municipal opportunity structures prevents majority-Black suburban governments from acquiring sufficient revenue from ``good'' sources such as sales taxes or property taxes, catalyzing a reliance on fines and fees to fund essential government services (\protect\hyperlink{ref-Pacewicz2020}{Pacewicz and N.Robinson 2020}). Importantly, Pacewicz and Robinson III note that these racialized municipal opportunity structures are tied to the political-historical processes of neoliberalism and fiscal austerity, an observation that aligns with recent scholarship detailing the origins of fees paid by incarcerated people (\protect\hyperlink{ref-Kirk2020}{Kirk, Fernandes, and Friedman 2020}). The late 20th century ``property tax revolt'' most significantly benefited white homeowners (\protect\hyperlink{ref-Martin2015}{\textbf{Martin2015?}}), and without property tax hikes as a revenue-raising option, smaller cities and towns have few choices.

Research regarding police stops and searches in response to local fiscal crisis shows how decreasing local revenues affect racist police practices. One study of all U.S. city governments found that local fiscal stress was related to increased ``revenue-generating arrests'' (e.g.~arrests involving civil asset forfeiture) and that Black and Hispanic people were arrested at higher rates (\protect\hyperlink{ref-Makowsky2009}{Makowsky and Stratmann 2009}). A study of four million North Carolina traffic stops found that fiscal stress caused a decrease in the probability of white drivers being searched, but no decrease for Black drivers {[}Shoub2020{]}. This suggests that higher reliance on fines and fees results in government officials and police targeting individuals who hold less political power --- whether those individuals are out-of-state motorists or members of local marginalized communities (\protect\hyperlink{ref-Makowsky2009}{Makowsky and Stratmann 2009}).

With this history in mind, we argue that Black Americans can situate exploitative ticketing practices in a longer historical legacy of collective disparate treatment and violence at the hands of the state, which may facilitate a stronger collective political analysis when police ticketing practices become more extreme. We expect that Black voters' political behavior in response to police ticketing will be distinct from the political behavior of white voters.

\hypertarget{data-and-design}{%
\section*{Data and Design}\label{data-and-design}}
\addcontentsline{toc}{section}{Data and Design}

We explore the effect of fees and fines collections on voter turnout by looking at two different levels: the municipal and the individual. Such an approach gives us both breadth and depth: our municipal-level analysis allows us to broadly understand the relationship between fees and fines across the entire United States, while the individual-level analyses allow us to interrogate the specific causal mechanisms at play.

\hypertarget{city-level-relationship-between-voter-turnout-and-fines-and-fees}{%
\subsection*{City-level relationship between voter turnout and fines and fees}\label{city-level-relationship-between-voter-turnout-and-fines-and-fees}}
\addcontentsline{toc}{subsection}{City-level relationship between voter turnout and fines and fees}

We begin with our nationwide analysis in which we observe the turnout and fees and fines collections of cities from around the country. Our data come from two primary sources: the US Census Bureau's Census of Governments Data (COG), and registered voter files from L2 Political.

\textbf{Census of Governments}: Every five years, the US Census Bureau collects data from governmental bodies around the country. We use two snapshots of the COG: one that covers the years 2008 - 2012, and another that covers 2013 - 2017. The COG includes a host of information about state and municipal finances. The COG asks municipalities to report how much revenue they collect from ``penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation\ldots{} and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).'' This data has been used as a proxy for the amount of tickets issued at the local level in scholarly research (see, for instance, \protect\hyperlink{ref-Goldstein2020}{Goldstein, Sances, and You 2020}; \protect\hyperlink{ref-Sances2017}{Sances and You 2017}).

The COG data are useful to isolate ticketing practices because other fines and fees (e.g.~fines imposed at sentencing in state court, probation fees, conviction fees, public defender fees) are typically collected by county or state governments. The COG data only include local revenues, which means the share of fines revenue corresponds more directly to local police practices.

\textbf{Registered Voter Files}: The COG data do not include estimates of turnout at the local level. To estimate local turnout, we leverage registered voter files provided by data vendor L2. Voters in Washington, DC, and every state in the country (with the exception of North Dakota) requires voters to register to vote prior to participating. These files are considered public record, and in most states contain information about each voter's age, residential address, political affiliation, and participation history. L2 collects these voter files from around the country and merges them with proprietary data that estimates other voter- and household-level characteristics such as race and education. L2 also geocodes voters' residential addresses. L2 does not collect all states' voter file on the same date; the date of the ``raw'' voter file from each state from which the L2 data are modelled can be found in Appendix A.

We merge these geocoded voter files with ``place'' and ``county subdivision'' shapefiles published by the US Census Bureau. By aggregating these individual-level records to the municipal level, we are able to estimate the number of registered voters and the number of ballots cast in every city in the country. By using the racial estimates provided by L2, we can estimate the number of ballots cast by voters of each race in each city. Although each voters' race is modeled based on L2's algorithms --- not self-reported --- it is possibly incorrect for some voters. We assume this does not present a problem when records are aggregated to the municipal level.

Although turnout could be calculated as a share of \emph{registered voters} who participated, such an approach could be biased. If fees and fines collection impact the number of individuals who register to vote, but not the share of registered voters who participate, our estimates will be compromised. We therefore calculate turnout by dividing the number of ballots cast according to L2 by the 5-year estimate of each municipality's citizen voting-age population (CVAP) from the US Census Bureau. These estimates are available for individual racial groups.

\textbf{Estimation Strategy}: We begin by merging each municipality's fees and fines per capita from the 2012 COG to its turnout from the 2014 midterm election, and the 2017 COG to its 2018 turnout. Because this measure is highly right-skewed, we use the natural log of fees and fines per capita plus one. We also control for other municipal and state characteristics. These include racial composition, population density, median income, collegiate education, median age, and share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality's revenue that comes from the state or federal government in the 2012 and 2017 COGs. We retain only municipalities whose data is reported to the COG in both 2012 and 2017. We then run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.

Unfortunately, the 5-year cycle of the COG does not neatly line up with the general 4-year cycle typical of American elections. The timing of the COG and midterm elections mean that our analytical strategy is conservative. If municipalities shift their fees and fines collections dramatically over the 2013 - 2017 period, this shift may influence their 2014 turnout. However, we assume that turnout in 2014 will still be influenced by the policing practices of the 2008 -- 2012 period, while 2018 turnout will be largely influenced by the practices of the 2013 -- 2017 period.

Our national two-way fixed effect model allows us to test our first two hypotheses:

\emph{Hypothesis 1: Increased reliance on fines and fees revenue at the city level affects voter turnout at the city level.}

\emph{Hypothesis 2: The effect of the city-level relationship between fines and voter turnout is distinct for Black voters --- i.e.~more pronounced than or in the opposite direction of the effect of fines on turnout for white voters.}

\hypertarget{individual-level-effects-of-ticketing}{%
\subsection*{Individual-Level Effects of Ticketing}\label{individual-level-effects-of-ticketing}}
\addcontentsline{toc}{subsection}{Individual-Level Effects of Ticketing}

Our national test of the relationship between municipal fees and fines collection and turnout offers novel insight into the political socialization of low-level police contact. It cannot, however, directly observe the causal mechanism we argue is at play: namely, that personal or proximal contact with the criminal legal system influences turnout. Our national analysis suffers from what is called the ecological fallacy: it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.

To test whether a ticket directly influences the turnout voters we turn to individual-level data from Hillsborough County, Florida (home to Tampa). Hillsborough County is interesting for theoretical reasons: Tampa is in the top decile of municipalities in terms of fees and fines increase between the 2012 and 2017 COGs, and its population puts it in the top 1 percent of cities nationwide. It also has a relatively large Black population, allowing us to test for racial differences in the turnout effect of ticketing.

Further, the Tampa Police Department was scrutinized by the Tampa Bay Times in 2015 for its relentless ticketing of Black bicyclists (\protect\hyperlink{ref-Zayas2015}{Zayas 2015}). This investigation catalyzed a U.S. Department of Justice investigation and report, requested by Tampa's mayor and police chief. In other words, there's strong evidence suggesting both racist targeting of tickets and potential publicity to catalyze distinct Black voter responses to the abusive behavior during the same time frame as our national analysis. Ticketing has also been expressly politicized in Tampa: Jane Castor, who was elected mayor in 2019, was Tampa's police chief until 2015 and publicly defended her department's disproportionate ticketing of Black bicyclists before retracting her defense during her mayoral campaign {[}CITE{]}. Her opponent, banker and philanthropist David Straz, campaigned against red-light cameras and focused his outreach in Tampa's Black communities.

Perhaps more prosaically, Hillsborough County also makes a unique set of data publicly available. The county clerk makes information available about every traffic stop in the county going back to 2003. This data includes the name and date of birth of the individual stopped; the date of the offense; and the amount the individual paid for a ticket. We retain only the records where the individual paid money.

To test the effect of ticketing on individual-level turnout, we match the first and last names and dates of birth against the Hillsborough County registered voter file from L2. To improve the quality of the match between the two datasets, we remove all punctuation from all names and convert all names to lower-case. This means that a ``Jonathan O'Shea'' in one file would match a ``jonathan oshea'' in the other. \protect\hyperlink{ref-Meredith2014}{Meredith and Morse} (\protect\hyperlink{ref-Meredith2014}{2014}) develops a test for assessing the prevalence of false-positives in administrative record matching. We present the results of that test in Appendix B, but we likely have a false-positive match of around 0.03 percent.

By matching these records, we identify all voters who were ticketed between the 2012 and 2018 general elections. Voters are considered ``treated'' for every general election following their first ticket. This means that a voter who was ticketed in early 2014 was considered treated''= for the 2014, 2016, and 2018 elections. A voter treated in 2017, on the other hand, is only considered treated in the 2018 election.

These voters are then matched to one control voter using what methodologists call a ``genetic'' process (\protect\hyperlink{ref-Sekhon2011}{Sekhon 2011}). The pool of potential control voters are the individuals who are never stopped during the 2012 -- 2018 period, regardless of whether they paid a fine. We match voters on individual-level characteristics (race / ethnicity; gender; party affiliation; age; registration date; number of traffic stops between 2003 and the 2012 election) and block group-level characteristics from the 2012 5-year ACS estimates (median income; share of the population with some college; unemployment rate).

We also match treated and control voters on their 2010 and 2012 general election turnout, as well as any other even-yeared general election turnout in the pre-treatment period. In other words, a voter ticketed in 2013 is matched to controls based on turnout in 2010 and 2012, while a voter ticketed in 2017 is matched to their control using 2010, 2012, 2014, and 2016 turnout. Because voters treated in later periods are matched to their controls along more covariates, we run three separate matches: one for voters stopped between the 2012 and 2014 elections; for voters stopped between the 2014 and 2016 elections; and for those stopped between the 2016 and 2018 elections.

\emph{Hypothesis 3: Among individuals who were ticketed (``treated'') in Tampa, their likelihood of turning out in a subsequent election roughly matches the racioethnic distribution apparent in the national city-level data. If fines uniquely mobilize Black voters nationally, they should also uniquely mobilize Black voters in Tampa.}

Because Tampa holds off-year local elections, we are able to test whether mobilized voters target officials who are able to change local police practices. \protect\hyperlink{ref-Laniyonu2019}{Laniyonu} (\protect\hyperlink{ref-Laniyonu2019}{2019}) gives us reason to believe that the effect should be stronger for local elections.

\emph{Hypothesis 4: Any potential mobilizing turnout effect in Tampa is stronger for local (mayoral) elections, since those elections directly affect police practices.}

That said, Laniyonu found that heavily policed, majority-Black New York City neighborhoods tended to vote for William Thompson, a Black candidate who opposed police reform --- which could suggest that Black voters prioritized descriptive representation over outward-facing policy messaging. In Tampa, however, both leading candidates were white, and Castor was the police chief during the city's racist ticketing scandal. Thus, the racioethnic identity of the candidates in 2019 should not affect ticketed Black voters' responses to candidates' policy messaging in the same way.

One novel feature of our analysis is that we are able to assess the political effects of both proximal and personal criminal legal contact during the same time frame. The COG data likely capture the voting behavior of people who were not personally ticketed, but know one or several people who were; and the Tampa data capture the voting behavior of people who were themselves ticketed.

Additionally, our analysis eliminates measurement problems that potentially affected past research and accounts for the temporal features of the relationship between criminal legal contact and voting. Several prior studies regarding criminalization and political behavior (\protect\hyperlink{ref-Walker2014}{Walker 2014}; \protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}) involve surveys where the measure of police contact is self-reported intensity of contact --- ``have you ever been stopped by police? Arrested? Incarcerated?'' Respondents were then asked to indicate how likely they might be to vote. Our analysis allows us to assess the actual voting behavior of people who we verify were ticketed and gauge the strength of the treatment effect over time by comparing each individual's participation in subsequent elections. It is also advantageous that we are able to capture actual voting behavior within a few months or weeks of treatment application --- only Walker and White conduct individual-level analyses consistent with voter file data, and Laniyonu conducts a neighborhood-level analysis using voter file data. This feature of our data also helps us avoid measurement issues with survey instruments used in prior studies --- for example, Lerman and Weaver are careful to note that people who have been arrested or incarcerated sometimes misreport their political behavior in survey research. Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to police ticketing.

\hypertarget{results}{%
\section*{Results}\label{results}}
\addcontentsline{toc}{section}{Results}

Before testing the causal effect of fees and fines collections, we begin with a cross-sectional analysis of the relationship between fees and fines and turnout. Here, we regress municipality-level turnout in 2018 against fees and fines collections as reported in the 2017 COG, as well as a number of other covariates. In Figure \ref{fig:mef-2018} we present the marginal effect of fees and fines on municipal-level turnout. The plot shows the results from two separate models: one in which the dependent variable is Black turnout (as a share of CVAP), and a second in which the dependent variable is non-Black turnout. The figure also marks the interdecile range. The full regression table can be found in Appendix XX.

\begin{figure}[H]

{\centering \includegraphics{draft_paper_files/figure-latex/cross-18-1}

}

\caption{\label{fig:mef-2018}Marginal Effect of per-capita Fees and Fines on Turnout, 2018}\label{fig:cross-18}
\end{figure}

As Figure \ref{fig:mef-2018} makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 1 percentage point over the interdecile range, after controlling for the other covariates. The opposite is true for Black voters: over the same range, Black turnout \emph{increases} by roughly 2.5 percentage points. Both of these relationships are statistically significant at the 95 confidence level. To be sure, this does not prove that higher fees and fines increase Black turnout; these cross-sectional regressions cannot establish causality. Nevertheless, Figure \ref{fig:mef-2018} is consistent with this story.

We turn now to our two-way fixed effects model. As discussed above, we retain each municipality that reported their fees and fines data to the COG in both 2012 and 2017 (and met the other criteria discussed in the \emph{Data and Design} section). The dependent variable in each model is calculated by dividing the number of ballots cast in 2014 and 2018 by the 5-year CVAP estimate from the same year. We run the two-way fixed effects on overall turnout, Black turnout, and non-Black turnout. The results of these models can be found in Table \ref{tab:twfe}.

\begin{singlespace}
\input{"../temp/2wfe_reg_clean.tex"}
\end{singlespace}

The results of the two-way fixed effects model are slightly different than what we saw in the 2018 cross-sectional approach; namely, while Table \ref{tab:twfe} indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not impact Black turnout. The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.06 percentage points. Moreover, because of the relative stability in fees and fines collections at the municipal level over this time period (the mean increase in per-capita fees and fines collections was just 6 percent, and the median municipality decreased by about 1.5 percent), it is not clear how informative this approach is.

In Table \ref{tab:coarser}, we re-estimate the model from Table \ref{tab:twfe} but coarsen the data. Here, we test whether turnout changed for municipalities who increased their fees and fines collections differently than municipalities where collections stayed the same or decreased. Municipalities that increased their per-capita fees and fines are considered ``treated.''

The coefficient on \emph{Treated × 2018} indicates that non-Black turnout dropped by about 0.5 percentage points in municipalities where fees and fines collections increased relative to other municipalities. While this coefficient is also negative for Black voters, it is not statistically significantly different from 0. In other words, both Tables \ref{tab:twfe} and \ref{tab:coarser} indicate that increased fees and fines collections decrease non-Black turnout but have no impact on Black turnout.

\hypertarget{individual-level-results}{%
\subsection*{Individual-Level Results}\label{individual-level-results}}
\addcontentsline{toc}{subsection}{Individual-Level Results}

Thus far, we have shown that the turnout effects of fees and fines collection impact municipal-level turnout, and that the effects are different for Black and non-Black Americans. We argue that this relationship is causal: increased fees and fines collections means that more residents have direct interactions with the criminal legal system. Based on prior literature, we assume there are indirect effects as well, as more residents know a family or community member who has been ticketed. While the national analysis gives us great breadth and an increased understanding of how this plays out across the country, municipal-level data leaves us unable to directly observe the causal mechanisms at play.

To directly observe the effect of being ticketed on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida. As discussed above, we match (\protect\hyperlink{ref-Sekhon2011}{Sekhon 2011}) individuals who were stopped and assessed a fine between the 2012 and 2018 elections to individuals who were not stopped during this time period.\footnote{Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights. The full sample is used in the actual matching process.} Matching is done with replacement and ties are not broken, meaning some treated voters may have more than XX controls; the regression weights reflect this possibility. In Table \ref{tab:balance} we present the results of the matching algorithm. We manage to reduce between treated and control voters substantially along all observed characteristics with the exception of 2012 turnout. However, this is not likely a problem: the turnout of all potential and actual controls were both within 0.1 percentage points of the treatment group's turnout that year.

\begin{singlespace}
\input{"../temp/coarser_reg_clean.tex"}
\end{singlespace}

\hypertarget{individual-level-results-1}{%
\subsection*{Individual-Level Results}\label{individual-level-results-1}}
\addcontentsline{toc}{subsection}{Individual-Level Results}

Thus far, we have shown that the turnout effects of fees and fines collection impact municipal-level turnout, and that the effects are different for Black and non-Black Americans. We argue that this relationship is causal: increased fees and fines collections means that more residents have direct interactions with the criminal legal system. Based on prior literature, we assume there are indirect effects as well, as more residents know a family or community member who has been ticketed. While the national analysis gives us great breadth and an increased understanding of how this plays out across the country, municipal-level data leaves us unable to directly observe the causal mechanisms at play.

To directly observe the effect of being ticketed on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida. As discussed above, we match (\protect\hyperlink{ref-Sekhon2011}{Sekhon 2011}) individuals who were stopped and assessed a fine between the 2012 and 2018 elections to individuals who were not stopped during this time period.\footnote{Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights. The full sample is used in the actual matching process.} Matching is done with replacement and ties are not broken, meaning some treated voters may have more than XX controls; the regression weights reflect this possibility. In Table \ref{tab:balance} we present the results of the matching algorithm. We manage to reduce between treated and control voters substantially along all observed characteristics with the exception of 2012 turnout. However, this is not likely a problem: the turnout of all potential and actual controls were both within 0.1 percentage points of the treatment group's turnout that year.

INSERT BALANCE TABLE

It is worth noting that voters who were stopped between 2012 and 2018 were far more likely to be Black, males, and registered Democrats than the general electorate, and live in Census block groups with moderately lower incomes. Unsurprisingly, they were also stopped at higher rates in the pre-treatment period than those never stopped between 2012 and 2018.

While Table \ref{tab:balance} indicates that our treatment voters and their matches are substantially similar to their matches, the validity of the difference-in-differences design requires that the treatment and control voters turned out at comparable rates in the baseline period. In Figure \ref{fig:did1}, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped. The first election following a treated voter's stop is denoted as \emph{t = 0}; subsequent elections take higher positive numbers, while the years in which \emph{t} is less than zero are the periods prior to the stop. This means that for someone stopped in 2013, \emph{t} is 0 in 2014, while \emph{t} is equal to 0 in 2018 for an individual stopped between the 2016 and 2018 elections.

\begin{figure}[H]

{\centering \includegraphics{draft_paper_files/figure-latex/did1-1}

}

\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout}\label{fig:did1}
\end{figure}

Figure \ref{fig:did1} makes a number of things immediately apparent. First, we can see that for both Black and non-Black voters the parallel trends assumption is satisfied. Because we matched treated and control voters based on turnout prior to the ticket, this is unsurprising. The visual results of the post-treatment trend corroborate what we found nationwide using the municipal-level data; namely, ticketing has a different effect for Black voters than for others..

Figure \ref{fig:did2} makes this effect even clearer. Here, we limit the analysis to voters who were stopped within the 90 days prior to an election (and their controls). We expected that the ticket would be more salient for individuals stopped shortly before the election. This appears to be the case --- \emph{especially for Black voters.}

\begin{figure}[H]

{\centering \includegraphics{draft_paper_files/figure-latex/did2-1}

}

\caption{\label{fig:did-2}Effect of Being Ticketed Within 90 Days of Election on Turnout}\label{fig:did2}
\end{figure}

Table \ref{tab:dind-table} formalizes Figures ref\{fig:did1\} and ref\{fig:did2\} into an ordinary least squares regression. Models 1 and 2 present the causal estimates of being stopped at any point in the two years prior to an election; Models 3 and 4 re-estimate the effect of being stopped within 90 days of an election. Models 1 and 3 show our overall causal effect, while Models 2 and 4 allow for the possibility that a ticket differentially mobilizes Black voters. The coefficients of note are \emph{Treated X Post Treatment} and \emph{Treated X Post Treatment X Black}. In models 1 and 3, \emph{Treated X Post Treatment} measures the overall treatment effect, and in models 2 and 4 it measures the treatment effect for non-Black voters. \emph{Treated X Post Treatment X Black} measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.

\begin{singlespace}
\input{"../temp/dind_reg.tex"}
\end{singlespace}

\newpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Behrens2003}{}%
Behrens, A., C. Uggen, and Jeff Manza. 2003. {``Ballot {Manipulation} and the {`{Menace} of {Negro Domination}'}: {Racial Threat} and {Felon Disenfranchisement} in the {United States}, 1850--20021.''} \emph{American Journal of Sociology}. \url{https://doi.org/10.1086/378647}.

\leavevmode\hypertarget{ref-Bell2017}{}%
Bell, Monica C. 2017. {``Police {Reform} and the {Dismantling} of {Legal Estrangement}.''} \emph{The Yale Law Journal} 126 (7): 2054--150. \url{http://www.jstor.org/stable/45222555}.

\leavevmode\hypertarget{ref-Blessett2016}{}%
Blessett, Brandi, and Richard Box. 2016. {``Sharecropper {Finance}: {Using} the {Justice System} as a {Public Revenue Source}.''} \emph{Public Integrity} 18 (January): 113--26. \url{https://doi.org/10.1080/10999922.2015.1111742}.

\leavevmode\hypertarget{ref-Brayne2014}{}%
Brayne, Sarah. 2014. {``Surveillance and {System Avoidance}: {Criminal Justice Contact} and {Institutional Attachment}.''} \emph{American Sociological Review} 79 (3): 367--91. \url{https://doi.org/10.1177/0003122414530398}.

\leavevmode\hypertarget{ref-Burch2014}{}%
Burch, Traci R. 2014. {``Effects of {Imprisonment} and {Community Supervision} on {Neighborhood Political Participation} in {North Carolina}.''} \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 184--201. \url{https://doi.org/10.1177/0002716213503093}.

\leavevmode\hypertarget{ref-Campbell2021}{}%
Campbell, Travis. 2021. {``Black {Lives Matter}'s {Effect} on {Police Lethal Use}-of-{Force}.''} SSRN Scholarly Paper ID 3767097. {Rochester, NY}: {Social Science Research Network}. \url{https://doi.org/10.2139/ssrn.3767097}.

\leavevmode\hypertarget{ref-CarpenterII2019}{}%
Carpenter II, Dick M, Kyle Sweetland, and Jennifer McDonald. 2019. {``The {Price} of {Taxation} by {Citation}: {Case Studies} of {Three Georgia Cities That Rely Heavily} on {Fines} and {Fees}.''} {Institute for Justice}.

\leavevmode\hypertarget{ref-Colgan2019}{}%
Colgan, Beth A. 2019. {``Wealth-{Based Penal Disenfranchisement}.''} \emph{Vanderbilt Law Review} 72 (January). \url{https://papers.ssrn.com/abstract=3312439}.

\leavevmode\hypertarget{ref-Desmond2016}{}%
Desmond, Matthew, Andrew V. Papachristos, and David S. Kirk. 2016. {``Police {Violence} and {Citizen Crime Reporting} in the {Black Community}.''} \emph{American Sociological Review} 81 (5): 857--76. \url{https://doi.org/10.1177/0003122416663494}.

\leavevmode\hypertarget{ref-DuBois1935}{}%
Du Bois, W. E. B. 1935. \emph{Black {Reconstruction} in {America}}. {Harcourt, Brace, and Howe}.

\leavevmode\hypertarget{ref-Dunn2009}{}%
Dunn, Ronnie A. 2009. {``Measuring {Racial Disparities} in {Traffic Ticketing Within Large Urban Jurisdictions}.''} \emph{Public Performance \& Management Review} 32 (4): 537--61. \url{https://doi.org/10.2753/PMR1530-9576320403}.

\leavevmode\hypertarget{ref-Edwards2020}{}%
Edwards, Frank, and Alexes Harris. 2020. {``An {Analysis} of {Court Imposed Monetary Sanctions} in {Seattle Municipal Courts}, 2000-2017.''} August. \url{https://doi.org/10.31235/osf.io/ajpqc}.

\leavevmode\hypertarget{ref-Friedman2020}{}%
Friedman, Brittany. 2020. {``Carceral {Immobility} and {Financial Capture}: {A Framework} for the {Consequences} of {Racial Capitalism Penology} and {Monetary Sanctions}.''} \emph{UCLA Criminal Justice Law Review} 4 (1). \url{https://escholarship.org/uc/item/31r669wf}.

\leavevmode\hypertarget{ref-Goldstein2020}{}%
Goldstein, Rebecca, Michael W. Sances, and Hye Young You. 2020. {``Exploitative {Revenues}, {Law Enforcement}, and the {Quality} of {Government Service}.''} \emph{Urban Affairs Review} 56 (1): 5--31. \url{https://doi.org/10.1177/1078087418791775}.

\leavevmode\hypertarget{ref-Goncalves2020}{}%
Goncalves, Felipe, and Steven Mello. 2020. {``A {Few Bad Apples}? {Racial Bias} in {Policing}.''} SSRN Scholarly Paper ID 3627809. {Rochester, NY}: {Social Science Research Network}. \url{https://doi.org/10.2139/ssrn.3627809}.

\leavevmode\hypertarget{ref-BoardofGovernorsoftheFederalReserveSystem2020}{}%
Governors of the Federal Reserve System, Board of. 2020. {``Report on the {Economic Well}-{Being} of {U}.{S}. {Households} in 2019, {Featuring Supplemental Data} from {April} 2020.''} {Federal Reserve System}. \url{https://www.federalreserve.gov/publications/report-economic-well-being-us-households.htm}.

\leavevmode\hypertarget{ref-Hadden2003}{}%
Hadden, Sally. 2003. \emph{Slave {Patrols}}. \url{https://www.hup.harvard.edu/catalog.php?isbn=9780674012349}.

\leavevmode\hypertarget{ref-Harris2010}{}%
Harris, Alexes, Heather Evans, and Katherine Beckett. 2010. {``Drawing {Blood} from {Stones}: {Legal Debt} and {Social Inequality} in the {Contemporary United States}.''} \emph{American Journal of Sociology} 115 (6): 1753--99. \url{https://doi.org/10.1086/651940}.

\leavevmode\hypertarget{ref-Harris2011}{}%
---------. 2011. {``Courtesy {Stigma} and {Monetary Sanctions}: {Toward} a {Socio}-{Cultural Theory} of {Punishment}.''} \emph{American Sociological Review} 76 (2): 234--64. \url{https://doi.org/10.1177/0003122411400054}.

\leavevmode\hypertarget{ref-Harris2017}{}%
Harris, Alexes, Beth Huebner, Karin Martin, Mary Pattillo, Becky Pettit, Sarah Shannon, Bryan Sykes, Chris Uggen, and April Fernandes. 2017. {``Monetary {Sanctions} in the {Criminal Justice System}.''}

\leavevmode\hypertarget{ref-Hinton2021}{}%
Hinton, Elizabeth, and DeAnza Cook. 2021. {``The {Mass Criminalization} of {Black Americans}: {A Historical Overview}.''} \emph{Annual Review of Criminology} 4 (1): 261--86. \url{https://doi.org/10.1146/annurev-criminol-060520-033306}.

\leavevmode\hypertarget{ref-EqualJusticeInitiative2017}{}%
Initiative, Equal Justice. 2017. {``Lynching in {America}: {Confronting} the {Legacy} of {Racial Terror}.''} \url{https://lynchinginamerica.eji.org/report/}.

\leavevmode\hypertarget{ref-Kirk2020}{}%
Kirk, Gabriela, April Fernandes, and Brittany Friedman. 2020. {``Who {Pays} for the {Welfare State}? {Austerity Politics} and the {Origin} of {Pay}-to-{Stay Fees} as {Revenue Generation}.''} \emph{Sociological Perspectives} 63 (6): 921--38. \url{https://doi.org/10.1177/0731121420967037}.

\leavevmode\hypertarget{ref-Laniyonu2019}{}%
Laniyonu, Ayobami. 2019. {``The {Political Consequences} of {Policing}: {Evidence} from {New York City}.''} \emph{Political Behavior} 41 (2): 527--58. \url{https://doi.org/10.1007/s11109-018-9461-9}.

\leavevmode\hypertarget{ref-Lee2014}{}%
Lee, Hedwig, Lauren C. Porter, and Megan Comfort. 2014. {``Consequences of {Family Member Incarceration}: {Impacts} on {Civic Participation} and {Perceptions} of the {Legitimacy} and {Fairness} of {Government}.''} \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 44--73. \url{https://doi.org/10.1177/0002716213502920}.

\leavevmode\hypertarget{ref-Lerman2014}{}%
Lerman, Amy E., and Vesla M. Weaver. 2014. \emph{Arresting Citizenship: The Democratic Consequences of {American} Crime Control}. Chicago Studies in {American} Politics. {Chicago ; London}: {The University of Chicago Press}.

\leavevmode\hypertarget{ref-Lichtenstein1996}{}%
Lichtenstein, Alexander C. 1996. \emph{Twice the {Work} of {Free Labor}}. {Verso}. \url{https://www.versobooks.com/books/738-twice-the-work-of-free-labor}.

\leavevmode\hypertarget{ref-Makowsky2009}{}%
Makowsky, Michael D., and Thomas Stratmann. 2009. {``Political {Economy} at {Any Speed}: {What Determines Traffic Citations}?''} \emph{The American Economic Review} 99 (1): 509--27. \url{http://www.jstor.org/stable/29730194}.

\leavevmode\hypertarget{ref-Mancini1978}{}%
Mancini, Matthew J. 1978. {``Race, {Economics}, and {The Abandonment} of {Convict Leasing}.''} \emph{The Journal of Negro History} 63 (4): 339--52. \url{https://doi.org/10.2307/2716851}.

\leavevmode\hypertarget{ref-Meredith2014}{}%
Meredith, Marc, and Michael Morse. 2014. {``Do {Voting Rights Notification Laws Increase Ex}-{Felon Turnout}?''} \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 220--49. \url{https://doi.org/10.1177/0002716213502931}.

\leavevmode\hypertarget{ref-Meredith2017}{}%
---------. 2017. {``Discretionary {Disenfranchisement}: {The Case} of {Legal Financial Obligations}.''} \emph{The Journal of Legal Studies} 46 (2): 309--38. \url{https://doi.org/10.1086/694323}.

\leavevmode\hypertarget{ref-Morris2020}{}%
Morris, Kevin. 2020. {``Neighborhoods and {Felony Disenfranchisement}: {The Case} of {New York City}.''} \emph{Urban Affairs Review}, May, 1078087420921522. \url{https://doi.org/10.1177/1078087420921522}.

\leavevmode\hypertarget{ref-Mughan2020}{}%
Mughan, Siân. 2020. {``Municipal {Reliance} on {Fine} and {Fee Revenues}: {How Local Courts Contribute} to {Extractive Revenue Practices} in {U}.{S}. {Cities}.''} \emph{Public Budgeting \& Finance}, December. \url{https://doi.org/10.1111/pbaf.12277}.

\leavevmode\hypertarget{ref-Muhammad2010}{}%
Muhammad, Khalil Gibran. 2010. \emph{The {Condemnation} of {Blackness} --- {Khalil Gibran Muhammad} \textbar{} {Harvard University Press}}. {Harvard University Press}. \url{https://www.hup.harvard.edu/catalog.php?isbn=9780674238145}.

\leavevmode\hypertarget{ref-Pacewicz2020}{}%
Pacewicz, Josh, and John N.Robinson III. 2020. {``Pocketbook Policing: {How} Race Shapes Municipal Reliance on Punitive Fines and Fees in the {Chicago} Suburbs.''} \emph{Socio-Economic Review}, October. \url{https://doi.org/10.1093/ser/mwaa029}.

\leavevmode\hypertarget{ref-Remster2018}{}%
Remster, Brianna, and Rory Kramer. 2018/ed. {``{SHIFTING POWER}: {The Impact} of {Incarceration} on {Political Representation}.''} \emph{Du Bois Review: Social Science Research on Race} 15 (2): 417--39. \url{https://doi.org/10.1017/S1742058X18000206}.

\leavevmode\hypertarget{ref-Rothstein2017}{}%
Rothstein, Richard. 2017. \emph{The Color of Law: A Forgotten History of How Our Government Segregated {America}}. First edition. {New York ; London}: {Liveright Publishing Corporation, a division of W. W. Norton \& Company}.

\leavevmode\hypertarget{ref-Sances2017}{}%
Sances, Michael W., and Hye Young You. 2017. {``Who {Pays} for {Government}? {Descriptive Representation} and {Exploitative Revenue Sources}.''} \emph{The Journal of Politics} 79 (3): 1090--94. \url{https://doi.org/10.1086/691354}.

\leavevmode\hypertarget{ref-Sekhon2011}{}%
Sekhon, Jasjeet S. 2011. {``Multivariate and {Propensity Score Matching Software} with {Automated Balance Optimization}: {The Matching} Package for {R}.''} \emph{Journal of Statistical Software} 42 (7): 1--52. \url{https://doi.org/10.18637/jss.v042.i07}.

\leavevmode\hypertarget{ref-Singla2020}{}%
Singla, Akheil, Charlotte Kirschner, and Samuel B. Stone. 2020. {``Race, {Representation}, and {Revenue}: {Reliance} on {Fines} and {Forfeitures} in {City Governments}.''} \emph{Urban Affairs Review} 56 (4): 1132--67. \url{https://doi.org/10.1177/1078087419834632}.

\leavevmode\hypertarget{ref-Sugie2015}{}%
Sugie, Naomi F. 2015. {``Chilling {Effects}: {Diminished Political Participation} Among {Partners} of {Formerly Incarcerated Men}.''} \emph{Social Problems} 62 (4): 550--71. \url{http://www.jstor.org/stable/44014875}.

\leavevmode\hypertarget{ref-Tyler2014}{}%
Tyler, Tom R., Jeffrey Fagan, and Amanda Geller. 2014. {``Street {Stops} and {Police Legitimacy}: {Teachable Moments} in {Young Urban Men}'s {Legal Socialization}.''} \emph{Journal of Empirical Legal Studies} 11 (4): 751--85. \url{https://doi.org/10.1111/jels.12055}.

\leavevmode\hypertarget{ref-Uggen2020}{}%
Uggen, Christopher, Ryan Larson, Sarah Shannon, and Arleth Pulido-Nava. 2020. {``Locked {Out} 2020: {Estimates} of {People Denied Voting Rights Due} to a {Felony Conviction}.''} Research report. {The Sentencing Project}. \url{https://www.sentencingproject.org/wp-content/uploads/2020/10/Locked-Out-2020.pdf}.

\leavevmode\hypertarget{ref-UnitedStatesCommissiononCivilRights2017}{}%
United States Commission on Civil Rights. 2017. {``Targeted {Fines} and {Fees Against Communities} of {Color}.''} \url{https://www.usccr.gov/pubs/2017/Statutory_Enforcement_Report2017.pdf}.

\leavevmode\hypertarget{ref-UnitedStatesDepartmentofJusticeCivilRightsDivision2015}{}%
United States Department of Justice Civil Rights Division. 2015. {``Investigation of the {Ferguson Police Department}.''} \url{https://www.justice.gov/sites/default/files/opa/press-releases/attachments/2015/03/04/ferguson_police_department_report.pdf}.

\leavevmode\hypertarget{ref-Walker2014}{}%
Walker, Hannah L. 2014. {``Extending the {Effects} of the {Carceral State}: {Proximal Contact}, {Political Participation}, and {Race}.''} \emph{Political Research Quarterly}, July. \url{https://doi.org/10.1177/1065912914542522}.

\leavevmode\hypertarget{ref-Walker2020}{}%
---------. 2020. {``Targeted: {The Mobilizing Effect} of {Perceptions} of {Unfair Policing Practices}.''} \emph{The Journal of Politics} 82 (1): 119--34. \url{https://doi.org/10.1086/705684}.

\leavevmode\hypertarget{ref-Walker2017}{}%
Walker, Hannah L., and Marcela García-Castañon. 2017. {``For {Love} and {Justice}: {The Mobilizing} of {Race}, {Gender}, and {Criminal Justice Contact}.''} \emph{Politics \& Gender} 13 (4): 541--68. \url{https://doi.org/10.1017/S1743923X17000198}.

\leavevmode\hypertarget{ref-Weaver2010}{}%
Weaver, Vesla M., and Amy E. Lerman. 2010. {``Political {Consequences} of the {Carceral State}.''} \emph{American Political Science Review} 104 (4): 817--33. \url{https://doi.org/10.1017/S0003055410000456}.

\leavevmode\hypertarget{ref-White2019}{}%
White, Ariel. 2019. {``Family {Matters}? {Voting Behavior} in {Households} with {Criminal Justice Contact}.''} \emph{American Political Science Review} 113 (2): 607--13. \url{https://doi.org/10.1017/S0003055418000862}.

\leavevmode\hypertarget{ref-Zayas2015}{}%
Zayas, Alexandra. 2015. {``How Riding Your Bike Can Land You in Trouble with the Cops --- If You're Black.''} \emph{Tampa Bay Times}, April 15, 2015. \url{https://www.tampabay.com/news/publicsafety/how-riding-your-bike-can-land-you-in-trouble-with-the-cops—if-youre-black/2225966/}.

\end{CSLReferences}

\end{document}

### 2021-03-16 markdown/draft_paper.Rmd
draft paper

@@
 In Tampa, Florida, we estimate that Black voters who were ticketed in the 90-day period preceding a federal election were 3 percentage points more likely to turn out in federal elections.
+
+  |
+  |
+  **Keywords**: voting, monetary sanctions, race, punishment, political participation
 ---
+
 \pagenumbering{gobble}
@@
 \doublespacing
+
+# Introduction {-}
+
 Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities’ alienation from government.
@@
                   align = c("l", "l", "l"), "latex") %>%
-  kable_styling(latex_options = c("HOLD_position"),
+  kable_styling(latex_options = c("HOLD_position", "striped"),
                 full_width = F) %>% 
@@
 
+\begin{singlespace}
+\input{"../temp/coarser_reg_clean.tex"}
+\end{singlespace}
+
 The coefficient on *Treated × 2018* indicates that non-Black turnout dropped by about 0.5 percentage points in municipalities where fees and fines collections increased relative to other municipalities.
@@
 In other words, both Tables \ref{tab:twfe} and \ref{tab:coarser} indicate that increased fees and fines collections decrease non-Black turnout but have no impact on Black turnout.
-
-## Individual-Level Results {-}
-
-Thus far, we have shown that the turnout effects of fees and fines collection impact municipal-level turnout, and that the effects are different for Black and non-Black Americans.
-We argue that this relationship is causal: increased fees and fines collections means that more residents have direct interactions with the criminal legal system.
-Based on prior literature, we assume there are indirect effects as well, as more residents know a family or community member who has been ticketed.
-While the national analysis gives us great breadth and an increased understanding of how this plays out across the country, municipal-level data leaves us unable to directly observe the causal mechanisms at play.
-
-To directly observe the effect of being ticketed on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
-As discussed above, we match [@Sekhon2011] individuals who were stopped and assessed a fine between the 2012 and 2018 elections to individuals who were not stopped during this time period.^[Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
-The full sample is used in the actual matching process.]  Matching is done with replacement and ties are not broken, meaning some treated voters may have more than XX controls; the regression weights reflect this possibility.
-In Table \ref{tab:balance} we present the results of the matching algorithm.
-We manage to reduce between treated and control voters substantially along all observed characteristics with the exception of 2012 turnout.
-However, this is not likely a problem: the turnout of all potential and actual controls were both within 0.1 percentage points of the treatment group’s turnout that year.
-
-\begin{singlespace}
-\input{"../temp/coarser_reg_clean.tex"}
-\end{singlespace}
 

### 2021-03-16 code/hills/03_match.R
clean up latex. build balance table

@@ -344,10 +344,10 @@ stargazer(models1, models2,
           covariate.labels = c("Treated",
                                "Post Treatment",
                                "Black",
-                               "Treated X Post Treatment",
-                               "Treated X Black",
-                               "Post Treatment X Black",
-                               "Treated X Post Treatment X Black"),
+                               "Treated $\\times$ Post Treatment",
+                               "Treated $\\times$ Black",
+                               "Post Treatment $\\times$ Black",
+                               "Treated $\\times$ Post Treatment $\\times$ Black"),
           table.layout = "-cm#-t-a-s-n",
           notes = "TO REPLACE",
           title = "\\label{tab:dind-table} Turnout Effects of Tickets",
@@ -370,6 +370,17 @@ j <- bind_rows(j, data.frame(V1 = c(insert1, insert2), n = c(5.1, nrow(j) + 1 - 
   arrange(n) %>%
   select(-n)
 
+j <- mutate(j, n = row_number())
+
+j$V1 <- gsub("Stopped within 90 Days of Election", "Stopped within 90", j$V1)
+
+ins <- "&&&\\multicolumn{2}{c}{Days of Election} \\\\"
+
+j <- bind_rows(j,
+               data.table(V1 = ins,
+                          n = 9.1)) %>% 
+  arrange(n) %>% 
+  select(-n)
 
 write.table(j, "./temp/dind_reg.tex", quote = F, col.names = F,
             row.names = F)
@@ -428,11 +439,11 @@ write.table(j, "./temp/dind_reg.tex", quote = F, col.names = F,
 ###############
 
 demos_all_control <- filter(hills_pre_match, fd > "2018-11-06") %>% 
-  select(-LALVOTERID, -GEOID, -fd, -max_amount, -v14, -v16) %>% 
+  select(-voter_id, -GEOID, -fd, -max_amount, -v14, -v16) %>% 
   summarize_all(mean) %>% 
   mutate(group = "All Untreated")
 
-demos_reg <- inner_join(matches_wide, hills_pre_match, by = c("voter" = "LALVOTERID")) %>% 
+demos_reg <- inner_join(matches_wide, hills_pre_match, by = c("voter" = "voter_id")) %>% 
   mutate(group = ifelse(group == voter, "Treated", "Actual Controls")) %>% 
[…]

### 2021-03-16 markdown/draft_paper.Rmd
write

@@
 Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level [@Burch2014].
-KEVIN WRITE A SENTENCE ABOUT YOUR PAPER HERE.
-[@Morris2020].
+@Morris2020 similarly finds that neighborhoods with more active voters lost to felony disenfranchisement turned out at lower rates in the 2017 mayoral race in NYC, and that this effect was particularly pronounced in Black neighborhoods.
 
@@
 If proximal contact mobilizes, then, mobilized voters are likely targeting officials who they perceive as holding the power to change police practices.
-To the extent that descriptive representation mitigates exploitative fines and fees practices [-@Sances2017], this could constitute an effective political strategy.
+To the extent that descriptive representation mitigates exploitative fines and fees practices [@Sances2017], this could constitute an effective political strategy.
 
@@
 
+Type of criminal legal contact
+Personal contact effect on political behavior (individual level)
+Proximal contact effect on political behavior (social network/geography)
+Stopped
+Weaver and Lerman find chilling effect; Walker finds mobilizing effect
+Laniyonu and Walker find mobilizing effect
+Arrested
+Weaver and Lerman find chilling effect; Walker finds mobilizing effect
+Walker finds mobilizing effect
+Convicted / Supervision
+Burch, Weaver and Lerman find chilling effect; Walker finds mobilizing effect 
+Burch, Lee, Sugie, White, and Morris find chilling effect; Walker finds mobilizing effect
+Incarcerated
+Burch, White, Weaver and Lerman find chilling effect; Walker finds mobilizing effect
+Burch, Lee, Sugie, White, and Morris find chilling effect; Walker finds mobilizing effect
+
+\begin{singlespace}
 ```{r lit-table, echo = F, warning = F}
 t <- fread("./raw_data/lit_table.csv")
-j <- knitr::kable(t, booktabs = T, caption = "\\label{tab:lit-table} Summary of Literature", linesep = "",
+j <- knitr::kable(t, booktabs = T, caption = "(\\#tab:lit-table) Summary of Literature", linesep = "",
                   align = c("l", "l", "l"), "latex") %>%
@@
   column_spec(3, width = "10em")
-write(j, "./temp/tab_lit.tex")
+j
 ```
-\begin{singlespace}
-\input{"../temp/tab_lit.tex"}
 \end{singlespace}
@@
 It’s possible that any potentially mobilizing effects of criminal legal contact became stronger in the 2010s --- in other words, Black Lives Matter could have facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis.
-That said, -@Laniyonu2019 did demonstrate mobilization in Black neighborhoods before the beginning of the Black Lives Matter movement.
+That said, Laniyonu did demonstrate mobilization in Black neighborhoods before the beginning of the Black Lives Matter movement.
 
@@
 
-Cedric Robinson’s articulation of racial capitalism offers a useful theoretical framework for interpreting the trajectory of American anti-Black political economy [@Robinson2005].
-Brittany Friedman theorizes fines and fees as a “progression of racial capitalism penology,” emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices [@Friedman2020, page 177].
+Cedric Robinson’s articulation of racial capitalism offers a useful theoretical framework for interpreting the trajectory of American anti-Black political economy [@Robinson2000].
+Brittany Friedman theorizes fines and fees as a “progression of racial capitalism penology,” emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices [@Friedman2020, page177].
 Robinson argues that European industrial capitalism continued a longer political-economic trend of differentiating racial groups in order to dispossess them and exploit their labor.
@@
 In the 20th century, residential segregation simultaneously fueled the racial wealth gap and ensured that criminalization was both spatially and racially concentrated [@Rothstein2017; @Hinton2021].
-At the level of federal policy, racial threat and whites’ attribution of criminality to Blackness [@Muhammad2010] prompted a shift “from the War on Poverty to the War on Crime” wherein Black communities’ demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration [@Hinton2016; @Vargas2016].
+At the level of federal policy, racial threat and whites’ attribution of criminality to Blackness [@Muhammad2010] prompted a shift “from the War on Poverty to the War on Crime” wherein Black communities’ demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration [@Hinton2017; @Vargas2017].
 Ruth Wilson Gilmore explains how mid to late 20th-century whites “demanded that the state become leaner and meaner, except when directed to do otherwise” --- in other words, Keynesian welfare guarantees were undermined by the racist myth of “welfare queens” and supplanted by expanded police power [@Gilmore2007, page 53].
@@
 Importantly, Pacewicz and Robinson III note that these racialized municipal opportunity structures are tied to the political-historical processes of neoliberalism and fiscal austerity, an observation that aligns with recent scholarship detailing the origins of fees paid by incarcerated people [@Kirk2020].
-The late 20th century “property tax revolt” most significantly benefited white homeowners [@Martin2015], and without property tax hikes as a revenue-raising option, smaller cities and towns have few choices.
+The late 20th century “property tax revolt” most significantly benefited white homeowners [@Martin2017], and without property tax hikes as a revenue-raising option, smaller cities and towns have few choices.
 
@@
 arrests involving civil asset forfeiture) and that Black and Hispanic people were arrested at higher rates [@Makowsky2009].
-A study of four million North Carolina traffic stops found that fiscal stress caused a decrease in the probability of white drivers being searched, but no decrease for Black drivers [Shoub2020].
+A study of four million North Carolina traffic stops found that fiscal stress caused a decrease in the probability of white drivers being searched, but no decrease for Black drivers [@Shoub2020].
 This suggests that higher reliance on fines and fees results in government officials and police targeting individuals who hold less political power --- whether those individuals are out-of-state motorists or members of local marginalized communities [@Makowsky2009].
@@
 We expect that Black voters’ political behavior in response to police ticketing will be distinct from the political behavior of white voters.
+
+## Fines, perceptions of government, and voting {-}
+
+The explosion of the reach of the criminal legal system in recent years --- both in terms of fees and fines collection, overzealous prosecution, and mass incarceration --- have had major ramifications on how Americans understand their identities and citizens and their relationship to their government.
+This is doubly true for Black Americans.
+As discussed above, this is not new: the “hidden curriculum” of the criminal legal system has long been a site of political socialization in the United States.
+In recent years, research has helped us make sense of the democratic ramifications of this.Traffic stops affect far more Americans than arrests and incarceration do: in 2018, more than 24 million people experienced police contact in the context of a traffic stop, whereas about 5.17 million people are disenfranchised as a result of a felony conviction [@Harrell2020; @Uggen2020].
+Sances and You [@Sances2017] explicitly suggested that “fines may make descriptive representation less likely by depressing minority turnout,” and called for further research regarding voter turnout and the imposition of fines.
+Our analysis picks up where they left off.
+
+These political barriers also disproportionately affect Black people.
+In Alabama, for example, Black people with felony convictions applying to have their voting rights restored were 26 percentage points more likely to have their application denied over outstanding fines and fees [@Meredith2017].
+
+Although the majority of voters in our analysis do not have felony convictions,
 
@@
 In other words, there’s strong evidence suggesting both racist targeting of tickets and potential publicity to catalyze distinct Black voter responses to the abusive behavior during the same time frame as our national analysis.
-Ticketing has also been expressly politicized in Tampa: Jane Castor, who was elected mayor in 2019, was Tampa’s police chief until 2015 and publicly defended her department’s disproportionate ticketing of Black bicyclists before retracting her defense during her mayoral campaign [CITE].
-Her opponent, banker and philanthropist David Straz, campaigned against red-light cameras and focused his outreach in Tampa’s Black communities.
+Ticketing has also been expressly politicized in Tampa: Jane Castor, who was elected mayor in 2019, was Tampa’s police chief until 2015 and publicly defended her department’s disproportionate ticketing of Black bicyclists before retracting her defense ahead of her mayoral campaign [@Carlton2018].
+Her opponent, banker and philanthropist David Straz, campaigned against red-light cameras and focused his outreach in Tampa’s Black communities [@Frago2019].
 
-Perhaps more prosaically, Hillsborough County also makes a unique set of data publicly available.
+Hillsborough County also makes a unique set of data publicly available.
 The county clerk makes information available about every traffic stop in the county going back to 2003.
@@
 
-INSERT BALANCE TABLE
+\begin{singlespace}
+```{r baltab-chunk, echo = F, warning = F}
+t <- readRDS("temp/balance_table.rds")
+j <- knitr::kable(t, booktabs = T,  caption = "(\\#tab:balance) Balance Table", linesep = "") %>%
+  kable_styling(latex_options = c("scale_down", "HOLD_position"))
+j
+```
+\end{singlespace}
 
@@
 
-Table \ref{tab:dind-table} formalizes Figures ref{fig:did1} and ref{fig:did2} into an ordinary least squares regression.
+Table \ref{tab:dind-table} formalizes Figures \ref{fig:did1} and \ref{fig:did2} into an ordinary least squares regression.
 Models 1 and 2 present the causal estimates of being stopped at any point in the two years prior to an election; Models 3 and 4 re-estimate the effect of being stopped within 90 days of an election.
 Models 1 and 3 show our overall causal effect, while Models 2 and 4 allow for the possibility that a ticket differentially mobilizes Black voters.
-The coefficients of note are *Treated X Post Treatment* and *Treated X Post Treatment X Black*.
-In models 1 and 3, *Treated X Post Treatment* measures the overall treatment effect, and in models 2 and 4 it measures the treatment effect for non-Black voters.
-*Treated X Post Treatment X Black* measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
+The coefficients of note are *Treated × Post Treatment* and *Treated × Post Treatment × Black*.
+In models 1 and 3, *Treated × Post Treatment* measures the overall treatment effect, and in models 2 and 4 it measures the treatment effect for non-Black voters.
+*Treated × Post Treatment × Black* measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
 
@@
 
-\newpage
-# References {-}
+Model 3 indicates that a ticket is neither mobilizing nor demobilizing --- the coefficient is small and nonsignificant (*p* = 0.34) but that tickets do mobilize Black voters.
+Receiving a ticket increases the average turnout for Black voters in the first two elections by about 1.1 percentage points.
+Model 4 shows that ticketing shortly before an election increases the turnout of non-Black voters by about 0.9 percentage points, and there is no statistically significantly different effect for Black voters.
+However, Figure \ref{fig:did2} visually indicates that the effect might be larger for Black voters, and the coefficient on *Treated × Post Treatment × Black* is large (as is its standard error).
+These two facts taken together indicate that our inability to detect a differentially mobilizing effect for Black voters stopped shortly before an election may have more to do with issues of statistical power than an additional effect that is really equal to zero.
+
+[Tampa - local figure/table]
+
+[Tampa local analysis]
+
+### Discussion {-}
+
+[Our results provide support for Walker’s theory of low-level police contact mobilizing nonwhite political participation.
+
+the role of fines and fees in the context of felony disenfranchisement has recently taken on greater political significance.
+After Floridians voted to restore voting rights to individuals with felony convictions in 2018, Florida Republicans passed legislation requiring these individuals to pay off the fines and fees associated with their original sentence.
+Because Florida does not maintain good records on who owes how much, this has proved to be a major hurdle for potential voters.
+
+[Laniyonu] - [he writes that block groups with higher Black pop and higher SQF density voted at higher rates for Thompson, the candidate who pledged not to implement SQF reform, but who was Black.
+The descriptive representation from Sances2017 kind of covers for this, tactically speaking - electing Black politicians should reduce fines and fees abuses.
+But in Tampa, the current mayor, Jane Castor, was the police chief until 2015 --- which overlaps with the treatment period in our analysis.
+One voter told the Tampa Bay Times that he voted against Castor as “payback” for the racist ticketing practices she oversaw, and the article notes that her opponent won five majority-Black precincts [@Frago2019].
+In 2015, Castor even released a statement as police chief supporting the racist ticketing, insisting that “Many individuals receiving bike citations are involved in criminal activity.”
+
+[Why do we think Black voters are mobilized? “Linked fate,” history, contemporary practices, Black Lives Matter.]
+
+[Limitations of research.] [We don’t look at people who aren’t registered to vote in 2018, so there could be some proportion of ticketed Black motorists who are now less likely to register to vote in the first place, for example.
+In other words our mobilization effect size only applies to people who were registered to vote.
+At the same time, perhaps people who weren’t registered were equally likely to be deterred by something else.]
+
+[Because we only look at Tampa, we don’t have a good idea of whether the revenue reliance trends interact with the experience of ticketing.
+Is ticketing a particularly alienating-mobilizing phenomenon in cities that are palpably dialing up their revenue collection efforts?
+Future research could test this hypothesis in cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.]
+
+[Unlike previous studies using survey data, we are unable to tell whether individuals in Tampa have non-ticketing criminal legal exposure.
+Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.]
+
+[Relevance for other scholars. Future research agenda.]

### 2021-03-16 markdown/draft_paper.tex
draft paper
write

@@
 In Tampa, Florida, we estimate that Black voters who were ticketed in the 90-day period preceding a federal election were 3 percentage points more likely to turn out in federal elections.
+
+\hfill\break
+
+\textbf{Keywords}: voting, monetary sanctions, race, punishment, political participation
 \end{abstract}
@@
 \doublespacing
+
+\hypertarget{introduction}{%
+\section*{Introduction}\label{introduction}}
+\addcontentsline{toc}{section}{Introduction}
 
@@
 Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level (\protect\hyperlink{ref-Burch2014}{Burch 2014}).
-KEVIN WRITE A SENTENCE ABOUT YOUR PAPER HERE.
-(\protect\hyperlink{ref-Morris2020}{Morris 2020}).
+\protect\hyperlink{ref-Morris2020}{Morris} (\protect\hyperlink{ref-Morris2020}{2020}) similarly finds that neighborhoods with more active voters lost to felony disenfranchisement turned out at lower rates in the 2017 mayoral race in NYC, and that this effect was particularly pronounced in Black neighborhoods.
 
@@
 If proximal contact mobilizes, then, mobilized voters are likely targeting officials who they perceive as holding the power to change police practices.
-To the extent that descriptive representation mitigates exploitative fines and fees practices (\protect\hyperlink{ref-Sances2017}{2017}), this could constitute an effective political strategy.
+To the extent that descriptive representation mitigates exploitative fines and fees practices (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}), this could constitute an effective political strategy.
 
@@
 
+Type of criminal legal contact
+Personal contact effect on political behavior (individual level)
+Proximal contact effect on political behavior (social network/geography)
+Stopped
+Weaver and Lerman find chilling effect; Walker finds mobilizing effect
+Laniyonu and Walker find mobilizing effect
+Arrested
+Weaver and Lerman find chilling effect; Walker finds mobilizing effect
+Walker finds mobilizing effect
+Convicted / Supervision
+Burch, Weaver and Lerman find chilling effect; Walker finds mobilizing effect
+Burch, Lee, Sugie, White, and Morris find chilling effect; Walker finds mobilizing effect
+Incarcerated
+Burch, White, Weaver and Lerman find chilling effect; Walker finds mobilizing effect
+Burch, Lee, Sugie, White, and Morris find chilling effect; Walker finds mobilizing effect
+
 \begin{singlespace}
-\input{"../temp/tab_lit.tex"}
+\begin{table}[H]
+
+\caption{\label{tab:lit-table}\label{tab:lit-table} Summary of Literature}
+\centering
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}}
+\toprule
+Type of criminal legal contact & Personal contact effect on political behavior (individual level) & Proximal contact effect on political behavior (social network/geography)\\
+\midrule
+\cellcolor{gray!6}{Stopped} & \cellcolor{gray!6}{Weaver and Lerman find chilling effect; Walker finds mobilizing effect} & \cellcolor{gray!6}{Laniyonu and Walker find mobilizing effect}\\
+Arrested & Weaver and Lerman find chilling effect; Walker finds mobilizing effect & Walker finds mobilizing effect\\
+\cellcolor{gray!6}{Convicted / Supervision} & \cellcolor{gray!6}{Burch, Weaver and Lerman find chilling effect; Walker finds mobilizing effect} & \cellcolor{gray!6}{Burch, Lee, Sugie, White, and Morris find chilling effect; Walker finds mobilizing effect}\\
+Incarcerated & Burch, White, Weaver and Lerman find chilling effect; Walker finds mobilizing effect & Burch, Lee, Sugie, White, and Morris find chilling effect; Walker finds mobilizing effect\\
+\bottomrule
+\end{tabular}
+\end{table}
 \end{singlespace}
@@
 It's possible that any potentially mobilizing effects of criminal legal contact became stronger in the 2010s --- in other words, Black Lives Matter could have facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis.
-That said, (\protect\hyperlink{ref-Laniyonu2019}{2019}) did demonstrate mobilization in Black neighborhoods before the beginning of the Black Lives Matter movement.
+That said, Laniyonu did demonstrate mobilization in Black neighborhoods before the beginning of the Black Lives Matter movement.
 
@@
 
-Cedric Robinson's articulation of racial capitalism offers a useful theoretical framework for interpreting the trajectory of American anti-Black political economy (\protect\hyperlink{ref-Robinson2005}{\textbf{Robinson2005?}}).
-Brittany Friedman theorizes fines and fees as a ``progression of racial capitalism penology,'' emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices (\protect\hyperlink{ref-Friedman2020}{Friedman 2020, 177}).
+Cedric Robinson's articulation of racial capitalism offers a useful theoretical framework for interpreting the trajectory of American anti-Black political economy (\protect\hyperlink{ref-Robinson2000}{Robinson 2000}).
+Brittany Friedman theorizes fines and fees as a ``progression of racial capitalism penology,'' emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices (\protect\hyperlink{ref-Friedman2020}{Friedman 2020, page177}).
 Robinson argues that European industrial capitalism continued a longer political-economic trend of differentiating racial groups in order to dispossess them and exploit their labor.
@@
 In the 20th century, residential segregation simultaneously fueled the racial wealth gap and ensured that criminalization was both spatially and racially concentrated (\protect\hyperlink{ref-Rothstein2017}{Rothstein 2017}; \protect\hyperlink{ref-Hinton2021}{Hinton and Cook 2021}).
-At the level of federal policy, racial threat and whites' attribution of criminality to Blackness (\protect\hyperlink{ref-Muhammad2010}{Muhammad 2010}) prompted a shift ``from the War on Poverty to the War on Crime'' wherein Black communities' demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration (\protect\hyperlink{ref-Hinton2016}{\textbf{Hinton2016?}}; \protect\hyperlink{ref-Vargas2016}{\textbf{Vargas2016?}}).
-Ruth Wilson Gilmore explains how mid to late 20th-century whites ``demanded that the state become leaner and meaner, except when directed to do otherwise'' --- in other words, Keynesian welfare guarantees were undermined by the racist myth of ``welfare queens'' and supplanted by expanded police power (\protect\hyperlink{ref-Gilmore2007}{\textbf{Gilmore2007?}}).
+At the level of federal policy, racial threat and whites' attribution of criminality to Blackness (\protect\hyperlink{ref-Muhammad2010}{Muhammad 2010}) prompted a shift ``from the War on Poverty to the War on Crime'' wherein Black communities' demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration (\protect\hyperlink{ref-Hinton2017}{Hinton 2017}; \protect\hyperlink{ref-Vargas2017}{\textbf{Vargas2017?}}).
+Ruth Wilson Gilmore explains how mid to late 20th-century whites ``demanded that the state become leaner and meaner, except when directed to do otherwise'' --- in other words, Keynesian welfare guarantees were undermined by the racist myth of ``welfare queens'' and supplanted by expanded police power (\protect\hyperlink{ref-Gilmore2007}{Gilmore 2007, 53}).
 
@@
 
-Today, fines and fees primarily target Black Americans: traffic stops and searches disproportionately affect Black motorists nationwide (\protect\hyperlink{ref-Pierson2020}{\textbf{Pierson2020?}}), and a host of local analyses confirm this finding (\protect\hyperlink{ref-Dunn2009}{Dunn 2009}; \protect\hyperlink{ref-Goncalves2020}{Goncalves and Mello 2020}; \protect\hyperlink{ref-Mughan2020}{Mughan 2020}).
+Today, fines and fees primarily target Black Americans: traffic stops and searches disproportionately affect Black motorists nationwide (\protect\hyperlink{ref-Pierson2020}{Pierson et al.
+2020}), and a host of local analyses confirm this finding (\protect\hyperlink{ref-Dunn2009}{Dunn 2009}; \protect\hyperlink{ref-Goncalves2020}{Goncalves and Mello 2020}; \protect\hyperlink{ref-Mughan2020}{Mughan 2020}).
 In criminal court proceedings, Black defendants tend to face more severe monetary sanctions (\protect\hyperlink{ref-Edwards2020}{Edwards and Harris 2020}; \protect\hyperlink{ref-Harris2011}{Harris, Evans, and Beckett 2011}).
@@
 Importantly, Pacewicz and Robinson III note that these racialized municipal opportunity structures are tied to the political-historical processes of neoliberalism and fiscal austerity, an observation that aligns with recent scholarship detailing the origins of fees paid by incarcerated people (\protect\hyperlink{ref-Kirk2020}{Kirk, Fernandes, and Friedman 2020}).
-The late 20th century ``property tax revolt'' most significantly benefited white homeowners (\protect\hyperlink{ref-Martin2015}{\textbf{Martin2015?}}), and without property tax hikes as a revenue-raising option, smaller cities and towns have few choices.
+The late 20th century ``property tax revolt'' most significantly benefited white homeowners (\protect\hyperlink{ref-Martin2017}{Martin and Beck 2017}), and without property tax hikes as a revenue-raising option, smaller cities and towns have few choices.
 
@@
 city governments found that local fiscal stress was related to increased ``revenue-generating arrests'' (e.g.~arrests involving civil asset forfeiture) and that Black and Hispanic people were arrested at higher rates (\protect\hyperlink{ref-Makowsky2009}{Makowsky and Stratmann 2009}).
-A study of four million North Carolina traffic stops found that fiscal stress caused a decrease in the probability of white drivers being searched, but no decrease for Black drivers {[}Shoub2020{]}.
+A study of four million North Carolina traffic stops found that fiscal stress caused a decrease in the probability of white drivers being searched, but no decrease for Black drivers (\protect\hyperlink{ref-Shoub2020}{\textbf{Shoub2020?}}).
 This suggests that higher reliance on fines and fees results in government officials and police targeting individuals who hold less political power --- whether those individuals are out-of-state motorists or members of local marginalized communities (\protect\hyperlink{ref-Makowsky2009}{Makowsky and Stratmann 2009}).
@@
 We expect that Black voters' political behavior in response to police ticketing will be distinct from the political behavior of white voters.
+
+\hypertarget{fines-perceptions-of-government-and-voting}{%
+\subsection*{Fines, perceptions of government, and voting}\label{fines-perceptions-of-government-and-voting}}
+\addcontentsline{toc}{subsection}{Fines, perceptions of government, and voting}
+
+The explosion of the reach of the criminal legal system in recent years --- both in terms of fees and fines collection, overzealous prosecution, and mass incarceration --- have had major ramifications on how Americans understand their identities and citizens and their relationship to their government.
+This is doubly true for Black Americans.
+As discussed above, this is not new: the ``hidden curriculum'' of the criminal legal system has long been a site of political socialization in the United States.
+In recent years, research has helped us make sense of the democratic ramifications of this.Traffic stops affect far more Americans than arrests and incarceration do: in 2018, more than 24 million people experienced police contact in the context of a traffic stop, whereas about 5.17 million people are disenfranchised as a result of a felony conviction (\protect\hyperlink{ref-Harrell2020}{Harrell and Davis 2020}; \protect\hyperlink{ref-Uggen2020}{Uggen et al.
+2020}).
+Sances and You (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}) explicitly suggested that ``fines may make descriptive representation less likely by depressing minority turnout,'' and called for further research regarding voter turnout and the imposition of fines.
+Our analysis picks up where they left off.
+
+These political barriers also disproportionately affect Black people.
+In Alabama, for example, Black people with felony convictions applying to have their voting rights restored were 26 percentage points more likely to have their application denied over outstanding fines and fees (\protect\hyperlink{ref-Meredith2017}{Meredith and Morse 2017}).
+
+Although the majority of voters in our analysis do not have felony convictions,
 
@@
 In other words, there's strong evidence suggesting both racist targeting of tickets and potential publicity to catalyze distinct Black voter responses to the abusive behavior during the same time frame as our national analysis.
-Ticketing has also been expressly politicized in Tampa: Jane Castor, who was elected mayor in 2019, was Tampa's police chief until 2015 and publicly defended her department's disproportionate ticketing of Black bicyclists before retracting her defense during her mayoral campaign {[}CITE{]}.
-Her opponent, banker and philanthropist David Straz, campaigned against red-light cameras and focused his outreach in Tampa's Black communities.
+Ticketing has also been expressly politicized in Tampa: Jane Castor, who was elected mayor in 2019, was Tampa's police chief until 2015 and publicly defended her department's disproportionate ticketing of Black bicyclists before retracting her defense ahead of her mayoral campaign (\protect\hyperlink{ref-Carlton2018}{Carlton 2018}).
+Her opponent, banker and philanthropist David Straz, campaigned against red-light cameras and focused his outreach in Tampa's Black communities (\protect\hyperlink{ref-Frago2019}{Frago 2019}).
 
-Perhaps more prosaically, Hillsborough County also makes a unique set of data publicly available.
+Hillsborough County also makes a unique set of data publicly available.
 The county clerk makes information available about every traffic stop in the county going back to 2003.
@@
 
+\begin{singlespace}
+\input{"../temp/coarser_reg_clean.tex"}
+\end{singlespace}
+
 The coefficient on \emph{Treated × 2018} indicates that non-Black turnout dropped by about 0.5 percentage points in municipalities where fees and fines collections increased relative to other municipalities.
@@
 \begin{singlespace}
-\input{"../temp/coarser_reg_clean.tex"}
+\begin{table}[H]
+
+\caption{\label{tab:baltab-chunk}\label{tab:balance} Balance Table}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{lllll}
+\toprule
+Variable & Treated & All Untreated & Actual Controls & Mean Improvement\\
+\midrule
+\% White & 49.1\% & 62.3\% & 49.2\% & 99.60\%\\
+\% Black & 22.9\% & 12.7\% & 22.9\% & 99.69\%\\
+\% Latino & 18.9\% & 16.3\% & 18.8\% & 99.23\%\\
+\% Asian & 2.2\% & 2.7\% & 2.2\% & 99.82\%\\
+\% Male & 51.1\% & 43.1\% & 51.2\% & 99.21\%\\
+\% Democrat & 42.0\% & 37.6\% & 41.8\% & 97.38\%\\
+\% Republican & 24.5\% & 31.4\% & 24.7\% & 97.83\%\\
+Age & 43.58 & 51.88 & 43.53 & 99.47\%\\
+Registration Date & 2006-06-13 & 2004-08-08 & 2006-06-20 & 99.00\%\\
+Stops Prior to 2012 Election & 1.29 & 0.36 & 1.11 & 80.11\%\\
+Turnout in 2010 & 20.9\% & 27.2\% & 20.6\% & 94.96\%\\
+Turnout in 2012 & 46.9\% & 45.5\% & 46.8\% & 87.69\%\\
+Median Income & \$63,782 & \$67,952 & \$63,859 & 98.17\%\\
+\% with Some College & 74.5\% & 76.6\% & 74.7\% & 89.50\%\\
+Unemployment Rate & 6.5\% & 5.8\% & 6.4\% & 91.07\%\\
+\bottomrule
+\end{tabular}}
+\end{table}
 \end{singlespace}
-
-\hypertarget{individual-level-results-1}{%
-\subsection*{Individual-Level Results}\label{individual-level-results-1}}
-\addcontentsline{toc}{subsection}{Individual-Level Results}
-
-Thus far, we have shown that the turnout effects of fees and fines collection impact municipal-level turnout, and that the effects are different for Black and non-Black Americans.
-We argue that this relationship is causal: increased fees and fines collections means that more residents have direct interactions with the criminal legal system.
-Based on prior literature, we assume there are indirect effects as well, as more residents know a family or community member who has been ticketed.
-While the national analysis gives us great breadth and an increased understanding of how this plays out across the country, municipal-level data leaves us unable to directly observe the causal mechanisms at play.
-
-To directly observe the effect of being ticketed on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
-As discussed above, we match (\protect\hyperlink{ref-Sekhon2011}{Sekhon 2011}) individuals who were stopped and assessed a fine between the 2012 and 2018 elections to individuals who were not stopped during this time period.\footnote{Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
-The full sample is used in the actual matching process.} Matching is done with replacement and ties are not broken, meaning some treated voters may have more than XX controls; the regression weights reflect this possibility.
-In Table \ref{tab:balance} we present the results of the matching algorithm.
-We manage to reduce between treated and control voters substantially along all observed characteristics with the exception of 2012 turnout.
-However, this is not likely a problem: the turnout of all potential and actual controls were both within 0.1 percentage points of the treatment group's turnout that year.
-
-INSERT BALANCE TABLE
 
@@
 
-Table \ref{tab:dind-table} formalizes Figures ref\{fig:did1\} and ref\{fig:did2\} into an ordinary least squares regression.
+Table \ref{tab:dind-table} formalizes Figures \ref{fig:did1} and \ref{fig:did2} into an ordinary least squares regression.
 Models 1 and 2 present the causal estimates of being stopped at any point in the two years prior to an election; Models 3 and 4 re-estimate the effect of being stopped within 90 days of an election.
 Models 1 and 3 show our overall causal effect, while Models 2 and 4 allow for the possibility that a ticket differentially mobilizes Black voters.
-The coefficients of note are \emph{Treated X Post Treatment} and \emph{Treated X Post Treatment X Black}.
-In models 1 and 3, \emph{Treated X Post Treatment} measures the overall treatment effect, and in models 2 and 4 it measures the treatment effect for non-Black voters.
-\emph{Treated X Post Treatment X Black} measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
+The coefficients of note are \emph{Treated × Post Treatment} and \emph{Treated × Post Treatment × Black}.
+In models 1 and 3, \emph{Treated × Post Treatment} measures the overall treatment effect, and in models 2 and 4 it measures the treatment effect for non-Black voters.
+\emph{Treated × Post Treatment × Black} measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
 
@@
 
-\newpage
+Model 3 indicates that a ticket is neither mobilizing nor demobilizing --- the coefficient is small and nonsignificant (\emph{p} = 0.34) but that tickets do mobilize Black voters.
+Receiving a ticket increases the average turnout for Black voters in the first two elections by about 1.1 percentage points.
+Model 4 shows that ticketing shortly before an election increases the turnout of non-Black voters by about 0.9 percentage points, and there is no statistically significantly different effect for Black voters.
+However, Figure \ref{fig:did2} visually indicates that the effect might be larger for Black voters, and the coefficient on \emph{Treated × Post Treatment × Black} is large (as is its standard error).
+These two facts taken together indicate that our inability to detect a differentially mobilizing effect for Black voters stopped shortly before an election may have more to do with issues of statistical power than an additional effect that is really equal to zero.
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
+{[}Tampa - local figure/table{]}
+
+{[}Tampa local analysis{]}
+
+\hypertarget{discussion}{%
+\subsubsection*{Discussion}\label{discussion}}
+\addcontentsline{toc}{subsubsection}{Discussion}
+
+{[}Our results provide support for Walker's theory of low-level police contact mobilizing nonwhite political participation.
+
+the role of fines and fees in the context of felony disenfranchisement has recently taken on greater political significance.
+After Floridians voted to restore voting rights to individuals with felony convictions in 2018, Florida Republicans passed legislation requiring these individuals to pay off the fines and fees associated with their original sentence.
+Because Florida does not maintain good records on who owes how much, this has proved to be a major hurdle for potential voters.
+
+{[}Laniyonu{]} - {[}he writes that block groups with higher Black pop and higher SQF density voted at higher rates for Thompson, the candidate who pledged not to implement SQF reform, but who was Black.
+The descriptive representation from Sances2017 kind of covers for this, tactically speaking - electing Black politicians should reduce fines and fees abuses.
+But in Tampa, the current mayor, Jane Castor, was the police chief until 2015 --- which overlaps with the treatment period in our analysis.
+One voter told the Tampa Bay Times that he voted against Castor as ``payback'' for the racist ticketing practices she oversaw, and the article notes that her opponent won five majority-Black precincts (\protect\hyperlink{ref-Frago2019}{Frago 2019}).
+In 2015, Castor even released a statement as police chief supporting the racist ticketing, insisting that ``Many individuals receiving bike citations are involved in criminal activity.''
+
+{[}Why do we think Black voters are mobilized? ``Linked fate,'' history, contemporary practices, Black Lives Matter.{]}
+
+{[}Limitations of research.{]} {[}We don't look at people who aren't registered to vote in 2018, so there could be some proportion of ticketed Black motorists who are now less likely to register to vote in the first place, for example.
+In other words our mobilization effect size only applies to people who were registered to vote.
+At the same time, perhaps people who weren't registered were equally likely to be deterred by something else.{]}
+
+{[}Because we only look at Tampa, we don't have a good idea of whether the revenue reliance trends interact with the experience of ticketing.
+Is ticketing a particularly alienating-mobilizing phenomenon in cities that are palpably dialing up their revenue collection efforts?
+Future research could test this hypothesis in cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.{]}
+
+{[}Unlike previous studies using survey data, we are unable to tell whether individuals in Tampa have non-ticketing criminal legal exposure.
+Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.{]}
+
+{[}Relevance for other scholars. Future research agenda.{]}
 
@@
 
+\leavevmode\hypertarget{ref-Carlton2018}{}%
+Carlton, Sue.
+2018.
+{``Carlton: {Jane Castor} Now Says Biking-While-Black Tickets Were Wrong.''} \emph{Tampa Bay Times}, April 12, 2018.
+\url{https://www.tampabay.com/news/politics/local/Carlton-Jane-Castor-now-says-biking-while-black-tickets-were-wrong_167233952/}.
+
 \leavevmode\hypertarget{ref-CarpenterII2019}{}%
@@
 
+\leavevmode\hypertarget{ref-Frago2019}{}%
+Frago, Charlie.
+2019.
+{``Tampa Police Have {`Evolved'} on Biking While Black, Chief Says.''} \emph{Tampa Bay Times}, October 24, 2019.
+\url{https://www.tampabay.com/news/tampa/2019/10/24/tampa-police-have-evolved-on-biking-while-black-chief-says/}.
+
 \leavevmode\hypertarget{ref-Friedman2020}{}%
@@
 \url{https://escholarship.org/uc/item/31r669wf}.
+
+\leavevmode\hypertarget{ref-Gilmore2007}{}%
+Gilmore, Ruth Wilson. 2007. \emph{Golden {Gulag}: {Prisons}, {Surplus}, {Crisis}, and {Opposition} in {Globalizing California}}. {University of California Press}.
 
@@
 
+\leavevmode\hypertarget{ref-Harrell2020}{}%
+Harrell, Erika, and Elizabeth Davis.
+2020.
+{``Contacts {Between Police} and the {Public}, 2018 - {Statistical Tables}.''} {Bureau of Justice Statistics}.
+\url{https://www.bjs.gov/index.cfm?ty=pbdetail\&iid=7167}.
+
 \leavevmode\hypertarget{ref-Harris2010}{}%
@@
 {``Monetary {Sanctions} in the {Criminal Justice System}.''}
+
+\leavevmode\hypertarget{ref-Hinton2017}{}%
+Hinton, Elizabeth. 2017. \emph{From the {War} on {Poverty} to the {War} on {Crime}: {The Making} of {Mass Incarceration} in {America}}. {Harvard University Press}.
 
@@
 
+\leavevmode\hypertarget{ref-Martin2017}{}%
+Martin, Isaac William, and Kevin Beck.
+2017.
+{``Property {Tax Limitation} and {Racial Inequality} in {Effective Tax Rates}.''} \emph{Critical Sociology} 43 (2): 221--36.
+\url{https://doi.org/10.1177/0896920515607073}.
+
 \leavevmode\hypertarget{ref-Meredith2014}{}%
@@
 
+\leavevmode\hypertarget{ref-Pierson2020}{}%
+Pierson, Emma, Camelia Simoiu, Jan Overgoor, Sam Corbett-Davies, Daniel Jenson, Amy Shoemaker, Vignesh Ramachandran, et al.
+2020.
+{``A Large-Scale Analysis of Racial Disparities in Police Stops Across the {United States}.''} \emph{Nature Human Behaviour} 4 (7, 7): 736--45.
+\url{https://doi.org/10.1038/s41562-020-0858-1}.
+
 \leavevmode\hypertarget{ref-Remster2018}{}%
@@
 \url{https://doi.org/10.1017/S1742058X18000206}.
+
+\leavevmode\hypertarget{ref-Robinson2000}{}%
+Robinson, Cedric J. 2000. \emph{Black {Marxism}: The {Making} of the {Black Radical Tradition}}. {University of North Carolina Press}. \url{https://uncpress.org/book/9780807848296/black-marxism/}.
 

### 2021-03-17 code/hills/03_match.R
change to left join to make sure nothing is being dropped

@@ -224,12 +224,12 @@ pot_con <- left_join(pot_con, periods) %>%
   mutate(black = ifelse(black, "Black Voters", "Non-Black Voters"),
          treated = "All Controls")
 
-matches <- inner_join(matches,
+matches <- left_join(matches,
                      hills_pre_match %>%
                        select(-GEOID, -fd, -max_amount),
                      by = c("voter" = "voter_id"))
 
-matches <- inner_join(matches,
+matches <- left_join(matches,
                      hills_pre_match %>%
                        select(voter_id, max_amount, fd, black_t = black),
                      by = c("group" = "voter_id")) %>% 
@@ -305,7 +305,7 @@ p2 <- ggplot(data = ll) +
        shape = "Treatment Group",
        caption = "Treatment occurs inside of yellow band.") +
   coord_cartesian(ylim = c(0.05, 0.75))
-
+p2
 saveRDS(p2, "temp/stopped_any_time.rds")
 ############### overall
 matches$first <- matches$period == 0.5

### 2021-03-17 markdown/draft_paper.Rmd
drafting

@@
 Despite this burgeoning literature, no research has directly investigated how ticketing for low-level offenses affects political participation.
-Using data from the Census of Governments and the national voter file, we conduct the first quasi-experimental analysis of the causal effect of fines and fees practices on American voting behavior at the city level.
-Additionally, we exploit individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019.
-We find that municipal fines and fees practices mobilize Black voters.
-Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 3.3 percentage point decrease in 2018 federal turnout, and a 1.8 percentage point decrease in the Black-white turnout gap.
-In Tampa, Florida, we estimate that Black voters who were ticketed in the 90-day period preceding a federal election were 3 percentage points more likely to turn out in federal elections.
+Using data from the Census of Governments and the national voter file, we test the causal effect of fines and fees practices on American voting behavior at the city level.
+Additionally, we exploit individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019 to determine whether getting a ticket impacts political participation.
+Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.6 percentage point decrease in nonBlack turnout but was not associated with Black turnout.
+In Tampa, Florida, we estimate being ticketed increases a nonBlack individual’s likelihood of voting by 3.7 percentage points, and that the effect is larger for Black voters.
 
@@
 Although some work has leveraged survey data and qualitative approaches to interrogate lower-level police interactions --- such as ticketing --- our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
-We begin by joining fees and fines data from XX municipalities around the country in 2012 and 2017 with a novel data set estimating racial turnout for each municipality in the country.
-We find that higher fees and fines collections are associated with lower turnout for white Americans, but higher turnout for Black Americans --- and that this relationship is likely causal.
+We begin by joining fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for each municipality in the country.
+While we find that increased fees and fines likely cause lower turnout among non-Black Americans, we find no effect of fees and fines on Black turnout.
 
@@
 By matching individuals who were ticketed to other, similar voters who were not ticketed and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout.
-Using self-reported race from the Florida registered voter file, we identify a modest, negative effect for non-Black voters, and a modest positive effect for Black voters.
-These individual-level analyses corroborate our municipal-level analyses from around the country.
+Using self-reported race from the Florida registered voter file, we identify large, *positive* treatment effects for all voters --- effects that were especially large for Black voters..
 
-We demonstrate that police ticketing practices --- the most widespread form of police contact in America --- influence the political behavior of Americans, with distinct effects for white and Black voters.
-This finding extends and supports Hannah Walker’s theory of criminal legal contact mobilizing nonwhite political participation [@Walker2020; @Walker2014].
-On an individual level, we also find that Black voters who were ticketed turn out at higher rates in subsequent elections.
+We demonstrate that police ticketing practices --- the most widespread form of police contact in America --- influence the political behavior of Americans, with distinct effects for Black and non-Black voters.
+This finding supports and extends Hannah Walker’s theory of criminal legal contact is mobilizing / less demobilizing for nonwhite political participation [@Walker2020; @Walker2014].
+On an individual level, we also find that voters who were ticketed turn out at higher rates in subsequent elections, and that this effect was especially large for Black individuals.
 This finding complicates Vesla Weaver and Amy Lerman’s theory of low-level criminal legal contact discouraging political participation [@Weaver2010].
@@
 states passed laws denying voting rights to people who were convicted of felonies.
-In their analysis of how racial threat catalyzes felon disenfranchisement, Behrens, Uggen, and Manza found that increases in a state’s nonwhite prison population drastically increase the likelihood of legislation permanently disenfranchising people convicted of felonies [@Behrens2003].
+In their analysis of how racial threat catalyzes felon disenfranchisement, @Behrens2003 found that increases in a state’s nonwhite prison population drastically increase the likelihood of legislation permanently disenfranchising people convicted of felonies.
+As @Shofner1963 notes, this has often been tied explicitly to the increased presence of Black Americans in the electorate.
 
@@
 This practice inflates the voting power of rural and white voters while diminishing the power of urban, Black, and Latino voters [@Remster2018].
+
+Tthe role of fines and fees in the context of felony disenfranchisement has recently garnered national attentiontaken on greater political significance.
+After Floridians passed Amendment 4 voted to restore voting rights to individuals with felony convictions in 2018, Florida Republicans passed legislation requiring these individuals to pay off the fines and fees associated with their original sentence.
+Because Florida does not maintain good records on who owes how much, this has proved to be a major hurdle for potential voters.
+Despite a dissenting judge arguing that ““[h]ad Florida wanted to create a system to obstruct, impede, and impair the ability of felons to vote under Amendment 4, it could not have come up with a better one,” an en bank ruling by the U.S.
+Court of Appeals for the 11th Circuit upheld this legislation.^[Jones et al.
+v.
+DeSantis et al., 4:19cv300-RH/MJF (United States Court of Appeals for the Eleventh Circuit).]
 
@@
 In addition to influencing perceptions of government, recent scholarship indicates that criminalization influences political behavior.
+The “hidden curriculum” of the criminal legal system [@Justice2014; @Meares2017] teaches individuals about their position within the political system, and the criminal legal system consequently serves as a primary site of political socialization for convicted individuals and their families [e.g.
+@Lee2014].
 Several studies indicate that potential voters are discouraged from voting due to personal or proximal contact with the criminal legal system, and this chilling effect is most salient for what we consider “high-intensity” criminal legal involvement, such as being convicted of a crime or being incarcerated.
 
-Using existing national survey data and new extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) [@Weaver2010].
-Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective racial political consciousness, or a “linked fate” of all Black Americans.
-Their interview data lead them to conclude that “a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing” --- and interview respondents who had been incarcerated reported that withdrawal from public institutions constituted a form of self-preservation [@Lerman2014].
+Using existing national survey data and extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) [@Weaver2010].
+Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a “linked fate” where group members believe that group-level phenomena affect all group members [@Cox2019] of all Black Americans.
+Their interview data lead them to conclude that “a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing” --- and interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation [@Lerman2014].
 
@@
 Brayne’s analysis demonstrates how lower-intensity criminal legal contact can be theorized as a mechanism for discouraging Americans’ participation in public institutions.
+Similarly, @Remster2018a finds that men who return home from prison are more likely to avoid contact with their childrens’ schools.
 
@@
 
-Proximal exposure to criminalization --- “having a loved one who is a custodial citizen without yourself having had contact” [@Walker2017] --- also influences Americans’ perceptions of government and political behavior, and the emerging literature has produced mixed findings.
-Using survey and ethnographic interview data, @Lee2014 found that adult children of incarcerated parents are less likely to vote, report lower trust in government, and are less likely to engage in other prosocial behaviors like community service [@Lee2014].
-@Sugie2015 used survey data to show that partners of formerly incarcerated men are less likely to vote, but not less likely to participate in religious or civic institutions [@Sugie2015].
+Proximal exposure to criminalization --- “having a loved one who is a custodial citizen without yourself having had contact” [@Walker2017] --- also influences Americans’ perceptions of government and political behavior, and the emerging literature has produced mixed findings of its effect on civic engagement.
+Using survey and ethnographic interview data, @Lee2014 found that adult children of incarcerated parents are less likely to vote, report lower trust in government, and are less likely to engage in other prosocial behaviors like community service.
+@Sugie2015 used survey data to show that partners of formerly incarcerated men are less likely to vote, but not less likely to participate in religious or civic institutions.
+
+Hannah Walker’s research specifically tests differences between the effects of proximal and personal criminal legal contact on political behavior, and her findings underscore how a “linked fate” political analysis could catalyze distinct political behavior among Black voters [@Walker2014].
+Using data from a 2012 survey of Washington state residents, she found that as the degree of an individual’s proximity to a criminalized person increases, so does their likelihood of participating in political activities (such as voting, signing a petition, volunteering, donating to politicians, etc.).
+Importantly, Walker found that nonwhite people who had experienced *either* proximal or personal contact *at any level of intensity*, including being stopped and questioned by police, were politically mobilized --- and the same held true for whites, but with a much smaller effect size.
+Walker theorizes that this finding suggests that nonwhite people view criminalization “as a form of systemic political threat,” an analysis comparable to “linked fate.” Notably, Walker’s survey questions excluded “minor traffic stops,” the primary focus of this paper.
+
+Ariel White leveraged administrative court records from Harris County, Texas, to identify voters who lived within individuals who were charged with a misdemeanor offense and arrested, convicted, or jailed [@White2019].
+She found that living with someone who was charged but not convicted in the 30 day period preceding an election increased voter turnout by 3 percentage points, whereas “convicted but not jailed” decreased turnout by 6 percentage points and “convicted and jailed” decreased turnout by 12 percentage points.
+This provides further support for the theory that increasing intensity of criminalization could change the direction of the effect of criminalization on political behavior --- and, in fact, that lower-level contact can mobilize even as higher-level contact demobilizes.
 
@@
 
-White also conducted a proximal contact analysis using Harris County administrative data regarding households wherein one member was charged with a misdemeanor offense and arrested, convicted, or jailed [@White2019].
-She found that a household member who was charged but not convicted in the 30 day period preceding an election increased voter turnout by 3 percentage points, whereas “convicted but not jailed” decreased turnout by 6 percentage points and “convicted and jailed” decreased turnout by 12 percentage points.
-This provides further support for the theory that increasing intensity of criminalization could change the direction of the effect of criminalization on political behavior.
-
 This chilling effect does not appear uniformly across all studies.
@@
 To the extent that descriptive representation mitigates exploitative fines and fees practices [@Sances2017], this could constitute an effective political strategy.
-
-Hannah Walker’s research specifically tests differences between the effects of proximal and personal criminal legal contact on political behavior, and her findings underscore how a “linked fate” political analysis could catalyze distinct political behavior among Black voters [@Walker2014].
-Using data from a 2012 survey of Washington state residents, she found that as the degree of an individual’s proximity to a criminalized person increases, so does their likelihood of participating in political activities (such as voting, signing a petition, volunteering, donating to politicians, etc.).
-Importantly, Walker found that nonwhite people who had experienced *either* proximal or personal contact *at any level of intensity*, including being stopped and questioned by police, were politically mobilized --- and the same held true for whites, but with a much smaller effect size.
-Walker theorizes that this finding suggests that nonwhite people view criminalization “as a form of systemic political threat,” an analysis comparable to “linked fate.” Notably, Walker’s survey questions excluded “minor traffic stops,” the primary focus of this paper.
 
@@
 
-Researchers have used administrative data linked with registered voter files to explore the effects of stops, arrests, conviction, and incarceration on political behavior.
-We can say, with some reservations, that such contact likely reduces participation at the ballot box.
-To date, however, no work has leveraged administrative data to test the effect of police ticketing routine police stops on political behavior, and relatively little work has investigated the effects of police stops.
-Some qualitative research [@Weaver2010] indicates that these low-level stops are demobilizing; Laniyou, on the other hand, finds that neighborhoods with many police stops can turnout at higher rates, and survey data analyzed by Walker similarly shows that police stops can mobilize.
-By identifying all individuals subjected to a traffic stop in Hillsborough County, this project pushes us forward along the lines of other work using administrative data.
-
 Most of the aforementioned studies were conducted using data collected before the rise of the Black Lives Matter movement in 2013, which could be construed as a significant development for the political socialization of Black Americans with respect to policing and incarceration.
@@
 It’s possible that any potentially mobilizing effects of criminal legal contact became stronger in the 2010s --- in other words, Black Lives Matter could have facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis.
-That said, Laniyonu did demonstrate mobilization in Black neighborhoods before the beginning of the Black Lives Matter movement.
+That said, @Laniyonu2019 did demonstrate mobilization in Black neighborhoods before the beginning of the Black Lives Matter movement.
 
@@
 In the 20th century, residential segregation simultaneously fueled the racial wealth gap and ensured that criminalization was both spatially and racially concentrated [@Rothstein2017; @Hinton2021].
-At the level of federal policy, racial threat and whites’ attribution of criminality to Blackness [@Muhammad2010] prompted a shift “from the War on Poverty to the War on Crime” wherein Black communities’ demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration [@Hinton2017; @Vargas2017].
+At the level of federal policy, racial threat and whites’ attribution of criminality to Blackness [@Muhammad2010] prompted a shift “from the War on Poverty to the War on Crime” wherein Black communities’ demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration [@Hinton2017; @Vargas2017a].
 Ruth Wilson Gilmore explains how mid to late 20th-century whites “demanded that the state become leaner and meaner, except when directed to do otherwise” --- in other words, Keynesian welfare guarantees were undermined by the racist myth of “welfare queens” and supplanted by expanded police power [@Gilmore2007, page 53].
@@
 With this history in mind, we argue that Black Americans can situate exploitative ticketing practices in a longer historical legacy of collective disparate treatment and violence at the hands of the state, which may facilitate a stronger collective political analysis when police ticketing practices become more extreme.
-We expect that Black voters’ political behavior in response to police ticketing will be distinct from the political behavior of white voters.
-
-## Fines, perceptions of government, and voting {-}
-
-The explosion of the reach of the criminal legal system in recent years --- both in terms of fees and fines collection, overzealous prosecution, and mass incarceration --- have had major ramifications on how Americans understand their identities and citizens and their relationship to their government.
-This is doubly true for Black Americans.
-As discussed above, this is not new: the “hidden curriculum” of the criminal legal system has long been a site of political socialization in the United States.
-In recent years, research has helped us make sense of the democratic ramifications of this.Traffic stops affect far more Americans than arrests and incarceration do: in 2018, more than 24 million people experienced police contact in the context of a traffic stop, whereas about 5.17 million people are disenfranchised as a result of a felony conviction [@Harrell2020; @Uggen2020].
-Sances and You [@Sances2017] explicitly suggested that “fines may make descriptive representation less likely by depressing minority turnout,” and called for further research regarding voter turnout and the imposition of fines.
-Our analysis picks up where they left off.
-
-These political barriers also disproportionately affect Black people.
-In Alabama, for example, Black people with felony convictions applying to have their voting rights restored were 26 percentage points more likely to have their application denied over outstanding fines and fees [@Meredith2017].
-
-Although the majority of voters in our analysis do not have felony convictions,
+@Walker2020 makes clear that, when Black Americans locate their contact with the criminal legal system in a narrative of racial injustice, they can be mobilized to vote.
+The historical use of fees and fines make this sort of police contact especially likely to evoke such narratives.
+Accordingly, we expect that Black voters’ political behavior in response to police ticketing will be distinct from the political behavior of white voters.
 
@@
 The COG data only include local revenues, which means the share of fines revenue corresponds more directly to local police practices.
+Following the guidance of @Sances2017, we retain only municipalities with police and/or court systems, and only municipalities with populations of at least 2,500.
 
@@
 By using the racial estimates provided by L2, we can estimate the number of ballots cast by voters of each race in each city.
-Although each voters’ race is modeled based on L2’s algorithms --- not self-reported --- it is possibly incorrect for some voters.
+Although each voters’ race is modeled based on L2’s algorithms --- and is not self-reported --- it is possibly incorrect for some voters.
 We assume this does not present a problem when records are aggregated to the municipal level.
@@
 These estimates are available for individual racial groups.
+Because our turnout numerator and denominators come from different sources there is slight measurement error: our estimate indicates, for instance, that roughly 1 percent of municipalities had Black turnout above 100 percent.
+Where more votes were cast than the Census estimate for CVAP, we recode turnout as 100 percent.
+Our results do not change if we instead simply remove these municipalities.
 
@@
 We retain only municipalities whose data is reported to the COG in both 2012 and 2017.
+
 We then run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
@@
 The timing of the COG and midterm elections mean that our analytical strategy is conservative.
-If municipalities shift their fees and fines collections dramatically over the 2013 - 2017 period, this shift may influence their 2014 turnout.
+If municipalities shift their fees and fines collections dramatically over the 2013 -- 2017 period, this shift may influence their 2014 turnout.
 However, we assume that turnout in 2014 will still be influenced by the policing practices of the 2008 -- 2012 period, while 2018 turnout will be largely influenced by the practices of the 2013 -- 2017 period.
@@
 
-*Hypothesis 2: The effect of the city-level relationship between fines and voter turnout is distinct for Black voters --- i.e.
-more pronounced than or in the opposite direction of the effect of fines on turnout for white voters.*
+*Hypothesis 2: The effect of the city-level relationship between fines and voter turnout is less demobilizing or more mobilizing for Black voters, given the historical and explicit racial injustice narratives used to explain these practices..*
 
@@
 Our national test of the relationship between municipal fees and fines collection and turnout offers novel insight into the political socialization of low-level police contact.
-It cannot, however, directly observe the causal mechanism we argue is at play: namely, that personal or proximal contact with the criminal legal system influences turnout.
-Our national analysis suffers from what is called the ecological fallacy: it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
+It cannot, however, directly observe the causal mechanism we argue is at play: namely, that direct contact with the criminal legal system influences turnout.
+Our national analysis suffers from what is called the “ecological fallacy:” it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
 
@@
 Department of Justice investigation and report, requested by Tampa’s mayor and police chief.
-In other words, there’s strong evidence suggesting both racist targeting of tickets and potential publicity to catalyze distinct Black voter responses to the abusive behavior during the same time frame as our national analysis.
+In other words, there is strong evidence suggesting both racist targeting of tickets and potential publicity to catalyze distinct Black voter responses to the abusive behavior during the same time frame as our national analysis.
 Ticketing has also been expressly politicized in Tampa: Jane Castor, who was elected mayor in 2019, was Tampa’s police chief until 2015 and publicly defended her department’s disproportionate ticketing of Black bicyclists before retracting her defense ahead of her mayoral campaign [@Carlton2018].
@@
 
-To test the effect of ticketing on individual-level turnout, we match the first and last names and dates of birth against the Hillsborough County registered voter file from L2.
+To test the effect of ticketing on individual-level turnout, we match the first and last names and dates of birth against the Hillsborough County registered voter file.
+Here, rather than rely on a snapshot from L2, we use the raw voter file directly from the state.
+Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status [see @Nyhan2017].
+Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.
+We thus observe virtually all individuals who were registered  to vote at any time during our period of study.
+Unique voter identification numbers allow us to avoid double-counting voters who are registered in multiple snapshots.
+We each voter’s earliest record, and geocode voters to their home census block groups.
+
 To improve the quality of the match between the two datasets, we remove all punctuation from all names and convert all names to lower-case.
@@
 
-By matching these records, we identify all voters who were ticketed between the 2012 and 2018 general elections.
+By matching the police stop and voter records, we identify all voters who were ticketed between the 2012 and 2018 general elections.
 Voters are considered “treated” for every general election following their first ticket.
-This means that a voter who was ticketed in early 2014 was considered treated”= for the 2014, 2016, and 2018 elections.
+This means that a voter who was ticketed in early 2014 was considered treated for the 2014, 2016, and 2018 elections.
 A voter treated in 2017, on the other hand, is only considered treated in the 2018 election.
 
-These voters are then matched to one control voter using what methodologists call a “genetic” process [@Sekhon2011].
+These voters are then matched to two control voters using what methodologists call a “genetic” process [@Sekhon2011].
 The pool of potential control voters are the individuals who are never stopped during the 2012 -- 2018 period, regardless of whether they paid a fine.
@@
 
+We then run ordinary least squares difference-in-difference regressions to test the following hypotheses.
+
 *Hypothesis 3: Among individuals who were ticketed (“treated”) in Tampa, their likelihood of turning out in a subsequent election roughly matches the racioethnic distribution apparent in the national city-level data.
@@
 
-Because Tampa holds off-year local elections, we are able to test whether mobilized voters target officials who are able to change local police practices.
+<!-- Because Tampa holds off-year local elections, we are able to test whether mobilized voters target officials who are able to change local police practices.
 @Laniyonu2019 gives us reason to believe that the effect should be stronger for local elections.
+-->
 
-*Hypothesis 4: Any potential mobilizing turnout effect in Tampa is stronger for local (mayoral) elections, since those elections directly affect police practices.*
+<!-- *Hypothesis 4: Any potential mobilizing turnout effect in Tampa is stronger for local (mayoral) elections, since those elections directly affect police practices.* -->
 
-That said, Laniyonu found that heavily policed, majority-Black New York City neighborhoods tended to vote for William Thompson, a Black candidate who opposed police reform --- which could suggest that Black voters prioritized descriptive representation over outward-facing policy messaging.
-In Tampa, however, both leading candidates were white, and Castor was the police chief during the city’s racist ticketing scandal.
-Thus, the racioethnic identity of the candidates in 2019 should not affect ticketed Black voters’ responses to candidates’ policy messaging in the same way.
+<!-- One novel feature of our analysis is that we are able to assess the political effects of both proximal and personal criminal legal contact during the same time frame.
+The COG data likely capture the voting behavior of people who were not personally ticketed, but know one or several people who were; and the Tampa data capture the voting behavior of people who were themselves ticketed.
+-->
 
-One novel feature of our analysis is that we are able to assess the political effects of both proximal and personal criminal legal contact during the same time frame.
-The COG data likely capture the voting behavior of people who were not personally ticketed, but know one or several people who were; and the Tampa data capture the voting behavior of people who were themselves ticketed.
-
-Additionally, our analysis eliminates measurement problems that potentially affected past research and accounts for the temporal features of the relationship between criminal legal contact and voting.
-Several prior studies regarding criminalization and political behavior [@Walker2014; @Weaver2010] involve surveys where the measure of police contact is self-reported intensity of contact --- “have you ever been stopped by police?
-Arrested?
-Incarcerated?” Respondents were then asked to indicate how likely they might be to vote.
-Our analysis allows us to assess the actual voting behavior of people who we verify were ticketed and gauge the strength of the treatment effect over time by comparing each individual’s participation in subsequent elections.
-It is also advantageous that we are able to capture actual voting behavior within a few months or weeks of treatment application --- only Walker and White conduct individual-level analyses consistent with voter file data, and Laniyonu conducts a neighborhood-level analysis using voter file data.
-This feature of our data also helps us avoid measurement issues with survey instruments used in prior studies --- for example, Lerman and Weaver are careful to note that people who have been arrested or incarcerated sometimes misreport their political behavior in survey research.
+The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures participation.
+Past work looking at the individual-level effects of low-level contact has relied entirely on survey or qualitative data [e.g.
+@Walker2014; @Weaver2010].
+Their in-depth research allows for the testing of specific psychological mechanisms and personal interpretations of criminal legal contact, but does not allow us to generalize more broadly.
+As Weaver and Lerman [-@Weaver2010, page 821] note, it may also introduce measurement bias.
 Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to police ticketing.
+The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of the 232,568 individuals ticketed over the 6 year period --- a far larger pool than even the most robust surveys.
 
@@
 The coefficient on *Treated × 2018* indicates that non-Black turnout dropped by about 0.5 percentage points in municipalities where fees and fines collections increased relative to other municipalities.
-While this coefficient is also negative for Black voters, it is not statistically significantly different from 0.
+While this coefficient is slightly positive for Black voters, it is not statistically significantly different from 0.
 In other words, both Tables \ref{tab:twfe} and \ref{tab:coarser} indicate that increased fees and fines collections decrease non-Black turnout but have no impact on Black turnout.
@@
 As discussed above, we match [@Sekhon2011] individuals who were stopped and assessed a fine between the 2012 and 2018 elections to individuals who were not stopped during this time period.^[Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
-The full sample is used in the actual matching process.]  Matching is done with replacement and ties are not broken, meaning some treated voters may have more than XX controls; the regression weights reflect this possibility.
+The full sample is used in the actual matching process.]  Matching is done with replacement and ties are not broken, meaning some treated voters may have more than 2 controls; the regression weights reflect this possibility.
 In Table \ref{tab:balance} we present the results of the matching algorithm.
@@
 
-[Our results provide support for Walker’s theory of low-level police contact mobilizing nonwhite political participation.
+Our results provide support for Walker’s theory of criminal legal contact mobilizing nonwhite political participation.
+Our individual-level analysis in Hillsborough County shows that being ticketed mobilizes voters, and mobilizes Black voters to a greater degree than non-Black voters---and our city-level analysis shows that while greater fines and fees reliance reduces white voter turnout, it has no effect on Black turnout.
 
-the role of fines and fees in the context of felony disenfranchisement has recently taken on greater political significance.
-After Floridians voted to restore voting rights to individuals with felony convictions in 2018, Florida Republicans passed legislation requiring these individuals to pay off the fines and fees associated with their original sentence.
-Because Florida does not maintain good records on who owes how much, this has proved to be a major hurdle for potential voters.
+[Particularly following the rise of the Black Lives Matter movement in 2013, our findings are consistent with the theory that Black voters interpret exploitative police practices as a threat to the wellbeing of all Black Americans.]
+
+We were somewhat surprised by the differences that arose between our two sets of findings---our city-level analysis did not produce statistically significant results for Black voters.
+We think there are a few potential explanations for this mismatch.
+First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes are smaller or not statistically significant.
+Along a similar vein, it’s possible that the effect size for Black voters in the city-level analysis is affected by higher-intensity forms of criminal legal contact, such as arrest and incarceration.
+The bulk of existing literature suggests that incarceration discourages political participation, and it’s not unreasonable to assume that cities that ramp up ticketing of Black residents also ramp up arrest and incarceration of Black residents.
+If these phenomena coincide, that could explain why the city-level analysis produced no statistically significant effect for Black voters---the personally mobilizing effect of ticketing could be counterbalanced by the proximal chilling effect of incarceration, and because the city-level analysis is not as temporally sensitive, it’s more difficult to isolate the effect of ticketing.
+
+**Limitations**: Because our individual-level analysis is limited to Hillsborough County, we don’t have a good idea of whether the city-level revenue reliance trend interacts with the individual experience of being ticketed.
+Is ticketing more politically mobilizing in cities that are palpably dialing up their revenue collection efforts?
+Future research could test this hypothesis in cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.
+
+Additionally, in our analysis of Hillsborough County voters, we don’t look at people who weren’t registered to vote in 2018.
+This means that there could be some proportion of ticketed Black motorists who are now less likely to register to vote in the first place, for example.
+In other words the mobilization effect in our findings only applies to people who were registered to vote---we are unable to make claims about whether being ticketed makes an individual more likely to register to vote.
+
+**Future research**: Unlike previous studies using survey data, we are unable to tell whether individuals in Tampa have non-ticketing criminal legal exposure.
+Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.]
 
@@
 
-[Why do we think Black voters are mobilized? “Linked fate,” history, contemporary practices, Black Lives Matter.]
+\newpage
 
-[Limitations of research.] [We don’t look at people who aren’t registered to vote in 2018, so there could be some proportion of ticketed Black motorists who are now less likely to register to vote in the first place, for example.
-In other words our mobilization effect size only applies to people who were registered to vote.
-At the same time, perhaps people who weren’t registered were equally likely to be deterred by something else.]
-
-[Because we only look at Tampa, we don’t have a good idea of whether the revenue reliance trends interact with the experience of ticketing.
-Is ticketing a particularly alienating-mobilizing phenomenon in cities that are palpably dialing up their revenue collection efforts?
-Future research could test this hypothesis in cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.]
-
-[Unlike previous studies using survey data, we are unable to tell whether individuals in Tampa have non-ticketing criminal legal exposure.
-Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.]
-
-[Relevance for other scholars. Future research agenda.]
+# References {-}

### 2021-03-17 markdown/draft_paper.tex
drafting

@@
 \author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
-\date{March 16, 2021}
+\date{March 17, 2021}
 
@@
 Despite this burgeoning literature, no research has directly investigated how ticketing for low-level offenses affects political participation.
-Using data from the Census of Governments and the national voter file, we conduct the first quasi-experimental analysis of the causal effect of fines and fees practices on American voting behavior at the city level.
-Additionally, we exploit individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019.
-We find that municipal fines and fees practices mobilize Black voters.
-Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 3.3 percentage point decrease in 2018 federal turnout, and a 1.8 percentage point decrease in the Black-white turnout gap.
-In Tampa, Florida, we estimate that Black voters who were ticketed in the 90-day period preceding a federal election were 3 percentage points more likely to turn out in federal elections.
+Using data from the Census of Governments and the national voter file, we test the causal effect of fines and fees practices on American voting behavior at the city level.
+Additionally, we exploit individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019 to determine whether getting a ticket impacts political participation.
+Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.6 percentage point decrease in nonBlack turnout but was not associated with Black turnout.
+In Tampa, Florida, we estimate being ticketed increases a nonBlack individual's likelihood of voting by 3.7 percentage points, and that the effect is larger for Black voters.
 
@@
 By matching individuals who were ticketed to other, similar voters who were not ticketed and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout.
-Using self-reported race from the Florida registered voter file, we identify a modest, negative effect for non-Black voters, and a modest positive effect for Black voters.
-These individual-level analyses corroborate our municipal-level analyses from around the country.
-
-We demonstrate that police ticketing practices --- the most widespread form of police contact in America --- influence the political behavior of Americans, with distinct effects for white and Black voters.
-This finding extends and supports Hannah Walker's theory of criminal legal contact mobilizing nonwhite political participation (\protect\hyperlink{ref-Walker2020}{Walker 2020}, \protect\hyperlink{ref-Walker2014}{2014}).
-On an individual level, we also find that Black voters who were ticketed turn out at higher rates in subsequent elections.
+Using self-reported race from the Florida registered voter file, we identify large, \emph{positive} treatment effects for all voters --- effects that were especially large for Black voters..
+
+We demonstrate that police ticketing practices --- the most widespread form of police contact in America --- influence the political behavior of Americans, with distinct effects for Black and non-Black voters.
+This finding supports and extends Hannah Walker's theory of criminal legal contact is mobilizing / less demobilizing for nonwhite political participation (\protect\hyperlink{ref-Walker2020}{Walker 2020}, \protect\hyperlink{ref-Walker2014}{2014}).
+On an individual level, we also find that voters who were ticketed turn out at higher rates in subsequent elections, and that this effect was especially large for Black individuals.
 This finding complicates Vesla Weaver and Amy Lerman's theory of low-level criminal legal contact discouraging political participation (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
@@
 states passed laws denying voting rights to people who were convicted of felonies.
-In their analysis of how racial threat catalyzes felon disenfranchisement, Behrens, Uggen, and Manza found that increases in a state's nonwhite prison population drastically increase the likelihood of legislation permanently disenfranchising people convicted of felonies (\protect\hyperlink{ref-Behrens2003}{Behrens, Uggen, and Manza 2003}).
+In their analysis of how racial threat catalyzes felon disenfranchisement, \protect\hyperlink{ref-Behrens2003}{Behrens, Uggen, and Manza} (\protect\hyperlink{ref-Behrens2003}{2003}) found that increases in a state's nonwhite prison population drastically increase the likelihood of legislation permanently disenfranchising people convicted of felonies.
+As \protect\hyperlink{ref-Shofner1963}{Shofner} (\protect\hyperlink{ref-Shofner1963}{1963}) notes, this has often been tied explicitly to the increased presence of Black Americans in the electorate.
 
@@
 This practice inflates the voting power of rural and white voters while diminishing the power of urban, Black, and Latino voters (\protect\hyperlink{ref-Remster2018}{Remster and Kramer 2018/ed}).
+
+Tthe role of fines and fees in the context of felony disenfranchisement has recently garnered national attentiontaken on greater political significance.
+After Floridians passed Amendment 4 voted to restore voting rights to individuals with felony convictions in 2018, Florida Republicans passed legislation requiring these individuals to pay off the fines and fees associated with their original sentence.
+Because Florida does not maintain good records on who owes how much, this has proved to be a major hurdle for potential voters.
+Despite a dissenting judge arguing that ````{[}h{]}ad Florida wanted to create a system to obstruct, impede, and impair the ability of felons to vote under Amendment 4, it could not have come up with a better one,'' an en bank ruling by the U.S.
+Court of Appeals for the 11th Circuit upheld this legislation.\footnote{Jones et al.~v.
+DeSantis et al., 4:19cv300-RH/MJF (United States Court of Appeals for the Eleventh Circuit).}
 
@@
 In addition to influencing perceptions of government, recent scholarship indicates that criminalization influences political behavior.
+The ``hidden curriculum'' of the criminal legal system (\protect\hyperlink{ref-Justice2014}{Justice and Meares 2014}; \protect\hyperlink{ref-Meares2017}{Meares 2017}) teaches individuals about their position within the political system, and the criminal legal system consequently serves as a primary site of political socialization for convicted individuals and their families (e.g.
+\protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}).
 Several studies indicate that potential voters are discouraged from voting due to personal or proximal contact with the criminal legal system, and this chilling effect is most salient for what we consider ``high-intensity'' criminal legal involvement, such as being convicted of a crime or being incarcerated.
 
-Using existing national survey data and new extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
-Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective racial political consciousness, or a ``linked fate'' of all Black Americans.
-Their interview data lead them to conclude that ``a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing'' --- and interview respondents who had been incarcerated reported that withdrawal from public institutions constituted a form of self-preservation (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}).
+Using existing national survey data and extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
+Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a ``linked fate'' where group members believe that group-level phenomena affect all group members (\protect\hyperlink{ref-Cox2019}{Cox 2019}) of all Black Americans.
+Their interview data lead them to conclude that ``a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing'' --- and interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}).
 
@@
 Brayne's analysis demonstrates how lower-intensity criminal legal contact can be theorized as a mechanism for discouraging Americans' participation in public institutions.
+Similarly, \protect\hyperlink{ref-Remster2018a}{Remster and Kramer} (\protect\hyperlink{ref-Remster2018a}{2018}) finds that men who return home from prison are more likely to avoid contact with their childrens' schools.
 
@@
 
-Proximal exposure to criminalization --- ``having a loved one who is a custodial citizen without yourself having had contact'' (\protect\hyperlink{ref-Walker2017}{Walker and García-Castañon 2017}) --- also influences Americans' perceptions of government and political behavior, and the emerging literature has produced mixed findings.
-Using survey and ethnographic interview data, \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort} (\protect\hyperlink{ref-Lee2014}{2014}) found that adult children of incarcerated parents are less likely to vote, report lower trust in government, and are less likely to engage in other prosocial behaviors like community service (\protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}).
-\protect\hyperlink{ref-Sugie2015}{Sugie} (\protect\hyperlink{ref-Sugie2015}{2015}) used survey data to show that partners of formerly incarcerated men are less likely to vote, but not less likely to participate in religious or civic institutions (\protect\hyperlink{ref-Sugie2015}{Sugie 2015}).
+Proximal exposure to criminalization --- ``having a loved one who is a custodial citizen without yourself having had contact'' (\protect\hyperlink{ref-Walker2017}{Walker and García-Castañon 2017}) --- also influences Americans' perceptions of government and political behavior, and the emerging literature has produced mixed findings of its effect on civic engagement.
+Using survey and ethnographic interview data, \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort} (\protect\hyperlink{ref-Lee2014}{2014}) found that adult children of incarcerated parents are less likely to vote, report lower trust in government, and are less likely to engage in other prosocial behaviors like community service.
+\protect\hyperlink{ref-Sugie2015}{Sugie} (\protect\hyperlink{ref-Sugie2015}{2015}) used survey data to show that partners of formerly incarcerated men are less likely to vote, but not less likely to participate in religious or civic institutions.
+
+Hannah Walker's research specifically tests differences between the effects of proximal and personal criminal legal contact on political behavior, and her findings underscore how a ``linked fate'' political analysis could catalyze distinct political behavior among Black voters (\protect\hyperlink{ref-Walker2014}{Walker 2014}).
+Using data from a 2012 survey of Washington state residents, she found that as the degree of an individual's proximity to a criminalized person increases, so does their likelihood of participating in political activities (such as voting, signing a petition, volunteering, donating to politicians, etc.).
+Importantly, Walker found that nonwhite people who had experienced \emph{either} proximal or personal contact \emph{at any level of intensity}, including being stopped and questioned by police, were politically mobilized --- and the same held true for whites, but with a much smaller effect size.
+Walker theorizes that this finding suggests that nonwhite people view criminalization ``as a form of systemic political threat,'' an analysis comparable to ``linked fate.'' Notably, Walker's survey questions excluded ``minor traffic stops,'' the primary focus of this paper.
+
+Ariel White leveraged administrative court records from Harris County, Texas, to identify voters who lived within individuals who were charged with a misdemeanor offense and arrested, convicted, or jailed (\protect\hyperlink{ref-White2019}{White 2019}).
+She found that living with someone who was charged but not convicted in the 30 day period preceding an election increased voter turnout by 3 percentage points, whereas ``convicted but not jailed'' decreased turnout by 6 percentage points and ``convicted and jailed'' decreased turnout by 12 percentage points.
+This provides further support for the theory that increasing intensity of criminalization could change the direction of the effect of criminalization on political behavior --- and, in fact, that lower-level contact can mobilize even as higher-level contact demobilizes.
 
@@
 \protect\hyperlink{ref-Morris2020}{Morris} (\protect\hyperlink{ref-Morris2020}{2020}) similarly finds that neighborhoods with more active voters lost to felony disenfranchisement turned out at lower rates in the 2017 mayoral race in NYC, and that this effect was particularly pronounced in Black neighborhoods.
-
-White also conducted a proximal contact analysis using Harris County administrative data regarding households wherein one member was charged with a misdemeanor offense and arrested, convicted, or jailed (\protect\hyperlink{ref-White2019}{White 2019}).
-She found that a household member who was charged but not convicted in the 30 day period preceding an election increased voter turnout by 3 percentage points, whereas ``convicted but not jailed'' decreased turnout by 6 percentage points and ``convicted and jailed'' decreased turnout by 12 percentage points.
-This provides further support for the theory that increasing intensity of criminalization could change the direction of the effect of criminalization on political behavior.
 
@@
 To the extent that descriptive representation mitigates exploitative fines and fees practices (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}), this could constitute an effective political strategy.
-
-Hannah Walker's research specifically tests differences between the effects of proximal and personal criminal legal contact on political behavior, and her findings underscore how a ``linked fate'' political analysis could catalyze distinct political behavior among Black voters (\protect\hyperlink{ref-Walker2014}{Walker 2014}).
-Using data from a 2012 survey of Washington state residents, she found that as the degree of an individual's proximity to a criminalized person increases, so does their likelihood of participating in political activities (such as voting, signing a petition, volunteering, donating to politicians, etc.).
-Importantly, Walker found that nonwhite people who had experienced \emph{either} proximal or personal contact \emph{at any level of intensity}, including being stopped and questioned by police, were politically mobilized --- and the same held true for whites, but with a much smaller effect size.
-Walker theorizes that this finding suggests that nonwhite people view criminalization ``as a form of systemic political threat,'' an analysis comparable to ``linked fate.'' Notably, Walker's survey questions excluded ``minor traffic stops,'' the primary focus of this paper.
 
@@
 
-Researchers have used administrative data linked with registered voter files to explore the effects of stops, arrests, conviction, and incarceration on political behavior.
-We can say, with some reservations, that such contact likely reduces participation at the ballot box.
-To date, however, no work has leveraged administrative data to test the effect of police ticketing routine police stops on political behavior, and relatively little work has investigated the effects of police stops.
-Some qualitative research (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}) indicates that these low-level stops are demobilizing; Laniyou, on the other hand, finds that neighborhoods with many police stops can turnout at higher rates, and survey data analyzed by Walker similarly shows that police stops can mobilize.
-By identifying all individuals subjected to a traffic stop in Hillsborough County, this project pushes us forward along the lines of other work using administrative data.
-
 Most of the aforementioned studies were conducted using data collected before the rise of the Black Lives Matter movement in 2013, which could be construed as a significant development for the political socialization of Black Americans with respect to policing and incarceration.
@@
 It's possible that any potentially mobilizing effects of criminal legal contact became stronger in the 2010s --- in other words, Black Lives Matter could have facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis.
-That said, Laniyonu did demonstrate mobilization in Black neighborhoods before the beginning of the Black Lives Matter movement.
+That said, \protect\hyperlink{ref-Laniyonu2019}{Laniyonu} (\protect\hyperlink{ref-Laniyonu2019}{2019}) did demonstrate mobilization in Black neighborhoods before the beginning of the Black Lives Matter movement.
 
@@
 In the 20th century, residential segregation simultaneously fueled the racial wealth gap and ensured that criminalization was both spatially and racially concentrated (\protect\hyperlink{ref-Rothstein2017}{Rothstein 2017}; \protect\hyperlink{ref-Hinton2021}{Hinton and Cook 2021}).
-At the level of federal policy, racial threat and whites' attribution of criminality to Blackness (\protect\hyperlink{ref-Muhammad2010}{Muhammad 2010}) prompted a shift ``from the War on Poverty to the War on Crime'' wherein Black communities' demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration (\protect\hyperlink{ref-Hinton2017}{Hinton 2017}; \protect\hyperlink{ref-Vargas2017}{\textbf{Vargas2017?}}).
+At the level of federal policy, racial threat and whites' attribution of criminality to Blackness (\protect\hyperlink{ref-Muhammad2010}{Muhammad 2010}) prompted a shift ``from the War on Poverty to the War on Crime'' wherein Black communities' demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration (\protect\hyperlink{ref-Hinton2017}{Hinton 2017}; \protect\hyperlink{ref-Vargas2017a}{Vargas and McHarris 2017}).
 Ruth Wilson Gilmore explains how mid to late 20th-century whites ``demanded that the state become leaner and meaner, except when directed to do otherwise'' --- in other words, Keynesian welfare guarantees were undermined by the racist myth of ``welfare queens'' and supplanted by expanded police power (\protect\hyperlink{ref-Gilmore2007}{Gilmore 2007, 53}).
@@
 With this history in mind, we argue that Black Americans can situate exploitative ticketing practices in a longer historical legacy of collective disparate treatment and violence at the hands of the state, which may facilitate a stronger collective political analysis when police ticketing practices become more extreme.
-We expect that Black voters' political behavior in response to police ticketing will be distinct from the political behavior of white voters.
-
-\hypertarget{fines-perceptions-of-government-and-voting}{%
-\subsection*{Fines, perceptions of government, and voting}\label{fines-perceptions-of-government-and-voting}}
-\addcontentsline{toc}{subsection}{Fines, perceptions of government, and voting}
-
-The explosion of the reach of the criminal legal system in recent years --- both in terms of fees and fines collection, overzealous prosecution, and mass incarceration --- have had major ramifications on how Americans understand their identities and citizens and their relationship to their government.
-This is doubly true for Black Americans.
-As discussed above, this is not new: the ``hidden curriculum'' of the criminal legal system has long been a site of political socialization in the United States.
-In recent years, research has helped us make sense of the democratic ramifications of this.Traffic stops affect far more Americans than arrests and incarceration do: in 2018, more than 24 million people experienced police contact in the context of a traffic stop, whereas about 5.17 million people are disenfranchised as a result of a felony conviction (\protect\hyperlink{ref-Harrell2020}{Harrell and Davis 2020}; \protect\hyperlink{ref-Uggen2020}{Uggen et al.
-2020}).
-Sances and You (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}) explicitly suggested that ``fines may make descriptive representation less likely by depressing minority turnout,'' and called for further research regarding voter turnout and the imposition of fines.
-Our analysis picks up where they left off.
-
-These political barriers also disproportionately affect Black people.
-In Alabama, for example, Black people with felony convictions applying to have their voting rights restored were 26 percentage points more likely to have their application denied over outstanding fines and fees (\protect\hyperlink{ref-Meredith2017}{Meredith and Morse 2017}).
-
-Although the majority of voters in our analysis do not have felony convictions,
+\protect\hyperlink{ref-Walker2020}{Walker} (\protect\hyperlink{ref-Walker2020}{2020}) makes clear that, when Black Americans locate their contact with the criminal legal system in a narrative of racial injustice, they can be mobilized to vote.
+The historical use of fees and fines make this sort of police contact especially likely to evoke such narratives.
+Accordingly, we expect that Black voters' political behavior in response to police ticketing will be distinct from the political behavior of white voters.
 
@@
 The COG data only include local revenues, which means the share of fines revenue corresponds more directly to local police practices.
+Following the guidance of \protect\hyperlink{ref-Sances2017}{Sances and You} (\protect\hyperlink{ref-Sances2017}{2017}), we retain only municipalities with police and/or court systems, and only municipalities with populations of at least 2,500.
 
@@
 By using the racial estimates provided by L2, we can estimate the number of ballots cast by voters of each race in each city.
-Although each voters' race is modeled based on L2's algorithms --- not self-reported --- it is possibly incorrect for some voters.
+Although each voters' race is modeled based on L2's algorithms --- and is not self-reported --- it is possibly incorrect for some voters.
 We assume this does not present a problem when records are aggregated to the municipal level.
@@
 
-\emph{Hypothesis 2: The effect of the city-level relationship between fines and voter turnout is distinct for Black voters --- i.e.~more pronounced than or in the opposite direction of the effect of fines on turnout for white voters.}
+\emph{Hypothesis 2: The effect of the city-level relationship between fines and voter turnout is less demobilizing or more mobilizing for Black voters, given the historical and explicit racial injustice narratives used to explain these practices..}
 
@@
 Our national test of the relationship between municipal fees and fines collection and turnout offers novel insight into the political socialization of low-level police contact.
-It cannot, however, directly observe the causal mechanism we argue is at play: namely, that personal or proximal contact with the criminal legal system influences turnout.
-Our national analysis suffers from what is called the ecological fallacy: it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
+It cannot, however, directly observe the causal mechanism we argue is at play: namely, that direct contact with the criminal legal system influences turnout.
+Our national analysis suffers from what is called the ``ecological fallacy:'' it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
 
@@
 Department of Justice investigation and report, requested by Tampa's mayor and police chief.
-In other words, there's strong evidence suggesting both racist targeting of tickets and potential publicity to catalyze distinct Black voter responses to the abusive behavior during the same time frame as our national analysis.
+In other words, there is strong evidence suggesting both racist targeting of tickets and potential publicity to catalyze distinct Black voter responses to the abusive behavior during the same time frame as our national analysis.
 Ticketing has also been expressly politicized in Tampa: Jane Castor, who was elected mayor in 2019, was Tampa's police chief until 2015 and publicly defended her department's disproportionate ticketing of Black bicyclists before retracting her defense ahead of her mayoral campaign (\protect\hyperlink{ref-Carlton2018}{Carlton 2018}).
@@
 
-To test the effect of ticketing on individual-level turnout, we match the first and last names and dates of birth against the Hillsborough County registered voter file from L2.
+To test the effect of ticketing on individual-level turnout, we match the first and last names and dates of birth against the Hillsborough County registered voter file.
+Here, rather than rely on a snapshot from L2, we use the raw voter file directly from the state.
+Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status (see \protect\hyperlink{ref-Nyhan2017}{Nyhan, Skovron, and Titiunik 2017}).
+Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.
+We thus observe virtually all individuals who were registered to vote at any time during our period of study.
+Unique voter identification numbers allow us to avoid double-counting voters who are registered in multiple snapshots.
+We each voter's earliest record, and geocode voters to their home census block groups.
+
 To improve the quality of the match between the two datasets, we remove all punctuation from all names and convert all names to lower-case.
@@
 
-By matching these records, we identify all voters who were ticketed between the 2012 and 2018 general elections.
+By matching the police stop and voter records, we identify all voters who were ticketed between the 2012 and 2018 general elections.
 Voters are considered ``treated'' for every general election following their first ticket.
-This means that a voter who was ticketed in early 2014 was considered treated''= for the 2014, 2016, and 2018 elections.
+This means that a voter who was ticketed in early 2014 was considered treated for the 2014, 2016, and 2018 elections.
 A voter treated in 2017, on the other hand, is only considered treated in the 2018 election.
 
-These voters are then matched to one control voter using what methodologists call a ``genetic'' process (\protect\hyperlink{ref-Sekhon2011}{Sekhon 2011}).
+These voters are then matched to two control voters using what methodologists call a ``genetic'' process (\protect\hyperlink{ref-Sekhon2011}{Sekhon 2011}).
 The pool of potential control voters are the individuals who are never stopped during the 2012 -- 2018 period, regardless of whether they paid a fine.
@@
 
+We then run ordinary least squares difference-in-difference regressions to test the following hypotheses.
+
 \emph{Hypothesis 3: Among individuals who were ticketed (``treated'') in Tampa, their likelihood of turning out in a subsequent election roughly matches the racioethnic distribution apparent in the national city-level data.
@@
 
-Because Tampa holds off-year local elections, we are able to test whether mobilized voters target officials who are able to change local police practices.
-\protect\hyperlink{ref-Laniyonu2019}{Laniyonu} (\protect\hyperlink{ref-Laniyonu2019}{2019}) gives us reason to believe that the effect should be stronger for local elections.
-
-\emph{Hypothesis 4: Any potential mobilizing turnout effect in Tampa is stronger for local (mayoral) elections, since those elections directly affect police practices.}
-
-That said, Laniyonu found that heavily policed, majority-Black New York City neighborhoods tended to vote for William Thompson, a Black candidate who opposed police reform --- which could suggest that Black voters prioritized descriptive representation over outward-facing policy messaging.
-In Tampa, however, both leading candidates were white, and Castor was the police chief during the city's racist ticketing scandal.
-Thus, the racioethnic identity of the candidates in 2019 should not affect ticketed Black voters' responses to candidates' policy messaging in the same way.
-
-One novel feature of our analysis is that we are able to assess the political effects of both proximal and personal criminal legal contact during the same time frame.
-The COG data likely capture the voting behavior of people who were not personally ticketed, but know one or several people who were; and the Tampa data capture the voting behavior of people who were themselves ticketed.
-
-Additionally, our analysis eliminates measurement problems that potentially affected past research and accounts for the temporal features of the relationship between criminal legal contact and voting.
-Several prior studies regarding criminalization and political behavior (\protect\hyperlink{ref-Walker2014}{Walker 2014}; \protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}) involve surveys where the measure of police contact is self-reported intensity of contact --- ``have you ever been stopped by police?
-Arrested?
-Incarcerated?'' Respondents were then asked to indicate how likely they might be to vote.
-Our analysis allows us to assess the actual voting behavior of people who we verify were ticketed and gauge the strength of the treatment effect over time by comparing each individual's participation in subsequent elections.
-It is also advantageous that we are able to capture actual voting behavior within a few months or weeks of treatment application --- only Walker and White conduct individual-level analyses consistent with voter file data, and Laniyonu conducts a neighborhood-level analysis using voter file data.
-This feature of our data also helps us avoid measurement issues with survey instruments used in prior studies --- for example, Lerman and Weaver are careful to note that people who have been arrested or incarcerated sometimes misreport their political behavior in survey research.
+The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures participation.
+Past work looking at the individual-level effects of low-level contact has relied entirely on survey or qualitative data (e.g.
+\protect\hyperlink{ref-Walker2014}{Walker 2014}; \protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
+Their in-depth research allows for the testing of specific psychological mechanisms and personal interpretations of criminal legal contact, but does not allow us to generalize more broadly.
+As Weaver and Lerman (\protect\hyperlink{ref-Weaver2010}{2010, 821}) note, it may also introduce measurement bias.
 Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to police ticketing.
+The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of the 232,568 individuals ticketed over the 6 year period --- a far larger pool than even the most robust surveys.
 
@@
 The coefficient on \emph{Treated × 2018} indicates that non-Black turnout dropped by about 0.5 percentage points in municipalities where fees and fines collections increased relative to other municipalities.
-While this coefficient is also negative for Black voters, it is not statistically significantly different from 0.
+While this coefficient is slightly positive for Black voters, it is not statistically significantly different from 0.
 In other words, both Tables \ref{tab:twfe} and \ref{tab:coarser} indicate that increased fees and fines collections decrease non-Black turnout but have no impact on Black turnout.
@@
 As discussed above, we match (\protect\hyperlink{ref-Sekhon2011}{Sekhon 2011}) individuals who were stopped and assessed a fine between the 2012 and 2018 elections to individuals who were not stopped during this time period.\footnote{Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
-The full sample is used in the actual matching process.} Matching is done with replacement and ties are not broken, meaning some treated voters may have more than XX controls; the regression weights reflect this possibility.
+The full sample is used in the actual matching process.} Matching is done with replacement and ties are not broken, meaning some treated voters may have more than 2 controls; the regression weights reflect this possibility.
 In Table \ref{tab:balance} we present the results of the matching algorithm.
@@
 \midrule
-\% White & 49.1\% & 62.3\% & 49.2\% & 99.60\%\\
-\% Black & 22.9\% & 12.7\% & 22.9\% & 99.69\%\\
-\% Latino & 18.9\% & 16.3\% & 18.8\% & 99.23\%\\
-\% Asian & 2.2\% & 2.7\% & 2.2\% & 99.82\%\\
-\% Male & 51.1\% & 43.1\% & 51.2\% & 99.21\%\\
-\% Democrat & 42.0\% & 37.6\% & 41.8\% & 97.38\%\\
-\% Republican & 24.5\% & 31.4\% & 24.7\% & 97.83\%\\
-Age & 43.58 & 51.88 & 43.53 & 99.47\%\\
-Registration Date & 2006-06-13 & 2004-08-08 & 2006-06-20 & 99.00\%\\
-Stops Prior to 2012 Election & 1.29 & 0.36 & 1.11 & 80.11\%\\
-Turnout in 2010 & 20.9\% & 27.2\% & 20.6\% & 94.96\%\\
-Turnout in 2012 & 46.9\% & 45.5\% & 46.8\% & 87.69\%\\
-Median Income & \$63,782 & \$67,952 & \$63,859 & 98.17\%\\
-\% with Some College & 74.5\% & 76.6\% & 74.7\% & 89.50\%\\
-Unemployment Rate & 6.5\% & 5.8\% & 6.4\% & 91.07\%\\
+\% White & 49.2\% & 62.3\% & 49.2\% & 99.97\%\\
+\% Black & 23.1\% & 12.7\% & 23.1\% & 99.72\%\\
+\% Latino & 18.8\% & 16.3\% & 18.8\% & 99.83\%\\
+\% Asian & 2.2\% & 2.7\% & 2.2\% & 97.90\%\\
+\% Male & 50.8\% & 43.1\% & 50.7\% & 98.29\%\\
+\% Democrat & 42.0\% & 37.6\% & 42.2\% & 93.45\%\\
+\% Republican & 24.6\% & 31.4\% & 24.0\% & 91.52\%\\
+Age & 43.42 & 51.88 & 43.37 & 99.40\%\\
+Registration Date & 2006-06-27 & 2004-08-08 & 2006-07-06 & 98.65\%\\
+Stops Prior to 2012 Election & 1.31 & 0.36 & 1.31 & 99.82\%\\
+Turnout in 2010 & 20.8\% & 27.2\% & 20.7\% & 97.98\%\\
+Turnout in 2012 & 47.1\% & 45.5\% & 47.1\% & 99.14\%\\
+Median Income & \$63,885 & \$67,952 & \$63,757 & 96.85\%\\
+\% with Some College & 74.6\% & 76.6\% & 74.8\% & 90.88\%\\
+Unemployment Rate & 6.5\% & 5.8\% & 6.4\% & 92.64\%\\
 \bottomrule
@@
 
-{[}Our results provide support for Walker's theory of low-level police contact mobilizing nonwhite political participation.
-
-the role of fines and fees in the context of felony disenfranchisement has recently taken on greater political significance.
-After Floridians voted to restore voting rights to individuals with felony convictions in 2018, Florida Republicans passed legislation requiring these individuals to pay off the fines and fees associated with their original sentence.
-Because Florida does not maintain good records on who owes how much, this has proved to be a major hurdle for potential voters.
+Our results provide support for Walker's theory of criminal legal contact mobilizing nonwhite political participation.
+Our individual-level analysis in Hillsborough County shows that being ticketed mobilizes voters, and mobilizes Black voters to a greater degree than non-Black voters---and our city-level analysis shows that while greater fines and fees reliance reduces white voter turnout, it has no effect on Black turnout.
+
+{[}Particularly following the rise of the Black Lives Matter movement in 2013, our findings are consistent with the theory that Black voters interpret exploitative police practices as a threat to the wellbeing of all Black Americans.{]}
+
+We were somewhat surprised by the differences that arose between our two sets of findings---our city-level analysis did not produce statistically significant results for Black voters.
+We think there are a few potential explanations for this mismatch.
+First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes are smaller or not statistically significant.
+Along a similar vein, it's possible that the effect size for Black voters in the city-level analysis is affected by higher-intensity forms of criminal legal contact, such as arrest and incarceration.
+The bulk of existing literature suggests that incarceration discourages political participation, and it's not unreasonable to assume that cities that ramp up ticketing of Black residents also ramp up arrest and incarceration of Black residents.
+If these phenomena coincide, that could explain why the city-level analysis produced no statistically significant effect for Black voters---the personally mobilizing effect of ticketing could be counterbalanced by the proximal chilling effect of incarceration, and because the city-level analysis is not as temporally sensitive, it's more difficult to isolate the effect of ticketing.
+
+\textbf{Limitations}: Because our individual-level analysis is limited to Hillsborough County, we don't have a good idea of whether the city-level revenue reliance trend interacts with the individual experience of being ticketed.
+Is ticketing more politically mobilizing in cities that are palpably dialing up their revenue collection efforts?
+Future research could test this hypothesis in cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.
+
+Additionally, in our analysis of Hillsborough County voters, we don't look at people who weren't registered to vote in 2018.
+This means that there could be some proportion of ticketed Black motorists who are now less likely to register to vote in the first place, for example.
+In other words the mobilization effect in our findings only applies to people who were registered to vote---we are unable to make claims about whether being ticketed makes an individual more likely to register to vote.
+
+\textbf{Future research}: Unlike previous studies using survey data, we are unable to tell whether individuals in Tampa have non-ticketing criminal legal exposure.
+Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.{]}
 
@@
 
-{[}Why do we think Black voters are mobilized? ``Linked fate,'' history, contemporary practices, Black Lives Matter.{]}
-
-{[}Limitations of research.{]} {[}We don't look at people who aren't registered to vote in 2018, so there could be some proportion of ticketed Black motorists who are now less likely to register to vote in the first place, for example.
-In other words our mobilization effect size only applies to people who were registered to vote.
-At the same time, perhaps people who weren't registered were equally likely to be deterred by something else.{]}
-
-{[}Because we only look at Tampa, we don't have a good idea of whether the revenue reliance trends interact with the experience of ticketing.
-Is ticketing a particularly alienating-mobilizing phenomenon in cities that are palpably dialing up their revenue collection efforts?
-Future research could test this hypothesis in cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.{]}
-
-{[}Unlike previous studies using survey data, we are unable to tell whether individuals in Tampa have non-ticketing criminal legal exposure.
-Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.{]}
-
-{[}Relevance for other scholars. Future research agenda.{]}
+\newpage
+
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
 
@@
 
+\leavevmode\hypertarget{ref-Cox2019}{}%
+Cox, Kiana.
+2019.
+{``Most {U}.{S}.
+Adults Feel What Happens to Their Own Racial or Ethnic Group Affects Them Personally.''} {Pew Research Center}.
+July 11, 2019.
+\url{https://www.pewresearch.org/fact-tank/2019/07/11/linked-fate-connectedness-americans/}.
+
 \leavevmode\hypertarget{ref-Desmond2016}{}%
@@
 
-\leavevmode\hypertarget{ref-Harrell2020}{}%
-Harrell, Erika, and Elizabeth Davis.
-2020.
-{``Contacts {Between Police} and the {Public}, 2018 - {Statistical Tables}.''} {Bureau of Justice Statistics}.
-\url{https://www.bjs.gov/index.cfm?ty=pbdetail\&iid=7167}.
-
 \leavevmode\hypertarget{ref-Harris2010}{}%
@@
 Initiative, Equal Justice. 2017. {``Lynching in {America}: {Confronting} the {Legacy} of {Racial Terror}.''} \url{https://lynchinginamerica.eji.org/report/}.
+
+\leavevmode\hypertarget{ref-Justice2014}{}%
+Justice, Benjamin, and Tracey L.
+Meares.
+2014.
+{``How the {Criminal Justice System Educates Citizens}.''} \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 159--77.
+\url{https://doi.org/10.1177/0002716213502929}.
 
@@
 
+\leavevmode\hypertarget{ref-Meares2017}{}%
+Meares, Tracey. 2017. {``Policing and {Procedural Justice}: {Shaping Citizens}' {Identities} to {Increase Democratic Participation}.''} \emph{Northwestern University Law Review} 111 (6): 1525--36.
+
 \leavevmode\hypertarget{ref-Meredith2014}{}%
@@
 
+\leavevmode\hypertarget{ref-Nyhan2017}{}%
+Nyhan, Brendan, Christopher Skovron, and Rocío Titiunik.
+2017.
+{``Differential {Registration Bias} in {Voter File Data}: {A Sensitivity Analysis Approach}.''} \emph{American Journal of Political Science} 61 (3): 744--60.
+\url{https://doi.org/10.1111/ajps.12288}.
+
 \leavevmode\hypertarget{ref-Pacewicz2020}{}%
@@
 \url{https://doi.org/10.1017/S1742058X18000206}.
+
+\leavevmode\hypertarget{ref-Remster2018a}{}%
+---------.
+2018.
+{``Race, {Space}, and {Surveillance}: {Understanding} the {Relationship} Between {Criminal Justice Contact} and {Institutional Involvement}.''} \emph{Socius} 4 (January).
+\url{https://doi.org/10.1177/2378023118761434}.
 
@@
 
+\leavevmode\hypertarget{ref-Shofner1963}{}%
+Shofner, Jerrell H. 1963. {``The {Constitution} of 1868.''} \emph{The Florida Historical Quarterly} 41 (4): 356--74. \url{http://www.jstor.org/stable/30139965}.
+
 \leavevmode\hypertarget{ref-Singla2020}{}%
@@
 
+\leavevmode\hypertarget{ref-Vargas2017a}{}%
+Vargas, Robert, and Philip McHarris.
+2017.
+{``Race and {State} in {City Police Spending Growth}: 1980 to 2010.''} \emph{Sociology of Race and Ethnicity} 3 (1): 96--112.
+\url{https://doi.org/10.1177/2332649216650692}.
+
 \leavevmode\hypertarget{ref-Walker2014}{}%

### 2021-03-22 code/hills/rob/rob1_match.R
build out robustness checks. rob1 will become primary analyses

@@ -1,0 +1,214 @@
+library(Matching)
+library(data.table)
+library(scales)
+library(kableExtra)
+library(tidyverse)
+require(snow)
+require(parallel)
+
+
+hills_pre_match <- readRDS("temp/hills_pre_match.rds")
+
+############## 2014
+
+hills14_t <- filter(hills_pre_match, first_tr_year == "2014-11-04") %>% 
+  mutate(treated = 1) %>% 
+  select(-pre_stops_c)
+
+hills14_c <- filter(hills_pre_match, first_tr_year == "2016-11-08",
+                    !(voter_id %in% hills14_t$voter_id)) %>% 
+  mutate(treated = 0) %>% 
+  select(-pre_stops) %>% 
+  rename(pre_stops = pre_stops_c)
+
+
+hills14 <- bind_rows(hills14_t, hills14_c) %>%  
+  mutate(first_tr_year = 1) %>% 
+  select(-v14, -v16, -pre) %>% 
+  rename(v1 = v08,
+         v2 = v10,
+         v3 = v12)
+
+############## 2016
+
+hills16_t <- filter(hills_pre_match, first_tr_year == "2016-11-08") %>% 
+  mutate(treated = 1) %>% 
+  select(-pre_stops_c)
+
+hills16_c <- filter(hills_pre_match, first_tr_year == "2018-11-06",
+                    !(voter_id %in% hills16_t$voter_id)) %>% 
+  mutate(treated = 0) %>% 
+  select(-pre_stops) %>% 
+  rename(pre_stops = pre_stops_c)
+
+
+hills16 <- bind_rows(hills16_t, hills16_c) %>%  
+  mutate(first_tr_year = 2) %>% 
+  rename(v1 = v10,
+         v2 = v12,
+         v3 = v14)
+
+############## 2018
+
+hills18_t <- filter(hills_pre_match, first_tr_year == "2018-11-06") %>% 
+  mutate(treated = 1) %>% 
+  select(-pre_stops_c)
+
+hills18_c <- filter(hills_pre_match, first_tr_year == "2020-11-03",
+                    !(voter_id %in% hills18_t$voter_id)) %>% 
+  mutate(treated = 0) %>% 
+  select(-pre_stops) %>% 
+  rename(pre_stops = pre_stops_c)
+
+
+hills18 <- bind_rows(hills18_t, hills18_c) %>%  
+  mutate(first_tr_year = 3) %>% 
+  rename(v1 = v12,
+         v2 = v14,
+         v3 = v16)
+
+###########################################
[…]

### 2021-03-22 code/hills/rob/rob1_reg.R

@@ -1,0 +1,244 @@
+
+#####
+hills_pre_match <- readRDS("temp/hills_pre_match.rds") %>% 
+  ungroup()
+
+matches <- readRDS("temp/matches_hills_y.rds")
+
+matches <- left_join(matches, select(hills_pre_match, voter_id, fd),
+                     by = c("group" = "voter_id")) %>% 
+  mutate(first_tr_year = ifelse(fd <= "2014-11-04", "2014-11-04",
+                                ifelse(fd <= "2016-11-08", "2016-11-08",
+                                       ifelse(fd <= "2018-11-06", "2018-11-06", "XX"))),
+         first_tr_year = as.Date(first_tr_year)) %>% 
+  select(-fd)
+
+hist <- readRDS("temp/full_raw_coded_hills_w_bgs.rds") %>%
+  select(voter_id, starts_with("v1"), v08) %>%
+  pivot_longer(!starts_with("vo"), names_to = "year", values_to = "to")
+
+elec_dates <- fread("raw_data/election_dates.csv")
+
+hist <- left_join(hist, elec_dates) %>% 
+  select(-year) %>% 
+  rename(year = date) %>% 
+  mutate(year = as.Date(year, "%m/%d/%Y"))
+
+
+matches <- left_join(matches, hist %>% 
+                       filter(year(year) %% 2 == 0), by = c("voter" = "voter_id"))
+
+periods <- fread("raw_data/period_lu.csv") %>% 
+  mutate_at(vars(first_tr_year, year), as.Date, "%m/%d/%Y")
+
+matches <- left_join(matches, periods) %>% 
+  filter(period %in% c(-2.5, -1.5, -.5, .5))
+
+matches <- left_join(matches,
+                     hills_pre_match %>%
+                       select(-GEOID, -fd, -max_amount),
+                     by = c("voter" = "voter_id"))
+
+matches <- left_join(matches,
+                     hills_pre_match %>%
+                       select(voter_id, max_amount, fd, black_t = black),
+                     by = c("group" = "voter_id")) %>% 
+  mutate(post = period >= 0.5,
+         treated = voter == group)
+
+cleanup("matches")
+gc()
+ll <- matches %>%
+  filter(first_tr_year - fd <= 90,
+         year(first_tr_year) == 2018) %>%
+  group_by(treated, period, black_t) %>%
+  summarize(to = weighted.mean(to, weight)) %>% 
+  mutate(treated = ifelse(treated, "Treated", "Control"),
[…]

### 2021-03-22 code/hills/rob/rob2.R

@@ -1,0 +1,76 @@
+
+
+hills_pre_match <- readRDS("temp/hills_pre_match.rds") %>% 
+  ungroup()
+
+matches_wide <- rbindlist(lapply(c(
+  "temp/matches_hills_14_rob.rds",
+  "temp/matches_hills_16_rob.rds",
+  "temp/matches_hills_18_rob.rds"), readRDS))
+
+hist <- readRDS("temp/full_raw_coded_hills_w_bgs.rds") %>%
+  select(voter_id, starts_with("v1")) %>%
+  pivot_longer(starts_with("v1"), names_to = "year", values_to = "to")
+
+elec_dates <- fread("raw_data/election_dates.csv")
+
+hist <- left_join(hist, elec_dates) %>% 
+  select(-year) %>% 
+  rename(year = date) %>% 
+  mutate(year = as.Date(year))
+
+
+matches <- left_join(matches_wide, hist %>% 
+                       filter(year(year) %% 2 == 0), by = c("voter" = "voter_id"))
+
+periods <- fread("raw_data/period_lu.csv") %>% 
+  mutate_at(vars(first_tr_year, year), as.Date)
+
+matches <- left_join(matches, periods)
+
+matches <- left_join(matches,
+                     hills_pre_match %>%
+                       select(-GEOID, -fd, -max_amount),
+                     by = c("voter" = "voter_id"))
+
+matches <- left_join(matches,
+                     hills_pre_match %>%
+                       select(voter_id, max_amount, fd, black_t = black),
+                     by = c("group" = "voter_id")) %>% 
+  mutate(post = period >= 0.5,
+         treated = voter == group)
+
+ll <- matches %>%
+  filter(period <= 1.5) %>% 
+  group_by(treated, period, black_t) %>%
+  summarize(to = weighted.mean(to, weight)) %>% 
+  mutate(treated = ifelse(treated, "Treated", "Control"),
+         black = ifelse(black_t, "Black Voters", "Non-Black Voters"))
+
+
+ll$treated <- factor(ll$treated, levels = c("Treated", "Control"))
+
+p1 <- ggplot(data = ll) + 
+  facet_grid(~ black) +
+  geom_rect(aes(xmin = 0.5+.125, xmax = 0.5, ymin = 0, ymax = Inf),
+            alpha = 0.03, color = "black", fill = "yellow") +
+  geom_line(data =ll, aes(x = period, y = to, linetype = treated)) +
[…]

### 2021-03-22 markdown/draft_paper.Rmd
write

@@
 Additionally, we exploit individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019 to determine whether getting a ticket impacts political participation.
-Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.6 percentage point decrease in nonBlack turnout but was not associated with Black turnout.
-In Tampa, Florida, we estimate being ticketed increases a nonBlack individual’s likelihood of voting by 3.7 percentage points, and that the effect is larger for Black voters.
+Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.6 percentage point decrease in non-Black turnout but was not associated with Black turnout.
+In Tampa, Florida, we estimate that being ticketed increases a non-Black individual’s likelihood of voting by 3.7 percentage points, and that the effect is larger for Black voters.
 
@@
   **Keywords**: voting, monetary sanctions, race, punishment, political participation
+nocite: | 
+  @Burch2011, @Burch2013, @White2019a
+
 ---
@@
 It wasn’t just a Ferguson problem, or even a Missouri problem.
-American cities’ reliance on fines and fees revenue increased significantly following the 2008 recession --- as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services [@Singla2020; @Harris2017].
+American cities’ reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services [@Singla2020; @Harris2017].
 
@@
 This work, however, has largely focused on the effects of highly consequential contact with the criminal legal system such as incarceration and felony convictions [@Burch2014; @Lee2014].
-Although some work has leveraged survey data and qualitative approaches to interrogate lower-level police interactions --- such as ticketing --- our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
+Although some work has leveraged survey data and qualitative approaches to interrogate lower-level police interactions---such as ticketing---our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
 We begin by joining fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for each municipality in the country.
@@
 By matching individuals who were ticketed to other, similar voters who were not ticketed and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout.
-Using self-reported race from the Florida registered voter file, we identify large, *positive* treatment effects for all voters --- effects that were especially large for Black voters..
+Using self-reported race from the Florida registered voter file, we identify large, *positive* treatment effects for all voters---effects that were especially large for Black voters..
 
-We demonstrate that police ticketing practices --- the most widespread form of police contact in America --- influence the political behavior of Americans, with distinct effects for Black and non-Black voters.
+We demonstrate that police ticketing practices---the most widespread form of police contact in America---influence the political behavior of Americans, with distinct effects for Black and non-Black voters.
 This finding supports and extends Hannah Walker’s theory of criminal legal contact is mobilizing / less demobilizing for nonwhite political participation [@Walker2020; @Walker2014].
-On an individual level, we also find that voters who were ticketed turn out at higher rates in subsequent elections, and that this effect was especially large for Black individuals.
-This finding complicates Vesla Weaver and Amy Lerman’s theory of low-level criminal legal contact discouraging political participation [@Weaver2010].
+Our results also complicate Vesla Weaver and Amy Lerman’s theory of low-level criminal legal contact discouraging political participation [@Weaver2010].
 Our findings are relevant for interdisciplinary scholars of crime, race, politics, political economy, social movements, and policing.
@@
 
-Tthe role of fines and fees in the context of felony disenfranchisement has recently garnered national attentiontaken on greater political significance.
-After Floridians passed Amendment 4 voted to restore voting rights to individuals with felony convictions in 2018, Florida Republicans passed legislation requiring these individuals to pay off the fines and fees associated with their original sentence.
+The role of fines and fees in the context of felony disenfranchisement has recently garnered national attention.
+After Floridians passed Amendment 4 to restore voting rights to individuals with felony convictions in 2018, Florida Republicans passed legislation requiring these individuals to pay off the fines and fees associated with their original sentence.
 Because Florida does not maintain good records on who owes how much, this has proved to be a major hurdle for potential voters.
-Despite a dissenting judge arguing that ““[h]ad Florida wanted to create a system to obstruct, impede, and impair the ability of felons to vote under Amendment 4, it could not have come up with a better one,” an en bank ruling by the U.S.
+Despite a dissenting judge arguing that ““[h]ad Florida wanted to create a system to obstruct, impede, and impair the ability of felons to vote under Amendment 4, it could not have come up with a better one,” an en banc ruling by the U.S.
 Court of Appeals for the 11th Circuit upheld this legislation.^[Jones et al.
@@
 Using existing national survey data and extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) [@Weaver2010].
-Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a “linked fate” where group members believe that group-level phenomena affect all group members [@Cox2019] of all Black Americans.
-Their interview data lead them to conclude that “a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing” --- and interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation [@Lerman2014].
+Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a “linked fate” where “one’s individual opportunities are linked to the entire racial group” [@Lerman2014, page 267].
+Their interview data lead them to conclude that while criminal legal contact does increase perceptions of linked fate among Black respondents, “a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing”---and interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation [@Lerman2014].
 
@@
 It may be the case that Black and non-Black Americans employ different self-preservation strategies, however.
-Ariel White’s analysis of how short jail sentences affect voting in Harris County, Texas found that Black defendant turnout in subsequent elections dropped by 13 percentage points --- but the effect on white turnout was not statistically significant [@White2019].
+Ariel White’s analysis of how short jail sentences affect voting in Harris County, Texas found that Black defendant turnout in subsequent elections dropped by 13 percentage points---but the effect on white turnout was not statistically significant [@White2019].
 
-Proximal exposure to criminalization --- “having a loved one who is a custodial citizen without yourself having had contact” [@Walker2017] --- also influences Americans’ perceptions of government and political behavior, and the emerging literature has produced mixed findings of its effect on civic engagement.
+Proximal exposure to criminalization---“having a loved one who is a custodial citizen without yourself having had contact” [@Walker2017]---also influences Americans’ perceptions of government and political behavior, and the emerging literature has produced mixed findings of its effect on civic engagement.
 Using survey and ethnographic interview data, @Lee2014 found that adult children of incarcerated parents are less likely to vote, report lower trust in government, and are less likely to engage in other prosocial behaviors like community service.
@@
 Hannah Walker’s research specifically tests differences between the effects of proximal and personal criminal legal contact on political behavior, and her findings underscore how a “linked fate” political analysis could catalyze distinct political behavior among Black voters [@Walker2014].
-Using data from a 2012 survey of Washington state residents, she found that as the degree of an individual’s proximity to a criminalized person increases, so does their likelihood of participating in political activities (such as voting, signing a petition, volunteering, donating to politicians, etc.).
-Importantly, Walker found that nonwhite people who had experienced *either* proximal or personal contact *at any level of intensity*, including being stopped and questioned by police, were politically mobilized --- and the same held true for whites, but with a much smaller effect size.
+Using data from a 2012 survey of Washington state residents, she found that as the degree of an individual’s proximity to a criminalized person increases, so does their likelihood of participating in political activities other than voting (such as signing a petition, volunteering, donating to politicians, etc.).
+With respect to voting, she found that personal contact was demobilizing, while proximal contact had no statistically significant effect.
+
+Importantly, Walker found that nonwhite people who had experienced *either* proximal or personal contact *at any level of intensity*, including being stopped and questioned by police, were mobilized to take part in nonvoting political activity---and the same held true for whites, but with a much smaller effect size.
 Walker theorizes that this finding suggests that nonwhite people view criminalization “as a form of systemic political threat,” an analysis comparable to “linked fate.” Notably, Walker’s survey questions excluded “minor traffic stops,” the primary focus of this paper.
@@
 She found that living with someone who was charged but not convicted in the 30 day period preceding an election increased voter turnout by 3 percentage points, whereas “convicted but not jailed” decreased turnout by 6 percentage points and “convicted and jailed” decreased turnout by 12 percentage points.
-This provides further support for the theory that increasing intensity of criminalization could change the direction of the effect of criminalization on political behavior --- and, in fact, that lower-level contact can mobilize even as higher-level contact demobilizes.
+This provides further support for the theory that increasing intensity of criminalization could change the direction of the effect of criminalization on political behavior---and, in fact, that lower-level contact can mobilize even as higher-level contact demobilizes.
 
-Although geographic or spatial analyses of how criminalization affects political socialization technically move beyond proximal contact as an extant conceptual framework, we argue that geographic proximity should work similarly to social network proximity --- if one neighborhood is heavily policed, people who live in that neighborhood are more likely to have social ties who have experienced policing.
+Although geographic or spatial analyses of how criminalization affects political socialization technically move beyond proximal contact as an extant conceptual framework, we argue that geographic proximity should work similarly to social network proximity---if one neighborhood is heavily policed, people who live in that neighborhood are more likely to have social ties who have experienced policing.
 Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level [@Burch2014].
@@
 Over the past few years, scientific understanding of the political effects of more serious interactions with the criminal legal system has grown by leaps and bounds.
-The following table summarizes our understanding of the literature.
-
-Type of criminal legal contact
-Personal contact effect on political behavior (individual level)
-Proximal contact effect on political behavior (social network/geography)
-Stopped
-Weaver and Lerman find chilling effect; Walker finds mobilizing effect
-Laniyonu and Walker find mobilizing effect
-Arrested
-Weaver and Lerman find chilling effect; Walker finds mobilizing effect
-Walker finds mobilizing effect
-Convicted / Supervision
-Burch, Weaver and Lerman find chilling effect; Walker finds mobilizing effect 
-Burch, Lee, Sugie, White, and Morris find chilling effect; Walker finds mobilizing effect
-Incarcerated
-Burch, White, Weaver and Lerman find chilling effect; Walker finds mobilizing effect
-Burch, Lee, Sugie, White, and Morris find chilling effect; Walker finds mobilizing effect
+Table \ref{tab:lit-table} summarizes our understanding of the literature.
+As Table \ref{tab:lit-table} makes clear, a large body of research has now demonstrated the negative effects of high-level contact with the criminal legal system on voter turnout.
+Although lower-level stops are far more frequent, our knowledge of their (de)mobilizing effects is under-developed.
 
 \begin{singlespace}
-```{r lit-table, echo = F, warning = F}
-t <- fread("./raw_data/lit_table.csv")
-j <- knitr::kable(t, booktabs = T, caption = "(\\#tab:lit-table) Summary of Literature", linesep = "",
-                  align = c("l", "l", "l"), "latex") %>%
-  kable_styling(latex_options = c("HOLD_position", "striped"),
-                full_width = F) %>% 
-  column_spec(1, width = "10em") %>% 
-  column_spec(2, width = "10em") %>% 
-  column_spec(3, width = "10em")
-j
-```
+\input{../raw_data/lit_tab.tex}
 \end{singlespace}
@@
 The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious.
-Though racist police violence was and is a focal point for many Black Lives Matter actions, local chapters frequently use policing as an entry point into a wider set of demands regarding the material security of Black Americans and their marginalization in American politics --- and these demands affect police practices.
+Though racist police violence was and is a focal point for many Black Lives Matter actions, local chapters frequently use policing as an entry point into a wider set of demands regarding the material security of Black Americans and their marginalization in American politics---and these demands affect police practices.
 One recent study found that census places that saw Black Lives Matter protests experienced a 15 to 20 percent decrease in police killings over the following five year period [@Campbell2021].
-It’s possible that any potentially mobilizing effects of criminal legal contact became stronger in the 2010s --- in other words, Black Lives Matter could have facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis.
+It’s possible that any potentially mobilizing effects of criminal legal contact became stronger in the 2010---in other words, Black Lives Matter could have facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis.
 That said, @Laniyonu2019 did demonstrate mobilization in Black neighborhoods before the beginning of the Black Lives Matter movement.
@@
 At the level of federal policy, racial threat and whites’ attribution of criminality to Blackness [@Muhammad2010] prompted a shift “from the War on Poverty to the War on Crime” wherein Black communities’ demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration [@Hinton2017; @Vargas2017a].
-Ruth Wilson Gilmore explains how mid to late 20th-century whites “demanded that the state become leaner and meaner, except when directed to do otherwise” --- in other words, Keynesian welfare guarantees were undermined by the racist myth of “welfare queens” and supplanted by expanded police power [@Gilmore2007, page 53].
+Ruth Wilson Gilmore explains how mid to late 20th-century whites “demanded that the state become leaner and meaner, except when directed to do otherwise”---in other words, Keynesian welfare guarantees were undermined by the racist myth of “welfare queens” and supplanted by expanded police power [@Gilmore2007, page 53].
 
-The 2008 financial crisis solidified the connection between fiscal austerity and policing, prompting a decline in tax revenues that devastated state and local governments --- but law enforcement agencies were largely spared from cuts.
+The 2008 financial crisis solidified the connection between fiscal austerity and policing, prompting a decline in tax revenues that devastated state and local governments---but law enforcement agencies were largely spared from cuts.
 At the local level, this means that police budgets today constitute about thirty percent of city budgets nationwide, and cities where residents have lower median incomes dedicate a larger proportion of spending to policing [@Friedman2020].
@@
 Across the country, city government reliance on fines and fees revenue is associated with larger Black populations [@UnitedStatesCommissiononCivilRights2017].
-Although major urban centers collect high dollar amounts of fines and fees, some of the most egregious ticketing practices measured on a per-capita basis are concentrated in suburbs or smaller cities with municipal courts --- Ferguson being a prominent example [@UnitedStatesDepartmentofJusticeCivilRightsDivision2015; @Mughan2020].
+Although major urban centers collect high dollar amounts of fines and fees, some of the most egregious ticketing practices measured on a per-capita basis are concentrated in suburbs or smaller cities with municipal courts---Ferguson being a prominent example [@UnitedStatesDepartmentofJusticeCivilRightsDivision2015; @Mughan2020].
 The positive association between cities’ reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator, however [@Sances2017].
@@
 A study of four million North Carolina traffic stops found that fiscal stress caused a decrease in the probability of white drivers being searched, but no decrease for Black drivers [@Shoub2020].
-This suggests that higher reliance on fines and fees results in government officials and police targeting individuals who hold less political power --- whether those individuals are out-of-state motorists or members of local marginalized communities [@Makowsky2009].
+This suggests that higher reliance on fines and fees results in government officials and police targeting individuals who hold less political power---whether those individuals are out-of-state motorists or members of local marginalized communities [@Makowsky2009].
 
@@
 By using the racial estimates provided by L2, we can estimate the number of ballots cast by voters of each race in each city.
-Although each voters’ race is modeled based on L2’s algorithms --- and is not self-reported --- it is possibly incorrect for some voters.
+Although each voters’ race is modeled based on L2’s algorithms---and is not self-reported---it is possibly incorrect for some voters.
 We assume this does not present a problem when records are aggregated to the municipal level.
@@
 
-*Hypothesis 2: The effect of the city-level relationship between fines and voter turnout is less demobilizing or more mobilizing for Black voters, given the historical and explicit racial injustice narratives used to explain these practices..*
+*Hypothesis 2: The effect of the city-level relationship between fines and voter turnout is less demobilizing or more mobilizing for Black voters, given the historical and explicit racial injustice narratives used to explain these practices.*
 
@@
 Unique voter identification numbers allow us to avoid double-counting voters who are registered in multiple snapshots.
-We each voter’s earliest record, and geocode voters to their home census block groups.
+We retain each voter’s earliest record, and geocode voters to their home census block groups.
 
@@
 Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to police ticketing.
-The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of the 232,568 individuals ticketed over the 6 year period --- a far larger pool than even the most robust surveys.
+The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of the 232,568 individuals ticketed over the 6 year period---a far larger pool than even the most robust surveys.
 
@@
 In Table \ref{tab:balance} we present the results of the matching algorithm.
-We manage to reduce between treated and control voters substantially along all observed characteristics with the exception of 2012 turnout.
-However, this is not likely a problem: the turnout of all potential and actual controls were both within 0.1 percentage points of the treatment group’s turnout that year.
+We manage to reduce between treated and control voters substantially along all observed characteristics.
 
 \begin{singlespace}
-```{r baltab-chunk, echo = F, warning = F}
-t <- readRDS("temp/balance_table.rds")
-j <- knitr::kable(t, booktabs = T,  caption = "(\\#tab:balance) Balance Table", linesep = "") %>%
+```{r balance-tab-chunk, echo = F}
+t <- readRDS("./temp/balance_table_y.rds")
+j <- knitr::kable(t, booktabs = T, caption = "(\\#tab:balance) Balance Table", linesep = "",
+                  escape = F) %>%
+  add_header_above(c(" " = 1, "Means: Unmatched Data" = 2, "Means: Matched Data" = 2, "Percent Improvement" = 4), align = "c") %>%
   kable_styling(latex_options = c("scale_down", "HOLD_position"))
@@
 
-It is worth noting that voters who were stopped between 2012 and 2018 were far more likely to be Black, males, and registered Democrats than the general electorate, and live in Census block groups with moderately lower incomes.
+It is worth noting that voters who were stopped between 2012 and 2018 were far more likely to be Black and male than the general electorate, and live in Census block groups with moderately lower incomes.
 Unsurprisingly, they were also stopped at higher rates in the pre-treatment period than those never stopped between 2012 and 2018.
@@
 ```{r did1, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/stopped_any_time.rds")
+p2 <- readRDS("temp/stopped_any_time_y.rds")
 print(p2)
@@
 We expected that the ticket would be more salient for individuals stopped shortly before the election.
-This appears to be the case --- *especially for Black voters.*
+This appears to be the case---*especially for Black voters.*
 
 ```{r did2, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:did-2}Effect of Being Ticketed Within 90 Days of Election on Turnout", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/within90days.rds")
+p2 <- readRDS("temp/within90days_y.rds")
 print(p2)
@@
 \begin{singlespace}
-\input{"../temp/dind_reg.tex"}
+\input{"../temp/dind_reg_y.tex"}
 \end{singlespace}
 
-Model 3 indicates that a ticket is neither mobilizing nor demobilizing --- the coefficient is small and nonsignificant (*p* = 0.34) but that tickets do mobilize Black voters.
+Model 3 indicates that a ticket is neither mobilizing nor demobilizing---the coefficient is small and nonsignificant (*p* = 0.34) but that tickets do mobilize Black voters.
 Receiving a ticket increases the average turnout for Black voters in the first two elections by about 1.1 percentage points.
@@
 
-[Tampa - local figure/table]
-
-[Tampa local analysis]
+<!-- [Tampa - local figure/table] -->
 
@@
 
-[Particularly following the rise of the Black Lives Matter movement in 2013, our findings are consistent with the theory that Black voters interpret exploitative police practices as a threat to the wellbeing of all Black Americans.]
+Particularly following the rise of the Black Lives Matter movement in 2013, our findings are consistent with the theory that Black voters interpret exploitative police practices as a threat to the wellbeing of all Black Americans.
 
@@
 If these phenomena coincide, that could explain why the city-level analysis produced no statistically significant effect for Black voters---the personally mobilizing effect of ticketing could be counterbalanced by the proximal chilling effect of incarceration, and because the city-level analysis is not as temporally sensitive, it’s more difficult to isolate the effect of ticketing.
+
+That said, @Sances2017 specifically note that they didn't exploit the panel setup of the COG because of little variation between the 2007-2012 COG to the 2012-2017 one, and so they just stuck to cross sectional.
+The positive effect for Black turnout in Figure 1 is consistent with our Tampa analysis and doesn't totally contradict the TWFE.
 
@@
 **Future research**: Unlike previous studies using survey data, we are unable to tell whether individuals in Tampa have non-ticketing criminal legal exposure.
-Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.]
+Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.
 
-[Laniyonu] - [he writes that block groups with higher Black pop and higher SQF density voted at higher rates for Thompson, the candidate who pledged not to implement SQF reform, but who was Black.
+<!--  [Laniyonu] - [he writes that block groups with higher Black pop and higher SQF density voted at higher rates for Thompson, the candidate who pledged not to implement SQF reform, but who was Black.
 The descriptive representation from Sances2017 kind of covers for this, tactically speaking - electing Black politicians should reduce fines and fees abuses.
@@
 One voter told the Tampa Bay Times that he voted against Castor as “payback” for the racist ticketing practices she oversaw, and the article notes that her opponent won five majority-Black precincts [@Frago2019].
-In 2015, Castor even released a statement as police chief supporting the racist ticketing, insisting that “Many individuals receiving bike citations are involved in criminal activity.”
+In 2015, Castor even released a statement as police chief supporting the racist ticketing, insisting that “Many individuals receiving bike citations are involved in criminal activity.” -->
 

### 2021-03-22 markdown/draft_paper.tex
write

@@
 \author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
-\date{March 17, 2021}
+\date{March 19, 2021}
 
@@
 Additionally, we exploit individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019 to determine whether getting a ticket impacts political participation.
-Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.6 percentage point decrease in nonBlack turnout but was not associated with Black turnout.
-In Tampa, Florida, we estimate being ticketed increases a nonBlack individual's likelihood of voting by 3.7 percentage points, and that the effect is larger for Black voters.
+Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.6 percentage point decrease in non-Black turnout but was not associated with Black turnout.
+In Tampa, Florida, we estimate that being ticketed increases a non-Black individual's likelihood of voting by 3.7 percentage points, and that the effect is larger for Black voters.
 
@@
 It wasn't just a Ferguson problem, or even a Missouri problem.
-American cities' reliance on fines and fees revenue increased significantly following the 2008 recession --- as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (\protect\hyperlink{ref-Singla2020}{Singla, Kirschner, and Stone 2020}; \protect\hyperlink{ref-Harris2017}{Harris et al.
+American cities' reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (\protect\hyperlink{ref-Singla2020}{Singla, Kirschner, and Stone 2020}; \protect\hyperlink{ref-Harris2017}{Harris et al.
 2017}).
@@
 This work, however, has largely focused on the effects of highly consequential contact with the criminal legal system such as incarceration and felony convictions (\protect\hyperlink{ref-Burch2014}{Burch 2014}; \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}).
-Although some work has leveraged survey data and qualitative approaches to interrogate lower-level police interactions --- such as ticketing --- our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
+Although some work has leveraged survey data and qualitative approaches to interrogate lower-level police interactions---such as ticketing---our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
 We begin by joining fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for each municipality in the country.
@@
 By matching individuals who were ticketed to other, similar voters who were not ticketed and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout.
-Using self-reported race from the Florida registered voter file, we identify large, \emph{positive} treatment effects for all voters --- effects that were especially large for Black voters..
-
-We demonstrate that police ticketing practices --- the most widespread form of police contact in America --- influence the political behavior of Americans, with distinct effects for Black and non-Black voters.
+Using self-reported race from the Florida registered voter file, we identify large, \emph{positive} treatment effects for all voters---effects that were especially large for Black voters..
+
+We demonstrate that police ticketing practices---the most widespread form of police contact in America---influence the political behavior of Americans, with distinct effects for Black and non-Black voters.
 This finding supports and extends Hannah Walker's theory of criminal legal contact is mobilizing / less demobilizing for nonwhite political participation (\protect\hyperlink{ref-Walker2020}{Walker 2020}, \protect\hyperlink{ref-Walker2014}{2014}).
-On an individual level, we also find that voters who were ticketed turn out at higher rates in subsequent elections, and that this effect was especially large for Black individuals.
-This finding complicates Vesla Weaver and Amy Lerman's theory of low-level criminal legal contact discouraging political participation (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
+Our results also complicate Vesla Weaver and Amy Lerman's theory of low-level criminal legal contact discouraging political participation (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
 Our findings are relevant for interdisciplinary scholars of crime, race, politics, political economy, social movements, and policing.
@@
 
-Tthe role of fines and fees in the context of felony disenfranchisement has recently garnered national attentiontaken on greater political significance.
-After Floridians passed Amendment 4 voted to restore voting rights to individuals with felony convictions in 2018, Florida Republicans passed legislation requiring these individuals to pay off the fines and fees associated with their original sentence.
+The role of fines and fees in the context of felony disenfranchisement has recently garnered national attention.
+After Floridians passed Amendment 4 to restore voting rights to individuals with felony convictions in 2018, Florida Republicans passed legislation requiring these individuals to pay off the fines and fees associated with their original sentence.
 Because Florida does not maintain good records on who owes how much, this has proved to be a major hurdle for potential voters.
-Despite a dissenting judge arguing that ````{[}h{]}ad Florida wanted to create a system to obstruct, impede, and impair the ability of felons to vote under Amendment 4, it could not have come up with a better one,'' an en bank ruling by the U.S.
+Despite a dissenting judge arguing that ````{[}h{]}ad Florida wanted to create a system to obstruct, impede, and impair the ability of felons to vote under Amendment 4, it could not have come up with a better one,'' an en banc ruling by the U.S.
 Court of Appeals for the 11th Circuit upheld this legislation.\footnote{Jones et al.~v.
@@
 Using existing national survey data and extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
-Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a ``linked fate'' where group members believe that group-level phenomena affect all group members (\protect\hyperlink{ref-Cox2019}{Cox 2019}) of all Black Americans.
-Their interview data lead them to conclude that ``a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing'' --- and interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}).
+Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a ``linked fate'' where ``one's individual opportunities are linked to the entire racial group'' (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014, 267}).
+Their interview data lead them to conclude that while criminal legal contact does increase perceptions of linked fate among Black respondents, ``a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing''---and interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}).
 
@@
 It may be the case that Black and non-Black Americans employ different self-preservation strategies, however.
-Ariel White's analysis of how short jail sentences affect voting in Harris County, Texas found that Black defendant turnout in subsequent elections dropped by 13 percentage points --- but the effect on white turnout was not statistically significant (\protect\hyperlink{ref-White2019}{White 2019}).
-
-Proximal exposure to criminalization --- ``having a loved one who is a custodial citizen without yourself having had contact'' (\protect\hyperlink{ref-Walker2017}{Walker and García-Castañon 2017}) --- also influences Americans' perceptions of government and political behavior, and the emerging literature has produced mixed findings of its effect on civic engagement.
+Ariel White's analysis of how short jail sentences affect voting in Harris County, Texas found that Black defendant turnout in subsequent elections dropped by 13 percentage points---but the effect on white turnout was not statistically significant (\protect\hyperlink{ref-White2019}{White 2019a}).
+
+Proximal exposure to criminalization---``having a loved one who is a custodial citizen without yourself having had contact'' (\protect\hyperlink{ref-Walker2017}{Walker and García-Castañon 2017})---also influences Americans' perceptions of government and political behavior, and the emerging literature has produced mixed findings of its effect on civic engagement.
 Using survey and ethnographic interview data, \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort} (\protect\hyperlink{ref-Lee2014}{2014}) found that adult children of incarcerated parents are less likely to vote, report lower trust in government, and are less likely to engage in other prosocial behaviors like community service.
@@
 Hannah Walker's research specifically tests differences between the effects of proximal and personal criminal legal contact on political behavior, and her findings underscore how a ``linked fate'' political analysis could catalyze distinct political behavior among Black voters (\protect\hyperlink{ref-Walker2014}{Walker 2014}).
-Using data from a 2012 survey of Washington state residents, she found that as the degree of an individual's proximity to a criminalized person increases, so does their likelihood of participating in political activities (such as voting, signing a petition, volunteering, donating to politicians, etc.).
-Importantly, Walker found that nonwhite people who had experienced \emph{either} proximal or personal contact \emph{at any level of intensity}, including being stopped and questioned by police, were politically mobilized --- and the same held true for whites, but with a much smaller effect size.
+Using data from a 2012 survey of Washington state residents, she found that as the degree of an individual's proximity to a criminalized person increases, so does their likelihood of participating in political activities other than voting (such as signing a petition, volunteering, donating to politicians, etc.).
+With respect to voting, she found that personal contact was demobilizing, while proximal contact had no statistically significant effect.
+
+Importantly, Walker found that nonwhite people who had experienced \emph{either} proximal or personal contact \emph{at any level of intensity}, including being stopped and questioned by police, were mobilized to take part in nonvoting political activity---and the same held true for whites, but with a much smaller effect size.
 Walker theorizes that this finding suggests that nonwhite people view criminalization ``as a form of systemic political threat,'' an analysis comparable to ``linked fate.'' Notably, Walker's survey questions excluded ``minor traffic stops,'' the primary focus of this paper.
 
-Ariel White leveraged administrative court records from Harris County, Texas, to identify voters who lived within individuals who were charged with a misdemeanor offense and arrested, convicted, or jailed (\protect\hyperlink{ref-White2019}{White 2019}).
+Ariel White leveraged administrative court records from Harris County, Texas, to identify voters who lived within individuals who were charged with a misdemeanor offense and arrested, convicted, or jailed (\protect\hyperlink{ref-White2019}{White 2019a}).
 She found that living with someone who was charged but not convicted in the 30 day period preceding an election increased voter turnout by 3 percentage points, whereas ``convicted but not jailed'' decreased turnout by 6 percentage points and ``convicted and jailed'' decreased turnout by 12 percentage points.
-This provides further support for the theory that increasing intensity of criminalization could change the direction of the effect of criminalization on political behavior --- and, in fact, that lower-level contact can mobilize even as higher-level contact demobilizes.
-
-Although geographic or spatial analyses of how criminalization affects political socialization technically move beyond proximal contact as an extant conceptual framework, we argue that geographic proximity should work similarly to social network proximity --- if one neighborhood is heavily policed, people who live in that neighborhood are more likely to have social ties who have experienced policing.
+This provides further support for the theory that increasing intensity of criminalization could change the direction of the effect of criminalization on political behavior---and, in fact, that lower-level contact can mobilize even as higher-level contact demobilizes.
+
+Although geographic or spatial analyses of how criminalization affects political socialization technically move beyond proximal contact as an extant conceptual framework, we argue that geographic proximity should work similarly to social network proximity---if one neighborhood is heavily policed, people who live in that neighborhood are more likely to have social ties who have experienced policing.
 Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level (\protect\hyperlink{ref-Burch2014}{Burch 2014}).
@@
 Over the past few years, scientific understanding of the political effects of more serious interactions with the criminal legal system has grown by leaps and bounds.
-The following table summarizes our understanding of the literature.
-
-Type of criminal legal contact
-Personal contact effect on political behavior (individual level)
-Proximal contact effect on political behavior (social network/geography)
-Stopped
-Weaver and Lerman find chilling effect; Walker finds mobilizing effect
-Laniyonu and Walker find mobilizing effect
-Arrested
-Weaver and Lerman find chilling effect; Walker finds mobilizing effect
-Walker finds mobilizing effect
-Convicted / Supervision
-Burch, Weaver and Lerman find chilling effect; Walker finds mobilizing effect
-Burch, Lee, Sugie, White, and Morris find chilling effect; Walker finds mobilizing effect
-Incarcerated
-Burch, White, Weaver and Lerman find chilling effect; Walker finds mobilizing effect
-Burch, Lee, Sugie, White, and Morris find chilling effect; Walker finds mobilizing effect
+Table \ref{tab:lit-table} summarizes our understanding of the literature.
+As Table \ref{tab:lit-table} makes clear, a large body of research has now demonstrated the negative effects of high-level contact with the criminal legal system on voter turnout.
+Although lower-level stops are far more frequent, our knowledge of their (de)mobilizing effects is under-developed.
 
 \begin{singlespace}
-\begin{table}[H]
-
-\caption{\label{tab:lit-table}\label{tab:lit-table} Summary of Literature}
-\centering
-\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}}
-\toprule
-Type of criminal legal contact & Personal contact effect on political behavior (individual level) & Proximal contact effect on political behavior (social network/geography)\\
-\midrule
-\cellcolor{gray!6}{Stopped} & \cellcolor{gray!6}{Weaver and Lerman find chilling effect; Walker finds mobilizing effect} & \cellcolor{gray!6}{Laniyonu and Walker find mobilizing effect}\\
-Arrested & Weaver and Lerman find chilling effect; Walker finds mobilizing effect & Walker finds mobilizing effect\\
-\cellcolor{gray!6}{Convicted / Supervision} & \cellcolor{gray!6}{Burch, Weaver and Lerman find chilling effect; Walker finds mobilizing effect} & \cellcolor{gray!6}{Burch, Lee, Sugie, White, and Morris find chilling effect; Walker finds mobilizing effect}\\
-Incarcerated & Burch, White, Weaver and Lerman find chilling effect; Walker finds mobilizing effect & Burch, Lee, Sugie, White, and Morris find chilling effect; Walker finds mobilizing effect\\
-\bottomrule
-\end{tabular}
-\end{table}
+\input{../raw_data/lit_tab.tex}
 \end{singlespace}
@@
 The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious.
-Though racist police violence was and is a focal point for many Black Lives Matter actions, local chapters frequently use policing as an entry point into a wider set of demands regarding the material security of Black Americans and their marginalization in American politics --- and these demands affect police practices.
+Though racist police violence was and is a focal point for many Black Lives Matter actions, local chapters frequently use policing as an entry point into a wider set of demands regarding the material security of Black Americans and their marginalization in American politics---and these demands affect police practices.
 One recent study found that census places that saw Black Lives Matter protests experienced a 15 to 20 percent decrease in police killings over the following five year period (\protect\hyperlink{ref-Campbell2021}{Campbell 2021}).
-It's possible that any potentially mobilizing effects of criminal legal contact became stronger in the 2010s --- in other words, Black Lives Matter could have facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis.
+It's possible that any potentially mobilizing effects of criminal legal contact became stronger in the 2010---in other words, Black Lives Matter could have facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis.
 That said, \protect\hyperlink{ref-Laniyonu2019}{Laniyonu} (\protect\hyperlink{ref-Laniyonu2019}{2019}) did demonstrate mobilization in Black neighborhoods before the beginning of the Black Lives Matter movement.
@@
 At the level of federal policy, racial threat and whites' attribution of criminality to Blackness (\protect\hyperlink{ref-Muhammad2010}{Muhammad 2010}) prompted a shift ``from the War on Poverty to the War on Crime'' wherein Black communities' demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration (\protect\hyperlink{ref-Hinton2017}{Hinton 2017}; \protect\hyperlink{ref-Vargas2017a}{Vargas and McHarris 2017}).
-Ruth Wilson Gilmore explains how mid to late 20th-century whites ``demanded that the state become leaner and meaner, except when directed to do otherwise'' --- in other words, Keynesian welfare guarantees were undermined by the racist myth of ``welfare queens'' and supplanted by expanded police power (\protect\hyperlink{ref-Gilmore2007}{Gilmore 2007, 53}).
-
-The 2008 financial crisis solidified the connection between fiscal austerity and policing, prompting a decline in tax revenues that devastated state and local governments --- but law enforcement agencies were largely spared from cuts.
+Ruth Wilson Gilmore explains how mid to late 20th-century whites ``demanded that the state become leaner and meaner, except when directed to do otherwise''---in other words, Keynesian welfare guarantees were undermined by the racist myth of ``welfare queens'' and supplanted by expanded police power (\protect\hyperlink{ref-Gilmore2007}{Gilmore 2007, 53}).
+
+The 2008 financial crisis solidified the connection between fiscal austerity and policing, prompting a decline in tax revenues that devastated state and local governments---but law enforcement agencies were largely spared from cuts.
 At the local level, this means that police budgets today constitute about thirty percent of city budgets nationwide, and cities where residents have lower median incomes dedicate a larger proportion of spending to policing (\protect\hyperlink{ref-Friedman2020}{Friedman 2020}).
@@
 Across the country, city government reliance on fines and fees revenue is associated with larger Black populations (\protect\hyperlink{ref-UnitedStatesCommissiononCivilRights2017}{United States Commission on Civil Rights 2017}).
-Although major urban centers collect high dollar amounts of fines and fees, some of the most egregious ticketing practices measured on a per-capita basis are concentrated in suburbs or smaller cities with municipal courts --- Ferguson being a prominent example (\protect\hyperlink{ref-UnitedStatesDepartmentofJusticeCivilRightsDivision2015}{United States Department of Justice Civil Rights Division 2015}; \protect\hyperlink{ref-Mughan2020}{Mughan 2020}).
+Although major urban centers collect high dollar amounts of fines and fees, some of the most egregious ticketing practices measured on a per-capita basis are concentrated in suburbs or smaller cities with municipal courts---Ferguson being a prominent example (\protect\hyperlink{ref-UnitedStatesDepartmentofJusticeCivilRightsDivision2015}{United States Department of Justice Civil Rights Division 2015}; \protect\hyperlink{ref-Mughan2020}{Mughan 2020}).
 The positive association between cities' reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator, however (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
@@
 city governments found that local fiscal stress was related to increased ``revenue-generating arrests'' (e.g.~arrests involving civil asset forfeiture) and that Black and Hispanic people were arrested at higher rates (\protect\hyperlink{ref-Makowsky2009}{Makowsky and Stratmann 2009}).
-A study of four million North Carolina traffic stops found that fiscal stress caused a decrease in the probability of white drivers being searched, but no decrease for Black drivers (\protect\hyperlink{ref-Shoub2020}{\textbf{Shoub2020?}}).
-This suggests that higher reliance on fines and fees results in government officials and police targeting individuals who hold less political power --- whether those individuals are out-of-state motorists or members of local marginalized communities (\protect\hyperlink{ref-Makowsky2009}{Makowsky and Stratmann 2009}).
+A study of four million North Carolina traffic stops found that fiscal stress caused a decrease in the probability of white drivers being searched, but no decrease for Black drivers (\protect\hyperlink{ref-Shoub2020}{Shoub et al.
+2020}).
+This suggests that higher reliance on fines and fees results in government officials and police targeting individuals who hold less political power---whether those individuals are out-of-state motorists or members of local marginalized communities (\protect\hyperlink{ref-Makowsky2009}{Makowsky and Stratmann 2009}).
 
@@
 By using the racial estimates provided by L2, we can estimate the number of ballots cast by voters of each race in each city.
-Although each voters' race is modeled based on L2's algorithms --- and is not self-reported --- it is possibly incorrect for some voters.
+Although each voters' race is modeled based on L2's algorithms---and is not self-reported---it is possibly incorrect for some voters.
 We assume this does not present a problem when records are aggregated to the municipal level.
@@
 
-\emph{Hypothesis 2: The effect of the city-level relationship between fines and voter turnout is less demobilizing or more mobilizing for Black voters, given the historical and explicit racial injustice narratives used to explain these practices..}
+\emph{Hypothesis 2: The effect of the city-level relationship between fines and voter turnout is less demobilizing or more mobilizing for Black voters, given the historical and explicit racial injustice narratives used to explain these practices.}
 
@@
 Unique voter identification numbers allow us to avoid double-counting voters who are registered in multiple snapshots.
-We each voter's earliest record, and geocode voters to their home census block groups.
+We retain each voter's earliest record, and geocode voters to their home census block groups.
 
@@
 In Table \ref{tab:balance} we present the results of the matching algorithm.
-We manage to reduce between treated and control voters substantially along all observed characteristics with the exception of 2012 turnout.
-However, this is not likely a problem: the turnout of all potential and actual controls were both within 0.1 percentage points of the treatment group's turnout that year.
+We manage to reduce between treated and control voters substantially along all observed characteristics.
 
@@
 
-\caption{\label{tab:baltab-chunk}\label{tab:balance} Balance Table}
+\caption{\label{tab:balance-tab-chunk}\label{tab:balance} Balance Table}
 \centering
 \resizebox{\linewidth}{!}{
-\begin{tabular}[t]{lllll}
+\begin{tabular}[t]{lllllllll}
 \toprule
-Variable & Treated & All Untreated & Actual Controls & Mean Improvement\\
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Means: Unmatched Data} & \multicolumn{2}{c}{Means: Matched Data} & \multicolumn{4}{c}{Percent Improvement} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-9}
+ & Treated & Control & Treated & Control & Mean Diff & eQQ Med & eQQ Mean & eQQ Max\\
 \midrule
-\% White & 49.2\% & 62.3\% & 49.2\% & 99.97\%\\
-\% Black & 23.1\% & 12.7\% & 23.1\% & 99.72\%\\
-\% Latino & 18.8\% & 16.3\% & 18.8\% & 99.83\%\\
-\% Asian & 2.2\% & 2.7\% & 2.2\% & 97.90\%\\
-\% Male & 50.8\% & 43.1\% & 50.7\% & 98.29\%\\
-\% Democrat & 42.0\% & 37.6\% & 42.2\% & 93.45\%\\
-\% Republican & 24.6\% & 31.4\% & 24.0\% & 91.52\%\\
-Age & 43.42 & 51.88 & 43.37 & 99.40\%\\
-Registration Date & 2006-06-27 & 2004-08-08 & 2006-07-06 & 98.65\%\\
-Stops Prior to 2012 Election & 1.31 & 0.36 & 1.31 & 99.82\%\\
-Turnout in 2010 & 20.8\% & 27.2\% & 20.7\% & 97.98\%\\
-Turnout in 2012 & 47.1\% & 45.5\% & 47.1\% & 99.14\%\\
-Median Income & \$63,885 & \$67,952 & \$63,757 & 96.85\%\\
-\% with Some College & 74.6\% & 76.6\% & 74.8\% & 90.88\%\\
-Unemployment Rate & 6.5\% & 5.8\% & 6.4\% & 92.64\%\\
+\%White & 49.2\% & 49.5\% & 49.2\% & 49.2\% & 82.05 & 82.05 & 82.05 & 82.05\\
+\% Black & 23.1\% & 21.0\% & 23.1\% & 23.2\% & 92.48 & 92.48 & 92.48 & 92.48\\
+\% Latino & 18.8\% & 20.0\% & 18.8\% & 19.0\% & 79.27 & 79.27 & 79.27 & 79.27\\
+\% Asian & 2.2\% & 2.4\% & 2.2\% & 2.2\% & 98.45 & 98.45 & 98.45 & 98.45\\
+\% Male & 50.8\% & 49.8\% & 50.8\% & 50.8\% & 99.80 & 99.80 & 99.80 & 99.80\\
+\% Democrat & 42.0\% & 40.2\% & 42.0\% & 42.1\% & 92.87 & 92.87 & 92.87 & 92.87\\
+\% Republican & 24.6\% & 24.7\% & 24.6\% & 24.6\% & 100.00 & 100.00 & 100.00 & 100.00\\
+Age & 43.4 & 42.4 & 43.4 & 42.8 & 41.67 & -263.67 & 38.10 & 73.02\\
+Registration Date & 2006-06-27 & 2007-09-21 & 2006-06-27 & 2006-11-09 & 69.91 & 37.60 & 73.79 & 74.70\\
+Pre-2012 Tickets & 1.3 & 0.8 & 1.3 & 1.3 & 95.12 & 93.14 & 95.12 & 96.30\\
+Turnout\textsubscript{t=-3} & 33.2\% & 27.7\% & 33.2\% & 33.2\% & 99.99 & 99.99 & 99.99 & 99.99\\
+Turnout\textsubscript{t=-2} & 29.0\% & 25.9\% & 29.0\% & 29.0\% & 100.00 & 100.00 & 100.00 & 100.00\\
+Turnout\textsubscript{t=-1} & 47.1\% & 37.7\% & 47.1\% & 47.1\% & 99.89 & 99.89 & 99.89 & 99.89\\
+Median Income & \$63,885 & \$64,604 & \$63,885 & \$63,470 & 42.40 & 7.10 & -10.35 & -32.49\\
+\% with Some College & 74.6\% & 75.0\% & 74.6\% & 74.7\% & 67.33 & 27.90 & 29.43 & 15.52\\
+Unemployment Rate & 6.5\% & 6.3\% & 6.5\% & 6.3\% & -40.04 & -226.05 & -158.07 & -108.94\\
 \bottomrule
@@
 We expected that the ticket would be more salient for individuals stopped shortly before the election.
-This appears to be the case --- \emph{especially for Black voters.}
+This appears to be the case---\emph{especially for Black voters.}
 
@@
 \begin{singlespace}
-\input{"../temp/dind_reg.tex"}
+\input{"../temp/dind_reg_y.tex"}
 \end{singlespace}
 
-Model 3 indicates that a ticket is neither mobilizing nor demobilizing --- the coefficient is small and nonsignificant (\emph{p} = 0.34) but that tickets do mobilize Black voters.
+Model 3 indicates that a ticket is neither mobilizing nor demobilizing---the coefficient is small and nonsignificant (\emph{p} = 0.34) but that tickets do mobilize Black voters.
 Receiving a ticket increases the average turnout for Black voters in the first two elections by about 1.1 percentage points.
@@
 
-{[}Tampa - local figure/table{]}
-
-{[}Tampa local analysis{]}
-
 \hypertarget{discussion}{%
@@
 
-{[}Particularly following the rise of the Black Lives Matter movement in 2013, our findings are consistent with the theory that Black voters interpret exploitative police practices as a threat to the wellbeing of all Black Americans.{]}
+Particularly following the rise of the Black Lives Matter movement in 2013, our findings are consistent with the theory that Black voters interpret exploitative police practices as a threat to the wellbeing of all Black Americans.
 
@@
 
+That said, \protect\hyperlink{ref-Sances2017}{Sances and You} (\protect\hyperlink{ref-Sances2017}{2017}) specifically note that they didn't exploit the panel setup of the COG because of little variation between the 2007-2012 COG to the 2012-2017 one, and so they just stuck to cross sectional.
+The positive effect for Black turnout in Figure 1 is consistent with our Tampa analysis and doesn't totally contradict the TWFE.
+
 \textbf{Limitations}: Because our individual-level analysis is limited to Hillsborough County, we don't have a good idea of whether the city-level revenue reliance trend interacts with the individual experience of being ticketed.
@@
 \textbf{Future research}: Unlike previous studies using survey data, we are unable to tell whether individuals in Tampa have non-ticketing criminal legal exposure.
-Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.{]}
-
-{[}Laniyonu{]} - {[}he writes that block groups with higher Black pop and higher SQF density voted at higher rates for Thompson, the candidate who pledged not to implement SQF reform, but who was Black.
-The descriptive representation from Sances2017 kind of covers for this, tactically speaking - electing Black politicians should reduce fines and fees abuses.
-But in Tampa, the current mayor, Jane Castor, was the police chief until 2015 --- which overlaps with the treatment period in our analysis.
-One voter told the Tampa Bay Times that he voted against Castor as ``payback'' for the racist ticketing practices she oversaw, and the article notes that her opponent won five majority-Black precincts (\protect\hyperlink{ref-Frago2019}{Frago 2019}).
-In 2015, Castor even released a statement as police chief supporting the racist ticketing, insisting that ``Many individuals receiving bike citations are involved in criminal activity.''
+Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.
 
@@
 
+\leavevmode\hypertarget{ref-Burch2011}{}%
+Burch, Traci R.
+2011.
+{``Turnout and {Party Registration} Among {Criminal Offenders} in the 2008 {General Election}.''} \emph{Law \& Society Review} 45 (3): 699--730.
+\url{https://doi.org/10.1111/j.1540-5893.2011.00448.x}.
+
+\leavevmode\hypertarget{ref-Burch2013}{}%
+---------.
+2013.
+\emph{Trading Democracy for Justice: Criminal Convictions and the Decline of Neighborhood Political Participation}.
+Chicago Studies in {American} Politics.
+{Chicago ; London}: {The University of Chicago Press}.
+
 \leavevmode\hypertarget{ref-Burch2014}{}%
-Burch, Traci R.
+---------.
 2014.
@@
 Colgan, Beth A. 2019. {``Wealth-{Based Penal Disenfranchisement}.''} \emph{Vanderbilt Law Review} 72 (January). \url{https://papers.ssrn.com/abstract=3312439}.
-
-\leavevmode\hypertarget{ref-Cox2019}{}%
-Cox, Kiana.
-2019.
-{``Most {U}.{S}.
-Adults Feel What Happens to Their Own Racial or Ethnic Group Affects Them Personally.''} {Pew Research Center}.
-July 11, 2019.
-\url{https://www.pewresearch.org/fact-tank/2019/07/11/linked-fate-connectedness-americans/}.
 
@@
 
+\leavevmode\hypertarget{ref-Shoub2020}{}%
+Shoub, Kelsey, Leah Christiani, Frank R.
+Baumgartner, Derek A.
+Epp, and Kevin Roach.
+2020.
+{``Fines, {Fees}, {Forfeitures}, and {Disparities}: {A Link Between Municipal Reliance} on {Fines} and {Racial Disparities} in {Policing}.''} \emph{Policy Studies Journal}.
+\url{https://doi.org/10.1111/psj.12412}.
+
 \leavevmode\hypertarget{ref-Singla2020}{}%
@@
 White, Ariel.
-2019.
+2019a.
 {``Family {Matters}?
@@
 \url{https://doi.org/10.1017/S0003055418000862}.
+
+\leavevmode\hypertarget{ref-White2019a}{}%
+---------.
+2019b.
+{``Misdemeanor {Disenfranchisement}?
+{The Demobilizing Effects} of {Brief Jail Spells} on {Potential Voters}.''} \emph{American Political Science Review} 113 (2): 311--24.
+\url{https://doi.org/10.1017/S000305541800093X}.
 

### 2021-03-28 markdown/draft_paper.Rmd
write

@@
 
-Before testing the causal effect of fees and fines collections, we begin with a cross-sectional analysis of the relationship between fees and fines and turnout.
+Before testing the causal effect of fees and fines collections, we begin with a cross-sectional analysis of the relationship between fees and fines and turnout using ordinary least squares.
 Here, we regress municipality-level turnout in 2018 against fees and fines collections as reported in the 2017 COG, as well as a number of other covariates.
@@
 
-```{r cross-18, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:mef-2018}Marginal Effect of per-capita Fees and Fines on Turnout, 2018", fig.pos = "H", fig.align = "center"}
+```{r cross-18, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:mef-2018}Predicted Turnout, 2018", fig.pos = "H", fig.align = "center"}
 load("temp/mef_to.rdata")
@@
 ```{r balance-tab-chunk, echo = F}
-t <- readRDS("./temp/balance_table_y.rds")
+t <- readRDS("temp/balance_table_y.rds")
 j <- knitr::kable(t, booktabs = T, caption = "(\\#tab:balance) Balance Table", linesep = "",

### 2021-03-28 markdown/draft_paper.tex
write

@@
 \author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
-\date{March 19, 2021}
+\date{March 25, 2021}
 
@@
 
-\caption{\label{fig:mef-2018}Marginal Effect of per-capita Fees and Fines on Turnout, 2018}\label{fig:cross-18}
+\caption{\label{fig:mef-2018}Predicted Turnout, 2018}\label{fig:cross-18}
 \end{figure}
@@
 \midrule
-\%White & 49.2\% & 49.5\% & 49.2\% & 49.2\% & 82.05 & 82.05 & 82.05 & 82.05\\
-\% Black & 23.1\% & 21.0\% & 23.1\% & 23.2\% & 92.48 & 92.48 & 92.48 & 92.48\\
-\% Latino & 18.8\% & 20.0\% & 18.8\% & 19.0\% & 79.27 & 79.27 & 79.27 & 79.27\\
-\% Asian & 2.2\% & 2.4\% & 2.2\% & 2.2\% & 98.45 & 98.45 & 98.45 & 98.45\\
-\% Male & 50.8\% & 49.8\% & 50.8\% & 50.8\% & 99.80 & 99.80 & 99.80 & 99.80\\
-\% Democrat & 42.0\% & 40.2\% & 42.0\% & 42.1\% & 92.87 & 92.87 & 92.87 & 92.87\\
-\% Republican & 24.6\% & 24.7\% & 24.6\% & 24.6\% & 100.00 & 100.00 & 100.00 & 100.00\\
-Age & 43.4 & 42.4 & 43.4 & 42.8 & 41.67 & -263.67 & 38.10 & 73.02\\
-Registration Date & 2006-06-27 & 2007-09-21 & 2006-06-27 & 2006-11-09 & 69.91 & 37.60 & 73.79 & 74.70\\
-Pre-2012 Tickets & 1.3 & 0.8 & 1.3 & 1.3 & 95.12 & 93.14 & 95.12 & 96.30\\
-Turnout\textsubscript{t=-3} & 33.2\% & 27.7\% & 33.2\% & 33.2\% & 99.99 & 99.99 & 99.99 & 99.99\\
-Turnout\textsubscript{t=-2} & 29.0\% & 25.9\% & 29.0\% & 29.0\% & 100.00 & 100.00 & 100.00 & 100.00\\
-Turnout\textsubscript{t=-1} & 47.1\% & 37.7\% & 47.1\% & 47.1\% & 99.89 & 99.89 & 99.89 & 99.89\\
-Median Income & \$63,885 & \$64,604 & \$63,885 & \$63,470 & 42.40 & 7.10 & -10.35 & -32.49\\
-\% with Some College & 74.6\% & 75.0\% & 74.6\% & 74.7\% & 67.33 & 27.90 & 29.43 & 15.52\\
-Unemployment Rate & 6.5\% & 6.3\% & 6.5\% & 6.3\% & -40.04 & -226.05 & -158.07 & -108.94\\
+\%White & 45.8\% & 47.4\% & 45.8\% & 45.8\% & 99.70 & 99.70 & 99.70 & 99.70\\
+\% Black & 26.1\% & 23.0\% & 26.1\% & 26.1\% & 99.85 & 99.85 & 99.85 & 99.85\\
+\% Latino & 19.1\% & 20.2\% & 19.1\% & 19.1\% & 99.97 & 99.97 & 99.97 & 99.97\\
+\% Asian & 2.0\% & 2.3\% & 2.0\% & 2.0\% & 100.00 & 100.00 & 100.00 & 100.00\\
+\% Male & 51.9\% & 50.8\% & 51.9\% & 51.2\% & 36.61 & 36.46 & 36.46 & 36.46\\
+\% Democrat & 43.6\% & 41.6\% & 43.6\% & 43.3\% & 86.44 & 86.44 & 86.44 & 86.44\\
+\% Republican & 22.9\% & 23.7\% & 22.9\% & 22.0\% & -5.57 & -5.57 & -5.57 & -5.57\\
+Age & 42.7 & 42.4 & 42.7 & 42.2 & -67.69 & 11.98 & 33.08 & 70.35\\
+Registration Date & 2006-09-25 & 2007-08-20 & 2006-09-25 & 2006-10-21 & 92.30 & 60.54 & 91.16 & 93.26\\
+Stops in pre-period & 2.248 & 1.437 & 2.248 & 2.206 & 94.79 & 69.37 & 94.81 & 95.91\\
+Turnout\textsubscript{t=-3} & 32.4\% & 28.4\% & 32.4\% & 32.5\% & 97.59 & 97.59 & 97.59 & 97.59\\
+Turnout\textsubscript{t=-2} & 30.2\% & 27.5\% & 30.2\% & 30.2\% & 99.94 & 99.94 & 99.94 & 99.94\\
+Turnout\textsubscript{t=-1} & 45.0\% & 38.2\% & 45.0\% & 45.0\% & 99.97 & 99.97 & 99.97 & 99.97\\
+Median Income & \$62,193 & \$63,412 & \$62,193 & \$62,111 & 93.27 & 82.89 & 79.16 & 68.07\\
+\% with Some College & 73.8\% & 74.4\% & 73.8\% & 73.9\% & 78.57 & 53.38 & 57.55 & 53.15\\
+Unemployment Rate & 6.7\% & 6.5\% & 6.7\% & 6.6\% & 49.02 & -19.29 & -20.95 & -17.34\\
 \bottomrule

### 2021-04-07 code/hills/mayor/01_download_hills_stops_mayor.R
start mayor match analyses

@@ -1,0 +1,279 @@
+# setwd("E:\\R WORKING DIRECTORY E")
+# 
+# hills_stops <- rbindlist(lapply(c(2003:2021), function(l){
+#   print(l)
+#   if(l != "J"){
+#     if(!(file.exists(paste0("raw_data/hills_stops/civil_stops_", l, ".csv")))){
+#       download.file(paste0("https://publicrec.hillsclerk.com/Traffic/Civil_Traffic_Name_Index_files/Civil_Traffic_Name_Index_", l, ".csv"),
+#                     paste0("raw_data/hills_stops/civil_stops_", l, ".csv"))
+#     }
+#     
+#     ja <- fread(paste0("raw_data/hills_stops/civil_stops_", l, ".csv"))
+#     
+#     colnames(ja) <- clean_names(ja)
+#     
+#     ja <- ja %>%
+#       filter(!grepl("cam", tolower(statute_description))) %>%
+#       select(last_name, first_name, middle_name,
+#              date_of_birth,
+#              street = address_line_1,
+#              city,
+#              state,
+#              zip = zip_code,
+#              offense_date,
+#              amount_paid) %>%
+#       mutate(civil = 1)
+#     
+#     return(ja)
+#   }
+# }))
+# 
+# hills_stops_cr <- rbindlist(lapply(c(2003:2021), function(l){
+#   print(l)
+#   if(l != "J"){
+#     if(!(file.exists(paste0("raw_data/hills_stops/crim_stops_", l, ".csv")))){
+#       download.file(paste0("https://publicrec.hillsclerk.com/Traffic/Criminal_Traffic_Name_Index_files/Criminal_Traffic_Name_Index_", l, ".csv"),
+#                     paste0("raw_data/hills_stops/crim_stops_", l, ".csv"))
+#     }
+#     
+#     ja <- fread(paste0("raw_data/hills_stops/crim_stops_", l, ".csv"))
+#     
+#     colnames(ja) <- clean_names(ja)
+#     
+#     ja <- ja %>%
+#       select(last_name, first_name, middle_name,
+#              date_of_birth,
+#              offense_date, amount_paid) %>%
+#       mutate(civil = 0)
+#     
+#     return(ja)
+#   }
+# }))
+# hills_stops <- bind_rows(hills_stops, hills_stops_cr) %>%
[…]

### 2021-04-07 code/hills/mayor/02_genmatch_weights_mayor.R

@@ -1,0 +1,71 @@
+
+## needs to be run on nyu hpc or its way too slow
+## set seed for reproducibility. this is a random 5-digit number: floor(runif(1, min = 10000, max = 99999))
+set.seed(45251)
+
+library(Matching)
+library(data.table)
+library(scales)
+library(kableExtra)
+library(tidyverse)
+require(snow)
+require(parallel)
+
+
+Sys.info()
+
+NodeFile = Sys.getenv("MY_HOSTFILE")
+
+print(NodeFile)
+
+readLines(NodeFile)
+
+cl<-makeCluster(c(readLines(NodeFile)), type="SOCK")
+cl
+
+hills_pre_match <- readRDS("temp/hills_pre_match_mayor.rds")
+
+##############################################
+
+hills15_t <- filter(hills_pre_match, first_tr_year == "2015-03-03") %>% 
+  mutate(treated = last_date <= "2015-03-03",
+         first_tr_year = 1) %>% 
+  rename(v1 = v07,
+         v2 = v11)
+
+############## 2019
+
+hills19_t <- filter(hills_pre_match, first_tr_year == "2019-03-05") %>% 
+  mutate(treated = last_date <= "2019-03-05",
+         first_tr_year = 2) %>% 
+  rename(v1 = v11,
+         v2 = v15)
+
+###########################################
+pre <- bind_rows(hills15_t, hills19_t)
+
+
+###########################################
+pre <- bind_rows(hills15_t, hills19_t)
+
+samp <- pre %>% 
+  group_by(treated, first_tr_year) %>% 
+  sample_frac(0.05) %>% 
+  ungroup()
+
+match_data <- samp %>% 
+  select(-voter_id, -treated, -GEOID, -amount_paid, -last_date,
+         -pre, -v15, -v19, -v07) %>% 
+  mutate_at(vars(white, black, latino, asian, male, dem, rep, v1, v2, paid), ~ ifelse(. == T, 1, 0)) %>% 
+  mutate(reg_date = as.integer(reg_date)) %>% 
+  select(first_tr_year, paid, civil, everything())
+
+
+match_data <- match_data[complete.cases(match_data), ]
+
+genout <- GenMatch(Tr = samp$treated, X = match_data, replace = T, pop.size = 1000,
+                   exact = c(rep(T, 3), rep(F, 17)), cluster = cl)
+
+saveRDS(genout, "temp/genout_hills_y_mayor.rds")
+
+

### 2021-04-07 code/hills/mayor/03_match_mayor.R

@@ -1,0 +1,84 @@
+
+## needs to be run on nyu hpc or its way too slow
+## set seed for reproducibility. this is a random 5-digit number: floor(runif(1, min = 10000, max = 99999))
+set.seed(45251)
+
+library(Matching)
+library(data.table)
+library(scales)
+library(kableExtra)
+library(tidyverse)
+require(snow)
+require(parallel)
+
+
+hills_pre_match <- readRDS("temp/hills_pre_match_mayor.rds")
+
+##############################################
+
+hills15_t <- filter(hills_pre_match, first_tr_year == "2015-03-03") %>% 
+  mutate(treated = last_date <= "2015-03-03",
+         first_tr_year = 1) %>% 
+  rename(v1 = v07,
+         v2 = v11)
+
+############## 2019
+
+hills19_t <- filter(hills_pre_match, first_tr_year == "2019-03-05") %>% 
+  mutate(treated = last_date <= "2019-03-05",
+         first_tr_year = 2) %>% 
+  rename(v1 = v11,
+         v2 = v15)
+
+###########################################
+pre <- bind_rows(hills15_t, hills19_t)
+saveRDS(pre, "temp/real_pre_match_hills_mayor.rds")
+
+ids <- pre %>%
+  mutate(id = row_number()) %>%
+  select(id, voter_id, first_tr_year)
+
+X <- pre %>%
+  select(-voter_id, -treated, -GEOID, -amount_paid, -last_date,
+         -pre, -v15, -v19, -v07) %>% 
+  mutate_at(vars(white, black, latino, asian, male, dem, rep, v1, v2, paid), ~ ifelse(. == T, 1, 0)) %>% 
+  mutate(reg_date = as.integer(reg_date)) %>% 
+  select(first_tr_year, paid, civil, everything())
+
+
+genout <- readRDS("temp/genout_hills_y_mayor.rds")
+
+mout <- Matchby(Tr = pre$treated, X = X,
+                by = c(X$first_tr_year,
+                       X$white,
+                       X$black,
+                       X$latino,
+                       X$asian,
+                       X$male,
+                       X$dem,
+                       X$rep), estimand = "ATT", Weight.matrix = genout, M = 1, ties = T,
+                exact = c(rep(T, 3), rep(F, 17)))
+
+
+save(mout, file = "./temp/mout_hills_y_mayor.RData")
+
+load("temp/mout_hills_y_mayor.RData")
+
[…]

### 2021-04-07 code/hills/mayor/04_mayor_reg.R

@@ -1,0 +1,121 @@
+
+#####
+hills_pre_match <- readRDS("temp/real_pre_match_hills_mayor.rds") %>% 
+  ungroup()
+
+matches <- readRDS("temp/matches_hills_y_mayor.rds")
+
+matches <- left_join(matches, select(hills_pre_match, voter_id, first_tr_year),
+                     by = c("group" = "voter_id", "first_tr_year")) %>% 
+  mutate(fd = first_tr_year,
+         first_tr_year = ifelse(first_tr_year == 1, "2015-03-03",
+                                ifelse(first_tr_year == 2, "2019-03-05", "XX")),
+         first_tr_year = as.Date(first_tr_year))
+
+hist <- readRDS("temp/full_raw_coded_hills_w_bgs.rds") %>%
+  select(voter_id, starts_with("v1"), v08, v07) %>%
+  pivot_longer(!starts_with("vo"), names_to = "year", values_to = "to")
+
+elec_dates <- fread("raw_data/election_dates.csv")
+
+hist <- left_join(hist, elec_dates) %>% 
+  select(-year) %>% 
+  rename(year = date) %>% 
+  mutate(year = as.Date(year, "%m/%d/%Y"))
+
+
+matches <- left_join(matches, hist %>% 
+                       filter(year(year) %% 2 == 1), by = c("voter" = "voter_id"))
+
+periods <- fread("raw_data/period_lu_mayor.csv") %>% 
+  mutate_at(vars(first_tr_year, year), as.Date, "%m/%d/%Y")
+
+matches <- left_join(matches, periods) %>% 
+  filter(period %in% c(-2.5, -1.5, -.5, .5, 1.5))
+
+matches <- left_join(matches,
+                     hills_pre_match %>%
+                       select(-GEOID, -amount_paid, -last_date),
+                     by = c("voter" = "voter_id", "fd" = "first_tr_year"))
+
+matches <- left_join(matches,
+                     hills_pre_match %>%
+                       select(voter_id, amount_paid, last_date, first_tr_year, black_t = black,
+                              dem_t = dem),
+                     by = c("group" = "voter_id", "fd" = "first_tr_year")) %>% 
+  mutate(post = period >= 0.5,
+         treated = voter == group)
+
+cleanup("matches")
+gc()
+ll <- matches %>%
+  filter(first_tr_year - last_date <= 90, period <= 0.5, period >= -1.5) %>%
+  group_by(treated, period, black_t, paid) %>%
+  summarize(to = weighted.mean(to, weight)) %>% 
[…]

### 2021-04-07 markdown/draft_paper.tex
write

@@
 \author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
-\date{March 25, 2021}
+\date{April 07, 2021}
 
@@
 
+\begin{gather}
+\label{eq:1}
+v_{it}=\beta_0+\beta_1Treated_{i}+\beta_2Election Following Stop_{t} + \nonumber \\
+\beta_3Treated_{i}\times Election Following Stop_{t} + \\
+\delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
+\end{gather}
+
 \emph{Hypothesis 3: Among individuals who were ticketed (``treated'') in Tampa, their likelihood of turning out in a subsequent election roughly matches the racioethnic distribution apparent in the national city-level data.
@@
 \midrule
-\%White & 45.8\% & 47.4\% & 45.8\% & 45.8\% & 99.70 & 99.70 & 99.70 & 99.70\\
-\% Black & 26.1\% & 23.0\% & 26.1\% & 26.1\% & 99.85 & 99.85 & 99.85 & 99.85\\
-\% Latino & 19.1\% & 20.2\% & 19.1\% & 19.1\% & 99.97 & 99.97 & 99.97 & 99.97\\
-\% Asian & 2.0\% & 2.3\% & 2.0\% & 2.0\% & 100.00 & 100.00 & 100.00 & 100.00\\
-\% Male & 51.9\% & 50.8\% & 51.9\% & 51.2\% & 36.61 & 36.46 & 36.46 & 36.46\\
-\% Democrat & 43.6\% & 41.6\% & 43.6\% & 43.3\% & 86.44 & 86.44 & 86.44 & 86.44\\
-\% Republican & 22.9\% & 23.7\% & 22.9\% & 22.0\% & -5.57 & -5.57 & -5.57 & -5.57\\
-Age & 42.7 & 42.4 & 42.7 & 42.2 & -67.69 & 11.98 & 33.08 & 70.35\\
-Registration Date & 2006-09-25 & 2007-08-20 & 2006-09-25 & 2006-10-21 & 92.30 & 60.54 & 91.16 & 93.26\\
-Stops in pre-period & 2.248 & 1.437 & 2.248 & 2.206 & 94.79 & 69.37 & 94.81 & 95.91\\
-Turnout\textsubscript{t=-3} & 32.4\% & 28.4\% & 32.4\% & 32.5\% & 97.59 & 97.59 & 97.59 & 97.59\\
-Turnout\textsubscript{t=-2} & 30.2\% & 27.5\% & 30.2\% & 30.2\% & 99.94 & 99.94 & 99.94 & 99.94\\
-Turnout\textsubscript{t=-1} & 45.0\% & 38.2\% & 45.0\% & 45.0\% & 99.97 & 99.97 & 99.97 & 99.97\\
-Median Income & \$62,193 & \$63,412 & \$62,193 & \$62,111 & 93.27 & 82.89 & 79.16 & 68.07\\
-\% with Some College & 73.8\% & 74.4\% & 73.8\% & 73.9\% & 78.57 & 53.38 & 57.55 & 53.15\\
-Unemployment Rate & 6.7\% & 6.5\% & 6.7\% & 6.6\% & 49.02 & -19.29 & -20.95 & -17.34\\
+\%White & 47.3\% & 49.1\% & 47.3\% & 47.4\% & 97.14 & 97.14 & 97.14 & 97.14\\
+\% Black & 24.4\% & 21.0\% & 24.4\% & 24.4\% & 99.93 & 99.93 & 99.93 & 99.93\\
+\% Latino & 19.1\% & 20.2\% & 19.1\% & 19.5\% & 61.05 & 61.06 & 61.06 & 61.06\\
+\% Asian & 2.1\% & 2.4\% & 2.1\% & 2.1\% & 99.55 & 99.55 & 99.55 & 99.55\\
+\% Male & 53.2\% & 52.4\% & 53.2\% & 53.8\% & 19.36 & 19.66 & 19.66 & 19.66\\
+\% Democrat & 42.5\% & 40.0\% & 42.5\% & 42.4\% & 97.61 & 97.61 & 97.61 & 97.61\\
+\% Republican & 23.6\% & 24.5\% & 23.6\% & 23.2\% & 54.62 & 54.62 & 54.62 & 54.62\\
+Age & 42.3 & 41.5 & 42.3 & 41.8 & 36.76 & -135.34 & 29.65 & 71.41\\
+Registration Date & 2006-11-05 & 2007-12-11 & 2006-11-05 & 2007-01-04 & 84.91 & 78.16 & 79.83 & 72.00\\
+Stops in pre-period & 2.163 & 1.433 & 2.163 & 2.125 & 94.77 & 53.17 & 94.78 & 97.18\\
+Turnout\textsubscript{t=-3} & 31.9\% & 27.4\% & 31.9\% & 31.9\% & 99.89 & 99.89 & 99.89 & 99.89\\
+Turnout\textsubscript{t=-2} & 29.3\% & 26.7\% & 29.3\% & 29.3\% & 99.87 & 99.87 & 99.87 & 99.87\\
+Turnout\textsubscript{t=-1} & 44.9\% & 37.5\% & 44.9\% & 44.9\% & 99.85 & 99.85 & 99.85 & 99.85\\
+Median Income & \$62,832 & \$64,169 & \$62,832 & \$62,642 & 85.81 & 71.32 & 67.46 & 55.93\\
+\% with Some College & 73.9\% & 74.5\% & 73.9\% & 74.0\% & 88.43 & 46.05 & 53.04 & 45.74\\
+Unemployment Rate & 6.6\% & 6.4\% & 6.6\% & 6.5\% & 29.50 & -25.47 & -14.60 & -3.97\\
 \bottomrule

### 2021-04-19 markdown/draft_paper.Rmd
write
lots of changes

@@
 ---
-title: "Policing for Profit and the Mobilization of Black Voters"
-subtitle: "Fines, Fees, and Turnout"
+title: "Policing for Profit and the Undermining of Democracy"
+
 author:
@@
 abstract: |
-  The American criminal legal system is an important site of political socialization: sociologists show how the alienating effect of criminalization manifests as systems avoidance, and political scientists have measured the effects of policing and incarceration on political participation.
+  The American criminal legal system is an important site of political socialization: sociologists show how the alienating effect of criminalization pushes people away from public institutions, and political scientists have measured the effects of policing and incarceration on political participation.
 Despite this burgeoning literature, no research has directly investigated how ticketing for low-level offenses affects political participation.
-Using data from the Census of Governments and the national voter file, we test the causal effect of fines and fees practices on American voting behavior at the city level.
+Using data from the Census of Governments and the national voter file, we test the causal effect of fines and fees practices on American voting behavior at the city level (aggregate).
 Additionally, we exploit individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019 to determine whether getting a ticket impacts political participation.
-Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.6 percentage point decrease in non-Black turnout but was not associated with Black turnout.
-In Tampa, Florida, we estimate that being ticketed increases a non-Black individual’s likelihood of voting by 3.7 percentage points, and that the effect is larger for Black voters.
-
+Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.6 percentage point turnout decrease but was not associated with Black turnout.
+In Tampa, Florida, we estimate that being ticketed decreases an individual’s likelihood of voting in federal elections by 1.3 percentage points, but we do not uncover evidence of a distinct political effect for Black voter turnout.
+In local elections, however,
   |
@@
 Work exploring how criminalization directly and indirectly influences political participation has exploded in recent years.
+Scholars have found that criminal legal contact (i.e.
+arrest, conviction, incarceration) consistently discourages voting [@Weaver2010; @Burch2011; @White2019a].
 This work, however, has largely focused on the effects of highly consequential contact with the criminal legal system such as incarceration and felony convictions [@Burch2014; @Lee2014].
-Although some work has leveraged survey data and qualitative approaches to interrogate lower-level police interactions---such as ticketing---our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
+Our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
+
+The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures participation.
+Past work looking at the individual-level effects of low-level contact has relied entirely on survey or qualitative data [e.g.
+@Walker2014; @Weaver2010].
+Their in-depth research allows for the testing of specific psychological mechanisms and personal interpretations of criminal legal contact, but does not allow us to generalize more broadly.
+As Weaver and Lerman [-@Weaver2010, page 821] note, it may also introduce measurement bias.
+Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to police ticketing.
+The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of the 232,568 individuals ticketed over a 6 year period---a far larger pool than even the most robust surveys.
+
 We begin by joining fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for each municipality in the country.
@@
 
-After exploring national data, we use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were ticketed between the 2012 and 2018 elections.
-By matching individuals who were ticketed to other, similar voters who were not ticketed and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout.
-Using self-reported race from the Florida registered voter file, we identify large, *positive* treatment effects for all voters---effects that were especially large for Black voters..
+Because our national analysis does not allow us to directly observe the causal effect of police ticketing on voter turnout, we use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were ticketed between the 2012 and 2018 elections.
+By matching individual voters who were ticketed to similar voters who were ticketed at later points and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout.
+We find that being ticketed reduces the chance that an individual will turn out in the subsequent election.
 
-We demonstrate that police ticketing practices---the most widespread form of police contact in America---influence the political behavior of Americans, with distinct effects for Black and non-Black voters.
-This finding supports and extends Hannah Walker’s theory of criminal legal contact is mobilizing / less demobilizing for nonwhite political participation [@Walker2020; @Walker2014].
-Our results also complicate Vesla Weaver and Amy Lerman’s theory of low-level criminal legal contact discouraging political participation [@Weaver2010].
+We demonstrate that police ticketing practices---the most widespread form of police contact in America---influence the political behavior of Americans.
+This finding supports and extends Vesla Weaver and Amy Lerman’s theory of criminal legal contact discouraging political participation [@Weaver2010].
 Our findings are relevant for interdisciplinary scholars of crime, race, politics, political economy, social movements, and policing.
@@
 
-Sociologists have incorporated contemporary fines and fees practices into a broader empirical-historical theory of racialized punishment policy [@Harris2010; @Friedman2020].
-Additionally, an emerging political science literature directly investigates the relationship between criminalization and political behavior.
+An emerging political science literature directly investigates the relationship between criminalization and political behavior.
+Additionally, sociologists have incorporated contemporary fines and fees practices into a broader empirical-historical theory of racialized punishment policy [@Harris2010; @Friedman2020].
 
@@
 In Alabama, for example, Black people with felony convictions applying to have their voting rights restored were 26 percentage points more likely to have their application denied over outstanding fines and fees [@Meredith2017].
-
-Another process by which criminalization shapes the electorate is “prison gerrymandering,” or the practice of counting incarcerated people as residing in the district where their prison is located for the purposes of creating electoral districts.
-This practice inflates the voting power of rural and white voters while diminishing the power of urban, Black, and Latino voters [@Remster2018].
 
@@
 Using existing national survey data and extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) [@Weaver2010].
-Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a “linked fate” where “one’s individual opportunities are linked to the entire racial group” [@Lerman2014, page 267].
+Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a “linked fate” where “one’s individual opportunities are linked to the entire racial group” [@Lerman2014, page 197].
 Their interview data lead them to conclude that while criminal legal contact does increase perceptions of linked fate among Black respondents, “a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing”---and interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation [@Lerman2014].
@@
 It may be the case that Black and non-Black Americans employ different self-preservation strategies, however.
-Ariel White’s analysis of how short jail sentences affect voting in Harris County, Texas found that Black defendant turnout in subsequent elections dropped by 13 percentage points---but the effect on white turnout was not statistically significant [@White2019].
+@Walker2020 makes clear that, when Black Americans locate their contact with the criminal legal system in a narrative of racial injustice, they can be politically mobilized; on the other hand, @Lerman2014 shows that Black individuals’ ability to situate their life experiences in a larger legacy of exploitation can be demobilizing.
+Turning to administrative data analysis, Ariel White’s analysis of how short jail sentences affect voting in Harris County, Texas found that Black defendant turnout in subsequent elections dropped by 13 percentage points---but the effect on white turnout was not statistically significant [@White2019].
 
@@
 
-Importantly, Walker found that nonwhite people who had experienced *either* proximal or personal contact *at any level of intensity*, including being stopped and questioned by police, were mobilized to take part in nonvoting political activity---and the same held true for whites, but with a much smaller effect size.
-Walker theorizes that this finding suggests that nonwhite people view criminalization “as a form of systemic political threat,” an analysis comparable to “linked fate.” Notably, Walker’s survey questions excluded “minor traffic stops,” the primary focus of this paper.
+Walker found that nonwhite people who had experienced *either* proximal or personal contact *at any level of intensity*, including being stopped and questioned by police, were mobilized to take part in nonvoting political activity---and the same held true for whites, but with a much smaller effect size.
+Walker theorizes that this finding suggests that nonwhite people view criminalization “as a form of systemic political threat,” an analysis comparable to “linked fate.” Additionally, Walker’s survey questions excluded “minor traffic stops,” the primary focus of this paper.
 
@@
 
-Although geographic or spatial analyses of how criminalization affects political socialization technically move beyond proximal contact as an extant conceptual framework, we argue that geographic proximity should work similarly to social network proximity---if one neighborhood is heavily policed, people who live in that neighborhood are more likely to have social ties who have experienced policing.
+Although geographic or spatial analyses of how criminalization affects political socialization technically move beyond proximal contact as an extant conceptual framework, similar mechanisms should operate on the neighborhood level.
 Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level [@Burch2014].
@@
 Over the past few years, scientific understanding of the political effects of more serious interactions with the criminal legal system has grown by leaps and bounds.
-Table \ref{tab:lit-table} summarizes our understanding of the literature.
-As Table \ref{tab:lit-table} makes clear, a large body of research has now demonstrated the negative effects of high-level contact with the criminal legal system on voter turnout.
+The following table summarizes our understanding of the literature.
+As the table makes clear, a large body of research has now demonstrated the negative effects of high-level contact with the criminal legal system on voter turnout.
 Although lower-level stops are far more frequent, our knowledge of their (de)mobilizing effects is under-developed.
@@
 
-Apart from the fact that no prior work has directly investigated the relationship between police ticketing practices and political behavior, we argue that fines and fees invoke a distinct historical legacy of racist exploitation that merits further study.
+We argue that fines and fees invoke a distinct historical legacy of racist exploitation that merits further study.
 
@@
 Racial capitalist political economy imposes fiscal constraints regardless of city officials’ intentions.
-In their study of fines and fees reliance in Chicago suburbs, Josh Pacewicz and John Robinson, III show how the racialization of municipal opportunity structures prevents majority-Black suburban governments from acquiring sufficient revenue from “good” sources such as sales taxes or property taxes, catalyzing a reliance on fines and fees to fund essential government services [@Pacewicz2020].
-Importantly, Pacewicz and Robinson III note that these racialized municipal opportunity structures are tied to the political-historical processes of neoliberalism and fiscal austerity, an observation that aligns with recent scholarship detailing the origins of fees paid by incarcerated people [@Kirk2020].
+In their study of fines and fees reliance in Chicago suburbs, Josh Pacewicz and John Robinson, III show how the racialization of municipal opportunity structures prevents majority-Black suburban governments from acquiring sufficient revenue from “good” sources such as sales taxes or property taxes, catalyzing a reliance on fines and fees to fund government services [@Pacewicz2020].
+Pacewicz and Robinson III note that these racialized municipal opportunity structures are tied to the political-historical processes of neoliberalism and fiscal austerity, an observation that aligns with recent scholarship detailing the origins of fees paid by incarcerated people [@Kirk2020].
 The late 20th century “property tax revolt” most significantly benefited white homeowners [@Martin2017], and without property tax hikes as a revenue-raising option, smaller cities and towns have few choices.
@@
 With this history in mind, we argue that Black Americans can situate exploitative ticketing practices in a longer historical legacy of collective disparate treatment and violence at the hands of the state, which may facilitate a stronger collective political analysis when police ticketing practices become more extreme.
-@Walker2020 makes clear that, when Black Americans locate their contact with the criminal legal system in a narrative of racial injustice, they can be mobilized to vote.
 The historical use of fees and fines make this sort of police contact especially likely to evoke such narratives.
@@
 **Census of Governments**: Every five years, the US Census Bureau collects data from governmental bodies around the country.
-We use two snapshots of the COG: one that covers the years 2008 - 2012, and another that covers 2013 - 2017.
-The COG includes a host of information about state and municipal finances.
+We use two snapshots of the COG: one that covers the years 2008 -- 2012, and another that covers 2013 -- 2017.
 The COG asks municipalities to report how much revenue they collect from “penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation...
-and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).” This data has been used as a proxy for the amount of tickets issued at the local level in scholarly research [see, for instance, @Goldstein2020; @Sances2017].
+and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).” We divide these amounts by the population to estimate the per-capita fees and fines revenue raised in each municipality.
+This data has been used as a proxy for the amount of tickets issued at the local level in scholarly research [see, for instance, @Goldstein2020; @Sances2017].
 
@@
 The COG data only include local revenues, which means the share of fines revenue corresponds more directly to local police practices.
-Following the guidance of @Sances2017, we retain only municipalities with police and/or court systems, and only municipalities with populations of at least 2,500.
+Following the guidance of @Sances2017, we retain only municipalities with police and/or court systems, as these are the only municipalities capable of issuing tickets.
+We also only retain municipalities with populations of at least 2,500.
 
 **Registered Voter Files**: The COG data do not include estimates of turnout at the local level.
-To estimate local turnout, we leverage registered voter files provided by data vendor L2.
-Voters in Washington, DC, and every state in the country (with the exception of North Dakota) requires voters to register to vote prior to participating.
+To estimate local turnout, we leverage registered voter files provided by data vendor L2 Political.
+In Washington, DC, and every state in the country (with the exception of North Dakota) voters are required to register to vote prior to participating.
 These files are considered public record, and in most states contain information about each voter’s age, residential address, political affiliation, and participation history.
@@
 By aggregating these individual-level records to the municipal level, we are able to estimate the number of registered voters and the number of ballots cast in every city in the country.
-By using the racial estimates provided by L2, we can estimate the number of ballots cast by voters of each race in each city.
-Although each voters’ race is modeled based on L2’s algorithms---and is not self-reported---it is possibly incorrect for some voters.
+Moreover, by using the racial estimates provided by L2 we can estimate the number of ballots cast by voters of each race in each city.
+Each voters’ race is modeled based on L2’s algorithms and not self-reported, surely leading to errors at the individual-voter level.
 We assume this does not present a problem when records are aggregated to the municipal level.
 
-Although turnout could be calculated as a share of *registered voters* who participated, such an approach could be biased.
-If fees and fines collection impact the number of individuals who register to vote, but not the share of registered voters who participate, our estimates will be compromised.
-We therefore calculate turnout by dividing the number of ballots cast according to L2 by the 5-year estimate of each municipality’s citizen voting-age population (CVAP) from the US Census Bureau.
+We calculate turnout by dividing the number of ballots cast according to L2 by the 5-year estimate of each municipality’s citizen voting-age population (CVAP) from the US Census Bureau.
 These estimates are available for individual racial groups.
@@
 Where more votes were cast than the Census estimate for CVAP, we recode turnout as 100 percent.
-Our results do not change if we instead simply remove these municipalities.
+Our results do not change if we instead simply remove these municipalities, or use unmodified turnout estimates.
 
-**Estimation Strategy**: We begin by merging each municipality’s fees and fines per capita from the 2012 COG to its turnout from the 2014 midterm election, and the 2017 COG to its 2018 turnout.
+**Estimation Strategy**: We begin by merging each municipality’s fees and fines per capita (that is, dollars per resident) from the 2012 COG to its turnout from the 2014 midterm election, and the 2017 COG to its 2018 turnout.
 Because this measure is highly right-skewed, we use the natural log of fees and fines per capita plus one.
@@
 These include racial composition, population density, median income, collegiate education, median age, and share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality’s revenue that comes from the state or federal government in the 2012 and 2017 COGs.
-We retain only municipalities whose data is reported to the COG in both 2012 and 2017.
+We retain the 8,954 municipalities whose data is reported to the COG in both 2012 and 2017 and meet the other criteria noted above.
 
-We then run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
-
-Unfortunately, the 5-year cycle of the COG does not neatly line up with the general 4-year cycle typical of American elections.
+The 5-year cycle of the COG does not neatly line up with the general 4-year cycle typical of American elections.
 The timing of the COG and midterm elections mean that our analytical strategy is conservative.
@@
 
+We  run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
+
 Our national two-way fixed effect model allows us to test our first two hypotheses:
 
-*Hypothesis 1: Increased reliance on fines and fees revenue at the city level affects voter turnout at the city level.*
+**Hypothesis 1:** Increased reliance on fines and fees revenue at the city level reduces voter turnout at the city level.*
 
-*Hypothesis 2: The effect of the city-level relationship between fines and voter turnout is less demobilizing or more mobilizing for Black voters, given the historical and explicit racial injustice narratives used to explain these practices.*
+**Hypothesis 2:** The effect of the city-level relationship between fines and voter turnout is stronger for Black voters, given the historical and explicit racial injustice narratives used to explain these practices.*
 
@@
 It cannot, however, directly observe the causal mechanism we argue is at play: namely, that direct contact with the criminal legal system influences turnout.
-Our national analysis suffers from what is called the “ecological fallacy:” it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
+If interpreted in isolation, our national analysis would suffer from the ecological fallacy.
+In other words, it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
+Moreover, there are many other factors that could be at play.
+Increased fees and fines could be correlated with increased policing in general, for instance.
+We are also unable to isolate the individual-level effect of being ticketed on turnout using this setup.
 
-To test whether a ticket directly influences the turnout voters we turn to individual-level data from Hillsborough County, Florida (home to Tampa).
+Another drawback of the national analysis is that it can't distinguish personal contact from proximal contact (“having a loved one who is a custodial citizen without yourself having had contact”) [@Walker2017].
+Because existing research investigating the effect of proximal contact has produced mixed results [@Burch2014; @Lee2014; @Sugie2015; @White2019; @Walker2017; @Walker2020], we are unable to prove that personal police contact is the only dynamic driving effects observed in our national analysis.
+For that reason, we turn to individual-level data from Hillsborough County, Florida (home to Tampa).
+
 Hillsborough County is interesting for theoretical reasons: Tampa is in the top decile of municipalities in terms of fees and fines increase between the 2012 and 2017 COGs, and its population puts it in the top 1 percent of cities nationwide.
@@
 This data includes the name and date of birth of the individual stopped; the date of the offense; and the amount the individual paid for a ticket.
-We retain only the records where the individual paid money.
 
-To test the effect of ticketing on individual-level turnout, we match the first and last names and dates of birth against the Hillsborough County registered voter file.
-Here, rather than rely on a snapshot from L2, we use the raw voter file directly from the state.
+To identify ticketed voters, we match the first and last names and dates of birth from these data against the Hillsborough County registered voter file.
 Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status [see @Nyhan2017].
-Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.
-We thus observe virtually all individuals who were registered  to vote at any time during our period of study.
+Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.^[Because such frequent snapshots are not available from L2, we here use the registered voter file made freely available by the state of Florida.] We thus observe virtually all individuals who were registered to vote at any time during our period of study.
 Unique voter identification numbers allow us to avoid double-counting voters who are registered in multiple snapshots.
 We retain each voter’s earliest record, and geocode voters to their home census block groups.
+Because we argue that police contact is the driving force behind any turnout effect, we remove tickets issued by red-light cameras.
 
@@
 By matching the police stop and voter records, we identify all voters who were ticketed between the 2012 and 2018 general elections.
-Voters are considered “treated” for every general election following their first ticket.
-This means that a voter who was ticketed in early 2014 was considered treated for the 2014, 2016, and 2018 elections.
-A voter treated in 2017, on the other hand, is only considered treated in the 2018 election.
+Voters are considered “treated” in the general election following their ticket.
 
-These voters are then matched to two control voters using what methodologists call a “genetic” process [@Sekhon2011].
-The pool of potential control voters are the individuals who are never stopped during the 2012 -- 2018 period, regardless of whether they paid a fine.
-We match voters on individual-level characteristics (race / ethnicity; gender; party affiliation; age; registration date; number of traffic stops between 2003 and the 2012 election) and block group-level characteristics from the 2012 5-year ACS estimates (median income; share of the population with some college; unemployment rate).
+These voters are then matched to a control voter using a nearest-neighbor approach, with a genetic algorithm used to determine the best weight for each characteristic [@Sekhon2011].
+As we show in Appendix XX, there is real reason to believe that individuals who are ticketed differ in meaningful ways for which we cannot directly control.
+As such, control voters are individuals who are stopped in the two years following the post-treatment election of the treated voters.
+Put differently, if a voter is stopped between 2012 and 2014, their control voter must be an individual stopped between the 2014 and 2016 elections.
+A voter cannot both be a treated and control voter for the same election; therefore, someone ticketed between the 2012 and 2014 elections and again between the 2014 and 2016 elections cannot serve as a control for anyone ticketed between 2012 and 2014.
+We assume that after controlling for observable characteristics, psat turnout, *and* the unobservable characteristics associated with receiving a ticket the timing of the ticket is effectively random.
+In short, any turnout difference between the treated voters and their controls is the causal effect of a police stop on turnout.
 
-We also match treated and control voters on their 2010 and 2012 general election turnout, as well as any other even-yeared general election turnout in the pre-treatment period.
-In other words, a voter ticketed in 2013 is matched to controls based on turnout in 2010 and 2012, while a voter ticketed in 2017 is matched to their control using 2010, 2012, 2014, and 2016 turnout.
-Because voters treated in later periods are matched to their controls along more covariates, we run three separate matches: one for voters stopped between the 2012 and 2014 elections; for voters stopped between the 2014 and 2016 elections; and for those stopped between the 2016 and 2018 elections.
+We match voters on individual-level characteristics (race / ethnicity; gender; party affiliation; age; registration date; number of traffic stops between 2003 and the election prior to the treatment period) and block group-level characteristics from the 2012 5-year ACS estimates (median income; share of the population with some college; unemployment rate).
+We also match exactly on whether an individual was ticketed for a civil or criminal infraction, as well as whether they eventually paid a fine.
+We also match treated and control voters on their turnout in the three pre-treatment elections.
 
-We then run ordinary least squares difference-in-difference regressions to test the following hypotheses.
+Our analytical approach thus incorporates two different causal approaches.
+Leveraging pre-treatment turnout allows us to estimate a traditional difference-in-differences model.
+Difference-in-difference models assume that, in the absence of the treatment, any turnout gap between treated and control voters would have remained stable in the post-treatment period.
+While the validity of this assumption is commonly established by examining pre-treatment trends in turnout between the two groups, it can be improved upon by using the matching methodology described above.
+In the case at hand, we both establish that the turnout gap between treatment and control voters was constant prior to treatment, *and* that the observable characteristics of treated and control voters are similar---thus lending credence to the assumption that this gap would have remained constant absent treatment.
+Finally, by drawing controls from the population of individuals who were ticketed in subsequent years, we also indirectly control for any unobserved characteristics associated with receiving a ticket.
+For a more detailed discussion of how matching can improve upon traditional difference-in-difference approaches when using panel data, see @Imai2020.
 
-*Hypothesis 3: Among individuals who were ticketed (“treated”) in Tampa, their likelihood of turning out in a subsequent election roughly matches the racioethnic distribution apparent in the national city-level data.
-If fines uniquely mobilize Black voters nationally, they should also uniquely mobilize Black voters in Tampa.*
+It is important to note that while our primary analyses include all individuals who were stopped, our results hold even when we shrink the window around an election dramatically.
+As we show in Appendix XX, voters ticketed in the two months before an election turned out at lower rates than matched controls ticketed in the two months following an election.
 
-<!-- Because Tampa holds off-year local elections, we are able to test whether mobilized voters target officials who are able to change local police practices.
+We then estimate the following equation:
+
+\begin{gather}
+\label{eq:1}
+v_{it}=\beta_0+\beta_1Treated_{i}+\beta_2Post Treatment_{t} + \nonumber \\
+\beta_3Treated_{i}\times Post Treatment_{t} + \\
+\delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
+\end{gather}
+
+Individual *i*'s turnout (*v*) in year *t* is a function of the year and whether they were stopped by the police.
+In the equation, *$\beta$~1~Treated~i~* measures the historical difference between treated voters and their controls.
+*$\beta$~2~Post Treatment~t~* measures whether turnout increased for controls in the first election following the treated voter’s stop, while *$\beta$~3~Treated~i~ × Post Treatment~t~* tests whether turnout changed differently for treated voters than their controls in the election following their police stop.
+*$\beta$~3*, then, will capture the causal effect of a police stop on voter turnout.
+Finally, the matrix *$\delta$Z~i~* contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
+Equation 1 allows us to test Hypotheses 3:
+
+**Hypothesis 3**: Being ticketed reduces an individual’s likelihood of turning out in the subsequent election.
+
+We also estimate Equation 2, in which the treatment effect is interacted with whether a voter is Black (*$\beta$~4~Treated~i~ × Post Treatment~t~ × Black~i~*):
+
+\begin{gather}
+\label{eq:2}
+v_{it}=\beta_0+\beta_1Treated_{i}+\beta_2Post Treatment_{t} + \nonumber \\
+\beta_3Treated_{i}\times Post Treatment_{t} + \beta_4Treated_{i}\times Post Treatment_{t}\times Black_{i} +\\
+\delta{Y}_{i} + \delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
+\end{gather}
+
+where *$\delta$Y~it~* includes the dummy for Black interacted with the treatment and post treatment dummies.
+
+Equation 2 allows us to test Hypotheses 4:
+
+**Hypothesis 4**: The effect of being ticketed on an individual's turnout is less negative / more positive if that individual is Black.
+
+Because Tampa holds off-year local elections, we are able to test whether ticketed voters target officials who are able to change local police practices.
 @Laniyonu2019 gives us reason to believe that the effect should be stronger for local elections.
--->
 
-<!-- *Hypothesis 4: Any potential mobilizing turnout effect in Tampa is stronger for local (mayoral) elections, since those elections directly affect police practices.* -->
+**Hypothesis 5**: Any potential mobilizing turnout effect in Tampa is stronger for local (mayoral) elections, since those elections directly affect police practices.
 
@@
 -->
-
-The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures participation.
-Past work looking at the individual-level effects of low-level contact has relied entirely on survey or qualitative data [e.g.
-@Walker2014; @Weaver2010].
-Their in-depth research allows for the testing of specific psychological mechanisms and personal interpretations of criminal legal contact, but does not allow us to generalize more broadly.
-As Weaver and Lerman [-@Weaver2010, page 821] note, it may also introduce measurement bias.
-Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to police ticketing.
-The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of the 232,568 individuals ticketed over the 6 year period---a far larger pool than even the most robust surveys.
 
@@
 
-The results of the two-way fixed effects model are slightly different than what we saw in the 2018 cross-sectional approach; namely, while Table \ref{tab:twfe} indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not impact Black turnout.
+The results of the two-way fixed effects model are different than what we saw in the 2018 cross-sectional approach; namely, while Table \ref{tab:twfe} indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not significantly impact Black turnout.
 The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.06 percentage points.
-Moreover, because of the relative stability in fees and fines collections at the municipal level over this time period (the mean increase in per-capita fees and fines collections was just 6 percent, and the median municipality decreased by about 1.5 percent), it is not clear how informative this approach is.
 
 In Table \ref{tab:coarser}, we re-estimate the model from Table \ref{tab:twfe} but coarsen the data.
-Here, we test whether turnout changed for municipalities who increased their fees and fines collections differently than municipalities where collections stayed the same or decreased.
+Here, the dependent variable of interest is binary: we test whether turnout changed for municipalities who increased their per-capita fees and fines collections differently than municipalities where collections stayed the same or decreased.
 Municipalities that increased their per-capita fees and fines are considered “treated.”
@@
 
-The coefficient on *Treated × 2018* indicates that non-Black turnout dropped by about 0.5 percentage points in municipalities where fees and fines collections increased relative to other municipalities.
-While this coefficient is slightly positive for Black voters, it is not statistically significantly different from 0.
+The coefficient on *Treated × 2018* indicates that non-Black turnout dropped by about 0.5 percentage points in municipalities where fees and fines collections increased, relative to other municipalities.
+While this coefficient is slightly *positive* for Black voters, it is not statistically significantly different from 0.
 In other words, both Tables \ref{tab:twfe} and \ref{tab:coarser} indicate that increased fees and fines collections decrease non-Black turnout but have no impact on Black turnout.
@@
 
-Thus far, we have shown that the turnout effects of fees and fines collection impact municipal-level turnout, and that the effects are different for Black and non-Black Americans.
+Thus far, we have shown that voter turnout is decreased in municipalities that increase fines and fees collections.
 We argue that this relationship is causal: increased fees and fines collections means that more residents have direct interactions with the criminal legal system.
@@
 
-To directly observe the effect of being ticketed on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
-As discussed above, we match [@Sekhon2011] individuals who were stopped and assessed a fine between the 2012 and 2018 elections to individuals who were not stopped during this time period.^[Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
-The full sample is used in the actual matching process.]  Matching is done with replacement and ties are not broken, meaning some treated voters may have more than 2 controls; the regression weights reflect this possibility.
+To directly observe the effect of being stopped by the police on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
+As discussed above, we match individuals who were ticketed between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.^[Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
+The full sample is used in the actual matching process.]  Matching is done with replacement and ties are randomly broken.
 In Table \ref{tab:balance} we present the results of the matching algorithm.
-We manage to reduce between treated and control voters substantially along all observed characteristics.
+As the table demonstrates, the selected control voters are very similar to the treated voters.
 
 \begin{singlespace}
-```{r balance-tab-chunk, echo = F}
+```{r baltab-chunk, echo = F, warning = F}
 t <- readRDS("temp/balance_table_y.rds")
@@
                   escape = F)  %>%
-  add_header_above(c(" " = 1, "Means: Unmatched Data" = 2, "Means: Matched Data" = 2, "Percent Improvement" = 4), align = "c") %>%
-  kable_styling(latex_options = c("scale_down", "HOLD_position"))
+  kable_styling(latex_options = c("hold_position"))
 j
@@
 
-While Table \ref{tab:balance} indicates that our treatment voters and their matches are substantially similar to their matches, the validity of the difference-in-differences design requires that the treatment and control voters turned out at comparable rates in the baseline period.
+While Table \ref{tab:balance} indicates that our treatment voters and their matches are substantially similar to their matches, the validity of the difference-in-differences design requires that any turnout gap between treatment and control voters be comparable in the baseline period.
 In Figure \ref{fig:did1}, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped.
-The first election following a treated voter’s stop is denoted as *t = 0*; subsequent elections take higher positive numbers, while the years in which *t* is less than zero are the periods prior to the stop.
-This means that for someone stopped in 2013, *t* is 0 in 2014, while *t* is equal to 0 in 2018 for an individual stopped between the 2016 and 2018 elections.
+The first election following a treated voter’s stop is denoted as *t = 0* while the years in which *t* is less than zero are the periods prior to the stop.
+This means that for someone stopped in 2013 (and their controls), *t* is 0 in 2014, while *t* is equal to 0 in 2018 for an individual stopped between the 2016 and 2018 elections.
 
@@
 Because we matched treated and control voters based on turnout prior to the ticket, this is unsurprising.
-The visual results of the post-treatment trend corroborate what we found nationwide using the municipal-level data; namely, ticketing has a different effect for Black voters than for others..
 
-Figure \ref{fig:did2} makes this effect even clearer.
-Here, we limit the analysis to voters who were stopped within the 90 days prior to an election (and their controls).
-We expected that the ticket would be more salient for individuals stopped shortly before the election.
-This appears to be the case---*especially for Black voters.*
-
-```{r did2, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:did-2}Effect of Being Ticketed Within 90 Days of Election on Turnout", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/within90days_y.rds")
-print(p2)
-```
-
-Table \ref{tab:dind-table} formalizes Figures \ref{fig:did1} and \ref{fig:did2} into an ordinary least squares regression.
-Models 1 and 2 present the causal estimates of being stopped at any point in the two years prior to an election; Models 3 and 4 re-estimate the effect of being stopped within 90 days of an election.
-Models 1 and 3 show our overall causal effect, while Models 2 and 4 allow for the possibility that a ticket differentially mobilizes Black voters.
+Table \ref{tab:dind-table} formalizes Figure \ref{fig:did1} into an ordinary least squares regression.
+Model 1 shows our overall causal effect, while Model 2 allows for the possibility that a ticket differentially mobilizes Black voters.
 The coefficients of note are *Treated × Post Treatment* and *Treated × Post Treatment × Black*.
@@
 
-Model 3 indicates that a ticket is neither mobilizing nor demobilizing---the coefficient is small and nonsignificant (*p* = 0.34) but that tickets do mobilize Black voters.
-Receiving a ticket increases the average turnout for Black voters in the first two elections by about 1.1 percentage points.
-Model 4 shows that ticketing shortly before an election increases the turnout of non-Black voters by about 0.9 percentage points, and there is no statistically significantly different effect for Black voters.
-However, Figure \ref{fig:did2} visually indicates that the effect might be larger for Black voters, and the coefficient on *Treated × Post Treatment × Black* is large (as is its standard error).
-These two facts taken together indicate that our inability to detect a differentially mobilizing effect for Black voters stopped shortly before an election may have more to do with issues of statistical power than an additional effect that is really equal to zero.
+As both Figure \ref{fig:did1} and Table \ref{tab:dind-table} make clear, police tickets meaningfully depressed turnout.
+In models 1 and 2, the estimated overall treatment effect is -1.5 percentage points.
+In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---nonBlack turnout was depressed by 1.7 percentage points, while the negative effect was just -1.0 for Black individuals.
+Although the treatment effect is still sustantively quite large for Black individuals, the pattern follows our national analysis.
+It appears that, in Tampa and around the country, Black voters' turnout is not as negatively impacted by police contact as that of nonBlack individuals.
 

### 2021-04-19 markdown/draft_paper.tex
lots of changes

--- 2021-03-28 markdown/draft_paper.tex
@@
 \hypersetup{
-  pdftitle={Policing for Profit and the Mobilization of Black Voters},
+  pdftitle={Policing for Profit and the Undermining of Democracy},
   pdfauthor={Jonathan Ben-Menachem; Kevin Morris},
@@
 
-\title{Policing for Profit and the Mobilization of Black Voters}
-\usepackage{etoolbox}
-\makeatletter
-\providecommand{\subtitle}[1]{% add subtitle to \maketitle
-  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
-}
-\makeatother
-\subtitle{Fines, Fees, and Turnout}
+\title{Policing for Profit and the Undermining of Democracy}
 \author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
-\date{March 25, 2021}
+\date{April 19, 2021}
 
@@
 \begin{abstract}
-The American criminal legal system is an important site of political socialization: sociologists show how the alienating effect of criminalization manifests as systems avoidance, and political scientists have measured the effects of policing and incarceration on political participation.
+The American criminal legal system is an important site of political socialization: sociologists show how the alienating effect of criminalization pushes people away from public institutions, and political scientists have measured the effects of policing and incarceration on political participation.
 Despite this burgeoning literature, no research has directly investigated how ticketing for low-level offenses affects political participation.
-Using data from the Census of Governments and the national voter file, we test the causal effect of fines and fees practices on American voting behavior at the city level.
+Using data from the Census of Governments and the national voter file, we test the causal effect of fines and fees practices on American voting behavior at the city level (aggregate).
 Additionally, we exploit individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019 to determine whether getting a ticket impacts political participation.
-Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.6 percentage point decrease in non-Black turnout but was not associated with Black turnout.
-In Tampa, Florida, we estimate that being ticketed increases a non-Black individual's likelihood of voting by 3.7 percentage points, and that the effect is larger for Black voters.
-
-\hfill\break
-
+Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.6 percentage point turnout decrease but was not associated with Black turnout.
+In Tampa, Florida, we estimate that being ticketed decreases an individual's likelihood of voting in federal elections by 1.3 percentage points, but we do not uncover evidence of a distinct political effect for Black voter turnout.
+In local elections, however,\\
+\textbar{}
+\textbar{}
 \textbf{Keywords}: voting, monetary sanctions, race, punishment, political participation
@@
 Work exploring how criminalization directly and indirectly influences political participation has exploded in recent years.
+Scholars have found that criminal legal contact (i.e.~arrest, conviction, incarceration) consistently discourages voting (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}; \protect\hyperlink{ref-Burch2011}{Burch 2011}; \protect\hyperlink{ref-White2019a}{White 2019b}).
 This work, however, has largely focused on the effects of highly consequential contact with the criminal legal system such as incarceration and felony convictions (\protect\hyperlink{ref-Burch2014}{Burch 2014}; \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}).
-Although some work has leveraged survey data and qualitative approaches to interrogate lower-level police interactions---such as ticketing---our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
+Our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
+
+The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures participation.
+Past work looking at the individual-level effects of low-level contact has relied entirely on survey or qualitative data (e.g.
+\protect\hyperlink{ref-Walker2014}{Walker 2014}; \protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
+Their in-depth research allows for the testing of specific psychological mechanisms and personal interpretations of criminal legal contact, but does not allow us to generalize more broadly.
+As Weaver and Lerman (\protect\hyperlink{ref-Weaver2010}{2010, 821}) note, it may also introduce measurement bias.
+Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to police ticketing.
+The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of the 232,568 individuals ticketed over a 6 year period---a far larger pool than even the most robust surveys.
+
 We begin by joining fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for each municipality in the country.
@@
 
-After exploring national data, we use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were ticketed between the 2012 and 2018 elections.
-By matching individuals who were ticketed to other, similar voters who were not ticketed and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout.
-Using self-reported race from the Florida registered voter file, we identify large, \emph{positive} treatment effects for all voters---effects that were especially large for Black voters..
-
-We demonstrate that police ticketing practices---the most widespread form of police contact in America---influence the political behavior of Americans, with distinct effects for Black and non-Black voters.
-This finding supports and extends Hannah Walker's theory of criminal legal contact is mobilizing / less demobilizing for nonwhite political participation (\protect\hyperlink{ref-Walker2020}{Walker 2020}, \protect\hyperlink{ref-Walker2014}{2014}).
-Our results also complicate Vesla Weaver and Amy Lerman's theory of low-level criminal legal contact discouraging political participation (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
+Because our national analysis does not allow us to directly observe the causal effect of police ticketing on voter turnout, we use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were ticketed between the 2012 and 2018 elections.
+By matching individual voters who were ticketed to similar voters who were ticketed at later points and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout.
+We find that being ticketed reduces the chance that an individual will turn out in the subsequent election.
+
+We demonstrate that police ticketing practices---the most widespread form of police contact in America---influence the political behavior of Americans.
+This finding supports and extends Vesla Weaver and Amy Lerman's theory of criminal legal contact discouraging political participation (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
 Our findings are relevant for interdisciplinary scholars of crime, race, politics, political economy, social movements, and policing.
@@
 
-Sociologists have incorporated contemporary fines and fees practices into a broader empirical-historical theory of racialized punishment policy (\protect\hyperlink{ref-Harris2010}{Harris, Evans, and Beckett 2010}; \protect\hyperlink{ref-Friedman2020}{Friedman 2020}).
-Additionally, an emerging political science literature directly investigates the relationship between criminalization and political behavior.
+An emerging political science literature directly investigates the relationship between criminalization and political behavior.
+Additionally, sociologists have incorporated contemporary fines and fees practices into a broader empirical-historical theory of racialized punishment policy (\protect\hyperlink{ref-Harris2010}{Harris, Evans, and Beckett 2010}; \protect\hyperlink{ref-Friedman2020}{Friedman 2020}).
 
@@
 
-Another process by which criminalization shapes the electorate is ``prison gerrymandering,'' or the practice of counting incarcerated people as residing in the district where their prison is located for the purposes of creating electoral districts.
-This practice inflates the voting power of rural and white voters while diminishing the power of urban, Black, and Latino voters (\protect\hyperlink{ref-Remster2018}{Remster and Kramer 2018/ed}).
-
 The role of fines and fees in the context of felony disenfranchisement has recently garnered national attention.
@@
 Using existing national survey data and extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
-Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a ``linked fate'' where ``one's individual opportunities are linked to the entire racial group'' (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014, 267}).
+Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a ``linked fate'' where ``one's individual opportunities are linked to the entire racial group'' (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014, 197}).
 Their interview data lead them to conclude that while criminal legal contact does increase perceptions of linked fate among Black respondents, ``a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing''---and interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}).
@@
 It may be the case that Black and non-Black Americans employ different self-preservation strategies, however.
-Ariel White's analysis of how short jail sentences affect voting in Harris County, Texas found that Black defendant turnout in subsequent elections dropped by 13 percentage points---but the effect on white turnout was not statistically significant (\protect\hyperlink{ref-White2019}{White 2019a}).
+\protect\hyperlink{ref-Walker2020}{Walker} (\protect\hyperlink{ref-Walker2020}{2020}) makes clear that, when Black Americans locate their contact with the criminal legal system in a narrative of racial injustice, they can be politically mobilized; on the other hand, \protect\hyperlink{ref-Lerman2014}{Lerman and Weaver} (\protect\hyperlink{ref-Lerman2014}{2014}) shows that Black individuals' ability to situate their life experiences in a larger legacy of exploitation can be demobilizing.
+Turning to administrative data analysis, Ariel White's analysis of how short jail sentences affect voting in Harris County, Texas found that Black defendant turnout in subsequent elections dropped by 13 percentage points---but the effect on white turnout was not statistically significant (\protect\hyperlink{ref-White2019}{White 2019a}).
 
@@
 
-Importantly, Walker found that nonwhite people who had experienced \emph{either} proximal or personal contact \emph{at any level of intensity}, including being stopped and questioned by police, were mobilized to take part in nonvoting political activity---and the same held true for whites, but with a much smaller effect size.
-Walker theorizes that this finding suggests that nonwhite people view criminalization ``as a form of systemic political threat,'' an analysis comparable to ``linked fate.'' Notably, Walker's survey questions excluded ``minor traffic stops,'' the primary focus of this paper.
+Walker found that nonwhite people who had experienced \emph{either} proximal or personal contact \emph{at any level of intensity}, including being stopped and questioned by police, were mobilized to take part in nonvoting political activity---and the same held true for whites, but with a much smaller effect size.
+Walker theorizes that this finding suggests that nonwhite people view criminalization ``as a form of systemic political threat,'' an analysis comparable to ``linked fate.'' Additionally, Walker's survey questions excluded ``minor traffic stops,'' the primary focus of this paper.
 
@@
 
-Although geographic or spatial analyses of how criminalization affects political socialization technically move beyond proximal contact as an extant conceptual framework, we argue that geographic proximity should work similarly to social network proximity---if one neighborhood is heavily policed, people who live in that neighborhood are more likely to have social ties who have experienced policing.
+Although geographic or spatial analyses of how criminalization affects political socialization technically move beyond proximal contact as an extant conceptual framework, similar mechanisms should operate on the neighborhood level.
 Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level (\protect\hyperlink{ref-Burch2014}{Burch 2014}).
@@
 Racial capitalist political economy imposes fiscal constraints regardless of city officials' intentions.
-In their study of fines and fees reliance in Chicago suburbs, Josh Pacewicz and John Robinson, III show how the racialization of municipal opportunity structures prevents majority-Black suburban governments from acquiring sufficient revenue from ``good'' sources such as sales taxes or property taxes, catalyzing a reliance on fines and fees to fund essential government services (\protect\hyperlink{ref-Pacewicz2020}{Pacewicz and N.Robinson 2020}).
-Importantly, Pacewicz and Robinson III note that these racialized municipal opportunity structures are tied to the political-historical processes of neoliberalism and fiscal austerity, an observation that aligns with recent scholarship detailing the origins of fees paid by incarcerated people (\protect\hyperlink{ref-Kirk2020}{Kirk, Fernandes, and Friedman 2020}).
+In their study of fines and fees reliance in Chicago suburbs, Josh Pacewicz and John Robinson, III show how the racialization of municipal opportunity structures prevents majority-Black suburban governments from acquiring sufficient revenue from ``good'' sources such as sales taxes or property taxes, catalyzing a reliance on fines and fees to fund government services (\protect\hyperlink{ref-Pacewicz2020}{Pacewicz and N.Robinson 2020}).
+Pacewicz and Robinson III note that these racialized municipal opportunity structures are tied to the political-historical processes of neoliberalism and fiscal austerity, an observation that aligns with recent scholarship detailing the origins of fees paid by incarcerated people (\protect\hyperlink{ref-Kirk2020}{Kirk, Fernandes, and Friedman 2020}).
 The late 20th century ``property tax revolt'' most significantly benefited white homeowners (\protect\hyperlink{ref-Martin2017}{Martin and Beck 2017}), and without property tax hikes as a revenue-raising option, smaller cities and towns have few choices.
@@
 With this history in mind, we argue that Black Americans can situate exploitative ticketing practices in a longer historical legacy of collective disparate treatment and violence at the hands of the state, which may facilitate a stronger collective political analysis when police ticketing practices become more extreme.
-\protect\hyperlink{ref-Walker2020}{Walker} (\protect\hyperlink{ref-Walker2020}{2020}) makes clear that, when Black Americans locate their contact with the criminal legal system in a narrative of racial injustice, they can be mobilized to vote.
 The historical use of fees and fines make this sort of police contact especially likely to evoke such narratives.
@@
 \textbf{Census of Governments}: Every five years, the US Census Bureau collects data from governmental bodies around the country.
-We use two snapshots of the COG: one that covers the years 2008 - 2012, and another that covers 2013 - 2017.
-The COG includes a host of information about state and municipal finances.
-The COG asks municipalities to report how much revenue they collect from ``penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation\ldots{} and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).'' This data has been used as a proxy for the amount of tickets issued at the local level in scholarly research (see, for instance, \protect\hyperlink{ref-Goldstein2020}{Goldstein, Sances, and You 2020}; \protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
+We use two snapshots of the COG: one that covers the years 2008 -- 2012, and another that covers 2013 -- 2017.
+The COG asks municipalities to report how much revenue they collect from ``penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation\ldots{} and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).'' We divide these amounts by the population to estimate the per-capita fees and fines revenue raised in each municipality.
+This data has been used as a proxy for the amount of tickets issued at the local level in scholarly research (see, for instance, \protect\hyperlink{ref-Goldstein2020}{Goldstein, Sances, and You 2020}; \protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
 
@@
 The COG data only include local revenues, which means the share of fines revenue corresponds more directly to local police practices.
-Following the guidance of \protect\hyperlink{ref-Sances2017}{Sances and You} (\protect\hyperlink{ref-Sances2017}{2017}), we retain only municipalities with police and/or court systems, and only municipalities with populations of at least 2,500.
+Following the guidance of \protect\hyperlink{ref-Sances2017}{Sances and You} (\protect\hyperlink{ref-Sances2017}{2017}), we retain only municipalities with police and/or court systems, as these are the only municipalities capable of issuing tickets.
+We also only retain municipalities with populations of at least 2,500.
 
 \textbf{Registered Voter Files}: The COG data do not include estimates of turnout at the local level.
-To estimate local turnout, we leverage registered voter files provided by data vendor L2.
-Voters in Washington, DC, and every state in the country (with the exception of North Dakota) requires voters to register to vote prior to participating.
+To estimate local turnout, we leverage registered voter files provided by data vendor L2 Political.
+In Washington, DC, and every state in the country (with the exception of North Dakota) voters are required to register to vote prior to participating.
 These files are considered public record, and in most states contain information about each voter's age, residential address, political affiliation, and participation history.
@@
 By aggregating these individual-level records to the municipal level, we are able to estimate the number of registered voters and the number of ballots cast in every city in the country.
-By using the racial estimates provided by L2, we can estimate the number of ballots cast by voters of each race in each city.
-Although each voters' race is modeled based on L2's algorithms---and is not self-reported---it is possibly incorrect for some voters.
+Moreover, by using the racial estimates provided by L2 we can estimate the number of ballots cast by voters of each race in each city.
+Each voters' race is modeled based on L2's algorithms and not self-reported, surely leading to errors at the individual-voter level.
 We assume this does not present a problem when records are aggregated to the municipal level.
 
-Although turnout could be calculated as a share of \emph{registered voters} who participated, such an approach could be biased.
-If fees and fines collection impact the number of individuals who register to vote, but not the share of registered voters who participate, our estimates will be compromised.
-We therefore calculate turnout by dividing the number of ballots cast according to L2 by the 5-year estimate of each municipality's citizen voting-age population (CVAP) from the US Census Bureau.
+We calculate turnout by dividing the number of ballots cast according to L2 by the 5-year estimate of each municipality's citizen voting-age population (CVAP) from the US Census Bureau.
 These estimates are available for individual racial groups.
@@
 Where more votes were cast than the Census estimate for CVAP, we recode turnout as 100 percent.
-Our results do not change if we instead simply remove these municipalities.
-
-\textbf{Estimation Strategy}: We begin by merging each municipality's fees and fines per capita from the 2012 COG to its turnout from the 2014 midterm election, and the 2017 COG to its 2018 turnout.
+Our results do not change if we instead simply remove these municipalities, or use unmodified turnout estimates.
+
+\textbf{Estimation Strategy}: We begin by merging each municipality's fees and fines per capita (that is, dollars per resident) from the 2012 COG to its turnout from the 2014 midterm election, and the 2017 COG to its 2018 turnout.
 Because this measure is highly right-skewed, we use the natural log of fees and fines per capita plus one.
@@
 These include racial composition, population density, median income, collegiate education, median age, and share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality's revenue that comes from the state or federal government in the 2012 and 2017 COGs.
-We retain only municipalities whose data is reported to the COG in both 2012 and 2017.
-
-We then run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
-
-Unfortunately, the 5-year cycle of the COG does not neatly line up with the general 4-year cycle typical of American elections.
+We retain the 8,954 municipalities whose data is reported to the COG in both 2012 and 2017 and meet the other criteria noted above.
+
+The 5-year cycle of the COG does not neatly line up with the general 4-year cycle typical of American elections.
 The timing of the COG and midterm elections mean that our analytical strategy is conservative.
@@
 
+We run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
+
 Our national two-way fixed effect model allows us to test our first two hypotheses:
 
-\emph{Hypothesis 1: Increased reliance on fines and fees revenue at the city level affects voter turnout at the city level.}
-
-\emph{Hypothesis 2: The effect of the city-level relationship between fines and voter turnout is less demobilizing or more mobilizing for Black voters, given the historical and explicit racial injustice narratives used to explain these practices.}
+\textbf{Hypothesis 1:} Increased reliance on fines and fees revenue at the city level reduces voter turnout at the city level.*
+
+\textbf{Hypothesis 2:} The effect of the city-level relationship between fines and voter turnout is stronger for Black voters, given the historical and explicit racial injustice narratives used to explain these practices.*
 
@@
 It cannot, however, directly observe the causal mechanism we argue is at play: namely, that direct contact with the criminal legal system influences turnout.
-Our national analysis suffers from what is called the ``ecological fallacy:'' it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
-
-To test whether a ticket directly influences the turnout voters we turn to individual-level data from Hillsborough County, Florida (home to Tampa).
+If interpreted in isolation, our national analysis would suffer from the ecological fallacy.
+In other words, it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
+Moreover, there are many other factors that could be at play.
+Increased fees and fines could be correlated with increased policing in general, for instance.
+We are also unable to isolate the individual-level effect of being ticketed on turnout using this setup.
+
+Another drawback of the national analysis is that it can't distinguish personal contact from proximal contact (``having a loved one who is a custodial citizen without yourself having had contact'') (\protect\hyperlink{ref-Walker2017}{Walker and García-Castañon 2017}).
+Because existing research investigating the effect of proximal contact has produced mixed results (\protect\hyperlink{ref-Burch2014}{Burch 2014}; \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}; \protect\hyperlink{ref-Sugie2015}{Sugie 2015}; \protect\hyperlink{ref-White2019}{White 2019a}; \protect\hyperlink{ref-Walker2017}{Walker and García-Castañon 2017}; \protect\hyperlink{ref-Walker2020}{Walker 2020}), we are unable to prove that personal police contact is the only dynamic driving effects observed in our national analysis.
+For that reason, we turn to individual-level data from Hillsborough County, Florida (home to Tampa).
+
 Hillsborough County is interesting for theoretical reasons: Tampa is in the top decile of municipalities in terms of fees and fines increase between the 2012 and 2017 COGs, and its population puts it in the top 1 percent of cities nationwide.
@@
 This data includes the name and date of birth of the individual stopped; the date of the offense; and the amount the individual paid for a ticket.
-We retain only the records where the individual paid money.
-
-To test the effect of ticketing on individual-level turnout, we match the first and last names and dates of birth against the Hillsborough County registered voter file.
-Here, rather than rely on a snapshot from L2, we use the raw voter file directly from the state.
+
+To identify ticketed voters, we match the first and last names and dates of birth from these data against the Hillsborough County registered voter file.
 Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status (see \protect\hyperlink{ref-Nyhan2017}{Nyhan, Skovron, and Titiunik 2017}).
-Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.
-We thus observe virtually all individuals who were registered to vote at any time during our period of study.
+Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.\footnote{Because such frequent snapshots are not available from L2, we here use the registered voter file made freely available by the state of Florida.} We thus observe virtually all individuals who were registered to vote at any time during our period of study.
 Unique voter identification numbers allow us to avoid double-counting voters who are registered in multiple snapshots.
 We retain each voter's earliest record, and geocode voters to their home census block groups.
+Because we argue that police contact is the driving force behind any turnout effect, we remove tickets issued by red-light cameras.
 
@@
 By matching the police stop and voter records, we identify all voters who were ticketed between the 2012 and 2018 general elections.
-Voters are considered ``treated'' for every general election following their first ticket.
-This means that a voter who was ticketed in early 2014 was considered treated for the 2014, 2016, and 2018 elections.
-A voter treated in 2017, on the other hand, is only considered treated in the 2018 election.
-
-These voters are then matched to two control voters using what methodologists call a ``genetic'' process (\protect\hyperlink{ref-Sekhon2011}{Sekhon 2011}).
-The pool of potential control voters are the individuals who are never stopped during the 2012 -- 2018 period, regardless of whether they paid a fine.
-We match voters on individual-level characteristics (race / ethnicity; gender; party affiliation; age; registration date; number of traffic stops between 2003 and the 2012 election) and block group-level characteristics from the 2012 5-year ACS estimates (median income; share of the population with some college; unemployment rate).
-
-We also match treated and control voters on their 2010 and 2012 general election turnout, as well as any other even-yeared general election turnout in the pre-treatment period.
-In other words, a voter ticketed in 2013 is matched to controls based on turnout in 2010 and 2012, while a voter ticketed in 2017 is matched to their control using 2010, 2012, 2014, and 2016 turnout.
-Because voters treated in later periods are matched to their controls along more covariates, we run three separate matches: one for voters stopped between the 2012 and 2014 elections; for voters stopped between the 2014 and 2016 elections; and for those stopped between the 2016 and 2018 elections.
-
-We then run ordinary least squares difference-in-difference regressions to test the following hypotheses.
-
-\emph{Hypothesis 3: Among individuals who were ticketed (``treated'') in Tampa, their likelihood of turning out in a subsequent election roughly matches the racioethnic distribution apparent in the national city-level data.
-If fines uniquely mobilize Black voters nationally, they should also uniquely mobilize Black voters in Tampa.}
-
-The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures participation.
-Past work looking at the individual-level effects of low-level contact has relied entirely on survey or qualitative data (e.g.
-\protect\hyperlink{ref-Walker2014}{Walker 2014}; \protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
-Their in-depth research allows for the testing of specific psychological mechanisms and personal interpretations of criminal legal contact, but does not allow us to generalize more broadly.
-As Weaver and Lerman (\protect\hyperlink{ref-Weaver2010}{2010, 821}) note, it may also introduce measurement bias.
-Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to police ticketing.
-The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of the 232,568 individuals ticketed over the 6 year period---a far larger pool than even the most robust surveys.
+Voters are considered ``treated'' in the general election following their ticket.
+
+These voters are then matched to a control voter using a nearest-neighbor approach, with a genetic algorithm used to determine the best weight for each characteristic (\protect\hyperlink{ref-Sekhon2011}{Sekhon 2011}).
+As we show in Appendix XX, there is real reason to believe that individuals who are ticketed differ in meaningful ways for which we cannot directly control.
+As such, control voters are individuals who are stopped in the two years following the post-treatment election of the treated voters.
+Put differently, if a voter is stopped between 2012 and 2014, their control voter must be an individual stopped between the 2014 and 2016 elections.
+A voter cannot both be a treated and control voter for the same election; therefore, someone ticketed between the 2012 and 2014 elections and again between the 2014 and 2016 elections cannot serve as a control for anyone ticketed between 2012 and 2014.
+We assume that after controlling for observable characteristics, psat turnout, \emph{and} the unobservable characteristics associated with receiving a ticket the timing of the ticket is effectively random.
+In short, any turnout difference between the treated voters and their controls is the causal effect of a police stop on turnout.
+
+We match voters on individual-level characteristics (race / ethnicity; gender; party affiliation; age; registration date; number of traffic stops between 2003 and the election prior to the treatment period) and block group-level characteristics from the 2012 5-year ACS estimates (median income; share of the population with some college; unemployment rate).
+We also match exactly on whether an individual was ticketed for a civil or criminal infraction, as well as whether they eventually paid a fine.
+We also match treated and control voters on their turnout in the three pre-treatment elections.
+
+Our analytical approach thus incorporates two different causal approaches.
+Leveraging pre-treatment turnout allows us to estimate a traditional difference-in-differences model.
+Difference-in-difference models assume that, in the absence of the treatment, any turnout gap between treated and control voters would have remained stable in the post-treatment period.
+While the validity of this assumption is commonly established by examining pre-treatment trends in turnout between the two groups, it can be improved upon by using the matching methodology described above.
+In the case at hand, we both establish that the turnout gap between treatment and control voters was constant prior to treatment, \emph{and} that the observable characteristics of treated and control voters are similar---thus lending credence to the assumption that this gap would have remained constant absent treatment.
+Finally, by drawing controls from the population of individuals who were ticketed in subsequent years, we also indirectly control for any unobserved characteristics associated with receiving a ticket.
+For a more detailed discussion of how matching can improve upon traditional difference-in-difference approaches when using panel data, see \protect\hyperlink{ref-Imai2020}{Imai, Kim, and Wang} (\protect\hyperlink{ref-Imai2020}{2020}).
+
+It is important to note that while our primary analyses include all individuals who were stopped, our results hold even when we shrink the window around an election dramatically.
+As we show in Appendix XX, voters ticketed in the two months before an election turned out at lower rates than matched controls ticketed in the two months following an election.
+
+We then estimate the following equation:
+
+\begin{gather}
+\label{eq:1}
+v_{it}=\beta_0+\beta_1Treated_{i}+\beta_2Post Treatment_{t} + \nonumber \\
+\beta_3Treated_{i}\times Post Treatment_{t} + \\
+\delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
+\end{gather}
+
+Individual \emph{i}'s turnout (\emph{v}) in year \emph{t} is a function of the year and whether they were stopped by the police.
+In the equation, \emph{\(\beta\)\textsubscript{1}Treated\textsubscript{i}} measures the historical difference between treated voters and their controls.
+\emph{\(\beta\)\textsubscript{2}Post Treatment\textsubscript{t}} measures whether turnout increased for controls in the first election following the treated voter's stop, while \emph{\(\beta\)\textsubscript{3}Treated\textsubscript{i} × Post Treatment\textsubscript{t}} tests whether turnout changed differently for treated voters than their controls in the election following their police stop.
+\emph{\(\beta\)\textsubscript{3\emph{, then, will capture the causal effect of a police stop on voter turnout.
+Finally, the matrix }\(\delta\)Z}i\textasciitilde{}} contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
+Equation 1 allows us to test Hypotheses 3:
+
+\textbf{Hypothesis 3}: Being ticketed reduces an individual's likelihood of turning out in the subsequent election.
+
+We also estimate Equation 2, in which the treatment effect is interacted with whether a voter is Black (\emph{\(\beta\)\textsubscript{4}Treated\textsubscript{i} × Post Treatment\textsubscript{t} × Black\textsubscript{i}}):
+
+\begin{gather}
+\label{eq:2}
+v_{it}=\beta_0+\beta_1Treated_{i}+\beta_2Post Treatment_{t} + \nonumber \\
+\beta_3Treated_{i}\times Post Treatment_{t} + \beta_4Treated_{i}\times Post Treatment_{t}\times Black_{i} +\\
+\delta{Y}_{i} + \delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
+\end{gather}
+
+where \emph{\(\delta\)Y\textsubscript{it}} includes the dummy for Black interacted with the treatment and post treatment dummies.
+
+Equation 2 allows us to test Hypotheses 4:
+
+\textbf{Hypothesis 4}: The effect of being ticketed on an individual's turnout is less negative / more positive if that individual is Black.
+
+Because Tampa holds off-year local elections, we are able to test whether ticketed voters target officials who are able to change local police practices.
+\protect\hyperlink{ref-Laniyonu2019}{Laniyonu} (\protect\hyperlink{ref-Laniyonu2019}{2019}) gives us reason to believe that the effect should be stronger for local elections.
+
+\textbf{Hypothesis 5}: Any potential mobilizing turnout effect in Tampa is stronger for local (mayoral) elections, since those elections directly affect police practices.
 
@@
 
-The results of the two-way fixed effects model are slightly different than what we saw in the 2018 cross-sectional approach; namely, while Table \ref{tab:twfe} indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not impact Black turnout.
+The results of the two-way fixed effects model are different than what we saw in the 2018 cross-sectional approach; namely, while Table \ref{tab:twfe} indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not significantly impact Black turnout.
 The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.06 percentage points.
-Moreover, because of the relative stability in fees and fines collections at the municipal level over this time period (the mean increase in per-capita fees and fines collections was just 6 percent, and the median municipality decreased by about 1.5 percent), it is not clear how informative this approach is.
 
 In Table \ref{tab:coarser}, we re-estimate the model from Table \ref{tab:twfe} but coarsen the data.
-Here, we test whether turnout changed for municipalities who increased their fees and fines collections differently than municipalities where collections stayed the same or decreased.
+Here, the dependent variable of interest is binary: we test whether turnout changed for municipalities who increased their per-capita fees and fines collections differently than municipalities where collections stayed the same or decreased.
 Municipalities that increased their per-capita fees and fines are considered ``treated.''
@@
 
-The coefficient on \emph{Treated × 2018} indicates that non-Black turnout dropped by about 0.5 percentage points in municipalities where fees and fines collections increased relative to other municipalities.
-While this coefficient is slightly positive for Black voters, it is not statistically significantly different from 0.
+The coefficient on \emph{Treated × 2018} indicates that non-Black turnout dropped by about 0.5 percentage points in municipalities where fees and fines collections increased, relative to other municipalities.
+While this coefficient is slightly \emph{positive} for Black voters, it is not statistically significantly different from 0.
 In other words, both Tables \ref{tab:twfe} and \ref{tab:coarser} indicate that increased fees and fines collections decrease non-Black turnout but have no impact on Black turnout.
@@
 
-To directly observe the effect of being ticketed on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
-As discussed above, we match (\protect\hyperlink{ref-Sekhon2011}{Sekhon 2011}) individuals who were stopped and assessed a fine between the 2012 and 2018 elections to individuals who were not stopped during this time period.\footnote{Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
-The full sample is used in the actual matching process.} Matching is done with replacement and ties are not broken, meaning some treated voters may have more than 2 controls; the regression weights reflect this possibility.
+To directly observe the effect of being stopped by the police on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
+As discussed above, we match individuals who were ticketed between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.\footnote{Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
+The full sample is used in the actual matching process.} Matching is done with replacement and ties are not broken, meaning some treated voters may have more than 1 control; the regression weights reflect this possibility.
 In Table \ref{tab:balance} we present the results of the matching algorithm.
@@
 \begin{singlespace}
-\begin{table}[H]
-
-\caption{\label{tab:balance-tab-chunk}\label{tab:balance} Balance Table}
+\begin{table}[!h]
+
+\caption{\label{tab:baltab-chunk}\label{tab:balance} Balance Table}
 \centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}[t]{lllllllll}
+\begin{tabular}[t]{llll}
 \toprule
-\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Means: Unmatched Data} & \multicolumn{2}{c}{Means: Matched Data} & \multicolumn{4}{c}{Percent Improvement} \\
-\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-9}
- & Treated & Control & Treated & Control & Mean Diff & eQQ Med & eQQ Mean & eQQ Max\\
+Variable & Treated Voters & Control Voters & Never Stopped\\
 \midrule
-\%White & 45.8\% & 47.4\% & 45.8\% & 45.8\% & 99.70 & 99.70 & 99.70 & 99.70\\
-\% Black & 26.1\% & 23.0\% & 26.1\% & 26.1\% & 99.85 & 99.85 & 99.85 & 99.85\\
-\% Latino & 19.1\% & 20.2\% & 19.1\% & 19.1\% & 99.97 & 99.97 & 99.97 & 99.97\\
-\% Asian & 2.0\% & 2.3\% & 2.0\% & 2.0\% & 100.00 & 100.00 & 100.00 & 100.00\\
-\% Male & 51.9\% & 50.8\% & 51.9\% & 51.2\% & 36.61 & 36.46 & 36.46 & 36.46\\
-\% Democrat & 43.6\% & 41.6\% & 43.6\% & 43.3\% & 86.44 & 86.44 & 86.44 & 86.44\\
-\% Republican & 22.9\% & 23.7\% & 22.9\% & 22.0\% & -5.57 & -5.57 & -5.57 & -5.57\\
-Age & 42.7 & 42.4 & 42.7 & 42.2 & -67.69 & 11.98 & 33.08 & 70.35\\
-Registration Date & 2006-09-25 & 2007-08-20 & 2006-09-25 & 2006-10-21 & 92.30 & 60.54 & 91.16 & 93.26\\
-Stops in pre-period & 2.248 & 1.437 & 2.248 & 2.206 & 94.79 & 69.37 & 94.81 & 95.91\\
-Turnout\textsubscript{t=-3} & 32.4\% & 28.4\% & 32.4\% & 32.5\% & 97.59 & 97.59 & 97.59 & 97.59\\
-Turnout\textsubscript{t=-2} & 30.2\% & 27.5\% & 30.2\% & 30.2\% & 99.94 & 99.94 & 99.94 & 99.94\\
-Turnout\textsubscript{t=-1} & 45.0\% & 38.2\% & 45.0\% & 45.0\% & 99.97 & 99.97 & 99.97 & 99.97\\
-Median Income & \$62,193 & \$63,412 & \$62,193 & \$62,111 & 93.27 & 82.89 & 79.16 & 68.07\\
-\% with Some College & 73.8\% & 74.4\% & 73.8\% & 73.9\% & 78.57 & 53.38 & 57.55 & 53.15\\
-Unemployment Rate & 6.7\% & 6.5\% & 6.7\% & 6.6\% & 49.02 & -19.29 & -20.95 & -17.34\\
+\%White & 47.4\% & 47.6\% & 62.2\%\\
+\% Black & 24.4\% & 25.1\% & 13.1\%\\
+\% Latino & 19.0\% & 19.3\% & 16.0\%\\
+\% Asian & 2.1\% & 2.1\% & 2.7\%\\
+\% Male & 53.2\% & 53.0\% & 42.8\%\\
+\% Democrat & 42.5\% & 43.1\% & 37.9\%\\
+\% Republican & 23.7\% & 23.6\% & 31.3\%\\
+Age & 42.5 & 41.8 & 51.9\\
+Median Income & \$62,836 & \$62,497 & \$67,897\\
+\% with Some College & 73.9\% & 74.1\% & 76.5\%\\
+Unemployment Rate & 6.6\% & 6.6\% & 5.9\%\\
+Turnout\textsubscript{t=-3} & 31.7\% & 31.7\% & \\
+Turnout\textsubscript{t=-2} & 29.6\% & 29.6\% & \\
+Turnout\textsubscript{t=-1} & 44.6\% & 44.6\% & \\
+Stops in pre-period & 2.2 & 1.9 & \\
+Paid Money & 89.1\% & 89.1\% & \\
+Civil Stop & 82.6\% & 82.6\% & \\
+Stopped by Tampa PD & 47.0\% & 47.0\% & \\
 \bottomrule
-\end{tabular}}
+\end{tabular}
 \end{table}
@@
 
-While Table \ref{tab:balance} indicates that our treatment voters and their matches are substantially similar to their matches, the validity of the difference-in-differences design requires that the treatment and control voters turned out at comparable rates in the baseline period.
+While Table \ref{tab:balance} indicates that our treatment voters and their matches are substantially similar to their matches, the validity of the difference-in-differences design requires that any turnout gap between treatment and control voters be comparable in the baseline period.
 In Figure \ref{fig:did1}, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped.
-The first election following a treated voter's stop is denoted as \emph{t = 0}; subsequent elections take higher positive numbers, while the years in which \emph{t} is less than zero are the periods prior to the stop.
-This means that for someone stopped in 2013, \emph{t} is 0 in 2014, while \emph{t} is equal to 0 in 2018 for an individual stopped between the 2016 and 2018 elections.
+The first election following a treated voter's stop is denoted as \emph{t = 0} while the years in which \emph{t} is less than zero are the periods prior to the stop.
+This means that for someone stopped in 2013 (and their controls), \emph{t} is 0 in 2014, while \emph{t} is equal to 0 in 2018 for an individual stopped between the 2016 and 2018 elections.
 
@@
 Because we matched treated and control voters based on turnout prior to the ticket, this is unsurprising.
-The visual results of the post-treatment trend corroborate what we found nationwide using the municipal-level data; namely, ticketing has a different effect for Black voters than for others..
-
-Figure \ref{fig:did2} makes this effect even clearer.
-Here, we limit the analysis to voters who were stopped within the 90 days prior to an election (and their controls).
-We expected that the ticket would be more salient for individuals stopped shortly before the election.
-This appears to be the case---\emph{especially for Black voters.}
-
-\begin{figure}[H]
-
-{\centering \includegraphics{draft_paper_files/figure-latex/did2-1}
-
-}
-
-\caption{\label{fig:did-2}Effect of Being Ticketed Within 90 Days of Election on Turnout}\label{fig:did2}
-\end{figure}
-
-Table \ref{tab:dind-table} formalizes Figures \ref{fig:did1} and \ref{fig:did2} into an ordinary least squares regression.
-Models 1 and 2 present the causal estimates of being stopped at any point in the two years prior to an election; Models 3 and 4 re-estimate the effect of being stopped within 90 days of an election.
-Models 1 and 3 show our overall causal effect, while Models 2 and 4 allow for the possibility that a ticket differentially mobilizes Black voters.
+
+Table \ref{tab:dind-table} formalizes Figure \ref{fig:did1} into an ordinary least squares regression.
+Model 1 shows our overall causal effect, while Model 2 allows for the possibility that a ticket differentially mobilizes Black voters.
 The coefficients of note are \emph{Treated × Post Treatment} and \emph{Treated × Post Treatment × Black}.
@@
 
-Model 3 indicates that a ticket is neither mobilizing nor demobilizing---the coefficient is small and nonsignificant (\emph{p} = 0.34) but that tickets do mobilize Black voters.
-Receiving a ticket increases the average turnout for Black voters in the first two elections by about 1.1 percentage points.
-Model 4 shows that ticketing shortly before an election increases the turnout of non-Black voters by about 0.9 percentage points, and there is no statistically significantly different effect for Black voters.
-However, Figure \ref{fig:did2} visually indicates that the effect might be larger for Black voters, and the coefficient on \emph{Treated × Post Treatment × Black} is large (as is its standard error).
-These two facts taken together indicate that our inability to detect a differentially mobilizing effect for Black voters stopped shortly before an election may have more to do with issues of statistical power than an additional effect that is really equal to zero.
+As both Figure \ref{fig:did1} and Table \ref{tab:dind-table} make clear, police tickets meaningfully depressed turnout.
+In models 1 and 2, the estimated overall treatment effect is -1.5 percentage points.
+In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---nonBlack turnout was depressed by 1.7 percentage points, while the negative effect was just -1.0 for Black individuals.
+Although the treatment effect is still sustantively quite large for Black individuals, the pattern follows our national analysis.
+It appears that, in Tampa and around the country, Black voters' turnout is not as negatively impacted by police contact as that of nonBlack individuals.
 
@@
 
+\leavevmode\hypertarget{ref-Imai2020}{}%
+Imai, Kosuke, In Song Kim, and Erik Wang.
+2020.
+{``Matching {Methods} for {Causal Inference} with {Time}-{Series Cross}-{Sectional Data}.''} \emph{Working Paper}.
+\url{https://doi.org/Matching\%20Methods\%20for\%20Causal\%20Inference\%20with\%20Time-Series\%20Cross-Sectional\%20Data}.
+
 \leavevmode\hypertarget{ref-EqualJusticeInitiative2017}{}%
@@
 
-\leavevmode\hypertarget{ref-Remster2018}{}%
+\leavevmode\hypertarget{ref-Remster2018a}{}%
 Remster, Brianna, and Rory Kramer.
-2018/ed.
-{``{SHIFTING POWER}: {The Impact} of {Incarceration} on {Political Representation}.''} \emph{Du Bois Review: Social Science Research on Race} 15 (2): 417--39.
-\url{https://doi.org/10.1017/S1742058X18000206}.
-
-\leavevmode\hypertarget{ref-Remster2018a}{}%
----------.
 2018.

### 2021-04-19 code/hills/01_process_raw_vf.R

@@ -97,33 +97,14 @@ v2019 <- select(v2019,
                 registration_date) %>% 
   mutate(latest_mayor = T)
 roll <- bind_rows(roll, filter(v2019, !(voter_id %in% roll$voter_id)))
-#############################
-v2020 <- fread("E:/rolls/florida/FL 2021-03-09/FL 2021-03-09/20210309_VoterDetail/HIL_20210309.txt")
-colnames(v2020) <- vf_names
-v2020 <- select(v2020,
-                voter_id,
-                name_last,
-                name_first,
-                residence_address_line_1,
-                residence_address_line_2,
-                city = residence_city,
-                state = residence_state,
-                zip = residence_zipcode,
-                gender,
-                race,
-                birth_date,
-                party_affiliation,
-                registration_date) %>% 
-  mutate(latest_mayor = T)
-roll <- bind_rows(roll, filter(v2020, !(voter_id %in% roll$voter_id)))
-rm(v2012, v2014, v2016, v2018, v2019, v2020)
+
+rm(v2012, v2014, v2016, v2018, v2019)
 ##################################################
 hists <- rbindlist(lapply(c("E:/rolls/florida/FL-2013-1/VoterHistory_20130203/HIL_H_20130203-ReSave.txt",
                             "E:/rolls/florida/2014_12/VoterHistory/VoterHistory/VoterHistory/HIL_H_20141208.txt",
                             "E:/rolls/florida/2016_12/20161206_VoterHistory/HIL_H_20161206.txt",
                             "E:/rolls/florida/2018_12/Voter_History_20181211/20181211_VoterHistory/HIL_H_20181211.txt",
-                            "E:/rolls/florida/2019_08/Voter_History_20190813/20190813_VoterHistory/HIL_H_20190813.txt",
-                            "E:/rolls/florida/FL 2021-03-09/FL 2021-03-09/20210309_VoterHistory/HIL_H_20210309.txt"),
+                            "E:/rolls/florida/2019_08/Voter_History_20190813/20190813_VoterHistory/HIL_H_20190813.txt"),
                           fread))
 
 
[…]

### 2021-04-19 code/hills/02_download_hills_stops.R

@@ -23,7 +23,7 @@
 #            law_enf_agency_name) %>%
 #     mutate(civil = 1,
 #            tampa_pd = grepl("tampa police", tolower(law_enf_agency_name)),
-#            tampa_pd = ifelse(tampa_pd, T, law_enf_agency_name == "TPD")) %>% 
+#            tampa_pd = ifelse(tampa_pd, T, law_enf_agency_name == "TPD")) %>%
 #     select(-law_enf_agency_name)
 # 
 #   return(ja)
@@ -49,7 +49,7 @@
 #              law_enf_agency_name) %>%
 #       mutate(civil = 0,
 #              tampa_pd = grepl("tampa police", tolower(law_enf_agency_name)),
-#              tampa_pd = ifelse(tampa_pd, T, law_enf_agency_name == "TPD")) %>% 
+#              tampa_pd = ifelse(tampa_pd, T, law_enf_agency_name == "TPD")) %>%
 #       select(-law_enf_agency_name)
 # 
 #     return(ja)
@@ -63,143 +63,142 @@
 #                  last_name), ~ gsub("[[:punct:]]| ", "", ifelse(. == "", NA, toupper(.))))
 # 
 # saveRDS(hills_stops, "temp/hills_stops.rds")
-#
-# hills_stops <- readRDS("temp/hills_stops.rds")
-# 
-# zeros_only <- hills_stops %>%
-#   filter(offense_date > "2012-11-06",
-#          offense_date <= "2018-11-06")
-# 
-# zeros_only <- zeros_only[,
-#                          .(max_amount = max(amount_paid)),
-#                          .(first_name, last_name, date_of_birth)] %>%
-#   filter(max_amount == 0) %>%
-#   select(first_name, last_name, date_of_birth) %>%
-#   mutate(exclude = 1)
-# 
-# saveRDS(zeros_only, "temp/stopped_no_fine.rds")
 
-##########
-# 
-# pre12 <- filter(hills_stops, offense_date <= "2012-11-06")[,
-#                                                            .(stop_count = .N),
-#                                                            .(first_name, last_name, date_of_birth, offense_date)]  # using data.table syntax for speed
-# 
-# pre12 <-  pre12[,
-#                 .(stop_count = .N),
-#                 .(first_name, last_name, date_of_birth)]  # using data.table syntax for speed
-# 
-# pre14 <- filter(hills_stops, offense_date <= "2014-11-04")[,
-#                                                            .(stop_count = .N),
[…]

### 2021-04-19 code/hills/03_genmatch_weights.R

@@ -41,7 +41,7 @@ hills14_c <- filter(hills_pre_match, first_tr_year == "2016-11-08",
   
 hills14 <- bind_rows(hills14_t, hills14_c) %>%  
   mutate(first_tr_year = 1) %>% 
-  select(-v14, -v16, -pre) %>% 
+  select(-v14, -v16) %>% 
   rename(v1 = v08,
          v2 = v10,
          v3 = v12)
@@ -94,7 +94,7 @@ samp <- pre %>%
 
 match_data <- samp %>% 
   select(-voter_id, -treated, -GEOID, -amount_paid, -last_date,
-         -v08, -v16, -pre, -v10, -reg_date) %>% 
+         -v08, -v16, -v10, -reg_date) %>% 
   mutate_at(vars(white, black, latino, asian, male, dem, rep, v1, v2, v3, paid), ~ ifelse(. == T, 1, 0)) %>% 
   select(first_tr_year, paid, civil, tampa_pd, everything())
 

### 2021-04-19 code/hills/04_match.R

@@ -1,3 +1,8 @@
+
+## needs to be run on nyu hpc or its way too slow
+## set seed for reproducibility. this is a random 5-digit number: floor(runif(1, min = 10000, max = 99999))
+set.seed(45251)
+
 library(Matching)
 library(data.table)
 library(scales)
@@ -24,7 +29,7 @@ hills14_c <- filter(hills_pre_match, first_tr_year == "2016-11-08",
 
 hills14 <- bind_rows(hills14_t, hills14_c) %>%  
   mutate(first_tr_year = 1) %>% 
-  select(-v14, -v16, -pre) %>% 
+  select(-v14, -v16) %>% 
   rename(v1 = v08,
          v2 = v10,
          v3 = v12)
@@ -68,8 +73,7 @@ hills18 <- bind_rows(hills18_t, hills18_c) %>%
          v3 = v16)
 
 ###########################################
-pre <- bind_rows(hills14, hills16, hills18) %>% 
-  select(-v08, -v16, -pre, -v10)
+pre <- bind_rows(hills14, hills16, hills18)
 
 saveRDS(pre, "temp/real_pre_match_hills.rds")
 ids <- pre %>%
@@ -77,7 +81,8 @@ ids <- pre %>%
   select(id, voter_id, first_tr_year)
 
 X <- pre %>%
-  select(-voter_id, -treated, -GEOID, -amount_paid, -last_date, -reg_date) %>% 
+  select(-voter_id, -treated, -GEOID, -amount_paid, -last_date,
+         -v08, -v16, -v10, -reg_date) %>% 
   mutate_at(vars(white, black, latino, asian, male, dem, rep, v1, v2, v3, paid), ~ ifelse(. == T, 1, 0)) %>% 
   select(first_tr_year, paid, civil, tampa_pd, everything())
 
@@ -119,98 +124,3 @@ matches <- left_join(matches, ids, by = c("group" = "id")) %>%
   rename(group = voter_id)
 
 saveRDS(matches, "temp/matches_hills_y.rds")
-
-balance <- MatchBalance(treated ~ white + black + latino + asian + male +
-                          dem + rep + age + reg_date + pre_stops + v1 + v2 + v3 +
-                          median_income + some_college + unem,
-                        data = pre, match.out = mout)
-
-saveRDS(balance, "temp/balance_table.rds")
-
[…]

### 2021-04-19 code/hills/05_regression.R

@@ -53,17 +53,15 @@ cleanup("matches")
 gc()
 ll <- matches %>%
   filter(first_tr_year - last_date <= 90, period <= 0.5) %>%
-  group_by(treated, period, black_t, paid) %>%
+  group_by(treated, period, black) %>%
   summarize(to = weighted.mean(to, weight)) %>% 
   mutate(treated = ifelse(treated, "Treated", "Control"),
-         black = ifelse(black_t, "Black Voters", "Non-Black Voters"),
-         paid = ifelse(paid, "Paid Fine", "Did Not Pay Fine"))
-
+         black = ifelse(black, "Black Voters", "Non-Black Voters"))
 
 ll$treated <- factor(ll$treated, levels = c("Treated", "Control"))
 
 p1 <- ggplot(data = ll) + 
-  facet_grid(paid ~ black) +
+  facet_grid( ~ black) +
   geom_rect(aes(xmin = 0.5-.125, xmax = 0.5, ymin = 0, ymax = Inf),
             alpha = 0.03, color = "black", fill = "yellow") +
   geom_line(data =ll, aes(x = period, y = to, linetype = treated)) +
@@ -90,7 +88,7 @@ saveRDS(p1, "temp/within90days_y.rds")
 ##########################
 ll <- matches %>%
   filter(period <= 0.5) %>% 
-  group_by(treated, period, black = black_t) %>%
+  group_by(treated, period, black) %>%
   summarize(to = weighted.mean(to, weight)) %>% 
   mutate(treated = ifelse(treated, "Treated", "Control"),
          black = ifelse(black, "Black Voters", "Non-Black Voters"))
@@ -129,12 +127,20 @@ matches$days_before = as.numeric(matches$first_tr_year - matches$last_date)
 dat1 <- filter(matches, period <= 0.5)
 
 m1 <- to ~ treated * post + as.factor(year)
-m2 <- to ~ treated * post * days_before + as.factor(year)
-m3 <- to ~ treated * post * black_t + as.factor(year)
-m4 <- to ~ treated * post * civil + as.factor(year)
-m5 <- to ~ treated * post * paid + as.factor(year)
 
-models1 <- lapply(c(m1, m2, m3, m4, m5), function(f){
+m2 <- to ~ treated * post + as.factor(year) +
+  white + black + latino + asian + male +
+  dem + rep + age + reg_date + pre_stops + v1 + v2 + v3 +
[…]

### 2021-04-30 markdown/draft_paper.Rmd
first full draft

@@
 ---
-title: "Policing for Profit and the Undermining of Democracy"
+title: "Policing for Profit and the Mobilization of Black Voters"
 
@@
   The American criminal legal system is an important site of political socialization: sociologists show how the alienating effect of criminalization pushes people away from public institutions, and political scientists have measured the effects of policing and incarceration on political participation.
-Despite this burgeoning literature, no research has directly investigated how ticketing for low-level offenses affects political participation.
-Using data from the Census of Governments and the national voter file, we test the causal effect of fines and fees practices on American voting behavior at the city level (aggregate).
-Additionally, we exploit individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019 to determine whether getting a ticket impacts political participation.
+Despite this burgeoning literature, no research has directly investigated how police ticketing practices affect political participation.
+We use three approaches to answer this question: national survey data, a city-level analysis using Census of Governments data and the national voter file, and individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019.
+The survey data show that Black people who report that they were recently stopped by police are more likely to vote compared to those who were not stopped.
 Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.6 percentage point turnout decrease but was not associated with Black turnout.
-In Tampa, Florida, we estimate that being ticketed decreases an individual’s likelihood of voting in federal elections by 1.3 percentage points, but we do not uncover evidence of a distinct political effect for Black voter turnout.
-In local elections, however,
+In Tampa, Florida, we estimate that being ticketed decreases an individual’s likelihood of voting in federal elections by 1.7 percentage points, but depressive effects are smaller for Black residents.
+
   |
@@
   **Keywords**: voting, monetary sanctions, race, punishment, political participation
-nocite: | 
-  @Burch2011, @Burch2013, @White2019a
-
 ---
@@
 arrest, conviction, incarceration) consistently discourages voting [@Weaver2010; @Burch2011; @White2019a].
-This work, however, has largely focused on the effects of highly consequential contact with the criminal legal system such as incarceration and felony convictions [@Burch2014; @Lee2014].
-Our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
-
-The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures participation.
+Such work has largely focused on the effects of highly disruptive contact with the criminal legal system such as incarceration and felony convictions [@Burch2014; @Lee2014].
+This paper is the first to explicitly theorize how local ticketing practices shape the political socialization of ticketed individuals.
+Additionally, our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
+The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures political participation.
 Past work looking at the individual-level effects of low-level contact has relied entirely on survey or qualitative data [e.g.
 @Walker2014; @Weaver2010].
-Their in-depth research allows for the testing of specific psychological mechanisms and personal interpretations of criminal legal contact, but does not allow us to generalize more broadly.
+Existing research allows for the testing of specific psychological mechanisms and personal interpretations of criminal legal contact, but does not allow us to generalize more broadly.
 As Weaver and Lerman [-@Weaver2010, page 821] note, it may also introduce measurement bias.
@@
 
-We begin by joining fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for each municipality in the country.
+Before turning to the administrative data, we begin with a novel analysis of 2016 and 2020 national survey data regarding voters’ experience with police stops and arrests.
+We find that Black respondents who reported personal or proximal experience with police stops in the last 12 months are more likely to vote than Black people who did not, while we find no statistically significant relationship between stops and voting among non-Black respondents.
+
+Next, we join fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for each municipality in the country.
 While we find that increased fees and fines likely cause lower turnout among non-Black Americans, we find no effect of fees and fines on Black turnout.
 
-Because our national analysis does not allow us to directly observe the causal effect of police ticketing on voter turnout, we use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were ticketed between the 2012 and 2018 elections.
+Because our national analyses do not allow us to directly observe the causal effect of police ticketing on voter turnout, we use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were ticketed between the 2012 and 2018 elections.
 By matching individual voters who were ticketed to similar voters who were ticketed at later points and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout.
-We find that being ticketed reduces the chance that an individual will turn out in the subsequent election.
+We find that being ticketed reduces the chance that an individual will turn out in the subsequent election, and that this effect is smaller for Black voters.
 
-We demonstrate that police ticketing practices---the most widespread form of police contact in America---influence the political behavior of Americans.
-This finding supports and extends Vesla Weaver and Amy Lerman’s theory of criminal legal contact discouraging political participation [@Weaver2010].
+We demonstrate that police ticketing practices---the most widespread form of police contact in America---substantially reduce the turnout of non-Black American voters, but can mobilize Black voters.
+Our findings complicate existing theories of how criminalization politically socializes Americans, and Black Americans in particular [@Weaver2010].
+Additionally, while all forms of criminalization likely contribute to a subjective experience of alienation or group-level exclusion among Black Americans that is well-documented in sociological scholarship [@Bell2017; @Desmond2016], our contribution emphasizes the need for further research regarding how different forms of criminalization affect group-level perceptions of government and resultant political behavior.
+Accordingly, we propose a new theory explaining how ticketing may uniquely catalyze mobilizing narratives of racial injustice.
 Our findings are relevant for interdisciplinary scholars of crime, race, politics, political economy, social movements, and policing.
@@
 
-In order to theorize how fines and fees affect political behavior, we consider (1) how criminalization directly shapes the electorate, (2) the influence of criminalization on political socialization, and (3) how contemporary ticketing practices are tied to a longer legacy of racist exploitation.
+In order to theorize how fines and fees affect political behavior, we consider (1) how criminalization directly shapes the electorate, (2) the existing scholarly understanding of the influence of criminalization on political socialization, and (3) how contemporary ticketing practices are tied to a longer legacy of racist exploitation and thus ripe for political mobilization around narratives of racial injustice.
 
@@
 states passed laws denying voting rights to people who were convicted of felonies.
-In their analysis of how racial threat catalyzes felon disenfranchisement, @Behrens2003 found that increases in a state’s nonwhite prison population drastically increase the likelihood of legislation permanently disenfranchising people convicted of felonies.
-As @Shofner1963 notes, this has often been tied explicitly to the increased presence of Black Americans in the electorate.
+In their analysis of how racial threat catalyzes felon disenfranchisement, @Behrens2003 found that increases in the share of a state’s prison population that is nonwhite drastically increases the likelihood of legislation permanently disenfranchising people convicted of felonies.
+As @Shofner1963 notes, felony disenfranchisement has often been tied explicitly to the increased presence of Black Americans in the electorate.
 
@@
 More specifically, many states require payment of fees as a condition of criminal legal supervision or the payment of all legal financial obligations as a condition of completing a sentence, and failure to comply with supervision or sentence completion conditions can be a barrier to voting rights restoration.
-These political barriers also disproportionately affect Black people.
+Such political barriers also disproportionately affect Black people.
 In Alabama, for example, Black people with felony convictions applying to have their voting rights restored were 26 percentage points more likely to have their application denied over outstanding fines and fees [@Meredith2017].
@@
 After Floridians passed Amendment 4 to restore voting rights to individuals with felony convictions in 2018, Florida Republicans passed legislation requiring these individuals to pay off the fines and fees associated with their original sentence.
-Because Florida does not maintain good records on who owes how much, this has proved to be a major hurdle for potential voters.
-Despite a dissenting judge arguing that ““[h]ad Florida wanted to create a system to obstruct, impede, and impair the ability of felons to vote under Amendment 4, it could not have come up with a better one,” an en banc ruling by the U.S.
-Court of Appeals for the 11th Circuit upheld this legislation.^[Jones et al.
-v.
-DeSantis et al., 4:19cv300-RH/MJF (United States Court of Appeals for the Eleventh Circuit).]
+Because Florida does not maintain good records on who owes how much, the new law has proved to be a major hurdle for potential voters.
+As @Morris2021 argues, this could have severe implications for the future democratic participation of those excluded anew from the electorate after the state passed the amendment.
 
@@
 
-Beyond direct disenfranchisement, the spatial and racial concentration of criminalization significantly influences affected communities’ perceptions of government.
+Beyond de jure disenfranchisement, the spatial and racial concentration of criminalization influences affected communities’ perceptions of government.
 Monica Bell calls this process “legal estrangement,” a conceptual framework meant to capture those perceptions and cultural attitudes (“legal cynicism”) as well as the historical-structural conditions that produced them [@Bell2017].
@@
 
-In addition to influencing perceptions of government, recent scholarship indicates that criminalization influences political behavior.
+Sarah Brayne found related results in her analysis of survey data---as the intensity of criminal legal contact escalates (i.e.
+stopped, arrested, convicted), people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions [@Brayne2014].
+She calls this phenomenon “system avoidance,” and while her analysis did not specifically assess voting behavior, her findings demonstrate how criminal legal contact can discourage Americans’ participation in public institutions as well as how the effect may vary alongside the intensity of criminal legal intervention.
+Similarly, @Remster2018a finds that men who return home from prison are more likely to avoid contact with their childrens’ schools.
+
+In addition to influencing perceptions of government and participation in public institutions, recent scholarship indicates that criminalization influences political behavior.
 The “hidden curriculum” of the criminal legal system [@Justice2014; @Meares2017] teaches individuals about their position within the political system, and the criminal legal system consequently serves as a primary site of political socialization for convicted individuals and their families [e.g.
 @Lee2014].
-Several studies indicate that potential voters are discouraged from voting due to personal or proximal contact with the criminal legal system, and this chilling effect is most salient for what we consider “high-intensity” criminal legal involvement, such as being convicted of a crime or being incarcerated.
 
@@
 
-Sarah Brayne calls this phenomenon “system avoidance,” and she found similar results in her analysis of survey data: as the intensity of criminal legal contact escalates, people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions [@Brayne2014].
-Brayne’s analysis demonstrates how lower-intensity criminal legal contact can be theorized as a mechanism for discouraging Americans’ participation in public institutions.
-Similarly, @Remster2018a finds that men who return home from prison are more likely to avoid contact with their childrens’ schools.
+Lerman and Weaver’s finding has been corroborated by administrative data: Ariel White found that short jail sentences in Harris County, Texas reduced Black defendant turnout in subsequent elections by 13 percentage points---but the effect on white turnout was not statistically significant [@White2019].
+Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level [@Burch2014].
 
-It may be the case that Black and non-Black Americans employ different self-preservation strategies, however.
-@Walker2020 makes clear that, when Black Americans locate their contact with the criminal legal system in a narrative of racial injustice, they can be politically mobilized; on the other hand, @Lerman2014 shows that Black individuals’ ability to situate their life experiences in a larger legacy of exploitation can be demobilizing.
-Turning to administrative data analysis, Ariel White’s analysis of how short jail sentences affect voting in Harris County, Texas found that Black defendant turnout in subsequent elections dropped by 13 percentage points---but the effect on white turnout was not statistically significant [@White2019].
+Although most work documents a uniformly demobilizing effect from contact with the criminal legal system, recent work from Hannah Walker [-@Walker2020; -@Walker2020a] complicates this narrative by arguing that, when Black Americans understand their contact with the criminal legal system in the context of a narrative of racial injustice, such contact can actually prove mobilizing.
+She explains: “experiences with punitive policies are subject to interpretation and, when understood through narratives of injustice, lead to wholly different participation outcomes than we usually predict” [@Walker2020, page 132].
+While she finds that this sense of injustice is especially likely to increase political participation in non-voting ways (such as attending a protest or signing a petition), the logic could extend to electoral participation as well given a strong narrative or relatively weak contact with the criminal legal system.
 
-Proximal exposure to criminalization---“having a loved one who is a custodial citizen without yourself having had contact” [@Walker2017]---also influences Americans’ perceptions of government and political behavior, and the emerging literature has produced mixed findings of its effect on civic engagement.
-Using survey and ethnographic interview data, @Lee2014 found that adult children of incarcerated parents are less likely to vote, report lower trust in government, and are less likely to engage in other prosocial behaviors like community service.
-@Sugie2015 used survey data to show that partners of formerly incarcerated men are less likely to vote, but not less likely to participate in religious or civic institutions.
-
-Hannah Walker’s research specifically tests differences between the effects of proximal and personal criminal legal contact on political behavior, and her findings underscore how a “linked fate” political analysis could catalyze distinct political behavior among Black voters [@Walker2014].
-Using data from a 2012 survey of Washington state residents, she found that as the degree of an individual’s proximity to a criminalized person increases, so does their likelihood of participating in political activities other than voting (such as signing a petition, volunteering, donating to politicians, etc.).
-With respect to voting, she found that personal contact was demobilizing, while proximal contact had no statistically significant effect.
-
-Walker found that nonwhite people who had experienced *either* proximal or personal contact *at any level of intensity*, including being stopped and questioned by police, were mobilized to take part in nonvoting political activity---and the same held true for whites, but with a much smaller effect size.
-Walker theorizes that this finding suggests that nonwhite people view criminalization “as a form of systemic political threat,” an analysis comparable to “linked fate.” Additionally, Walker’s survey questions excluded “minor traffic stops,” the primary focus of this paper.
-
-Ariel White leveraged administrative court records from Harris County, Texas, to identify voters who lived within individuals who were charged with a misdemeanor offense and arrested, convicted, or jailed [@White2019].
-She found that living with someone who was charged but not convicted in the 30 day period preceding an election increased voter turnout by 3 percentage points, whereas “convicted but not jailed” decreased turnout by 6 percentage points and “convicted and jailed” decreased turnout by 12 percentage points.
-This provides further support for the theory that increasing intensity of criminalization could change the direction of the effect of criminalization on political behavior---and, in fact, that lower-level contact can mobilize even as higher-level contact demobilizes.
-
-Although geographic or spatial analyses of how criminalization affects political socialization technically move beyond proximal contact as an extant conceptual framework, similar mechanisms should operate on the neighborhood level.
-Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level [@Burch2014].
-@Morris2020 similarly finds that neighborhoods with more active voters lost to felony disenfranchisement turned out at lower rates in the 2017 mayoral race in NYC, and that this effect was particularly pronounced in Black neighborhoods.
-
-This chilling effect does not appear uniformly across all studies.
-In New York City, geographically concentrated stop-and-frisk activity was associated with *reduced* turnout in Congressional elections, but *increased* turnout in the 2008 presidential election as well as the local mayoral election in 2013 [@Laniyonu2019].
-If proximal contact mobilizes, then, mobilized voters are likely targeting officials who they perceive as holding the power to change police practices.
-To the extent that descriptive representation mitigates exploitative fines and fees practices [@Sances2017], this could constitute an effective political strategy.
-
-Over the past few years, scientific understanding of the political effects of more serious interactions with the criminal legal system has grown by leaps and bounds.
-The following table summarizes our understanding of the literature.
-As the table makes clear, a large body of research has now demonstrated the negative effects of high-level contact with the criminal legal system on voter turnout.
-Although lower-level stops are far more frequent, our knowledge of their (de)mobilizing effects is under-developed.
-
-\begin{singlespace}
-\input{../raw_data/lit_tab.tex}
-\end{singlespace}
-
-Most of the aforementioned studies were conducted using data collected before the rise of the Black Lives Matter movement in 2013, which could be construed as a significant development for the political socialization of Black Americans with respect to policing and incarceration.
-The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious.
-Though racist police violence was and is a focal point for many Black Lives Matter actions, local chapters frequently use policing as an entry point into a wider set of demands regarding the material security of Black Americans and their marginalization in American politics---and these demands affect police practices.
-One recent study found that census places that saw Black Lives Matter protests experienced a 15 to 20 percent decrease in police killings over the following five year period [@Campbell2021].
-It’s possible that any potentially mobilizing effects of criminal legal contact became stronger in the 2010---in other words, Black Lives Matter could have facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis.
-That said, @Laniyonu2019 did demonstrate mobilization in Black neighborhoods before the beginning of the Black Lives Matter movement.
+Despite the growing body of high-quality scholarship on the democratic implications of the American criminal legal system, we still know remarkably little about the effects of the most routine sort of contact---police stops and tickets that do not result in an arrest.
+We leverage Walker’s novel insights about the potentiality of a narrative of injustice to re-think how these sorts of contact with the state can structure political participation.
 
@@
 
-We argue that fines and fees invoke a distinct historical legacy of racist exploitation that merits further study.
+Fines and fees are situated in a distinct historical legacy of racist exploitation that may uniquely facilitate a collective “sense of injustice” among Black Americans---the sort of collective perception that @Walker2020a argues could prove to be politically mobilizing.
 
 Cedric Robinson’s articulation of racial capitalism offers a useful theoretical framework for interpreting the trajectory of American anti-Black political economy [@Robinson2000].
-Brittany Friedman theorizes fines and fees as a “progression of racial capitalism penology,” emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices [@Friedman2020, page177].
+Brittany Friedman theorizes fines and fees as a “progression of racial capitalism penology,” emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices [@Friedman2020, page 177].
 Robinson argues that European industrial capitalism continued a longer political-economic trend of differentiating racial groups in order to dispossess them and exploit their labor.
-Indeed, early American agrarian and mercantile economies relied on the labor-power of enslaved Black people, and the slave patrols created to terrorize and discipline enslaved laborers are the earliest antecedents of contemporary American police departments [@DuBois1935; @Hadden2003].
 
-Following the Civil War and the rise of global industrial capitalism, slave patrols were replaced by more formal police forces and vigilante lynch mobs [@EqualJusticeInitiative2017; @Hinton2021].
+Following the Civil War and the rise of global industrial capitalism, slave patrols were replaced by more formal police forces [@EqualJusticeInitiative2017; @Hinton2021].
 The implementation of the Black Codes, convict leasing, and sharecropping systems marked a transition to a new stage of racial capitalism, wherein criminalization provided an easily-exploited labor supply that offset costs that the state incurred by coercing their labor [@Lichtenstein1996; @Mancini1978].
-Criminal legal debt has also been directly compared to sharecropping because both structures share “a long-term pattern of financial exploitation based on race… that limits the life-choices of the affected population” [@Blessett2016, page 113].
+Contemporary fines and fees practices have been directly compared to sharecropping because both structures share “a long-term pattern of financial exploitation based on race… that limits the life-choices of the affected population” [@Blessett2016, page 113].
 
@@
 At the level of federal policy, racial threat and whites’ attribution of criminality to Blackness [@Muhammad2010] prompted a shift “from the War on Poverty to the War on Crime” wherein Black communities’ demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration [@Hinton2017; @Vargas2017a].
-Ruth Wilson Gilmore explains how mid to late 20th-century whites “demanded that the state become leaner and meaner, except when directed to do otherwise”---in other words, Keynesian welfare guarantees were undermined by the racist myth of “welfare queens” and supplanted by expanded police power [@Gilmore2007, page 53].
 
@@
 At the local level, this means that police budgets today constitute about thirty percent of city budgets nationwide, and cities where residents have lower median incomes dedicate a larger proportion of spending to policing [@Friedman2020].
+Similarly, municipalities where a larger share of the population is Black raise more fines and fees revenue per-capita than less-Black municipalities [@Sances2017; @UnitedStatesCommissiononCivilRights2017].
+Although major urban centers collect high dollar amounts of fines and fees, some of the most egregious ticketing practices measured on a per-capita basis are concentrated in suburbs or smaller cities with municipal courts---Ferguson being a prominent example [@UnitedStatesDepartmentofJusticeCivilRightsDivision2015; @Mughan2020].
 In municipalities with substantial Black populations, then, people who are most heavily affected by criminalization are expected to foot the bill for their own mistreatment.
+@Sances2017, however, finds that the discriminatory imposition of tickets can be mitigated by descriptive representation (i.e.
+Black elected officials): The positive association between cities’ reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator [@Sances2017].
 
-Today, fines and fees primarily target Black Americans: traffic stops and searches disproportionately affect Black motorists nationwide [@Pierson2020], and a host of local analyses confirm this finding [@Dunn2009; @Goncalves2020; @Mughan2020].
-In criminal court proceedings, Black defendants tend to face more severe monetary sanctions [@Edwards2020; @Harris2011].
+Racial capitalist political economy imposes fiscal constraints regardless of city officials’ identities or intentions.
+In their study of fines and fees reliance in Chicago suburbs, Josh Pacewicz and John Robinson, III show how the racialization of municipal opportunity structures prevents majority-Black suburban governments from acquiring sufficient revenue from “good” sources such as sales taxes or property taxes, catalyzing a reliance on fines and fees to fund government services [@Pacewicz2020].
+Pacewicz and Robinson III note that racialized municipal opportunity structures are tied to the political-historical processes of neoliberalism and fiscal austerity, an observation that aligns with recent scholarship detailing the origins of fees paid by incarcerated people [@Kirk2020].
 
-In 2020, a Federal Reserve survey found that five percent of white respondents reported “unpaid legal expenses, fines, or court costs,” whereas twelve percent of Black respondents reported such debt [@BoardofGovernorsoftheFederalReserveSystem2020].
-Across the country, city government reliance on fines and fees revenue is associated with larger Black populations [@UnitedStatesCommissiononCivilRights2017].
-Although major urban centers collect high dollar amounts of fines and fees, some of the most egregious ticketing practices measured on a per-capita basis are concentrated in suburbs or smaller cities with municipal courts---Ferguson being a prominent example [@UnitedStatesDepartmentofJusticeCivilRightsDivision2015; @Mughan2020].
-The positive association between cities’ reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator, however [@Sances2017].
+Today, fines and fees primarily target Black Americans: traffic stops and searches disproportionately affect Black motorists nationwide [@Pierson2020], and a host of local analyses confirm the national finding [@Dunn2009; @Goncalves2020; @Mughan2020].
+In criminal court proceedings, Black defendants tend to face more severe monetary sanctions [@Edwards2020; @Harris2011], and a 2020 Federal Reserve survey found that five percent of white respondents reported “unpaid legal expenses, fines, or court costs,” whereas twelve percent of Black respondents reported such debt [@BoardofGovernorsoftheFederalReserveSystem2020].
 
-Racial capitalist political economy imposes fiscal constraints regardless of city officials’ intentions.
-In their study of fines and fees reliance in Chicago suburbs, Josh Pacewicz and John Robinson, III show how the racialization of municipal opportunity structures prevents majority-Black suburban governments from acquiring sufficient revenue from “good” sources such as sales taxes or property taxes, catalyzing a reliance on fines and fees to fund government services [@Pacewicz2020].
-Pacewicz and Robinson III note that these racialized municipal opportunity structures are tied to the political-historical processes of neoliberalism and fiscal austerity, an observation that aligns with recent scholarship detailing the origins of fees paid by incarcerated people [@Kirk2020].
-The late 20th century “property tax revolt” most significantly benefited white homeowners [@Martin2017], and without property tax hikes as a revenue-raising option, smaller cities and towns have few choices.
-
-Research regarding police stops and searches in response to local fiscal crisis shows how decreasing local revenues affect racist police practices.
+Research regarding police stops and searches in response to local fiscal crises shows how decreasing local revenues affect racist police practices.
 One study of all U.S.
@@
 
-With this history in mind, we argue that Black Americans can situate exploitative ticketing practices in a longer historical legacy of collective disparate treatment and violence at the hands of the state, which may facilitate a stronger collective political analysis when police ticketing practices become more extreme.
-The historical use of fees and fines make this sort of police contact especially likely to evoke such narratives.
-Accordingly, we expect that Black voters’ political behavior in response to police ticketing will be distinct from the political behavior of white voters.
+Black Americans can therefore situate exploitative ticketing practices in a longer historical legacy of collective disparate treatment and violence at the hands of the state.
+We argue that Black voters’ recognition of discriminatory ticketing practices facilitates a “linked fate” political analysis that motivates voting behavior distinct from other forms of criminalization, such as criminal conviction or incarceration.
+We expect both ticketing and incarceration to spark a recognition of “a sense of injustice” among Black Americans, but we argue that ticketing should ultimately mobilize Black voters (unlike incarceration, which discourages Black voters more than whites [@White2019]).
+
+Ticketing produces substantively different experiences than being arrested or incarcerated.
+While tickets can lead to driver’s license suspensions or, in a smaller subset of cases, nonpayment incarceration, tickets are generally far less disruptive than criminal convictions and prison terms, and we argue that this difference should lead to different political behaviors.
+For example, one participant in @Lerman2014 who had served five years of probation after a criminal conviction reported, “I feel like if I contact a senator or governor, they’ll probably want to put me in jail and leave me as a troublemaker...
+That’s how I actually feel: ‘I better stay below the radar ’cause this guy’s tryin’ to start trouble’” [@Lerman2014, page 210].
+While formerly incarcerated people or people who have experienced criminal legal supervision may avoid voting due to the same type of fear of state surveillance and control that motivates their avoidance of medical or educational institutions [@Brayne2014], we argue that being ticketed should not produce the same chilling effect---ticketing should not prompt Black people to use political withdrawal as a self-preservation strategy.
+
+Additionally, we argue that “policing for profit”---the experience of being ticketed while a municipality is palpably ramping up its fines and fees practices to collect revenue---is also substantively distinct from the experience of being arrested or incarcerated.
+In doing so, we extend Epp et al.’s theory of pretextual traffic stops politically socializing Black voters to the specific context of discriminatory police ticketing [@Epp2014].
+Black Americans who experience disproportionate ticketing are likely aware that they are being targeted by police for reasons unrelated to traffic safety.
+One Buffalo, New York resident who is a plaintiff in a lawsuit regarding racist ticketing practices told a local newspaper in 2019: “In my mind, they weren’t balancing the budgets for Black lives, but with Black lives” [@McLeod2019].
+The city created a new traffic violations agency in 2015, spurring its yearly ticketing numbers to jump from around 32,000 to over 52,000.
+This financial aspect of ticketing should make it distinct from arrests and incarceration: much like the coercion of labor under the Black Codes, contemporary fines and fees practices are blatantly an effort to extract wealth from Black Americans.
+Although 20th century political rhetoric centered public safety as the mission of policing [CITE], exploitative ticketing practices cannot be reconciled with such rhetoric.
+In other words, to the extent that mass incarceration could be justified using narratives of “colorblind racism” (i.e., there’s a lot of crime happening in Black communities, so that’s why there’s more policing in those areas), racist ticketing practices do not enjoy the same rhetorical convenience.
+
+Ticketing is by far the most common form of criminal legal contact; in 2018, more than 24 million people experienced police contact in the context of a traffic stop, whereas about 5.17 million people are currently disenfranchised as a result of a felony conviction [@Harrell2020; @Uggen2020].
+At the same time, the most egregious local ticketing increases occurred largely over the past two decades [@Singla2020], and increases have been concentrated largely in Black municipalities [@Sances2017].
+These facts have been extensively discussed in mainstream media and should be widely known among Black voters [@Eligon2019; @Ehrenfreund2014].
+We expect a larger share of more affluent Black voters to be affected by ticketing than other forms of criminalization---arrests and incarceration are most common among individuals experiencing poverty [@Looney2018].
+Because perceptions of “linked fate” and related critiques of policing are even more salient among members of the Black middle class [@Dawson1995], we expect Black middle class voters to be mobilized by egregious ticketing practices.
+In other words, we argue that ticketing should ensnare more Black voters who are more likely to politicize the issue.
+
+Finally, the rise of the Black Lives Matter movement in 2013 constitutes a significant development for the political socialization of Black Americans, and the movement began in municipalities that targeted Black residents with tickets.
+The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious.
+Furthermore, local Black Lives Matter activism can change police practices.
+One recent study found that census places that saw Black Lives Matter protests experienced a 15 to 20 percent decrease in police killings over the following five year period [@Campbell2021].
+It’s possible that Black Lives Matter facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis---the movement arose shortly after fines and fees became a more salient and widespread threat to Black Americans’ material security, and many early Black Lives Matter protests either occurred in municipalities with exploitative ticketing practices or directly followed traffic stops that escalated into police violence [@Holpuch2015; @LaFraniere2016].
+
+Today, fines and fees disproportionately affect Black people, and Black political mobilization appears to mitigate some of the most egregious ticketing practices [@Sances2017].
+Accordingly, we expect that Black voters’ political behavior in response to police ticketing will be distinct from the political behavior of white voters, and further that ticketing should mobilize Black voter turnout in cities that have recently ramped up ticketing.
 
@@
 
-We explore the effect of fees and fines collections on voter turnout by looking at two different levels: the municipal and the individual.
-Such an approach gives us both breadth and depth: our municipal-level analysis allows us to broadly understand the relationship between fees and fines across the entire United States, while the individual-level analyses allow us to interrogate the specific causal mechanisms at play.
+We mobilize three distinct approaches to ask whether ticketing and police stops structure voter turnout, and whether these effects are unique for Black Americans.
+We look at national survey data, municipal-level finance data, and individual-level administrative records in a major American county to explore these effects.
+Each approach offers advantages and drawbacks; taken together, however, they dramatically advance our understanding of the political consequences of the most routine types of contact with the criminal legal system.
+
+## National Survey Data {-}
+
+We begin by turning to the American National Election Studies 2020 Time Series data (ANES).
+The ANES has been fielded in every presidential election year since 1948 and is among the most widely-used tools for understanding American’s political beliefs and behaviors, including their relationship with the criminal legal system [@Walker2020].
+It is weighted to be nationally representative of all American adults.
+In both 2016 and 2020, the ANES added new survey questions about respondent’s encounters with the police and the criminal legal system.
+We focus in particular on two questions: *During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?*, and *Have you ever been arrested, or has that never happened to you?* We include the roughly 87 percent of respondents that answered both questions, giving us a sample size of 7,347 respondents, of whom just over 11% identified as Black.
+
+We use the survey questions to test the effect of a police stop on voter turnout---and, specifically, whether the effect is different for Black respondents.
+We also test whether an arrest is associated in the 2020 ANES with a lower probability of voting as described in previous work.
+In addition to the respondent’s contact with the criminal legal system, we control for age; sex; income; party affiliation; and self-described ideology.
+Using the ANES, we test our first two hypotheses:
+
+*Hypothesis 1*: Personal and proximal experience of police stops is demobilizing for non-Black respondents, and mobilizing for Black respondents, other things equal.
+
+*Hypothesis 2*: Personal experience of an arrest is demobilizing for individuals of all races, other things equal.
+
+There is an important caveat to the use of the ANES survey---namely, while the police stop question asks whether the respondent *or anyone in their family* was stopped in the past year, the arrest question asks only about the individual respondent.
+While this may muddy the water between direct and proximal contact with the criminal legal system, we expect that the national survey data will give us some insight into the uniquely politicizing nature of police stops for Black Americans.
 
@@
 
-We begin with our nationwide analysis in which we observe the turnout and fees and fines collections of cities from around the country.
+After an examination of the cross-sectional national survey data, we turn to our nationwide analysis of the relationship between municipal revenue raised from fees and fines, and turnout in the 2018 federal election.
 Our data come from two primary sources: the US Census Bureau’s Census of Governments Data (COG), and registered voter files from L2 Political.
@@
 These files are considered public record, and in most states contain information about each voter’s age, residential address, political affiliation, and participation history.
-L2 collects these voter files from around the country and merges them with proprietary data that estimates other voter- and household-level characteristics such as race and education.
+L2 collects voter files from around the country and merges them with proprietary data that estimates other voter- and household-level characteristics such as race and education.
 L2 also geocodes voters’ residential addresses.
-L2 does not collect all states’ voter file on the same date; the date of the “raw” voter file from each state from which the L2 data are modelled can be found in Appendix A.
 
-We merge these geocoded voter files with “place” and “county subdivision” shapefiles published by the US Census Bureau.
-By aggregating these individual-level records to the municipal level, we are able to estimate the number of registered voters and the number of ballots cast in every city in the country.
+We merge the geocoded voter files with “place” and “county subdivision” shapefiles published by the US Census Bureau.
+By aggregating individual-level records to the municipal level, we are able to estimate the number of registered voters and the number of ballots cast in every city in the country.
 Moreover, by using the racial estimates provided by L2 we can estimate the number of ballots cast by voters of each race in each city.
@@
 **Estimation Strategy**: We begin by merging each municipality’s fees and fines per capita (that is, dollars per resident) from the 2012 COG to its turnout from the 2014 midterm election, and the 2017 COG to its 2018 turnout.
-Because this measure is highly right-skewed, we use the natural log of fees and fines per capita plus one.
-We also control for other municipal and state characteristics.
-These include racial composition, population density, median income, collegiate education, median age, and share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality’s revenue that comes from the state or federal government in the 2012 and 2017 COGs.
+Because this measure is highly right-skewed, we use the natural log of fees and fines per capita (plus 1, to account for municipalities that collected no fees and fines).
+We also control for other municipal and state characteristics: racial composition, population density, median income, collegiate education, median age, share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality’s revenue that comes from the state or federal government in the 2012 and 2017 COGs.
 We retain the 8,954 municipalities whose data is reported to the COG in both 2012 and 2017 and meet the other criteria noted above.
@@
 We run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
-
 Our national two-way fixed effect model allows us to test our first two hypotheses:
 
-**Hypothesis 1:** Increased reliance on fines and fees revenue at the city level reduces voter turnout at the city level.*
+*Hypothesis 3*: Increased reliance on fines and fees revenue at the city level reduces voter turnout at the city level.
 
-**Hypothesis 2:** The effect of the city-level relationship between fines and voter turnout is stronger for Black voters, given the historical and explicit racial injustice narratives used to explain these practices.*
+*Hypothesis 4*: The effect of the city-level relationship between fines and voter turnout is stronger for Black voters, given the historical and explicit racial injustice narratives used to explain these practices.
 
@@
 
-Our national test of the relationship between municipal fees and fines collection and turnout offers novel insight into the political socialization of low-level police contact.
-It cannot, however, directly observe the causal mechanism we argue is at play: namely, that direct contact with the criminal legal system influences turnout.
+Our national, cross-sectional analyses offer novel insight into the political socialization of low-level police contact.
+They cannot, however, directly observe the causal mechanism we argue is at play: namely, that direct contact with the criminal legal system influences turnout.
 If interpreted in isolation, our national analysis would suffer from the ecological fallacy.
@@
 
-Another drawback of the national analysis is that it can't distinguish personal contact from proximal contact (“having a loved one who is a custodial citizen without yourself having had contact”) [@Walker2017].
+Additionally, the national analyses cannot distinguish personal contact from proximal contact (“having a loved one who is a custodial citizen without yourself having had contact” [@Walker2017]).
 Because existing research investigating the effect of proximal contact has produced mixed results [@Burch2014; @Lee2014; @Sugie2015; @White2019; @Walker2017; @Walker2020], we are unable to prove that personal police contact is the only dynamic driving effects observed in our national analysis.
@@
 The county clerk makes information available about every traffic stop in the county going back to 2003.
-This data includes the name and date of birth of the individual stopped; the date of the offense; and the amount the individual paid for a ticket.
+This data includes the name and date of birth of the individual stopped; the date of the offense; and the amount the individual paid for a ticket; and other information.
 
-To identify ticketed voters, we match the first and last names and dates of birth from these data against the Hillsborough County registered voter file.
+To identify ticketed voters, we match the first and last names and dates of birth from court data against the Hillsborough County registered voter file.
 Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status [see @Nyhan2017].
@@
 @Meredith2014 develops a test for assessing the prevalence of false-positives in administrative record matching.
-We present the results of that test in Appendix B, but we likely have a false-positive match of around 0.03 percent.
+We present the results of that test in the Supplementary Information.
+We likely have a false-positive match of around 0.03 percent, a figure we consider too low to impact our results meaningfully.
 
-By matching the police stop and voter records, we identify all voters who were ticketed between the 2012 and 2018 general elections.
+By matching the police stop and voter records, we identify all voters who were ticketed between the 2012 and 2020 general elections (voters stopped between 2018 and 2020 elections serve only as controls).
 Voters are considered “treated” in the general election following their ticket.
-
-These voters are then matched to a control voter using a nearest-neighbor approach, with a genetic algorithm used to determine the best weight for each characteristic [@Sekhon2011].
-As we show in Appendix XX, there is real reason to believe that individuals who are ticketed differ in meaningful ways for which we cannot directly control.
-As such, control voters are individuals who are stopped in the two years following the post-treatment election of the treated voters.
+Treated voters are then matched to a control voter using a nearest-neighbor approach, with a genetic algorithm used to determine the best weight for each characteristic [@Sekhon2011].
+Control voters are individuals who are stopped in the two years following the post-treatment election of the treated voters.
 Put differently, if a voter is stopped between 2012 and 2014, their control voter must be an individual stopped between the 2014 and 2016 elections.
 A voter cannot both be a treated and control voter for the same election; therefore, someone ticketed between the 2012 and 2014 elections and again between the 2014 and 2016 elections cannot serve as a control for anyone ticketed between 2012 and 2014.
-We assume that after controlling for observable characteristics, psat turnout, *and* the unobservable characteristics associated with receiving a ticket the timing of the ticket is effectively random.
+
+We match voters on individual-level characteristics (race / ethnicity; gender; party affiliation; age; number of traffic stops prior to the treatment period) and block group-level characteristics from the 2012 5-year ACS estimates (median income; share of the population with some college; unemployment rate).
+We match exactly on the type of ticket (civil / criminal infraction; whether they paid a fine; whether they were stopped by the Tampa Police Department) to ensure that treated and control voters receive the same treatment.
+Finally, we exactly match treated and control voters on their turnout in the three pre-treatment elections.
+
+We assume that after controlling for observable characteristics, past turnout, *and* the unobservable characteristics associated with receiving a ticket, the timing of the ticket is effectively random.
 In short, any turnout difference between the treated voters and their controls is the causal effect of a police stop on turnout.
-
-We match voters on individual-level characteristics (race / ethnicity; gender; party affiliation; age; registration date; number of traffic stops between 2003 and the election prior to the treatment period) and block group-level characteristics from the 2012 5-year ACS estimates (median income; share of the population with some college; unemployment rate).
-We also match exactly on whether an individual was ticketed for a civil or criminal infraction, as well as whether they eventually paid a fine.
-We also match treated and control voters on their turnout in the three pre-treatment elections.
+It is important to note that our overall turnout effects are robust to much stricter assumptions.
+In the Supplementary Information we demonstrate that our primary reported results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
 
@@
 Leveraging pre-treatment turnout allows us to estimate a traditional difference-in-differences model.
-Difference-in-difference models assume that, in the absence of the treatment, any turnout gap between treated and control voters would have remained stable in the post-treatment period.
+Difference-in-differences models assume that, in the absence of the treatment, any turnout gap between treated and control voters would have remained stable in the post-treatment period.
 While the validity of this assumption is commonly established by examining pre-treatment trends in turnout between the two groups, it can be improved upon by using the matching methodology described above.
-In the case at hand, we both establish that the turnout gap between treatment and control voters was constant prior to treatment, *and* that the observable characteristics of treated and control voters are similar---thus lending credence to the assumption that this gap would have remained constant absent treatment.
+In the case at hand, we both establish that the turnout of treated voters was mirrored by that of their control voters prior to treatment, *and* that the observable characteristics of treated and control voters are similar---thus lending credence to the assumption that this gap would have remained constant absent treatment.
 Finally, by drawing controls from the population of individuals who were ticketed in subsequent years, we also indirectly control for any unobserved characteristics associated with receiving a ticket.
 For a more detailed discussion of how matching can improve upon traditional difference-in-difference approaches when using panel data, see @Imai2020.
-
-It is important to note that while our primary analyses include all individuals who were stopped, our results hold even when we shrink the window around an election dramatically.
-As we show in Appendix XX, voters ticketed in the two months before an election turned out at lower rates than matched controls ticketed in the two months following an election.
 
@@
 *$\beta$~2~Post Treatment~t~* measures whether turnout increased for controls in the first election following the treated voter’s stop, while *$\beta$~3~Treated~i~ × Post Treatment~t~* tests whether turnout changed differently for treated voters than their controls in the election following their police stop.
-*$\beta$~3*, then, will capture the causal effect of a police stop on voter turnout.
+*$\beta$~3~*, then, will capture the causal effect of a police stop on voter turnout.
 Finally, the matrix *$\delta$Z~i~* contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
-Equation 1 allows us to test Hypotheses 3:
+Equation 1 allows us to test Hypothesis 5:
 
-**Hypothesis 3**: Being ticketed reduces an individual’s likelihood of turning out in the subsequent election.
+*Hypothesis 5*: Being ticketed reduces an individual’s likelihood of turning out in the subsequent election.
 
@@
 
-where *$\delta$Y~it~* includes the dummy for Black interacted with the treatment and post treatment dummies.
+where *$\delta$Y~it~* includes the dummy for Black interacted with the treatment and post treatment dummies. Equation 2 allows us to test Hypothesis 6:
 
-Equation 2 allows us to test Hypotheses 4:
+*Hypothesis 6*: The effect of being ticketed on an individual’s voter turnout is less negative / more positive if that individual is Black.
 
-**Hypothesis 4**: The effect of being ticketed on an individual's turnout is less negative / more positive if that individual is Black.
-
-Because Tampa holds off-year local elections, we are able to test whether ticketed voters target officials who are able to change local police practices.
+<!-- Because Tampa holds off-year local elections, we are able to test whether ticketed voters target officials who are able to change local police practices.
 @Laniyonu2019 gives us reason to believe that the effect should be stronger for local elections.
 
-**Hypothesis 5**: Any potential mobilizing turnout effect in Tampa is stronger for local (mayoral) elections, since those elections directly affect police practices.
-
-<!-- One novel feature of our analysis is that we are able to assess the political effects of both proximal and personal criminal legal contact during the same time frame.
-The COG data likely capture the voting behavior of people who were not personally ticketed, but know one or several people who were; and the Tampa data capture the voting behavior of people who were themselves ticketed.
--->
+*Hypothesis 7*: Any potential mobilizing turnout effect for Black voters in Tampa is stronger for local (mayoral) elections, since those elections directly affect police practices. -->
 
 # Results {-}
+
+As discussed above, we begin by testing the relationship between police stops and turnout in the 2020 election, and then move to testing the relationship between fees and fines at the municipal level.
+While both tests give us insight into the political ramifications of low-level police contact, their cross-sectional nature cannot establish causality.
+To investigate causality, we also examine whether the turnout of individuals stopped by the police before an election was different than those stopped after the election in Hillsborough County, Florida.
+
+## National Survey Data {-}
+
+In this section we make use of the American National Election Studies 2020 Time Series Data (ANES).
+The test for this section is simple: we ask whether, after controlling for standard covariates, having personal or proximal contact with a police stop in the previous 12 months is associated with whether a respondent voted in the 2020 presidential election.
+We also ask whether this relationship was different for Black and non-Black respondents.
+We also use the ANES data to reconfirm prior literature demonstrating that higher-level contact with the criminal legal system is associated with lower turnout, as these relationships could have changed in the aftermath of the widespread protests following the police killing of George Floyd in 2020.
+
+Roughly 15 percent of non-Black respondents reported a police stop in the preceding 12 months, while the same was true for more than 22 percent of Black respondents.
+In Figure \ref{fig:anes} we present the results of our econometric models.
+In the left-hand panel, we show the predicted turnout of respondents who answered “yes” or “no” to the question *During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?* The right-hand panel, meanwhile, plots these relationships for respondents who answered “yes” or “no” to the question *Have you ever been arrested, or has that never happened to you?*.
+These are the predicted probabilities after controlling for respondents’ race / ethnicity; age; party; ideology; income; and education.
+The full regression table can be found in the Supplementary Information..
+
+```{r anes-cross, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:anes}Predicted Turnout, 2020", fig.pos = "!htpb", fig.align = "center"}
+load("temp/anes_plot.rdata")
+print(p2)
+```
+Figure \ref{fig:anes} demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (*p* = 0.006).
+The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (*p* = 0.52).
+Importantly, this effect is not a remnant of a white--nonwhite divide.
+As we show in the Supplementary Information, police stops were not differently related to turnout for Latinos than for non-Latinos; nor did they impact turnout differently for Asians than for non-Asians.
+The ANES results point, then, to the fact that police stops are uniquely associated with higher turnout for Black respondents.
+
+The second panel of Figure \ref{fig:anes} shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
+Importantly, the interaction between arrest status and the respondent’s race was not statistically significant.
+In other words, although police stops seem to be uniquely mobilizing for Black Americans, we fail to uncover evidence that arrests differentially structured subsequent Black- and non-Black turnout.
+
+These cross-sectional results cannot establish causality.
+It is possible that Black respondents who had been stopped by the police (or had family members who experienced a stop) differed from non-Black respondents with such contact in ways that cannot be captured by the survey data.
+However, our findings are consistent with a causal story that police stops are mobilizing for Black Americans---but that this is not the case for higher-level contact such as arrests.
+
+## Municipal-Level Results {-}
 
@@
 The figure also marks the interdecile range.
-The full regression table can be found in Appendix XX.
+The full regression table can be found in the Supplementary Information.
 
@@
 
-As Figure \ref{fig:mef-2018} makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 1 percentage point over the interdecile range, after controlling for the other covariates.
-The opposite is true for Black voters: over the same range, Black turnout *increases* by roughly 2.5 percentage points.
-Both of these relationships are statistically significant at the 95 confidence level.
-To be sure, this does not prove that higher fees and fines increase Black turnout; these cross-sectional regressions cannot establish causality.
+As Figure \ref{fig:mef-2018} makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 2.5 percentage points over the interdecile range, after controlling for the other covariates.
+The opposite is true for Black voters: over the same range, Black turnout *increases* by roughly 2.4 percentage points.
+Both relationships are statistically significant at the 95 confidence level.
+This does not prove that higher fees and fines increase Black turnout; cross-sectional regressions cannot establish causality.
 Nevertheless, Figure \ref{fig:mef-2018} is consistent with this story.
@@
 
-Thus far, we have shown that voter turnout is decreased in municipalities that increase fines and fees collections.
+Thus far, we have shown that voter turnout decreased in municipalities that increased fines and fees collections.
 We argue that this relationship is causal: increased fees and fines collections means that more residents have direct interactions with the criminal legal system.
@@
 As discussed above, we match individuals who were ticketed between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.^[Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
-The full sample is used in the actual matching process.]  Matching is done with replacement and ties are randomly broken.
+The full sample is used in the actual matching process.]  Matching is done with replacement and ties are not broken.
+This means that some treated voters have multiple controls; the regression weights are calculated to allow for this possibility.
 In Table \ref{tab:balance} we present the results of the matching algorithm.
@@
   kable_styling(latex_options = c("hold_position"))
+
 j
@@
 First, we can see that for both Black and non-Black voters the parallel trends assumption is satisfied.
-Because we matched treated and control voters based on turnout prior to the ticket, this is unsurprising.
+Of course, because we matched treated and control voters based on turnout prior to the ticket, this is unsurprising.
 
@@
 The coefficients of note are *Treated × Post Treatment* and *Treated × Post Treatment × Black*.
-In models 1 and 3, *Treated × Post Treatment* measures the overall treatment effect, and in models 2 and 4 it measures the treatment effect for non-Black voters.
+In models 1 and 2, *Treated × Post Treatment* measures the overall treatment effect, and in models 3 and 4 it measures the treatment effect for non-Black voters.
 *Treated × Post Treatment × Black* measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
@@
 In models 1 and 2, the estimated overall treatment effect is -1.5 percentage points.
-In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---nonBlack turnout was depressed by 1.7 percentage points, while the negative effect was just -1.0 for Black individuals.
-Although the treatment effect is still sustantively quite large for Black individuals, the pattern follows our national analysis.
-It appears that, in Tampa and around the country, Black voters' turnout is not as negatively impacted by police contact as that of nonBlack individuals.
+In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---nonBlack turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
+Although the treatment effect is still substantively quite large for Black individuals, the pattern follows our national analysis.
+It appears that, in Tampa and around the country, Black voters' turnout in federal elections is not as negatively impacted by police contact as that of non-Black individuals.
 
-<!-- [Tampa - local figure/table] -->
+<!-- As shown in model 5 and table XX, we find that being ticketed in the 90 days preceding a mayoral election in Tampa is demobilizing for Black voters, but not demobilizing for non-Black voters.
+Being ticketed decreased Black turnout by 0.5 percentage points.
+-->
 
@@
 
-Our results provide support for Walker’s theory of criminal legal contact mobilizing nonwhite political participation.
-Our individual-level analysis in Hillsborough County shows that being ticketed mobilizes voters, and mobilizes Black voters to a greater degree than non-Black voters---and our city-level analysis shows that while greater fines and fees reliance reduces white voter turnout, it has no effect on Black turnout.
+While existing sociology and political science literature has examined the rise and collateral consequences of fines and fees as well as the effects of criminalization on political socialization, no study has investigated the causal relationship between ticketing and voter turnout.
+Additionally, our study is among the first to use individual-level administrative data to investigate the relationship between criminalization and political participation.
 
-Particularly following the rise of the Black Lives Matter movement in 2013, our findings are consistent with the theory that Black voters interpret exploitative police practices as a threat to the wellbeing of all Black Americans.
+We first used survey data collected in the American National Election Studies 2016 and 2020 datasets to show how, unlike arrests, ticketing can mobilize Black voters.
+We found that Black people who reported personal or proximal police contact with a police stop in the last 12 months were 0.5 pp more likely to vote compared to Black people who did not report such contact.
+Non-Black respondents demonstrated no statistically significant result for police stops.
+Meanwhile, both Black and non-Black people who had been arrested at any point were less likely to vote, and we did not find significant differences between racial groups’ behaviors in response to arrests.
 
-We were somewhat surprised by the differences that arose between our two sets of findings---our city-level analysis did not produce statistically significant results for Black voters.
+Next, we used a two-way fixed effects model to estimate the effect of increased fines and fees reliance at the city level on aggregate voter turnout in federal elections.
+We found that each 10 percent increase in fines and fees collected per resident is associated with a voter turnout decrease of about 0.06 percentage points, with no significant impact on Black turnout in particular---in other words, the demobilizing effect of ticketing increases at the city level is largely driven by non-Black voters.
+
+In order to directly observe the causal mechanism, we then conducted an individual-level analysis of ticketing and voting behavior in Hillsborough County, Florida.
+Using a difference-in-differences design, we found that individuals who were ticketed in the 90-day period preceding a federal election were 1.7 percentage points less likely to vote compared to individuals who were ticketed following the election.
+The effect was smaller for Black individuals (1 percentage point less likely), which is consistent with our hypothesis that Black political responses to ticketing should be distinct from whites (and more mobilized by comparison).
+
+We were somewhat surprised by the differences that arose between our two sets of findings---our city-level analysis using a two-way fixed effects model did not produce statistically significant results for Black voters.
 We think there are a few potential explanations for this mismatch.
+
 First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes are smaller or not statistically significant.
@@
 That said, @Sances2017 specifically note that they didn't exploit the panel setup of the COG because of little variation between the 2007-2012 COG to the 2012-2017 one, and so they just stuck to cross sectional.
-The positive effect for Black turnout in Figure 1 is consistent with our Tampa analysis and doesn't totally contradict the TWFE.
+The positive effect for Black turnout in Figure 2 is consistent with our Tampa analysis and doesn't totally contradict the TWFE.
+
+Our findings point to several implications for political sociology and political science scholarship.
+While existing literature suggests that the most disruptive forms of criminal legal contact (i.e.
+criminal convictions and incarceration) consistently discourage voting [@Lerman2014; @Burch2011; @White2019a], research regarding police stops has produced more mixed results [@Laniyonu2019].
+We extend this theory to police ticketing, the most common form of police contact in America, and find that city-level increases in ticketing generally reduce turnout.
+For Black voters, however, our findings suggest that ticketing can be politically mobilizing.
+Particularly following the rise of the Black Lives Matter movement in 2013, our findings constitute new evidence in support of our theory that ticketing is distinct from other forms of criminal legal contact and therefore catalyzes different political behaviors among Black voters, who are disproportionately affected by both ticketing and criminalization in general.
 
 **Limitations**: Because our individual-level analysis is limited to Hillsborough County, we don’t have a good idea of whether the city-level revenue reliance trend interacts with the individual experience of being ticketed.
-Is ticketing more politically mobilizing in cities that are palpably dialing up their revenue collection efforts?
+Is ticketing more politically mobilizing for Black voters in cities that are palpably dialing up their revenue collection efforts?
 Future research could test this hypothesis in cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.
@@
 
-**Future research**: Unlike previous studies using survey data, we are unable to tell whether individuals in Tampa have non-ticketing criminal legal exposure.
+**Future research**: Future work should explore whether ticketing can be mobilizing for Black individuals under circumstances.
+We were unable to test whether what we're observing is just *decreased* demobilization, or whether some subgroups of the Black population were mobilized while others were demobilized.
+In other words, it could be the case that ticketing is demobilizing for all voters, but there is a subset of Black voters who are *mobilized* by this, though they aren't a large enough group to counteract the demobilization of other Black people.
+
+Unlike previous studies using survey data, we are unable to tell whether individuals in Tampa have non-ticketing criminal legal exposure.
 Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.
@@
 # References {-}
+
+<!-- 
+[stuff on Black MC]
+https://press.princeton.edu/books/paperback/9780691025438/behind-the-mule
+
+https://journals.sagepub.com/doi/abs/10.1177/0011128799045004006?casa_token=C1tIg2PtoRQAAAAA:jiOyqKAFal3XdvfUC7BI6ItWF4rJOFNuj-FhTScVU-vXfrpW1wduVWp-aXtGdzq8EnaDVC4sbTbj
+
+https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1745-9125.2002.tb00962.x?casa_token=CAPT_XZTho4AAAAA:EVzYhsgW-c44zwpabCYoP8QtZ3-6YNws9vjdBgjhau8f-ehG-GwkS6h0MdhfYncmV3t60_WUCykNUw
+
+https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1745-9125.2009.00159.x -->

### 2021-04-30 markdown/draft_paper.tex
first full draft

@@
 \hypersetup{
-  pdftitle={Policing for Profit and the Undermining of Democracy},
+  pdftitle={Policing for Profit and the Mobilization of Black Voters},
   pdfauthor={Jonathan Ben-Menachem; Kevin Morris},
@@
 
-\title{Policing for Profit and the Undermining of Democracy}
+\title{Policing for Profit and the Mobilization of Black Voters}
 \author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
-\date{April 19, 2021}
+\date{April 28, 2021}
 
@@
 The American criminal legal system is an important site of political socialization: sociologists show how the alienating effect of criminalization pushes people away from public institutions, and political scientists have measured the effects of policing and incarceration on political participation.
-Despite this burgeoning literature, no research has directly investigated how ticketing for low-level offenses affects political participation.
-Using data from the Census of Governments and the national voter file, we test the causal effect of fines and fees practices on American voting behavior at the city level (aggregate).
-Additionally, we exploit individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019 to determine whether getting a ticket impacts political participation.
+Despite this burgeoning literature, no research has directly investigated how police ticketing practices affect political participation.
+We use three approaches to answer this question: national survey data, a city-level analysis using Census of Governments data and the national voter file, and individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019.
+The survey data show that Black people who report that they were recently stopped by police are more likely to vote compared to those who were not stopped.
 Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.6 percentage point turnout decrease but was not associated with Black turnout.
-In Tampa, Florida, we estimate that being ticketed decreases an individual's likelihood of voting in federal elections by 1.3 percentage points, but we do not uncover evidence of a distinct political effect for Black voter turnout.
-In local elections, however,\\
-\textbar{}
-\textbar{}
+In Tampa, Florida, we estimate that being ticketed decreases an individual's likelihood of voting in federal elections by 1.7 percentage points, but depressive effects are smaller for Black residents.
+
+\hfill\break
+
 \textbf{Keywords}: voting, monetary sanctions, race, punishment, political participation
@@
 Scholars have found that criminal legal contact (i.e.~arrest, conviction, incarceration) consistently discourages voting (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}; \protect\hyperlink{ref-Burch2011}{Burch 2011}; \protect\hyperlink{ref-White2019a}{White 2019b}).
-This work, however, has largely focused on the effects of highly consequential contact with the criminal legal system such as incarceration and felony convictions (\protect\hyperlink{ref-Burch2014}{Burch 2014}; \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}).
-Our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
-
-The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures participation.
+Such work has largely focused on the effects of highly disruptive contact with the criminal legal system such as incarceration and felony convictions (\protect\hyperlink{ref-Burch2014}{Burch 2014}; \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}).
+This paper is the first to explicitly theorize how local ticketing practices shape the political socialization of ticketed individuals.
+Additionally, our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
+The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures political participation.
 Past work looking at the individual-level effects of low-level contact has relied entirely on survey or qualitative data (e.g.
 \protect\hyperlink{ref-Walker2014}{Walker 2014}; \protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
-Their in-depth research allows for the testing of specific psychological mechanisms and personal interpretations of criminal legal contact, but does not allow us to generalize more broadly.
+Existing research allows for the testing of specific psychological mechanisms and personal interpretations of criminal legal contact, but does not allow us to generalize more broadly.
 As Weaver and Lerman (\protect\hyperlink{ref-Weaver2010}{2010, 821}) note, it may also introduce measurement bias.
@@
 
-We begin by joining fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for each municipality in the country.
+Before turning to the administrative data, we begin with a novel analysis of 2016 and 2020 national survey data regarding voters' experience with police stops and arrests.
+We find that Black respondents who reported personal or proximal experience with police stops in the last 12 months are more likely to vote than Black people who did not, while we find no statistically significant relationship between stops and voting among non-Black respondents.
+
+Next, we join fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for each municipality in the country.
 While we find that increased fees and fines likely cause lower turnout among non-Black Americans, we find no effect of fees and fines on Black turnout.
 
-Because our national analysis does not allow us to directly observe the causal effect of police ticketing on voter turnout, we use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were ticketed between the 2012 and 2018 elections.
+Because our national analyses do not allow us to directly observe the causal effect of police ticketing on voter turnout, we use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were ticketed between the 2012 and 2018 elections.
 By matching individual voters who were ticketed to similar voters who were ticketed at later points and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout.
-We find that being ticketed reduces the chance that an individual will turn out in the subsequent election.
-
-We demonstrate that police ticketing practices---the most widespread form of police contact in America---influence the political behavior of Americans.
-This finding supports and extends Vesla Weaver and Amy Lerman's theory of criminal legal contact discouraging political participation (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
+We find that being ticketed reduces the chance that an individual will turn out in the subsequent election, and that this effect is smaller for Black voters.
+
+We demonstrate that police ticketing practices---the most widespread form of police contact in America---substantially reduce the turnout of non-Black American voters, but can mobilize Black voters.
+Our findings complicate existing theories of how criminalization politically socializes Americans, and Black Americans in particular (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
+Additionally, while all forms of criminalization likely contribute to a subjective experience of alienation or group-level exclusion among Black Americans that is well-documented in sociological scholarship (\protect\hyperlink{ref-Bell2017}{Bell 2017}; \protect\hyperlink{ref-Desmond2016}{Desmond, Papachristos, and Kirk 2016}), our contribution emphasizes the need for further research regarding how different forms of criminalization affect group-level perceptions of government and resultant political behavior.
+Accordingly, we propose a new theory explaining how ticketing may uniquely catalyze mobilizing narratives of racial injustice.
 Our findings are relevant for interdisciplinary scholars of crime, race, politics, political economy, social movements, and policing.
@@
 states passed laws denying voting rights to people who were convicted of felonies.
-In their analysis of how racial threat catalyzes felon disenfranchisement, \protect\hyperlink{ref-Behrens2003}{Behrens, Uggen, and Manza} (\protect\hyperlink{ref-Behrens2003}{2003}) found that increases in a state's nonwhite prison population drastically increase the likelihood of legislation permanently disenfranchising people convicted of felonies.
-As \protect\hyperlink{ref-Shofner1963}{Shofner} (\protect\hyperlink{ref-Shofner1963}{1963}) notes, this has often been tied explicitly to the increased presence of Black Americans in the electorate.
+In their analysis of how racial threat catalyzes felon disenfranchisement, \protect\hyperlink{ref-Behrens2003}{Behrens, Uggen, and Manza} (\protect\hyperlink{ref-Behrens2003}{2003}) found that increases in the share of a state's prison population that is nonwhite drastically increases the likelihood of legislation permanently disenfranchising people convicted of felonies.
+As \protect\hyperlink{ref-Shofner1963}{Shofner} (\protect\hyperlink{ref-Shofner1963}{1963}) notes, felony disenfranchisement has often been tied explicitly to the increased presence of Black Americans in the electorate.
 
@@
 More specifically, many states require payment of fees as a condition of criminal legal supervision or the payment of all legal financial obligations as a condition of completing a sentence, and failure to comply with supervision or sentence completion conditions can be a barrier to voting rights restoration.
-These political barriers also disproportionately affect Black people.
+Such political barriers also disproportionately affect Black people.
 In Alabama, for example, Black people with felony convictions applying to have their voting rights restored were 26 percentage points more likely to have their application denied over outstanding fines and fees (\protect\hyperlink{ref-Meredith2017}{Meredith and Morse 2017}).
@@
 After Floridians passed Amendment 4 to restore voting rights to individuals with felony convictions in 2018, Florida Republicans passed legislation requiring these individuals to pay off the fines and fees associated with their original sentence.
-Because Florida does not maintain good records on who owes how much, this has proved to be a major hurdle for potential voters.
-Despite a dissenting judge arguing that ````{[}h{]}ad Florida wanted to create a system to obstruct, impede, and impair the ability of felons to vote under Amendment 4, it could not have come up with a better one,'' an en banc ruling by the U.S.
-Court of Appeals for the 11th Circuit upheld this legislation.\footnote{Jones et al.~v.
-DeSantis et al., 4:19cv300-RH/MJF (United States Court of Appeals for the Eleventh Circuit).}
+Because Florida does not maintain good records on who owes how much, the new law has proved to be a major hurdle for potential voters.
+As \protect\hyperlink{ref-Morris2021}{Morris} (\protect\hyperlink{ref-Morris2021}{2021}) argues, this could have severe implications for the future democratic participation of those excluded anew from the electorate after the state passed the amendment.
 
@@
 
-Beyond direct disenfranchisement, the spatial and racial concentration of criminalization significantly influences affected communities' perceptions of government.
+Beyond de jure disenfranchisement, the spatial and racial concentration of criminalization influences affected communities' perceptions of government.
 Monica Bell calls this process ``legal estrangement,'' a conceptual framework meant to capture those perceptions and cultural attitudes (``legal cynicism'') as well as the historical-structural conditions that produced them (\protect\hyperlink{ref-Bell2017}{Bell 2017}).
@@
 
-In addition to influencing perceptions of government, recent scholarship indicates that criminalization influences political behavior.
+Sarah Brayne found related results in her analysis of survey data---as the intensity of criminal legal contact escalates (i.e.~stopped, arrested, convicted), people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions (\protect\hyperlink{ref-Brayne2014}{Brayne 2014}).
+She calls this phenomenon ``system avoidance,'' and while her analysis did not specifically assess voting behavior, her findings demonstrate how criminal legal contact can discourage Americans' participation in public institutions as well as how the effect may vary alongside the intensity of criminal legal intervention.
+Similarly, \protect\hyperlink{ref-Remster2018a}{Remster and Kramer} (\protect\hyperlink{ref-Remster2018a}{2018}) finds that men who return home from prison are more likely to avoid contact with their childrens' schools.
+
+In addition to influencing perceptions of government and participation in public institutions, recent scholarship indicates that criminalization influences political behavior.
 The ``hidden curriculum'' of the criminal legal system (\protect\hyperlink{ref-Justice2014}{Justice and Meares 2014}; \protect\hyperlink{ref-Meares2017}{Meares 2017}) teaches individuals about their position within the political system, and the criminal legal system consequently serves as a primary site of political socialization for convicted individuals and their families (e.g.
 \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}).
-Several studies indicate that potential voters are discouraged from voting due to personal or proximal contact with the criminal legal system, and this chilling effect is most salient for what we consider ``high-intensity'' criminal legal involvement, such as being convicted of a crime or being incarcerated.
 
@@
 
-Sarah Brayne calls this phenomenon ``system avoidance,'' and she found similar results in her analysis of survey data: as the intensity of criminal legal contact escalates, people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions (\protect\hyperlink{ref-Brayne2014}{Brayne 2014}).
-Brayne's analysis demonstrates how lower-intensity criminal legal contact can be theorized as a mechanism for discouraging Americans' participation in public institutions.
-Similarly, \protect\hyperlink{ref-Remster2018a}{Remster and Kramer} (\protect\hyperlink{ref-Remster2018a}{2018}) finds that men who return home from prison are more likely to avoid contact with their childrens' schools.
-
-It may be the case that Black and non-Black Americans employ different self-preservation strategies, however.
-\protect\hyperlink{ref-Walker2020}{Walker} (\protect\hyperlink{ref-Walker2020}{2020}) makes clear that, when Black Americans locate their contact with the criminal legal system in a narrative of racial injustice, they can be politically mobilized; on the other hand, \protect\hyperlink{ref-Lerman2014}{Lerman and Weaver} (\protect\hyperlink{ref-Lerman2014}{2014}) shows that Black individuals' ability to situate their life experiences in a larger legacy of exploitation can be demobilizing.
-Turning to administrative data analysis, Ariel White's analysis of how short jail sentences affect voting in Harris County, Texas found that Black defendant turnout in subsequent elections dropped by 13 percentage points---but the effect on white turnout was not statistically significant (\protect\hyperlink{ref-White2019}{White 2019a}).
-
-Proximal exposure to criminalization---``having a loved one who is a custodial citizen without yourself having had contact'' (\protect\hyperlink{ref-Walker2017}{Walker and García-Castañon 2017})---also influences Americans' perceptions of government and political behavior, and the emerging literature has produced mixed findings of its effect on civic engagement.
-Using survey and ethnographic interview data, \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort} (\protect\hyperlink{ref-Lee2014}{2014}) found that adult children of incarcerated parents are less likely to vote, report lower trust in government, and are less likely to engage in other prosocial behaviors like community service.
-\protect\hyperlink{ref-Sugie2015}{Sugie} (\protect\hyperlink{ref-Sugie2015}{2015}) used survey data to show that partners of formerly incarcerated men are less likely to vote, but not less likely to participate in religious or civic institutions.
-
-Hannah Walker's research specifically tests differences between the effects of proximal and personal criminal legal contact on political behavior, and her findings underscore how a ``linked fate'' political analysis could catalyze distinct political behavior among Black voters (\protect\hyperlink{ref-Walker2014}{Walker 2014}).
-Using data from a 2012 survey of Washington state residents, she found that as the degree of an individual's proximity to a criminalized person increases, so does their likelihood of participating in political activities other than voting (such as signing a petition, volunteering, donating to politicians, etc.).
-With respect to voting, she found that personal contact was demobilizing, while proximal contact had no statistically significant effect.
-
-Walker found that nonwhite people who had experienced \emph{either} proximal or personal contact \emph{at any level of intensity}, including being stopped and questioned by police, were mobilized to take part in nonvoting political activity---and the same held true for whites, but with a much smaller effect size.
-Walker theorizes that this finding suggests that nonwhite people view criminalization ``as a form of systemic political threat,'' an analysis comparable to ``linked fate.'' Additionally, Walker's survey questions excluded ``minor traffic stops,'' the primary focus of this paper.
-
-Ariel White leveraged administrative court records from Harris County, Texas, to identify voters who lived within individuals who were charged with a misdemeanor offense and arrested, convicted, or jailed (\protect\hyperlink{ref-White2019}{White 2019a}).
-She found that living with someone who was charged but not convicted in the 30 day period preceding an election increased voter turnout by 3 percentage points, whereas ``convicted but not jailed'' decreased turnout by 6 percentage points and ``convicted and jailed'' decreased turnout by 12 percentage points.
-This provides further support for the theory that increasing intensity of criminalization could change the direction of the effect of criminalization on political behavior---and, in fact, that lower-level contact can mobilize even as higher-level contact demobilizes.
-
-Although geographic or spatial analyses of how criminalization affects political socialization technically move beyond proximal contact as an extant conceptual framework, similar mechanisms should operate on the neighborhood level.
+Lerman and Weaver's finding has been corroborated by administrative data: Ariel White found that short jail sentences in Harris County, Texas reduced Black defendant turnout in subsequent elections by 13 percentage points---but the effect on white turnout was not statistically significant (\protect\hyperlink{ref-White2019}{White 2019a}).
 Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level (\protect\hyperlink{ref-Burch2014}{Burch 2014}).
-\protect\hyperlink{ref-Morris2020}{Morris} (\protect\hyperlink{ref-Morris2020}{2020}) similarly finds that neighborhoods with more active voters lost to felony disenfranchisement turned out at lower rates in the 2017 mayoral race in NYC, and that this effect was particularly pronounced in Black neighborhoods.
-
-This chilling effect does not appear uniformly across all studies.
-In New York City, geographically concentrated stop-and-frisk activity was associated with \emph{reduced} turnout in Congressional elections, but \emph{increased} turnout in the 2008 presidential election as well as the local mayoral election in 2013 (\protect\hyperlink{ref-Laniyonu2019}{Laniyonu 2019}).
-If proximal contact mobilizes, then, mobilized voters are likely targeting officials who they perceive as holding the power to change police practices.
-To the extent that descriptive representation mitigates exploitative fines and fees practices (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}), this could constitute an effective political strategy.
-
-Over the past few years, scientific understanding of the political effects of more serious interactions with the criminal legal system has grown by leaps and bounds.
-The following table summarizes our understanding of the literature.
-As the table makes clear, a large body of research has now demonstrated the negative effects of high-level contact with the criminal legal system on voter turnout.
-Although lower-level stops are far more frequent, our knowledge of their (de)mobilizing effects is under-developed.
-
-\begin{singlespace}
-\input{../raw_data/lit_tab.tex}
-\end{singlespace}
-
-Most of the aforementioned studies were conducted using data collected before the rise of the Black Lives Matter movement in 2013, which could be construed as a significant development for the political socialization of Black Americans with respect to policing and incarceration.
-The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious.
-Though racist police violence was and is a focal point for many Black Lives Matter actions, local chapters frequently use policing as an entry point into a wider set of demands regarding the material security of Black Americans and their marginalization in American politics---and these demands affect police practices.
-One recent study found that census places that saw Black Lives Matter protests experienced a 15 to 20 percent decrease in police killings over the following five year period (\protect\hyperlink{ref-Campbell2021}{Campbell 2021}).
-It's possible that any potentially mobilizing effects of criminal legal contact became stronger in the 2010---in other words, Black Lives Matter could have facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis.
-That said, \protect\hyperlink{ref-Laniyonu2019}{Laniyonu} (\protect\hyperlink{ref-Laniyonu2019}{2019}) did demonstrate mobilization in Black neighborhoods before the beginning of the Black Lives Matter movement.
+
+Although most work documents a uniformly demobilizing effect from contact with the criminal legal system, recent work from Hannah Walker (\protect\hyperlink{ref-Walker2020}{2020b}, \protect\hyperlink{ref-Walker2020a}{2020a}) complicates this narrative by arguing that, when Black Americans understand their contact with the criminal legal system in the context of a narrative of racial injustice, such contact can actually prove mobilizing.
+She explains: ``experiences with punitive policies are subject to interpretation and, when understood through narratives of injustice, lead to wholly different participation outcomes than we usually predict'' (\protect\hyperlink{ref-Walker2020}{Walker 2020b, 132}).
+While she finds that this sense of injustice is especially likely to increase political participation in non-voting ways (such as attending a protest or signing a petition), the logic could extend to electoral participation as well given a strong narrative or relatively weak contact with the criminal legal system.
+
+Despite the growing body of high-quality scholarship on the democratic implications of the American criminal legal system, we still know remarkably little about the effects of the most routine sort of contact---police stops and tickets that do not result in an arrest.
+We leverage Walker's novel insights about the potentiality of a narrative of injustice to re-think how these sorts of contact with the state can structure political participation.
 
@@
 
-We argue that fines and fees invoke a distinct historical legacy of racist exploitation that merits further study.
+Fines and fees are situated in a distinct historical legacy of racist exploitation that may uniquely facilitate a collective ``sense of injustice'' among Black Americans---the sort of collective perception that \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020a}) argues could prove to be politically mobilizing.
 
 Cedric Robinson's articulation of racial capitalism offers a useful theoretical framework for interpreting the trajectory of American anti-Black political economy (\protect\hyperlink{ref-Robinson2000}{Robinson 2000}).
-Brittany Friedman theorizes fines and fees as a ``progression of racial capitalism penology,'' emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices (\protect\hyperlink{ref-Friedman2020}{Friedman 2020, page177}).
+Brittany Friedman theorizes fines and fees as a ``progression of racial capitalism penology,'' emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices (\protect\hyperlink{ref-Friedman2020}{Friedman 2020, 177}).
 Robinson argues that European industrial capitalism continued a longer political-economic trend of differentiating racial groups in order to dispossess them and exploit their labor.
-Indeed, early American agrarian and mercantile economies relied on the labor-power of enslaved Black people, and the slave patrols created to terrorize and discipline enslaved laborers are the earliest antecedents of contemporary American police departments (\protect\hyperlink{ref-DuBois1935}{Du Bois 1935}; \protect\hyperlink{ref-Hadden2003}{Hadden 2003}).
-
-Following the Civil War and the rise of global industrial capitalism, slave patrols were replaced by more formal police forces and vigilante lynch mobs (\protect\hyperlink{ref-EqualJusticeInitiative2017}{Initiative 2017}; \protect\hyperlink{ref-Hinton2021}{Hinton and Cook 2021}).
+
+Following the Civil War and the rise of global industrial capitalism, slave patrols were replaced by more formal police forces (\protect\hyperlink{ref-EqualJusticeInitiative2017}{Initiative 2017}; \protect\hyperlink{ref-Hinton2021}{Hinton and Cook 2021}).
 The implementation of the Black Codes, convict leasing, and sharecropping systems marked a transition to a new stage of racial capitalism, wherein criminalization provided an easily-exploited labor supply that offset costs that the state incurred by coercing their labor (\protect\hyperlink{ref-Lichtenstein1996}{Lichtenstein 1996}; \protect\hyperlink{ref-Mancini1978}{Mancini 1978}).
-Criminal legal debt has also been directly compared to sharecropping because both structures share ``a long-term pattern of financial exploitation based on race\ldots{} that limits the life-choices of the affected population'' (\protect\hyperlink{ref-Blessett2016}{Blessett and Box 2016, 113}).
+Contemporary fines and fees practices have been directly compared to sharecropping because both structures share ``a long-term pattern of financial exploitation based on race\ldots{} that limits the life-choices of the affected population'' (\protect\hyperlink{ref-Blessett2016}{Blessett and Box 2016, 113}).
 
@@
 At the level of federal policy, racial threat and whites' attribution of criminality to Blackness (\protect\hyperlink{ref-Muhammad2010}{Muhammad 2010}) prompted a shift ``from the War on Poverty to the War on Crime'' wherein Black communities' demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration (\protect\hyperlink{ref-Hinton2017}{Hinton 2017}; \protect\hyperlink{ref-Vargas2017a}{Vargas and McHarris 2017}).
-Ruth Wilson Gilmore explains how mid to late 20th-century whites ``demanded that the state become leaner and meaner, except when directed to do otherwise''---in other words, Keynesian welfare guarantees were undermined by the racist myth of ``welfare queens'' and supplanted by expanded police power (\protect\hyperlink{ref-Gilmore2007}{Gilmore 2007, 53}).
 
@@
 At the local level, this means that police budgets today constitute about thirty percent of city budgets nationwide, and cities where residents have lower median incomes dedicate a larger proportion of spending to policing (\protect\hyperlink{ref-Friedman2020}{Friedman 2020}).
+Similarly, municipalities where a larger share of the population is Black raise more fines and fees revenue per-capita than less-Black municipalities (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}; \protect\hyperlink{ref-UnitedStatesCommissiononCivilRights2017}{United States Commission on Civil Rights 2017}).
+Although major urban centers collect high dollar amounts of fines and fees, some of the most egregious ticketing practices measured on a per-capita basis are concentrated in suburbs or smaller cities with municipal courts---Ferguson being a prominent example (\protect\hyperlink{ref-UnitedStatesDepartmentofJusticeCivilRightsDivision2015}{United States Department of Justice Civil Rights Division 2015}; \protect\hyperlink{ref-Mughan2020}{Mughan 2020}).
 In municipalities with substantial Black populations, then, people who are most heavily affected by criminalization are expected to foot the bill for their own mistreatment.
+\protect\hyperlink{ref-Sances2017}{Sances and You} (\protect\hyperlink{ref-Sances2017}{2017}), however, finds that the discriminatory imposition of tickets can be mitigated by descriptive representation (i.e.~Black elected officials): The positive association between cities' reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
+
+Racial capitalist political economy imposes fiscal constraints regardless of city officials' identities or intentions.
+In their study of fines and fees reliance in Chicago suburbs, Josh Pacewicz and John Robinson, III show how the racialization of municipal opportunity structures prevents majority-Black suburban governments from acquiring sufficient revenue from ``good'' sources such as sales taxes or property taxes, catalyzing a reliance on fines and fees to fund government services (\protect\hyperlink{ref-Pacewicz2020}{Pacewicz and N.Robinson 2020}).
+Pacewicz and Robinson III note that racialized municipal opportunity structures are tied to the political-historical processes of neoliberalism and fiscal austerity, an observation that aligns with recent scholarship detailing the origins of fees paid by incarcerated people (\protect\hyperlink{ref-Kirk2020}{Kirk, Fernandes, and Friedman 2020}).
 
 Today, fines and fees primarily target Black Americans: traffic stops and searches disproportionately affect Black motorists nationwide (\protect\hyperlink{ref-Pierson2020}{Pierson et al.
-2020}), and a host of local analyses confirm this finding (\protect\hyperlink{ref-Dunn2009}{Dunn 2009}; \protect\hyperlink{ref-Goncalves2020}{Goncalves and Mello 2020}; \protect\hyperlink{ref-Mughan2020}{Mughan 2020}).
-In criminal court proceedings, Black defendants tend to face more severe monetary sanctions (\protect\hyperlink{ref-Edwards2020}{Edwards and Harris 2020}; \protect\hyperlink{ref-Harris2011}{Harris, Evans, and Beckett 2011}).
-
-In 2020, a Federal Reserve survey found that five percent of white respondents reported ``unpaid legal expenses, fines, or court costs,'' whereas twelve percent of Black respondents reported such debt (\protect\hyperlink{ref-BoardofGovernorsoftheFederalReserveSystem2020}{Governors of the Federal Reserve System 2020}).
-Across the country, city government reliance on fines and fees revenue is associated with larger Black populations (\protect\hyperlink{ref-UnitedStatesCommissiononCivilRights2017}{United States Commission on Civil Rights 2017}).
-Although major urban centers collect high dollar amounts of fines and fees, some of the most egregious ticketing practices measured on a per-capita basis are concentrated in suburbs or smaller cities with municipal courts---Ferguson being a prominent example (\protect\hyperlink{ref-UnitedStatesDepartmentofJusticeCivilRightsDivision2015}{United States Department of Justice Civil Rights Division 2015}; \protect\hyperlink{ref-Mughan2020}{Mughan 2020}).
-The positive association between cities' reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator, however (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
-
-Racial capitalist political economy imposes fiscal constraints regardless of city officials' intentions.
-In their study of fines and fees reliance in Chicago suburbs, Josh Pacewicz and John Robinson, III show how the racialization of municipal opportunity structures prevents majority-Black suburban governments from acquiring sufficient revenue from ``good'' sources such as sales taxes or property taxes, catalyzing a reliance on fines and fees to fund government services (\protect\hyperlink{ref-Pacewicz2020}{Pacewicz and N.Robinson 2020}).
-Pacewicz and Robinson III note that these racialized municipal opportunity structures are tied to the political-historical processes of neoliberalism and fiscal austerity, an observation that aligns with recent scholarship detailing the origins of fees paid by incarcerated people (\protect\hyperlink{ref-Kirk2020}{Kirk, Fernandes, and Friedman 2020}).
-The late 20th century ``property tax revolt'' most significantly benefited white homeowners (\protect\hyperlink{ref-Martin2017}{Martin and Beck 2017}), and without property tax hikes as a revenue-raising option, smaller cities and towns have few choices.
-
-Research regarding police stops and searches in response to local fiscal crisis shows how decreasing local revenues affect racist police practices.
+2020}), and a host of local analyses confirm the national finding (\protect\hyperlink{ref-Dunn2009}{Dunn 2009}; \protect\hyperlink{ref-Goncalves2020}{Goncalves and Mello 2020}; \protect\hyperlink{ref-Mughan2020}{Mughan 2020}).
+In criminal court proceedings, Black defendants tend to face more severe monetary sanctions (\protect\hyperlink{ref-Edwards2020}{Edwards and Harris 2020}; \protect\hyperlink{ref-Harris2011}{Harris, Evans, and Beckett 2011}), and a 2020 Federal Reserve survey found that five percent of white respondents reported ``unpaid legal expenses, fines, or court costs,'' whereas twelve percent of Black respondents reported such debt (\protect\hyperlink{ref-BoardofGovernorsoftheFederalReserveSystem2020}{Governors of the Federal Reserve System 2020}).
+
+Research regarding police stops and searches in response to local fiscal crises shows how decreasing local revenues affect racist police practices.
 One study of all U.S.
@@
 
-With this history in mind, we argue that Black Americans can situate exploitative ticketing practices in a longer historical legacy of collective disparate treatment and violence at the hands of the state, which may facilitate a stronger collective political analysis when police ticketing practices become more extreme.
-The historical use of fees and fines make this sort of police contact especially likely to evoke such narratives.
-Accordingly, we expect that Black voters' political behavior in response to police ticketing will be distinct from the political behavior of white voters.
+Black Americans can therefore situate exploitative ticketing practices in a longer historical legacy of collective disparate treatment and violence at the hands of the state.
+We argue that Black voters' recognition of discriminatory ticketing practices facilitates a ``linked fate'' political analysis that motivates voting behavior distinct from other forms of criminalization, such as criminal conviction or incarceration.
+We expect both ticketing and incarceration to spark a recognition of ``a sense of injustice'' among Black Americans, but we argue that ticketing should ultimately mobilize Black voters (unlike incarceration, which discourages Black voters more than whites (\protect\hyperlink{ref-White2019}{White 2019a})).
+
+Ticketing produces substantively different experiences than being arrested or incarcerated.
+While tickets can lead to driver's license suspensions or, in a smaller subset of cases, nonpayment incarceration, tickets are generally far less disruptive than criminal convictions and prison terms, and we argue that this difference should lead to different political behaviors.
+For example, one participant in \protect\hyperlink{ref-Lerman2014}{Lerman and Weaver} (\protect\hyperlink{ref-Lerman2014}{2014}) who had served five years of probation after a criminal conviction reported, ``I feel like if I contact a senator or governor, they'll probably want to put me in jail and leave me as a troublemaker\ldots{} That's how I actually feel: `I better stay below the radar 'cause this guy's tryin' to start trouble''' (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014, 210}).
+While formerly incarcerated people or people who have experienced criminal legal supervision may avoid voting due to the same type of fear of state surveillance and control that motivates their avoidance of medical or educational institutions (\protect\hyperlink{ref-Brayne2014}{Brayne 2014}), we argue that being ticketed should not produce the same chilling effect---ticketing should not prompt Black people to use political withdrawal as a self-preservation strategy.
+
+Additionally, we argue that ``policing for profit''---the experience of being ticketed while a municipality is palpably ramping up its fines and fees practices to collect revenue---is also substantively distinct from the experience of being arrested or incarcerated.
+In doing so, we extend Epp et al.'s theory of pretextual traffic stops politically socializing Black voters to the specific context of discriminatory police ticketing (\protect\hyperlink{ref-Epp2014}{Epp, Maynard-Moody, and Haider-Markel 2014}).
+Black Americans who experience disproportionate ticketing are likely aware that they are being targeted by police for reasons unrelated to traffic safety.
+One Buffalo, New York resident who is a plaintiff in a lawsuit regarding racist ticketing practices told a local newspaper in 2019: ``In my mind, they weren't balancing the budgets for Black lives, but with Black lives'' (\protect\hyperlink{ref-McLeod2019}{McLeod 2019}).
+The city created a new traffic violations agency in 2015, spurring its yearly ticketing numbers to jump from around 32,000 to over 52,000.
+This financial aspect of ticketing should make it distinct from arrests and incarceration: much like the coercion of labor under the Black Codes, contemporary fines and fees practices are blatantly an effort to extract wealth from Black Americans.
+Although 20th century political rhetoric centered public safety as the mission of policing {[}CITE{]}, exploitative ticketing practices cannot be reconciled with such rhetoric.
+In other words, to the extent that mass incarceration could be justified using narratives of ``colorblind racism'' (i.e., there's a lot of crime happening in Black communities, so that's why there's more policing in those areas), racist ticketing practices do not enjoy the same rhetorical convenience.
+
+Ticketing is by far the most common form of criminal legal contact; in 2018, more than 24 million people experienced police contact in the context of a traffic stop, whereas about 5.17 million people are currently disenfranchised as a result of a felony conviction (\protect\hyperlink{ref-Harrell2020}{Harrell and Davis 2020}; \protect\hyperlink{ref-Uggen2020}{Uggen et al.
+2020}).
+At the same time, the most egregious local ticketing increases occurred largely over the past two decades (\protect\hyperlink{ref-Singla2020}{Singla, Kirschner, and Stone 2020}), and increases have been concentrated largely in Black municipalities (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
+These facts have been extensively discussed in mainstream media and should be widely known among Black voters (\protect\hyperlink{ref-Eligon2019}{Eligon 2019}; \protect\hyperlink{ref-Ehrenfreund2014}{Ehrenfreund 2014}).
+We expect a larger share of more affluent Black voters to be affected by ticketing than other forms of criminalization---arrests and incarceration are most common among individuals experiencing poverty (\protect\hyperlink{ref-Looney2018}{Looney and Turner 2018}).
+Because perceptions of ``linked fate'' and related critiques of policing are even more salient among members of the Black middle class (\protect\hyperlink{ref-Dawson1995}{Dawson 1995}), we expect Black middle class voters to be mobilized by egregious ticketing practices.
+In other words, we argue that ticketing should ensnare more Black voters who are more likely to politicize the issue.
+
+Finally, the rise of the Black Lives Matter movement in 2013 constitutes a significant development for the political socialization of Black Americans, and the movement began in municipalities that targeted Black residents with tickets.
+The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious.
+Furthermore, local Black Lives Matter activism can change police practices.
+One recent study found that census places that saw Black Lives Matter protests experienced a 15 to 20 percent decrease in police killings over the following five year period (\protect\hyperlink{ref-Campbell2021}{Campbell 2021}).
+It's possible that Black Lives Matter facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis---the movement arose shortly after fines and fees became a more salient and widespread threat to Black Americans' material security, and many early Black Lives Matter protests either occurred in municipalities with exploitative ticketing practices or directly followed traffic stops that escalated into police violence (\protect\hyperlink{ref-Holpuch2015}{Holpuch 2015}; \protect\hyperlink{ref-LaFraniere2016}{LaFraniere and Smith 2016}).
+
+Today, fines and fees disproportionately affect Black people, and Black political mobilization appears to mitigate some of the most egregious ticketing practices (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
+Accordingly, we expect that Black voters' political behavior in response to police ticketing will be distinct from the political behavior of white voters, and further that ticketing should mobilize Black voter turnout in cities that have recently ramped up ticketing.
 
@@
 
-We explore the effect of fees and fines collections on voter turnout by looking at two different levels: the municipal and the individual.
-Such an approach gives us both breadth and depth: our municipal-level analysis allows us to broadly understand the relationship between fees and fines across the entire United States, while the individual-level analyses allow us to interrogate the specific causal mechanisms at play.
+We mobilize three distinct approaches to ask whether ticketing and police stops structure voter turnout, and whether these effects are unique for Black Americans.
+We look at national survey data, municipal-level finance data, and individual-level administrative records in a major American county to explore these effects.
+Each approach offers advantages and drawbacks; taken together, however, they dramatically advance our understanding of the political consequences of the most routine types of contact with the criminal legal system.
+
+\hypertarget{national-survey-data}{%
+\subsection*{National Survey Data}\label{national-survey-data}}
+\addcontentsline{toc}{subsection}{National Survey Data}
+
+We begin by turning to the American National Election Studies 2020 Time Series data (ANES).
+The ANES has been fielded in every presidential election year since 1948 and is among the most widely-used tools for understanding American's political beliefs and behaviors, including their relationship with the criminal legal system (\protect\hyperlink{ref-Walker2020}{Walker 2020b}).
+It is weighted to be nationally representative of all American adults.
+In both 2016 and 2020, the ANES added new survey questions about respondent's encounters with the police and the criminal legal system.
+We focus in particular on two questions: \emph{During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?}, and \emph{Have you ever been arrested, or has that never happened to you?} We include the roughly 87 percent of respondents that answered both questions, giving us a sample size of 7,347 respondents, of whom just over 11\% identified as Black.
+
+We use the survey questions to test the effect of a police stop on voter turnout---and, specifically, whether the effect is different for Black respondents.
+We also test whether an arrest is associated in the 2020 ANES with a lower probability of voting as described in previous work.
+In addition to the respondent's contact with the criminal legal system, we control for age; sex; income; party affiliation; and self-described ideology.
+Using the ANES, we test our first two hypotheses:
+
+\emph{Hypothesis 1}: Personal and proximal experience of police stops is demobilizing for non-Black respondents, and mobilizing for Black respondents, other things equal.
+
+\emph{Hypothesis 2}: Personal experience of an arrest is demobilizing for individuals of all races, other things equal.
+
+There is an important caveat to the use of the ANES survey---namely, while the police stop question asks whether the respondent \emph{or anyone in their family} was stopped in the past year, the arrest question asks only about the individual respondent.
+While this may muddy the water between direct and proximal contact with the criminal legal system, we expect that the national survey data will give us some insight into the uniquely politicizing nature of police stops for Black Americans.
 
@@
 
-We begin with our nationwide analysis in which we observe the turnout and fees and fines collections of cities from around the country.
+After an examination of the cross-sectional national survey data, we turn to our nationwide analysis of the relationship between municipal revenue raised from fees and fines, and turnout in the 2018 federal election.
 Our data come from two primary sources: the US Census Bureau's Census of Governments Data (COG), and registered voter files from L2 Political.
@@
 These files are considered public record, and in most states contain information about each voter's age, residential address, political affiliation, and participation history.
-L2 collects these voter files from around the country and merges them with proprietary data that estimates other voter- and household-level characteristics such as race and education.
+L2 collects voter files from around the country and merges them with proprietary data that estimates other voter- and household-level characteristics such as race and education.
 L2 also geocodes voters' residential addresses.
-L2 does not collect all states' voter file on the same date; the date of the ``raw'' voter file from each state from which the L2 data are modelled can be found in Appendix A.
-
-We merge these geocoded voter files with ``place'' and ``county subdivision'' shapefiles published by the US Census Bureau.
-By aggregating these individual-level records to the municipal level, we are able to estimate the number of registered voters and the number of ballots cast in every city in the country.
+
+We merge the geocoded voter files with ``place'' and ``county subdivision'' shapefiles published by the US Census Bureau.
+By aggregating individual-level records to the municipal level, we are able to estimate the number of registered voters and the number of ballots cast in every city in the country.
 Moreover, by using the racial estimates provided by L2 we can estimate the number of ballots cast by voters of each race in each city.
@@
 \textbf{Estimation Strategy}: We begin by merging each municipality's fees and fines per capita (that is, dollars per resident) from the 2012 COG to its turnout from the 2014 midterm election, and the 2017 COG to its 2018 turnout.
-Because this measure is highly right-skewed, we use the natural log of fees and fines per capita plus one.
-We also control for other municipal and state characteristics.
-These include racial composition, population density, median income, collegiate education, median age, and share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality's revenue that comes from the state or federal government in the 2012 and 2017 COGs.
+Because this measure is highly right-skewed, we use the natural log of fees and fines per capita (plus 1, to account for municipalities that collected no fees and fines).
+We also control for other municipal and state characteristics: racial composition, population density, median income, collegiate education, median age, share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality's revenue that comes from the state or federal government in the 2012 and 2017 COGs.
 We retain the 8,954 municipalities whose data is reported to the COG in both 2012 and 2017 and meet the other criteria noted above.
@@
 We run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
-
 Our national two-way fixed effect model allows us to test our first two hypotheses:
 
-\textbf{Hypothesis 1:} Increased reliance on fines and fees revenue at the city level reduces voter turnout at the city level.*
-
-\textbf{Hypothesis 2:} The effect of the city-level relationship between fines and voter turnout is stronger for Black voters, given the historical and explicit racial injustice narratives used to explain these practices.*
+\emph{Hypothesis 3}: Increased reliance on fines and fees revenue at the city level reduces voter turnout at the city level.
+
+\emph{Hypothesis 4}: The effect of the city-level relationship between fines and voter turnout is stronger for Black voters, given the historical and explicit racial injustice narratives used to explain these practices.
 
@@
 
-Another drawback of the national analysis is that it can't distinguish personal contact from proximal contact (``having a loved one who is a custodial citizen without yourself having had contact'') (\protect\hyperlink{ref-Walker2017}{Walker and García-Castañon 2017}).
-Because existing research investigating the effect of proximal contact has produced mixed results (\protect\hyperlink{ref-Burch2014}{Burch 2014}; \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}; \protect\hyperlink{ref-Sugie2015}{Sugie 2015}; \protect\hyperlink{ref-White2019}{White 2019a}; \protect\hyperlink{ref-Walker2017}{Walker and García-Castañon 2017}; \protect\hyperlink{ref-Walker2020}{Walker 2020}), we are unable to prove that personal police contact is the only dynamic driving effects observed in our national analysis.
+Additionally, the national analyses cannot distinguish personal contact from proximal contact (``having a loved one who is a custodial citizen without yourself having had contact'' (\protect\hyperlink{ref-Walker2017}{Walker and García-Castañon 2017})).
+Because existing research investigating the effect of proximal contact has produced mixed results (\protect\hyperlink{ref-Burch2014}{Burch 2014}; \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}; \protect\hyperlink{ref-Sugie2015}{Sugie 2015}; \protect\hyperlink{ref-White2019}{White 2019a}; \protect\hyperlink{ref-Walker2017}{Walker and García-Castañon 2017}; \protect\hyperlink{ref-Walker2020}{Walker 2020b}), we are unable to prove that personal police contact is the only dynamic driving effects observed in our national analysis.
 For that reason, we turn to individual-level data from Hillsborough County, Florida (home to Tampa).
@@
 The county clerk makes information available about every traffic stop in the county going back to 2003.
-This data includes the name and date of birth of the individual stopped; the date of the offense; and the amount the individual paid for a ticket.
-
-To identify ticketed voters, we match the first and last names and dates of birth from these data against the Hillsborough County registered voter file.
+This data includes the name and date of birth of the individual stopped; the date of the offense; and the amount the individual paid for a ticket; and other information.
+
+To identify ticketed voters, we match the first and last names and dates of birth from court data against the Hillsborough County registered voter file.
 Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status (see \protect\hyperlink{ref-Nyhan2017}{Nyhan, Skovron, and Titiunik 2017}).
@@
 \protect\hyperlink{ref-Meredith2014}{Meredith and Morse} (\protect\hyperlink{ref-Meredith2014}{2014}) develops a test for assessing the prevalence of false-positives in administrative record matching.
-We present the results of that test in Appendix B, but we likely have a false-positive match of around 0.03 percent.
-
-By matching the police stop and voter records, we identify all voters who were ticketed between the 2012 and 2018 general elections.
+We present the results of that test in the Supplementary Information.
+We likely have a false-positive match of around 0.03 percent, a figure we consider too low to impact our results meaningfully.
+
+By matching the police stop and voter records, we identify all voters who were ticketed between the 2012 and 2020 general elections (voters stopped between 2018 and 2020 elections serve only as controls).
 Voters are considered ``treated'' in the general election following their ticket.
-
-These voters are then matched to a control voter using a nearest-neighbor approach, with a genetic algorithm used to determine the best weight for each characteristic (\protect\hyperlink{ref-Sekhon2011}{Sekhon 2011}).
-As we show in Appendix XX, there is real reason to believe that individuals who are ticketed differ in meaningful ways for which we cannot directly control.
-As such, control voters are individuals who are stopped in the two years following the post-treatment election of the treated voters.
+Treated voters are then matched to a control voter using a nearest-neighbor approach, with a genetic algorithm used to determine the best weight for each characteristic (\protect\hyperlink{ref-Sekhon2011}{Sekhon 2011}).
+Control voters are individuals who are stopped in the two years following the post-treatment election of the treated voters.
 Put differently, if a voter is stopped between 2012 and 2014, their control voter must be an individual stopped between the 2014 and 2016 elections.
 A voter cannot both be a treated and control voter for the same election; therefore, someone ticketed between the 2012 and 2014 elections and again between the 2014 and 2016 elections cannot serve as a control for anyone ticketed between 2012 and 2014.
-We assume that after controlling for observable characteristics, psat turnout, \emph{and} the unobservable characteristics associated with receiving a ticket the timing of the ticket is effectively random.
+
+We match voters on individual-level characteristics (race / ethnicity; gender; party affiliation; age; number of traffic stops prior to the treatment period) and block group-level characteristics from the 2012 5-year ACS estimates (median income; share of the population with some college; unemployment rate).
+We match exactly on the type of ticket (civil / criminal infraction; whether they paid a fine; whether they were stopped by the Tampa Police Department) to ensure that treated and control voters receive the same treatment.
+Finally, we exactly match treated and control voters on their turnout in the three pre-treatment elections.
+
+We assume that after controlling for observable characteristics, past turnout, \emph{and} the unobservable characteristics associated with receiving a ticket, the timing of the ticket is effectively random.
 In short, any turnout difference between the treated voters and their controls is the causal effect of a police stop on turnout.
-
-We match voters on individual-level characteristics (race / ethnicity; gender; party affiliation; age; registration date; number of traffic stops between 2003 and the election prior to the treatment period) and block group-level characteristics from the 2012 5-year ACS estimates (median income; share of the population with some college; unemployment rate).
-We also match exactly on whether an individual was ticketed for a civil or criminal infraction, as well as whether they eventually paid a fine.
-We also match treated and control voters on their turnout in the three pre-treatment elections.
+It is important to note that our overall turnout effects are robust to much stricter assumptions.
+In the Supplementary Information we demonstrate that our primary reported results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
 
@@
 Leveraging pre-treatment turnout allows us to estimate a traditional difference-in-differences model.
-Difference-in-difference models assume that, in the absence of the treatment, any turnout gap between treated and control voters would have remained stable in the post-treatment period.
+Difference-in-differences models assume that, in the absence of the treatment, any turnout gap between treated and control voters would have remained stable in the post-treatment period.
 While the validity of this assumption is commonly established by examining pre-treatment trends in turnout between the two groups, it can be improved upon by using the matching methodology described above.
-In the case at hand, we both establish that the turnout gap between treatment and control voters was constant prior to treatment, \emph{and} that the observable characteristics of treated and control voters are similar---thus lending credence to the assumption that this gap would have remained constant absent treatment.
+In the case at hand, we both establish that the turnout of treated voters was mirrored by that of their control voters prior to treatment, \emph{and} that the observable characteristics of treated and control voters are similar---thus lending credence to the assumption that this gap would have remained constant absent treatment.
 Finally, by drawing controls from the population of individuals who were ticketed in subsequent years, we also indirectly control for any unobserved characteristics associated with receiving a ticket.
 For a more detailed discussion of how matching can improve upon traditional difference-in-difference approaches when using panel data, see \protect\hyperlink{ref-Imai2020}{Imai, Kim, and Wang} (\protect\hyperlink{ref-Imai2020}{2020}).
-
-It is important to note that while our primary analyses include all individuals who were stopped, our results hold even when we shrink the window around an election dramatically.
-As we show in Appendix XX, voters ticketed in the two months before an election turned out at lower rates than matched controls ticketed in the two months following an election.
 
@@
 \emph{\(\beta\)\textsubscript{2}Post Treatment\textsubscript{t}} measures whether turnout increased for controls in the first election following the treated voter's stop, while \emph{\(\beta\)\textsubscript{3}Treated\textsubscript{i} × Post Treatment\textsubscript{t}} tests whether turnout changed differently for treated voters than their controls in the election following their police stop.
-\emph{\(\beta\)\textsubscript{3\emph{, then, will capture the causal effect of a police stop on voter turnout.
-Finally, the matrix }\(\delta\)Z}i\textasciitilde{}} contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
-Equation 1 allows us to test Hypotheses 3:
-
-\textbf{Hypothesis 3}: Being ticketed reduces an individual's likelihood of turning out in the subsequent election.
+\emph{\(\beta\)\textsubscript{3}}, then, will capture the causal effect of a police stop on voter turnout.
+Finally, the matrix \emph{\(\delta\)Z\textsubscript{i}} contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
+Equation 1 allows us to test Hypothesis 5:
+
+\emph{Hypothesis 5}: Being ticketed reduces an individual's likelihood of turning out in the subsequent election.
 
@@
 
-where \emph{\(\delta\)Y\textsubscript{it}} includes the dummy for Black interacted with the treatment and post treatment dummies.
-
-Equation 2 allows us to test Hypotheses 4:
-
-\textbf{Hypothesis 4}: The effect of being ticketed on an individual's turnout is less negative / more positive if that individual is Black.
-
-Because Tampa holds off-year local elections, we are able to test whether ticketed voters target officials who are able to change local police practices.
-\protect\hyperlink{ref-Laniyonu2019}{Laniyonu} (\protect\hyperlink{ref-Laniyonu2019}{2019}) gives us reason to believe that the effect should be stronger for local elections.
-
-\textbf{Hypothesis 5}: Any potential mobilizing turnout effect in Tampa is stronger for local (mayoral) elections, since those elections directly affect police practices.
+where \emph{\(\delta\)Y\textsubscript{it}} includes the dummy for Black interacted with the treatment and post treatment dummies. Equation 2 allows us to test Hypothesis 6:
+
+\emph{Hypothesis 6}: The effect of being ticketed on an individual's voter turnout is less negative / more positive if that individual is Black.
 
@@
 \addcontentsline{toc}{section}{Results}
+
+As discussed above, we begin by testing the relationship between police stops and turnout in the 2020 election, and then move to testing the relationship between fees and fines at the municipal level.
+While both tests give us insight into the political ramifications of low-level police contact, their cross-sectional nature cannot establish causality.
+To investigate causality, we also examine whether the turnout of individuals stopped by the police before an election was different than those stopped after the election in Hillsborough County, Florida.
+
+\hypertarget{national-survey-data-1}{%
+\subsection*{National Survey Data}\label{national-survey-data-1}}
+\addcontentsline{toc}{subsection}{National Survey Data}
+
+In this section we make use of the American National Election Studies 2020 Time Series Data (ANES).
+The test for this section is simple: we ask whether, after controlling for standard covariates, having personal or proximal contact with a police stop in the previous 12 months is associated with whether a respondent voted in the 2020 presidential election.
+We also ask whether this relationship was different for Black and non-Black respondents.
+We also use the ANES data to reconfirm prior literature demonstrating that higher-level contact with the criminal legal system is associated with lower turnout, as these relationships could have changed in the aftermath of the widespread protests following the police killing of George Floyd in 2020.
+
+Roughly 15 percent of non-Black respondents reported a police stop in the preceding 12 months, while the same was true for more than 22 percent of Black respondents.
+In Figure \ref{fig:anes} we present the results of our econometric models.
+In the left-hand panel, we show the predicted turnout of respondents who answered ``yes'' or ``no'' to the question \emph{During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?} The right-hand panel, meanwhile, plots these relationships for respondents who answered ``yes'' or ``no'' to the question \emph{Have you ever been arrested, or has that never happened to you?}.
+These are the predicted probabilities after controlling for respondents' race / ethnicity; age; party; ideology; income; and education.
+The full regression table can be found in the Supplementary Information..
+
+\begin{figure}[!htpb]
+
+{\centering \includegraphics{draft_paper_files/figure-latex/anes-cross-1}
+
+}
+
+\caption{\label{fig:anes}Predicted Turnout, 2020}\label{fig:anes-cross}
+\end{figure}
+
+Figure \ref{fig:anes} demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (\emph{p} = 0.006).
+The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (\emph{p} = 0.52).
+Importantly, this effect is not a remnant of a white--nonwhite divide.
+As we show in the Supplementary Information, police stops were not differently related to turnout for Latinos than for non-Latinos; nor did they impact turnout differently for Asians than for non-Asians.
+The ANES results point, then, to the fact that police stops are uniquely associated with higher turnout for Black respondents.
+
+The second panel of Figure \ref{fig:anes} shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
+Importantly, the interaction between arrest status and the respondent's race was not statistically significant.
+In other words, although police stops seem to be uniquely mobilizing for Black Americans, we fail to uncover evidence that arrests differentially structured subsequent Black- and non-Black turnout.
+
+These cross-sectional results cannot establish causality.
+It is possible that Black respondents who had been stopped by the police (or had family members who experienced a stop) differed from non-Black respondents with such contact in ways that cannot be captured by the survey data.
+However, our findings are consistent with a causal story that police stops are mobilizing for Black Americans---but that this is not the case for higher-level contact such as arrests.
+
+\hypertarget{municipal-level-results}{%
+\subsection*{Municipal-Level Results}\label{municipal-level-results}}
+\addcontentsline{toc}{subsection}{Municipal-Level Results}
 
@@
 
-As Figure \ref{fig:mef-2018} makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 1 percentage point over the interdecile range, after controlling for the other covariates.
-The opposite is true for Black voters: over the same range, Black turnout \emph{increases} by roughly 2.5 percentage points.
-Both of these relationships are statistically significant at the 95 confidence level.
-To be sure, this does not prove that higher fees and fines increase Black turnout; these cross-sectional regressions cannot establish causality.
+As Figure \ref{fig:mef-2018} makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 2.5 percentage points over the interdecile range, after controlling for the other covariates.
+The opposite is true for Black voters: over the same range, Black turnout \emph{increases} by roughly 2.4 percentage points.
+Both relationships are statistically significant at the 95 confidence level.
+This does not prove that higher fees and fines increase Black turnout; cross-sectional regressions cannot establish causality.
 Nevertheless, Figure \ref{fig:mef-2018} is consistent with this story.
@@
 As discussed above, we match individuals who were ticketed between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.\footnote{Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
-The full sample is used in the actual matching process.} Matching is done with replacement and ties are not broken, meaning some treated voters may have more than 1 control; the regression weights reflect this possibility.
+The full sample is used in the actual matching process.} Matching is done with replacement and ties are not broken.
+This means that some treated voters have multiple controls; the regression weights are calculated to allow for this possibility.
 In Table \ref{tab:balance} we present the results of the matching algorithm.
-We manage to reduce between treated and control voters substantially along all observed characteristics.
+As the table demonstrates, the selected control voters are very similar to the treated voters.
 
@@
 The coefficients of note are \emph{Treated × Post Treatment} and \emph{Treated × Post Treatment × Black}.
-In models 1 and 3, \emph{Treated × Post Treatment} measures the overall treatment effect, and in models 2 and 4 it measures the treatment effect for non-Black voters.
+In models 1 and 2, \emph{Treated × Post Treatment} measures the overall treatment effect, and in models 3 and 4 it measures the treatment effect for non-Black voters.
 \emph{Treated × Post Treatment × Black} measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
@@
 In models 1 and 2, the estimated overall treatment effect is -1.5 percentage points.
-In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---nonBlack turnout was depressed by 1.7 percentage points, while the negative effect was just -1.0 for Black individuals.
-Although the treatment effect is still sustantively quite large for Black individuals, the pattern follows our national analysis.
-It appears that, in Tampa and around the country, Black voters' turnout is not as negatively impacted by police contact as that of nonBlack individuals.
+In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---nonBlack turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
+Although the treatment effect is still substantively quite large for Black individuals, the pattern follows our national analysis.
+It appears that, in Tampa and around the country, Black voters' turnout in federal elections is not as negatively impacted by police contact as that of non-Black individuals.
 
@@
 
-Our results provide support for Walker's theory of criminal legal contact mobilizing nonwhite political participation.
-Our individual-level analysis in Hillsborough County shows that being ticketed mobilizes voters, and mobilizes Black voters to a greater degree than non-Black voters---and our city-level analysis shows that while greater fines and fees reliance reduces white voter turnout, it has no effect on Black turnout.
-
-Particularly following the rise of the Black Lives Matter movement in 2013, our findings are consistent with the theory that Black voters interpret exploitative police practices as a threat to the wellbeing of all Black Americans.
-
-We were somewhat surprised by the differences that arose between our two sets of findings---our city-level analysis did not produce statistically significant results for Black voters.
+While existing sociology and political science literature has examined the rise and collateral consequences of fines and fees as well as the effects of criminalization on political socialization, no study has investigated the causal relationship between ticketing and voter turnout.
+Additionally, our study is among the first to use individual-level administrative data to investigate the relationship between criminalization and political participation.
+
+We first used survey data collected in the American National Election Studies 2016 and 2020 datasets to show how, unlike arrests, ticketing can mobilize Black voters.
+We found that Black people who reported personal or proximal police contact with a police stop in the last 12 months were 0.5 pp more likely to vote compared to Black people who did not report such contact.
+Non-Black respondents demonstrated no statistically significant result for police stops.
+Meanwhile, both Black and non-Black people who had been arrested at any point were less likely to vote, and we did not find significant differences between racial groups' behaviors in response to arrests.
+
+Next, we used a two-way fixed effects model to estimate the effect of increased fines and fees reliance at the city level on aggregate voter turnout in federal elections.
+We found that each 10 percent increase in fines and fees collected per resident is associated with a voter turnout decrease of about 0.06 percentage points, with no significant impact on Black turnout in particular---in other words, the demobilizing effect of ticketing increases at the city level is largely driven by non-Black voters.
+
+In order to directly observe the causal mechanism, we then conducted an individual-level analysis of ticketing and voting behavior in Hillsborough County, Florida.
+Using a difference-in-differences design, we found that individuals who were ticketed in the 90-day period preceding a federal election were 1.7 percentage points less likely to vote compared to individuals who were ticketed following the election.
+The effect was smaller for Black individuals (1 percentage point less likely), which is consistent with our hypothesis that Black political responses to ticketing should be distinct from whites (and more mobilized by comparison).
+
+We were somewhat surprised by the differences that arose between our two sets of findings---our city-level analysis using a two-way fixed effects model did not produce statistically significant results for Black voters.
 We think there are a few potential explanations for this mismatch.
+
 First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes are smaller or not statistically significant.
@@
 That said, \protect\hyperlink{ref-Sances2017}{Sances and You} (\protect\hyperlink{ref-Sances2017}{2017}) specifically note that they didn't exploit the panel setup of the COG because of little variation between the 2007-2012 COG to the 2012-2017 one, and so they just stuck to cross sectional.
-The positive effect for Black turnout in Figure 1 is consistent with our Tampa analysis and doesn't totally contradict the TWFE.
+The positive effect for Black turnout in Figure 2 is consistent with our Tampa analysis and doesn't totally contradict the TWFE.
+
+Our findings point to several implications for political sociology and political science scholarship.
+While existing literature suggests that the most disruptive forms of criminal legal contact (i.e.~criminal convictions and incarceration) consistently discourage voting (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}; \protect\hyperlink{ref-Burch2011}{Burch 2011}; \protect\hyperlink{ref-White2019a}{White 2019b}), research regarding police stops has produced more mixed results (\protect\hyperlink{ref-Laniyonu2019}{Laniyonu 2019}).
+We extend this theory to police ticketing, the most common form of police contact in America, and find that city-level increases in ticketing generally reduce turnout.
+For Black voters, however, our findings suggest that ticketing can be politically mobilizing.
+Particularly following the rise of the Black Lives Matter movement in 2013, our findings constitute new evidence in support of our theory that ticketing is distinct from other forms of criminal legal contact and therefore catalyzes different political behaviors among Black voters, who are disproportionately affected by both ticketing and criminalization in general.
 
 \textbf{Limitations}: Because our individual-level analysis is limited to Hillsborough County, we don't have a good idea of whether the city-level revenue reliance trend interacts with the individual experience of being ticketed.
-Is ticketing more politically mobilizing in cities that are palpably dialing up their revenue collection efforts?
+Is ticketing more politically mobilizing for Black voters in cities that are palpably dialing up their revenue collection efforts?
 Future research could test this hypothesis in cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.
@@
 
-\textbf{Future research}: Unlike previous studies using survey data, we are unable to tell whether individuals in Tampa have non-ticketing criminal legal exposure.
+\textbf{Future research}: Future work should explore whether ticketing can be mobilizing for Black individuals under circumstances.
+We were unable to test whether what we're observing is just \emph{decreased} demobilization, or whether some subgroups of the Black population were mobilized while others were demobilized.
+In other words, it could be the case that ticketing is demobilizing for all voters, but there is a subset of Black voters who are \emph{mobilized} by this, though they aren't a large enough group to counteract the demobilization of other Black people.
+
+Unlike previous studies using survey data, we are unable to tell whether individuals in Tampa have non-ticketing criminal legal exposure.
 Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.
@@
 
-\leavevmode\hypertarget{ref-Burch2013}{}%
----------.
-2013.
-\emph{Trading Democracy for Justice: Criminal Convictions and the Decline of Neighborhood Political Participation}.
-Chicago Studies in {American} Politics.
-{Chicago ; London}: {The University of Chicago Press}.
-
 \leavevmode\hypertarget{ref-Burch2014}{}%
@@
 Colgan, Beth A. 2019. {``Wealth-{Based Penal Disenfranchisement}.''} \emph{Vanderbilt Law Review} 72 (January). \url{https://papers.ssrn.com/abstract=3312439}.
+
+\leavevmode\hypertarget{ref-Dawson1995}{}%
+Dawson, Michael C. 1995. \emph{Behind the Mule: Race and Class in {African}-{American} Politics}. 1st pbk printing. {Princeton, NJ}: {Princeton Univ. Press}.
 
@@
 
-\leavevmode\hypertarget{ref-DuBois1935}{}%
-Du Bois, W. E. B. 1935. \emph{Black {Reconstruction} in {America}}. {Harcourt, Brace, and Howe}.
-
 \leavevmode\hypertarget{ref-Dunn2009}{}%
@@
 
+\leavevmode\hypertarget{ref-Ehrenfreund2014}{}%
+Ehrenfreund, Max.
+2014.
+{``How Segregation Led to Speed Traps, Traffic Tickets and Distrust Outside {St}.
+{Louis}.''} \emph{Washington Post}, November 26, 2014.
+\url{https://www.washingtonpost.com/news/wonk/wp/2014/11/26/how-segregation-led-to-speed-traps-traffic-tickets-and-distrust-outside-st-louis/}.
+
+\leavevmode\hypertarget{ref-Eligon2019}{}%
+Eligon, John.
+2019.
+{``Stopped, {Ticketed}, {Fined}: {The Pitfalls} of {Driving While Black} in {Ferguson}.''} \emph{The New York Times: U.S.}, August 6, 2019.
+\url{https://www.nytimes.com/2019/08/06/us/black-drivers-traffic-stops.html}.
+
+\leavevmode\hypertarget{ref-Epp2014}{}%
+Epp, Charles R., Steven Maynard-Moody, and Donald P.
+Haider-Markel.
+2014.
+\emph{Pulled {Over}}.
+{The University of Chicago Press}.
+\url{https://press.uchicago.edu/ucp/books/book/chicago/P/bo17322831.html}.
+
 \leavevmode\hypertarget{ref-Frago2019}{}%
@@
 
-\leavevmode\hypertarget{ref-Gilmore2007}{}%
-Gilmore, Ruth Wilson. 2007. \emph{Golden {Gulag}: {Prisons}, {Surplus}, {Crisis}, and {Opposition} in {Globalizing California}}. {University of California Press}.
-
 \leavevmode\hypertarget{ref-Goldstein2020}{}%
@@
 
-\leavevmode\hypertarget{ref-Hadden2003}{}%
-Hadden, Sally. 2003. \emph{Slave {Patrols}}. \url{https://www.hup.harvard.edu/catalog.php?isbn=9780674012349}.
+\leavevmode\hypertarget{ref-Harrell2020}{}%
+Harrell, Erika, and Elizabeth Davis.
+2020.
+{``Contacts {Between Police} and the {Public}, 2018 - {Statistical Tables}.''} {Bureau of Justice Statistics}.
+\url{https://www.bjs.gov/index.cfm?ty=pbdetail\&iid=7167}.
 
@@
 \url{https://doi.org/10.1146/annurev-criminol-060520-033306}.
+
+\leavevmode\hypertarget{ref-Holpuch2015}{}%
+Holpuch, Amanda.
+2015.
+{``Walter {Scott}: Protesters Demand Justice -- and an End to Police Discrimination.''} \emph{The Guardian: US News}, April 8, 2015.
+\url{http://www.theguardian.com/us-news/2015/apr/08/protesters-demand-justice-walter-scott-north-charleston}.
 
@@
 \url{https://doi.org/10.1177/0731121420967037}.
+
+\leavevmode\hypertarget{ref-LaFraniere2016}{}%
+LaFraniere, Sharon, and Mitch Smith.
+2016.
+{``Philando {Castile Was Pulled Over} 49 {Times} in 13 {Years}, {Often} for {Minor Infractions}.''} \emph{The New York Times: U.S.}, July 16, 2016.
+\url{https://www.nytimes.com/2016/07/17/us/before-philando-castiles-fatal-encounter-a-costly-trail-of-minor-traffic-stops.html}.
 
@@
 
+\leavevmode\hypertarget{ref-Looney2018}{}%
+Looney, Adam, and Nicholas Turner.
+2018.
+{``Work and Opportunity Before and After Incarceration.''} {The Brookings Institution}.
+\url{https://www.brookings.edu/wp-content/uploads/2018/03/es_20180314_looneyincarceration_final.pdf}.
+
 \leavevmode\hypertarget{ref-Makowsky2009}{}%
@@
 
-\leavevmode\hypertarget{ref-Martin2017}{}%
-Martin, Isaac William, and Kevin Beck.
-2017.
-{``Property {Tax Limitation} and {Racial Inequality} in {Effective Tax Rates}.''} \emph{Critical Sociology} 43 (2): 221--36.
-\url{https://doi.org/10.1177/0896920515607073}.
+\leavevmode\hypertarget{ref-McLeod2019}{}%
+McLeod, Marsha.
+2019.
+{``City {Hall} Cashing in on Traffic Tickets.''} {Investigative Post}.
+February 27, 2019.
+\url{https://www.investigativepost.org/2019/02/27/city-hall-cashing-in-on-traffic-tickets/}.
 
@@
 
-\leavevmode\hypertarget{ref-Morris2020}{}%
+\leavevmode\hypertarget{ref-Morris2021}{}%
 Morris, Kevin.
-2020.
-{``Neighborhoods and {Felony Disenfranchisement}: {The Case} of {New York City}.''} \emph{Urban Affairs Review}, May, 1078087420921522.
-\url{https://doi.org/10.1177/1078087420921522}.
+2021.
+{``Turnout and {Amendment Four}: {Mobilizing Eligible Voters Close} to {Formerly Incarcerated Floridians}.''} \emph{American Political Science Review}, April, 1--16.
+\url{https://doi.org/10.1017/S0003055421000253}.
 
@@
 
+\leavevmode\hypertarget{ref-Walker2020a}{}%
+---------. 2020a. \emph{Mobilized by Injustice: Criminal Justice Contact, Political Participation, and Race}. {NewYork}: {Oxford University Press 2020}.
+
 \leavevmode\hypertarget{ref-Walker2020}{}%
----------. 2020. {``Targeted: {The Mobilizing Effect} of {Perceptions} of {Unfair Policing Practices}.''} \emph{The Journal of Politics} 82 (1): 119--34. \url{https://doi.org/10.1086/705684}.
+---------. 2020b. {``Targeted: {The Mobilizing Effect} of {Perceptions} of {Unfair Policing Practices}.''} \emph{The Journal of Politics} 82 (1): 119--34. \url{https://doi.org/10.1086/705684}.
 

### 2021-04-30 markdown/si.Rmd
first full draft

---
title: "Supplementary Information"
output:
  bookdown::pdf_document2:
    toc: yes
    fig_caption: yes
    latex_engine: xelatex
    keep_tex: true
bibliography: "policing_turnout.bib"
link-citations: yes
fontsize: 12pt
header-includes:
    - \usepackage{rotating}
    - \usepackage{setspace}
---
```{r setup, echo = F, message = F, warning = F}
knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf")
library(systemfit)
library(AER)
library(sandwich)
library(lmtest)
library(scales)
library(tidyverse)
library(extrafont)
library(kableExtra)
library(data.table)
library(stargazer)
loadfonts()
```
\pagenumbering{gobble}
\pagenumbering{arabic}
\doublespacing

# Testing Robustness of L2 Racial Estimates {-}

As discussed in the body of this manuscript, our municipality-level racial estimates are constructed by aggregating up from individual-level records provided by L2. Because L2 uses statistical modeling to infer voters' race---not self-reported information---there is potential room for error in these estimates.

While most states in the country do not ask voters to self-report their race when they register to vote, a handful *do* collect this information. The raw voter files in these states, then, include true individual-level information about the racial makeup of the electorate.

To test the validity of the L2 records, we use the L2 estimates and self-reported race from the raw voter files in Florida, Georgia, and North Carolina. We use both sets of data to estimate the Black share of the electorate in each municipality used in the body of this paper. Comparing the "estimated" share Black from L2 to the "real" share Black from the voter file gives us a good sense of how well our approach works in these states.

In Table \ref{tab:mae} we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level. The MAE is commonly used to measure how different an estimated set of numbers are from their real value. Because it seems possible that these errors could be larger in smaller municipalities, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.

\begin{singlespace}
```{r mae-chunck, echo = F, warning = F}
t <- readRDS("./temp/maes.rds") %>% 
  mutate_all(~ gsub("[%]", "\\\\%", .))
j <- t %>% 
  mutate_all(linebreak) %>% 
  knitr::kable(booktabs = T, caption = "(\\#tab:mae) MAE of L2 Municipality Estimates (Florida, Georgia, North Carolina)", linesep = "", escape = F,
               col.names = linebreak(colnames(t)),
               align = "c") %>% 
  kable_styling(latex_options = c("HOLD_position"),
                position = "center")
j
```
\end{singlespace}

Table \ref{tab:mae} makes clear that for no group of municipalities does the MAE exceed 1.5%. Although this robustness check is limited to just 3 states, the available evidence indicates that aggregating from individual-level racial estimates in the L2 data to municipality-level demographics of the electorate does not result in unacceptable biases.

# Regression Table for Survey Data {-}

Here we present the regression table reported in the national survey data section of the manuscript. In model 1 we test whether personal or proximal contact with a police stop is differentially associated with turnout for Black and non-Black respondents. In this model, *Stopped in Past 12 Months* captures the relationship between police stops and non-Black respondents; *Stopped in Past 12 Months × Black* tests whether this relationship is different for Black respondents.

Models 2, 3, and 4 test whether the relationship is different for other non-white groups. Finally, model 5 tests the relationship between turnout and a historical arrest.

\begin{singlespace}
\input{"../temp/anes_clean.tex"}
\end{singlespace}

Model 1 in Table \ref{tab:anes-reg} shows that Black individuals who had been stopped by the police (or had a family member stopped) in the preceding 12 months were 9 percentage points more likely to vote in 2020, other things equal; they were not related to turnout for non-Black respondents. Police stops are not, however, associated with different turnout effects for other non-white groups. Moreover, as discussed in the body of the paper, historical arrests were uniformly associated with a decrease in turnout of 4 percentage points for Black and non-Black respondents alike.

# Regression Table for 2018 Cross-Sectional Municipality Model {-}

In Table \ref{tab:cog-cross-reg} we present the full results of the econometric used to test the cross-sectional relationship between per-capita fees and fines, and 2018 municipal turnout. The table shows that a doubling of the fees and fines collected per capita is associated with a 0.3 percentage point reduction in overall turnout. That same doubling, however, is associated with a 0.4 percentage point *increase* in the Black turnout. While these point estimates are quite small, it is worth keeping in mind that the range of fees and fines per capita is very wide. The interquartile ranges of fees and fines per capita stretches from \$1.96 to \$20.63---a more than ten-fold increase.

\begin{singlespace}
\input{"../temp/cog_cross_clean.tex"}
\end{singlespace}

# Administrative Matching Robustness Check {-}

Our models exploring the turnout effects of traffic stops in Hillsborough County, Florida, require that we merge administrative records using the identifiers in the data. This runs the risk of identifying false positives. To test the prevalence of false positives in our administrative matching procedure, we use the test developed by @Meredith2014. By systematically permuting the birth dates in one set of records, we can see whether false positive matches are a major concern. In Table \ref{tab:change-dobs} we begin by merging all names and dates of birth in the traffic stop data with the names and dates of birth in the Hillsborough County registered voter file. We then add and subtract 35 days from the birth dates in the traffic stop data. If there are no false positives, these records should match with no records from the registered voter file.

\begin{singlespace}
```{r shift-dobs-chunk, echo = F}
table <- readRDS("./temp/plus_minus_35.rds")

j <- table %>% 
  mutate_all(linebreak) %>% 
  knitr::kable(booktabs = T, caption = "(\\#tab:change-dobs) Results of Shifting Birthdates", linesep = "", escape = F,
               col.names = linebreak(c("Group", "Number of Matches Between\nTraffic Stop and Voter File Records")),
               align = "c") %>% 
  kable_styling(latex_options = c("HOLD_position"),
                position = "center")
j
```
\end{singlespace}

As the table makes clear, more than a quarter-million registered voters in Hillsborough County match at least one record in the traffic stop database when merging by first and last name, and date of birth. Once we permute the birth dates, however, the match rate drops dramatically---to 60 or 78, depending on how these dates of birth are permuted. This translates into a false positive rate of roughly 0.03 percent. We consider this rate of false positives too low to meaningfully impact our results.

# Sensitivity to Narrower Windows {-}

In the individual-level section of this manuscript, voters stopped in the 2 years prior to an election are considered treated, and we draw our controls from the voters stopped 2 years after the election. It is perhaps the case that this large window results in implausible matches; under this design, a treated voter stopped in December of 2012 could draw a control not stopped until October of 2016. Voters stopped nearly 4 years apart from one another might differ in meaningful ways that our matching models cannot capture.

Here, we re-run our matching process on a variety of different windows around the elections. In the most conservative approach, we force voters stopped in the month before an election to match with voters stopped in the month after the election; we then gradually relax this assumption by allowing voters stopped in the 2 months before the election to match to those stopped in the 2 months afterwards, etc.

Figure \ref{fig:rob-window} shows that our overall treatment effect is remarkably consistent regardless of the size of the window drawn around the election. As we expand the window, we gain more treated voters (and treated voters have a larger pool of potential controls). As such, the confidence interval shrinks, but the overall effect is clearly robust to very strict assumptions. In each case, we are re-estimating our primary models in which the covariates used in the matching exercise are also included in the econometric model.

```{r windows, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:rob-window}Estimated Treatment Effect for Different Treatment Windows", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/windows_rob.rds")
print(p2)
```

\newpage
# References {-}

### 2021-04-30 markdown/si.tex
first full draft

--- 2021-04-30 markdown/si.Rmd
@@
----
-title: "Supplementary Information"
-output:
-  bookdown::pdf_document2:
-    toc: yes
-    fig_caption: yes
-    latex_engine: xelatex
-    keep_tex: true
-bibliography: "policing_turnout.bib"
-link-citations: yes
-fontsize: 12pt
-header-includes:
-    - \usepackage{rotating}
-    - \usepackage{setspace}
----
-```{r setup, echo = F, message = F, warning = F}
-knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf")
-library(systemfit)
-library(AER)
-library(sandwich)
-library(lmtest)
-library(scales)
-library(tidyverse)
-library(extrafont)
-library(kableExtra)
-library(data.table)
-library(stargazer)
-loadfonts()
-```
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  12pt,
+]{article}
+\usepackage{lmodern}
+\usepackage{amsmath}
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+  \usepackage{amssymb}
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Supplementary Information},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage[margin=1in]{geometry}
+\usepackage{longtable,booktabs}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{5}
+\usepackage{rotating}
+\usepackage{setspace}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
+\title{Supplementary Information}
+\author{}
+\date{\vspace{-2.5em}}
+
+\begin{document}
+\maketitle
+
+{
+\setcounter{tocdepth}{2}
+\tableofcontents
+}
 \pagenumbering{gobble}
@@
 
-# Testing Robustness of L2 Racial Estimates {-}
+\hypertarget{testing-robustness-of-l2-racial-estimates}{%
+\section*{Testing Robustness of L2 Racial Estimates}\label{testing-robustness-of-l2-racial-estimates}}
+\addcontentsline{toc}{section}{Testing Robustness of L2 Racial Estimates}
 
@@
 
-While most states in the country do not ask voters to self-report their race when they register to vote, a handful *do* collect this information.
+While most states in the country do not ask voters to self-report their race when they register to vote, a handful \emph{do} collect this information.
 The raw voter files in these states, then, include true individual-level information about the racial makeup of the electorate.
@@
 We use both sets of data to estimate the Black share of the electorate in each municipality used in the body of this paper.
-Comparing the "estimated" share Black from L2 to the "real" share Black from the voter file gives us a good sense of how well our approach works in these states.
+Comparing the ``estimated'' share Black from L2 to the ``real'' share Black from the voter file gives us a good sense of how well our approach works in these states.
 
-In Table \ref{tab:mae} we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level.
-The MAE is commonly used to measure how different an estimated set of numbers are from their real value.
+In Table \ref{tab:mae} we present the mean average error (MAE) of the L2 estimates aggregated up to the municipality level.
+The MAE is commonly used to measure how different an estimated number is from its real value.
 Because it seems possible that these errors could be larger in smaller municipalities, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.
@@
 \begin{singlespace}
-```{r mae-chunck, echo = F, warning = F}
-t <- readRDS("./temp/maes.rds") %>% 
-  mutate_all(~ gsub("[%]", "\\\\%", .))
-j <- t %>% 
-  mutate_all(linebreak) %>% 
-  knitr::kable(booktabs = T, caption = "(\\#tab:mae) MAE of L2 Municipality Estimates (Florida, Georgia, North Carolina)", linesep = "", escape = F,
-               col.names = linebreak(colnames(t)),
-               align = "c") %>% 
-  kable_styling(latex_options = c("HOLD_position"),
-                position = "center")
-j
-```
+\begin{table}[H]
+
+\caption{\label{tab:mae-chunck}\label{tab:mae} MAE of L2 Municipality Estimates (Florida, Georgia, North Carolina)}
+\centering
+\begin{tabular}[t]{ccccc}
+\toprule
+Bottom Quartile & Second Quartile & Third Quartile & Fourth Quartile & Overall\\
+\midrule
+1.08\% & 1.38\% & 1.36\% & 1.48\% & 1.32\%\\
+\bottomrule
+\end{tabular}
+\end{table}
 \end{singlespace}
 
-Table \ref{tab:mae} makes clear that for no group of municipalities does the MAE exceed 1.5%.
+Table \ref{tab:mae} makes clear that for no group of municipalities does the MAE exceed 1.5\%.
 Although this robustness check is limited to just 3 states, the available evidence indicates that aggregating from individual-level racial estimates in the L2 data to municipality-level demographics of the electorate does not result in unacceptable biases.
 
-# Regression Table for Survey Data {-}
+\hypertarget{regression-table-for-survey-data}{%
+\section*{Regression Table for Survey Data}\label{regression-table-for-survey-data}}
+\addcontentsline{toc}{section}{Regression Table for Survey Data}
 
@@
 In model 1 we test whether personal or proximal contact with a police stop is differentially associated with turnout for Black and non-Black respondents.
-In this model, *Stopped in Past 12 Months* captures the relationship between police stops and non-Black respondents; *Stopped in Past 12 Months × Black* tests whether this relationship is different for Black respondents.
+In this model, \emph{Stopped in Past 12 Months} captures the relationship between police stops and non-Black respondents; \emph{Stopped in Past 12 Months × Black} tests whether this relationship is different for Black respondents.
 
@@
 
-# Regression Table for 2018 Cross-Sectional Municipality Model {-}
+\hypertarget{regression-table-for-2018-cross-sectional-municipality-model}{%
+\section*{Regression Table for 2018 Cross-Sectional Municipality Model}\label{regression-table-for-2018-cross-sectional-municipality-model}}
+\addcontentsline{toc}{section}{Regression Table for 2018 Cross-Sectional Municipality Model}
 
@@
 The table shows that a doubling of the fees and fines collected per capita is associated with a 0.3 percentage point reduction in overall turnout.
-That same doubling, however, is associated with a 0.4 percentage point *increase* in the Black turnout.
+That same doubling, however, is associated with a 0.4 percentage point \emph{increase} in the Black turnout.
 While these point estimates are quite small, it is worth keeping in mind that the range of fees and fines per capita is very wide.
@@
 
-# Administrative Matching Robustness Check {-}
+\hypertarget{administrative-matching-robustness-check}{%
+\section*{Administrative Matching Robustness Check}\label{administrative-matching-robustness-check}}
+\addcontentsline{toc}{section}{Administrative Matching Robustness Check}
 
@@
 This runs the risk of identifying false positives.
-To test the prevalence of false positives in our administrative matching procedure, we use the test developed by @Meredith2014.
+To test the prevalence of false positives in our administrative matching procedure, we use the test developed by \protect\hyperlink{ref-Meredith2014}{Meredith and Morse} (\protect\hyperlink{ref-Meredith2014}{2014}).
 By systematically permuting the birth dates in one set of records, we can see whether false positive matches are a major concern.
@@
 \begin{singlespace}
-```{r shift-dobs-chunk, echo = F}
-table <- readRDS("./temp/plus_minus_35.rds")
+\begin{table}[H]
 
-j <- table %>% 
-  mutate_all(linebreak) %>% 
-  knitr::kable(booktabs = T, caption = "(\\#tab:change-dobs) Results of Shifting Birthdates", linesep = "", escape = F,
-               col.names = linebreak(c("Group", "Number of Matches Between\nTraffic Stop and Voter File Records")),
-               align = "c") %>% 
-  kable_styling(latex_options = c("HOLD_position"),
-                position = "center")
-j
-```
+\caption{\label{tab:shift-dobs-chunk}\label{tab:change-dobs} Results of Shifting Birthdates}
+\centering
+\begin{tabular}[t]{cc}
+\toprule
+Group & \makecell[c]{Number of Matches Between\\Traffic Stop and Voter File Records}\\
+\midrule
+Actual Birthdate & 263,152\\
+Birthdate + 35 Days & 78\\
+Birthdate - 35 Days & 60\\
+\bottomrule
+\end{tabular}
+\end{table}
 \end{singlespace}
@@
 
-# Sensitivity to Narrower Windows {-}
+\hypertarget{sensitivity-to-narrower-windows}{%
+\section*{Sensitivity to Narrower Windows}\label{sensitivity-to-narrower-windows}}
+\addcontentsline{toc}{section}{Sensitivity to Narrower Windows}
 
@@
 
-```{r windows, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:rob-window}Estimated Treatment Effect for Different Treatment Windows", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/windows_rob.rds")
-print(p2)
-```
+\begin{figure}[H]
+
+{\centering \includegraphics{si_files/figure-latex/windows-1}
+
+}
+
+\caption{\label{fig:rob-window}Estimated Treatment Effect for Different Treatment Windows}\label{fig:windows}
+\end{figure}
 
 \newpage
-# References {-}
+
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Meredith2014}{}%
+Meredith, Marc, and Michael Morse.
+2014.
+{``Do {Voting Rights Notification Laws Increase Ex}-{Felon Turnout}?''} \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 220--49.
+\url{https://doi.org/10.1177/0002716213502931}.
+
+\end{CSLReferences}
+
+\end{document}

### 2021-04-30 code/00_initialize.R

@@ -1,10 +1,14 @@
 library(splitstackshape)
 library(PanelMatch)
 library(rgdal)
+library(Metrics)
+library(RSQLite)
 library(multcomp)
 library(miceadds)
 library(Matching)
 library(plm)
+library(readstata13)
+library(lubridate)
 library(ggeffects)
 library(scales)
 library(extrafont)

### 2021-04-30 code/02_2018_cross_sectional.R

@@ -79,9 +79,11 @@ p1
 
 #################################################
 
-full_set <- rename(full_set, share_s_fed = share_state_fed)
+full_set <- rename(full_set, share_s_fed = share_state_fed) %>% 
+  mutate(median_income = median_income / 10000,
+         lpd = log(pop_dens))
 
-covars <- gsub("\\n|            ", "", "lndper + nh_white + nh_black + latino + asian + pop_dens +
+covars <- gsub("\\n|            ", "", "lndper + nh_white + nh_black + latino + asian + lpd +
             median_income + some_college + median_age + share_over_64 +
             state + total_revenue + share_taxes + share_s_fed")
 
@@ -104,13 +106,13 @@ ses <- lapply(ms$m, function(f){
 stargazer(models, type = "text", omit = c("state"),
           column.labels = ms$name,
           dep.var.labels = "",
-          covariate.labels = c("Log(Dollars / Resident)",
+          covariate.labels = c("Log((Dollars / Resident) + 1)",
                                "% nonHispanic White",
                                "% nonHispanic Black",
                                "% Latinx",
                                "% Asian",
-                               "Population Density",
-                               "Median Income",
+                               "Log(Population Density)",
+                               "Median Income (dollarsign10,000s)",
                                "% with Some College",
                                "Median Age",
                                "Share over 64",
@@ -119,45 +121,84 @@ stargazer(models, type = "text", omit = c("state"),
                                "% of Rev from State / Fed Gov."),
           se = ses,
           add.lines = list(c("State fixed effects", "X", "X", "X")),
-          notes = "Robust standard errors clustered by state.")
+          notes = "TO REPLACE",
+          omit.stat = c("F", "ser"),
+          out = "temp/cog_cross_raw.tex",
+          table.placement = "H",
+          title = "\\label{tab:cog-cross-reg} Fees and Fines and 2020 Turnout")
+
+
+j <- fread("./temp/cog_cross_raw.tex", header = F, sep = "+") %>% 
+  mutate(V1 = gsub("[%]", "Share", V1))
+
[…]

### 2021-04-30 code/03_2wayfe.R

@@ -123,7 +123,8 @@ stargazer(models, type = "text",
           dep.var.labels = "",
           notes = "TO REPLACE",
           title = "\\label{tab:twfe} Two-Way Fixed Effects Models",
-          out = "temp/2wfe_reg.tex")
+          out = "temp/2wfe_reg.tex",
+          omit.stat = c("F", "ser"))
 
 j <- fread("./temp/2wfe_reg.tex", header = F, sep = "+")
 
@@ -245,7 +246,8 @@ stargazer(models, type = "text",
           notes = "TO REPLACE",
           title = "\\label{tab:coarser} Two-Way Fixed Effects Models, Binary Treatment",
           out = "temp/coarser_reg.tex",
-          order = 12)
+          order = 12,
+          omit.stat = c("F", "ser"))
 
 j <- fread("./temp/coarser_reg.tex", header = F, sep = "+")
 

### 2021-04-30 code/04_anes.R

@@ -1,0 +1,189 @@
+
+anes_pre <- read.dta13("../regular_data/anes/anes_timeseries_2020_stata_20210324/anes_timeseries_2020_stata_20210324.dta")
+
+
+anes_pre <- anes_pre %>% 
+  mutate(ideol = V201200,
+         age = V201507x,
+         to = (V201022 == 1 & V201023 == 1) | V202066 == 4,
+         white = V201549x == 1,
+         black = V201549x == 2,
+         latino = V201549x == 3,
+         asian = V201549x == 4,
+         party = ifelse(V201228 == 1 | V201230 == 3, "DEM",
+                        ifelse(V201228 == 2 | V201230 == 1, "REP", "OTH")))
+
+anes_pre$party <- factor(anes_pre$party, levels = c("DEM", "REP", "OTH"))
+
+income <- fread("../washington_covid/raw_data/income_lu.csv")
+
+anes_pre <- left_join(anes_pre, income) %>% 
+  mutate(income = income / 10000)
+
+reg_d <- select(anes_pre, ideol, white, black, latino, party, V200002,
+                age, income, V200010b, to, asian, V201600, V201201,
+                state = V201011, V201510, V202456, V202457) %>% 
+  filter(V202456 %in% c(1, 2),
+         V202457 %in% c(1, 2)) %>% 
+  mutate(stopped = V202456 == 1,
+         arrested = V202457 == 1,
+         ideol = ifelse(ideol < 0, "Ideology Missing",
+                        ifelse(ideol == 1, "Extremely Liberal",
+                               ifelse(ideol == 2, "Liberal",
+                                      ifelse(ideol == 3, "Slightly Liberal",
+                                             ifelse(ideol == 4, "Moderate",
+                                                    ifelse(ideol == 5, "Slightly Conservative",
+                                                           ifelse(ideol == 6, "Conservative",
+                                                                  ifelse(ideol == 7, "Extremely Conservative", "Don't Know Ideology")))))))),
+         ideol = ifelse(ideol == "Don't Know Ideology" & V201201 == 1, "Slightly Liberal",
+                        ifelse(ideol == "Don't Know Ideology" & V201201 == 2, "Slightly Conservative",
+                               ideol)),
+         ideol = factor(ideol, levels = c("Moderate", "Ideology Missing", "Don't Know Ideology",
+                                          "Extremely Liberal", "Liberal", "Slightly Liberal",
[…]

### 2021-04-30 code/hills/02_download_hills_stops.R

@@ -209,31 +209,39 @@ joined <- left_join(hills_voters, hills_stops_ll,
   filter(!is.na(pre_stops))
 
 
-######################## test permuting birth dates to check for false positives
-# joined2 <- inner_join(hills_voters,
-#                     select(hills_stops_ll, first_name,
-#                            last_name, date_of_birth, count) %>%
-#                       mutate(date_of_birth = date_of_birth + 35),
-#                     by = c("name_first" = "first_name",
-#                            "name_last" = "last_name",
-#                            "birth_date" = "date_of_birth",
-#                            "count"))
-# 
-# joined3 <- inner_join(hills_voters,
-#                     select(hills_stops_ll, first_name,
-#                            last_name, date_of_birth, count) %>%
-#                       mutate(date_of_birth = date_of_birth - 35),
-#                     by = c("name_first" = "first_name",
-#                            "name_last" = "last_name",
-#                            "birth_date" = "date_of_birth",
-#                            "count"))
-# 
-# test <- data.table(dates = c("Good", "Plus", "Minus"),
-#                    values = c(sum(!is.na(joined$fd)),
-#                               nrow(joined2),
-#                               nrow(joined3)))
-# 
-# saveRDS(test, "temp/plus_minus_35.rds")
+####################### test permuting birth dates to check for false positives
+
+stops_names_dobs <- select(hills_stops_ll, first_name,
+                           last_name, date_of_birth) %>% 
+  distinct()
+
+j1 <- inner_join(hills_voters,
+                 stops_names_dobs,
+                 by = c("name_first" = "first_name",
+                        "name_last" = "last_name",
+                        "birth_date" = "date_of_birth"))
+
+joined2 <- inner_join(hills_voters,
+                      stops_names_dobs %>%
+                      mutate(date_of_birth = date_of_birth + 35),
+                    by = c("name_first" = "first_name",
+                           "name_last" = "last_name",
+                           "birth_date" = "date_of_birth"))
+
+joined3 <- inner_join(hills_voters,
+                      stops_names_dobs %>%
+                      mutate(date_of_birth = date_of_birth - 35),
+                    by = c("name_first" = "first_name",
+                           "name_last" = "last_name",
+                           "birth_date" = "date_of_birth"))
+
+test <- data.table(group = c("Actual Birthdate", "Birthdate + 35 Days", "Birthdate - 35 Days"),
+                   values = c(nrow(j1),
[…]

### 2021-04-30 code/hills/05_regression.R

@@ -3,9 +3,7 @@
 hills_pre_match <- readRDS("temp/real_pre_match_hills.rds") %>% 
   ungroup()
 
-matches <- readRDS("temp/matches_hills_y.rds") %>% 
-  select(-first_tr_year.y) %>% 
-  rename(first_tr_year = first_tr_year.x)
+matches <- readRDS("temp/matches_hills_yem.rds")
 
 matches <- left_join(matches, select(hills_pre_match, voter_id, first_tr_year),
                      by = c("group" = "voter_id", "first_tr_year")) %>% 
@@ -51,47 +49,14 @@ matches <- left_join(matches,
 
 cleanup("matches")
 gc()
-ll <- matches %>%
-  filter(first_tr_year - last_date <= 90, period <= 0.5) %>%
-  group_by(treated, period, black) %>%
-  summarize(to = weighted.mean(to, weight)) %>% 
-  mutate(treated = ifelse(treated, "Treated", "Control"),
-         black = ifelse(black, "Black Voters", "Non-Black Voters"))
 
-ll$treated <- factor(ll$treated, levels = c("Treated", "Control"))
-
-p1 <- ggplot(data = ll) + 
-  facet_grid( ~ black) +
-  geom_rect(aes(xmin = 0.5-.125, xmax = 0.5, ymin = 0, ymax = Inf),
-            alpha = 0.03, color = "black", fill = "yellow") +
-  geom_line(data =ll, aes(x = period, y = to, linetype = treated)) +
-  geom_point(data = ll, aes(x = period, y = to, shape = treated)) +
-  scale_x_continuous(minor_breaks = seq(-3.5, 3.5, 1),
-                     breaks = seq(-3.5, 3.5, 1),
-                     labels = c("-4",
-                                "-3",
-                                "-2",
-                                "-1",
-                                "0",
-                                "1",
-                                "2",
-                                "3")) +
-  theme_bc(base_family = "LM Roman 10") +
-  scale_y_continuous(labels = percent) +
-  labs(x = "t", y = "Turnout",
-       linetype = "Treatment Group",
-       shape = "Treatment Group",
-       caption = "Treatment occurs inside of yellow band.") +
-  coord_cartesian(ylim = c(0.05, 0.75))
-p1
-saveRDS(p1, "temp/within90days_y.rds")
-##########################
[…]

### 2021-04-30 code/hills/06_rob_windows.R

@@ -1,0 +1,195 @@
+library(Matching)
+library(tidyverse)
+library(lubridate)
+library(data.table)
+
+lapply(c(1:23), function(i){
+  pre <- readRDS("temp/real_pre_match_hills.rds") %>% 
+    filter(((last_date >= (ymd(as.Date("2014-11-04")) %m+% months(-i))) &
+              (last_date <= ymd(as.Date("2014-11-04")) %m+% months(i)) & (first_tr_year == 1)) |
+             ((last_date >= (ymd(as.Date("2016-11-08")) %m+% months(-i))) &
+                (last_date <= ymd(as.Date("2016-11-08")) %m+% months(i)) & (first_tr_year == 2)) |
+             ((last_date >= (ymd(as.Date("2018-11-06")) %m+% months(-i))) &
+                (last_date <= ymd(as.Date("2018-11-06")) %m+% months(i)) & (first_tr_year == 3)))
+  
+  
+  ids <- pre %>%
+    mutate(id = row_number()) %>%
+    select(id, voter_id, first_tr_year)
+  
+  X <- pre %>%
+    select(-voter_id, -treated, -GEOID, -amount_paid, -last_date,
+           -v08, -v16, -v10, -reg_date) %>% 
+    mutate_at(vars(white, black, latino, asian, male, dem, rep, v1, v2, v3, paid), ~ ifelse(. == T, 1, 0)) %>% 
+    select(first_tr_year, paid, civil, tampa_pd, v1, v2, v3, everything())
+  
+  genout <- readRDS("temp/genout_hills_yem.rds")
+  
+  
+  mout <- Matchby(Tr = pre$treated, X = X,
+                  by = c(X$first_tr_year,
+                         X$white,
+                         X$black,
+                         X$latino,
+                         X$asian,
+                         X$male,
+                         X$dem,
+                         X$rep), estimand = "ATT", Weight.matrix = genout, M = 1,
+                  exact = c(rep(T, 7), rep(F, 14)), ties = T)
+  
+  matches <- data.table(voter = c(mout$index.control,
+                                  mout$index.treated),
+                        group = rep(mout$index.treated, 2),
+                        weight = rep(mout$weights, 2)) %>%
+    group_by(voter, group) %>%
+    summarize(weight = sum(weight)) %>%
+    ungroup()
+  
+  
+  matches <- left_join(matches, ids, by = c("voter" = "id")) %>%
[…]

### 2021-04-30 code/hills/07_make_prox.R

@@ -1,0 +1,68 @@
+
+stopped <- readRDS("temp/hills_pre_match.rds")
+
+voters <- readRDS("temp/full_raw_coded_hills_w_bgs.rds") %>% 
+  filter(count == 1) %>% 
+  ungroup() %>% 
+  mutate_at(vars(street, city), tolower) %>% 
+  group_by(city, street) %>% 
+  mutate(count = n()) %>% 
+  filter(count <= 5) %>% 
+  ungroup() %>% 
+  select(-count)
+
+
+stopped <- left_join(stopped, select(voters, voter_id, street, city))
+
+
+ads <- stopped %>% 
+  mutate_at(vars(street, city), tolower) %>% 
+  group_by(first_tr_year, street, city) %>% 
+  tally() %>% 
+  select(-n)
+
+
+voters2 <- left_join(voters,
+                    ads)
+
+prox14 <- filter(voters2, first_tr_year == "2014-11-04",
+                 !(voter_id %in% filter(stopped, first_tr_year == "2014-11-04")$voter_id))
+
+prox16 <- filter(voters2, first_tr_year == "2016-11-08",
+                 !(voter_id %in% filter(stopped, first_tr_year == "2016-11-08")$voter_id))
+
+prox18 <- filter(voters2, first_tr_year == "2018-11-06",
+                 !(voter_id %in% filter(stopped, first_tr_year == "2018-11-06")$voter_id))
+
+prox20 <- filter(voters2, first_tr_year == "2020-11-03",
+                 !(voter_id %in% filter(stopped, first_tr_year == "2020-11-03")$voter_id))
+
+proximals <- bind_rows(prox14, prox16, prox18, prox20) %>% 
+  mutate(white = race == 5,
+         black = race == 3,
+         latino = race == 4,
+         asian = race == 2,
+         male = gender == "M",
+         dem = party_affiliation == "DEM",
+         rep = party_affiliation == "REP",
+         reg_date = as.Date(registration_date, "%m/%d/%Y")) %>% 
+  select(voter_id, GEOID,
+         white, black, latino, asian, male, dem, rep, age, 
+         reg_date, name_first, name_last, birth_date,
+         v08, v10, v12, v14, v16, v18, latitude, longitude, first_tr_year)
+
+#######################
+
+census <- readRDS("../regular_data/census_bgs_18.rds")
+
+proximals <- left_join(proximals, census %>% 
[…]

### 2021-04-30 code/hills/07_rob_reg_2months.R

@@ -1,237 +1,0 @@
-
-#####
-hills_pre_match <- readRDS("temp/real_pre_match_hills.rds") %>% 
-  ungroup()
-
-matches <- readRDS("temp/matches_hills_y.rds") %>% 
-  select(-first_tr_year.y) %>% 
-  rename(first_tr_year = first_tr_year.x)
-
-matches <- left_join(matches, select(hills_pre_match, voter_id, first_tr_year),
-                     by = c("group" = "voter_id", "first_tr_year")) %>% 
-  mutate(fd = first_tr_year,
-         first_tr_year = ifelse(first_tr_year == 1, "2014-11-04",
-                                ifelse(first_tr_year == 2, "2016-11-08",
-                                       ifelse(first_tr_year == 3, "2018-11-06", "XX"))),
-         first_tr_year = as.Date(first_tr_year))
-
-hist <- readRDS("temp/full_raw_coded_hills_w_bgs.rds") %>%
-  select(voter_id, starts_with("v1"), v08) %>%
-  pivot_longer(!starts_with("vo"), names_to = "year", values_to = "to")
-
-elec_dates <- fread("raw_data/election_dates.csv")
-
-hist <- left_join(hist, elec_dates) %>% 
-  select(-year) %>% 
-  rename(year = date) %>% 
-  mutate(year = as.Date(year, "%m/%d/%Y"))
-
-
-matches <- left_join(matches, hist %>% 
-                       filter(year(year) %% 2 == 0), by = c("voter" = "voter_id"))
-
-periods <- fread("raw_data/period_lu.csv") %>% 
-  mutate_at(vars(first_tr_year, year), as.Date, "%m/%d/%Y")
-
-matches <- left_join(matches, periods) %>% 
-  filter(period %in% c(-2.5, -1.5, -.5, .5, 1.5))
-
-matches <- left_join(matches,
-                     hills_pre_match %>%
-                       select(-GEOID, -amount_paid, -last_date),
-                     by = c("voter" = "voter_id", "fd" = "first_tr_year"))
-
-matches <- left_join(matches,
-                     hills_pre_match %>%
-                       select(voter_id, amount_paid, last_date, first_tr_year, black_t = black,
-                              dem_t = dem),
-                     by = c("group" = "voter_id", "fd" = "first_tr_year")) %>% 
-  mutate(post = period >= 0.5,
-         treated = voter == group)
-
-cleanup("matches")
-gc()
-ll <- matches %>%
[…]

### 2021-04-30 code/hills/08_genmatch_prox.R

@@ -24,21 +24,18 @@ cl<-makeCluster(c(readLines(NodeFile)), type="SOCK")
 cl
 
 
-hills_pre_match <- readRDS("temp/hills_pre_match.rds")
+hills_pre_match <- readRDS("temp/hills_pre_match_proximal.rds")
 
 ############## 2014
 
 hills14_t <- filter(hills_pre_match, first_tr_year == "2014-11-04") %>% 
-  mutate(treated = 1) %>% 
-  select(-pre_stops_c)
+  mutate(treated = 1)
 
 hills14_c <- filter(hills_pre_match, first_tr_year == "2016-11-08",
                     !(voter_id %in% hills14_t$voter_id)) %>% 
-  mutate(treated = 0) %>% 
-  select(-pre_stops) %>% 
-  rename(pre_stops = pre_stops_c)
-  
-  
+  mutate(treated = 0)
+
+
 hills14 <- bind_rows(hills14_t, hills14_c) %>%  
   mutate(first_tr_year = 1) %>% 
   select(-v14, -v16) %>% 
@@ -49,14 +46,11 @@ hills14 <- bind_rows(hills14_t, hills14_c) %>%
 ############## 2016
 
 hills16_t <- filter(hills_pre_match, first_tr_year == "2016-11-08") %>% 
-  mutate(treated = 1) %>% 
-  select(-pre_stops_c)
+  mutate(treated = 1)
 
 hills16_c <- filter(hills_pre_match, first_tr_year == "2018-11-06",
                     !(voter_id %in% hills16_t$voter_id)) %>% 
-  mutate(treated = 0) %>% 
-  select(-pre_stops) %>% 
-  rename(pre_stops = pre_stops_c)
+  mutate(treated = 0)
 
 
 hills16 <- bind_rows(hills16_t, hills16_c) %>%  
@@ -68,15 +62,11 @@ hills16 <- bind_rows(hills16_t, hills16_c) %>%
 ############## 2018
 
 hills18_t <- filter(hills_pre_match, first_tr_year == "2018-11-06") %>% 
-  mutate(treated = 1) %>% 
-  select(-pre_stops_c)
+  mutate(treated = 1)
 
 hills18_c <- filter(hills_pre_match, first_tr_year == "2020-11-03",
                     !(voter_id %in% hills18_t$voter_id)) %>% 
-  mutate(treated = 0) %>% 
-  select(-pre_stops) %>% 
[…]

### 2021-04-30 code/hills/09_match_prox.R

@@ -12,19 +12,16 @@ require(snow)
 require(parallel)
 
 
-hills_pre_match <- readRDS("temp/hills_pre_match.rds")
+hills_pre_match <- readRDS("temp/hills_pre_match_proximal.rds")
 
 ############## 2014
 
 hills14_t <- filter(hills_pre_match, first_tr_year == "2014-11-04") %>% 
-  mutate(treated = 1) %>% 
-  select(-pre_stops_c)
+  mutate(treated = 1)
 
 hills14_c <- filter(hills_pre_match, first_tr_year == "2016-11-08",
                     !(voter_id %in% hills14_t$voter_id)) %>% 
-  mutate(treated = 0) %>% 
-  select(-pre_stops) %>% 
-  rename(pre_stops = pre_stops_c)
+  mutate(treated = 0)
 
 
 hills14 <- bind_rows(hills14_t, hills14_c) %>%  
@@ -37,14 +34,11 @@ hills14 <- bind_rows(hills14_t, hills14_c) %>%
 ############## 2016
 
 hills16_t <- filter(hills_pre_match, first_tr_year == "2016-11-08") %>% 
-  mutate(treated = 1) %>% 
-  select(-pre_stops_c)
+  mutate(treated = 1)
 
 hills16_c <- filter(hills_pre_match, first_tr_year == "2018-11-06",
                     !(voter_id %in% hills16_t$voter_id)) %>% 
-  mutate(treated = 0) %>% 
-  select(-pre_stops) %>% 
-  rename(pre_stops = pre_stops_c)
+  mutate(treated = 0)
 
 
 hills16 <- bind_rows(hills16_t, hills16_c) %>%  
@@ -56,15 +50,11 @@ hills16 <- bind_rows(hills16_t, hills16_c) %>%
 ############## 2018
 
 hills18_t <- filter(hills_pre_match, first_tr_year == "2018-11-06") %>% 
-  mutate(treated = 1) %>% 
-  select(-pre_stops_c)
+  mutate(treated = 1)
 
 hills18_c <- filter(hills_pre_match, first_tr_year == "2020-11-03",
                     !(voter_id %in% hills18_t$voter_id)) %>% 
-  mutate(treated = 0) %>% 
-  select(-pre_stops) %>% 
-  rename(pre_stops = pre_stops_c)
-
+  mutate(treated = 0)
 
 hills18 <- bind_rows(hills18_t, hills18_c) %>%  
   mutate(first_tr_year = 3) %>% 
[…]

### 2021-04-30 code/hills/10_reg_prox.R

@@ -1,19 +1,20 @@
 
 #####
-hills_pre_match <- readRDS("temp/real_pre_match_hills_mayor.rds") %>% 
+hills_pre_match <- readRDS("temp/real_pre_match_hills_prox.rds") %>% 
   ungroup()
 
-matches <- readRDS("temp/matches_hills_y_mayor.rds")
+matches <- readRDS("temp/matches_hills_yem_prox.rds")
 
 matches <- left_join(matches, select(hills_pre_match, voter_id, first_tr_year),
                      by = c("group" = "voter_id", "first_tr_year")) %>% 
   mutate(fd = first_tr_year,
-         first_tr_year = ifelse(first_tr_year == 1, "2015-03-03",
-                                ifelse(first_tr_year == 2, "2019-03-05", "XX")),
+         first_tr_year = ifelse(first_tr_year == 1, "2014-11-04",
+                                ifelse(first_tr_year == 2, "2016-11-08",
+                                       ifelse(first_tr_year == 3, "2018-11-06", "XX"))),
          first_tr_year = as.Date(first_tr_year))
 
 hist <- readRDS("temp/full_raw_coded_hills_w_bgs.rds") %>%
-  select(voter_id, starts_with("v1"), v08, v07) %>%
+  select(voter_id, starts_with("v1"), v08) %>%
   pivot_longer(!starts_with("vo"), names_to = "year", values_to = "to")
 
 elec_dates <- fread("raw_data/election_dates.csv")
@@ -25,9 +26,9 @@ hist <- left_join(hist, elec_dates) %>%
 
 
 matches <- left_join(matches, hist %>% 
-                       filter(year(year) %% 2 == 1), by = c("voter" = "voter_id"))
+                       filter(year(year) %% 2 == 0), by = c("voter" = "voter_id"))
 
-periods <- fread("raw_data/period_lu_mayor.csv") %>% 
+periods <- fread("raw_data/period_lu.csv") %>% 
   mutate_at(vars(first_tr_year, year), as.Date, "%m/%d/%Y")
 
 matches <- left_join(matches, periods) %>% 
@@ -35,12 +36,12 @@ matches <- left_join(matches, periods) %>%
 
 matches <- left_join(matches,
                      hills_pre_match %>%
-                       select(-GEOID, -amount_paid, -last_date),
+                       select(-GEOID),
                      by = c("voter" = "voter_id", "fd" = "first_tr_year"))
 
 matches <- left_join(matches,
                      hills_pre_match %>%
[…]

### 2021-04-30 code/hills/mayor/01_download_hills_stops_mayor.R

@@ -85,115 +85,123 @@ hills_stops <- readRDS("temp/hills_stops.rds") %>%
 # CONSIDERED TREATED
 
 # WE'LL START BY PULLING ALL THE PRE-TREATEMENT PERIOD STOPS FOR BOTH GROUPS TO MERGE BACK IN LATER
-pre13 <- filter(hills_stops, offense_date <= "2013-03-03")[,
-                                                           .(stop_count = .N),
-                                                           .(first_name, last_name, date_of_birth, offense_date)]  # using data.table syntax for speed
-pre13 <-  pre13[,
-                .(stop_count = .N),
-                .(first_name, last_name, date_of_birth)]  # using data.table syntax for speed
-
-pre17 <- filter(hills_stops, offense_date <= "2017-03-05")[,
-                                                           .(stop_count = .N),
-                                                           .(first_name, last_name, date_of_birth, offense_date)]  # using data.table syntax for speed
-
-pre17 <-  pre17[,
-                .(stop_count = .N),
-                .(first_name, last_name, date_of_birth)]  # using data.table syntax for speed
-
-
-##############################
-
-# FROM HERE IT'S RELATIVELY STRAIGHTFORWARD: WE NEED TO MAKE THOSE 4 GROUPS
-# TREATNEBT GROUP 1
-s13_15 <- filter(hills_stops, offense_date > "2013-03-03",
-                 offense_date <= "2015-03-03")[,
-                                               .(amount_paid = sum(amount_paid),
-                                                 civil = min(civil)),
-                                               .(first_name, last_name, date_of_birth, offense_date)]
-s13_15 <- s13_15[,
-                 .(stop_count = .N,
-                   last_date = max(offense_date),
-                   amount_paid = sum(amount_paid),
-                   civil = min(civil)),
-                 .(first_name, last_name, date_of_birth)] %>%
-  mutate(first_tr_year = as.Date("2015-03-03"))
-
-s13_15 <- left_join(s13_15, pre13) %>% 
-  rename(pre_stops = stop_count)
-
-# CONTROL GROUP 1
-s15_17 <- filter(hills_stops, offense_date > "2015-03-03",
-                 offense_date <= "2017-03-03")[,
-                                               .(amount_paid = sum(amount_paid),
-                                                 civil = min(civil)),
[…]

### 2021-04-30 code/hills/mayor/02_genmatch_weights_mayor.R

@@ -44,10 +44,6 @@ hills19_t <- filter(hills_pre_match, first_tr_year == "2019-03-05") %>%
 ###########################################
 pre <- bind_rows(hills15_t, hills19_t)
 
-
-###########################################
-pre <- bind_rows(hills15_t, hills19_t)
-
 samp <- pre %>% 
   group_by(treated, first_tr_year) %>% 
   sample_frac(0.05) %>% 
@@ -55,16 +51,15 @@ samp <- pre %>%
 
 match_data <- samp %>% 
   select(-voter_id, -treated, -GEOID, -amount_paid, -last_date,
-         -pre, -v15, -v19, -v07) %>% 
+         -v15, -v19, -v07, -reg_date) %>% 
   mutate_at(vars(white, black, latino, asian, male, dem, rep, v1, v2, paid), ~ ifelse(. == T, 1, 0)) %>% 
-  mutate(reg_date = as.integer(reg_date)) %>% 
-  select(first_tr_year, paid, civil, everything())
+  select(first_tr_year, paid, civil, tampa_pd, v1, v2, everything())
 
 
 match_data <- match_data[complete.cases(match_data), ]
 
 genout <- GenMatch(Tr = samp$treated, X = match_data, replace = T, pop.size = 1000,
-                   exact = c(rep(T, 3), rep(F, 17)), cluster = cl)
+                   exact = c(rep(T, 6), rep(F, 14)), cluster = cl)
 
 saveRDS(genout, "temp/genout_hills_y_mayor.rds")
 

### 2021-04-30 code/hills/mayor/03_match_mayor.R

@@ -40,11 +40,9 @@ ids <- pre %>%
 
 X <- pre %>%
   select(-voter_id, -treated, -GEOID, -amount_paid, -last_date,
-         -pre, -v15, -v19, -v07) %>% 
+         -v15, -v19, -v07, -reg_date) %>% 
   mutate_at(vars(white, black, latino, asian, male, dem, rep, v1, v2, paid), ~ ifelse(. == T, 1, 0)) %>% 
-  mutate(reg_date = as.integer(reg_date)) %>% 
-  select(first_tr_year, paid, civil, everything())
-
+  select(first_tr_year, paid, civil, tampa_pd, v1, v2, everything())
 
 genout <- readRDS("temp/genout_hills_y_mayor.rds")
 
@@ -57,7 +55,7 @@ mout <- Matchby(Tr = pre$treated, X = X,
                        X$male,
                        X$dem,
                        X$rep), estimand = "ATT", Weight.matrix = genout, M = 1, ties = T,
-                exact = c(rep(T, 3), rep(F, 17)))
+                exact = c(rep(T, 6), rep(F, 14)))
 
 
 save(mout, file = "./temp/mout_hills_y_mayor.RData")

### 2021-04-30 code/hills/mayor/07_windows.R

@@ -1,0 +1,188 @@
+library(Matching)
+library(tidyverse)
+library(lubridate)
+library(data.table)
+
+lapply(c(1:23), function(i){
+  pre <- readRDS("temp/real_pre_match_hills_mayor.rds") %>% 
+    filter(((last_date >= (ymd(as.Date("2015-03-03")) %m+% months(-i))) &
+              (last_date <= ymd(as.Date("2015-03-03")) %m+% months(i)) & (first_tr_year == 1)) |
+             ((last_date >= (ymd(as.Date("2019-03-05")) %m+% months(-i))) &
+                (last_date <= ymd(as.Date("2019-03-05")) %m+% months(i)) & (first_tr_year == 2)))
+  
+  
+  ids <- pre %>%
+    mutate(id = row_number()) %>%
+    select(id, voter_id, first_tr_year)
+  
+  X <- pre %>%
+    select(-voter_id, -treated, -GEOID, -amount_paid, -last_date,
+           -v15, -v19, -v07, -reg_date) %>% 
+    mutate_at(vars(white, black, latino, asian, male, dem, rep, v1, v2, paid), ~ ifelse(. == T, 1, 0)) %>% 
+    select(first_tr_year, paid, civil, tampa_pd, v1, v2, everything())
+  
+  genout <- readRDS("temp/genout_hills_y_mayor.rds")
+  
+  
+  mout <- Matchby(Tr = pre$treated, X = X,
+                  by = c(X$first_tr_year,
+                         X$white,
+                         X$black,
+                         X$latino,
+                         X$asian,
+                         X$male,
+                         X$dem,
+                         X$rep), estimand = "ATT", Weight.matrix = genout, M = 1, ties = T,
+                  exact = c(rep(T, 6), rep(F, 14)))
+  
+  matches <- data.table(voter = c(mout$index.control,
+                                  mout$index.treated),
+                        group = rep(mout$index.treated, 2),
+                        weight = rep(mout$weights, 2)) %>%
+    group_by(voter, group) %>%
+    summarize(weight = sum(weight)) %>%
+    ungroup()
+  
+  
+  matches <- left_join(matches, ids, by = c("voter" = "id")) %>%
+    select(-voter, -first_tr_year) %>%
+    rename(voter = voter_id)
+  
+  matches <- left_join(matches, ids, by = c("group" = "id")) %>%
+    select(-group) %>%
[…]

### 2021-04-30 code/robust/fl_real_modelled_race.R

@@ -1,0 +1,64 @@
+##################################
+
+db_raw <- dbConnect(SQLite(), "D:/rolls.db")
+fl_race <- dbGetQuery(db_raw, "select Race, Voter_ID from fl_roll_201902")
+
+
+l2_db <- dbConnect(SQLite(), "D:/national_file.db")
+fl_lookup <- dbGetQuery(l2_db, "select LALVOTERID, Voters_StateVoterID, EthnicGroups_EthnicGroup1Desc from fl")
+
+fl_coded <- readRDS("temp/subs_places_12.rds")
+
+fl_coded <- left_join(fl_coded, fl_lookup)
+
+fl_coded <- left_join(fl_coded, fl_race, by = c("Voters_StateVoterID" = "Voter_ID"))
+
+fl_places <- fl_coded %>%
+  filter(!is.na(Race)) %>% 
+  mutate(black = Race == 3) %>% 
+  group_by(black, plasub = place) %>%
+  tally()
+
+fl_subs <- fl_coded %>%
+  filter(!is.na(Race)) %>% 
+  mutate(black = Race == 3,
+         plasub = paste0(substring(county_s, 1, 2), substring(county_s, 6))) %>% 
+  group_by(black, plasub) %>%
+  tally() %>% 
+  filter(!(plasub %in% fl_places$plasub))
+  
+fl_real <- bind_rows(fl_subs, fl_places) %>% 
+  group_by(plasub) %>% 
+  mutate(share_black_vf = n / sum(n)) %>% 
+  filter(black) %>% 
+  select(plasub, share_black_vf)
+
+############################
+
+cog <- readRDS("temp/cog_cities.rds") %>% 
+  mutate(state = as.factor(state),
+         fines_rev = dper / total_revenue)
+
+place_to <- readRDS("temp/place_to.rds") %>% 
+  rename(plasub = place)
+
+county_s_to <- readRDS("temp/county_s_to.rds") %>% 
+  rename(plasub = county_s)
+
+county_s_to <- county_s_to[!(county_s_to$plasub %in% place_to$plasub),]
+
+city_to <- bind_rows(place_to, county_s_to)
+
+city_to <- city_to[city_to$plasub %in% cog$GEOID, ] %>% 
+  mutate(black = EthnicGroups_EthnicGroup1Desc == "Likely African-American") %>% 
+  group_by(plasub, black) %>% 
+  summarize(count = sum(count)) %>% 
[…]

### 2021-04-30 code/robust/ga_real_modelled_race.R

@@ -1,0 +1,66 @@
+##################################
+
+db_raw <- dbConnect(SQLite(), "D:/rolls.db")
+ga_race <- dbGetQuery(db_raw, "select REGISTRATION_NUMBER, RACE from ga_roll_0319")
+
+
+l2_db <- dbConnect(SQLite(), "D:/national_file.db")
+ga_lookup <- dbGetQuery(l2_db, "select LALVOTERID, Voters_StateVoterID, EthnicGroups_EthnicGroup1Desc from ga")
+
+ga_coded <- readRDS("temp/subs_places_13.rds")
+
+ga_coded <- left_join(ga_coded, ga_lookup)
+
+ga_coded <- left_join(ga_coded, ga_race, by = c("Voters_StateVoterID" = "REGISTRATION_NUMBER"))
+
+ga_places <- ga_coded %>%
+  filter(!is.na(RACE)) %>% 
+  mutate(black = RACE == "BH") %>% 
+  group_by(black, plasub = place) %>%
+  tally()
+
+ga_subs <- ga_coded %>%
+  filter(!is.na(RACE)) %>% 
+  mutate(black = RACE == "BH",
+         plasub = paste0(substring(county_s, 1, 2), substring(county_s, 6))) %>% 
+  group_by(black, plasub) %>%
+  tally() %>% 
+  filter(!(plasub %in% ga_places$plasub))
+
+ga_real <- bind_rows(ga_subs, ga_places) %>% 
+  group_by(plasub) %>% 
+  mutate(share_black_vf = n / sum(n)) %>% 
+  filter(black) %>% 
+  select(plasub, share_black_vf)
+
+############################
+
+cog <- readRDS("temp/cog_cities.rds") %>% 
+  mutate(state = as.factor(state),
+         fines_rev = dper / total_revenue)
+
+place_to <- readRDS("temp/place_to.rds") %>% 
+  rename(plasub = place)
+
+county_s_to <- readRDS("temp/county_s_to.rds") %>% 
+  rename(plasub = county_s)
+
+county_s_to <- county_s_to[!(county_s_to$plasub %in% place_to$plasub),]
+
+city_to <- bind_rows(place_to, county_s_to)
+
+city_to <- city_to[city_to$plasub %in% cog$GEOID, ] %>% 
+  mutate(black = EthnicGroups_EthnicGroup1Desc == "Likely African-American") %>% 
+  group_by(plasub, black) %>% 
[…]

### 2021-04-30 code/robust/maes.R

@@ -1,0 +1,60 @@
+
+test_set <- bind_rows(
+  readRDS("temp/ga_real_model_city.rds"),
+  readRDS("temp/nc_real_model_city.rds"),
+  readRDS("temp/fl_real_model_city.rds")
+)
+
+ggplot(test_set, aes(x = share_black_vf, y = share_black_l2)) + geom_point() +
+  theme_bc(base_family = "LM Roman 10") +
+  scale_y_continuous(name = "Predicted Share Black",
+                     labels = percent) +
+  scale_x_continuous(name = "Actual Share Black",
+                     labels = percent) +
+  geom_abline(slope = 1)
+
+
+cog <- readRDS("temp/cog_cities.rds") %>% 
+  mutate(state = as.factor(state),
+         fines_rev = dper / total_revenue)
+
+test_set <- left_join(test_set, cog, by = c("plasub" = "GEOID"))
+
+#####################
+
+m1 <- mae(filter(test_set,
+                 population <= quantile(test_set$population, 0.25))$share_black_vf,
+          filter(test_set,
+                 population <= quantile(test_set$population, 0.25))$share_black_l2)
+
+m2 <- mae(filter(test_set,
+                 population > quantile(test_set$population, 0.25),
+                 population <= quantile(test_set$population, 0.5))$share_black_vf,
+          filter(test_set,
+                 population > quantile(test_set$population, 0.25),
+                 population <= quantile(test_set$population, 0.5))$share_black_l2)
+
+m3 <- mae(filter(test_set,
+                 population > quantile(test_set$population, 0.5),
+                 population <= quantile(test_set$population, 0.75))$share_black_vf,
+          filter(test_set,
+                 population > quantile(test_set$population, 0.5),
+                 population <= quantile(test_set$population, 0.75))$share_black_l2)
+
+m4 <- mae(filter(test_set,
+                 population > quantile(test_set$population, 0.75))$share_black_vf,
+          filter(test_set,
+                 population > quantile(test_set$population, 0.75))$share_black_l2)
+
+m5 <- mae(test_set$share_black_vf, test_set$share_black_l2)
+
+
+dat <- data.table("Bottom Quartile" = m1,
+                  "Second Quartile" = m2,
+                  "Third Quartile" = m3,
+                  "Fourth Quartile" = m4,
+                  "Overall" = m5) %>% 
+  mutate_all(percent, accuracy = .02)
+
+saveRDS(dat, "temp/maes.rds")
+

### 2021-04-30 code/robust/nc_real_modelled_race.R

@@ -1,0 +1,64 @@
+##################################
+
+db_raw <- dbConnect(SQLite(), "D:/rolls.db")
+nc_race <- dbGetQuery(db_raw, "select ncid, race_code from nc_roll_0219")
+
+
+l2_db <- dbConnect(SQLite(), "D:/national_file.db")
+nc_lookup <- dbGetQuery(l2_db, "select LALVOTERID, Voters_StateVoterID, EthnicGroups_EthnicGroup1Desc from nc")
+
+nc_coded <- readRDS("temp/subs_places_37.rds")
+
+nc_coded <- left_join(nc_coded, nc_lookup)
+
+nc_coded <- left_join(nc_coded, nc_race, by = c("Voters_StateVoterID" = "ncid"))
+
+nc_places <- nc_coded %>%
+  filter(!is.na(race_code)) %>% 
+  mutate(black = race_code == "B") %>% 
+  group_by(black, plasub = place) %>%
+  tally()
+
+nc_subs <- nc_coded %>%
+  filter(!is.na(race_code)) %>% 
+  mutate(black = race_code == "B",
+         plasub = paste0(substring(county_s, 1, 2), substring(county_s, 6))) %>% 
+  group_by(black, plasub) %>%
+  tally() %>% 
+  filter(!(plasub %in% nc_places$plasub))
+
+nc_real <- bind_rows(nc_subs, nc_places) %>% 
+  group_by(plasub) %>% 
+  mutate(share_black_vf = n / sum(n)) %>% 
+  filter(black) %>% 
+  select(plasub, share_black_vf)
+
+############################
+
+cog <- readRDS("temp/cog_cities.rds") %>% 
+  mutate(state = as.factor(state),
+         fines_rev = dper / total_revenue)
+
+place_to <- readRDS("temp/place_to.rds") %>% 
+  rename(plasub = place)
+
+county_s_to <- readRDS("temp/county_s_to.rds") %>% 
+  rename(plasub = county_s)
+
+county_s_to <- county_s_to[!(county_s_to$plasub %in% place_to$plasub),]
+
+city_to <- bind_rows(place_to, county_s_to)
+
+city_to <- city_to[city_to$plasub %in% cog$GEOID, ] %>% 
+  mutate(black = EthnicGroups_EthnicGroup1Desc == "Likely African-American") %>% 
+  group_by(plasub, black) %>% 
+  summarize(count = sum(count)) %>% 
[…]

### 2021-04-30 markdown/si.Rmd
fix typo

@@
 The MAE is commonly used to measure how different an estimated set of numbers are from their real value.
-Because it seems possible that these errors could be larger in smaller municipalities, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.
+Because it seems possible that these errors vary by population size, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.
 

### 2021-04-30 markdown/si.tex
fix typo

@@
 
-In Table \ref{tab:mae} we present the mean average error (MAE) of the L2 estimates aggregated up to the municipality level.
-The MAE is commonly used to measure how different an estimated number is from its real value.
-Because it seems possible that these errors could be larger in smaller municipalities, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.
+In Table \ref{tab:mae} we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level.
+The MAE is commonly used to measure how different an estimated set of numbers are from their real value.
+Because it seems possible that these errors vary by population size, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.
 

### 2021-05-01 markdown/draft_paper.Rmd
clean up language about reasonability of municipality racial estimates

@@
 Moreover, by using the racial estimates provided by L2 we can estimate the number of ballots cast by voters of each race in each city.
-Each voters’ race is modeled based on L2’s algorithms and not self-reported, surely leading to errors at the individual-voter level.
-We assume this does not present a problem when records are aggregated to the municipal level.
+While in a few states race is self-reported by voters, race is in most cases modeled by L2 using first, middle, and last name, as well as Census block demographic information.
+Although this is a commonly used way to determine voters’ races [@Imai2016], it is subject to some error.
+We assume, however, that after controlling for other municipality-level characteristics, the errors in these predictions will be uncorrelated with fees and fines collections.
+Put differently, although we acknowledge that these estimates are imprecise, we expect that these errors are effectively random.
+Further, as we show in the Supplemental Information, the estimated Black share of the electorate tracks very closely with the share of the citizen voting age population that is non-Hispanic Black.
+After accounting for state-level voter registration differentials, the mean absolute error between these two measures is 2.4% and is unrelated to per-capita fines and fees after controlling for other covariates (*p* = 0.92).
+The individual-level racial estimates, when aggregated to the municipal level, thus provide a reasonably unbiased picture of the municipal electorate.
 

### 2021-05-01 markdown/draft_paper.tex
clean up language about reasonability of municipality racial estimates

@@
 \author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
-\date{April 28, 2021}
+\date{May 01, 2021}
 
@@
 Moreover, by using the racial estimates provided by L2 we can estimate the number of ballots cast by voters of each race in each city.
-Each voters' race is modeled based on L2's algorithms and not self-reported, surely leading to errors at the individual-voter level.
-We assume this does not present a problem when records are aggregated to the municipal level.
+While in a few states race is self-reported by voters, race is in most cases modeled by L2 using first, middle, and last name, as well as Census block demographic information.
+Although this is a commonly used way to determine voters' races (\protect\hyperlink{ref-Imai2016}{Imai and Khanna 2016/ed}), it is subject to some error.
+We assume, however, that after controlling for other municipality-level characteristics, the errors in these predictions will be uncorrelated with fees and fines collections.
+Put differently, although we acknowledge that these estimates are imprecise, we expect that these errors are effectively random.
+Further, as we show in the Supplemental Information, the estimated Black share of the electorate tracks very closely with the share of the citizen voting age population that is non-Hispanic Black.
+After accounting for state-level voter registration differentials, the mean absolute error between these two measures is 2.4\% and is unrelated to per-capita fines and fees after controlling for other covariates (\emph{p} = 0.92).
+The individual-level racial estimates, when aggregated to the municipal level, thus provide a reasonably unbiased picture of the municipal electorate.
 
@@
 
+\leavevmode\hypertarget{ref-Imai2016}{}%
+Imai, Kosuke, and Kabir Khanna.
+2016/ed.
+{``Improving {Ecological Inference} by {Predicting Individual Ethnicity} from {Voter Registration Records}.''} \emph{Political Analysis} 24 (2): 263--72.
+\url{https://doi.org/10.1093/pan/mpw001}.
+
 \leavevmode\hypertarget{ref-Imai2020}{}%

### 2021-05-01 markdown/si.Rmd
clean up language about reasonability of municipality racial estimates

@@
 
-While most states in the country do not ask voters to self-report their race when they register to vote, a handful *do* collect this information.
-The raw voter files in these states, then, include true individual-level information about the racial makeup of the electorate.
+Because there are no precise estimates of the racial demographics of the registered electorate in each state, we compare the estimated Black share of each municipality to the Black share of the citizen voting age population (CVAP) in each municipality.
+This method is not without drawbacks: if different cities have different racial registration rates, they will not track the perfectly.
+To mitigate some of this discrepancy, we adjust the Black share of the electorate in each municipality by the racial registration gap in that municipality's state, according to the Current Population Survey's (CPS) 2018 data.
+For example, according to the CPS, 27.0% of the CVAP in Alabama was Black in 2018, but just 26.4% of registered voters were Black.
+We therefore add 0.6% to the estimated Black share of the electorate in each municipality in Alabama, so that it might more closely mirror the Black share of CVAP.
 
-To test the validity of the L2 records, we use the L2 estimates and self-reported race from the raw voter files in Florida, Georgia, and North Carolina.
-We use both sets of data to estimate the Black share of the electorate in each municipality used in the body of this paper.
-Comparing the "estimated" share Black from L2 to the "real" share Black from the voter file gives us a good sense of how well our approach works in these states.
-
-In Table \ref{tab:mae} we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level.
-The MAE is commonly used to measure how different an estimated set of numbers are from their real value.
+In Table \ref{tab:mae} we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level and adjusted according to the CPS, relative to the Census Bureau's CVAP estimate.
 Because it seems possible that these errors vary by population size, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.
@@
   mutate_all(linebreak) %>% 
-  knitr::kable(booktabs = T, caption = "(\\#tab:mae) MAE of L2 Municipality Estimates (Florida, Georgia, North Carolina)", linesep = "", escape = F,
+  knitr::kable(booktabs = T, caption = "(\\#tab:mae) MAE of L2 Municipality Estimates, CVAP", linesep = "", escape = F,
                col.names = linebreak(colnames(t)),
@@
 
-Table \ref{tab:mae} makes clear that for no group of municipalities does the MAE exceed 1.5%.
-Although this robustness check is limited to just 3 states, the available evidence indicates that aggregating from individual-level racial estimates in the L2 data to municipality-level demographics of the electorate does not result in unacceptable biases.
+Table \ref{tab:mae} makes clear that the adjusted Black estimates of the electorate mirror the Black share of CVAP very closely: for no group of municipalities does the MAE exceed 3%.
+This seems to indicate that the L2 racial estimates are quite good when aggregated to the municipal level.
+
+In Table \ref{tab:mae:reg}, we show that the difference between the adjusted estimate of the Black share of the electorate and the Black share of the CVAP is entirely unrelated to cities' per-capita fees and fines, after controlling for other characteristics.
+Given the low MAE and the lack of relationship between the error and the fees and fines, we conclude that the municipal-level racial estimates from the individual-level records are reasonable and unbiased.
+
+\begin{singlespace}
+\input{"../temp/mae_clean.tex"}
+\end{singlespace}
 

### 2021-05-01 markdown/si.tex
clean up language about reasonability of municipality racial estimates

@@
 
-While most states in the country do not ask voters to self-report their race when they register to vote, a handful \emph{do} collect this information.
-The raw voter files in these states, then, include true individual-level information about the racial makeup of the electorate.
+Because there are no precise estimates of the racial demographics of the registered electorate in each state, we compare the estimated Black share of each municipality to the Black share of the citizen voting age population (CVAP) in each municipality.
+This method is not without drawbacks: if different cities have different racial registration rates, they will not track the perfectly.
+To mitigate some of this discrepancy, we adjust the Black share of the electorate in each municipality by the racial registration gap in that municipality's state, according to the Current Population Survey's (CPS) 2018 data.
+For example, according to the CPS, 27.0\% of the CVAP in Alabama was Black in 2018, but just 26.4\% of registered voters were Black.
+We therefore add 0.6\% to the estimated Black share of the electorate in each municipality in Alabama, so that it might more closely mirror the Black share of CVAP.
 
-To test the validity of the L2 records, we use the L2 estimates and self-reported race from the raw voter files in Florida, Georgia, and North Carolina.
-We use both sets of data to estimate the Black share of the electorate in each municipality used in the body of this paper.
-Comparing the ``estimated'' share Black from L2 to the ``real'' share Black from the voter file gives us a good sense of how well our approach works in these states.
-
-In Table \ref{tab:mae} we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level.
-The MAE is commonly used to measure how different an estimated set of numbers are from their real value.
+In Table \ref{tab:mae} we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level and adjusted according to the CPS, relative to the Census Bureau's CVAP estimate.
 Because it seems possible that these errors vary by population size, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.
@@
 
-\caption{\label{tab:mae-chunck}\label{tab:mae} MAE of L2 Municipality Estimates (Florida, Georgia, North Carolina)}
+\caption{\label{tab:mae-chunck}\label{tab:mae} MAE of L2 Municipality Estimates, CVAP}
 \centering
@@
 \midrule
-1.08\% & 1.38\% & 1.36\% & 1.48\% & 1.32\%\\
+2.40\% & 2.38\% & 2.24\% & 2.70\% & 2.42\%\\
 \bottomrule
@@
 
-Table \ref{tab:mae} makes clear that for no group of municipalities does the MAE exceed 1.5\%.
-Although this robustness check is limited to just 3 states, the available evidence indicates that aggregating from individual-level racial estimates in the L2 data to municipality-level demographics of the electorate does not result in unacceptable biases.
+Table \ref{tab:mae} makes clear that the adjusted Black estimates of the electorate mirror the Black share of CVAP very closely: for no group of municipalities does the MAE exceed 3\%.
+This seems to indicate that the L2 racial estimates are quite good when aggregated to the municipal level.
+
+In Table \ref{tab:mae:reg}, we show that the difference between the adjusted estimate of the Black share of the electorate and the Black share of the CVAP is entirely unrelated to cities' per-capita fees and fines, after controlling for other characteristics.
+Given the low MAE and the lack of relationship between the error and the fees and fines, we conclude that the municipal-level racial estimates from the individual-level records are reasonable and unbiased.
+
+\begin{singlespace}
+\input{"../temp/mae_clean.tex"}
+\end{singlespace}
 

### 2021-05-01 code/02_2018_cross_sectional.R

@@ -38,12 +38,14 @@ to <- bind_rows(city_to %>%
             to_16 = sum(votes_16) / sum(count),
             votes_18 = sum(votes_18),
             votes_16 = sum(votes_16),
-            votes_10 = sum(votes_10)) %>% 
+            votes_10 = sum(votes_10),
+            voters = sum(count)) %>% 
   pivot_wider(id_cols = "plasub", names_from = "race", values_from = c("to_18",
                                                                        "to_16",
                                                                        "votes_18",
                                                                        "votes_16",
-                                                                       "votes_10"))
+                                                                       "votes_10",
+                                                                       "voters"))
 
 full_set <- inner_join(cog, to, by = c("GEOID" = "plasub")) %>% 
   mutate(vap_to_18_overall = votes_18_overall / cvap,
@@ -61,7 +63,9 @@ full_set <- inner_join(cog, to, by = c("GEOID" = "plasub")) %>%
          vap_to_18_asian = votes_18_asian / asian_cvap,
          vap_to_10_asian = votes_10_asian / asian_cvap,
          vap_to_18_other = votes_18_other / other_cvap,
-         vap_to_10_other = votes_10_other / other_cvap)
+         vap_to_10_other = votes_10_other / other_cvap,
+         share_electorate_black = voters_black / voters_overall,
+         cvap_share_black = black_cvap / cvap)
 
 p1 <- ggplot(full_set, aes(x = lndper, y = vap_to_18_black)) + geom_point(shape = 1) + geom_smooth(method = "lm") +
   xlab("Dollars per Resident") +
@@ -82,6 +86,8 @@ p1
 full_set <- rename(full_set, share_s_fed = share_state_fed) %>% 
   mutate(median_income = median_income / 10000,
          lpd = log(pop_dens))
+
+saveRDS(full_set, "temp/full_set_for_mae.rds")
 
 covars <- gsub("\\n|            ", "", "lndper + nh_white + nh_black + latino + asian + lpd +
             median_income + some_college + median_age + share_over_64 +
@@ -125,7 +131,7 @@ stargazer(models, type = "text", omit = c("state"),
           omit.stat = c("F", "ser"),
           out = "temp/cog_cross_raw.tex",
           table.placement = "H",
-          title = "\\label{tab:cog-cross-reg} Fees and Fines and 2020 Turnout")
[…]

### 2021-05-01 code/robust/maes.R

@@ -1,52 +1,42 @@
 
-test_set <- bind_rows(
-  readRDS("temp/ga_real_model_city.rds"),
-  readRDS("temp/nc_real_model_city.rds"),
-  readRDS("temp/fl_real_model_city.rds")
-)
-
-ggplot(test_set, aes(x = share_black_vf, y = share_black_l2)) + geom_point() +
-  theme_bc(base_family = "LM Roman 10") +
-  scale_y_continuous(name = "Predicted Share Black",
-                     labels = percent) +
-  scale_x_continuous(name = "Actual Share Black",
-                     labels = percent) +
-  geom_abline(slope = 1)
+test_set <- readRDS("temp/full_set_for_mae.rds") %>% 
+  filter(!is.na(share_electorate_black), !is.na(cvap_share_black))
 
 
-cog <- readRDS("temp/cog_cities.rds") %>% 
-  mutate(state = as.factor(state),
-         fines_rev = dper / total_revenue)
+adj_regs <- fread("raw_data/adj_regs.csv") %>% 
+  mutate(state = str_pad(state, width = 2, side = "left", pad = "0"))
 
-test_set <- left_join(test_set, cog, by = c("plasub" = "GEOID"))
 
-#####################
+test_set <- left_join(test_set, adj_regs)
+
+test_set$share_electorate_black <- test_set$share_electorate_black + test_set$to_add
+################################
 
 m1 <- mae(filter(test_set,
-                 population <= quantile(test_set$population, 0.25))$share_black_vf,
+                 population <= quantile(test_set$population, 0.25))$cvap_share_black,
           filter(test_set,
-                 population <= quantile(test_set$population, 0.25))$share_black_l2)
+                 population <= quantile(test_set$population, 0.25))$share_electorate_black)
 
 m2 <- mae(filter(test_set,
                  population > quantile(test_set$population, 0.25),
-                 population <= quantile(test_set$population, 0.5))$share_black_vf,
+                 population <= quantile(test_set$population, 0.5))$cvap_share_black,
           filter(test_set,
                  population > quantile(test_set$population, 0.25),
-                 population <= quantile(test_set$population, 0.5))$share_black_l2)
+                 population <= quantile(test_set$population, 0.5))$share_electorate_black)
 
 m3 <- mae(filter(test_set,
                  population > quantile(test_set$population, 0.5),
-                 population <= quantile(test_set$population, 0.75))$share_black_vf,
[…]

### 2021-05-07 markdown/draft_paper.Rmd
FINAL FIRST DRAFT!!

@@
 We use three approaches to answer this question: national survey data, a city-level analysis using Census of Governments data and the national voter file, and individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019.
-The survey data show that Black people who report that they were recently stopped by police are more likely to vote compared to those who were not stopped.
-Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.6 percentage point turnout decrease but was not associated with Black turnout.
-In Tampa, Florida, we estimate that being ticketed decreases an individual’s likelihood of voting in federal elections by 1.7 percentage points, but depressive effects are smaller for Black residents.
+The survey data show that Black people who report that they or a family member were recently stopped by police are more likely to vote than those who reported no such contact.
+Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.04 percentage point turnout decrease but was not associated with Black turnout.
+In Tampa, Florida, we estimate that being ticketed decreases an individual's likelihood of voting in federal elections by 1.7 percentage points, but depressive effects are smaller for Black residents.
 
@@
 
-Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities’ alienation from government.
-After Michael Brown was killed by the Ferguson Police Department in 2014, a US Department of Justice investigation into the city’s police and courts demonstrated that the municipality was engaged in a practice that advocates now refer to as “policing for profit.” The city’s reliance on fines and fees to fund government functions grew from 13 to 23 percent of the total budget between fiscal years 2012 and 2015.
+Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities' alienation from government.
+After Michael Brown was killed by the Ferguson Police Department in 2014, a US Department of Justice investigation into the city's police and courts demonstrated that the municipality was engaged in a practice that advocates now refer to as "policing for profit." The city's reliance on fines and fees to fund government functions grew from 13 to 23 percent of the total budget between fiscal years 2012 and 2015.
 From 2012 to 2014, the Department of Justice found that 85 percent of vehicle stops, 90 percent of citations, and 93 percent of arrests targeted Black people.
-By contrast, just two-thirds of Ferguson’s residents are Black [@UnitedStatesDepartmentofJusticeCivilRightsDivision2015].
+By contrast, just two-thirds of Ferguson's residents are Black [@UnitedStatesDepartmentofJusticeCivilRightsDivision2015].
 
-It wasn’t just a Ferguson problem, or even a Missouri problem.
-American cities’ reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services [@Singla2020; @Harris2017].
+It wasn't just a Ferguson problem, or even a Missouri problem.
+American cities' reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services [@Singla2020; @Harris2017].
 
@@
 Such work has largely focused on the effects of highly disruptive contact with the criminal legal system such as incarceration and felony convictions [@Burch2014; @Lee2014].
-This paper is the first to explicitly theorize how local ticketing practices shape the political socialization of ticketed individuals.
+Building on recent theoretical work from @Walker2020a and an analysis of the historical context of fees and fines collections in the United States, this paper is the first to explicitly theorize how local ticketing practices shape the political socialization of ticketed individuals.
 Additionally, our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
-The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures political participation.
+
+In addition to our theoretical contribution, the use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures political participation.
 Past work looking at the individual-level effects of low-level contact has relied entirely on survey or qualitative data [e.g.
@@
 Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to police ticketing.
-The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of the 232,568 individuals ticketed over a 6 year period---a far larger pool than even the most robust surveys.
+The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of the quarter-million individuals ticketed over a 6 year period---a far larger pool than even the most robust surveys.
 
-Before turning to the administrative data, we begin with a novel analysis of 2016 and 2020 national survey data regarding voters’ experience with police stops and arrests.
+Before turning to the administrative data, we begin with a novel analysis of 2020 national survey data regarding voters' experience with police stops.
 We find that Black respondents who reported personal or proximal experience with police stops in the last 12 months are more likely to vote than Black people who did not, while we find no statistically significant relationship between stops and voting among non-Black respondents.
 
-Next, we join fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for each municipality in the country.
+Next, we join fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for thousands of municipalities around the country.
 While we find that increased fees and fines likely cause lower turnout among non-Black Americans, we find no effect of fees and fines on Black turnout.
@@
 states passed laws denying voting rights to people who were convicted of felonies.
-In their analysis of how racial threat catalyzes felon disenfranchisement, @Behrens2003 found that increases in the share of a state’s prison population that is nonwhite drastically increases the likelihood of legislation permanently disenfranchising people convicted of felonies.
+In their analysis of how racial threat catalyzes felon disenfranchisement, @Behrens2003 found that increases in the share of a state's prison population that is nonwhite drastically increases the likelihood of legislation permanently disenfranchising people convicted of felonies.
 As @Shofner1963 notes, felony disenfranchisement has often been tied explicitly to the increased presence of Black Americans in the electorate.
@@
 
-Beyond de jure disenfranchisement, the spatial and racial concentration of criminalization influences affected communities’ perceptions of government.
-Monica Bell calls this process “legal estrangement,” a conceptual framework meant to capture those perceptions and cultural attitudes (“legal cynicism”) as well as the historical-structural conditions that produced them [@Bell2017].
+Beyond de jure disenfranchisement, the spatial and racial concentration of criminalization influences affected communities' perceptions of government.
+Monica Bell calls this process "legal estrangement," a conceptual framework meant to capture those perceptions and cultural attitudes ("legal cynicism") as well as the historical-structural conditions that produced them [@Bell2017].
 Research on legal cynicism has found that public perceptions of abusive police practices can reduce willingness to report crimes or cooperate with law enforcement [@Desmond2016; @Tyler2014].
@@
 stopped, arrested, convicted), people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions [@Brayne2014].
-She calls this phenomenon “system avoidance,” and while her analysis did not specifically assess voting behavior, her findings demonstrate how criminal legal contact can discourage Americans’ participation in public institutions as well as how the effect may vary alongside the intensity of criminal legal intervention.
-Similarly, @Remster2018a finds that men who return home from prison are more likely to avoid contact with their childrens’ schools.
+She calls this phenomenon "system avoidance," and while her analysis did not specifically assess voting behavior, her findings demonstrate how criminal legal contact can discourage Americans' participation in public institutions as well as how the effect may vary alongside the intensity of criminal legal intervention.
+Similarly, @Remster2018a finds that men who return home from prison are more likely to avoid contact with their childrens' schools.
 
 In addition to influencing perceptions of government and participation in public institutions, recent scholarship indicates that criminalization influences political behavior.
-The “hidden curriculum” of the criminal legal system [@Justice2014; @Meares2017] teaches individuals about their position within the political system, and the criminal legal system consequently serves as a primary site of political socialization for convicted individuals and their families [e.g.
+The "hidden curriculum" of the criminal legal system [@Justice2014; @Meares2017] teaches individuals about their position within the political system, and the criminal legal system consequently serves as a primary site of political socialization for convicted individuals and their families [e.g.
 @Lee2014].
@@
 Using existing national survey data and extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) [@Weaver2010].
-Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a “linked fate” where “one’s individual opportunities are linked to the entire racial group” [@Lerman2014, page 197].
-Their interview data lead them to conclude that while criminal legal contact does increase perceptions of linked fate among Black respondents, “a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing”---and interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation [@Lerman2014].
+Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a "linked fate" where "one's individual opportunities are linked to the entire racial group" [@Lerman2014, page 197].
+Their interview data lead them to conclude that while criminal legal contact does increase perceptions of linked fate among Black respondents, "a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing"---and interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation [@Lerman2014].
 
-Lerman and Weaver’s finding has been corroborated by administrative data: Ariel White found that short jail sentences in Harris County, Texas reduced Black defendant turnout in subsequent elections by 13 percentage points---but the effect on white turnout was not statistically significant [@White2019].
+Lerman and Weaver's finding has been corroborated by administrative data: Ariel White found that short jail sentences in Harris County, Texas reduced Black defendant turnout in subsequent elections by 13 percentage points---but the effect on white turnout was not statistically significant [@White2019].
 Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level [@Burch2014].
@@
 Although most work documents a uniformly demobilizing effect from contact with the criminal legal system, recent work from Hannah Walker [-@Walker2020; -@Walker2020a] complicates this narrative by arguing that, when Black Americans understand their contact with the criminal legal system in the context of a narrative of racial injustice, such contact can actually prove mobilizing.
-She explains: “experiences with punitive policies are subject to interpretation and, when understood through narratives of injustice, lead to wholly different participation outcomes than we usually predict” [@Walker2020, page 132].
+She explains: "experiences with punitive policies are subject to interpretation and, when understood through narratives of injustice, lead to wholly different participation outcomes than we usually predict" [@Walker2020, page 132].
 While she finds that this sense of injustice is especially likely to increase political participation in non-voting ways (such as attending a protest or signing a petition), the logic could extend to electoral participation as well given a strong narrative or relatively weak contact with the criminal legal system.
@@
 Despite the growing body of high-quality scholarship on the democratic implications of the American criminal legal system, we still know remarkably little about the effects of the most routine sort of contact---police stops and tickets that do not result in an arrest.
-We leverage Walker’s novel insights about the potentiality of a narrative of injustice to re-think how these sorts of contact with the state can structure political participation.
+We leverage Walker's novel insights about the potentiality of a narrative of injustice to re-think how these sorts of contact with the state can structure political participation.
 
@@
 
-Fines and fees are situated in a distinct historical legacy of racist exploitation that may uniquely facilitate a collective “sense of injustice” among Black Americans---the sort of collective perception that @Walker2020a argues could prove to be politically mobilizing.
+Fines and fees are situated in a distinct historical legacy of racist exploitation that may uniquely facilitate a collective "sense of injustice" among Black Americans---the sort of collective perception that @Walker2020a argues could prove to be politically mobilizing.
 
-Cedric Robinson’s articulation of racial capitalism offers a useful theoretical framework for interpreting the trajectory of American anti-Black political economy [@Robinson2000].
-Brittany Friedman theorizes fines and fees as a “progression of racial capitalism penology,” emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices [@Friedman2020, page 177].
+Cedric Robinson's articulation of racial capitalism offers a useful theoretical framework for interpreting the trajectory of American anti-Black political economy [@Robinson2000].
+Brittany Friedman theorizes fines and fees as a "progression of racial capitalism penology," emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices [@Friedman2020, page 177].
 Robinson argues that European industrial capitalism continued a longer political-economic trend of differentiating racial groups in order to dispossess them and exploit their labor.
@@
 The implementation of the Black Codes, convict leasing, and sharecropping systems marked a transition to a new stage of racial capitalism, wherein criminalization provided an easily-exploited labor supply that offset costs that the state incurred by coercing their labor [@Lichtenstein1996; @Mancini1978].
-Contemporary fines and fees practices have been directly compared to sharecropping because both structures share “a long-term pattern of financial exploitation based on race… that limits the life-choices of the affected population” [@Blessett2016, page 113].
+Contemporary fines and fees practices have been directly compared to sharecropping because both structures share "a long-term pattern of financial exploitation based on race… that limits the life-choices of the affected population" [@Blessett2016, page 113].
 
 In the 20th century, residential segregation simultaneously fueled the racial wealth gap and ensured that criminalization was both spatially and racially concentrated [@Rothstein2017; @Hinton2021].
-At the level of federal policy, racial threat and whites’ attribution of criminality to Blackness [@Muhammad2010] prompted a shift “from the War on Poverty to the War on Crime” wherein Black communities’ demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration [@Hinton2017; @Vargas2017a].
+At the level of federal policy, racial threat and whites' attribution of criminality to Blackness [@Muhammad2010] prompted a shift "from the War on Poverty to the War on Crime" wherein Black communities' demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration [@Hinton2017; @Vargas2017a].
 
@@
 @Sances2017, however, finds that the discriminatory imposition of tickets can be mitigated by descriptive representation (i.e.
-Black elected officials): The positive association between cities’ reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator [@Sances2017].
+Black elected officials): The positive association between cities' reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator [@Sances2017].
 
-Racial capitalist political economy imposes fiscal constraints regardless of city officials’ identities or intentions.
-In their study of fines and fees reliance in Chicago suburbs, Josh Pacewicz and John Robinson, III show how the racialization of municipal opportunity structures prevents majority-Black suburban governments from acquiring sufficient revenue from “good” sources such as sales taxes or property taxes, catalyzing a reliance on fines and fees to fund government services [@Pacewicz2020].
+Racial capitalist political economy imposes fiscal constraints regardless of city officials' identities or intentions.
+In their study of fines and fees reliance in Chicago suburbs, Josh Pacewicz and John Robinson, III show how the racialization of municipal opportunity structures prevents majority-Black suburban governments from acquiring sufficient revenue from "good" sources such as sales taxes or property taxes, catalyzing a reliance on fines and fees to fund government services [@Pacewicz2020].
 Pacewicz and Robinson III note that racialized municipal opportunity structures are tied to the political-historical processes of neoliberalism and fiscal austerity, an observation that aligns with recent scholarship detailing the origins of fees paid by incarcerated people [@Kirk2020].
@@
 Today, fines and fees primarily target Black Americans: traffic stops and searches disproportionately affect Black motorists nationwide [@Pierson2020], and a host of local analyses confirm the national finding [@Dunn2009; @Goncalves2020; @Mughan2020].
-In criminal court proceedings, Black defendants tend to face more severe monetary sanctions [@Edwards2020; @Harris2011], and a 2020 Federal Reserve survey found that five percent of white respondents reported “unpaid legal expenses, fines, or court costs,” whereas twelve percent of Black respondents reported such debt [@BoardofGovernorsoftheFederalReserveSystem2020].
+In criminal court proceedings, Black defendants tend to face more severe monetary sanctions [@Edwards2020; @Harris2011], and a 2020 Federal Reserve survey found that five percent of white respondents reported "unpaid legal expenses, fines, or court costs," whereas twelve percent of Black respondents reported such debt [@BoardofGovernorsoftheFederalReserveSystem2020].
 
@@
 One study of all U.S.
-city governments found that local fiscal stress was related to increased “revenue-generating arrests” (e.g.
+city governments found that local fiscal stress was related to increased "revenue-generating arrests" (e.g.
 arrests involving civil asset forfeiture) and that Black and Hispanic people were arrested at higher rates [@Makowsky2009].
@@
 Black Americans can therefore situate exploitative ticketing practices in a longer historical legacy of collective disparate treatment and violence at the hands of the state.
-We argue that Black voters’ recognition of discriminatory ticketing practices facilitates a “linked fate” political analysis that motivates voting behavior distinct from other forms of criminalization, such as criminal conviction or incarceration.
-We expect both ticketing and incarceration to spark a recognition of “a sense of injustice” among Black Americans, but we argue that ticketing should ultimately mobilize Black voters (unlike incarceration, which discourages Black voters more than whites [@White2019]).
+We argue that Black voters' recognition of discriminatory ticketing practices facilitates a "linked fate" political analysis that motivates voting behavior distinct from other forms of criminalization, such as criminal conviction or incarceration.
+We expect both ticketing and incarceration to spark a recognition of "a sense of injustice" among Black Americans, but we argue that ticketing should ultimately mobilize Black voters (unlike incarceration, which discourages Black voters more than whites [@White2019]).
 
 Ticketing produces substantively different experiences than being arrested or incarcerated.
-While tickets can lead to driver’s license suspensions or, in a smaller subset of cases, nonpayment incarceration, tickets are generally far less disruptive than criminal convictions and prison terms, and we argue that this difference should lead to different political behaviors.
-For example, one participant in @Lerman2014 who had served five years of probation after a criminal conviction reported, “I feel like if I contact a senator or governor, they’ll probably want to put me in jail and leave me as a troublemaker...
-That’s how I actually feel: ‘I better stay below the radar ’cause this guy’s tryin’ to start trouble’” [@Lerman2014, page 210].
+While tickets can lead to driver's license suspensions or, in a smaller subset of cases, nonpayment incarceration, tickets are generally far less disruptive than criminal convictions and prison terms, and we argue that this difference should lead to different political behaviors.
+For example, one participant in @Lerman2014 who had served five years of probation after a criminal conviction reported, "I feel like if I contact a senator or governor, they'll probably want to put me in jail and leave me as a troublemaker...
+That's how I actually feel: ‘I better stay below the radar 'cause this guy's tryin' to start trouble'" [@Lerman2014, page 210].
 While formerly incarcerated people or people who have experienced criminal legal supervision may avoid voting due to the same type of fear of state surveillance and control that motivates their avoidance of medical or educational institutions [@Brayne2014], we argue that being ticketed should not produce the same chilling effect---ticketing should not prompt Black people to use political withdrawal as a self-preservation strategy.
 
-Additionally, we argue that “policing for profit”---the experience of being ticketed while a municipality is palpably ramping up its fines and fees practices to collect revenue---is also substantively distinct from the experience of being arrested or incarcerated.
-In doing so, we extend Epp et al.’s theory of pretextual traffic stops politically socializing Black voters to the specific context of discriminatory police ticketing [@Epp2014].
+Additionally, we argue that "policing for profit"---the experience of being ticketed while a municipality is palpably ramping up its fines and fees practices to collect revenue---is also substantively distinct from the experience of being arrested or incarcerated.
+In doing so, we extend Epp et al.'s theory of pretextual traffic stops politically socializing Black voters to the specific context of discriminatory police ticketing [@Epp2014].
 Black Americans who experience disproportionate ticketing are likely aware that they are being targeted by police for reasons unrelated to traffic safety.
-One Buffalo, New York resident who is a plaintiff in a lawsuit regarding racist ticketing practices told a local newspaper in 2019: “In my mind, they weren’t balancing the budgets for Black lives, but with Black lives” [@McLeod2019].
+One Buffalo, New York resident who is a plaintiff in a lawsuit regarding racist ticketing practices told a local newspaper in 2019: "In my mind, they weren't balancing the budgets for Black lives, but with Black lives" [@McLeod2019].
 The city created a new traffic violations agency in 2015, spurring its yearly ticketing numbers to jump from around 32,000 to over 52,000.
 This financial aspect of ticketing should make it distinct from arrests and incarceration: much like the coercion of labor under the Black Codes, contemporary fines and fees practices are blatantly an effort to extract wealth from Black Americans.
-Although 20th century political rhetoric centered public safety as the mission of policing [CITE], exploitative ticketing practices cannot be reconciled with such rhetoric.
-In other words, to the extent that mass incarceration could be justified using narratives of “colorblind racism” (i.e., there’s a lot of crime happening in Black communities, so that’s why there’s more policing in those areas), racist ticketing practices do not enjoy the same rhetorical convenience.
+In other words, to the extent that mass incarceration could be justified using narratives of "colorblind racism" (i.e., high crime rates in Black communities results in more policing in those areas), racist ticketing practices do not enjoy the same rhetorical convenience.
+It may not be possible for revenue-motivated, racist ticketing to be reconciled with the idea that policing is primarily meant to improve public safety.
 
@@
 We expect a larger share of more affluent Black voters to be affected by ticketing than other forms of criminalization---arrests and incarceration are most common among individuals experiencing poverty [@Looney2018].
-Because perceptions of “linked fate” and related critiques of policing are even more salient among members of the Black middle class [@Dawson1995], we expect Black middle class voters to be mobilized by egregious ticketing practices.
+Because perceptions of "linked fate" and related critiques of policing are even more salient among members of the Black middle class [@Dawson1995], we expect Black middle class voters to be mobilized by egregious ticketing practices.
 In other words, we argue that ticketing should ensnare more Black voters who are more likely to politicize the issue.
@@
 One recent study found that census places that saw Black Lives Matter protests experienced a 15 to 20 percent decrease in police killings over the following five year period [@Campbell2021].
-It’s possible that Black Lives Matter facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis---the movement arose shortly after fines and fees became a more salient and widespread threat to Black Americans’ material security, and many early Black Lives Matter protests either occurred in municipalities with exploitative ticketing practices or directly followed traffic stops that escalated into police violence [@Holpuch2015; @LaFraniere2016].
+It's possible that Black Lives Matter facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis---the movement arose shortly after fines and fees became a more salient and widespread threat to Black Americans' material security, and many early Black Lives Matter protests either occurred in municipalities with exploitative ticketing practices or directly followed traffic stops that escalated into police violence [@Holpuch2015; @LaFraniere2016].
 
 Today, fines and fees disproportionately affect Black people, and Black political mobilization appears to mitigate some of the most egregious ticketing practices [@Sances2017].
-Accordingly, we expect that Black voters’ political behavior in response to police ticketing will be distinct from the political behavior of white voters, and further that ticketing should mobilize Black voter turnout in cities that have recently ramped up ticketing.
+As we have shown, contemporary fees and fines practices are just one iteration of a longer anti-Black project in the United States.
+Moreover, organizing in recent years by groups affiliated with the BLM movement have made this narrative easily accessible to citizens around the country.
+Based on the strength and accessibility of this narrative and the injustice framework proposed by @Walker2020a, we  expect that Black voters' political behavior in response to police ticketing will be distinct from the political behavior of white voters, and further that ticketing should mobilize Black voter turnout in cities that have recently ramped up ticketing.
 
@@
 We begin by turning to the American National Election Studies 2020 Time Series data (ANES).
-The ANES has been fielded in every presidential election year since 1948 and is among the most widely-used tools for understanding American’s political beliefs and behaviors, including their relationship with the criminal legal system [@Walker2020].
+The ANES has been fielded in every presidential election year since 1948 and is among the most widely-used tools for understanding American's political beliefs and behaviors, including their relationship with the criminal legal system [@Walker2020].
 It is weighted to be nationally representative of all American adults.
-In both 2016 and 2020, the ANES added new survey questions about respondent’s encounters with the police and the criminal legal system.
+In both 2016 and 2020, the ANES added new survey questions about respondent's encounters with the police and the criminal legal system.
 We focus in particular on two questions: *During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?*, and *Have you ever been arrested, or has that never happened to you?* We include the roughly 87 percent of respondents that answered both questions, giving us a sample size of 7,347 respondents, of whom just over 11% identified as Black.
@@
 We also test whether an arrest is associated in the 2020 ANES with a lower probability of voting as described in previous work.
-In addition to the respondent’s contact with the criminal legal system, we control for age; sex; income; party affiliation; and self-described ideology.
+In addition to the respondent's contact with the criminal legal system, we control for age; sex; income; education; party affiliation; self-described ideology; and reported 2016 turnout.
 Using the ANES, we test our first two hypotheses:
@@
 After an examination of the cross-sectional national survey data, we turn to our nationwide analysis of the relationship between municipal revenue raised from fees and fines, and turnout in the 2018 federal election.
-Our data come from two primary sources: the US Census Bureau’s Census of Governments Data (COG), and registered voter files from L2 Political.
+Our data come from two primary sources: the US Census Bureau's Census of Governments Data (COG), and registered voter files from L2 Political.
 
 **Census of Governments**: Every five years, the US Census Bureau collects data from governmental bodies around the country.
-We use two snapshots of the COG: one that covers the years 2008 -- 2012, and another that covers 2013 -- 2017.
-The COG asks municipalities to report how much revenue they collect from “penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation...
-and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).” We divide these amounts by the population to estimate the per-capita fees and fines revenue raised in each municipality.
+We use two waves of the COG: one that covers the years 2008 -- 2012, and another that covers 2013 -- 2017.
+The COG asks municipalities to report how much revenue they collect from "penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation...
+and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral)." We divide these amounts by the population to estimate the per-capita fees and fines revenue raised in each municipality.
 This data has been used as a proxy for the amount of tickets issued at the local level in scholarly research [see, for instance, @Goldstein2020; @Sances2017].
@@
 In Washington, DC, and every state in the country (with the exception of North Dakota) voters are required to register to vote prior to participating.
-These files are considered public record, and in most states contain information about each voter’s age, residential address, political affiliation, and participation history.
+These files are considered public record, and in most states contain information about each voter's age, residential address, political affiliation, and participation history.
 L2 collects voter files from around the country and merges them with proprietary data that estimates other voter- and household-level characteristics such as race and education.
-L2 also geocodes voters’ residential addresses.
+L2 also geocodes voters' residential addresses.
 
-We merge the geocoded voter files with “place” and “county subdivision” shapefiles published by the US Census Bureau.
+We merge the geocoded voter files with "place" and "county subdivision" shapefiles published by the US Census Bureau.
+These divisions correspond to the governmental bodies who report to the COG.
 By aggregating individual-level records to the municipal level, we are able to estimate the number of registered voters and the number of ballots cast in every city in the country.
@@
 While in a few states race is self-reported by voters, race is in most cases modeled by L2 using first, middle, and last name, as well as Census block demographic information.
-Although this is a commonly used way to determine voters’ races [@Imai2016], it is subject to some error.
+Although this is a commonly used way to determine voters' races [@Imai2016], it is subject to some error.
 We assume, however, that after controlling for other municipality-level characteristics, the errors in these predictions will be uncorrelated with fees and fines collections.
 Put differently, although we acknowledge that these estimates are imprecise, we expect that these errors are effectively random.
-Further, as we show in the Supplemental Information, the estimated Black share of the electorate tracks very closely with the share of the citizen voting age population that is non-Hispanic Black.
+As we show in the Supplemental Information, the estimated Black share of the electorate tracks very closely with the share of the citizen voting age population that is non-Hispanic Black.
 After accounting for state-level voter registration differentials, the mean absolute error between these two measures is 2.4% and is unrelated to per-capita fines and fees after controlling for other covariates (*p* = 0.92).
@@
 
-We calculate turnout by dividing the number of ballots cast according to L2 by the 5-year estimate of each municipality’s citizen voting-age population (CVAP) from the US Census Bureau.
+We calculate turnout by dividing the number of ballots cast according to L2 by the 5-year estimate of each municipality's citizen voting-age population (CVAP) from the US Census Bureau.
 These estimates are available for individual racial groups.
@@
 
-**Estimation Strategy**: We begin by merging each municipality’s fees and fines per capita (that is, dollars per resident) from the 2012 COG to its turnout from the 2014 midterm election, and the 2017 COG to its 2018 turnout.
+**Estimation Strategy**: We begin by merging each municipality's fees and fines per capita (that is, dollars per resident) from the 2012 COG to its turnout from the 2014 midterm election, and the 2017 COG to its 2018 turnout.
 Because this measure is highly right-skewed, we use the natural log of fees and fines per capita (plus 1, to account for municipalities that collected no fees and fines).
-We also control for other municipal and state characteristics: racial composition, population density, median income, collegiate education, median age, share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality’s revenue that comes from the state or federal government in the 2012 and 2017 COGs.
+We also control for other municipal and state characteristics: racial composition, population density, median income, collegiate education, median age, share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality's revenue that comes from the state or federal government in the 2012 and 2017 COGs.
 We retain the 8,954 municipalities whose data is reported to the COG in both 2012 and 2017 and meet the other criteria noted above.
@@
 We run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
-Our national two-way fixed effect model allows us to test our first two hypotheses:
+Our national two-way fixed effect model allows us to test our next hypotheses:
 
-*Hypothesis 3*: Increased reliance on fines and fees revenue at the city level reduces voter turnout at the city level.
+*Hypothesis 3*: Increased reliance on fines and fees revenue at the city level reduces voter turnout at the city level among non-Black residents.
 
-*Hypothesis 4*: The effect of the city-level relationship between fines and voter turnout is stronger for Black voters, given the historical and explicit racial injustice narratives used to explain these practices.
+*Hypothesis 4*: Increased reliance on fines and fees revenue at the city level increases voter turnout at the city level among Black residents.
 
@@
 
-Our national, cross-sectional analyses offer novel insight into the political socialization of low-level police contact.
+Our national analyses offer novel insight into the political socialization of low-level police contact.
 They cannot, however, directly observe the causal mechanism we argue is at play: namely, that direct contact with the criminal legal system influences turnout.
@@
 Increased fees and fines could be correlated with increased policing in general, for instance.
-We are also unable to isolate the individual-level effect of being ticketed on turnout using this setup.
+Similarly, respondents in the ANES who report contact with a police stop may differ from those who report no such contact, even after controlling for available characteristics in the survey responses.
 
-Additionally, the national analyses cannot distinguish personal contact from proximal contact (“having a loved one who is a custodial citizen without yourself having had contact” [@Walker2017]).
+Additionally, the national analyses cannot distinguish personal contact from proximal contact ("having a loved one who is a custodial citizen without yourself having had contact" [@Walker2017]).
 Because existing research investigating the effect of proximal contact has produced mixed results [@Burch2014; @Lee2014; @Sugie2015; @White2019; @Walker2017; @Walker2020], we are unable to prove that personal police contact is the only dynamic driving effects observed in our national analysis.
@@
 This investigation catalyzed a U.S.
-Department of Justice investigation and report, requested by Tampa’s mayor and police chief.
+Department of Justice investigation and report, requested by Tampa's mayor and police chief.
 In other words, there is strong evidence suggesting both racist targeting of tickets and potential publicity to catalyze distinct Black voter responses to the abusive behavior during the same time frame as our national analysis.
-Ticketing has also been expressly politicized in Tampa: Jane Castor, who was elected mayor in 2019, was Tampa’s police chief until 2015 and publicly defended her department’s disproportionate ticketing of Black bicyclists before retracting her defense ahead of her mayoral campaign [@Carlton2018].
-Her opponent, banker and philanthropist David Straz, campaigned against red-light cameras and focused his outreach in Tampa’s Black communities [@Frago2019].
+Ticketing has also been expressly politicized in Tampa: Jane Castor, who was elected mayor in 2019, was Tampa's police chief until 2015 and publicly defended her department's disproportionate ticketing of Black bicyclists before retracting her defense ahead of her mayoral campaign [@Carlton2018].
+Her opponent, banker and philanthropist David Straz, campaigned against red-light cameras and focused his outreach in Tampa's Black communities [@Frago2019].
 
@@
 
-To identify ticketed voters, we match the first and last names and dates of birth from court data against the Hillsborough County registered voter file.
+To identify ticketed voters, we match the first and last names and dates of birth from the stop data against the Hillsborough County registered voter file.
 Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status [see @Nyhan2017].
@@
 Unique voter identification numbers allow us to avoid double-counting voters who are registered in multiple snapshots.
-We retain each voter’s earliest record, and geocode voters to their home census block groups.
+We retain each voter's earliest record, and geocode voters to their home census block groups.
 Because we argue that police contact is the driving force behind any turnout effect, we remove tickets issued by red-light cameras.
@@
 To improve the quality of the match between the two datasets, we remove all punctuation from all names and convert all names to lower-case.
-This means that a “Jonathan O’Shea” in one file would match a “jonathan oshea” in the other.
+This means that a "Jonathan O'Shea" in one file would match a "jonathan oshea" in the other.
 @Meredith2014 develops a test for assessing the prevalence of false-positives in administrative record matching.
@@
 By matching the police stop and voter records, we identify all voters who were ticketed between the 2012 and 2020 general elections (voters stopped between 2018 and 2020 elections serve only as controls).
-Voters are considered “treated” in the general election following their ticket.
+Voters are considered "treated" in the general election following their ticket.
 Treated voters are then matched to a control voter using a nearest-neighbor approach, with a genetic algorithm used to determine the best weight for each characteristic [@Sekhon2011].
@@
 It is important to note that our overall turnout effects are robust to much stricter assumptions.
-In the Supplementary Information we demonstrate that our primary reported results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
+In the Supplementary Information we demonstrate that our overall turnout results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
 
@@
 \beta_3Treated_{i}\times Post Treatment_{t} + \\
-\delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
+\beta_4Year_{t} + \delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
 \end{gather}
@@
 In the equation, *$\beta$~1~Treated~i~* measures the historical difference between treated voters and their controls.
-*$\beta$~2~Post Treatment~t~* measures whether turnout increased for controls in the first election following the treated voter’s stop, while *$\beta$~3~Treated~i~ × Post Treatment~t~* tests whether turnout changed differently for treated voters than their controls in the election following their police stop.
+*$\beta$~2~Post Treatment~t~* measures whether turnout increased for controls in the first election following the treated voter's stop, while *$\beta$~3~Treated~i~ × Post Treatment~t~* tests whether turnout changed differently for treated voters than their controls in the election following their police stop.
 *$\beta$~3~*, then, will capture the causal effect of a police stop on voter turnout.
-Finally, the matrix *$\delta$Z~i~* contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
+*$\beta$~4~Year~t~* captures year fixed-effects depending on the timing of the police stop, and the matrix *$\delta$Z~i~* contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
 Equation 1 allows us to test Hypothesis 5:
 
-*Hypothesis 5*: Being ticketed reduces an individual’s likelihood of turning out in the subsequent election.
+*Hypothesis 5*: Being ticketed reduces an individual's likelihood of turning out in the subsequent election.
 
@@
 \beta_3Treated_{i}\times Post Treatment_{t} + \beta_4Treated_{i}\times Post Treatment_{t}\times Black_{i} +\\
-\delta{Y}_{i} + \delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
+\beta_5Year_{t} + \delta{Y}_{i} + \delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
 \end{gather}
@@
 
-*Hypothesis 6*: The effect of being ticketed on an individual’s voter turnout is less negative / more positive if that individual is Black.
+*Hypothesis 6*: The effect of being ticketed on an individual's voter turnout is less negative / more positive if that individual is Black.
 
@@
 As discussed above, we begin by testing the relationship between police stops and turnout in the 2020 election, and then move to testing the relationship between fees and fines at the municipal level.
-While both tests give us insight into the political ramifications of low-level police contact, their cross-sectional nature cannot establish causality.
-To investigate causality, we also examine whether the turnout of individuals stopped by the police before an election was different than those stopped after the election in Hillsborough County, Florida.
+We also examine whether the turnout of individuals stopped by the police before an election was different than those stopped after the election in Hillsborough County, Florida.
 
@@
 We also ask whether this relationship was different for Black and non-Black respondents.
-We also use the ANES data to reconfirm prior literature demonstrating that higher-level contact with the criminal legal system is associated with lower turnout, as these relationships could have changed in the aftermath of the widespread protests following the police killing of George Floyd in 2020.
+Finally, we use the ANES data to reconfirm prior literature demonstrating that higher-level contact with the criminal legal system is associated with lower turnout, as these relationships could have changed in the aftermath of the widespread protests following the police murder of George Floyd in 2020.
 
@@
 In Figure \ref{fig:anes} we present the results of our econometric models.
-In the left-hand panel, we show the predicted turnout of respondents who answered “yes” or “no” to the question *During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?* The right-hand panel, meanwhile, plots these relationships for respondents who answered “yes” or “no” to the question *Have you ever been arrested, or has that never happened to you?*.
-These are the predicted probabilities after controlling for respondents’ race / ethnicity; age; party; ideology; income; and education.
+In the left-hand panel, we show the predicted turnout of respondents who answered "yes" or "no" to the question *During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?* The right-hand panel, meanwhile, plots these relationships for respondents who answered "yes" or "no" to the question *Have you ever been arrested, or has that never happened to you?*.
+These are the predicted probabilities after controlling for respondents' race / ethnicity; age; party; ideology; income; 2016 turnout; and education.
 The full regression table can be found in the Supplementary Information..
@@
 ```
-Figure \ref{fig:anes} demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (*p* = 0.006).
-The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (*p* = 0.52).
+Figure \ref{fig:anes} demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (*p* = 0.005).
+The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (*p* = 0.27).
 Importantly, this effect is not a remnant of a white--nonwhite divide.
@@
 The second panel of Figure \ref{fig:anes} shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
-Importantly, the interaction between arrest status and the respondent’s race was not statistically significant.
+Importantly, the interaction between arrest status and the respondent's race was not statistically significant.
 In other words, although police stops seem to be uniquely mobilizing for Black Americans, we fail to uncover evidence that arrests differentially structured subsequent Black- and non-Black turnout.
@@
 
-Before testing the causal effect of fees and fines collections, we begin with a cross-sectional analysis of the relationship between fees and fines and turnout using ordinary least squares.
+Before testing the causal effect of fees and fines collections on turnout, we begin with a cross-sectional analysis of the relationship using ordinary least squares.
 Here, we regress municipality-level turnout in 2018 against fees and fines collections as reported in the 2017 COG, as well as a number of other covariates.
@@
 
-As Figure \ref{fig:mef-2018} makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 2.5 percentage points over the interdecile range, after controlling for the other covariates.
+As Figure \ref{fig:mef-2018} makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 1.5 percentage points over the interdecile range, after controlling for the other covariates.
 The opposite is true for Black voters: over the same range, Black turnout *increases* by roughly 2.4 percentage points.
@@
 The results of these models can be found in Table \ref{tab:twfe}.
+The average municipality included in this analysis raised $2.17 in fees and fines per resident in 2012, and the average municipality increased or decreased this per-capita figure by $0.47 between 2012 and 2017.
+Just over 10% of municipalities raised no revenue from fees and fines in either year.
 
@@
 
-The results of the two-way fixed effects model are different than what we saw in the 2018 cross-sectional approach; namely, while Table \ref{tab:twfe} indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not significantly impact Black turnout.
-The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.06 percentage points.
-
-In Table \ref{tab:coarser}, we re-estimate the model from Table \ref{tab:twfe} but coarsen the data.
-Here, the dependent variable of interest is binary: we test whether turnout changed for municipalities who increased their per-capita fees and fines collections differently than municipalities where collections stayed the same or decreased.
-Municipalities that increased their per-capita fees and fines are considered “treated.”
-
-\begin{singlespace}
-\input{"../temp/coarser_reg_clean.tex"}
-\end{singlespace}
-
-The coefficient on *Treated × 2018* indicates that non-Black turnout dropped by about 0.5 percentage points in municipalities where fees and fines collections increased, relative to other municipalities.
-While this coefficient is slightly *positive* for Black voters, it is not statistically significantly different from 0.
-In other words, both Tables \ref{tab:twfe} and \ref{tab:coarser} indicate that increased fees and fines collections decrease non-Black turnout but have no impact on Black turnout.
+The results of the two-way fixed effects model are different than what we saw in the 2018 cross-sectional approach; namely, Table \ref{tab:twfe} indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not significantly impact Black turnout.
+The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.04 percentage points.
 
@@
 
-Thus far, we have shown that voter turnout decreased in municipalities that increased fines and fees collections.
+Thus far, we have shown that Black individuals with police contact reported participating at higher rates in the 2020 election than those without such contact.
+We also demonstrated that voter turnout decreases in municipalities that increased fines and fees collections.
 We argue that this relationship is causal: increased fees and fines collections means that more residents have direct interactions with the criminal legal system.
 Based on prior literature, we assume there are indirect effects as well, as more residents know a family or community member who has been ticketed.
-While the national analysis gives us great breadth and an increased understanding of how this plays out across the country, municipal-level data leaves us unable to directly observe the causal mechanisms at play.
+While the national analyses give us great breadth and an increased understanding of how this plays out across the country, they leave us unable to directly observe the causal mechanisms at play.
 
@@
 
-It is worth noting that voters who were stopped between 2012 and 2018 were far more likely to be Black and male than the general electorate, and live in Census block groups with moderately lower incomes.
-Unsurprisingly, they were also stopped at higher rates in the pre-treatment period than those never stopped between 2012 and 2018.
+It is worth noting that voters who were stopped between 2012 and 2020 were far more likely to be Black and male than the general electorate, and live in Census block groups with moderately lower incomes.
 
@@
 In Figure \ref{fig:did1}, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped.
-The first election following a treated voter’s stop is denoted as *t = 0* while the years in which *t* is less than zero are the periods prior to the stop.
+The first election following a treated voter's stop is denoted as *t = 0* while the years in which *t* is less than zero are the periods prior to the stop.
 This means that for someone stopped in 2013 (and their controls), *t* is 0 in 2014, while *t* is equal to 0 in 2018 for an individual stopped between the 2016 and 2018 elections.
@@
 First, we can see that for both Black and non-Black voters the parallel trends assumption is satisfied.
-Of course, because we matched treated and control voters based on turnout prior to the ticket, this is unsurprising.
+Because we matched treated and control voters based on turnout prior to the ticket, this is by design.
 
 Table \ref{tab:dind-table} formalizes Figure \ref{fig:did1} into an ordinary least squares regression.
-Model 1 shows our overall causal effect, while Model 2 allows for the possibility that a ticket differentially mobilizes Black voters.
+Models 1 and 2 show our overall causal effect, while models 3 and 4 allow for the possibility that a ticket differentially mobilizes Black voters.
+In models 1 and 3, we include only the treatment, timing, and race dummies, while the full set of covariates used for the matching procedure are included in models 2 and 4.
 The coefficients of note are *Treated × Post Treatment* and *Treated × Post Treatment × Black*.
@@
 In models 1 and 2, the estimated overall treatment effect is -1.5 percentage points.
-In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---nonBlack turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
+In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---non-Black turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
 Although the treatment effect is still substantively quite large for Black individuals, the pattern follows our national analysis.
@@
 
-We first used survey data collected in the American National Election Studies 2016 and 2020 datasets to show how, unlike arrests, ticketing can mobilize Black voters.
-We found that Black people who reported personal or proximal police contact with a police stop in the last 12 months were 0.5 pp more likely to vote compared to Black people who did not report such contact.
-Non-Black respondents demonstrated no statistically significant result for police stops.
-Meanwhile, both Black and non-Black people who had been arrested at any point were less likely to vote, and we did not find significant differences between racial groups’ behaviors in response to arrests.
+Given how widespread police stops are and their relationship to racial injustice, their political implications demand close study.
+Accordingly, we investigate this question from a variety of perspectives, using multiple data sources and empirical approaches.
+What we find complicates our understanding of how lower-level police contact affects political participation.
+On one hand, the national survey data and cross-sectional municipal-level analysis indicate that police contact is associated with higher turnout for Black Americans, and either unrelated or negatively related to turnout for others.
+Our causal models, on the other hand, tell a slightly different story---namely, they fail to uncover mobilizing effects for Black Americans.
+Nevertheless, our causal models *do* indicate that police stops are less demobilizing for Black individuals than for others.
+In this sense, our results all point in the same direction.
+Based on these three independent approaches, we conclude that the political consequences of police stops are unique for Black Americans---and that they are less demobilizing for Black Americans than others.
 
-Next, we used a two-way fixed effects model to estimate the effect of increased fines and fees reliance at the city level on aggregate voter turnout in federal elections.
-We found that each 10 percent increase in fines and fees collected per resident is associated with a voter turnout decrease of about 0.06 percentage points, with no significant impact on Black turnout in particular---in other words, the demobilizing effect of ticketing increases at the city level is largely driven by non-Black voters.
+The difference between the cross-sectional and two-way fixed effects models using the municipality-level data is somewhat surprising. There are a few potential explanations for this mismatch.
 
-In order to directly observe the causal mechanism, we then conducted an individual-level analysis of ticketing and voting behavior in Hillsborough County, Florida.
-Using a difference-in-differences design, we found that individuals who were ticketed in the 90-day period preceding a federal election were 1.7 percentage points less likely to vote compared to individuals who were ticketed following the election.
-The effect was smaller for Black individuals (1 percentage point less likely), which is consistent with our hypothesis that Black political responses to ticketing should be distinct from whites (and more mobilized by comparison).
+First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes in the two-way fixed effects models are smaller or not statistically significant.
+Along a similar vein, it's possible that the effect size for Black voters in the city-level analysis is influenced by higher-intensity forms of criminal legal contact, such as arrest and incarceration.
+The bulk of existing literature suggests that incarceration discourages political participation, and it's not unreasonable to assume that cities that ramp up ticketing of Black residents also ramp up arrest and incarceration of Black residents.
+If these phenomena coincide, that could explain why the city-level analysis produced no statistically significant effect for Black voters---the personally mobilizing effect of ticketing could be counterbalanced by the proximal chilling effect of incarceration, and because the city-level analysis is not as temporally sensitive, it's more difficult to isolate the effect of ticketing.
+We were unable to incorporate a measure of local incarceration trends due to a lack of consistent data nationwide.
 
-We were somewhat surprised by the differences that arose between our two sets of findings---our city-level analysis using a two-way fixed effects model did not produce statistically significant results for Black voters.
-We think there are a few potential explanations for this mismatch.
+Moreover, Sances and You [-@Sances2017, page 1091]---the paper that originally detailed the relationship between fees and fines collections and municipalities' racial composition using the Census of Governments data---specifically notes that they did not exploit the panel setup of the COG because of "little variation within a city in terms of revenues from fines." Instead, they present only the results of a cross-sectional study.
+Here, we present both the cross-sectional and panel results, acknowledging that each have limitations but that, taken together, they shed light on the unique politicization of fees and fines for Black Americans.
 
-First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes are smaller or not statistically significant.
-Along a similar vein, it’s possible that the effect size for Black voters in the city-level analysis is affected by higher-intensity forms of criminal legal contact, such as arrest and incarceration.
-The bulk of existing literature suggests that incarceration discourages political participation, and it’s not unreasonable to assume that cities that ramp up ticketing of Black residents also ramp up arrest and incarceration of Black residents.
-If these phenomena coincide, that could explain why the city-level analysis produced no statistically significant effect for Black voters---the personally mobilizing effect of ticketing could be counterbalanced by the proximal chilling effect of incarceration, and because the city-level analysis is not as temporally sensitive, it’s more difficult to isolate the effect of ticketing.
-
-That said, @Sances2017 specifically note that they didn't exploit the panel setup of the COG because of little variation between the 2007-2012 COG to the 2012-2017 one, and so they just stuck to cross sectional.
-The positive effect for Black turnout in Figure 2 is consistent with our Tampa analysis and doesn't totally contradict the TWFE.
+Our individual-level analysis based on Hillsborough County, Florida, advances our understanding of this dynamic while raising new questions.
+On the one hand, the causal results are highly robust, and the ticketing data allows us to identify the treatment fairly precisely.
+On the other hand, these are the only results in which a police stop are associated with a *decrease* in turnout for Black individuals.
+This may be because this analysis tests the impact of direct contact with the police, rather than direct *or* proximal contact, as the ANES questions do.
+It may be because we can isolate the effect of a police stop from other, broader changes that may be correlated with increased fees and fines revenue in the municipal-level data.
+Or it may point to unique political circumstances surrounding race, policing, and political participation in Hillsborough County.
+We look forward to future scholarship that replicates and extends these Hillsborough County results.
+Nevertheless, that police stops are less demobilizing for Black Floridians in Hillsborough County---an effect that does not extend to other nonwhite residents---provides support for our general thesis that the political interpretation of these contacts with the criminal legal system are unique for Black Americans.
 
@@
 
-**Limitations**: Because our individual-level analysis is limited to Hillsborough County, we don’t have a good idea of whether the city-level revenue reliance trend interacts with the individual experience of being ticketed.
+In this sense, our analysis points to a political contestation of criminal legal policy, a phenomenon that aligns with dozens of recent campaigns to reform local fines and fees practices (or abolish them entirely).^[See https://finesandfeesjusticecenter.org/clearinghouse.]  We know that fines and fees result from political economy (i.e.
+austerity at the federal level), but our analysis suggests that this is a "two way street" wherein people who are harmed by policing practices are politically socialized into resistance.
+
+**Limitations**: Because our individual-level analysis is limited to Hillsborough County, we don't have a good sense of how the city-level revenue reliance trend interacts with the individual experience of being ticketed.
 Is ticketing more politically mobilizing for Black voters in cities that are palpably dialing up their revenue collection efforts?
-Future research could test this hypothesis in cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.
+Future research could test this hypothesis at the individual level within cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.
 
-Additionally, in our analysis of Hillsborough County voters, we don’t look at people who weren’t registered to vote in 2018.
+Additionally, in our analysis of Hillsborough County voters, we don't look at people who weren't registered to vote in 2018.
 This means that there could be some proportion of ticketed Black motorists who are now less likely to register to vote in the first place, for example.
-In other words the mobilization effect in our findings only applies to people who were registered to vote---we are unable to make claims about whether being ticketed makes an individual more likely to register to vote.
+In other words the mobilization effect (or decreased demobilization effect) in our findings only applies to people who were registered to vote---we are unable to make claims about whether being ticketed makes an individual more likely to register to vote.
 
-**Future research**: Future work should explore whether ticketing can be mobilizing for Black individuals under circumstances.
-We were unable to test whether what we're observing is just *decreased* demobilization, or whether some subgroups of the Black population were mobilized while others were demobilized.
+**Future research**: This work looks at the difference between the political behavior of Black and non-Black Americans.
+Future work should explore variation *within* the Black community.
+When is this sort of contact mobilizing?
+For whom?
+Can organizers build on this potential for broad-based political action?
+We were unable to test whether what we're observing is simply *decreased* demobilization, or whether some subgroups of the Black population were mobilized while others were demobilized.
 In other words, it could be the case that ticketing is demobilizing for all voters, but there is a subset of Black voters who are *mobilized* by this, though they aren't a large enough group to counteract the demobilization of other Black people.
 
-Unlike previous studies using survey data, we are unable to tell whether individuals in Tampa have non-ticketing criminal legal exposure.
+Also, unlike previous studies using survey data, we are unable to tell whether treated individuals in Tampa have non-ticketing criminal legal exposure.
 Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.
 
-<!--  [Laniyonu] - [he writes that block groups with higher Black pop and higher SQF density voted at higher rates for Thompson, the candidate who pledged not to implement SQF reform, but who was Black.
-The descriptive representation from Sances2017 kind of covers for this, tactically speaking - electing Black politicians should reduce fines and fees abuses.
-But in Tampa, the current mayor, Jane Castor, was the police chief until 2015 --- which overlaps with the treatment period in our analysis.
-One voter told the Tampa Bay Times that he voted against Castor as “payback” for the racist ticketing practices she oversaw, and the article notes that her opponent won five majority-Black precincts [@Frago2019].
-In 2015, Castor even released a statement as police chief supporting the racist ticketing, insisting that “Many individuals receiving bike citations are involved in criminal activity.” -->
+Although we have generated new evidence suggesting that police stops and related exploitative ticketing practices may mobilize Black voters, we emphasize that this finding does not redeem or justify such police practices.
+Black Americans already suffer from disproportionate police contact and the racial wealth gap, and racist revenue-motivated ticketing only increases the burden on Black communities nationwide.
+Policymakers should work to ensure that Black Americans no longer have to struggle to enjoy the same political power as whites---to that end, the current trend of voting rights restriction policies across the country is especially pernicious.
+Even if Black Americans understand the ballot box as one tool they can use to limit the state's power to exploit and harm them, policymakers should still feel an obligation to support voting rights and stop disproportionate ticketing in Black communities.
 

### 2021-05-07 markdown/draft_paper.tex
FINAL FIRST DRAFT!!

@@
 \author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
-\date{May 01, 2021}
+\date{May 07, 2021}
 
@@
 We use three approaches to answer this question: national survey data, a city-level analysis using Census of Governments data and the national voter file, and individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019.
-The survey data show that Black people who report that they were recently stopped by police are more likely to vote compared to those who were not stopped.
-Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.6 percentage point turnout decrease but was not associated with Black turnout.
+The survey data show that Black people who report that they or a family member were recently stopped by police are more likely to vote than those who reported no such contact.
+Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.04 percentage point turnout decrease but was not associated with Black turnout.
 In Tampa, Florida, we estimate that being ticketed decreases an individual's likelihood of voting in federal elections by 1.7 percentage points, but depressive effects are smaller for Black residents.
@@
 Such work has largely focused on the effects of highly disruptive contact with the criminal legal system such as incarceration and felony convictions (\protect\hyperlink{ref-Burch2014}{Burch 2014}; \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}).
-This paper is the first to explicitly theorize how local ticketing practices shape the political socialization of ticketed individuals.
+Building on recent theoretical work from \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020a}) and an analysis of the historical context of fees and fines collections in the United States, this paper is the first to explicitly theorize how local ticketing practices shape the political socialization of ticketed individuals.
 Additionally, our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
-The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures political participation.
+
+In addition to our theoretical contribution, the use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures political participation.
 Past work looking at the individual-level effects of low-level contact has relied entirely on survey or qualitative data (e.g.
@@
 Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to police ticketing.
-The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of the 232,568 individuals ticketed over a 6 year period---a far larger pool than even the most robust surveys.
-
-Before turning to the administrative data, we begin with a novel analysis of 2016 and 2020 national survey data regarding voters' experience with police stops and arrests.
+The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of the quarter-million individuals ticketed over a 6 year period---a far larger pool than even the most robust surveys.
+
+Before turning to the administrative data, we begin with a novel analysis of 2020 national survey data regarding voters' experience with police stops.
 We find that Black respondents who reported personal or proximal experience with police stops in the last 12 months are more likely to vote than Black people who did not, while we find no statistically significant relationship between stops and voting among non-Black respondents.
 
-Next, we join fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for each municipality in the country.
+Next, we join fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for thousands of municipalities around the country.
 While we find that increased fees and fines likely cause lower turnout among non-Black Americans, we find no effect of fees and fines on Black turnout.
@@
 This financial aspect of ticketing should make it distinct from arrests and incarceration: much like the coercion of labor under the Black Codes, contemporary fines and fees practices are blatantly an effort to extract wealth from Black Americans.
-Although 20th century political rhetoric centered public safety as the mission of policing {[}CITE{]}, exploitative ticketing practices cannot be reconciled with such rhetoric.
-In other words, to the extent that mass incarceration could be justified using narratives of ``colorblind racism'' (i.e., there's a lot of crime happening in Black communities, so that's why there's more policing in those areas), racist ticketing practices do not enjoy the same rhetorical convenience.
+In other words, to the extent that mass incarceration could be justified using narratives of ``colorblind racism'' (i.e., high crime rates in Black communities results in more policing in those areas), racist ticketing practices do not enjoy the same rhetorical convenience.
+It may not be possible for revenue-motivated, racist ticketing to be reconciled with the idea that policing is primarily meant to improve public safety.
 
@@
 Today, fines and fees disproportionately affect Black people, and Black political mobilization appears to mitigate some of the most egregious ticketing practices (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
-Accordingly, we expect that Black voters' political behavior in response to police ticketing will be distinct from the political behavior of white voters, and further that ticketing should mobilize Black voter turnout in cities that have recently ramped up ticketing.
+As we have shown, contemporary fees and fines practices are just one iteration of a longer anti-Black project in the United States.
+Moreover, organizing in recent years by groups affiliated with the BLM movement have made this narrative easily accessible to citizens around the country.
+Based on the strength and accessibility of this narrative and the injustice framework proposed by \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020a}), we expect that Black voters' political behavior in response to police ticketing will be distinct from the political behavior of white voters, and further that ticketing should mobilize Black voter turnout in cities that have recently ramped up ticketing.
 
@@
 We also test whether an arrest is associated in the 2020 ANES with a lower probability of voting as described in previous work.
-In addition to the respondent's contact with the criminal legal system, we control for age; sex; income; party affiliation; and self-described ideology.
+In addition to the respondent's contact with the criminal legal system, we control for age; sex; income; education; party affiliation; self-described ideology; and reported 2016 turnout.
 Using the ANES, we test our first two hypotheses:
@@
 \textbf{Census of Governments}: Every five years, the US Census Bureau collects data from governmental bodies around the country.
-We use two snapshots of the COG: one that covers the years 2008 -- 2012, and another that covers 2013 -- 2017.
+We use two waves of the COG: one that covers the years 2008 -- 2012, and another that covers 2013 -- 2017.
 The COG asks municipalities to report how much revenue they collect from ``penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation\ldots{} and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).'' We divide these amounts by the population to estimate the per-capita fees and fines revenue raised in each municipality.
@@
 We merge the geocoded voter files with ``place'' and ``county subdivision'' shapefiles published by the US Census Bureau.
+These divisions correspond to the governmental bodies who report to the COG.
 By aggregating individual-level records to the municipal level, we are able to estimate the number of registered voters and the number of ballots cast in every city in the country.
@@
 While in a few states race is self-reported by voters, race is in most cases modeled by L2 using first, middle, and last name, as well as Census block demographic information.
-Although this is a commonly used way to determine voters' races (\protect\hyperlink{ref-Imai2016}{Imai and Khanna 2016/ed}), it is subject to some error.
+Although this is a commonly used way to determine voters' races (\protect\hyperlink{ref-Imai2016}{Imai and Khanna 2016}), it is subject to some error.
 We assume, however, that after controlling for other municipality-level characteristics, the errors in these predictions will be uncorrelated with fees and fines collections.
 Put differently, although we acknowledge that these estimates are imprecise, we expect that these errors are effectively random.
-Further, as we show in the Supplemental Information, the estimated Black share of the electorate tracks very closely with the share of the citizen voting age population that is non-Hispanic Black.
+As we show in the Supplemental Information, the estimated Black share of the electorate tracks very closely with the share of the citizen voting age population that is non-Hispanic Black.
 After accounting for state-level voter registration differentials, the mean absolute error between these two measures is 2.4\% and is unrelated to per-capita fines and fees after controlling for other covariates (\emph{p} = 0.92).
@@
 We run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
-Our national two-way fixed effect model allows us to test our first two hypotheses:
-
-\emph{Hypothesis 3}: Increased reliance on fines and fees revenue at the city level reduces voter turnout at the city level.
-
-\emph{Hypothesis 4}: The effect of the city-level relationship between fines and voter turnout is stronger for Black voters, given the historical and explicit racial injustice narratives used to explain these practices.
+Our national two-way fixed effect model allows us to test our next hypotheses:
+
+\emph{Hypothesis 3}: Increased reliance on fines and fees revenue at the city level reduces voter turnout at the city level among non-Black residents.
+
+\emph{Hypothesis 4}: Increased reliance on fines and fees revenue at the city level increases voter turnout at the city level among Black residents.
 
@@
 Increased fees and fines could be correlated with increased policing in general, for instance.
-We are also unable to isolate the individual-level effect of being ticketed on turnout using this setup.
+Similarly, respondents in the ANES who report contact with a police stop may differ from those who report no such contact, even after controlling for available characteristics in the survey responses.
 
@@
 
-To identify ticketed voters, we match the first and last names and dates of birth from court data against the Hillsborough County registered voter file.
+To identify ticketed voters, we match the first and last names and dates of birth from the stop data against the Hillsborough County registered voter file.
 Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status (see \protect\hyperlink{ref-Nyhan2017}{Nyhan, Skovron, and Titiunik 2017}).
@@
 \emph{\(\beta\)\textsubscript{3}}, then, will capture the causal effect of a police stop on voter turnout.
-Finally, the matrix \emph{\(\delta\)Z\textsubscript{i}} contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
+\emph{\(\beta\)\textsubscript{4}Year\textsubscript{t}} captures year fixed-effects depending on the timing of the police stop, and the matrix \emph{\(\delta\)Z\textsubscript{i}} contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
 Equation 1 allows us to test Hypothesis 5:
@@
 In the left-hand panel, we show the predicted turnout of respondents who answered ``yes'' or ``no'' to the question \emph{During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?} The right-hand panel, meanwhile, plots these relationships for respondents who answered ``yes'' or ``no'' to the question \emph{Have you ever been arrested, or has that never happened to you?}.
-These are the predicted probabilities after controlling for respondents' race / ethnicity; age; party; ideology; income; and education.
+These are the predicted probabilities after controlling for respondents' race / ethnicity; age; party; ideology; income; 2016 turnout; and education.
 The full regression table can be found in the Supplementary Information..
@@
 
-Figure \ref{fig:anes} demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (\emph{p} = 0.006).
-The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (\emph{p} = 0.52).
+Figure \ref{fig:anes} demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (\emph{p} = 0.005).
+The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (\emph{p} = 0.27).
 Importantly, this effect is not a remnant of a white--nonwhite divide.
@@
 
-As Figure \ref{fig:mef-2018} makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 2.5 percentage points over the interdecile range, after controlling for the other covariates.
+As Figure \ref{fig:mef-2018} makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 1.5 percentage points over the interdecile range, after controlling for the other covariates.
 The opposite is true for Black voters: over the same range, Black turnout \emph{increases} by roughly 2.4 percentage points.
@@
 The results of these models can be found in Table \ref{tab:twfe}.
+The average municipality included in this analysis raised \$2.17 in fees and fines per resident in 2012, and the average municipality increased or decreased this per-capita figure by \$0.47 between 2012 and 2017.
+Just over 10\% of municipalities raised no revenue from fees and fines in either year.
 
@@
 
-The results of the two-way fixed effects model are different than what we saw in the 2018 cross-sectional approach; namely, while Table \ref{tab:twfe} indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not significantly impact Black turnout.
-The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.06 percentage points.
-
-In Table \ref{tab:coarser}, we re-estimate the model from Table \ref{tab:twfe} but coarsen the data.
-Here, the dependent variable of interest is binary: we test whether turnout changed for municipalities who increased their per-capita fees and fines collections differently than municipalities where collections stayed the same or decreased.
-Municipalities that increased their per-capita fees and fines are considered ``treated.''
-
-\begin{singlespace}
-\input{"../temp/coarser_reg_clean.tex"}
-\end{singlespace}
-
-The coefficient on \emph{Treated × 2018} indicates that non-Black turnout dropped by about 0.5 percentage points in municipalities where fees and fines collections increased, relative to other municipalities.
-While this coefficient is slightly \emph{positive} for Black voters, it is not statistically significantly different from 0.
-In other words, both Tables \ref{tab:twfe} and \ref{tab:coarser} indicate that increased fees and fines collections decrease non-Black turnout but have no impact on Black turnout.
+The results of the two-way fixed effects model are different than what we saw in the 2018 cross-sectional approach; namely, Table \ref{tab:twfe} indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not significantly impact Black turnout.
+The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.04 percentage points.
 
@@
 First, we can see that for both Black and non-Black voters the parallel trends assumption is satisfied.
-Of course, because we matched treated and control voters based on turnout prior to the ticket, this is unsurprising.
+Because we matched treated and control voters based on turnout prior to the ticket, this is by design.
 
 Table \ref{tab:dind-table} formalizes Figure \ref{fig:did1} into an ordinary least squares regression.
-Model 1 shows our overall causal effect, while Model 2 allows for the possibility that a ticket differentially mobilizes Black voters.
+Models 1 and 2 show our overall causal effect, while models 3 and 4 allow for the possibility that a ticket differentially mobilizes Black voters.
+In models 1 and 3, we include only the treatment, timing, and race dummies, while the full set of covariates used for the matching procedure are included in models 2 and 4.
 The coefficients of note are \emph{Treated × Post Treatment} and \emph{Treated × Post Treatment × Black}.
@@
 
-We first used survey data collected in the American National Election Studies 2016 and 2020 datasets to show how, unlike arrests, ticketing can mobilize Black voters.
-We found that Black people who reported personal or proximal police contact with a police stop in the last 12 months were 0.5 pp more likely to vote compared to Black people who did not report such contact.
-Non-Black respondents demonstrated no statistically significant result for police stops.
-Meanwhile, both Black and non-Black people who had been arrested at any point were less likely to vote, and we did not find significant differences between racial groups' behaviors in response to arrests.
-
-Next, we used a two-way fixed effects model to estimate the effect of increased fines and fees reliance at the city level on aggregate voter turnout in federal elections.
-We found that each 10 percent increase in fines and fees collected per resident is associated with a voter turnout decrease of about 0.06 percentage points, with no significant impact on Black turnout in particular---in other words, the demobilizing effect of ticketing increases at the city level is largely driven by non-Black voters.
-
-In order to directly observe the causal mechanism, we then conducted an individual-level analysis of ticketing and voting behavior in Hillsborough County, Florida.
-Using a difference-in-differences design, we found that individuals who were ticketed in the 90-day period preceding a federal election were 1.7 percentage points less likely to vote compared to individuals who were ticketed following the election.
-The effect was smaller for Black individuals (1 percentage point less likely), which is consistent with our hypothesis that Black political responses to ticketing should be distinct from whites (and more mobilized by comparison).
-
-We were somewhat surprised by the differences that arose between our two sets of findings---our city-level analysis using a two-way fixed effects model did not produce statistically significant results for Black voters.
-We think there are a few potential explanations for this mismatch.
-
-First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes are smaller or not statistically significant.
-Along a similar vein, it's possible that the effect size for Black voters in the city-level analysis is affected by higher-intensity forms of criminal legal contact, such as arrest and incarceration.
+Given how widespread police stops are and their relationship to racial injustice, their political implications demand close study.
+Accordingly, we investigate this question from a variety of perspectives, using multiple data sources and empirical approaches.
+What we find complicates our understanding of how lower-level police contact affects political participation.
+On one hand, the national survey data and cross-sectional municipal-level analysis indicate that police contact is associated with higher turnout for Black Americans, and either unrelated or negatively related to turnout for others.
+Our causal models, on the other hand, tell a slightly different story---namely, they fail to uncover mobilizing effects for Black Americans.
+Nevertheless, our causal models \emph{do} indicate that police stops are less demobilizing for Black individuals than for others.
+In this sense, our results all point in the same direction.
+Based on these three independent approaches, we conclude that the political consequences of police stops are unique for Black Americans---and that they are less demobilizing for Black Americans than others.
+
+The difference between the cross-sectional and two-way fixed effects models using the municipality-level data is somewhat surprising. There are a few potential explanations for this mismatch.
+
+First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes in the two-way fixed effects models are smaller or not statistically significant.
+Along a similar vein, it's possible that the effect size for Black voters in the city-level analysis is influenced by higher-intensity forms of criminal legal contact, such as arrest and incarceration.
 The bulk of existing literature suggests that incarceration discourages political participation, and it's not unreasonable to assume that cities that ramp up ticketing of Black residents also ramp up arrest and incarceration of Black residents.
 If these phenomena coincide, that could explain why the city-level analysis produced no statistically significant effect for Black voters---the personally mobilizing effect of ticketing could be counterbalanced by the proximal chilling effect of incarceration, and because the city-level analysis is not as temporally sensitive, it's more difficult to isolate the effect of ticketing.
-
-That said, \protect\hyperlink{ref-Sances2017}{Sances and You} (\protect\hyperlink{ref-Sances2017}{2017}) specifically note that they didn't exploit the panel setup of the COG because of little variation between the 2007-2012 COG to the 2012-2017 one, and so they just stuck to cross sectional.
-The positive effect for Black turnout in Figure 2 is consistent with our Tampa analysis and doesn't totally contradict the TWFE.
+We were unable to incorporate a measure of local incarceration trends due to a lack of consistent data nationwide.
+
+Moreover, Sances and You (\protect\hyperlink{ref-Sances2017}{2017, 1091})---the paper that originally detailed the relationship between fees and fines collections and municipalities' racial composition using the Census of Governments data---specifically notes that they did not exploit the panel setup of the COG because of ``little variation within a city in terms of revenues from fines.'' Instead, they present only the results of a cross-sectional study.
+Here, we present both the cross-sectional and panel results, acknowledging that each have limitations but that, taken together, they shed light on the unique politicization of fees and fines for Black Americans.
+
+Our individual-level analysis based on Hillsborough County, Florida, advances our understanding of this dynamic while raising new questions.
+On the one hand, the causal results are highly robust, and the ticketing data allows us to identify the treatment fairly precisely.
+On the other hand, these are the only results in which a police stop are associated with a \emph{decrease} in turnout for Black individuals.
+This may be because this analysis tests the impact of direct contact with the police, rather than direct \emph{or} proximal contact, as the ANES questions do.
+It may be because we can isolate the effect of a police stop from other, broader changes that may be correlated with increased fees and fines revenue in the municipal-level data.
+Or it may point to unique political circumstances surrounding race, policing, and political participation in Hillsborough County.
+We look forward to future scholarship that replicates and extends these Hillsborough County results.
+Nevertheless, that police stops are less demobilizing for Black Floridians in Hillsborough County---an effect that does not extend to other nonwhite residents---provides support for our general thesis that the political interpretation of these contacts with the criminal legal system are unique for Black Americans.
 
@@
 
-\textbf{Limitations}: Because our individual-level analysis is limited to Hillsborough County, we don't have a good idea of whether the city-level revenue reliance trend interacts with the individual experience of being ticketed.
+In this sense, our analysis points to a political contestation of criminal legal policy, a phenomenon that aligns with dozens of recent campaigns to reform local fines and fees practices (or abolish them entirely).\footnote{See \url{https://finesandfeesjusticecenter.org/clearinghouse}.} We know that fines and fees result from political economy (i.e.~austerity at the federal level), but our analysis suggests that this is a ``two way street'' wherein people who are harmed by policing practices are politically socialized into resistance.
+
+\textbf{Limitations}: Because our individual-level analysis is limited to Hillsborough County, we don't have a good sense of how the city-level revenue reliance trend interacts with the individual experience of being ticketed.
 Is ticketing more politically mobilizing for Black voters in cities that are palpably dialing up their revenue collection efforts?
-Future research could test this hypothesis in cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.
+Future research could test this hypothesis at the individual level within cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.
 
@@
 This means that there could be some proportion of ticketed Black motorists who are now less likely to register to vote in the first place, for example.
-In other words the mobilization effect in our findings only applies to people who were registered to vote---we are unable to make claims about whether being ticketed makes an individual more likely to register to vote.
-
-\textbf{Future research}: Future work should explore whether ticketing can be mobilizing for Black individuals under circumstances.
-We were unable to test whether what we're observing is just \emph{decreased} demobilization, or whether some subgroups of the Black population were mobilized while others were demobilized.
+In other words the mobilization effect (or decreased demobilization effect) in our findings only applies to people who were registered to vote---we are unable to make claims about whether being ticketed makes an individual more likely to register to vote.
+
+\textbf{Future research}: This work looks at the difference between the political behavior of Black and non-Black Americans.
+Future work should explore variation \emph{within} the Black community.
+When is this sort of contact mobilizing?
+For whom?
+Can organizers build on this potential for broad-based political action?
+We were unable to test whether what we're observing is simply \emph{decreased} demobilization, or whether some subgroups of the Black population were mobilized while others were demobilized.
 In other words, it could be the case that ticketing is demobilizing for all voters, but there is a subset of Black voters who are \emph{mobilized} by this, though they aren't a large enough group to counteract the demobilization of other Black people.
 
-Unlike previous studies using survey data, we are unable to tell whether individuals in Tampa have non-ticketing criminal legal exposure.
+Also, unlike previous studies using survey data, we are unable to tell whether treated individuals in Tampa have non-ticketing criminal legal exposure.
 Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.
+
+Although we have generated new evidence suggesting that police stops and related exploitative ticketing practices may mobilize Black voters, we emphasize that this finding does not redeem or justify such police practices.
+Black Americans already suffer from disproportionate police contact and the racial wealth gap, and racist revenue-motivated ticketing only increases the burden on Black communities nationwide.
+Policymakers should work to ensure that Black Americans no longer have to struggle to enjoy the same political power as whites---to that end, the current trend of voting rights restriction policies across the country is especially pernicious.
+Even if Black Americans understand the ballot box as one tool they can use to limit the state's power to exploit and harm them, policymakers should still feel an obligation to support voting rights and stop disproportionate ticketing in Black communities.
 
@@
 Imai, Kosuke, and Kabir Khanna.
-2016/ed.
+2016.
 {``Improving {Ecological Inference} by {Predicting Individual Ethnicity} from {Voter Registration Records}.''} \emph{Political Analysis} 24 (2): 263--72.
@@
 \leavevmode\hypertarget{ref-Pacewicz2020}{}%
-Pacewicz, Josh, and John N.Robinson III.
+Pacewicz, Josh, and John N.
+N.Robinson.
 2020.

### 2021-05-10 code/hills/mayor/04_mayor_reg.R
local stuff

@@ -48,44 +48,10 @@ matches <- left_join(matches,
 
 cleanup("matches")
 gc()
-ll <- matches %>%
-  filter(first_tr_year - last_date <= 90, period <= 0.5, period >= -1.5) %>%
-  group_by(treated, period, black_t) %>%
-  summarize(to = weighted.mean(to, weight)) %>% 
-  mutate(treated = ifelse(treated, "Treated", "Control"),
-         black = ifelse(black_t, "Black Voters", "Non-Black Voters"))
-
-
-ll$treated <- factor(ll$treated, levels = c("Treated", "Control"))
-
-p1 <- ggplot(data = ll) + 
-  facet_grid(. ~ black) +
-  geom_rect(aes(xmin = 0.5-.125, xmax = 0.5, ymin = 0, ymax = Inf),
-            alpha = 0.03, color = "black", fill = "yellow") +
-  geom_line(data =ll, aes(x = period, y = to, linetype = treated)) +
-  geom_point(data = ll, aes(x = period, y = to, shape = treated)) +
-  scale_x_continuous(minor_breaks = seq(-3.5, 3.5, 1),
-                     breaks = seq(-3.5, 3.5, 1),
-                     labels = c("-4",
-                                "-3",
-                                "-2",
-                                "-1",
-                                "0",
-                                "1",
-                                "2",
-                                "3")) +
-  theme_bc(base_family = "LM Roman 10") +
-  scale_y_continuous(labels = percent) +
-  labs(x = "t", y = "Turnout",
-       linetype = "Treatment Group",
-       shape = "Treatment Group",
-       caption = "Treatment occurs inside of yellow band.") 
-p1
-saveRDS(p1, "temp/within90days_y.rds")
 ##########################
 ll <- matches %>%
   filter(period <= .5, period >= -1.5) %>% 
-  group_by(treated, period, black_t, first_tr_year) %>%
+  group_by(treated, period, black_t) %>%
   summarize(to = weighted.mean(to, weight)) %>% 
   mutate(treated = ifelse(treated, "Treated", "Control"),
          black = ifelse(black_t, "Black Voters", "Non-Black Voters"))
@@ -93,7 +59,7 @@ ll <- matches %>%
 ll$treated <- factor(ll$treated, levels = c("Treated", "Control"))
 
 p2 <- ggplot(data = ll) + 
[…]

### 2021-05-24 markdown/draft_paper.tex
incorporate 2014 turnout

@@
 \author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
-\date{May 07, 2021}
+\date{May 24, 2021}
 
@@
 Racial capitalist political economy imposes fiscal constraints regardless of city officials' identities or intentions.
-In their study of fines and fees reliance in Chicago suburbs, Josh Pacewicz and John Robinson, III show how the racialization of municipal opportunity structures prevents majority-Black suburban governments from acquiring sufficient revenue from ``good'' sources such as sales taxes or property taxes, catalyzing a reliance on fines and fees to fund government services (\protect\hyperlink{ref-Pacewicz2020}{Pacewicz and N.Robinson 2020}).
+In their study of fines and fees reliance in Chicago suburbs, Josh Pacewicz and John Robinson, III show how the racialization of municipal opportunity structures prevents majority-Black suburban governments from acquiring sufficient revenue from ``good'' sources such as sales taxes or property taxes, catalyzing a reliance on fines and fees to fund government services (\protect\hyperlink{ref-Pacewicz2020}{Pacewicz and Robinson 2020}).
 Pacewicz and Robinson III note that racialized municipal opportunity structures are tied to the political-historical processes of neoliberalism and fiscal austerity, an observation that aligns with recent scholarship detailing the origins of fees paid by incarcerated people (\protect\hyperlink{ref-Kirk2020}{Kirk, Fernandes, and Friedman 2020}).
@@
 Pacewicz, Josh, and John N.
-N.Robinson.
+Robinson III.
 2020.

### 2021-05-24 code/00_initialize.R

@@ -1,6 +1,7 @@
 library(splitstackshape)
 library(PanelMatch)
 library(rgdal)
+library(sqldf)
 library(Metrics)
 library(RSQLite)
 library(multcomp)

### 2021-05-24 code/02_2018_cross_sectional.R

@@ -85,7 +85,8 @@ p1
 
 full_set <- rename(full_set, share_s_fed = share_state_fed) %>% 
   mutate(median_income = median_income / 10000,
-         lpd = log(pop_dens))
+         lpd = log(pop_dens),
+         total_revenue = log(total_revenue))
 
 saveRDS(full_set, "temp/full_set_for_mae.rds")
 
@@ -122,7 +123,7 @@ stargazer(models, type = "text", omit = c("state"),
                                "% with Some College",
                                "Median Age",
                                "Share over 64",
-                               "Total Revenue",
+                               "Log(Total Revenue)",
                                "% of Rev from Taxes",
                                "% of Rev from State / Fed Gov."),
           se = ses,

### 2021-05-24 code/03_2wayfe.R

@@ -22,10 +22,34 @@ census <- bind_rows(
 cities <- left_join(cities, census)
 
 place_to <- readRDS("temp/place_to.rds") %>% 
-  rename(plasub = place)
+  rename(plasub = place) %>% 
+  mutate(votes_18 = count * to_18) %>% 
+  select(plasub, votes_18, voters_18 = count,
+         EthnicGroups_EthnicGroup1Desc)
 
+p14 <- readRDS("temp/places_14_national.rds") %>% 
+  select(plasub = place,
+         EthnicGroups_EthnicGroup1Desc,
+         votes_14 = ballots_14,
+         voters_14)
+
+place_to <- full_join(place_to, p14) %>% 
+  mutate_at(vars(starts_with("vote")), ~ ifelse(is.na(.), 0, .))
+################################
 county_s_to <- readRDS("temp/county_s_to.rds") %>% 
-  rename(plasub = county_s)
+  rename(plasub = county_s) %>% 
+  mutate(votes_18 = count * to_18) %>% 
+  select(plasub, votes_18, voters_18 = count,
+         EthnicGroups_EthnicGroup1Desc)
+
+cs14 <- readRDS("temp/countysubs_14_national.rds") %>% 
+  select(plasub = cousub,
+         EthnicGroups_EthnicGroup1Desc,
+         votes_14 = ballots_14,
+         voters_14)
+
+county_s_to <- full_join(county_s_to, cs14) %>% 
+  mutate_at(vars(starts_with("vote")), ~ ifelse(is.na(.), 0, .))
 
 county_s_to <- county_s_to[!(county_s_to$plasub %in% place_to$plasub),]
 
@@ -48,13 +72,13 @@ to <- bind_rows(city_to %>%
                   mutate(race = ifelse(EthnicGroups_EthnicGroup1Desc == "Hispanic and Portuguese", "latino",
                                        ifelse(EthnicGroups_EthnicGroup1Desc == "East and South Asian", "asian", "other")))) %>% 
   group_by(plasub, race) %>%
-  mutate(votes_18 = count * to_18,
-         votes_14 = count * to_14) %>% 
-  summarize(to_18 = sum(votes_18) / sum(count),
-            to_14 = sum(votes_14) / sum(count),
-            votes_18 = sum(votes_18),
-            votes_14 = sum(votes_14)) %>% 
[…]

### 2021-05-24 code/04_anes.R

@@ -97,7 +97,7 @@ stargazer(m_stop, m_stop2, m_stop3, m_arrest, type = "text",
                                "Age",
                                "Republican",
                                "Other Party",
-                               "Income (dollarsign10s)",
+                               "Income (dollarsign10,000s)",
                                "Male",
                                "Refused Sex Question",
                                "Ideology Missing",

### 2021-05-24 code/process14.R

@@ -1,0 +1,172 @@
+files <- list.files("D:/national/post_2014", full.names = T, pattern = "*.zip")
+
+
+for(f in files){
+  f2 <- substring(f, 1, nchar(f) - 4)
+  state <- substring(f, 37, 38)
+  print(state)
+  if(!dir.exists(f2)){
+    unzip(f, exdir = f2)
+  }else{
+    print("Already Unzipped")
+  }
+  if(!file.exists(paste0("temp/", state, "_to_14_block.rds"))){
+    l <- list.files(f2, full.names = T, pattern = "*.tab")
+    k <- read.csv.sql(l, sep = "\t",
+                      sql = "select LALVOTERID, Voters_FIPS,
+                             Residence_Addresses_AddressLine, 
+                             Residence_Addresses_ExtraAddressLine, 
+                             Residence_Addresses_City, 
+                             Residence_Addresses_State,
+                             Residence_Addresses_CensusTract,
+                             Residence_Addresses_CensusBlockGroup,
+                             Residence_Addresses_CensusBlock,
+                             EthnicGroups_EthnicGroup1Desc,
+                             [General_2014.11.04] from file") %>%
+      mutate(state = state)
+    
+    saveRDS(filter(k,
+                   Residence_Addresses_CensusTract == "" |
+                     is.na(Residence_Addresses_CensusTract) | 
+                     Residence_Addresses_CensusTract == 0), paste0("temp/", state, "_to_14_no_block.rds"))
+    
+    saveRDS(filter(k,
+                   Residence_Addresses_CensusTract != "" &
+                     !is.na(Residence_Addresses_CensusTract) & 
+                     Residence_Addresses_CensusTract != 0), paste0("temp/", state, "_to_14_block.rds"))
+    print(state)
+    print(mean(k$Residence_Addresses_CensusTract == "" | is.na(k$Residence_Addresses_CensusTract) | k$Residence_Addresses_CensusTract == 0))
+  }
+}
+##############################
+files <- list.files("temp", pattern = "*to_14_no_block.rds", full.names = T)
+
+db18 <- dbConnect(SQLite(), "D:/national_file.db")
+
+for(f in files){
+  s <- substring(f, 6, 7)
+  if(file.exists(paste0("temp/cleaned_", s, "_2014.rds"))){
[…]

### 2021-07-23 markdown/not_blind.Rmd
submission docs

--- 2021-05-01 markdown/draft_paper.Rmd
@@
 ---
-title: "Policing for Profit and the Mobilization of Black Voters"
-
+title: "Ticketing and Turnout: How Policing for Profit Shapes Democratic Participation"
 author:
@@
 - Kevin Morris^[PhD Student, CUNY Graduate Center, Department of Sociology (kmorris@gradcenter.cuny.edu)]
+
 date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
 Despite this burgeoning literature, no research has directly investigated how police ticketing practices affect political participation.
-We use three approaches to answer this question: national survey data, a city-level analysis using Census of Governments data and the national voter file, and individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019.
-The survey data show that Black people who report that they were recently stopped by police are more likely to vote compared to those who were not stopped.
-Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.6 percentage point turnout decrease but was not associated with Black turnout.
-In Tampa, Florida, we estimate that being ticketed decreases an individual’s likelihood of voting in federal elections by 1.7 percentage points, but depressive effects are smaller for Black residents.
+We use three approaches to answer this question: we leverage individual-level ticketing data from Hillsborough County, Florida between 2010 and 2020, a city-level analysis using Census of Governments data and the national voter file, and  national survey data.
+In Hillsborough County, we estimate that being ticketed decreases an individual’s likelihood of voting in federal elections by 1.7 percentage points, but depressive effects are smaller for Black residents.
+Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 was associated with a roughly 0.04 percentage point turnout decrease but was not associated with any change in Black turnout.
+The survey data show that Black people who report that they or a family member were recently stopped by police are more likely to vote than those who reported no such contact.
 
@@
 
-Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities’ alienation from government.
+Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities’ alienation from government [@Sanders2017; @McCoy2015; @Shaer2019].
 After Michael Brown was killed by the Ferguson Police Department in 2014, a US Department of Justice investigation into the city’s police and courts demonstrated that the municipality was engaged in a practice that advocates now refer to as “policing for profit.” The city’s reliance on fines and fees to fund government functions grew from 13 to 23 percent of the total budget between fiscal years 2012 and 2015.
@@
 It wasn’t just a Ferguson problem, or even a Missouri problem.
-American cities’ reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services [@Singla2020; @Harris2017].
+American cities’ reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services [@Singla2020; @Harris2017; @Harris2020].
 
-Work exploring how criminalization directly and indirectly influences political participation has exploded in recent years.
+Work exploring how criminalization directly and indirectly influences political participation has exploded in recent years following path-breaking work from political sociologists Chris Uggen and Jeff Manza [@Uggen2002; @Manza2006].
 Scholars have found that criminal legal contact (i.e.
@@
 Such work has largely focused on the effects of highly disruptive contact with the criminal legal system such as incarceration and felony convictions [@Burch2014; @Lee2014].
-This paper is the first to explicitly theorize how local ticketing practices shape the political socialization of ticketed individuals.
+While ticketing involves potentially negative interactions with the state, it does not necessarily carry the disruptive consequences of a felony conviction and might thus politicize Americans in unique ways.
+Building on recent theoretical work from @Walker2020a and an analysis of the historical context of fees and fines collections in the United States, this paper is the first to explicitly theorize how local ticketing practices shape the political socialization of ticketed individuals.
+We argue that ticketing depresses voter turnout overall, but also catalyzes a “linked fate” political analysis among Black voters that either causes increased turnout or mitigates the turnout reductions observed among non-Black individuals.
+
 Additionally, our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
@@
 Existing research allows for the testing of specific psychological mechanisms and personal interpretations of criminal legal contact, but does not allow us to generalize more broadly.
-As Weaver and Lerman [-@Weaver2010, page 821] note, it may also introduce measurement bias.
+As Weaver and Lerman [-@Weaver2010: 821] note, it may also introduce measurement bias.
 Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to police ticketing.
-The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of the 232,568 individuals ticketed over a 6 year period---a far larger pool than even the most robust surveys.
+The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of a quarter-million individuals ticketed over a 6 year period---a far larger pool than even the most robust surveys.
 
-Before turning to the administrative data, we begin with a novel analysis of 2016 and 2020 national survey data regarding voters’ experience with police stops and arrests.
-We find that Black respondents who reported personal or proximal experience with police stops in the last 12 months are more likely to vote than Black people who did not, while we find no statistically significant relationship between stops and voting among non-Black respondents.
+We use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were ticketed between the 2012 and 2018 elections.
+By matching individual voters who were ticketed to similar voters who were ticketed at later points and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout.
+We find that being ticketed reduces the chance that an individual will turn out in the subsequent election, but that this effect is smaller for Black voters.
 
-Next, we join fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for each municipality in the country.
+To test the generalizability of our findings in Hillsborough County, we leverage two different datasets that are national in scope.
+First, we join fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for thousands of municipalities around the country.
 While we find that increased fees and fines likely cause lower turnout among non-Black Americans, we find no effect of fees and fines on Black turnout.
 
-Because our national analyses do not allow us to directly observe the causal effect of police ticketing on voter turnout, we use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were ticketed between the 2012 and 2018 elections.
-By matching individual voters who were ticketed to similar voters who were ticketed at later points and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout.
-We find that being ticketed reduces the chance that an individual will turn out in the subsequent election, and that this effect is smaller for Black voters.
+Second, we conduct a novel analysis of 2020 national survey data regarding voters’ experience with police stops.
+We find that Black respondents who reported personal or proximal experience with police stops in the last 12 months are more likely to vote than Black people who did not, while we find no statistically significant relationship between stops and voting among non-Black respondents.
+While both the municipal-level and survey data present some drawbacks relative to the individual-level administrative data, their national scope provides helpful corroboration for the unique turnout effects of tickets for Black Americans observed in Hillsborough County.
 
@@
 Our findings complicate existing theories of how criminalization politically socializes Americans, and Black Americans in particular [@Weaver2010].
-Additionally, while all forms of criminalization likely contribute to a subjective experience of alienation or group-level exclusion among Black Americans that is well-documented in sociological scholarship [@Bell2017; @Desmond2016], our contribution emphasizes the need for further research regarding how different forms of criminalization affect group-level perceptions of government and resultant political behavior.
-Accordingly, we propose a new theory explaining how ticketing may uniquely catalyze mobilizing narratives of racial injustice.
+Additionally, while all forms of criminalization likely contribute to a subjective experience of alienation or group-level exclusion among Black Americans that is well-documented in sociological scholarship [@Bell2017; @Desmond2016], our contribution emphasizes the need for further research regarding how different forms of criminalization affect group-level perceptions of government and resultant political behaviors.
+Accordingly, we propose a new theory explaining how ticketing may uniquely catalyze Black political participation.
 Our findings are relevant for interdisciplinary scholars of crime, race, politics, political economy, social movements, and policing.
@@
 
-In order to theorize how fines and fees affect political behavior, we consider (1) how criminalization directly shapes the electorate, (2) the existing scholarly understanding of the influence of criminalization on political socialization, and (3) how contemporary ticketing practices are tied to a longer legacy of racist exploitation and thus ripe for political mobilization around narratives of racial injustice.
-
-## Criminalization and the American electorate {-}
-
-The American criminal legal system directly shapes the American electorate and excludes Black voters.
-Today, more than five million Americans are legally barred from voting due to a felony conviction, and one in every sixteen Black Americans of voting age is disenfranchised [@Uggen2020].
-Following the implementation of the Fifteenth Amendment in 1870, over a dozen U.S.
-states passed laws denying voting rights to people who were convicted of felonies.
-In their analysis of how racial threat catalyzes felon disenfranchisement, @Behrens2003 found that increases in the share of a state’s prison population that is nonwhite drastically increases the likelihood of legislation permanently disenfranchising people convicted of felonies.
-As @Shofner1963 notes, felony disenfranchisement has often been tied explicitly to the increased presence of Black Americans in the electorate.
-
-Notably, fines and fees legally disenfranchise Americans: 48 states and the District of Columbia authorize some form of wealth-based penal disenfranchisement [@Colgan2019].
-More specifically, many states require payment of fees as a condition of criminal legal supervision or the payment of all legal financial obligations as a condition of completing a sentence, and failure to comply with supervision or sentence completion conditions can be a barrier to voting rights restoration.
-Such political barriers also disproportionately affect Black people.
-In Alabama, for example, Black people with felony convictions applying to have their voting rights restored were 26 percentage points more likely to have their application denied over outstanding fines and fees [@Meredith2017].
-
-The role of fines and fees in the context of felony disenfranchisement has recently garnered national attention.
-After Floridians passed Amendment 4 to restore voting rights to individuals with felony convictions in 2018, Florida Republicans passed legislation requiring these individuals to pay off the fines and fees associated with their original sentence.
-Because Florida does not maintain good records on who owes how much, the new law has proved to be a major hurdle for potential voters.
-As @Morris2021 argues, this could have severe implications for the future democratic participation of those excluded anew from the electorate after the state passed the amendment.
+In order to theorize how fines and fees affect political behavior, we consider how criminalization directly shapes the electorate; the existing scholarly understanding of the influence of criminalization on political socialization; and how contemporary ticketing practices are tied to a longer legacy of racist exploitation and thus ripe for political mobilization around narratives of racial injustice.
 
 ## Criminalization and political socialization {-}
+
+The American criminal legal system directly shapes the American electorate and excludes voters.
+Today, more than five million Americans are legally barred from voting due to a felony conviction, and one in every sixteen Black Americans of voting age is disenfranchised [@Uggen2020].
+Notably, fines and fees legally disenfranchise Americans as well: 48 states and the District of Columbia authorize some form of wealth-based penal disenfranchisement [@Colgan2019].
+Many states require payment of fees as a condition of criminal legal supervision or the payment of all legal financial obligations as a condition of completing a sentence, and failure to comply with supervision or sentence completion conditions can be a barrier to voting rights restoration.
 
@@
 Research on legal cynicism has found that public perceptions of abusive police practices can reduce willingness to report crimes or cooperate with law enforcement [@Desmond2016; @Tyler2014].
-Because police are the most visible agents of the state, perceptions of unfairness in policing can translate to a recognition of actual group-level structural exclusion from public institutions [@Bell2017].
+In short, the “hidden curriculum” [@Justice2014; @Meares2017] of the criminal legal system teaches Americans about their identities as citizens---even parts of their identities that have little to do with policing or incarceration.
 New evidence related to ticketing and legal estrangement has recently emerged: in a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government compared to residents who were not ticketed [@CarpenterII2019].
 
-Sarah Brayne found related results in her analysis of survey data---as the intensity of criminal legal contact escalates (i.e.
+Because police are the most visible agents of the state, perceptions of unfairness in policing can translate to a recognition of actual group-level structural exclusion from public institutions [@Bell2017].
+Soss and Weaver explain how criminal legal contact shapes perceptions of government and political participation: “interviewees have looked, not to City Hall, Congress, or political parties, but rather to their direct experiences with police, jails and prisons, welfare offices, courts, and reentry agencies as they sought to ground their explanations of how government works, what political life is like for them, and how they understand their own political identities” [@Soss2017: 574].
+
+Sarah Brayne found related results in her analysis of survey data.
+As the intensity of criminal legal contact escalates (i.e.
 stopped, arrested, convicted), people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions [@Brayne2014].
@@
 Similarly, @Remster2018a finds that men who return home from prison are more likely to avoid contact with their childrens’ schools.
+Vesla Weaver and colleagues helpfully describe this form of self-preserving withdrawal from public institutions as a “strategic retreat” [@Weaver2020].
 
 In addition to influencing perceptions of government and participation in public institutions, recent scholarship indicates that criminalization influences political behavior.
-The “hidden curriculum” of the criminal legal system [@Justice2014; @Meares2017] teaches individuals about their position within the political system, and the criminal legal system consequently serves as a primary site of political socialization for convicted individuals and their families [e.g.
-@Lee2014].
+Using existing national survey data and extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) [@Weaver2010].
+Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a “linked fate” where “one’s individual opportunities are linked to the entire racial group” [@Lerman2014: 197].
+Their interview data lead them to conclude that while criminal legal contact does increase perceptions of linked fate among Black respondents, “a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing.” Interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation [@Lerman2014].
 
-Using existing national survey data and extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) [@Weaver2010].
-Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a “linked fate” where “one’s individual opportunities are linked to the entire racial group” [@Lerman2014, page 197].
-Their interview data lead them to conclude that while criminal legal contact does increase perceptions of linked fate among Black respondents, “a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing”---and interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation [@Lerman2014].
+Lerman and Weaver’s findings have been corroborated using administrative data: Ariel White found that short jail sentences in Harris County, Texas reduced Black defendant turnout in subsequent elections by 13 percentage points---but the effect on white turnout was not statistically significant [@White2019].
+Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level [@Burch2014].
+These effects can also extend to family members, and the political consequences can be quite durable [@Morris2021].
 
-Lerman and Weaver’s finding has been corroborated by administrative data: Ariel White found that short jail sentences in Harris County, Texas reduced Black defendant turnout in subsequent elections by 13 percentage points---but the effect on white turnout was not statistically significant [@White2019].
-Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level [@Burch2014].
-
-Although most work documents a uniformly demobilizing effect from contact with the criminal legal system, recent work from Hannah Walker [-@Walker2020; -@Walker2020a] complicates this narrative by arguing that, when Black Americans understand their contact with the criminal legal system in the context of a narrative of racial injustice, such contact can actually prove mobilizing.
-She explains: “experiences with punitive policies are subject to interpretation and, when understood through narratives of injustice, lead to wholly different participation outcomes than we usually predict” [@Walker2020, page 132].
-While she finds that this sense of injustice is especially likely to increase political participation in non-voting ways (such as attending a protest or signing a petition), the logic could extend to electoral participation as well given a strong narrative or relatively weak contact with the criminal legal system.
+Although most work documents how contact with the criminal legal system causes strategic retreat, recent work from Hannah Walker [-@Walker2020; -@Walker2020a] complicates this narrative.
+She argues that when Black Americans understand their contact with the criminal legal system in the context of a narrative of racial injustice, such contact can actually mobilize.
+She explains: “experiences with punitive policies are subject to interpretation and, when understood through narratives of injustice, lead to wholly different participation outcomes than we usually predict” [@Walker2020: 132].
+While she finds that this sense of injustice is especially likely to increase political participation in non-voting ways (such as attending a protest or signing a petition), the logic could extend to electoral participation as well given a relevant electoral context, strong injustice narrative, or relatively weak contact with the criminal legal system.
+Findings presented in @Laniyonu2019 provide support for this concept: concentrated Stop, Question, and Frisk (SQF) policing in New York City neighborhoods was associated with reduced turnout in federal midterm elections but increased turnout in presidential and mayoral primary elections.
+Laniyonu also uncovered an association regarding candidate choice—he demonstrates higher turnout for a candidate who opposed SQF policing and lower turnout for a candidate who supported it.
+In other words, low-level police contact mobilized voters to participate in a local election (which could plausibly affect police practices).
 
 Despite the growing body of high-quality scholarship on the democratic implications of the American criminal legal system, we still know remarkably little about the effects of the most routine sort of contact---police stops and tickets that do not result in an arrest.
-We leverage Walker’s novel insights about the potentiality of a narrative of injustice to re-think how these sorts of contact with the state can structure political participation.
 
@@
 Cedric Robinson’s articulation of racial capitalism offers a useful theoretical framework for interpreting the trajectory of American anti-Black political economy [@Robinson2000].
-Brittany Friedman theorizes fines and fees as a “progression of racial capitalism penology,” emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices [@Friedman2020, page 177].
+Brittany Friedman theorizes fines and fees as a “progression of racial capitalism penology,” emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices [@Friedman2020: 177].
 Robinson argues that European industrial capitalism continued a longer political-economic trend of differentiating racial groups in order to dispossess them and exploit their labor.
@@
 The implementation of the Black Codes, convict leasing, and sharecropping systems marked a transition to a new stage of racial capitalism, wherein criminalization provided an easily-exploited labor supply that offset costs that the state incurred by coercing their labor [@Lichtenstein1996; @Mancini1978].
-Contemporary fines and fees practices have been directly compared to sharecropping because both structures share “a long-term pattern of financial exploitation based on race… that limits the life-choices of the affected population” [@Blessett2016, page 113].
+Contemporary fines and fees practices have been directly compared to sharecropping because both structures share “a long-term pattern of financial exploitation based on race… that limits the life-choices of the affected population” [@Blessett2016: 113].
 
 In the 20th century, residential segregation simultaneously fueled the racial wealth gap and ensured that criminalization was both spatially and racially concentrated [@Rothstein2017; @Hinton2021].
-At the level of federal policy, racial threat and whites’ attribution of criminality to Blackness [@Muhammad2010] prompted a shift “from the War on Poverty to the War on Crime” wherein Black communities’ demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration [@Hinton2017; @Vargas2017a].
+At the level of federal policy, racial threat and whites’ attribution of criminality to Blackness [@Muhammad2010] prompted a shift from the War on Poverty to the War on Crime wherein Black communities’ demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration [@Hinton2017; @Vargas2017a].
 
@@
 Black elected officials): The positive association between cities’ reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator [@Sances2017].
+This result aligns with recent research demonstrating that states with more Black legislators spend less on corrections budgets; that racial disparities in arrests are reduced in municipalities represented by a majority-nonwhite city council; and that descriptive representation can reduce racial disparities in the criminal legal system  [@Butler2011; @Gunderson2020; @Eckhouse2016].
+It thus seems that the ballot box can be a site from which Black Americans can secure some protections against the most egregious forms of revenue extraction.
 
@@
 
-Black Americans can therefore situate exploitative ticketing practices in a longer historical legacy of collective disparate treatment and violence at the hands of the state.
-We argue that Black voters’ recognition of discriminatory ticketing practices facilitates a “linked fate” political analysis that motivates voting behavior distinct from other forms of criminalization, such as criminal conviction or incarceration.
-We expect both ticketing and incarceration to spark a recognition of “a sense of injustice” among Black Americans, but we argue that ticketing should ultimately mobilize Black voters (unlike incarceration, which discourages Black voters more than whites [@White2019]).
+# Theory {-}
 
-Ticketing produces substantively different experiences than being arrested or incarcerated.
-While tickets can lead to driver’s license suspensions or, in a smaller subset of cases, nonpayment incarceration, tickets are generally far less disruptive than criminal convictions and prison terms, and we argue that this difference should lead to different political behaviors.
-For example, one participant in @Lerman2014 who had served five years of probation after a criminal conviction reported, “I feel like if I contact a senator or governor, they’ll probably want to put me in jail and leave me as a troublemaker...
-That’s how I actually feel: ‘I better stay below the radar ’cause this guy’s tryin’ to start trouble’” [@Lerman2014, page 210].
-While formerly incarcerated people or people who have experienced criminal legal supervision may avoid voting due to the same type of fear of state surveillance and control that motivates their avoidance of medical or educational institutions [@Brayne2014], we argue that being ticketed should not produce the same chilling effect---ticketing should not prompt Black people to use political withdrawal as a self-preservation strategy.
+We argue that Black voters’ recognition of discriminatory ticketing practices facilitates a linked fate political analysis that motivates voting behavior distinct from other forms of criminalization, such as criminal conviction or incarceration.
+We expect both ticketing and incarceration to spark a recognition of “a sense of injustice” among Black Americans (catalyzing “linked fate”), but we argue that ticketing should ultimately mobilize Black voters---unlike incarceration, which discourages Black voters more than whites [@White2019].
+In other words, while incarceration may prompt Black voters’ strategic retreat via linked fate, ticketing could produce the opposite effect.
 
-Additionally, we argue that “policing for profit”---the experience of being ticketed while a municipality is palpably ramping up its fines and fees practices to collect revenue---is also substantively distinct from the experience of being arrested or incarcerated.
+Ticketing is by far the most common form of criminal legal contact: in 2018, more than 24 million people experienced police contact in the context of a traffic stop, whereas about 5.17 million people are currently disenfranchised as a result of a felony conviction [@Harrell2020; @Uggen2020].
+At the same time, the most egregious local ticketing increases occurred largely over the past two decades [@Singla2020], and increases have been concentrated largely in Black municipalities [@Sances2017].
+These facts have been extensively discussed in mainstream media and should be widely known among Black voters [@Eligon2019; @Ehrenfreund2014].
+We also expect a larger share of more affluent Black voters to be affected by ticketing compared to other forms of criminalization---arrests and incarceration are most common among individuals experiencing poverty [@Looney2018].
+Because perceptions of “linked fate” and related critiques of policing are even more salient among members of the Black middle class [@Dawson1995], we expect Black middle class voters to be mobilized by egregious ticketing practices.
+In other words, we argue that ticketing should ensnare more Black voters who are more likely to politicize the issue.
+
+The rise of the Black Lives Matter movement in 2013 constitutes a significant development for the political socialization of Black Americans, and many early Black Lives Matter protests either occurred in municipalities with exploitative ticketing practices or directly followed traffic stops that escalated into police violence [@Holpuch2015; @LaFraniere2016].
+The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious.
+Furthermore, local Black Lives Matter activism can change police practices.
+One recent study found that census places that saw Black Lives Matter protests experienced a 15 to 20 percent decrease in police killings over the following five year period [@Campbell2021].
+It is possible that Black Lives Matter facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis---the movement arose shortly after fines and fees became a more salient and widespread threat to Black Americans’ material security, and the BLM movement helped to publicize these disparities.
+Our understanding of the broader literature on criminalization and political behavior is that injustice narratives and the “linked fate” mechanism explain how Black individuals connect broad political trends to the “micro” experience of being personally stopped by police (and this micro-macro connection is what would motivate resultant voting behavior).
+We argue that exposure to BLM protests or messaging likely strengthened this process, which might explain potentially mobilizing effects of ticketing for Black voters.
+Based on the strength and accessibility of ticketing-related injustice narratives and the mobilization framework proposed by @Walker2020a, we expect that Black voters’ political behavior in response to police ticketing will be distinct from the political behavior of white voters, and further that ticketing should mobilize Black voter turnout in cities that have recently ramped up ticketing.
+
+Of course, these disparities are also present in patterns of conviction and incarceration.
+We argue, however, that “policing for profit”---the experience of being ticketed while a municipality is palpably ramping up its fines and fees practices to collect revenue---is substantively distinct from the experience of being arrested or incarcerated.
 In doing so, we extend Epp et al.’s theory of pretextual traffic stops politically socializing Black voters to the specific context of discriminatory police ticketing [@Epp2014].
@@
 The city created a new traffic violations agency in 2015, spurring its yearly ticketing numbers to jump from around 32,000 to over 52,000.
-This financial aspect of ticketing should make it distinct from arrests and incarceration: much like the coercion of labor under the Black Codes, contemporary fines and fees practices are blatantly an effort to extract wealth from Black Americans.
-Although 20th century political rhetoric centered public safety as the mission of policing [CITE], exploitative ticketing practices cannot be reconciled with such rhetoric.
-In other words, to the extent that mass incarceration could be justified using narratives of “colorblind racism” (i.e., there’s a lot of crime happening in Black communities, so that’s why there’s more policing in those areas), racist ticketing practices do not enjoy the same rhetorical convenience.
+This financial aspect of ticketing should make it distinct from arrests and incarceration: much like the coercion of labor under the Black Codes, contemporary fines and fees practices are blatant efforts to extract wealth from Black Americans.
+In other words, to the extent that mass incarceration could be justified using “colorblind” narratives (i.e., high crime rates in Black communities results in more policing in those areas), racist ticketing practices do not enjoy the same rhetorical convenience.
+It may not be possible for revenue-motivated, racist ticketing to be reconciled with the idea that policing is primarily meant to improve public safety---in other words, we expect ticketing to actively feel less fair and activate salient linked fate analyses among Black individuals.
 
-Ticketing is by far the most common form of criminal legal contact; in 2018, more than 24 million people experienced police contact in the context of a traffic stop, whereas about 5.17 million people are currently disenfranchised as a result of a felony conviction [@Harrell2020; @Uggen2020].
-At the same time, the most egregious local ticketing increases occurred largely over the past two decades [@Singla2020], and increases have been concentrated largely in Black municipalities [@Sances2017].
-These facts have been extensively discussed in mainstream media and should be widely known among Black voters [@Eligon2019; @Ehrenfreund2014].
-We expect a larger share of more affluent Black voters to be affected by ticketing than other forms of criminalization---arrests and incarceration are most common among individuals experiencing poverty [@Looney2018].
-Because perceptions of “linked fate” and related critiques of policing are even more salient among members of the Black middle class [@Dawson1995], we expect Black middle class voters to be mobilized by egregious ticketing practices.
-In other words, we argue that ticketing should ensnare more Black voters who are more likely to politicize the issue.
+Finally, ticketing produces substantively different experiences than being arrested or incarcerated.
+While tickets can lead to driver’s license suspensions or, in a smaller subset of cases, nonpayment incarceration, tickets are generally far less disruptive than criminal convictions and prison terms.
+People who have been convicted of a crime and incarcerated are relegated to an alternate political membership status that Reuben Jonathan Miller and Forrest Stuart call “carceral citizenship,” subjecting them to forms of supervision and sanction “that are otherwise unavailable to [people] who have not been accused of a crime” [@Miller2017: 536].
+Ticketing does not involve the same degree of surveillance and control as criminal conviction and incarceration.
+We argue that this difference in severity should lead to different political behaviors.
+For example, one participant in @Lerman2014 who had served five years of probation after a criminal conviction reported, “I feel like if I contact a senator or governor, they’ll probably want to put me in jail and leave me as a troublemaker...
+That’s how I actually feel: ‘I better stay below the radar ’cause this guy’s tryin’ to start trouble’” [@Lerman2014: 210].
+While formerly incarcerated people or people who have experienced criminal legal supervision may pursue a strategic retreat from voting (i.e.
+withdraw in order to protect themselves), we argue that being ticketed should not produce the same chilling effect---ticketing should not prompt Black people to use political withdrawal as a self-preservation strategy.
 
-Finally, the rise of the Black Lives Matter movement in 2013 constitutes a significant development for the political socialization of Black Americans, and the movement began in municipalities that targeted Black residents with tickets.
-The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious.
-Furthermore, local Black Lives Matter activism can change police practices.
-One recent study found that census places that saw Black Lives Matter protests experienced a 15 to 20 percent decrease in police killings over the following five year period [@Campbell2021].
-It’s possible that Black Lives Matter facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis---the movement arose shortly after fines and fees became a more salient and widespread threat to Black Americans’ material security, and many early Black Lives Matter protests either occurred in municipalities with exploitative ticketing practices or directly followed traffic stops that escalated into police violence [@Holpuch2015; @LaFraniere2016].
-
-Today, fines and fees disproportionately affect Black people, and Black political mobilization appears to mitigate some of the most egregious ticketing practices [@Sances2017].
-Accordingly, we expect that Black voters’ political behavior in response to police ticketing will be distinct from the political behavior of white voters, and further that ticketing should mobilize Black voter turnout in cities that have recently ramped up ticketing.
+We argue that the combined psychological mechanism of “linked fate” and resultant political socialization among Black voters should elicit different responses to different forms of police contact---and our analysis constitutes a quantitative test of how the “input” of ticketing may produce a different behavioral “output” compared to arrest, conviction, or incarceration.
+Accordingly, we expect to see across multiple quantitative approaches that ticketing reduces voter turnout overall, but not for Black Americans---or at least not to the same extent.
 
@@
 
-We mobilize three distinct approaches to ask whether ticketing and police stops structure voter turnout, and whether these effects are unique for Black Americans.
-We look at national survey data, municipal-level finance data, and individual-level administrative records in a major American county to explore these effects.
-Each approach offers advantages and drawbacks; taken together, however, they dramatically advance our understanding of the political consequences of the most routine types of contact with the criminal legal system.
+We leverage three distinct approaches to ask whether ticketing and police stops structure voter turnout, and whether these effects are unique for Black Americans.
 
-## National Survey Data {-}
+Each approach offers advantages and drawbacks.
+Our individual-level analysis in Hillsborough County exploits unusually detailed public data, which allows for a precise causal analysis that cannot be conducted in counties that do not provide ticketing records with personally identifiable information or states that do not include self-reported race data in the voter file.
+In isolation, however, results from one county may not be generalizable to other U.S.
+counties.
 
-We begin by turning to the American National Election Studies 2020 Time Series data (ANES).
-The ANES has been fielded in every presidential election year since 1948 and is among the most widely-used tools for understanding American’s political beliefs and behaviors, including their relationship with the criminal legal system [@Walker2020].
-It is weighted to be nationally representative of all American adults.
-In both 2016 and 2020, the ANES added new survey questions about respondent’s encounters with the police and the criminal legal system.
-We focus in particular on two questions: *During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?*, and *Have you ever been arrested, or has that never happened to you?* We include the roughly 87 percent of respondents that answered both questions, giving us a sample size of 7,347 respondents, of whom just over 11% identified as Black.
+We include two additional analyses to test the generalizability of the results from Hillsborough County.
+First, we analyze change in municipal-level revenue from fees and fines and voter turnout, which allows us to expand our analysis outside of Hillsborough County to about nine thousand American municipalities.
+This test does not allow us to directly observe the causal mechanism we argue is at play (police stops influencing political socialization, which in turn drives individual voter turnout), and replaces individual ticketing events with less-precise budget data.
+Also, if interpreted in isolation, the municipal-level analysis would suffer from the ecological fallacy: it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
 
-We use the survey questions to test the effect of a police stop on voter turnout---and, specifically, whether the effect is different for Black respondents.
-We also test whether an arrest is associated in the 2020 ANES with a lower probability of voting as described in previous work.
-In addition to the respondent’s contact with the criminal legal system, we control for age; sex; income; party affiliation; and self-described ideology.
-Using the ANES, we test our first two hypotheses:
+Finally, data from the 2020 American National Election Studies allow us to observe how tickets and arrests differentially influence voting behavior at the individual level among a nationally representative sample, but survey data analysis is subject to the vulnerabilities detailed in our introduction (e.g.
+measurement bias).
+Nevertheless, it provides important national insight into the phenomena we observe locally in Hillsborough County.
 
-*Hypothesis 1*: Personal and proximal experience of police stops is demobilizing for non-Black respondents, and mobilizing for Black respondents, other things equal.
+Taken together, these approaches dramatically advance our understanding of the political consequences of the most routine types of contact with the criminal legal system.
 
-*Hypothesis 2*: Personal experience of an arrest is demobilizing for individuals of all races, other things equal.
+## Individual-Level Causal Effects of Ticketing {-}
 
-There is an important caveat to the use of the ANES survey---namely, while the police stop question asks whether the respondent *or anyone in their family* was stopped in the past year, the arrest question asks only about the individual respondent.
-While this may muddy the water between direct and proximal contact with the criminal legal system, we expect that the national survey data will give us some insight into the uniquely politicizing nature of police stops for Black Americans.
-
-## City-level relationship between voter turnout and fines and fees {-}
-
-After an examination of the cross-sectional national survey data, we turn to our nationwide analysis of the relationship between municipal revenue raised from fees and fines, and turnout in the 2018 federal election.
-Our data come from two primary sources: the US Census Bureau’s Census of Governments Data (COG), and registered voter files from L2 Political.
-
-**Census of Governments**: Every five years, the US Census Bureau collects data from governmental bodies around the country.
-We use two snapshots of the COG: one that covers the years 2008 -- 2012, and another that covers 2013 -- 2017.
-The COG asks municipalities to report how much revenue they collect from “penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation...
-and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).” We divide these amounts by the population to estimate the per-capita fees and fines revenue raised in each municipality.
-This data has been used as a proxy for the amount of tickets issued at the local level in scholarly research [see, for instance, @Goldstein2020; @Sances2017].
-
-The COG data are useful to isolate ticketing practices because other fines and fees (e.g.
-fines imposed at sentencing in state court, probation fees, conviction fees, public defender fees) are typically collected by county or state governments.
-The COG data only include local revenues, which means the share of fines revenue corresponds more directly to local police practices.
-Following the guidance of @Sances2017, we retain only municipalities with police and/or court systems, as these are the only municipalities capable of issuing tickets.
-We also only retain municipalities with populations of at least 2,500.
-
-**Registered Voter Files**: The COG data do not include estimates of turnout at the local level.
-To estimate local turnout, we leverage registered voter files provided by data vendor L2 Political.
-In Washington, DC, and every state in the country (with the exception of North Dakota) voters are required to register to vote prior to participating.
-These files are considered public record, and in most states contain information about each voter’s age, residential address, political affiliation, and participation history.
-L2 collects voter files from around the country and merges them with proprietary data that estimates other voter- and household-level characteristics such as race and education.
-L2 also geocodes voters’ residential addresses.
-
-We merge the geocoded voter files with “place” and “county subdivision” shapefiles published by the US Census Bureau.
-By aggregating individual-level records to the municipal level, we are able to estimate the number of registered voters and the number of ballots cast in every city in the country.
-Moreover, by using the racial estimates provided by L2 we can estimate the number of ballots cast by voters of each race in each city.
-While in a few states race is self-reported by voters, race is in most cases modeled by L2 using first, middle, and last name, as well as Census block demographic information.
-Although this is a commonly used way to determine voters’ races [@Imai2016], it is subject to some error.
-We assume, however, that after controlling for other municipality-level characteristics, the errors in these predictions will be uncorrelated with fees and fines collections.
-Put differently, although we acknowledge that these estimates are imprecise, we expect that these errors are effectively random.
-Further, as we show in the Supplemental Information, the estimated Black share of the electorate tracks very closely with the share of the citizen voting age population that is non-Hispanic Black.
-After accounting for state-level voter registration differentials, the mean absolute error between these two measures is 2.4% and is unrelated to per-capita fines and fees after controlling for other covariates (*p* = 0.92).
-The individual-level racial estimates, when aggregated to the municipal level, thus provide a reasonably unbiased picture of the municipal electorate.
-
-We calculate turnout by dividing the number of ballots cast according to L2 by the 5-year estimate of each municipality’s citizen voting-age population (CVAP) from the US Census Bureau.
-These estimates are available for individual racial groups.
-Because our turnout numerator and denominators come from different sources there is slight measurement error: our estimate indicates, for instance, that roughly 1 percent of municipalities had Black turnout above 100 percent.
-Where more votes were cast than the Census estimate for CVAP, we recode turnout as 100 percent.
-Our results do not change if we instead simply remove these municipalities, or use unmodified turnout estimates.
-
-**Estimation Strategy**: We begin by merging each municipality’s fees and fines per capita (that is, dollars per resident) from the 2012 COG to its turnout from the 2014 midterm election, and the 2017 COG to its 2018 turnout.
-Because this measure is highly right-skewed, we use the natural log of fees and fines per capita (plus 1, to account for municipalities that collected no fees and fines).
-We also control for other municipal and state characteristics: racial composition, population density, median income, collegiate education, median age, share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality’s revenue that comes from the state or federal government in the 2012 and 2017 COGs.
-We retain the 8,954 municipalities whose data is reported to the COG in both 2012 and 2017 and meet the other criteria noted above.
-
-The 5-year cycle of the COG does not neatly line up with the general 4-year cycle typical of American elections.
-The timing of the COG and midterm elections mean that our analytical strategy is conservative.
-If municipalities shift their fees and fines collections dramatically over the 2013 -- 2017 period, this shift may influence their 2014 turnout.
-However, we assume that turnout in 2014 will still be influenced by the policing practices of the 2008 -- 2012 period, while 2018 turnout will be largely influenced by the practices of the 2013 -- 2017 period.
-
-We run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
-Our national two-way fixed effect model allows us to test our first two hypotheses:
-
-*Hypothesis 3*: Increased reliance on fines and fees revenue at the city level reduces voter turnout at the city level.
-
-*Hypothesis 4*: The effect of the city-level relationship between fines and voter turnout is stronger for Black voters, given the historical and explicit racial injustice narratives used to explain these practices.
-
-## Individual-Level Effects of Ticketing {-}
-
-Our national, cross-sectional analyses offer novel insight into the political socialization of low-level police contact.
-They cannot, however, directly observe the causal mechanism we argue is at play: namely, that direct contact with the criminal legal system influences turnout.
-If interpreted in isolation, our national analysis would suffer from the ecological fallacy.
-In other words, it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
-Moreover, there are many other factors that could be at play.
-Increased fees and fines could be correlated with increased policing in general, for instance.
-We are also unable to isolate the individual-level effect of being ticketed on turnout using this setup.
-
-Additionally, the national analyses cannot distinguish personal contact from proximal contact (“having a loved one who is a custodial citizen without yourself having had contact” [@Walker2017]).
-Because existing research investigating the effect of proximal contact has produced mixed results [@Burch2014; @Lee2014; @Sugie2015; @White2019; @Walker2017; @Walker2020], we are unable to prove that personal police contact is the only dynamic driving effects observed in our national analysis.
-For that reason, we turn to individual-level data from Hillsborough County, Florida (home to Tampa).
-
-Hillsborough County is interesting for theoretical reasons: Tampa is in the top decile of municipalities in terms of fees and fines increase between the 2012 and 2017 COGs, and its population puts it in the top 1 percent of cities nationwide.
+First, we turn to individual-level data from Hillsborough County, Florida (home to Tampa).
+Hillsborough County is interesting for theoretical reasons: Tampa is in the top decile of municipalities in terms of fees and fines increase between the 2012 and 2017 Census of Governments datasets, and its population puts it in the top 1 percent of cities nationwide.
 It also has a relatively large Black population, allowing us to test for racial differences in the turnout effect of ticketing.
 
-Further, the Tampa Police Department was scrutinized by the Tampa Bay Times in 2015 for its relentless ticketing of Black bicyclists [@Zayas2015].
+Further, the Tampa Police Department was scrutinized by the *Tampa Bay Times* in 2015 for its relentless ticketing of Black bicyclists [@Zayas2015].
 This investigation catalyzed a U.S.
@@
 The county clerk makes information available about every traffic stop in the county going back to 2003.
-This data includes the name and date of birth of the individual stopped; the date of the offense; and the amount the individual paid for a ticket; and other information.
+This data includes the name and date of birth of the individual stopped; the date of the offense; the amount the individual paid for a ticket; and other information.
 
-To identify ticketed voters, we match the first and last names and dates of birth from court data against the Hillsborough County registered voter file.
+To identify ticketed voters, we match the first and last names and dates of birth from the stop data against the Hillsborough County registered voter file.
 Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status [see @Nyhan2017].
@@
 In short, any turnout difference between the treated voters and their controls is the causal effect of a police stop on turnout.
-It is important to note that our overall turnout effects are robust to much stricter assumptions.
-In the Supplementary Information we demonstrate that our primary reported results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
+Our overall turnout effects are robust to much weaker assumptions: in the Supplementary Information, we demonstrate that our overall turnout results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
 
-Our analytical approach thus incorporates two different causal approaches.
+Our analytical design thus incorporates two different causal approaches in order to improve the credibility of our identification assumptions.
 Leveraging pre-treatment turnout allows us to estimate a traditional difference-in-differences model.
 Difference-in-differences models assume that, in the absence of the treatment, any turnout gap between treated and control voters would have remained stable in the post-treatment period.
-While the validity of this assumption is commonly established by examining pre-treatment trends in turnout between the two groups, it can be improved upon by using the matching methodology described above.
+While the validity of this identification assumption is commonly established by examining pre-treatment trends in turnout between the two groups, it can be improved upon by using the matching methodology described above.
 In the case at hand, we both establish that the turnout of treated voters was mirrored by that of their control voters prior to treatment, *and* that the observable characteristics of treated and control voters are similar---thus lending credence to the assumption that this gap would have remained constant absent treatment.
-Finally, by drawing controls from the population of individuals who were ticketed in subsequent years, we also indirectly control for any unobserved characteristics associated with receiving a ticket.
+Finally, by drawing controls from the population of individuals who were ticketed in subsequent years (i.e.
+restricting the target population to people who are ticketed at some point), we also control for any unobserved characteristics associated with receiving a ticket.
 For a more detailed discussion of how matching can improve upon traditional difference-in-difference approaches when using panel data, see @Imai2020.
@@
 *$\beta$~2~Post Treatment~t~* measures whether turnout increased for controls in the first election following the treated voter’s stop, while *$\beta$~3~Treated~i~ × Post Treatment~t~* tests whether turnout changed differently for treated voters than their controls in the election following their police stop.
-*$\beta$~3~*, then, will capture the causal effect of a police stop on voter turnout.
-Finally, the matrix *$\delta$Z~i~* contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
-Equation 1 allows us to test Hypothesis 5:
+*$\beta$~3~*, then, will capture the causal effect of a police stop on voter turnout; it is the unit-specific quantity measured in our empirical estimand [@Lundberg2021].
+*$\beta$~4~Year~t~* captures year fixed-effects depending on the timing of the police stop, and the matrix *$\delta$Z~i~* contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
 
-*Hypothesis 5*: Being ticketed reduces an individual’s likelihood of turning out in the subsequent election.
+The empirical estimand is the voter turnout gap between Hillsborough County residents who have recently been ticketed and residents who will be ticketed in a future period, conditional on similar turnout in past elections and similar demographic characteristics.
+The theoretical estimand [@Lundberg2021] is the effect of police ticketing on the political socialization of ticketed individuals, which we proxy using their their voter turnout.
 
@@
 \beta_3Treated_{i}\times Post Treatment_{t} + \beta_4Treated_{i}\times Post Treatment_{t}\times Black_{i} +\\
-\delta{Y}_{i} + \delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
+\beta_5Year_{t} + \delta{Y}_{i} + \delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
 \end{gather}
 
-where *$\delta$Y~it~* includes the dummy for Black interacted with the treatment and post treatment dummies. Equation 2 allows us to test Hypothesis 6:
+where *$\delta$Y~it~* includes the dummy for Black interacted with the treatment and post treatment dummies separately.
 
-*Hypothesis 6*: The effect of being ticketed on an individual’s voter turnout is less negative / more positive if that individual is Black.
+Here, the empirical and theoretical estimands are simply modified to accommodate racial difference; we measure the turnout gap between Black people who have been ticketed and Black people who will be ticketed in a future period.
+Thus, the theoretical estimand is the effect of ticketing on the political socialization (and connected voter turnout) of Black ticketed individuals.
 
-<!-- Because Tampa holds off-year local elections, we are able to test whether ticketed voters target officials who are able to change local police practices.
-@Laniyonu2019 gives us reason to believe that the effect should be stronger for local elections.
+## Voter turnout and municipal fines and fees collections {-}
 
-*Hypothesis 7*: Any potential mobilizing turnout effect for Black voters in Tampa is stronger for local (mayoral) elections, since those elections directly affect police practices. -->
+Next, we turn to our nationwide analysis of the relationship between municipal revenue raised from fees and fines and turnout.
+Our data come from two primary sources: the US Census Bureau’s Census of Governments Data (COG), and registered voter files from L2 Political.
+
+**Census of Governments**: Every five years, the US Census Bureau collects data from governmental bodies around the country.
+We use two waves of the COG: one that covers the years 2008 -- 2012, and another that covers 2013 -- 2017.
+The COG asks municipalities to report how much revenue they collect from “penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation...
+and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).” We divide these amounts by the population to estimate the per-capita fees and fines revenue raised in each municipality.
+This data has been used as a proxy for the amount of tickets issued at the local level in scholarly research [see, for instance, @Goldstein2020; @Sances2017].
+
+The COG data are useful to isolate ticketing practices because other fines and fees (e.g.
+fines imposed at sentencing in state court, probation fees, conviction fees, public defender fees) are typically collected by county or state governments.
+The COG data only include local revenues, which means the share of fines revenue corresponds more directly to local police practices.
+Following the guidance of @Sances2017, we retain only municipalities with police and/or court systems, as these are the only municipalities capable of issuing tickets.
+We also only retain municipalities with populations of at least 2,500.
+
+**Registered Voter Files**: The COG data do not include estimates of turnout at the local level.
+To estimate local turnout, we leverage registered voter files provided by data vendor L2 Political.
+In Washington, DC, and every state in the country (with the exception of North Dakota) voters are required to register to vote prior to participating.
+These files are considered public record, and in most states contain information about each voter’s age, residential address, political affiliation, and participation history.
+L2 collects voter files from around the country and merges them with proprietary data that estimates other voter- and household-level characteristics such as race and education.
+L2 also now geocodes voters’ residential addresses.
+In the post-2018 file, L2 was able to geocode more than 99% of voters.
+
+To construct municipality-level turnout in 2018, we start by merging the geocoded voter files with “place” and “county subdivision” shapefiles published by the US Census Bureau.
+These divisions correspond to the governmental bodies who report to the COG.
+By aggregating individual-level records to the municipal level, we are able to estimate the number of registered voters and the number of ballots cast in every city in the country.
+Moreover, by using the racial estimates provided by L2 we can estimate the number of ballots cast by voters of each race in each city.
+While in a few states race is self-reported by voters, race is in most cases modeled by L2 using first, middle, and last name, as well as Census block demographic information.
+Although this is a commonly used way to determine voters’ races [@Imai2016], it is subject to some error.
+We assume, however, that after controlling for other municipality-level characteristics, the errors in these predictions will be uncorrelated with fees and fines collections.
+Put differently, although we acknowledge that these estimates are imprecise, we expect that these errors are effectively random.
+As we show in the Supplemental Information, the estimated Black share of the electorate in the post-2018 file tracks very closely with the share of the citizen voting age population that is non-Hispanic Black.
+After accounting for state-level voter registration differentials, the mean absolute error between these two measures is 2.4 percentage points and is unrelated to per-capita fines and fees after controlling for other covariates (*p* = 0.92).
+The individual-level racial estimates, when aggregated to the municipal level, thus provide a reasonably unbiased picture of the municipal electorate.
+
+The process for calculating the number of ballots cast in each municipality in 2014 is slightly different.
+L2 did not provide the latitude and longitude for voters in the post-2014 voter file, but rather geocoded voters to their home Census block.
+These blocks are directly aggregated to the 2014 place and county subdivision level.
+Some voters in the post-2014 file are not coded to their block.
+To identify these voters’ municipalities, we merge records from the post-2014 file to the post-2018 file using the registration address in each file.
+Using both the L2 coded data and the merged address data, we obtain the Census block for 98.3% of voters in the post-2014 file.
+
+We calculate turnout by dividing the number of ballots cast according to L2 by the 5-year estimate of each municipality’s citizen voting-age population (CVAP) from the US Census Bureau.
+These estimates are available for individual racial groups.
+Because our turnout numerator and denominators come from different sources, there is slight measurement error: our estimate indicates, for instance, that roughly 1 percent of municipalities had Black turnout above 100 percent.
+Where more votes were cast than the Census estimate for CVAP, we recode turnout as 100 percent.
+Our results do not change if we instead simply remove these municipalities, or use unmodified turnout estimates.
+
+**Estimation Strategy**: We begin by merging each municipality’s fees and fines per capita (that is, dollars per resident) from the 2012 COG to its turnout from the 2014 midterm election, and the 2017 COG to its 2018 turnout.
+Because this measure is highly right-skewed, we use the natural log of fees and fines per capita (plus 1, to account for municipalities that collected no fees and fines).
+We also control for other municipal and state characteristics: racial composition, population density, median income, collegiate education, median age, and share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality’s revenue that comes from the state or federal government in the 2012 and 2017 COGs.
+We retain the 8,954 municipalities whose data is reported to the COG in both 2012 and 2017 and meet the other criteria noted above; these constitute the target population.
+
+The 5-year cycle of the COG does not neatly line up with the general 4-year cycle typical of American elections.
+The timing of the COG and midterm elections mean that our analytical strategy is conservative.
+If municipalities shift their fees and fines collections dramatically over the 2013 -- 2017 period, this shift may influence their 2014 turnout.
+However, we assume that turnout in 2014 will still be influenced by the policing practices of the 2008 -- 2012 period, while 2018 turnout will be largely influenced by the practices of the 2013 -- 2017 period.
+
+We run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
+These empirical estimands allow us to investigate our theoretical estimand; namely, the city-wide political-socialization effects of increased fines and fees collections proxied by voter turnout.
+
+## National Survey Data {-}
+
+Next, we turn to the American National Election Studies 2020 Time Series data (ANES).
+The ANES has been fielded in every presidential election year since 1948 and is among the most widely-used tools for understanding American’s political beliefs and behaviors, including their relationship with the criminal legal system [@Walker2020].
+It is weighted to be nationally representative of all American adults.
+In both 2016 and 2020, the ANES added new survey questions about respondent’s encounters with the police and the criminal legal system.
+We focus in particular on two questions: *During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?*, and *Have you ever been arrested, or has that never happened to you?* We include the roughly 87 percent of respondents that answered both questions, giving us a sample size of 7,347 respondents, of whom just over 11% identified as Black.
+
+We use these survey questions to make descriptive inferences about how stops and arrests affect the voting behavior of the general population.
+The first descriptive theoretical estimand is the gap between the voter turnout rate of individuals who were recently stopped by the police or who have ever been arrested, and another is whether stops or arrests uniquely influence the political behavior of Black Americans.
+In addition to the respondent’s contact with the criminal legal system, we control for age; sex; income; education; party affiliation; self-described ideology; and reported 2016 turnout.
+
+There is an important caveat to the use of the ANES survey---namely, while the police stop question asks whether the respondent *or anyone in their family* was stopped in the past year, the arrest question asks only about the individual respondent.
+While this may muddy the water between direct and proximal contact with the criminal legal system, we expect that the national survey data will give us some insight into the uniquely politicizing nature of police stops for Black Americans.
 
@@
 
-As discussed above, we begin by testing the relationship between police stops and turnout in the 2020 election, and then move to testing the relationship between fees and fines at the municipal level.
-While both tests give us insight into the political ramifications of low-level police contact, their cross-sectional nature cannot establish causality.
-To investigate causality, we also examine whether the turnout of individuals stopped by the police before an election was different than those stopped after the election in Hillsborough County, Florida.
+As discussed above, we begin by examining whether the turnout of individuals ticketed before an election was different from those ticketed after the election in Hillsborough County, Florida.
+Next, we test the relationship between fines and fees revenue reliance and voter turnout at the municipal level.
+We also test the relationship between police stops and turnout in the 2020 election using survey data.
 
-## National Survey Data {-}
+## Individual-Level Results {-}
 
-In this section we make use of the American National Election Studies 2020 Time Series Data (ANES).
-The test for this section is simple: we ask whether, after controlling for standard covariates, having personal or proximal contact with a police stop in the previous 12 months is associated with whether a respondent voted in the 2020 presidential election.
-We also ask whether this relationship was different for Black and non-Black respondents.
-We also use the ANES data to reconfirm prior literature demonstrating that higher-level contact with the criminal legal system is associated with lower turnout, as these relationships could have changed in the aftermath of the widespread protests following the police killing of George Floyd in 2020.
+To directly observe the effect of being stopped by the police on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
+As discussed above, we match individuals who were ticketed between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.^[Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
+The full sample is used in the actual matching process.]  Matching is done with replacement and ties are not broken.
+This means that some treated voters have multiple controls; the regression weights are calculated to allow for this possibility.
+In Table \ref{tab:balance} we present the results of the matching algorithm.
+As the table demonstrates, the selected control voters are very similar to the treated voters.
 
-Roughly 15 percent of non-Black respondents reported a police stop in the preceding 12 months, while the same was true for more than 22 percent of Black respondents.
-In Figure \ref{fig:anes} we present the results of our econometric models.
-In the left-hand panel, we show the predicted turnout of respondents who answered “yes” or “no” to the question *During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?* The right-hand panel, meanwhile, plots these relationships for respondents who answered “yes” or “no” to the question *Have you ever been arrested, or has that never happened to you?*.
-These are the predicted probabilities after controlling for respondents’ race / ethnicity; age; party; ideology; income; and education.
-The full regression table can be found in the Supplementary Information..
+Table 1 About Here
 
-```{r anes-cross, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:anes}Predicted Turnout, 2020", fig.pos = "!htpb", fig.align = "center"}
-load("temp/anes_plot.rdata")
-print(p2)
-```
-Figure \ref{fig:anes} demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (*p* = 0.006).
-The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (*p* = 0.52).
-Importantly, this effect is not a remnant of a white--nonwhite divide.
-As we show in the Supplementary Information, police stops were not differently related to turnout for Latinos than for non-Latinos; nor did they impact turnout differently for Asians than for non-Asians.
-The ANES results point, then, to the fact that police stops are uniquely associated with higher turnout for Black respondents.
+It is worth noting that voters who were ticketed between 2012 and 2020 were far more likely to be Black and male than the general electorate, and live in Census block groups with moderately lower incomes.
 
-The second panel of Figure \ref{fig:anes} shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
-Importantly, the interaction between arrest status and the respondent’s race was not statistically significant.
-In other words, although police stops seem to be uniquely mobilizing for Black Americans, we fail to uncover evidence that arrests differentially structured subsequent Black- and non-Black turnout.
+In Figure \ref{fig:did1}, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped.
+In the top row, we present the turnout in 2008--2014 of the individuals stopped between 2012 and 2014 and their controls; the second row shows the 2010--2016 turnout for individuals stopped between 2014 and 2016 and their controls; and the third shows the treatment effect for those stopped in the 2 years prior to the 2018 midterms.
+Finally, in the bottom row, we present the overall turnout effects for these three elections.
+The first election following a treated voter’s stop is denoted as *t = 0* while the years in which *t* is less than zero are the periods prior to the stop.
 
-These cross-sectional results cannot establish causality.
-It is possible that Black respondents who had been stopped by the police (or had family members who experienced a stop) differed from non-Black respondents with such contact in ways that cannot be captured by the survey data.
-However, our findings are consistent with a causal story that police stops are mobilizing for Black Americans---but that this is not the case for higher-level contact such as arrests.
+Figure 1 About Here
+
+Figure \ref{fig:did1} makes a number of things immediately apparent.
+First, we can see that for both Black and non-Black voters the parallel trends assumption is satisfied.
+Because we matched treated and control voters based on turnout prior to the ticket, this is by design.
+Secondly, Figure \ref{fig:did1} provides preliminary visual evidence of the demobilizing effects of police stops in Hillsborough County.
+However, as the figure also makes clear, it seems that the negative effects are concentrated in the lower-salience midterm elections; there is little evidence of turnout effects in the 2016 presidential election.
+
+Table \ref{tab:dind-table} formalizes the final row of Figure \ref{fig:did1} into an ordinary least squares regression.
+Models 1 and 2 show our overall causal effect, while models 3 and 4 allow for the possibility that a ticket differentially mobilizes Black voters.
+In models 1 and 3, we include only the treatment, timing, and race dummies, while the full set of covariates used for the matching procedure are included in models 2 and 4.
+The empirical estimands are *Treated × Post Treatment* and *Treated × Post Treatment × Black*.
+In models 1 and 2, *Treated × Post Treatment* measures the overall treatment effect, and in models 3 and 4 it measures the treatment effect for non-Black voters.
+*Treated × Post Treatment × Black* measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
+
+Table 2 About Here
+
+As both Figure \ref{fig:did1} and Table \ref{tab:dind-table} make clear, police tickets meaningfully depressed turnout.
+In models 1 and 2, the estimated overall treatment effect is -1.5 percentage points.
+In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---non-Black turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
+Although the treatment effect is still substantively quite large for Black individuals, Hillsborough County Black voters' turnout in federal elections was not as negatively impacted by police contact as that of non-Black individuals.
 
@@
 
-```{r cross-18, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:mef-2018}Predicted Turnout, 2018", fig.pos = "H", fig.align = "center"}
-load("temp/mef_to.rdata")
-print(p2)
-```
+Figure 2 About Here
 
-As Figure \ref{fig:mef-2018} makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 2.5 percentage points over the interdecile range, after controlling for the other covariates.
+As Figure \ref{fig:mef-2018} makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 1.5 percentage points over the interdecile range, after controlling for the other covariates.
 The opposite is true for Black voters: over the same range, Black turnout *increases* by roughly 2.4 percentage points.
@@
 The results of these models can be found in Table \ref{tab:twfe}.
+The average municipality included in this analysis raised $2.17 in fees and fines per resident in 2012, and the average municipality increased this per-capita figure by $0.47 between 2012 and 2017.
+Just over 10% of municipalities raised no revenue from fees and fines in either year.
+
+Table 3 About Here
+
+The results of the two-way fixed effects model are different from what we saw in the 2018 cross-sectional approach; namely, Table \ref{tab:twfe} indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not significantly impact Black turnout.
+The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.04 percentage points.
+
+## National Survey Data {-}
+
+In this section we make use of the American National Election Studies 2020 Time Series Data (ANES).
+The first test is simple: we ask whether, after controlling for standard covariates, having personal or proximal contact with a police stop in the previous 12 months is associated with whether a respondent voted in the 2020 presidential election.
+We also ask whether this relationship was different for Black and non-Black respondents.
+Finally, we use the ANES data to reconfirm prior literature demonstrating that higher-level contact with the criminal legal system is associated with lower turnout, as these relationships could have changed in the aftermath of the widespread protests following the police murder of George Floyd in 2020.
+
+Roughly 15 percent of non-Black respondents reported a police stop in the preceding 12 months, while the same was true for more than 22 percent of Black respondents.
+In Figure \ref{fig:anes} we present the results of our econometric models.
+In the left-hand panel, we show the predicted turnout of respondents who answered “yes” or “no” to the question *During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?* The right-hand panel, meanwhile, plots these relationships for respondents who answered “yes” or “no” to the question *Have you ever been arrested, or has that never happened to you?*.
+These are the predicted probabilities after controlling for respondents’ race / ethnicity; age; party; ideology; income; education; and 2016 turnout.
+The full regression table can be found in the Supplementary Information..
+
+Figure 3 About Here
+
+Figure \ref{fig:anes} demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (*p* = 0.005).
+The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (*p* = 0.27).
+Importantly, this effect is not a remnant of a white--nonwhite divide.
+As we show in the Supplementary Information, police stops were not differently related to turnout for Latinos than for non-Latinos; nor did they impact turnout differently for Asians than for non-Asians.
+The ANES results point, then, to the fact that police stops are uniquely associated with higher turnout for Black respondents.
+
+The second panel of Figure \ref{fig:anes} shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
+Importantly, the interaction between arrest status and the respondent’s race was not statistically significant.
+In other words, although police stops seem to be uniquely mobilizing for Black Americans, we fail to uncover evidence that arrests differentially structured subsequent Black and non-Black turnout.
+
+This theoretical estimand is descriptive, and cross-sectional results cannot establish causality.
+It is possible that Black respondents who had been stopped by the police (or had family members who experienced a stop) differed from non-Black respondents with such contact in ways that cannot be captured by the survey data.
+However, our findings are consistent with a causal story that police stops are uniquely mobilizing for Black Americans---but this is not the case for higher-level contact, such as arrests.
+
+### Discussion {-}
+
+While existing sociological and political science literature has examined the rise and collateral consequences of fines and fees as well as the effects of criminalization on political socialization, no study has investigated the causal relationship between ticketing and voter turnout.
+Additionally, our study is among the first to use individual-level administrative data to investigate the relationship between criminalization and political participation.
+
+Given how widespread police stops are and their relationship to racial injustice, their political implications demand close study.
+Accordingly, we investigate this question from a variety of perspectives, using multiple data sources and empirical approaches.
+What we find complicates our understanding of how lower-level police contact affects political participation.
+The national survey data and cross-sectional municipal-level analysis indicate that police contact is associated with higher turnout for Black Americans, and either unrelated or negatively related to turnout for others.
+Our causal models tell a slightly different story---they fail to uncover mobilizing effects for Black Americans.
+Nevertheless, our causal models *do* indicate that police stops are less demobilizing for Black individuals than for others.
+In this sense, our results all point in the same direction.
+Based on these three independent approaches, we conclude that the political consequences of police stops are unique for Black Americans---and that they are less demobilizing for Black Americans than others.
+Additionally, as @Walker2020a suggests, ticketed Black individuals may be politically mobilized for activities other than voting not observed in this study, such as contacting elected representatives or volunteering for campaigns.
+
+Our individual-level analysis based on Hillsborough County, Florida, advances our understanding of this dynamic while raising new questions.
+On the one hand, the causal results are highly robust, and the ticketing data allows us to identify the treatment fairly precisely.
+On the other hand, these are the only results in which police stops are associated with a *decrease* in turnout for Black individuals.
+This may be because this analysis tests the impact of direct contact with the police, rather than direct *or* proximal contact, as the ANES questions do.
+It may be because we can isolate the effect of a police stop from other, broader changes that may be correlated with increased fees and fines revenue in the municipal-level data.
+Or it may point to unique political circumstances surrounding race, policing, and political participation in Hillsborough County.
+We look forward to future scholarship that replicates and extends these Hillsborough County results.
+Nevertheless, that police stops are less demobilizing for Black Floridians in Hillsborough County---an effect that does not extend to other nonwhite residents---provides support for our general thesis that the political interpretation of these contacts with the criminal legal system are unique for Black Americans.
+
+The difference between the cross-sectional and two-way fixed effects models using the municipality-level data is somewhat surprising.
+There are a few potential explanations for this mismatch.
+First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes in the two-way fixed effects models are smaller or not statistically significant.
+Along a similar vein, it is possible that a mobilizing effect of ticketing for Black voters in the city-level analysis is offset by higher-intensity forms of criminal legal contact, such as arrest and incarceration.
+The bulk of existing literature suggests that incarceration discourages political participation, and it is not unreasonable to assume that cities that ramp up ticketing of Black residents also ramp up arrest and incarceration of Black residents.
+If these phenomena coincide, that could explain why the city-level analysis produced no statistically significant effect for Black voters---the personally mobilizing effect of ticketing could be counterbalanced by the proximal chilling effect of incarceration, and because the city-level analysis is not as temporally sensitive, it is more difficult to isolate the effect of ticketing.
+At the same time, @Harris2020 indicates that when municipalities increase their fees and fines collections, relatively more *white* individuals are ticketed.
+@Shoub2020 demonstrates the corollary: when municipalities stop fewer motorists, the decrease is concentrated among white individuals.
+Existing research, then, indicates that a relatively constant share of the Black population is stopped by the police; changes in fees and fines collections largely impacts the white population.
+The overall changes in revenue we observe in our two-way fixed effects models might reflect changes largely for the white populations in these municipalities, while ticketing---and turnout---remain more or less constant for Black populations.
+We were unable to incorporate a race-specific measure of police stops or measures of local incarceration or policing trends due to a lack of consistent data nationwide.
+
+Finally, Sances and You [-@Sances2017: 1091]---the paper that originally detailed the relationship between fees and fines collections and municipalities’ racial composition using the Census of Governments data---specifically notes that they did not exploit the panel setup of the COG because of “little variation within a city in terms of revenues from fines.” Instead, they present only the results of a cross-sectional study.
+Here, we present both the cross-sectional and panel results, acknowledging that each have limitations but that, taken together, they shed light on the unique politicization of fees and fines for Black Americans.
+
+Our findings have several implications for political sociology and political science scholarship.
+While existing literature suggests that the most disruptive forms of criminal legal contact (i.e.
+criminal convictions and incarceration) consistently discourage voting [@Lerman2014; @Burch2011; @White2019a], research regarding police stops has produced more mixed results [@Laniyonu2019].
+We extend this theory to police ticketing, the most common form of police contact in America, and find that ticketing generally reduces turnout.
+For Black voters, however, our findings suggest that ticketing can be politically mobilizing.
+Particularly following the rise of the Black Lives Matter movement in 2013, our findings constitute new evidence in support of our theory that ticketing is distinct from other forms of criminal legal contact and therefore catalyzes different political behaviors among Black voters, who are disproportionately affected by both ticketing and criminalization in general.
+
+In this sense, our analysis points to a political contestation of criminal legal policy, a phenomenon that aligns with dozens of recent campaigns to reform local fines and fees practices (or abolish them entirely).^[See https://finesandfeesjusticecenter.org/clearinghouse.]  We know that increased fines and fees result from political economy (i.e.
+austerity at the federal level), but our analysis suggests that this is a “two way street” wherein people who are harmed by policing practices can be politically socialized into resistance.
+
+**Limitations**: Because our individual-level administrative data analysis is limited to Hillsborough County where fines collections increased over the period, we do not have a good sense of how the city-level revenue reliance trend interacts with the individual experience of being ticketed in areas where fees and fines are constant or decreasing.
+Is ticketing more politically mobilizing for Black voters in cities that are palpably dialing up their revenue collection efforts?
+Future research could test this hypothesis at the individual level within cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.
+
+Additionally, in our analysis of Hillsborough County voters, we do not look at people who were not registered to vote in 2018.
+Because we cannot tell whether unregistered individuals who were stopped in Hillsborough County were unregistered because they were *ineligible* to do so (by virtue of living in a different county or being a non-citizen, for instance) or chose to eschew electoral politics, our analysis is necessarily limited to individuals who were registered to vote.
+This likely makes our results conservative: we cannot capture the lost participation of individuals who would have registered and voted if they were not stopped by the police.
+
+**Future research**: This work looks at the difference between the political behavior of Black and non-Black Americans.
+Future work should explore variation *within* the Black community.
+When is this sort of contact mobilizing?
+For whom?
+Can organizers build on this potential for broad-based political action?
+We were unable to test whether what we observed was simply *decreased* demobilization, or whether some subgroups of the Black population were mobilized while others were demobilized.
+Put differently: it could be the case that ticketing is demobilizing for most voters of all races, but that a subset of the Black population is affirmatively mobilized, leading to lower group-level demobilization.
+Scholars should also investigate the interactive effects of criminal legal contact, asking whether police stops result in different political behavior for formerly incarcerated individuals than individuals with no other contact with the system.
+
+Finally, we are sensitive to the fact that although administrative data provides real-world evidence of actual behavior, such an approach limits our ability to understand the psychological processes in play.
+This means that although we demonstrate that police stops are demobilizing, future work must further investigate how stops are interpreted by individuals and translated into political behavior.
+
+Although we have generated new evidence suggesting that police stops and related exploitative ticketing practices may mobilize Black voters, we emphasize that this finding does not redeem or justify such police practices.
+Black Americans already suffer from disproportionate police contact and the racial wealth gap, and racist revenue-motivated ticketing only increases the burden on Black communities nationwide.
+Policymakers should work to ensure that Black Americans no longer have to struggle to enjoy the same political power as whites---to that end, the current trend of voting rights restriction policies across the country is especially pernicious.
+Even if Black Americans understand the ballot box as one tool they can use to limit the state’s power to exploit and harm them, policymakers should still feel an obligation to support voting rights protections and stop disproportionate ticketing in Black communities.
+
+\newpage
+
+# References {-}
+
+<div id="refs"></div>
+
+\newpage
+
+# Tables {-}
+
+\begin{singlespace}
+\input{"../temp/balance_table.tex"}
+\end{singlespace}
+
+\begin{singlespace}
+\input{"../temp/dind_reg_y.tex"}
+\end{singlespace}
 
@@
 
-The results of the two-way fixed effects model are different than what we saw in the 2018 cross-sectional approach; namely, while Table \ref{tab:twfe} indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not significantly impact Black turnout.
-The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.06 percentage points.
+# Figures {-}
 
-In Table \ref{tab:coarser}, we re-estimate the model from Table \ref{tab:twfe} but coarsen the data.
-Here, the dependent variable of interest is binary: we test whether turnout changed for municipalities who increased their per-capita fees and fines collections differently than municipalities where collections stayed the same or decreased.
-Municipalities that increased their per-capita fees and fines are considered “treated.”
-
-\begin{singlespace}
-\input{"../temp/coarser_reg_clean.tex"}
-\end{singlespace}
-
-The coefficient on *Treated × 2018* indicates that non-Black turnout dropped by about 0.5 percentage points in municipalities where fees and fines collections increased, relative to other municipalities.
-While this coefficient is slightly *positive* for Black voters, it is not statistically significantly different from 0.
-In other words, both Tables \ref{tab:twfe} and \ref{tab:coarser} indicate that increased fees and fines collections decrease non-Black turnout but have no impact on Black turnout.
-
-## Individual-Level Results {-}
-
-Thus far, we have shown that voter turnout decreased in municipalities that increased fines and fees collections.
-We argue that this relationship is causal: increased fees and fines collections means that more residents have direct interactions with the criminal legal system.
-Based on prior literature, we assume there are indirect effects as well, as more residents know a family or community member who has been ticketed.
-While the national analysis gives us great breadth and an increased understanding of how this plays out across the country, municipal-level data leaves us unable to directly observe the causal mechanisms at play.
-
-To directly observe the effect of being stopped by the police on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
-As discussed above, we match individuals who were ticketed between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.^[Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
-The full sample is used in the actual matching process.]  Matching is done with replacement and ties are not broken.
-This means that some treated voters have multiple controls; the regression weights are calculated to allow for this possibility.
-In Table \ref{tab:balance} we present the results of the matching algorithm.
-As the table demonstrates, the selected control voters are very similar to the treated voters.
-
-\begin{singlespace}
-```{r baltab-chunk, echo = F, warning = F}
-t <- readRDS("temp/balance_table_y.rds")
-j <- knitr::kable(t, booktabs = T, caption = "(\\#tab:balance) Balance Table", linesep = "",
-                  escape = F)  %>%
-  kable_styling(latex_options = c("hold_position"))
-
-j
-```
-\end{singlespace}
-
-It is worth noting that voters who were stopped between 2012 and 2018 were far more likely to be Black and male than the general electorate, and live in Census block groups with moderately lower incomes.
-Unsurprisingly, they were also stopped at higher rates in the pre-treatment period than those never stopped between 2012 and 2018.
-
-While Table \ref{tab:balance} indicates that our treatment voters and their matches are substantially similar to their matches, the validity of the difference-in-differences design requires that any turnout gap between treatment and control voters be comparable in the baseline period.
-In Figure \ref{fig:did1}, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped.
-The first election following a treated voter’s stop is denoted as *t = 0* while the years in which *t* is less than zero are the periods prior to the stop.
-This means that for someone stopped in 2013 (and their controls), *t* is 0 in 2014, while *t* is equal to 0 in 2018 for an individual stopped between the 2016 and 2018 elections.
-
-```{r did1, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
+```{r did1, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
 p2 <- readRDS("temp/stopped_any_time_y.rds")
@@
 
-Figure \ref{fig:did1} makes a number of things immediately apparent.
-First, we can see that for both Black and non-Black voters the parallel trends assumption is satisfied.
-Of course, because we matched treated and control voters based on turnout prior to the ticket, this is unsurprising.
+```{r cross-18, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:mef-2018}Predicted Turnout, 2018", fig.pos = "H", fig.align = "center"}
+load("temp/mef_to.rdata")
+print(p2)
+```
 
-Table \ref{tab:dind-table} formalizes Figure \ref{fig:did1} into an ordinary least squares regression.
-Model 1 shows our overall causal effect, while Model 2 allows for the possibility that a ticket differentially mobilizes Black voters.
-The coefficients of note are *Treated × Post Treatment* and *Treated × Post Treatment × Black*.
-In models 1 and 2, *Treated × Post Treatment* measures the overall treatment effect, and in models 3 and 4 it measures the treatment effect for non-Black voters.
-*Treated × Post Treatment × Black* measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
-
-\begin{singlespace}
-\input{"../temp/dind_reg_y.tex"}
-\end{singlespace}
-
-As both Figure \ref{fig:did1} and Table \ref{tab:dind-table} make clear, police tickets meaningfully depressed turnout.
-In models 1 and 2, the estimated overall treatment effect is -1.5 percentage points.
-In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---nonBlack turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
-Although the treatment effect is still substantively quite large for Black individuals, the pattern follows our national analysis.
-It appears that, in Tampa and around the country, Black voters' turnout in federal elections is not as negatively impacted by police contact as that of non-Black individuals.
-
-<!-- As shown in model 5 and table XX, we find that being ticketed in the 90 days preceding a mayoral election in Tampa is demobilizing for Black voters, but not demobilizing for non-Black voters.
-Being ticketed decreased Black turnout by 0.5 percentage points.
--->
-
-### Discussion {-}
-
-While existing sociology and political science literature has examined the rise and collateral consequences of fines and fees as well as the effects of criminalization on political socialization, no study has investigated the causal relationship between ticketing and voter turnout.
-Additionally, our study is among the first to use individual-level administrative data to investigate the relationship between criminalization and political participation.
-
-We first used survey data collected in the American National Election Studies 2016 and 2020 datasets to show how, unlike arrests, ticketing can mobilize Black voters.
-We found that Black people who reported personal or proximal police contact with a police stop in the last 12 months were 0.5 pp more likely to vote compared to Black people who did not report such contact.
-Non-Black respondents demonstrated no statistically significant result for police stops.
-Meanwhile, both Black and non-Black people who had been arrested at any point were less likely to vote, and we did not find significant differences between racial groups’ behaviors in response to arrests.
-
-Next, we used a two-way fixed effects model to estimate the effect of increased fines and fees reliance at the city level on aggregate voter turnout in federal elections.
-We found that each 10 percent increase in fines and fees collected per resident is associated with a voter turnout decrease of about 0.06 percentage points, with no significant impact on Black turnout in particular---in other words, the demobilizing effect of ticketing increases at the city level is largely driven by non-Black voters.
-
-In order to directly observe the causal mechanism, we then conducted an individual-level analysis of ticketing and voting behavior in Hillsborough County, Florida.
-Using a difference-in-differences design, we found that individuals who were ticketed in the 90-day period preceding a federal election were 1.7 percentage points less likely to vote compared to individuals who were ticketed following the election.
-The effect was smaller for Black individuals (1 percentage point less likely), which is consistent with our hypothesis that Black political responses to ticketing should be distinct from whites (and more mobilized by comparison).
-
-We were somewhat surprised by the differences that arose between our two sets of findings---our city-level analysis using a two-way fixed effects model did not produce statistically significant results for Black voters.
-We think there are a few potential explanations for this mismatch.
-
-First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes are smaller or not statistically significant.
-Along a similar vein, it’s possible that the effect size for Black voters in the city-level analysis is affected by higher-intensity forms of criminal legal contact, such as arrest and incarceration.
-The bulk of existing literature suggests that incarceration discourages political participation, and it’s not unreasonable to assume that cities that ramp up ticketing of Black residents also ramp up arrest and incarceration of Black residents.
-If these phenomena coincide, that could explain why the city-level analysis produced no statistically significant effect for Black voters---the personally mobilizing effect of ticketing could be counterbalanced by the proximal chilling effect of incarceration, and because the city-level analysis is not as temporally sensitive, it’s more difficult to isolate the effect of ticketing.
-
-That said, @Sances2017 specifically note that they didn't exploit the panel setup of the COG because of little variation between the 2007-2012 COG to the 2012-2017 one, and so they just stuck to cross sectional.
-The positive effect for Black turnout in Figure 2 is consistent with our Tampa analysis and doesn't totally contradict the TWFE.
-
-Our findings point to several implications for political sociology and political science scholarship.
-While existing literature suggests that the most disruptive forms of criminal legal contact (i.e.
-criminal convictions and incarceration) consistently discourage voting [@Lerman2014; @Burch2011; @White2019a], research regarding police stops has produced more mixed results [@Laniyonu2019].
-We extend this theory to police ticketing, the most common form of police contact in America, and find that city-level increases in ticketing generally reduce turnout.
-For Black voters, however, our findings suggest that ticketing can be politically mobilizing.
-Particularly following the rise of the Black Lives Matter movement in 2013, our findings constitute new evidence in support of our theory that ticketing is distinct from other forms of criminal legal contact and therefore catalyzes different political behaviors among Black voters, who are disproportionately affected by both ticketing and criminalization in general.
-
-**Limitations**: Because our individual-level analysis is limited to Hillsborough County, we don’t have a good idea of whether the city-level revenue reliance trend interacts with the individual experience of being ticketed.
-Is ticketing more politically mobilizing for Black voters in cities that are palpably dialing up their revenue collection efforts?
-Future research could test this hypothesis in cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.
-
-Additionally, in our analysis of Hillsborough County voters, we don’t look at people who weren’t registered to vote in 2018.
-This means that there could be some proportion of ticketed Black motorists who are now less likely to register to vote in the first place, for example.
-In other words the mobilization effect in our findings only applies to people who were registered to vote---we are unable to make claims about whether being ticketed makes an individual more likely to register to vote.
-
-**Future research**: Future work should explore whether ticketing can be mobilizing for Black individuals under circumstances.
-We were unable to test whether what we're observing is just *decreased* demobilization, or whether some subgroups of the Black population were mobilized while others were demobilized.
-In other words, it could be the case that ticketing is demobilizing for all voters, but there is a subset of Black voters who are *mobilized* by this, though they aren't a large enough group to counteract the demobilization of other Black people.
-
-Unlike previous studies using survey data, we are unable to tell whether individuals in Tampa have non-ticketing criminal legal exposure.
-Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.
-
-<!--  [Laniyonu] - [he writes that block groups with higher Black pop and higher SQF density voted at higher rates for Thompson, the candidate who pledged not to implement SQF reform, but who was Black.
-The descriptive representation from Sances2017 kind of covers for this, tactically speaking - electing Black politicians should reduce fines and fees abuses.
-But in Tampa, the current mayor, Jane Castor, was the police chief until 2015 --- which overlaps with the treatment period in our analysis.
-One voter told the Tampa Bay Times that he voted against Castor as “payback” for the racist ticketing practices she oversaw, and the article notes that her opponent won five majority-Black precincts [@Frago2019].
-In 2015, Castor even released a statement as police chief supporting the racist ticketing, insisting that “Many individuals receiving bike citations are involved in criminal activity.” -->
-
-\newpage
-
-# References {-}
-
-<!-- 
-[stuff on Black MC]
-https://press.princeton.edu/books/paperback/9780691025438/behind-the-mule
-
-https://journals.sagepub.com/doi/abs/10.1177/0011128799045004006?casa_token=C1tIg2PtoRQAAAAA:jiOyqKAFal3XdvfUC7BI6ItWF4rJOFNuj-FhTScVU-vXfrpW1wduVWp-aXtGdzq8EnaDVC4sbTbj
-
-https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1745-9125.2002.tb00962.x?casa_token=CAPT_XZTho4AAAAA:EVzYhsgW-c44zwpabCYoP8QtZ3-6YNws9vjdBgjhau8f-ehG-GwkS6h0MdhfYncmV3t60_WUCykNUw
-
-https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1745-9125.2009.00159.x -->
+```{r anes-cross, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:anes}Predicted Turnout, 2020", fig.pos = "!htpb", fig.align = "center"}
+load("temp/anes_plot.rdata")
+print(p2)
+```

### 2021-07-23 markdown/not_blind.tex
submission docs

--- 2021-05-24 markdown/draft_paper.tex
@@
 ]{article}
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amsmath}
 \usepackage{ifxetex,ifluatex}
@@
   \usepackage{textcomp} % provide euro and other symbols
-  \usepackage{amssymb}
 \else % if luatex or xetex
@@
 \hypersetup{
-  pdftitle={Policing for Profit and the Mobilization of Black Voters},
+  pdftitle={Ticketing and Turnout: How Policing for Profit Shapes Democratic Participation},
   pdfauthor={Jonathan Ben-Menachem; Kevin Morris},
@@
 \usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs}
+\usepackage{longtable,booktabs,array}
 \usepackage{calc} % for calculating minipage widths
@@
 
-\title{Policing for Profit and the Mobilization of Black Voters}
+\title{Ticketing and Turnout: How Policing for Profit Shapes Democratic Participation}
 \author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
-\date{May 24, 2021}
+\date{July 21, 2021}
 
@@
 Despite this burgeoning literature, no research has directly investigated how police ticketing practices affect political participation.
-We use three approaches to answer this question: national survey data, a city-level analysis using Census of Governments data and the national voter file, and individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019.
+We use three approaches to answer this question: we leverage individual-level ticketing data from Hillsborough County, Florida between 2010 and 2020, a city-level analysis using Census of Governments data and the national voter file, and national survey data.
+In Hillsborough County, we estimate that being ticketed decreases an individual's likelihood of voting in federal elections by 1.7 percentage points, but depressive effects are smaller for Black residents.
+Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 was associated with a roughly 0.04 percentage point turnout decrease but was not associated with any change in Black turnout.
 The survey data show that Black people who report that they or a family member were recently stopped by police are more likely to vote than those who reported no such contact.
-Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.04 percentage point turnout decrease but was not associated with Black turnout.
-In Tampa, Florida, we estimate that being ticketed decreases an individual's likelihood of voting in federal elections by 1.7 percentage points, but depressive effects are smaller for Black residents.
 
@@
 
-Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities' alienation from government.
+Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities' alienation from government (\protect\hyperlink{ref-Sanders2017}{Sanders and Conarck 2017}; \protect\hyperlink{ref-McCoy2015}{McCoy 2015}; \protect\hyperlink{ref-Shaer2019}{Shaer 2019}).
 After Michael Brown was killed by the Ferguson Police Department in 2014, a US Department of Justice investigation into the city's police and courts demonstrated that the municipality was engaged in a practice that advocates now refer to as ``policing for profit.'' The city's reliance on fines and fees to fund government functions grew from 13 to 23 percent of the total budget between fiscal years 2012 and 2015.
@@
 It wasn't just a Ferguson problem, or even a Missouri problem.
-American cities' reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (\protect\hyperlink{ref-Singla2020}{Singla, Kirschner, and Stone 2020}; \protect\hyperlink{ref-Harris2017}{Harris et al.
-2017}).
-
-Work exploring how criminalization directly and indirectly influences political participation has exploded in recent years.
+American cities' reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (\protect\hyperlink{ref-Singla2020}{Singla, Kirschner, and Stone 2020}; \protect\hyperlink{ref-Harris2017}{A.
+Harris et al.
+2017}; \protect\hyperlink{ref-Harris2020}{A.
+P.
+Harris, Ash, and Fagan 2020}).
+
+Work exploring how criminalization directly and indirectly influences political participation has exploded in recent years following path-breaking work from political sociologists Chris Uggen and Jeff Manza (\protect\hyperlink{ref-Uggen2002}{Uggen and Manza 2002}; \protect\hyperlink{ref-Manza2006}{Manza and Uggen 2006}).
 Scholars have found that criminal legal contact (i.e.~arrest, conviction, incarceration) consistently discourages voting (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}; \protect\hyperlink{ref-Burch2011}{Burch 2011}; \protect\hyperlink{ref-White2019a}{White 2019b}).
 Such work has largely focused on the effects of highly disruptive contact with the criminal legal system such as incarceration and felony convictions (\protect\hyperlink{ref-Burch2014}{Burch 2014}; \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}).
+While ticketing involves potentially negative interactions with the state, it does not necessarily carry the disruptive consequences of a felony conviction and might thus politicize Americans in unique ways.
 Building on recent theoretical work from \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020a}) and an analysis of the historical context of fees and fines collections in the United States, this paper is the first to explicitly theorize how local ticketing practices shape the political socialization of ticketed individuals.
+We argue that ticketing depresses voter turnout overall, but also catalyzes a ``linked fate'' political analysis among Black voters that either causes increased turnout or mitigates the turnout reductions observed among non-Black individuals.
+
 Additionally, our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
-
-In addition to our theoretical contribution, the use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures political participation.
+The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures political participation.
 Past work looking at the individual-level effects of low-level contact has relied entirely on survey or qualitative data (e.g.
@@
 Existing research allows for the testing of specific psychological mechanisms and personal interpretations of criminal legal contact, but does not allow us to generalize more broadly.
-As Weaver and Lerman (\protect\hyperlink{ref-Weaver2010}{2010, 821}) note, it may also introduce measurement bias.
+As Weaver and Lerman (\protect\hyperlink{ref-Weaver2010}{2010}: 821) note, it may also introduce measurement bias.
 Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to police ticketing.
-The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of the quarter-million individuals ticketed over a 6 year period---a far larger pool than even the most robust surveys.
-
-Before turning to the administrative data, we begin with a novel analysis of 2020 national survey data regarding voters' experience with police stops.
+The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of a quarter-million individuals ticketed over a 6 year period---a far larger pool than even the most robust surveys.
+
+We use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were ticketed between the 2012 and 2018 elections.
+By matching individual voters who were ticketed to similar voters who were ticketed at later points and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout.
+We find that being ticketed reduces the chance that an individual will turn out in the subsequent election, but that this effect is smaller for Black voters.
+
+To test the generalizability of our findings in Hillsborough County, we leverage two different datasets that are national in scope.
+First, we join fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for thousands of municipalities around the country.
+While we find that increased fees and fines likely cause lower turnout among non-Black Americans, we find no effect of fees and fines on Black turnout.
+
+Second, we conduct a novel analysis of 2020 national survey data regarding voters' experience with police stops.
 We find that Black respondents who reported personal or proximal experience with police stops in the last 12 months are more likely to vote than Black people who did not, while we find no statistically significant relationship between stops and voting among non-Black respondents.
-
-Next, we join fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for thousands of municipalities around the country.
-While we find that increased fees and fines likely cause lower turnout among non-Black Americans, we find no effect of fees and fines on Black turnout.
-
-Because our national analyses do not allow us to directly observe the causal effect of police ticketing on voter turnout, we use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were ticketed between the 2012 and 2018 elections.
-By matching individual voters who were ticketed to similar voters who were ticketed at later points and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout.
-We find that being ticketed reduces the chance that an individual will turn out in the subsequent election, and that this effect is smaller for Black voters.
+While both the municipal-level and survey data present some drawbacks relative to the individual-level administrative data, their national scope provides helpful corroboration for the unique turnout effects of tickets for Black Americans observed in Hillsborough County.
 
@@
 Our findings complicate existing theories of how criminalization politically socializes Americans, and Black Americans in particular (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
-Additionally, while all forms of criminalization likely contribute to a subjective experience of alienation or group-level exclusion among Black Americans that is well-documented in sociological scholarship (\protect\hyperlink{ref-Bell2017}{Bell 2017}; \protect\hyperlink{ref-Desmond2016}{Desmond, Papachristos, and Kirk 2016}), our contribution emphasizes the need for further research regarding how different forms of criminalization affect group-level perceptions of government and resultant political behavior.
-Accordingly, we propose a new theory explaining how ticketing may uniquely catalyze mobilizing narratives of racial injustice.
+Additionally, while all forms of criminalization likely contribute to a subjective experience of alienation or group-level exclusion among Black Americans that is well-documented in sociological scholarship (\protect\hyperlink{ref-Bell2017}{Bell 2017}; \protect\hyperlink{ref-Desmond2016}{Desmond, Papachristos, and Kirk 2016}), our contribution emphasizes the need for further research regarding how different forms of criminalization affect group-level perceptions of government and resultant political behaviors.
+Accordingly, we propose a new theory explaining how ticketing may uniquely catalyze Black political participation.
 Our findings are relevant for interdisciplinary scholars of crime, race, politics, political economy, social movements, and policing.
@@
 An emerging political science literature directly investigates the relationship between criminalization and political behavior.
-Additionally, sociologists have incorporated contemporary fines and fees practices into a broader empirical-historical theory of racialized punishment policy (\protect\hyperlink{ref-Harris2010}{Harris, Evans, and Beckett 2010}; \protect\hyperlink{ref-Friedman2020}{Friedman 2020}).
-
-In order to theorize how fines and fees affect political behavior, we consider (1) how criminalization directly shapes the electorate, (2) the existing scholarly understanding of the influence of criminalization on political socialization, and (3) how contemporary ticketing practices are tied to a longer legacy of racist exploitation and thus ripe for political mobilization around narratives of racial injustice.
-
-\hypertarget{criminalization-and-the-american-electorate}{%
-\subsection*{Criminalization and the American electorate}\label{criminalization-and-the-american-electorate}}
-\addcontentsline{toc}{subsection}{Criminalization and the American electorate}
-
-The American criminal legal system directly shapes the American electorate and excludes Black voters.
-Today, more than five million Americans are legally barred from voting due to a felony conviction, and one in every sixteen Black Americans of voting age is disenfranchised (\protect\hyperlink{ref-Uggen2020}{Uggen et al.
-2020}).
-Following the implementation of the Fifteenth Amendment in 1870, over a dozen U.S.
-states passed laws denying voting rights to people who were convicted of felonies.
-In their analysis of how racial threat catalyzes felon disenfranchisement, \protect\hyperlink{ref-Behrens2003}{Behrens, Uggen, and Manza} (\protect\hyperlink{ref-Behrens2003}{2003}) found that increases in the share of a state's prison population that is nonwhite drastically increases the likelihood of legislation permanently disenfranchising people convicted of felonies.
-As \protect\hyperlink{ref-Shofner1963}{Shofner} (\protect\hyperlink{ref-Shofner1963}{1963}) notes, felony disenfranchisement has often been tied explicitly to the increased presence of Black Americans in the electorate.
-
-Notably, fines and fees legally disenfranchise Americans: 48 states and the District of Columbia authorize some form of wealth-based penal disenfranchisement (\protect\hyperlink{ref-Colgan2019}{Colgan 2019}).
-More specifically, many states require payment of fees as a condition of criminal legal supervision or the payment of all legal financial obligations as a condition of completing a sentence, and failure to comply with supervision or sentence completion conditions can be a barrier to voting rights restoration.
-Such political barriers also disproportionately affect Black people.
-In Alabama, for example, Black people with felony convictions applying to have their voting rights restored were 26 percentage points more likely to have their application denied over outstanding fines and fees (\protect\hyperlink{ref-Meredith2017}{Meredith and Morse 2017}).
-
-The role of fines and fees in the context of felony disenfranchisement has recently garnered national attention.
-After Floridians passed Amendment 4 to restore voting rights to individuals with felony convictions in 2018, Florida Republicans passed legislation requiring these individuals to pay off the fines and fees associated with their original sentence.
-Because Florida does not maintain good records on who owes how much, the new law has proved to be a major hurdle for potential voters.
-As \protect\hyperlink{ref-Morris2021}{Morris} (\protect\hyperlink{ref-Morris2021}{2021}) argues, this could have severe implications for the future democratic participation of those excluded anew from the electorate after the state passed the amendment.
+Additionally, sociologists have incorporated contemporary fines and fees practices into a broader empirical-historical theory of racialized punishment policy (\protect\hyperlink{ref-Harris2010}{A.
+Harris, Evans, and Beckett 2010}; \protect\hyperlink{ref-Friedman2020}{Friedman 2020}).
+
+In order to theorize how fines and fees affect political behavior, we consider how criminalization directly shapes the electorate; the existing scholarly understanding of the influence of criminalization on political socialization; and how contemporary ticketing practices are tied to a longer legacy of racist exploitation and thus ripe for political mobilization around narratives of racial injustice.
 
@@
 
+The American criminal legal system directly shapes the American electorate and excludes voters.
+Today, more than five million Americans are legally barred from voting due to a felony conviction, and one in every sixteen Black Americans of voting age is disenfranchised (\protect\hyperlink{ref-Uggen2020}{Uggen et al.
+2020}).
+Notably, fines and fees legally disenfranchise Americans as well: 48 states and the District of Columbia authorize some form of wealth-based penal disenfranchisement (\protect\hyperlink{ref-Colgan2019}{Colgan 2019}).
+Many states require payment of fees as a condition of criminal legal supervision or the payment of all legal financial obligations as a condition of completing a sentence, and failure to comply with supervision or sentence completion conditions can be a barrier to voting rights restoration.
+
 Beyond de jure disenfranchisement, the spatial and racial concentration of criminalization influences affected communities' perceptions of government.
@@
 Research on legal cynicism has found that public perceptions of abusive police practices can reduce willingness to report crimes or cooperate with law enforcement (\protect\hyperlink{ref-Desmond2016}{Desmond, Papachristos, and Kirk 2016}; \protect\hyperlink{ref-Tyler2014}{Tyler, Fagan, and Geller 2014}).
+In short, the ``hidden curriculum'' (\protect\hyperlink{ref-Justice2014}{Justice and Meares 2014}; \protect\hyperlink{ref-Meares2017}{Meares 2017}) of the criminal legal system teaches Americans about their identities as citizens---even parts of their identities that have little to do with policing or incarceration.
+New evidence related to ticketing and legal estrangement has recently emerged: in a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government compared to residents who were not ticketed (\protect\hyperlink{ref-CarpenterII2019}{Carpenter II, Sweetland, and McDonald 2019}).
+
 Because police are the most visible agents of the state, perceptions of unfairness in policing can translate to a recognition of actual group-level structural exclusion from public institutions (\protect\hyperlink{ref-Bell2017}{Bell 2017}).
-New evidence related to ticketing and legal estrangement has recently emerged: in a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government compared to residents who were not ticketed (\protect\hyperlink{ref-CarpenterII2019}{Carpenter II, Sweetland, and McDonald 2019}).
-
-Sarah Brayne found related results in her analysis of survey data---as the intensity of criminal legal contact escalates (i.e.~stopped, arrested, convicted), people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions (\protect\hyperlink{ref-Brayne2014}{Brayne 2014}).
+Soss and Weaver explain how criminal legal contact shapes perceptions of government and political participation: ``interviewees have looked, not to City Hall, Congress, or political parties, but rather to their direct experiences with police, jails and prisons, welfare offices, courts, and reentry agencies as they sought to ground their explanations of how government works, what political life is like for them, and how they understand their own political identities'' (\protect\hyperlink{ref-Soss2017}{Soss and Weaver 2017}: 574).
+
+Sarah Brayne found related results in her analysis of survey data.
+As the intensity of criminal legal contact escalates (i.e.~stopped, arrested, convicted), people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions (\protect\hyperlink{ref-Brayne2014}{Brayne 2014}).
 She calls this phenomenon ``system avoidance,'' and while her analysis did not specifically assess voting behavior, her findings demonstrate how criminal legal contact can discourage Americans' participation in public institutions as well as how the effect may vary alongside the intensity of criminal legal intervention.
 Similarly, \protect\hyperlink{ref-Remster2018a}{Remster and Kramer} (\protect\hyperlink{ref-Remster2018a}{2018}) finds that men who return home from prison are more likely to avoid contact with their childrens' schools.
+Vesla Weaver and colleagues helpfully describe this form of self-preserving withdrawal from public institutions as a ``strategic retreat'' (\protect\hyperlink{ref-Weaver2020}{Weaver, Prowse, and Piston 2020}).
 
 In addition to influencing perceptions of government and participation in public institutions, recent scholarship indicates that criminalization influences political behavior.
-The ``hidden curriculum'' of the criminal legal system (\protect\hyperlink{ref-Justice2014}{Justice and Meares 2014}; \protect\hyperlink{ref-Meares2017}{Meares 2017}) teaches individuals about their position within the political system, and the criminal legal system consequently serves as a primary site of political socialization for convicted individuals and their families (e.g.
-\protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}).
-
 Using existing national survey data and extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
-Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a ``linked fate'' where ``one's individual opportunities are linked to the entire racial group'' (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014, 197}).
-Their interview data lead them to conclude that while criminal legal contact does increase perceptions of linked fate among Black respondents, ``a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing''---and interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}).
-
-Lerman and Weaver's finding has been corroborated by administrative data: Ariel White found that short jail sentences in Harris County, Texas reduced Black defendant turnout in subsequent elections by 13 percentage points---but the effect on white turnout was not statistically significant (\protect\hyperlink{ref-White2019}{White 2019a}).
+Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a ``linked fate'' where ``one's individual opportunities are linked to the entire racial group'' (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}: 197).
+Their interview data lead them to conclude that while criminal legal contact does increase perceptions of linked fate among Black respondents, ``a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing.'' Interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}).
+
+Lerman and Weaver's findings have been corroborated using administrative data: Ariel White found that short jail sentences in Harris County, Texas reduced Black defendant turnout in subsequent elections by 13 percentage points---but the effect on white turnout was not statistically significant (\protect\hyperlink{ref-White2019}{White 2019a}).
 Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level (\protect\hyperlink{ref-Burch2014}{Burch 2014}).
-
-Although most work documents a uniformly demobilizing effect from contact with the criminal legal system, recent work from Hannah Walker (\protect\hyperlink{ref-Walker2020}{2020b}, \protect\hyperlink{ref-Walker2020a}{2020a}) complicates this narrative by arguing that, when Black Americans understand their contact with the criminal legal system in the context of a narrative of racial injustice, such contact can actually prove mobilizing.
-She explains: ``experiences with punitive policies are subject to interpretation and, when understood through narratives of injustice, lead to wholly different participation outcomes than we usually predict'' (\protect\hyperlink{ref-Walker2020}{Walker 2020b, 132}).
-While she finds that this sense of injustice is especially likely to increase political participation in non-voting ways (such as attending a protest or signing a petition), the logic could extend to electoral participation as well given a strong narrative or relatively weak contact with the criminal legal system.
+These effects can also extend to family members, and the political consequences can be quite durable (\protect\hyperlink{ref-Morris2021}{Morris 2021}).
+
+Although most work documents how contact with the criminal legal system causes strategic retreat, recent work from Hannah Walker (\protect\hyperlink{ref-Walker2020}{2020b}, \protect\hyperlink{ref-Walker2020a}{2020a}) complicates this narrative.
+She argues that when Black Americans understand their contact with the criminal legal system in the context of a narrative of racial injustice, such contact can actually mobilize.
+She explains: ``experiences with punitive policies are subject to interpretation and, when understood through narratives of injustice, lead to wholly different participation outcomes than we usually predict'' (\protect\hyperlink{ref-Walker2020}{Walker 2020b}: 132).
+While she finds that this sense of injustice is especially likely to increase political participation in non-voting ways (such as attending a protest or signing a petition), the logic could extend to electoral participation as well given a relevant electoral context, strong injustice narrative, or relatively weak contact with the criminal legal system.
+Findings presented in \protect\hyperlink{ref-Laniyonu2019}{Laniyonu} (\protect\hyperlink{ref-Laniyonu2019}{2019}) provide support for this concept: concentrated Stop, Question, and Frisk (SQF) policing in New York City neighborhoods was associated with reduced turnout in federal midterm elections but increased turnout in presidential and mayoral primary elections.
+Laniyonu also uncovered an association regarding candidate choice---he demonstrates higher turnout for a candidate who opposed SQF policing and lower turnout for a candidate who supported it.
+In other words, low-level police contact mobilized voters to participate in a local election (which could plausibly affect police practices).
 
 Despite the growing body of high-quality scholarship on the democratic implications of the American criminal legal system, we still know remarkably little about the effects of the most routine sort of contact---police stops and tickets that do not result in an arrest.
-We leverage Walker's novel insights about the potentiality of a narrative of injustice to re-think how these sorts of contact with the state can structure political participation.
 
@@
 Cedric Robinson's articulation of racial capitalism offers a useful theoretical framework for interpreting the trajectory of American anti-Black political economy (\protect\hyperlink{ref-Robinson2000}{Robinson 2000}).
-Brittany Friedman theorizes fines and fees as a ``progression of racial capitalism penology,'' emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices (\protect\hyperlink{ref-Friedman2020}{Friedman 2020, 177}).
+Brittany Friedman theorizes fines and fees as a ``progression of racial capitalism penology,'' emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices (\protect\hyperlink{ref-Friedman2020}{Friedman 2020}: 177).
 Robinson argues that European industrial capitalism continued a longer political-economic trend of differentiating racial groups in order to dispossess them and exploit their labor.
@@
 The implementation of the Black Codes, convict leasing, and sharecropping systems marked a transition to a new stage of racial capitalism, wherein criminalization provided an easily-exploited labor supply that offset costs that the state incurred by coercing their labor (\protect\hyperlink{ref-Lichtenstein1996}{Lichtenstein 1996}; \protect\hyperlink{ref-Mancini1978}{Mancini 1978}).
-Contemporary fines and fees practices have been directly compared to sharecropping because both structures share ``a long-term pattern of financial exploitation based on race\ldots{} that limits the life-choices of the affected population'' (\protect\hyperlink{ref-Blessett2016}{Blessett and Box 2016, 113}).
+Contemporary fines and fees practices have been directly compared to sharecropping because both structures share ``a long-term pattern of financial exploitation based on race\ldots{} that limits the life-choices of the affected population'' (\protect\hyperlink{ref-Blessett2016}{Blessett and Box 2016}: 113).
 
 In the 20th century, residential segregation simultaneously fueled the racial wealth gap and ensured that criminalization was both spatially and racially concentrated (\protect\hyperlink{ref-Rothstein2017}{Rothstein 2017}; \protect\hyperlink{ref-Hinton2021}{Hinton and Cook 2021}).
-At the level of federal policy, racial threat and whites' attribution of criminality to Blackness (\protect\hyperlink{ref-Muhammad2010}{Muhammad 2010}) prompted a shift ``from the War on Poverty to the War on Crime'' wherein Black communities' demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration (\protect\hyperlink{ref-Hinton2017}{Hinton 2017}; \protect\hyperlink{ref-Vargas2017a}{Vargas and McHarris 2017}).
+At the level of federal policy, racial threat and whites' attribution of criminality to Blackness (\protect\hyperlink{ref-Muhammad2010}{Muhammad 2010}) prompted a shift from the War on Poverty to the War on Crime wherein Black communities' demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration (\protect\hyperlink{ref-Hinton2017}{Hinton 2017}; \protect\hyperlink{ref-Vargas2017a}{Vargas and McHarris 2017}).
 
@@
 \protect\hyperlink{ref-Sances2017}{Sances and You} (\protect\hyperlink{ref-Sances2017}{2017}), however, finds that the discriminatory imposition of tickets can be mitigated by descriptive representation (i.e.~Black elected officials): The positive association between cities' reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
+This result aligns with recent research demonstrating that states with more Black legislators spend less on corrections budgets; that racial disparities in arrests are reduced in municipalities represented by a majority-nonwhite city council; and that descriptive representation can reduce racial disparities in the criminal legal system (\protect\hyperlink{ref-Butler2011}{Butler and Broockman 2011}; \protect\hyperlink{ref-Gunderson2020}{Gunderson 2020}; \protect\hyperlink{ref-Eckhouse2016}{Eckhouse 2016}).
+It thus seems that the ballot box can be a site from which Black Americans can secure some protections against the most egregious forms of revenue extraction.
 
@@
 2020}), and a host of local analyses confirm the national finding (\protect\hyperlink{ref-Dunn2009}{Dunn 2009}; \protect\hyperlink{ref-Goncalves2020}{Goncalves and Mello 2020}; \protect\hyperlink{ref-Mughan2020}{Mughan 2020}).
-In criminal court proceedings, Black defendants tend to face more severe monetary sanctions (\protect\hyperlink{ref-Edwards2020}{Edwards and Harris 2020}; \protect\hyperlink{ref-Harris2011}{Harris, Evans, and Beckett 2011}), and a 2020 Federal Reserve survey found that five percent of white respondents reported ``unpaid legal expenses, fines, or court costs,'' whereas twelve percent of Black respondents reported such debt (\protect\hyperlink{ref-BoardofGovernorsoftheFederalReserveSystem2020}{Governors of the Federal Reserve System 2020}).
+In criminal court proceedings, Black defendants tend to face more severe monetary sanctions (\protect\hyperlink{ref-Edwards2020}{Edwards and Harris 2020}; \protect\hyperlink{ref-Harris2011}{A.
+Harris, Evans, and Beckett 2011}), and a 2020 Federal Reserve survey found that five percent of white respondents reported ``unpaid legal expenses, fines, or court costs,'' whereas twelve percent of Black respondents reported such debt (\protect\hyperlink{ref-BoardofGovernorsoftheFederalReserveSystem2020}{Governors of the Federal Reserve System 2020}).
 
@@
 
-Black Americans can therefore situate exploitative ticketing practices in a longer historical legacy of collective disparate treatment and violence at the hands of the state.
-We argue that Black voters' recognition of discriminatory ticketing practices facilitates a ``linked fate'' political analysis that motivates voting behavior distinct from other forms of criminalization, such as criminal conviction or incarceration.
-We expect both ticketing and incarceration to spark a recognition of ``a sense of injustice'' among Black Americans, but we argue that ticketing should ultimately mobilize Black voters (unlike incarceration, which discourages Black voters more than whites (\protect\hyperlink{ref-White2019}{White 2019a})).
-
-Ticketing produces substantively different experiences than being arrested or incarcerated.
-While tickets can lead to driver's license suspensions or, in a smaller subset of cases, nonpayment incarceration, tickets are generally far less disruptive than criminal convictions and prison terms, and we argue that this difference should lead to different political behaviors.
-For example, one participant in \protect\hyperlink{ref-Lerman2014}{Lerman and Weaver} (\protect\hyperlink{ref-Lerman2014}{2014}) who had served five years of probation after a criminal conviction reported, ``I feel like if I contact a senator or governor, they'll probably want to put me in jail and leave me as a troublemaker\ldots{} That's how I actually feel: `I better stay below the radar 'cause this guy's tryin' to start trouble''' (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014, 210}).
-While formerly incarcerated people or people who have experienced criminal legal supervision may avoid voting due to the same type of fear of state surveillance and control that motivates their avoidance of medical or educational institutions (\protect\hyperlink{ref-Brayne2014}{Brayne 2014}), we argue that being ticketed should not produce the same chilling effect---ticketing should not prompt Black people to use political withdrawal as a self-preservation strategy.
-
-Additionally, we argue that ``policing for profit''---the experience of being ticketed while a municipality is palpably ramping up its fines and fees practices to collect revenue---is also substantively distinct from the experience of being arrested or incarcerated.
+\hypertarget{theory}{%
+\section*{Theory}\label{theory}}
+\addcontentsline{toc}{section}{Theory}
+
+We argue that Black voters' recognition of discriminatory ticketing practices facilitates a linked fate political analysis that motivates voting behavior distinct from other forms of criminalization, such as criminal conviction or incarceration.
+We expect both ticketing and incarceration to spark a recognition of ``a sense of injustice'' among Black Americans (catalyzing ``linked fate''), but we argue that ticketing should ultimately mobilize Black voters---unlike incarceration, which discourages Black voters more than whites (\protect\hyperlink{ref-White2019}{White 2019a}).
+In other words, while incarceration may prompt Black voters' strategic retreat via linked fate, ticketing could produce the opposite effect.
+
+Ticketing is by far the most common form of criminal legal contact: in 2018, more than 24 million people experienced police contact in the context of a traffic stop, whereas about 5.17 million people are currently disenfranchised as a result of a felony conviction (\protect\hyperlink{ref-Harrell2020}{Harrell and Davis 2020}; \protect\hyperlink{ref-Uggen2020}{Uggen et al.
+2020}).
+At the same time, the most egregious local ticketing increases occurred largely over the past two decades (\protect\hyperlink{ref-Singla2020}{Singla, Kirschner, and Stone 2020}), and increases have been concentrated largely in Black municipalities (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
+These facts have been extensively discussed in mainstream media and should be widely known among Black voters (\protect\hyperlink{ref-Eligon2019}{Eligon 2019}; \protect\hyperlink{ref-Ehrenfreund2014}{Ehrenfreund 2014}).
+We also expect a larger share of more affluent Black voters to be affected by ticketing compared to other forms of criminalization---arrests and incarceration are most common among individuals experiencing poverty (\protect\hyperlink{ref-Looney2018}{Looney and Turner 2018}).
+Because perceptions of ``linked fate'' and related critiques of policing are even more salient among members of the Black middle class (\protect\hyperlink{ref-Dawson1995}{Dawson 1995}), we expect Black middle class voters to be mobilized by egregious ticketing practices.
+In other words, we argue that ticketing should ensnare more Black voters who are more likely to politicize the issue.
+
+The rise of the Black Lives Matter movement in 2013 constitutes a significant development for the political socialization of Black Americans, and many early Black Lives Matter protests either occurred in municipalities with exploitative ticketing practices or directly followed traffic stops that escalated into police violence (\protect\hyperlink{ref-Holpuch2015}{Holpuch 2015}; \protect\hyperlink{ref-LaFraniere2016}{LaFraniere and Smith 2016}).
+The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious.
+Furthermore, local Black Lives Matter activism can change police practices.
+One recent study found that census places that saw Black Lives Matter protests experienced a 15 to 20 percent decrease in police killings over the following five year period (\protect\hyperlink{ref-Campbell2021}{Campbell 2021}).
+It is possible that Black Lives Matter facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis---the movement arose shortly after fines and fees became a more salient and widespread threat to Black Americans' material security, and the BLM movement helped to publicize these disparities.
+Our understanding of the broader literature on criminalization and political behavior is that injustice narratives and the ``linked fate'' mechanism explain how Black individuals connect broad political trends to the ``micro'' experience of being personally stopped by police (and this micro-macro connection is what would motivate resultant voting behavior).
+We argue that exposure to BLM protests or messaging likely strengthened this process, which might explain potentially mobilizing effects of ticketing for Black voters.
+Based on the strength and accessibility of ticketing-related injustice narratives and the mobilization framework proposed by \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020a}), we expect that Black voters' political behavior in response to police ticketing will be distinct from the political behavior of white voters, and further that ticketing should mobilize Black voter turnout in cities that have recently ramped up ticketing.
+
+Of course, these disparities are also present in patterns of conviction and incarceration.
+We argue, however, that ``policing for profit''---the experience of being ticketed while a municipality is palpably ramping up its fines and fees practices to collect revenue---is substantively distinct from the experience of being arrested or incarcerated.
 In doing so, we extend Epp et al.'s theory of pretextual traffic stops politically socializing Black voters to the specific context of discriminatory police ticketing (\protect\hyperlink{ref-Epp2014}{Epp, Maynard-Moody, and Haider-Markel 2014}).
@@
 The city created a new traffic violations agency in 2015, spurring its yearly ticketing numbers to jump from around 32,000 to over 52,000.
-This financial aspect of ticketing should make it distinct from arrests and incarceration: much like the coercion of labor under the Black Codes, contemporary fines and fees practices are blatantly an effort to extract wealth from Black Americans.
-In other words, to the extent that mass incarceration could be justified using narratives of ``colorblind racism'' (i.e., high crime rates in Black communities results in more policing in those areas), racist ticketing practices do not enjoy the same rhetorical convenience.
-It may not be possible for revenue-motivated, racist ticketing to be reconciled with the idea that policing is primarily meant to improve public safety.
-
-Ticketing is by far the most common form of criminal legal contact; in 2018, more than 24 million people experienced police contact in the context of a traffic stop, whereas about 5.17 million people are currently disenfranchised as a result of a felony conviction (\protect\hyperlink{ref-Harrell2020}{Harrell and Davis 2020}; \protect\hyperlink{ref-Uggen2020}{Uggen et al.
-2020}).
-At the same time, the most egregious local ticketing increases occurred largely over the past two decades (\protect\hyperlink{ref-Singla2020}{Singla, Kirschner, and Stone 2020}), and increases have been concentrated largely in Black municipalities (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
-These facts have been extensively discussed in mainstream media and should be widely known among Black voters (\protect\hyperlink{ref-Eligon2019}{Eligon 2019}; \protect\hyperlink{ref-Ehrenfreund2014}{Ehrenfreund 2014}).
-We expect a larger share of more affluent Black voters to be affected by ticketing than other forms of criminalization---arrests and incarceration are most common among individuals experiencing poverty (\protect\hyperlink{ref-Looney2018}{Looney and Turner 2018}).
-Because perceptions of ``linked fate'' and related critiques of policing are even more salient among members of the Black middle class (\protect\hyperlink{ref-Dawson1995}{Dawson 1995}), we expect Black middle class voters to be mobilized by egregious ticketing practices.
-In other words, we argue that ticketing should ensnare more Black voters who are more likely to politicize the issue.
-
-Finally, the rise of the Black Lives Matter movement in 2013 constitutes a significant development for the political socialization of Black Americans, and the movement began in municipalities that targeted Black residents with tickets.
-The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious.
-Furthermore, local Black Lives Matter activism can change police practices.
-One recent study found that census places that saw Black Lives Matter protests experienced a 15 to 20 percent decrease in police killings over the following five year period (\protect\hyperlink{ref-Campbell2021}{Campbell 2021}).
-It's possible that Black Lives Matter facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis---the movement arose shortly after fines and fees became a more salient and widespread threat to Black Americans' material security, and many early Black Lives Matter protests either occurred in municipalities with exploitative ticketing practices or directly followed traffic stops that escalated into police violence (\protect\hyperlink{ref-Holpuch2015}{Holpuch 2015}; \protect\hyperlink{ref-LaFraniere2016}{LaFraniere and Smith 2016}).
-
-Today, fines and fees disproportionately affect Black people, and Black political mobilization appears to mitigate some of the most egregious ticketing practices (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
-As we have shown, contemporary fees and fines practices are just one iteration of a longer anti-Black project in the United States.
-Moreover, organizing in recent years by groups affiliated with the BLM movement have made this narrative easily accessible to citizens around the country.
-Based on the strength and accessibility of this narrative and the injustice framework proposed by \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020a}), we expect that Black voters' political behavior in response to police ticketing will be distinct from the political behavior of white voters, and further that ticketing should mobilize Black voter turnout in cities that have recently ramped up ticketing.
+This financial aspect of ticketing should make it distinct from arrests and incarceration: much like the coercion of labor under the Black Codes, contemporary fines and fees practices are blatant efforts to extract wealth from Black Americans.
+In other words, to the extent that mass incarceration could be justified using ``colorblind'' narratives (i.e., high crime rates in Black communities results in more policing in those areas), racist ticketing practices do not enjoy the same rhetorical convenience.
+It may not be possible for revenue-motivated, racist ticketing to be reconciled with the idea that policing is primarily meant to improve public safety---in other words, we expect ticketing to actively feel less fair and activate salient linked fate analyses among Black individuals.
+
+Finally, ticketing produces substantively different experiences than being arrested or incarcerated.
+While tickets can lead to driver's license suspensions or, in a smaller subset of cases, nonpayment incarceration, tickets are generally far less disruptive than criminal convictions and prison terms.
+People who have been convicted of a crime and incarcerated are relegated to an alternate political membership status that Reuben Jonathan Miller and Forrest Stuart call ``carceral citizenship,'' subjecting them to forms of supervision and sanction ``that are otherwise unavailable to {[}people{]} who have not been accused of a crime'' (\protect\hyperlink{ref-Miller2017}{Miller and Stuart 2017}: 536).
+Ticketing does not involve the same degree of surveillance and control as criminal conviction and incarceration.
+We argue that this difference in severity should lead to different political behaviors.
+For example, one participant in \protect\hyperlink{ref-Lerman2014}{Lerman and Weaver} (\protect\hyperlink{ref-Lerman2014}{2014}) who had served five years of probation after a criminal conviction reported, ``I feel like if I contact a senator or governor, they'll probably want to put me in jail and leave me as a troublemaker\ldots{} That's how I actually feel: `I better stay below the radar 'cause this guy's tryin' to start trouble''' (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}: 210).
+While formerly incarcerated people or people who have experienced criminal legal supervision may pursue a strategic retreat from voting (i.e.~withdraw in order to protect themselves), we argue that being ticketed should not produce the same chilling effect---ticketing should not prompt Black people to use political withdrawal as a self-preservation strategy.
+
+We argue that the combined psychological mechanism of ``linked fate'' and resultant political socialization among Black voters should elicit different responses to different forms of police contact---and our analysis constitutes a quantitative test of how the ``input'' of ticketing may produce a different behavioral ``output'' compared to arrest, conviction, or incarceration.
+Accordingly, we expect to see across multiple quantitative approaches that ticketing reduces voter turnout overall, but not for Black Americans---or at least not to the same extent.
 
@@
 
-We mobilize three distinct approaches to ask whether ticketing and police stops structure voter turnout, and whether these effects are unique for Black Americans.
-We look at national survey data, municipal-level finance data, and individual-level administrative records in a major American county to explore these effects.
-Each approach offers advantages and drawbacks; taken together, however, they dramatically advance our understanding of the political consequences of the most routine types of contact with the criminal legal system.
-
-\hypertarget{national-survey-data}{%
-\subsection*{National Survey Data}\label{national-survey-data}}
-\addcontentsline{toc}{subsection}{National Survey Data}
-
-We begin by turning to the American National Election Studies 2020 Time Series data (ANES).
-The ANES has been fielded in every presidential election year since 1948 and is among the most widely-used tools for understanding American's political beliefs and behaviors, including their relationship with the criminal legal system (\protect\hyperlink{ref-Walker2020}{Walker 2020b}).
-It is weighted to be nationally representative of all American adults.
-In both 2016 and 2020, the ANES added new survey questions about respondent's encounters with the police and the criminal legal system.
-We focus in particular on two questions: \emph{During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?}, and \emph{Have you ever been arrested, or has that never happened to you?} We include the roughly 87 percent of respondents that answered both questions, giving us a sample size of 7,347 respondents, of whom just over 11\% identified as Black.
-
-We use the survey questions to test the effect of a police stop on voter turnout---and, specifically, whether the effect is different for Black respondents.
-We also test whether an arrest is associated in the 2020 ANES with a lower probability of voting as described in previous work.
-In addition to the respondent's contact with the criminal legal system, we control for age; sex; income; education; party affiliation; self-described ideology; and reported 2016 turnout.
-Using the ANES, we test our first two hypotheses:
-
-\emph{Hypothesis 1}: Personal and proximal experience of police stops is demobilizing for non-Black respondents, and mobilizing for Black respondents, other things equal.
-
-\emph{Hypothesis 2}: Personal experience of an arrest is demobilizing for individuals of all races, other things equal.
-
-There is an important caveat to the use of the ANES survey---namely, while the police stop question asks whether the respondent \emph{or anyone in their family} was stopped in the past year, the arrest question asks only about the individual respondent.
-While this may muddy the water between direct and proximal contact with the criminal legal system, we expect that the national survey data will give us some insight into the uniquely politicizing nature of police stops for Black Americans.
-
-\hypertarget{city-level-relationship-between-voter-turnout-and-fines-and-fees}{%
-\subsection*{City-level relationship between voter turnout and fines and fees}\label{city-level-relationship-between-voter-turnout-and-fines-and-fees}}
-\addcontentsline{toc}{subsection}{City-level relationship between voter turnout and fines and fees}
-
-After an examination of the cross-sectional national survey data, we turn to our nationwide analysis of the relationship between municipal revenue raised from fees and fines, and turnout in the 2018 federal election.
+We leverage three distinct approaches to ask whether ticketing and police stops structure voter turnout, and whether these effects are unique for Black Americans.
+
+Each approach offers advantages and drawbacks.
+Our individual-level analysis in Hillsborough County exploits unusually detailed public data, which allows for a precise causal analysis that cannot be conducted in counties that do not provide ticketing records with personally identifiable information or states that do not include self-reported race data in the voter file.
+In isolation, however, results from one county may not be generalizable to other U.S.
+counties.
+
+We include two additional analyses to test the generalizability of the results from Hillsborough County.
+First, we analyze change in municipal-level revenue from fees and fines and voter turnout, which allows us to expand our analysis outside of Hillsborough County to about nine thousand American municipalities.
+This test does not allow us to directly observe the causal mechanism we argue is at play (police stops influencing political socialization, which in turn drives individual voter turnout), and replaces individual ticketing events with less-precise budget data.
+Also, if interpreted in isolation, the municipal-level analysis would suffer from the ecological fallacy: it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
+
+Finally, data from the 2020 American National Election Studies allow us to observe how tickets and arrests differentially influence voting behavior at the individual level among a nationally representative sample, but survey data analysis is subject to the vulnerabilities detailed in our introduction (e.g.~measurement bias).
+Nevertheless, it provides important national insight into the phenomena we observe locally in Hillsborough County.
+
+Taken together, these approaches dramatically advance our understanding of the political consequences of the most routine types of contact with the criminal legal system.
+
+\hypertarget{individual-level-causal-effects-of-ticketing}{%
+\subsection*{Individual-Level Causal Effects of Ticketing}\label{individual-level-causal-effects-of-ticketing}}
+\addcontentsline{toc}{subsection}{Individual-Level Causal Effects of Ticketing}
+
+First, we turn to individual-level data from Hillsborough County, Florida (home to Tampa).
+Hillsborough County is interesting for theoretical reasons: Tampa is in the top decile of municipalities in terms of fees and fines increase between the 2012 and 2017 Census of Governments datasets, and its population puts it in the top 1 percent of cities nationwide.
+It also has a relatively large Black population, allowing us to test for racial differences in the turnout effect of ticketing.
+
+Further, the Tampa Police Department was scrutinized by the \emph{Tampa Bay Times} in 2015 for its relentless ticketing of Black bicyclists (\protect\hyperlink{ref-Zayas2015}{Zayas 2015}).
+This investigation catalyzed a U.S.
+Department of Justice investigation and report, requested by Tampa's mayor and police chief.
+In other words, there is strong evidence suggesting both racist targeting of tickets and potential publicity to catalyze distinct Black voter responses to the abusive behavior during the same time frame as our national analysis.
+Ticketing has also been expressly politicized in Tampa: Jane Castor, who was elected mayor in 2019, was Tampa's police chief until 2015 and publicly defended her department's disproportionate ticketing of Black bicyclists before retracting her defense ahead of her mayoral campaign (\protect\hyperlink{ref-Carlton2018}{Carlton 2018}).
+Her opponent, banker and philanthropist David Straz, campaigned against red-light cameras and focused his outreach in Tampa's Black communities (\protect\hyperlink{ref-Frago2019}{Frago 2019}).
+
+Hillsborough County also makes a unique set of data publicly available.
+The county clerk makes information available about every traffic stop in the county going back to 2003.
+This data includes the name and date of birth of the individual stopped; the date of the offense; the amount the individual paid for a ticket; and other information.
+
+To identify ticketed voters, we match the first and last names and dates of birth from the stop data against the Hillsborough County registered voter file.
+Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status (see \protect\hyperlink{ref-Nyhan2017}{Nyhan, Skovron, and Titiunik 2017}).
+Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.\footnote{Because such frequent snapshots are not available from L2, we here use the registered voter file made freely available by the state of Florida.} We thus observe virtually all individuals who were registered to vote at any time during our period of study.
+Unique voter identification numbers allow us to avoid double-counting voters who are registered in multiple snapshots.
+We retain each voter's earliest record, and geocode voters to their home census block groups.
+Because we argue that police contact is the driving force behind any turnout effect, we remove tickets issued by red-light cameras.
+
+To improve the quality of the match between the two datasets, we remove all punctuation from all names and convert all names to lower-case.
+This means that a ``Jonathan O'Shea'' in one file would match a ``jonathan oshea'' in the other.
+\protect\hyperlink{ref-Meredith2014}{Meredith and Morse} (\protect\hyperlink{ref-Meredith2014}{2014}) develops a test for assessing the prevalence of false-positives in administrative record matching.
+We present the results of that test in the Supplementary Information.
+We likely have a false-positive match of around 0.03 percent, a figure we consider too low to impact our results meaningfully.
+
+By matching the police stop and voter records, we identify all voters who were ticketed between the 2012 and 2020 general elections (voters stopped between 2018 and 2020 elections serve only as controls).
+Voters are considered ``treated'' in the general election following their ticket.
+Treated voters are then matched to a control voter using a nearest-neighbor approach, with a genetic algorithm used to determine the best weight for each characteristic (\protect\hyperlink{ref-Sekhon2011}{Sekhon 2011}).
+Control voters are individuals who are stopped in the two years following the post-treatment election of the treated voters.
+Put differently, if a voter is stopped between 2012 and 2014, their control voter must be an individual stopped between the 2014 and 2016 elections.
+A voter cannot both be a treated and control voter for the same election; therefore, someone ticketed between the 2012 and 2014 elections and again between the 2014 and 2016 elections cannot serve as a control for anyone ticketed between 2012 and 2014.
+
+We match voters on individual-level characteristics (race / ethnicity; gender; party affiliation; age; number of traffic stops prior to the treatment period) and block group-level characteristics from the 2012 5-year ACS estimates (median income; share of the population with some college; unemployment rate).
+We match exactly on the type of ticket (civil / criminal infraction; whether they paid a fine; whether they were stopped by the Tampa Police Department) to ensure that treated and control voters receive the same treatment.
+Finally, we exactly match treated and control voters on their turnout in the three pre-treatment elections.
+
+We assume that after controlling for observable characteristics, past turnout, \emph{and} the unobservable characteristics associated with receiving a ticket, the timing of the ticket is effectively random.
+In short, any turnout difference between the treated voters and their controls is the causal effect of a police stop on turnout.
+Our overall turnout effects are robust to much weaker assumptions: in the Supplementary Information, we demonstrate that our overall turnout results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
+
+Our analytical design thus incorporates two different causal approaches in order to improve the credibility of our identification assumptions.
+Leveraging pre-treatment turnout allows us to estimate a traditional difference-in-differences model.
+Difference-in-differences models assume that, in the absence of the treatment, any turnout gap between treated and control voters would have remained stable in the post-treatment period.
+While the validity of this identification assumption is commonly established by examining pre-treatment trends in turnout between the two groups, it can be improved upon by using the matching methodology described above.
+In the case at hand, we both establish that the turnout of treated voters was mirrored by that of their control voters prior to treatment, \emph{and} that the observable characteristics of treated and control voters are similar---thus lending credence to the assumption that this gap would have remained constant absent treatment.
+Finally, by drawing controls from the population of individuals who were ticketed in subsequent years (i.e.~restricting the target population to people who are ticketed at some point), we also control for any unobserved characteristics associated with receiving a ticket.
+For a more detailed discussion of how matching can improve upon traditional difference-in-difference approaches when using panel data, see \protect\hyperlink{ref-Imai2020}{Imai, Kim, and Wang} (\protect\hyperlink{ref-Imai2020}{2020}).
+
+We then estimate the following equation:
+
+\begin{gather}
+\label{eq:1}
+v_{it}=\beta_0+\beta_1Treated_{i}+\beta_2Post Treatment_{t} + \nonumber \\
+\beta_3Treated_{i}\times Post Treatment_{t} + \\
+\beta_4Year_{t} + \delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
+\end{gather}
+
+Individual \emph{i}'s turnout (\emph{v}) in year \emph{t} is a function of the year and whether they were stopped by the police.
+In the equation, \emph{\(\beta\)\textsubscript{1}Treated\textsubscript{i}} measures the historical difference between treated voters and their controls.
+\emph{\(\beta\)\textsubscript{2}Post Treatment\textsubscript{t}} measures whether turnout increased for controls in the first election following the treated voter's stop, while \emph{\(\beta\)\textsubscript{3}Treated\textsubscript{i} × Post Treatment\textsubscript{t}} tests whether turnout changed differently for treated voters than their controls in the election following their police stop.
+\emph{\(\beta\)\textsubscript{3}}, then, will capture the causal effect of a police stop on voter turnout; it is the unit-specific quantity measured in our empirical estimand (\protect\hyperlink{ref-Lundberg2021}{Lundberg, Johnson, and Stewart 2021}).
+\emph{\(\beta\)\textsubscript{4}Year\textsubscript{t}} captures year fixed-effects depending on the timing of the police stop, and the matrix \emph{\(\delta\)Z\textsubscript{i}} contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
+
+The empirical estimand is the voter turnout gap between Hillsborough County residents who have recently been ticketed and residents who will be ticketed in a future period, conditional on similar turnout in past elections and similar demographic characteristics.
+The theoretical estimand (\protect\hyperlink{ref-Lundberg2021}{Lundberg, Johnson, and Stewart 2021}) is the effect of police ticketing on the political socialization of ticketed individuals, which we proxy using their their voter turnout.
+
+We also estimate Equation 2, in which the treatment effect is interacted with whether a voter is Black (\emph{\(\beta\)\textsubscript{4}Treated\textsubscript{i} × Post Treatment\textsubscript{t} × Black\textsubscript{i}}):
+
+\begin{gather}
+\label{eq:2}
+v_{it}=\beta_0+\beta_1Treated_{i}+\beta_2Post Treatment_{t} + \nonumber \\
+\beta_3Treated_{i}\times Post Treatment_{t} + \beta_4Treated_{i}\times Post Treatment_{t}\times Black_{i} +\\
+\beta_5Year_{t} + \delta{Y}_{i} + \delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
+\end{gather}
+
+where \emph{\(\delta\)Y\textsubscript{it}} includes the dummy for Black interacted with the treatment and post treatment dummies separately.
+
+Here, the empirical and theoretical estimands are simply modified to accommodate racial difference; we measure the turnout gap between Black people who have been ticketed and Black people who will be ticketed in a future period.
+Thus, the theoretical estimand is the effect of ticketing on the political socialization (and connected voter turnout) of Black ticketed individuals.
+
+\hypertarget{voter-turnout-and-municipal-fines-and-fees-collections}{%
+\subsection*{Voter turnout and municipal fines and fees collections}\label{voter-turnout-and-municipal-fines-and-fees-collections}}
+\addcontentsline{toc}{subsection}{Voter turnout and municipal fines and fees collections}
+
+Next, we turn to our nationwide analysis of the relationship between municipal revenue raised from fees and fines and turnout.
 Our data come from two primary sources: the US Census Bureau's Census of Governments Data (COG), and registered voter files from L2 Political.
@@
 L2 collects voter files from around the country and merges them with proprietary data that estimates other voter- and household-level characteristics such as race and education.
-L2 also geocodes voters' residential addresses.
-
-We merge the geocoded voter files with ``place'' and ``county subdivision'' shapefiles published by the US Census Bureau.
+L2 also now geocodes voters' residential addresses.
+In the post-2018 file, L2 was able to geocode more than 99\% of voters.
+
+To construct municipality-level turnout in 2018, we start by merging the geocoded voter files with ``place'' and ``county subdivision'' shapefiles published by the US Census Bureau.
 These divisions correspond to the governmental bodies who report to the COG.
@@
 Put differently, although we acknowledge that these estimates are imprecise, we expect that these errors are effectively random.
-As we show in the Supplemental Information, the estimated Black share of the electorate tracks very closely with the share of the citizen voting age population that is non-Hispanic Black.
-After accounting for state-level voter registration differentials, the mean absolute error between these two measures is 2.4\% and is unrelated to per-capita fines and fees after controlling for other covariates (\emph{p} = 0.92).
+As we show in the Supplemental Information, the estimated Black share of the electorate in the post-2018 file tracks very closely with the share of the citizen voting age population that is non-Hispanic Black.
+After accounting for state-level voter registration differentials, the mean absolute error between these two measures is 2.4 percentage points and is unrelated to per-capita fines and fees after controlling for other covariates (\emph{p} = 0.92).
 The individual-level racial estimates, when aggregated to the municipal level, thus provide a reasonably unbiased picture of the municipal electorate.
+
+The process for calculating the number of ballots cast in each municipality in 2014 is slightly different.
+L2 did not provide the latitude and longitude for voters in the post-2014 voter file, but rather geocoded voters to their home Census block.
+These blocks are directly aggregated to the 2014 place and county subdivision level.
+Some voters in the post-2014 file are not coded to their block.
+To identify these voters' municipalities, we merge records from the post-2014 file to the post-2018 file using the registration address in each file.
+Using both the L2 coded data and the merged address data, we obtain the Census block for 98.3\% of voters in the post-2014 file.
 
@@
 These estimates are available for individual racial groups.
-Because our turnout numerator and denominators come from different sources there is slight measurement error: our estimate indicates, for instance, that roughly 1 percent of municipalities had Black turnout above 100 percent.
+Because our turnout numerator and denominators come from different sources, there is slight measurement error: our estimate indicates, for instance, that roughly 1 percent of municipalities had Black turnout above 100 percent.
 Where more votes were cast than the Census estimate for CVAP, we recode turnout as 100 percent.
@@
 Because this measure is highly right-skewed, we use the natural log of fees and fines per capita (plus 1, to account for municipalities that collected no fees and fines).
-We also control for other municipal and state characteristics: racial composition, population density, median income, collegiate education, median age, share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality's revenue that comes from the state or federal government in the 2012 and 2017 COGs.
-We retain the 8,954 municipalities whose data is reported to the COG in both 2012 and 2017 and meet the other criteria noted above.
+We also control for other municipal and state characteristics: racial composition, population density, median income, collegiate education, median age, and share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality's revenue that comes from the state or federal government in the 2012 and 2017 COGs.
+We retain the 8,954 municipalities whose data is reported to the COG in both 2012 and 2017 and meet the other criteria noted above; these constitute the target population.
 
@@
 We run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
-Our national two-way fixed effect model allows us to test our next hypotheses:
-
-\emph{Hypothesis 3}: Increased reliance on fines and fees revenue at the city level reduces voter turnout at the city level among non-Black residents.
-
-\emph{Hypothesis 4}: Increased reliance on fines and fees revenue at the city level increases voter turnout at the city level among Black residents.
-
-\hypertarget{individual-level-effects-of-ticketing}{%
-\subsection*{Individual-Level Effects of Ticketing}\label{individual-level-effects-of-ticketing}}
-\addcontentsline{toc}{subsection}{Individual-Level Effects of Ticketing}
-
-Our national analyses offer novel insight into the political socialization of low-level police contact.
-They cannot, however, directly observe the causal mechanism we argue is at play: namely, that direct contact with the criminal legal system influences turnout.
-If interpreted in isolation, our national analysis would suffer from the ecological fallacy.
-In other words, it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
-Moreover, there are many other factors that could be at play.
-Increased fees and fines could be correlated with increased policing in general, for instance.
-Similarly, respondents in the ANES who report contact with a police stop may differ from those who report no such contact, even after controlling for available characteristics in the survey responses.
-
-Additionally, the national analyses cannot distinguish personal contact from proximal contact (``having a loved one who is a custodial citizen without yourself having had contact'' (\protect\hyperlink{ref-Walker2017}{Walker and García-Castañon 2017})).
-Because existing research investigating the effect of proximal contact has produced mixed results (\protect\hyperlink{ref-Burch2014}{Burch 2014}; \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}; \protect\hyperlink{ref-Sugie2015}{Sugie 2015}; \protect\hyperlink{ref-White2019}{White 2019a}; \protect\hyperlink{ref-Walker2017}{Walker and García-Castañon 2017}; \protect\hyperlink{ref-Walker2020}{Walker 2020b}), we are unable to prove that personal police contact is the only dynamic driving effects observed in our national analysis.
-For that reason, we turn to individual-level data from Hillsborough County, Florida (home to Tampa).
-
-Hillsborough County is interesting for theoretical reasons: Tampa is in the top decile of municipalities in terms of fees and fines increase between the 2012 and 2017 COGs, and its population puts it in the top 1 percent of cities nationwide.
-It also has a relatively large Black population, allowing us to test for racial differences in the turnout effect of ticketing.
-
-Further, the Tampa Police Department was scrutinized by the Tampa Bay Times in 2015 for its relentless ticketing of Black bicyclists (\protect\hyperlink{ref-Zayas2015}{Zayas 2015}).
-This investigation catalyzed a U.S.
-Department of Justice investigation and report, requested by Tampa's mayor and police chief.
-In other words, there is strong evidence suggesting both racist targeting of tickets and potential publicity to catalyze distinct Black voter responses to the abusive behavior during the same time frame as our national analysis.
-Ticketing has also been expressly politicized in Tampa: Jane Castor, who was elected mayor in 2019, was Tampa's police chief until 2015 and publicly defended her department's disproportionate ticketing of Black bicyclists before retracting her defense ahead of her mayoral campaign (\protect\hyperlink{ref-Carlton2018}{Carlton 2018}).
-Her opponent, banker and philanthropist David Straz, campaigned against red-light cameras and focused his outreach in Tampa's Black communities (\protect\hyperlink{ref-Frago2019}{Frago 2019}).
-
-Hillsborough County also makes a unique set of data publicly available.
-The county clerk makes information available about every traffic stop in the county going back to 2003.
-This data includes the name and date of birth of the individual stopped; the date of the offense; and the amount the individual paid for a ticket; and other information.
-
-To identify ticketed voters, we match the first and last names and dates of birth from the stop data against the Hillsborough County registered voter file.
-Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status (see \protect\hyperlink{ref-Nyhan2017}{Nyhan, Skovron, and Titiunik 2017}).
-Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.\footnote{Because such frequent snapshots are not available from L2, we here use the registered voter file made freely available by the state of Florida.} We thus observe virtually all individuals who were registered to vote at any time during our period of study.
-Unique voter identification numbers allow us to avoid double-counting voters who are registered in multiple snapshots.
-We retain each voter's earliest record, and geocode voters to their home census block groups.
-Because we argue that police contact is the driving force behind any turnout effect, we remove tickets issued by red-light cameras.
-
-To improve the quality of the match between the two datasets, we remove all punctuation from all names and convert all names to lower-case.
-This means that a ``Jonathan O'Shea'' in one file would match a ``jonathan oshea'' in the other.
-\protect\hyperlink{ref-Meredith2014}{Meredith and Morse} (\protect\hyperlink{ref-Meredith2014}{2014}) develops a test for assessing the prevalence of false-positives in administrative record matching.
-We present the results of that test in the Supplementary Information.
-We likely have a false-positive match of around 0.03 percent, a figure we consider too low to impact our results meaningfully.
-
-By matching the police stop and voter records, we identify all voters who were ticketed between the 2012 and 2020 general elections (voters stopped between 2018 and 2020 elections serve only as controls).
-Voters are considered ``treated'' in the general election following their ticket.
-Treated voters are then matched to a control voter using a nearest-neighbor approach, with a genetic algorithm used to determine the best weight for each characteristic (\protect\hyperlink{ref-Sekhon2011}{Sekhon 2011}).
-Control voters are individuals who are stopped in the two years following the post-treatment election of the treated voters.
-Put differently, if a voter is stopped between 2012 and 2014, their control voter must be an individual stopped between the 2014 and 2016 elections.
-A voter cannot both be a treated and control voter for the same election; therefore, someone ticketed between the 2012 and 2014 elections and again between the 2014 and 2016 elections cannot serve as a control for anyone ticketed between 2012 and 2014.
-
-We match voters on individual-level characteristics (race / ethnicity; gender; party affiliation; age; number of traffic stops prior to the treatment period) and block group-level characteristics from the 2012 5-year ACS estimates (median income; share of the population with some college; unemployment rate).
-We match exactly on the type of ticket (civil / criminal infraction; whether they paid a fine; whether they were stopped by the Tampa Police Department) to ensure that treated and control voters receive the same treatment.
-Finally, we exactly match treated and control voters on their turnout in the three pre-treatment elections.
-
-We assume that after controlling for observable characteristics, past turnout, \emph{and} the unobservable characteristics associated with receiving a ticket, the timing of the ticket is effectively random.
-In short, any turnout difference between the treated voters and their controls is the causal effect of a police stop on turnout.
-It is important to note that our overall turnout effects are robust to much stricter assumptions.
-In the Supplementary Information we demonstrate that our overall turnout results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
-
-Our analytical approach thus incorporates two different causal approaches.
-Leveraging pre-treatment turnout allows us to estimate a traditional difference-in-differences model.
-Difference-in-differences models assume that, in the absence of the treatment, any turnout gap between treated and control voters would have remained stable in the post-treatment period.
-While the validity of this assumption is commonly established by examining pre-treatment trends in turnout between the two groups, it can be improved upon by using the matching methodology described above.
-In the case at hand, we both establish that the turnout of treated voters was mirrored by that of their control voters prior to treatment, \emph{and} that the observable characteristics of treated and control voters are similar---thus lending credence to the assumption that this gap would have remained constant absent treatment.
-Finally, by drawing controls from the population of individuals who were ticketed in subsequent years, we also indirectly control for any unobserved characteristics associated with receiving a ticket.
-For a more detailed discussion of how matching can improve upon traditional difference-in-difference approaches when using panel data, see \protect\hyperlink{ref-Imai2020}{Imai, Kim, and Wang} (\protect\hyperlink{ref-Imai2020}{2020}).
-
-We then estimate the following equation:
-
-\begin{gather}
-\label{eq:1}
-v_{it}=\beta_0+\beta_1Treated_{i}+\beta_2Post Treatment_{t} + \nonumber \\
-\beta_3Treated_{i}\times Post Treatment_{t} + \\
-\beta_4Year_{t} + \delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
-\end{gather}
-
-Individual \emph{i}'s turnout (\emph{v}) in year \emph{t} is a function of the year and whether they were stopped by the police.
-In the equation, \emph{\(\beta\)\textsubscript{1}Treated\textsubscript{i}} measures the historical difference between treated voters and their controls.
-\emph{\(\beta\)\textsubscript{2}Post Treatment\textsubscript{t}} measures whether turnout increased for controls in the first election following the treated voter's stop, while \emph{\(\beta\)\textsubscript{3}Treated\textsubscript{i} × Post Treatment\textsubscript{t}} tests whether turnout changed differently for treated voters than their controls in the election following their police stop.
-\emph{\(\beta\)\textsubscript{3}}, then, will capture the causal effect of a police stop on voter turnout.
-\emph{\(\beta\)\textsubscript{4}Year\textsubscript{t}} captures year fixed-effects depending on the timing of the police stop, and the matrix \emph{\(\delta\)Z\textsubscript{i}} contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
-Equation 1 allows us to test Hypothesis 5:
-
-\emph{Hypothesis 5}: Being ticketed reduces an individual's likelihood of turning out in the subsequent election.
-
-We also estimate Equation 2, in which the treatment effect is interacted with whether a voter is Black (\emph{\(\beta\)\textsubscript{4}Treated\textsubscript{i} × Post Treatment\textsubscript{t} × Black\textsubscript{i}}):
-
-\begin{gather}
-\label{eq:2}
-v_{it}=\beta_0+\beta_1Treated_{i}+\beta_2Post Treatment_{t} + \nonumber \\
-\beta_3Treated_{i}\times Post Treatment_{t} + \beta_4Treated_{i}\times Post Treatment_{t}\times Black_{i} +\\
-\beta_5Year_{t} + \delta{Y}_{i} + \delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
-\end{gather}
-
-where \emph{\(\delta\)Y\textsubscript{it}} includes the dummy for Black interacted with the treatment and post treatment dummies. Equation 2 allows us to test Hypothesis 6:
-
-\emph{Hypothesis 6}: The effect of being ticketed on an individual's voter turnout is less negative / more positive if that individual is Black.
+These empirical estimands allow us to investigate our theoretical estimand; namely, the city-wide political-socialization effects of increased fines and fees collections proxied by voter turnout.
+
+\hypertarget{national-survey-data}{%
+\subsection*{National Survey Data}\label{national-survey-data}}
+\addcontentsline{toc}{subsection}{National Survey Data}
+
+Next, we turn to the American National Election Studies 2020 Time Series data (ANES).
+The ANES has been fielded in every presidential election year since 1948 and is among the most widely-used tools for understanding American's political beliefs and behaviors, including their relationship with the criminal legal system (\protect\hyperlink{ref-Walker2020}{Walker 2020b}).
+It is weighted to be nationally representative of all American adults.
+In both 2016 and 2020, the ANES added new survey questions about respondent's encounters with the police and the criminal legal system.
+We focus in particular on two questions: \emph{During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?}, and \emph{Have you ever been arrested, or has that never happened to you?} We include the roughly 87 percent of respondents that answered both questions, giving us a sample size of 7,347 respondents, of whom just over 11\% identified as Black.
+
+We use these survey questions to make descriptive inferences about how stops and arrests affect the voting behavior of the general population.
+The first descriptive theoretical estimand is the gap between the voter turnout rate of individuals who were recently stopped by the police or who have ever been arrested, and another is whether stops or arrests uniquely influence the political behavior of Black Americans.
+In addition to the respondent's contact with the criminal legal system, we control for age; sex; income; education; party affiliation; self-described ideology; and reported 2016 turnout.
+
+There is an important caveat to the use of the ANES survey---namely, while the police stop question asks whether the respondent \emph{or anyone in their family} was stopped in the past year, the arrest question asks only about the individual respondent.
+While this may muddy the water between direct and proximal contact with the criminal legal system, we expect that the national survey data will give us some insight into the uniquely politicizing nature of police stops for Black Americans.
 
@@
 
-As discussed above, we begin by testing the relationship between police stops and turnout in the 2020 election, and then move to testing the relationship between fees and fines at the municipal level.
-We also examine whether the turnout of individuals stopped by the police before an election was different than those stopped after the election in Hillsborough County, Florida.
-
-\hypertarget{national-survey-data-1}{%
-\subsection*{National Survey Data}\label{national-survey-data-1}}
-\addcontentsline{toc}{subsection}{National Survey Data}
-
-In this section we make use of the American National Election Studies 2020 Time Series Data (ANES).
-The test for this section is simple: we ask whether, after controlling for standard covariates, having personal or proximal contact with a police stop in the previous 12 months is associated with whether a respondent voted in the 2020 presidential election.
-We also ask whether this relationship was different for Black and non-Black respondents.
-Finally, we use the ANES data to reconfirm prior literature demonstrating that higher-level contact with the criminal legal system is associated with lower turnout, as these relationships could have changed in the aftermath of the widespread protests following the police murder of George Floyd in 2020.
-
-Roughly 15 percent of non-Black respondents reported a police stop in the preceding 12 months, while the same was true for more than 22 percent of Black respondents.
-In Figure \ref{fig:anes} we present the results of our econometric models.
-In the left-hand panel, we show the predicted turnout of respondents who answered ``yes'' or ``no'' to the question \emph{During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?} The right-hand panel, meanwhile, plots these relationships for respondents who answered ``yes'' or ``no'' to the question \emph{Have you ever been arrested, or has that never happened to you?}.
-These are the predicted probabilities after controlling for respondents' race / ethnicity; age; party; ideology; income; 2016 turnout; and education.
-The full regression table can be found in the Supplementary Information..
-
-\begin{figure}[!htpb]
-
-{\centering \includegraphics{draft_paper_files/figure-latex/anes-cross-1}
-
-}
-
-\caption{\label{fig:anes}Predicted Turnout, 2020}\label{fig:anes-cross}
-\end{figure}
-
-Figure \ref{fig:anes} demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (\emph{p} = 0.005).
-The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (\emph{p} = 0.27).
-Importantly, this effect is not a remnant of a white--nonwhite divide.
-As we show in the Supplementary Information, police stops were not differently related to turnout for Latinos than for non-Latinos; nor did they impact turnout differently for Asians than for non-Asians.
-The ANES results point, then, to the fact that police stops are uniquely associated with higher turnout for Black respondents.
-
-The second panel of Figure \ref{fig:anes} shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
-Importantly, the interaction between arrest status and the respondent's race was not statistically significant.
-In other words, although police stops seem to be uniquely mobilizing for Black Americans, we fail to uncover evidence that arrests differentially structured subsequent Black- and non-Black turnout.
-
-These cross-sectional results cannot establish causality.
-It is possible that Black respondents who had been stopped by the police (or had family members who experienced a stop) differed from non-Black respondents with such contact in ways that cannot be captured by the survey data.
-However, our findings are consistent with a causal story that police stops are mobilizing for Black Americans---but that this is not the case for higher-level contact such as arrests.
+As discussed above, we begin by examining whether the turnout of individuals ticketed before an election was different from those ticketed after the election in Hillsborough County, Florida.
+Next, we test the relationship between fines and fees revenue reliance and voter turnout at the municipal level.
+We also test the relationship between police stops and turnout in the 2020 election using survey data.
+
+\hypertarget{individual-level-results}{%
+\subsection*{Individual-Level Results}\label{individual-level-results}}
+\addcontentsline{toc}{subsection}{Individual-Level Results}
+
+To directly observe the effect of being stopped by the police on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
+As discussed above, we match individuals who were ticketed between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.\footnote{Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
+The full sample is used in the actual matching process.} Matching is done with replacement and ties are not broken.
+This means that some treated voters have multiple controls; the regression weights are calculated to allow for this possibility.
+In Table \ref{tab:balance} we present the results of the matching algorithm.
+As the table demonstrates, the selected control voters are very similar to the treated voters.
+
+Table 1 About Here
+
+It is worth noting that voters who were ticketed between 2012 and 2020 were far more likely to be Black and male than the general electorate, and live in Census block groups with moderately lower incomes.
+
+In Figure \ref{fig:did1}, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped.
+In the top row, we present the turnout in 2008--2014 of the individuals stopped between 2012 and 2014 and their controls; the second row shows the 2010--2016 turnout for individuals stopped between 2014 and 2016 and their controls; and the third shows the treatment effect for those stopped in the 2 years prior to the 2018 midterms.
+Finally, in the bottom row, we present the overall turnout effects for these three elections.
+The first election following a treated voter's stop is denoted as \emph{t = 0} while the years in which \emph{t} is less than zero are the periods prior to the stop.
+
+Figure 1 About Here
+
+Figure \ref{fig:did1} makes a number of things immediately apparent.
+First, we can see that for both Black and non-Black voters the parallel trends assumption is satisfied.
+Because we matched treated and control voters based on turnout prior to the ticket, this is by design.
+Secondly, Figure \ref{fig:did1} provides preliminary visual evidence of the demobilizing effects of police stops in Hillsborough County.
+However, as the figure also makes clear, it seems that the negative effects are concentrated in the lower-salience midterm elections; there is little evidence of turnout effects in the 2016 presidential election.
+
+Table \ref{tab:dind-table} formalizes the final row of Figure \ref{fig:did1} into an ordinary least squares regression.
+Models 1 and 2 show our overall causal effect, while models 3 and 4 allow for the possibility that a ticket differentially mobilizes Black voters.
+In models 1 and 3, we include only the treatment, timing, and race dummies, while the full set of covariates used for the matching procedure are included in models 2 and 4.
+The empirical estimands are \emph{Treated × Post Treatment} and \emph{Treated × Post Treatment × Black}.
+In models 1 and 2, \emph{Treated × Post Treatment} measures the overall treatment effect, and in models 3 and 4 it measures the treatment effect for non-Black voters.
+\emph{Treated × Post Treatment × Black} measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
+
+Table 2 About Here
+
+As both Figure \ref{fig:did1} and Table \ref{tab:dind-table} make clear, police tickets meaningfully depressed turnout.
+In models 1 and 2, the estimated overall treatment effect is -1.5 percentage points.
+In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---non-Black turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
+Although the treatment effect is still substantively quite large for Black individuals, Hillsborough County Black voters' turnout in federal elections was not as negatively impacted by police contact as that of non-Black individuals.
 
@@
 
-\begin{figure}[H]
-
-{\centering \includegraphics{draft_paper_files/figure-latex/cross-18-1}
-
-}
-
-\caption{\label{fig:mef-2018}Predicted Turnout, 2018}\label{fig:cross-18}
-\end{figure}
+Figure 2 About Here
 
@@
 The results of these models can be found in Table \ref{tab:twfe}.
-The average municipality included in this analysis raised \$2.17 in fees and fines per resident in 2012, and the average municipality increased or decreased this per-capita figure by \$0.47 between 2012 and 2017.
+The average municipality included in this analysis raised \$2.17 in fees and fines per resident in 2012, and the average municipality increased this per-capita figure by \$0.47 between 2012 and 2017.
 Just over 10\% of municipalities raised no revenue from fees and fines in either year.
 
-\begin{singlespace}
-\input{"../temp/2wfe_reg_clean.tex"}
-\end{singlespace}
-
-The results of the two-way fixed effects model are different than what we saw in the 2018 cross-sectional approach; namely, Table \ref{tab:twfe} indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not significantly impact Black turnout.
+Table 3 About Here
+
+The results of the two-way fixed effects model are different from what we saw in the 2018 cross-sectional approach; namely, Table \ref{tab:twfe} indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not significantly impact Black turnout.
 The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.04 percentage points.
 
-\hypertarget{individual-level-results}{%
-\subsection*{Individual-Level Results}\label{individual-level-results}}
-\addcontentsline{toc}{subsection}{Individual-Level Results}
-
-Thus far, we have shown that Black individuals with police contact reported participating at higher rates in the 2020 election than those without such contact.
-We also demonstrated that voter turnout decreases in municipalities that increased fines and fees collections.
-We argue that this relationship is causal: increased fees and fines collections means that more residents have direct interactions with the criminal legal system.
-Based on prior literature, we assume there are indirect effects as well, as more residents know a family or community member who has been ticketed.
-While the national analyses give us great breadth and an increased understanding of how this plays out across the country, they leave us unable to directly observe the causal mechanisms at play.
-
-To directly observe the effect of being stopped by the police on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
-As discussed above, we match individuals who were ticketed between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.\footnote{Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
-The full sample is used in the actual matching process.} Matching is done with replacement and ties are not broken.
-This means that some treated voters have multiple controls; the regression weights are calculated to allow for this possibility.
-In Table \ref{tab:balance} we present the results of the matching algorithm.
-As the table demonstrates, the selected control voters are very similar to the treated voters.
-
-\begin{singlespace}
-\begin{table}[!h]
-
-\caption{\label{tab:baltab-chunk}\label{tab:balance} Balance Table}
-\centering
-\begin{tabular}[t]{llll}
-\toprule
-Variable & Treated Voters & Control Voters & Never Stopped\\
-\midrule
-\%White & 47.4\% & 47.6\% & 62.2\%\\
-\% Black & 24.4\% & 25.1\% & 13.1\%\\
-\% Latino & 19.0\% & 19.3\% & 16.0\%\\
-\% Asian & 2.1\% & 2.1\% & 2.7\%\\
-\% Male & 53.2\% & 53.0\% & 42.8\%\\
-\% Democrat & 42.5\% & 43.1\% & 37.9\%\\
-\% Republican & 23.7\% & 23.6\% & 31.3\%\\
-Age & 42.5 & 41.8 & 51.9\\
-Median Income & \$62,836 & \$62,497 & \$67,897\\
-\% with Some College & 73.9\% & 74.1\% & 76.5\%\\
-Unemployment Rate & 6.6\% & 6.6\% & 5.9\%\\
-Turnout\textsubscript{t=-3} & 31.7\% & 31.7\% & \\
-Turnout\textsubscript{t=-2} & 29.6\% & 29.6\% & \\
-Turnout\textsubscript{t=-1} & 44.6\% & 44.6\% & \\
-Stops in pre-period & 2.2 & 1.9 & \\
-Paid Money & 89.1\% & 89.1\% & \\
-Civil Stop & 82.6\% & 82.6\% & \\
-Stopped by Tampa PD & 47.0\% & 47.0\% & \\
-\bottomrule
-\end{tabular}
-\end{table}
-\end{singlespace}
-
-It is worth noting that voters who were stopped between 2012 and 2020 were far more likely to be Black and male than the general electorate, and live in Census block groups with moderately lower incomes.
-
-While Table \ref{tab:balance} indicates that our treatment voters and their matches are substantially similar to their matches, the validity of the difference-in-differences design requires that any turnout gap between treatment and control voters be comparable in the baseline period.
-In Figure \ref{fig:did1}, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped.
-The first election following a treated voter's stop is denoted as \emph{t = 0} while the years in which \emph{t} is less than zero are the periods prior to the stop.
-This means that for someone stopped in 2013 (and their controls), \emph{t} is 0 in 2014, while \emph{t} is equal to 0 in 2018 for an individual stopped between the 2016 and 2018 elections.
-
-\begin{figure}[H]
-
-{\centering \includegraphics{draft_paper_files/figure-latex/did1-1}
-
-}
-
-\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout}\label{fig:did1}
-\end{figure}
-
-Figure \ref{fig:did1} makes a number of things immediately apparent.
-First, we can see that for both Black and non-Black voters the parallel trends assumption is satisfied.
-Because we matched treated and control voters based on turnout prior to the ticket, this is by design.
-
-Table \ref{tab:dind-table} formalizes Figure \ref{fig:did1} into an ordinary least squares regression.
-Models 1 and 2 show our overall causal effect, while models 3 and 4 allow for the possibility that a ticket differentially mobilizes Black voters.
-In models 1 and 3, we include only the treatment, timing, and race dummies, while the full set of covariates used for the matching procedure are included in models 2 and 4.
-The coefficients of note are \emph{Treated × Post Treatment} and \emph{Treated × Post Treatment × Black}.
-In models 1 and 2, \emph{Treated × Post Treatment} measures the overall treatment effect, and in models 3 and 4 it measures the treatment effect for non-Black voters.
-\emph{Treated × Post Treatment × Black} measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
-
-\begin{singlespace}
-\input{"../temp/dind_reg_y.tex"}
-\end{singlespace}
-
-As both Figure \ref{fig:did1} and Table \ref{tab:dind-table} make clear, police tickets meaningfully depressed turnout.
-In models 1 and 2, the estimated overall treatment effect is -1.5 percentage points.
-In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---non-Black turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
-Although the treatment effect is still substantively quite large for Black individuals, the pattern follows our national analysis.
-It appears that, in Tampa and around the country, Black voters' turnout in federal elections is not as negatively impacted by police contact as that of non-Black individuals.
+\hypertarget{national-survey-data-1}{%
+\subsection*{National Survey Data}\label{national-survey-data-1}}
+\addcontentsline{toc}{subsection}{National Survey Data}
+
+In this section we make use of the American National Election Studies 2020 Time Series Data (ANES).
+The first test is simple: we ask whether, after controlling for standard covariates, having personal or proximal contact with a police stop in the previous 12 months is associated with whether a respondent voted in the 2020 presidential election.
+We also ask whether this relationship was different for Black and non-Black respondents.
+Finally, we use the ANES data to reconfirm prior literature demonstrating that higher-level contact with the criminal legal system is associated with lower turnout, as these relationships could have changed in the aftermath of the widespread protests following the police murder of George Floyd in 2020.
+
+Roughly 15 percent of non-Black respondents reported a police stop in the preceding 12 months, while the same was true for more than 22 percent of Black respondents.
+In Figure \ref{fig:anes} we present the results of our econometric models.
+In the left-hand panel, we show the predicted turnout of respondents who answered ``yes'' or ``no'' to the question \emph{During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?} The right-hand panel, meanwhile, plots these relationships for respondents who answered ``yes'' or ``no'' to the question \emph{Have you ever been arrested, or has that never happened to you?}.
+These are the predicted probabilities after controlling for respondents' race / ethnicity; age; party; ideology; income; education; and 2016 turnout.
+The full regression table can be found in the Supplementary Information..
+
+Figure 3 About Here
+
+Figure \ref{fig:anes} demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (\emph{p} = 0.005).
+The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (\emph{p} = 0.27).
+Importantly, this effect is not a remnant of a white--nonwhite divide.
+As we show in the Supplementary Information, police stops were not differently related to turnout for Latinos than for non-Latinos; nor did they impact turnout differently for Asians than for non-Asians.
+The ANES results point, then, to the fact that police stops are uniquely associated with higher turnout for Black respondents.
+
+The second panel of Figure \ref{fig:anes} shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
+Importantly, the interaction between arrest status and the respondent's race was not statistically significant.
+In other words, although police stops seem to be uniquely mobilizing for Black Americans, we fail to uncover evidence that arrests differentially structured subsequent Black and non-Black turnout.
+
+This theoretical estimand is descriptive, and cross-sectional results cannot establish causality.
+It is possible that Black respondents who had been stopped by the police (or had family members who experienced a stop) differed from non-Black respondents with such contact in ways that cannot be captured by the survey data.
+However, our findings are consistent with a causal story that police stops are uniquely mobilizing for Black Americans---but this is not the case for higher-level contact, such as arrests.
 
@@
 
-While existing sociology and political science literature has examined the rise and collateral consequences of fines and fees as well as the effects of criminalization on political socialization, no study has investigated the causal relationship between ticketing and voter turnout.
+While existing sociological and political science literature has examined the rise and collateral consequences of fines and fees as well as the effects of criminalization on political socialization, no study has investigated the causal relationship between ticketing and voter turnout.
 Additionally, our study is among the first to use individual-level administrative data to investigate the relationship between criminalization and political participation.
@@
 What we find complicates our understanding of how lower-level police contact affects political participation.
-On one hand, the national survey data and cross-sectional municipal-level analysis indicate that police contact is associated with higher turnout for Black Americans, and either unrelated or negatively related to turnout for others.
-Our causal models, on the other hand, tell a slightly different story---namely, they fail to uncover mobilizing effects for Black Americans.
+The national survey data and cross-sectional municipal-level analysis indicate that police contact is associated with higher turnout for Black Americans, and either unrelated or negatively related to turnout for others.
+Our causal models tell a slightly different story---they fail to uncover mobilizing effects for Black Americans.
 Nevertheless, our causal models \emph{do} indicate that police stops are less demobilizing for Black individuals than for others.
@@
 Based on these three independent approaches, we conclude that the political consequences of police stops are unique for Black Americans---and that they are less demobilizing for Black Americans than others.
-
-The difference between the cross-sectional and two-way fixed effects models using the municipality-level data is somewhat surprising. There are a few potential explanations for this mismatch.
-
-First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes in the two-way fixed effects models are smaller or not statistically significant.
-Along a similar vein, it's possible that the effect size for Black voters in the city-level analysis is influenced by higher-intensity forms of criminal legal contact, such as arrest and incarceration.
-The bulk of existing literature suggests that incarceration discourages political participation, and it's not unreasonable to assume that cities that ramp up ticketing of Black residents also ramp up arrest and incarceration of Black residents.
-If these phenomena coincide, that could explain why the city-level analysis produced no statistically significant effect for Black voters---the personally mobilizing effect of ticketing could be counterbalanced by the proximal chilling effect of incarceration, and because the city-level analysis is not as temporally sensitive, it's more difficult to isolate the effect of ticketing.
-We were unable to incorporate a measure of local incarceration trends due to a lack of consistent data nationwide.
-
-Moreover, Sances and You (\protect\hyperlink{ref-Sances2017}{2017, 1091})---the paper that originally detailed the relationship between fees and fines collections and municipalities' racial composition using the Census of Governments data---specifically notes that they did not exploit the panel setup of the COG because of ``little variation within a city in terms of revenues from fines.'' Instead, they present only the results of a cross-sectional study.
-Here, we present both the cross-sectional and panel results, acknowledging that each have limitations but that, taken together, they shed light on the unique politicization of fees and fines for Black Americans.
+Additionally, as \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020a}) suggests, ticketed Black individuals may be politically mobilized for activities other than voting not observed in this study, such as contacting elected representatives or volunteering for campaigns.
 
@@
 On the one hand, the causal results are highly robust, and the ticketing data allows us to identify the treatment fairly precisely.
-On the other hand, these are the only results in which a police stop are associated with a \emph{decrease} in turnout for Black individuals.
+On the other hand, these are the only results in which police stops are associated with a \emph{decrease} in turnout for Black individuals.
 This may be because this analysis tests the impact of direct contact with the police, rather than direct \emph{or} proximal contact, as the ANES questions do.
@@
 
-Our findings point to several implications for political sociology and political science scholarship.
+The difference between the cross-sectional and two-way fixed effects models using the municipality-level data is somewhat surprising.
+There are a few potential explanations for this mismatch.
+First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes in the two-way fixed effects models are smaller or not statistically significant.
+Along a similar vein, it is possible that a mobilizing effect of ticketing for Black voters in the city-level analysis is offset by higher-intensity forms of criminal legal contact, such as arrest and incarceration.
+The bulk of existing literature suggests that incarceration discourages political participation, and it is not unreasonable to assume that cities that ramp up ticketing of Black residents also ramp up arrest and incarceration of Black residents.
+If these phenomena coincide, that could explain why the city-level analysis produced no statistically significant effect for Black voters---the personally mobilizing effect of ticketing could be counterbalanced by the proximal chilling effect of incarceration, and because the city-level analysis is not as temporally sensitive, it is more difficult to isolate the effect of ticketing.
+At the same time, \protect\hyperlink{ref-Harris2020}{A.
+P.
+Harris, Ash, and Fagan} (\protect\hyperlink{ref-Harris2020}{2020}) indicates that when municipalities increase their fees and fines collections, relatively more \emph{white} individuals are ticketed.
+\protect\hyperlink{ref-Shoub2020}{Shoub et al.} (\protect\hyperlink{ref-Shoub2020}{2020}) demonstrates the corollary: when municipalities stop fewer motorists, the decrease is concentrated among white individuals.
+Existing research, then, indicates that a relatively constant share of the Black population is stopped by the police; changes in fees and fines collections largely impacts the white population.
+The overall changes in revenue we observe in our two-way fixed effects models might reflect changes largely for the white populations in these municipalities, while ticketing---and turnout---remain more or less constant for Black populations.
+We were unable to incorporate a race-specific measure of police stops or measures of local incarceration or policing trends due to a lack of consistent data nationwide.
+
+Finally, Sances and You (\protect\hyperlink{ref-Sances2017}{2017}: 1091)---the paper that originally detailed the relationship between fees and fines collections and municipalities' racial composition using the Census of Governments data---specifically notes that they did not exploit the panel setup of the COG because of ``little variation within a city in terms of revenues from fines.'' Instead, they present only the results of a cross-sectional study.
+Here, we present both the cross-sectional and panel results, acknowledging that each have limitations but that, taken together, they shed light on the unique politicization of fees and fines for Black Americans.
+
+Our findings have several implications for political sociology and political science scholarship.
 While existing literature suggests that the most disruptive forms of criminal legal contact (i.e.~criminal convictions and incarceration) consistently discourage voting (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}; \protect\hyperlink{ref-Burch2011}{Burch 2011}; \protect\hyperlink{ref-White2019a}{White 2019b}), research regarding police stops has produced more mixed results (\protect\hyperlink{ref-Laniyonu2019}{Laniyonu 2019}).
-We extend this theory to police ticketing, the most common form of police contact in America, and find that city-level increases in ticketing generally reduce turnout.
+We extend this theory to police ticketing, the most common form of police contact in America, and find that ticketing generally reduces turnout.
 For Black voters, however, our findings suggest that ticketing can be politically mobilizing.
@@
 
-In this sense, our analysis points to a political contestation of criminal legal policy, a phenomenon that aligns with dozens of recent campaigns to reform local fines and fees practices (or abolish them entirely).\footnote{See \url{https://finesandfeesjusticecenter.org/clearinghouse}.} We know that fines and fees result from political economy (i.e.~austerity at the federal level), but our analysis suggests that this is a ``two way street'' wherein people who are harmed by policing practices are politically socialized into resistance.
-
-\textbf{Limitations}: Because our individual-level analysis is limited to Hillsborough County, we don't have a good sense of how the city-level revenue reliance trend interacts with the individual experience of being ticketed.
+In this sense, our analysis points to a political contestation of criminal legal policy, a phenomenon that aligns with dozens of recent campaigns to reform local fines and fees practices (or abolish them entirely).\footnote{See \url{https://finesandfeesjusticecenter.org/clearinghouse}.} We know that increased fines and fees result from political economy (i.e.~austerity at the federal level), but our analysis suggests that this is a ``two way street'' wherein people who are harmed by policing practices can be politically socialized into resistance.
+
+\textbf{Limitations}: Because our individual-level administrative data analysis is limited to Hillsborough County where fines collections increased over the period, we do not have a good sense of how the city-level revenue reliance trend interacts with the individual experience of being ticketed in areas where fees and fines are constant or decreasing.
 Is ticketing more politically mobilizing for Black voters in cities that are palpably dialing up their revenue collection efforts?
@@
 
-Additionally, in our analysis of Hillsborough County voters, we don't look at people who weren't registered to vote in 2018.
-This means that there could be some proportion of ticketed Black motorists who are now less likely to register to vote in the first place, for example.
-In other words the mobilization effect (or decreased demobilization effect) in our findings only applies to people who were registered to vote---we are unable to make claims about whether being ticketed makes an individual more likely to register to vote.
+Additionally, in our analysis of Hillsborough County voters, we do not look at people who were not registered to vote in 2018.
+Because we cannot tell whether unregistered individuals who were stopped in Hillsborough County were unregistered because they were \emph{ineligible} to do so (by virtue of living in a different county or being a non-citizen, for instance) or chose to eschew electoral politics, our analysis is necessarily limited to individuals who were registered to vote.
+This likely makes our results conservative: we cannot capture the lost participation of individuals who would have registered and voted if they were not stopped by the police.
 
@@
 Can organizers build on this potential for broad-based political action?
-We were unable to test whether what we're observing is simply \emph{decreased} demobilization, or whether some subgroups of the Black population were mobilized while others were demobilized.
-In other words, it could be the case that ticketing is demobilizing for all voters, but there is a subset of Black voters who are \emph{mobilized} by this, though they aren't a large enough group to counteract the demobilization of other Black people.
-
-Also, unlike previous studies using survey data, we are unable to tell whether treated individuals in Tampa have non-ticketing criminal legal exposure.
-Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.
+We were unable to test whether what we observed was simply \emph{decreased} demobilization, or whether some subgroups of the Black population were mobilized while others were demobilized.
+Put differently: it could be the case that ticketing is demobilizing for most voters of all races, but that a subset of the Black population is affirmatively mobilized, leading to lower group-level demobilization.
+Scholars should also investigate the interactive effects of criminal legal contact, asking whether police stops result in different political behavior for formerly incarcerated individuals than individuals with no other contact with the system.
+
+Finally, we are sensitive to the fact that although administrative data provides real-world evidence of actual behavior, such an approach limits our ability to understand the psychological processes in play.
+This means that although we demonstrate that police stops are demobilizing, future work must further investigate how stops are interpreted by individuals and translated into political behavior.
 
@@
 Policymakers should work to ensure that Black Americans no longer have to struggle to enjoy the same political power as whites---to that end, the current trend of voting rights restriction policies across the country is especially pernicious.
-Even if Black Americans understand the ballot box as one tool they can use to limit the state's power to exploit and harm them, policymakers should still feel an obligation to support voting rights and stop disproportionate ticketing in Black communities.
+Even if Black Americans understand the ballot box as one tool they can use to limit the state's power to exploit and harm them, policymakers should still feel an obligation to support voting rights protections and stop disproportionate ticketing in Black communities.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-Behrens2003}{}%
-Behrens, A., C.
-Uggen, and Jeff Manza.
-2003.
-{``Ballot {Manipulation} and the {`{Menace} of {Negro Domination}'}: {Racial Threat} and {Felon Disenfranchisement} in the {United States}, 1850--20021.''} \emph{American Journal of Sociology}.
-\url{https://doi.org/10.1086/378647}.
-
 \leavevmode\hypertarget{ref-Bell2017}{}%
@@
 \url{https://doi.org/10.1177/0002716213503093}.
+
+\leavevmode\hypertarget{ref-Butler2011}{}%
+Butler, Daniel M., and David E.
+Broockman.
+2011.
+{``Do {Politicians Racially Discriminate Against Constituents}?
+{A Field Experiment} on {State Legislators}.''} \emph{American Journal of Political Science} 55 (3): 463--77.
+\url{https://doi.org/10.1111/j.1540-5907.2011.00515.x}.
 
@@
 
+\leavevmode\hypertarget{ref-Eckhouse2016}{}%
+Eckhouse, Laurel. 2016. {``Descriptive {Representation} and {Political Power}: {Explaining Racial Inequalities} in {Policing}.''} \emph{(Unpublished Manuscript)}.
+
 \leavevmode\hypertarget{ref-Edwards2020}{}%
@@
 
+\leavevmode\hypertarget{ref-Gunderson2020}{}%
+Gunderson, Anna.
+2020.
+{``Representation, {Incorporation}, and {Corrections Spending}: {The Counterbalancing Effect} of {Black Political Incorporation}.''} \emph{Journal of Race, Ethnicity, and Politics} 5 (3): 573--603.
+\url{https://doi.org/10.1017/rep.2020.15}.
+
 \leavevmode\hypertarget{ref-Harrell2020}{}%
@@
 {``Monetary {Sanctions} in the {Criminal Justice System}.''}
+
+\leavevmode\hypertarget{ref-Harris2020}{}%
+Harris, Allison P., Elliott Ash, and Jeffrey Fagan.
+2020.
+{``Fiscal {Pressures} and {Discriminatory Policing}: {Evidence} from {Traffic Stops} in {Missouri}.''} \emph{Journal of Race, Ethnicity, and Politics} 5 (3): 450--80.
+\url{https://doi.org/10.1017/rep.2020.10}.
 
@@
 
+\leavevmode\hypertarget{ref-Lundberg2021}{}%
+Lundberg, Ian, Rebecca Johnson, and Brandon M.
+Stewart.
+2021.
+{``What {Is Your Estimand}?
+{Defining} the {Target Quantity Connects Statistical Evidence} to {Theory}.''} \emph{American Sociological Review} 86 (3): 532--65.
+\url{https://doi.org/10.1177/00031224211004187}.
+
 \leavevmode\hypertarget{ref-Makowsky2009}{}%
@@
 Mancini, Matthew J. 1978. {``Race, {Economics}, and {The Abandonment} of {Convict Leasing}.''} \emph{The Journal of Negro History} 63 (4): 339--52. \url{https://doi.org/10.2307/2716851}.
+
+\leavevmode\hypertarget{ref-Manza2006}{}%
+Manza, Jeff, and Christopher Uggen. 2006. \emph{Locked Out: Felon Disenfranchisement and {American} Democracy}. Studies in Crime and Public Policy. {Oxford ; New York}: {Oxford University Press}.
+
+\leavevmode\hypertarget{ref-McCoy2015}{}%
+McCoy, Terrence.
+2015.
+{``Ferguson Shows How a Police Force Can Turn into a Plundering {`Collection Agency'}.''} \emph{Washington Post}, March 5, 2015.
+\url{https://www.washingtonpost.com/news/morning-mix/wp/2015/03/05/ferguson-shows-how-a-police-force-can-turn-into-a-plundering-collection-agency/}.
 
@@
 
-\leavevmode\hypertarget{ref-Meredith2017}{}%
----------. 2017. {``Discretionary {Disenfranchisement}: {The Case} of {Legal Financial Obligations}.''} \emph{The Journal of Legal Studies} 46 (2): 309--38. \url{https://doi.org/10.1086/694323}.
+\leavevmode\hypertarget{ref-Miller2017}{}%
+Miller, Reuben Jonathan, and Forrest Stuart.
+2017.
+{``Carceral {Citizenship}: {Race}, {Rights} and {Responsibility} in the {Age} of {Mass Supervision}.''} \emph{Theoretical Criminology} 21 (4): 532--48.
+\url{https://doi.org/10.1177/1362480617731203}.
 
@@
 
+\leavevmode\hypertarget{ref-Sanders2017}{}%
+Sanders, Topher, and Benjamin Conarck.
+2017.
+{``Florida {Police Issue Hundreds} of {Bad Pedestrian Tickets Every Year Because They Don}'t {Seem} to {Know} the {Law}.''} \emph{ProPublica}, December 20, 2017.
+\url{https://www.propublica.org/article/florida-police-issue-hundreds-of-bad-pedestrian-tickets-every-year-because-they-dont-seem-to-know-the-law?token=CpfrqXaMuR8UnJ5-FryRkVwuKl3C98Ae}.
+
 \leavevmode\hypertarget{ref-Sekhon2011}{}%
@@
 
-\leavevmode\hypertarget{ref-Shofner1963}{}%
-Shofner, Jerrell H. 1963. {``The {Constitution} of 1868.''} \emph{The Florida Historical Quarterly} 41 (4): 356--74. \url{http://www.jstor.org/stable/30139965}.
+\leavevmode\hypertarget{ref-Shaer2019}{}%
+Shaer, Matthew.
+2019.
+{``How {Cities Make Money} by {Fining} the {Poor}.''} \emph{The New York Times: Magazine}, January 8, 2019.
+\url{https://www.nytimes.com/2019/01/08/magazine/cities-fine-poor-jail.html}.
 
@@
 
-\leavevmode\hypertarget{ref-Sugie2015}{}%
-Sugie, Naomi F.
-2015.
-{``Chilling {Effects}: {Diminished Political Participation} Among {Partners} of {Formerly Incarcerated Men}.''} \emph{Social Problems} 62 (4): 550--71.
-\url{http://www.jstor.org/stable/44014875}.
+\leavevmode\hypertarget{ref-Soss2017}{}%
+Soss, Joe, and Vesla Weaver.
+2017.
+{``Police {Are Our Government}: {Politics}, {Political Science}, and the {Policing} of {Race}--{Class Subjugated Communities}.''} \emph{Annual Review of Political Science} 20 (1): 565--91.
+\url{https://doi.org/10.1146/annurev-polisci-060415-093825}.
 
@@
 
+\leavevmode\hypertarget{ref-Uggen2002}{}%
+Uggen, Christopher, and Jeff Manza.
+2002.
+{``Democratic {Contraction}?
+{Political Consequences} of {Felon Disenfranchisement} in the {United States}.''} \emph{American Sociological Review} 67 (6): 777--803.
+\url{https://doi.org/10.2307/3088970}.
+
 \leavevmode\hypertarget{ref-UnitedStatesCommissiononCivilRights2017}{}%
@@
 ---------. 2020b. {``Targeted: {The Mobilizing Effect} of {Perceptions} of {Unfair Policing Practices}.''} \emph{The Journal of Politics} 82 (1): 119--34. \url{https://doi.org/10.1086/705684}.
-
-\leavevmode\hypertarget{ref-Walker2017}{}%
-Walker, Hannah L., and Marcela García-Castañon.
-2017.
-{``For {Love} and {Justice}: {The Mobilizing} of {Race}, {Gender}, and {Criminal Justice Contact}.''} \emph{Politics \& Gender} 13 (4): 541--68.
-\url{https://doi.org/10.1017/S1743923X17000198}.
 
@@
 
+\leavevmode\hypertarget{ref-Weaver2020}{}%
+Weaver, Vesla M., Gwen Prowse, and Spencer Piston.
+2020.
+{``Withdrawing and {Drawing In}: {Political Discourse} in {Policed Communities}.''} \emph{Journal of Race, Ethnicity, and Politics} 5 (3): 604--47.
+\url{https://doi.org/10.1017/rep.2019.50}.
+
 \leavevmode\hypertarget{ref-White2019}{}%
@@
 {``How Riding Your Bike Can Land You in Trouble with the Cops --- If You're Black.''} \emph{Tampa Bay Times}, April 15, 2015.
-\url{https://www.tampabay.com/news/publicsafety/how-riding-your-bike-can-land-you-in-trouble-with-the-cops—if-youre-black/2225966/}.
+\url{https://www.tampabay.com/news/publicsafety/how-riding-your-bike-can-land-you-in-trouble-with-the-cops---if-youre-black/2225966/}.
 
@@
 
+\newpage
+
+\hypertarget{tables}{%
+\section*{Tables}\label{tables}}
+\addcontentsline{toc}{section}{Tables}
+
+\begin{singlespace}
+\input{"../temp/balance_table.tex"}
+\end{singlespace}
+
+\begin{singlespace}
+\input{"../temp/dind_reg_y.tex"}
+\end{singlespace}
+
+\begin{singlespace}
+\input{"../temp/2wfe_reg_clean.tex"}
+\end{singlespace}
+
+\hypertarget{figures}{%
+\section*{Figures}\label{figures}}
+\addcontentsline{toc}{section}{Figures}
+
+\begin{figure}[H]
+
+{\centering \includegraphics{not_blind_files/figure-latex/did1-1}
+
+}
+
+\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout}\label{fig:did1}
+\end{figure}
+
+\begin{figure}[H]
+
+{\centering \includegraphics{not_blind_files/figure-latex/cross-18-1}
+
+}
+
+\caption{\label{fig:mef-2018}Predicted Turnout, 2018}\label{fig:cross-18}
+\end{figure}
+
+\begin{figure}[!htpb]
+
+{\centering \includegraphics{not_blind_files/figure-latex/anes-cross-1}
+
+}
+
+\caption{\label{fig:anes}Predicted Turnout, 2020}\label{fig:anes-cross}
+\end{figure}
+
 \end{document}

### 2021-07-23 markdown/si.Rmd
submission docs

@@
 title: "Supplementary Information"
-output:
-  bookdown::pdf_document2:
-    toc: yes
-    fig_caption: yes
-    latex_engine: xelatex
-    keep_tex: true
+output: word_document
 bibliography: "policing_turnout.bib"
@@
 fontsize: 12pt
+always_allow_html: true
 header-includes:
@@
 
-# Testing Robustness of L2 Racial Estimates {-}
-
-As discussed in the body of this manuscript, our municipality-level racial estimates are constructed by aggregating up from individual-level records provided by L2.
-Because L2 uses statistical modeling to infer voters' race---not self-reported information---there is potential room for error in these estimates.
-
-Because there are no precise estimates of the racial demographics of the registered electorate in each state, we compare the estimated Black share of each municipality to the Black share of the citizen voting age population (CVAP) in each municipality.
-This method is not without drawbacks: if different cities have different racial registration rates, they will not track the perfectly.
-To mitigate some of this discrepancy, we adjust the Black share of the electorate in each municipality by the racial registration gap in that municipality's state, according to the Current Population Survey's (CPS) 2018 data.
-For example, according to the CPS, 27.0% of the CVAP in Alabama was Black in 2018, but just 26.4% of registered voters were Black.
-We therefore add 0.6% to the estimated Black share of the electorate in each municipality in Alabama, so that it might more closely mirror the Black share of CVAP.
-
-In Table \ref{tab:mae} we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level and adjusted according to the CPS, relative to the Census Bureau's CVAP estimate.
-Because it seems possible that these errors vary by population size, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.
-
-\begin{singlespace}
-```{r mae-chunck, echo = F, warning = F}
-t <- readRDS("./temp/maes.rds") %>% 
-  mutate_all(~ gsub("[%]", "\\\\%", .))
-j <- t %>% 
-  mutate_all(linebreak) %>% 
-  knitr::kable(booktabs = T, caption = "(\\#tab:mae) MAE of L2 Municipality Estimates, CVAP", linesep = "", escape = F,
-               col.names = linebreak(colnames(t)),
-               align = "c") %>% 
-  kable_styling(latex_options = c("HOLD_position"),
-                position = "center")
-j
-```
-\end{singlespace}
-
-Table \ref{tab:mae} makes clear that the adjusted Black estimates of the electorate mirror the Black share of CVAP very closely: for no group of municipalities does the MAE exceed 3%.
-This seems to indicate that the L2 racial estimates are quite good when aggregated to the municipal level.
-
-In Table \ref{tab:mae:reg}, we show that the difference between the adjusted estimate of the Black share of the electorate and the Black share of the CVAP is entirely unrelated to cities' per-capita fees and fines, after controlling for other characteristics.
-Given the low MAE and the lack of relationship between the error and the fees and fines, we conclude that the municipal-level racial estimates from the individual-level records are reasonable and unbiased.
-
-\begin{singlespace}
-\input{"../temp/mae_clean.tex"}
-\end{singlespace}
-
-# Regression Table for Survey Data {-}
-
-Here we present the regression table reported in the national survey data section of the manuscript.
-In model 1 we test whether personal or proximal contact with a police stop is differentially associated with turnout for Black and non-Black respondents.
-In this model, *Stopped in Past 12 Months* captures the relationship between police stops and non-Black respondents; *Stopped in Past 12 Months × Black* tests whether this relationship is different for Black respondents.
-
-Models 2, 3, and 4 test whether the relationship is different for other non-white groups. Finally, model 5 tests the relationship between turnout and a historical arrest.
-
-\begin{singlespace}
-\input{"../temp/anes_clean.tex"}
-\end{singlespace}
-
-Model 1 in Table \ref{tab:anes-reg} shows that Black individuals who had been stopped by the police (or had a family member stopped) in the preceding 12 months were 9 percentage points more likely to vote in 2020, other things equal; they were not related to turnout for non-Black respondents.
-Police stops are not, however, associated with different turnout effects for other non-white groups.
-Moreover, as discussed in the body of the paper, historical arrests were uniformly associated with a decrease in turnout of 4 percentage points for Black and non-Black respondents alike.
-
-# Regression Table for 2018 Cross-Sectional Municipality Model {-}
-
-In Table \ref{tab:cog-cross-reg} we present the full results of the econometric used to test the cross-sectional relationship between per-capita fees and fines, and 2018 municipal turnout.
-The table shows that a doubling of the fees and fines collected per capita is associated with a 0.3 percentage point reduction in overall turnout.
-That same doubling, however, is associated with a 0.4 percentage point *increase* in the Black turnout.
-While these point estimates are quite small, it is worth keeping in mind that the range of fees and fines per capita is very wide.
-The interquartile ranges of fees and fines per capita stretches from \$1.96 to \$20.63---a more than ten-fold increase.
-
-\begin{singlespace}
-\input{"../temp/cog_cross_clean.tex"}
-\end{singlespace}
-
 # Administrative Matching Robustness Check {-}
@@
 By systematically permuting the birth dates in one set of records, we can see whether false positive matches are a major concern.
-In Table \ref{tab:change-dobs} we begin by merging all names and dates of birth in the traffic stop data with the names and dates of birth in the Hillsborough County registered voter file.
+In Table 1 we begin by merging all names and dates of birth in the traffic stop data with the names and dates of birth in the Hillsborough County registered voter file.
 We then add and subtract 35 days from the birth dates in the traffic stop data.
@@
 
-Figure \ref{fig:rob-window} shows that our overall treatment effect is remarkably consistent regardless of the size of the window drawn around the election.
+Figure 1 shows that our overall treatment effect is remarkably consistent regardless of the size of the window drawn around the election.
 As we expand the window, we gain more treated voters (and treated voters have a larger pool of potential controls).
@@
 
+# Regression Tables for Individual Treatment Years {-}
+
+In the body of this manuscript, we present only the overall treatment effects for the police stops in Hillsborough County, which are effectively averaged across all three years.
+Here, in Tables 2--4, we present the results for each group of treated and control voters.
+In Table 2, all treated voters were stopped between the 2012 and 2014 elections, and all controls were stopped between the 2014 and 2016 elections.
+In Table 3, treated voters were stopped between 2014 and 2016, while controls were stopped between 2016 and 2018.
+Finally, Table 4 presents the treatment effect for voters stopped between 2016 and 2018, relative to their controls stopped between the 2018 and 2020 elections.
+In every year, there is a statistically significant, negative treatment effect for non-Black voters.
+In 2014 and 2016, the effect is significantly smaller for Black individuals, though in 2018 the treatment effect for Black and non-Black voters is statistically indistinguishable.
+
+\begin{singlespace}
+\input{"../temp/dind_reg_y2014-11-04.tex"}
+\end{singlespace}
+
+\begin{singlespace}
+\input{"../temp/dind_reg_y2016-11-08.tex"}
+\end{singlespace}
+
+\begin{singlespace}
+\input{"../temp/dind_reg_y2018-11-06.tex"}
+\end{singlespace}
+
+# Testing Robustness of L2 Racial Estimates {-}
+
+As discussed in the body of this manuscript, our municipality-level racial estimates are constructed by aggregating up from individual-level records provided by L2.
+Because L2 uses statistical modeling to infer voters' race---not self-reported information---there is potential room for error in these estimates.
+
+Because there are no precise estimates of the racial demographics of the registered electorate in each city, we compare the estimated Black share of each municipality to the Black share of the citizen voting age population (CVAP) in each municipality.
+This method is not without drawbacks: if different cities have different racial registration rates, they will not track perfectly.
+To mitigate some of this discrepancy, we adjust the Black share of the electorate in each municipality by the racial registration gap in that municipality's state, according to the Current Population Survey's (CPS) 2018 data.
+For example, according to the CPS, 27.0% of the citizen population in Alabama was Black in 2018, but just 26.4% of registered voters were Black.
+We therefore add 0.6% to the estimated Black share of the electorate in each municipality in Alabama, so that it might more closely mirror the Black share of CVAP.
+
+In Table 5 we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level and adjusted according to the CPS, relative to the Census Bureau's CVAP estimate.
+Because it seems possible that these errors vary by population size, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.
+
+\begin{singlespace}
+```{r mae-chunck, echo = F, warning = F}
+t <- readRDS("./temp/maes.rds") %>%
+  mutate_all(~ gsub("[%]", "\\\\%", .))
+j <- t %>%
+  mutate_all(linebreak) %>%
+  knitr::kable(booktabs = T, caption = "(\\#tab:mae) MAE of L2 Municipality Estimates, CVAP", linesep = "", escape = F,
+               col.names = linebreak(colnames(t)),
+               align = "c") %>%
+  kable_styling(latex_options = c("HOLD_position"),
+                position = "center")
+j
+```
+\end{singlespace}
+
+Table 5 makes clear that the adjusted Black estimates of the electorate mirror the Black share of CVAP very closely: for no group of municipalities does the MAE exceed 3%.
+This seems to indicate that the L2 racial estimates are quite good when aggregated to the municipal level.
+
+In Table 6, we show that the difference between the adjusted estimate of the Black share of the electorate and the Black share of the CVAP is entirely unrelated to cities' per-capita fees and fines, after controlling for other characteristics.
+Given the low MAE and the lack of relationship between the error and the fees and fines, we conclude that the municipal-level racial estimates from the individual-level records are reasonable and unbiased.
+
+\begin{singlespace}
+\input{"../temp/mae_clean.tex"}
+\end{singlespace}
+
+# Regression Table for 2018 Cross-Sectional Municipality Model {-}
+
+In Table 7 we present the full results of the econometric used to test the cross-sectional relationship between per-capita fees and fines, and 2018 municipal turnout.
+The table shows that a doubling of the fees and fines collected per capita is associated with a 0.3 percentage point reduction in overall turnout.
+That same doubling, however, is associated with a 0.4 percentage point *increase* in the Black turnout.
+While these point estimates are quite small, it is worth keeping in mind that the range of fees and fines per capita is very wide.
+The interquartile ranges of fees and fines per capita stretches from \$1.96 to \$20.63---a more than ten-fold increase.
+
+\begin{singlespace}
+\input{"../temp/cog_cross_clean.tex"}
+\end{singlespace}
+
+# Regression Table for Survey Data {-}
+
+Here we present the regression table reported in the national survey data section of the manuscript.
+In model 1 we test whether personal or proximal contact with a police stop is differentially associated with turnout for Black and non-Black respondents.
+In this model, *Stopped in Past 12 Months* captures the relationship between police stops and non-Black respondents; *Stopped in Past 12 Months × Black* tests whether this relationship is different for Black respondents.
+
+Models 2, 3, and 4 test whether the relationship is different for other non-white groups. Finally, model 5 tests the relationship between turnout and a historical arrest.
+
+\begin{singlespace}
+\input{"../temp/anes_clean.tex"}
+\end{singlespace}
+
+Model 1 in Table 8 shows that Black individuals who had been stopped by the police (or had a family member stopped) in the preceding 12 months were 9 percentage points more likely to vote in 2020, other things equal; they were not related to turnout for non-Black respondents.
+Police stops are not, however, associated with different turnout effects for other non-white groups.
+Moreover, as discussed in the body of the paper, historical arrests were uniformly associated with a decrease in turnout of 4 percentage points for Black and non-Black respondents alike.
+
 \newpage

### 2021-07-23 markdown/si.tex
submission docs

@@
 
-\hypertarget{testing-robustness-of-l2-racial-estimates}{%
-\section*{Testing Robustness of L2 Racial Estimates}\label{testing-robustness-of-l2-racial-estimates}}
-\addcontentsline{toc}{section}{Testing Robustness of L2 Racial Estimates}
-
-As discussed in the body of this manuscript, our municipality-level racial estimates are constructed by aggregating up from individual-level records provided by L2.
-Because L2 uses statistical modeling to infer voters' race---not self-reported information---there is potential room for error in these estimates.
-
-Because there are no precise estimates of the racial demographics of the registered electorate in each state, we compare the estimated Black share of each municipality to the Black share of the citizen voting age population (CVAP) in each municipality.
-This method is not without drawbacks: if different cities have different racial registration rates, they will not track the perfectly.
-To mitigate some of this discrepancy, we adjust the Black share of the electorate in each municipality by the racial registration gap in that municipality's state, according to the Current Population Survey's (CPS) 2018 data.
-For example, according to the CPS, 27.0\% of the CVAP in Alabama was Black in 2018, but just 26.4\% of registered voters were Black.
-We therefore add 0.6\% to the estimated Black share of the electorate in each municipality in Alabama, so that it might more closely mirror the Black share of CVAP.
-
-In Table \ref{tab:mae} we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level and adjusted according to the CPS, relative to the Census Bureau's CVAP estimate.
-Because it seems possible that these errors vary by population size, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.
-
-\begin{singlespace}
-\begin{table}[H]
-
-\caption{\label{tab:mae-chunck}\label{tab:mae} MAE of L2 Municipality Estimates, CVAP}
-\centering
-\begin{tabular}[t]{ccccc}
-\toprule
-Bottom Quartile & Second Quartile & Third Quartile & Fourth Quartile & Overall\\
-\midrule
-2.40\% & 2.38\% & 2.24\% & 2.70\% & 2.42\%\\
-\bottomrule
-\end{tabular}
-\end{table}
-\end{singlespace}
-
-Table \ref{tab:mae} makes clear that the adjusted Black estimates of the electorate mirror the Black share of CVAP very closely: for no group of municipalities does the MAE exceed 3\%.
-This seems to indicate that the L2 racial estimates are quite good when aggregated to the municipal level.
-
-In Table \ref{tab:mae:reg}, we show that the difference between the adjusted estimate of the Black share of the electorate and the Black share of the CVAP is entirely unrelated to cities' per-capita fees and fines, after controlling for other characteristics.
-Given the low MAE and the lack of relationship between the error and the fees and fines, we conclude that the municipal-level racial estimates from the individual-level records are reasonable and unbiased.
-
-\begin{singlespace}
-\input{"../temp/mae_clean.tex"}
-\end{singlespace}
-
-\hypertarget{regression-table-for-survey-data}{%
-\section*{Regression Table for Survey Data}\label{regression-table-for-survey-data}}
-\addcontentsline{toc}{section}{Regression Table for Survey Data}
-
-Here we present the regression table reported in the national survey data section of the manuscript.
-In model 1 we test whether personal or proximal contact with a police stop is differentially associated with turnout for Black and non-Black respondents.
-In this model, \emph{Stopped in Past 12 Months} captures the relationship between police stops and non-Black respondents; \emph{Stopped in Past 12 Months × Black} tests whether this relationship is different for Black respondents.
-
-Models 2, 3, and 4 test whether the relationship is different for other non-white groups. Finally, model 5 tests the relationship between turnout and a historical arrest.
-
-\begin{singlespace}
-\input{"../temp/anes_clean.tex"}
-\end{singlespace}
-
-Model 1 in Table \ref{tab:anes-reg} shows that Black individuals who had been stopped by the police (or had a family member stopped) in the preceding 12 months were 9 percentage points more likely to vote in 2020, other things equal; they were not related to turnout for non-Black respondents.
-Police stops are not, however, associated with different turnout effects for other non-white groups.
-Moreover, as discussed in the body of the paper, historical arrests were uniformly associated with a decrease in turnout of 4 percentage points for Black and non-Black respondents alike.
-
-\hypertarget{regression-table-for-2018-cross-sectional-municipality-model}{%
-\section*{Regression Table for 2018 Cross-Sectional Municipality Model}\label{regression-table-for-2018-cross-sectional-municipality-model}}
-\addcontentsline{toc}{section}{Regression Table for 2018 Cross-Sectional Municipality Model}
-
-In Table \ref{tab:cog-cross-reg} we present the full results of the econometric used to test the cross-sectional relationship between per-capita fees and fines, and 2018 municipal turnout.
-The table shows that a doubling of the fees and fines collected per capita is associated with a 0.3 percentage point reduction in overall turnout.
-That same doubling, however, is associated with a 0.4 percentage point \emph{increase} in the Black turnout.
-While these point estimates are quite small, it is worth keeping in mind that the range of fees and fines per capita is very wide.
-The interquartile ranges of fees and fines per capita stretches from \$1.96 to \$20.63---a more than ten-fold increase.
-
-\begin{singlespace}
-\input{"../temp/cog_cross_clean.tex"}
-\end{singlespace}
-
 \hypertarget{administrative-matching-robustness-check}{%
@@
 
+\hypertarget{regression-tables-for-individual-treatment-years}{%
+\section*{Regression Tables for Individual Treatment Years}\label{regression-tables-for-individual-treatment-years}}
+\addcontentsline{toc}{section}{Regression Tables for Individual Treatment Years}
+
+In the body of this manuscript, we present only the overall treatment effects for the police stops in Hillsborough County, which are effectively averaged across all three years.
+Here, in Tables \ref{tab:dind-table-2014}--\ref{tab:dind-table-2018}, we present the results for each group of treated and control voters.
+In Table \ref{tab:dind-table-2014}, all treated voters were stopped between the 2012 and 2014 elections, and all controls were stopped between the 2014 and 2016 elections.
+In Table \ref{tab:dind-table-2016}, treated voters were stopped between 2014 and 2016, while controls were stopped between 2016 and 2018.
+Finally, Table \ref{tab:dind-table-2018} presents the treatment effect for voters stopped between 2016 and 2018, relative to their controls stopped between the 2018 and 2020 elections.
+In every year, there is a statistically significant, negative treatment effect for non-Black voters.
+In 2014 and 2016, the effect is significantly smaller for Black individuals, though in 2018 the treatment effect for Black and non-Black voters is statistically indistinguishable.
+
+\begin{singlespace}
+\input{"../temp/dind_reg_y2014-11-04.tex"}
+\end{singlespace}
+
+\begin{singlespace}
+\input{"../temp/dind_reg_y2016-11-08.tex"}
+\end{singlespace}
+
+\begin{singlespace}
+\input{"../temp/dind_reg_y2018-11-06.tex"}
+\end{singlespace}
+
+\hypertarget{testing-robustness-of-l2-racial-estimates}{%
+\section*{Testing Robustness of L2 Racial Estimates}\label{testing-robustness-of-l2-racial-estimates}}
+\addcontentsline{toc}{section}{Testing Robustness of L2 Racial Estimates}
+
+As discussed in the body of this manuscript, our municipality-level racial estimates are constructed by aggregating up from individual-level records provided by L2.
+Because L2 uses statistical modeling to infer voters' race---not self-reported information---there is potential room for error in these estimates.
+
+Because there are no precise estimates of the racial demographics of the registered electorate in each city, we compare the estimated Black share of each municipality to the Black share of the citizen voting age population (CVAP) in each municipality.
+This method is not without drawbacks: if different cities have different racial registration rates, they will not track perfectly.
+To mitigate some of this discrepancy, we adjust the Black share of the electorate in each municipality by the racial registration gap in that municipality's state, according to the Current Population Survey's (CPS) 2018 data.
+For example, according to the CPS, 27.0\% of the citizen population in Alabama was Black in 2018, but just 26.4\% of registered voters were Black.
+We therefore add 0.6\% to the estimated Black share of the electorate in each municipality in Alabama, so that it might more closely mirror the Black share of CVAP.
+
+In Table \ref{tab:mae} we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level and adjusted according to the CPS, relative to the Census Bureau's CVAP estimate.
+Because it seems possible that these errors vary by population size, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.
+
+\begin{singlespace}
+\begin{table}[H]
+
+\caption{\label{tab:mae-chunck}\label{tab:mae} MAE of L2 Municipality Estimates, CVAP}
+\centering
+\begin{tabular}[t]{ccccc}
+\toprule
+Bottom Quartile & Second Quartile & Third Quartile & Fourth Quartile & Overall\\
+\midrule
+2.40\% & 2.38\% & 2.24\% & 2.70\% & 2.42\%\\
+\bottomrule
+\end{tabular}
+\end{table}
+\end{singlespace}
+
+Table \ref{tab:mae} makes clear that the adjusted Black estimates of the electorate mirror the Black share of CVAP very closely: for no group of municipalities does the MAE exceed 3\%.
+This seems to indicate that the L2 racial estimates are quite good when aggregated to the municipal level.
+
+In Table \ref{tab:mae:reg}, we show that the difference between the adjusted estimate of the Black share of the electorate and the Black share of the CVAP is entirely unrelated to cities' per-capita fees and fines, after controlling for other characteristics.
+Given the low MAE and the lack of relationship between the error and the fees and fines, we conclude that the municipal-level racial estimates from the individual-level records are reasonable and unbiased.
+
+\begin{singlespace}
+\input{"../temp/mae_clean.tex"}
+\end{singlespace}
+
+\hypertarget{regression-table-for-2018-cross-sectional-municipality-model}{%
+\section*{Regression Table for 2018 Cross-Sectional Municipality Model}\label{regression-table-for-2018-cross-sectional-municipality-model}}
+\addcontentsline{toc}{section}{Regression Table for 2018 Cross-Sectional Municipality Model}
+
+In Table \ref{tab:cog-cross-reg} we present the full results of the econometric used to test the cross-sectional relationship between per-capita fees and fines, and 2018 municipal turnout.
+The table shows that a doubling of the fees and fines collected per capita is associated with a 0.3 percentage point reduction in overall turnout.
+That same doubling, however, is associated with a 0.4 percentage point \emph{increase} in the Black turnout.
+While these point estimates are quite small, it is worth keeping in mind that the range of fees and fines per capita is very wide.
+The interquartile ranges of fees and fines per capita stretches from \$1.96 to \$20.63---a more than ten-fold increase.
+
+\begin{singlespace}
+\input{"../temp/cog_cross_clean.tex"}
+\end{singlespace}
+
+\hypertarget{regression-table-for-survey-data}{%
+\section*{Regression Table for Survey Data}\label{regression-table-for-survey-data}}
+\addcontentsline{toc}{section}{Regression Table for Survey Data}
+
+Here we present the regression table reported in the national survey data section of the manuscript.
+In model 1 we test whether personal or proximal contact with a police stop is differentially associated with turnout for Black and non-Black respondents.
+In this model, \emph{Stopped in Past 12 Months} captures the relationship between police stops and non-Black respondents; \emph{Stopped in Past 12 Months × Black} tests whether this relationship is different for Black respondents.
+
+Models 2, 3, and 4 test whether the relationship is different for other non-white groups. Finally, model 5 tests the relationship between turnout and a historical arrest.
+
+\begin{singlespace}
+\input{"../temp/anes_clean.tex"}
+\end{singlespace}
+
+Model 1 in Table \ref{tab:anes-reg} shows that Black individuals who had been stopped by the police (or had a family member stopped) in the preceding 12 months were 9 percentage points more likely to vote in 2020, other things equal; they were not related to turnout for non-Black respondents.
+Police stops are not, however, associated with different turnout effects for other non-white groups.
+Moreover, as discussed in the body of the paper, historical arrests were uniformly associated with a decrease in turnout of 4 percentage points for Black and non-Black respondents alike.
+
 \newpage

### 2021-07-23 code/00_initialize.R

@@ -4,6 +4,7 @@ library(rgdal)
 library(sqldf)
 library(Metrics)
 library(RSQLite)
+library(tidycensus)
 library(multcomp)
 library(miceadds)
 library(Matching)

### 2021-07-23 code/04_anes.R

@@ -16,7 +16,7 @@ anes_pre <- anes_pre %>%
 
 anes_pre$party <- factor(anes_pre$party, levels = c("DEM", "REP", "OTH"))
 
-income <- fread("../washington_covid/raw_data/income_lu.csv")
+income <- fread("../regular_data/anes/income_lu.csv")
 
 anes_pre <- left_join(anes_pre, income) %>% 
   mutate(income = income / 10000)

### 2021-07-23 code/hills/05_regression.R

@@ -13,7 +13,7 @@ matches <- left_join(matches, select(hills_pre_match, voter_id, first_tr_year),
                                        ifelse(first_tr_year == 3, "2018-11-06", "XX"))),
          first_tr_year = as.Date(first_tr_year))
 
-hist <- readRDS("temp/full_raw_coded_hills_w_bgs.rds") %>%
+hist <- readRDS("C:/Users/morrisk/Desktop/full_raw_coded_hills_w_bgs.rds") %>%
   select(voter_id, starts_with("v1"), v08) %>%
   pivot_longer(!starts_with("vo"), names_to = "year", values_to = "to")
 
@@ -51,17 +51,24 @@ cleanup("matches")
 gc()
 
 ##########################################################
-ll <- matches %>%
+ll <- bind_rows(mutate(matches, first_tr_year = as.character(first_tr_year)),
+                mutate(matches, first_tr_year = "Overall")) %>%
   filter(period <= 0.5) %>% 
-  group_by(treated, period, black_t) %>%
+  group_by(treated, period, black_t, first_tr_year) %>%
   summarize(to = weighted.mean(to, weight)) %>% 
   mutate(treated = ifelse(treated, "Treated", "Control"),
          black = ifelse(black_t, "Black Voters", "Non-Black Voters"))
 
 ll$treated <- factor(ll$treated, levels = c("Treated", "Control"))
 
+ll <- ll %>% 
+  mutate(first_tr_year = ifelse(first_tr_year == "Overall", first_tr_year,
+                                paste("t = 0\nin", substring(first_tr_year, 1, 4))))
+
+ll$first_tr_year <- factor(ll$first_tr_year, levels = unique(ll$first_tr_year))
+
 p2 <- ggplot(data = ll) + 
-  facet_grid( ~ black) +
+  facet_grid(first_tr_year ~ black) +
   geom_rect(aes(xmin = -.49, xmax = 0.5, ymin = 0, ymax = Inf),
             alpha = 0.03, color = "black", fill = "yellow") +
   geom_line(data =ll, aes(x = period, y = to, linetype = treated)) +
@@ -81,13 +88,12 @@ p2 <- ggplot(data = ll) +
   labs(x = "t", y = "Turnout",
        linetype = "Treatment Group",
        shape = "Treatment Group",
-       caption = "Treatment occurs inside of yellow band.") +
+       caption = "Treatment occurs inside of yellow band.", ) +
[…]

### 2021-07-23 code/hills/06_rob_windows.R

@@ -59,7 +59,7 @@ lapply(c(1:23), function(i){
 
 
 #####################################
-hist <- readRDS("temp/full_raw_coded_hills_w_bgs.rds") %>%
+hist <- readRDS("C:/Users/morrisk/Desktop/full_raw_coded_hills_w_bgs.rds") %>%
   select(voter_id, starts_with("v1"), v08, v07) %>%
   pivot_longer(!starts_with("vo"), names_to = "year", values_to = "to")
 

### 2021-07-23 code/misc/code_for_natinoal_to.R

@@ -1,0 +1,235 @@
+library(RSQLite)
+library(rgdal)
+library(data.table)
+library(tidyverse)
+
+db_rolls <- dbConnect(SQLite(), "./data/national_file.db")
+
+fips_codes <- fread("./data/fips_codes.csv")
+
+dbListTables(db_rolls)
+
+national_file <- rbindlist(lapply(dbListTables(db_rolls), function(s){
+  scode <- substring(s, 1, 2)
+  code_good <- str_pad(as.character(unique(filter(fips_codes, state == scode)$state_code)),
+                       pad = "0", side = "left", width = 2)
+  d <- dbGetQuery(db_rolls, paste0("select LALVOTERID,
+                                           Voters_FIPS,
+                                           Residence_Addresses_CensusTract,
+                                           Residence_Addresses_CensusBlockGroup,
+                                           Voters_Age,
+                                           Parties_Description,
+                                           EthnicGroups_EthnicGroup1Desc,
+                                           Voters_Gender,
+                                           State_Senate_District,
+                                           State_House_District,
+                                           State_Legislative_District,
+                                           Residence_Addresses_Latitude,
+                                           Residence_Addresses_Longitude,
+                                           Voters_OfficialRegDate,
+                                           state from [", s, "]")) %>% 
+    mutate(State_Senate_District = ifelse(State_Senate_District == "",
+                                          State_Legislative_District,
+                                          State_Senate_District),
+           GEOID = paste0(code_good, str_pad(Voters_FIPS, width = 3, side = "left", pad = "0"),
+                          str_pad(Residence_Addresses_CensusTract, width = 6, side = "left", pad = "0"),
+                          Residence_Addresses_CensusBlockGroup)) %>% 
+    select(-State_Legislative_District, -Voters_FIPS, -Residence_Addresses_CensusTract,
+           -Residence_Addresses_CensusBlockGroup)
+}))
+
+db_history <- dbConnect(SQLite(), "./data/national_file_history.db")
[…]

### 2021-07-23 code/process14.R

@@ -1,4 +1,4 @@
-files <- list.files("D:/national/post_2014", full.names = T, pattern = "*.zip")
+files <- list.files("E:/national/post_2014", full.names = T, pattern = "*.zip")
 
 
 for(f in files){
@@ -41,7 +41,7 @@ for(f in files){
 ##############################
 files <- list.files("temp", pattern = "*to_14_no_block.rds", full.names = T)
 
-db18 <- dbConnect(SQLite(), "D:/national_file.db")
+db18 <- dbConnect(SQLite(), "E:/national_file.db")
 
 for(f in files){
   s <- substring(f, 6, 7)

### 2022-02-14 markdown/draft_paper.Rmd
pre 2022 edits

--- 2021-04-30 markdown/draft_paper.Rmd
@@
 ---
-title: "Policing for Profit and the Mobilization of Black Voters"
+title: "Ticketing and Turnout: How Policing for Profit Shapes Democratic Participation"
 
@@
 Despite this burgeoning literature, no research has directly investigated how police ticketing practices affect political participation.
-We use three approaches to answer this question: national survey data, a city-level analysis using Census of Governments data and the national voter file, and individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019.
-The survey data show that Black people who report that they were recently stopped by police are more likely to vote compared to those who were not stopped.
-Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.6 percentage point turnout decrease but was not associated with Black turnout.
-In Tampa, Florida, we estimate that being ticketed decreases an individual’s likelihood of voting in federal elections by 1.7 percentage points, but depressive effects are smaller for Black residents.
+We use three approaches to answer this question: we leverage individual-level administrative ticketing data from Hillsborough County, Florida between 2010 and 2020, a city-level analysis using Census of Governments data and the national voter file, and national survey data.
+We use a genetic matching algorithm and difference-in-differences to estimate that being ticketed decreases an individual’s likelihood of voting in federal elections by 1.7 percentage points, but depressive effects are smaller for Black residents.
+Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 was associated with a roughly 0.04 percentage point turnout decrease but was not associated with any change in Black turnout.
+The survey data show that Black people who report that they or a family member were recently stopped by police are more likely to vote than those who reported no such contact.
 
@@
 The implementation of the Black Codes, convict leasing, and sharecropping systems marked a transition to a new stage of racial capitalism, wherein criminalization provided an easily-exploited labor supply that offset costs that the state incurred by coercing their labor [@Lichtenstein1996; @Mancini1978].
-Contemporary fines and fees practices have been directly compared to sharecropping because both structures share “a long-term pattern of financial exploitation based on race… that limits the life-choices of the affected population” [@Blessett2016, page 113].
+Contemporary fines and fees practices have been directly compared to sharecropping because both structures share “a long-term pattern of financial exploitation based on race… that limits the life-choices of the affected population” [@Blessett2016: 113].
 
 In the 20th century, residential segregation simultaneously fueled the racial wealth gap and ensured that criminalization was both spatially and racially concentrated [@Rothstein2017; @Hinton2021].
-At the level of federal policy, racial threat and whites’ attribution of criminality to Blackness [@Muhammad2010] prompted a shift “from the War on Poverty to the War on Crime” wherein Black communities’ demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration [@Hinton2017; @Vargas2017a].
+At the level of federal policy, racial threat and whites’ attribution of criminality to Blackness [@Muhammad2010] prompted a shift from the War on Poverty to the War on Crime wherein Black communities’ demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration [@Hinton2017; @Vargas2017].
 
@@
 
-Black Americans can therefore situate exploitative ticketing practices in a longer historical legacy of collective disparate treatment and violence at the hands of the state.
-We argue that Black voters’ recognition of discriminatory ticketing practices facilitates a “linked fate” political analysis that motivates voting behavior distinct from other forms of criminalization, such as criminal conviction or incarceration.
-We expect both ticketing and incarceration to spark a recognition of “a sense of injustice” among Black Americans, but we argue that ticketing should ultimately mobilize Black voters (unlike incarceration, which discourages Black voters more than whites [@White2019]).
+# Theory {-}
 
-Ticketing produces substantively different experiences than being arrested or incarcerated.
-While tickets can lead to driver’s license suspensions or, in a smaller subset of cases, nonpayment incarceration, tickets are generally far less disruptive than criminal convictions and prison terms, and we argue that this difference should lead to different political behaviors.
-For example, one participant in @Lerman2014 who had served five years of probation after a criminal conviction reported, “I feel like if I contact a senator or governor, they’ll probably want to put me in jail and leave me as a troublemaker...
-That’s how I actually feel: ‘I better stay below the radar ’cause this guy’s tryin’ to start trouble’” [@Lerman2014, page 210].
-While formerly incarcerated people or people who have experienced criminal legal supervision may avoid voting due to the same type of fear of state surveillance and control that motivates their avoidance of medical or educational institutions [@Brayne2014], we argue that being ticketed should not produce the same chilling effect---ticketing should not prompt Black people to use political withdrawal as a self-preservation strategy.
+As the preceding sections make clear, past work on the political ramifications of criminal legal contact has largely determined that such contact is demobilizing.
+Scholars have argued that all contact with the criminal legal system causes political withdrawal, and that the severity of the withdrawal varies according to the intensity of the contact.
+This finding may not hold true for lower-level criminal legal contact, however.
+We argue that police ticketing may be an exception to this rule for two reasons: (1) police stops are far less disruptive to Americans’ lives than arrests or periods of incarceration, and (2), the injustice narrative framework [@Walker2020a] indicates that the explicit politicization of police stops by the Black Lives Matter movement in recent years should be mobilizing for Black Americans.
 
-Additionally, we argue that “policing for profit”---the experience of being ticketed while a municipality is palpably ramping up its fines and fees practices to collect revenue---is also substantively distinct from the experience of being arrested or incarcerated.
-In doing so, we extend Epp et al.’s theory of pretextual traffic stops politically socializing Black voters to the specific context of discriminatory police ticketing [@Epp2014].
-Black Americans who experience disproportionate ticketing are likely aware that they are being targeted by police for reasons unrelated to traffic safety.
+Receiving a ticket is a substantively different experience than being arrested or incarcerated.
+People who have been convicted of a crime and incarcerated are relegated to an alternate political membership status that Reuben Jonathan Miller and Forrest Stuart call “carceral citizenship,” subjecting them to forms of supervision and sanction “that are otherwise unavailable to [people] who have not been accused of a crime” [@Miller2017: 536].
+The politically discouraging effects of criminalization are even stronger for people who are convicted of felonies, who lose their right to vote in all but two U.S.
+states.
+This “civil death” [@Ewald2002; @Miller2012] explicitly removes Americans from the electorate; the felony conviction becomes “a durable constraint and marker of their citizenship” [@Lerman2014: 133].
+The experience of formal legal exclusion from voting forms a powerful piece of the “hidden curriculum” [@Meares2017] that teaches convicted individuals about their identities as citizens.
+Finally, the financial and social costs following a period of incarceration [@Bushway2007] can make it less likely that citizens invest the time and energy into registering to vote, learning where their polling place is, and determining which candidates they support.
+
+While tickets can lead to driver’s license suspensions or, in a smaller subset of cases, nonpayment incarceration, tickets are generally far less disruptive than criminal convictions and prison terms.
+Ticketed drivers are not disenfranchised, and they are not subject to the same forms of supervision and sanction that affect people with criminal convictions.
+Accordingly, individuals who have *not* been subjected to such intense supervision may be less likely to avoid state institutions compared to formerly incarcerated people pursuing a “strategic retreat.” [@Brayne2014], In short, if higher-intensity contact with the criminal legal system leads to political withdrawal because of carceral control, surveillance, and resultant lessons about citizenship, these same arguments are unlikely to apply to ticketed individuals.
+
+This is not to say that ticketing should be considered completely distinct from more intense forms of criminalization, but rather that a ticketed individual has not yet been relegated to “carceral citizenship.” .
+Walker’s research gives us reason to believe that drivers who feel that they were unfairly targeted by the police---and link that unfair experience to broader social narratives---can be *mobilized* by that experience.
+Moreover, given political organizing in recent years specifically about the racial injustices of discriminatory traffic stops, this injustice narrative is likely particularly accessible---and mobilizing---for Black Americans.
+
+The rise of the Black Lives Matter movement in 2013 constitutes a significant development for the political socialization of Black Americans, and many early Black Lives Matter protests either occurred in municipalities with exploitative ticketing practices or directly followed traffic stops that escalated into police violence [@Holpuch2015; @LaFraniere2016].
+The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious.
+It is possible that Black Lives Matter facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis---the movement arose shortly after fines and fees became a more salient and widespread threat to Black Americans’ material security, and the BLM movement helped to publicize these disparities.
+The injustice narrative framework proposed by @Walker2020a explains how individuals connect their “micro” experience of criminal legal contact with the “macro” narrative of racially discriminatory policing.
+
+The financially exploitative nature of recent ticketing increases should be particularly fertile ground for robust injustice narratives.
 One Buffalo, New York resident who is a plaintiff in a lawsuit regarding racist ticketing practices told a local newspaper in 2019: “In my mind, they weren’t balancing the budgets for Black lives, but with Black lives” [@McLeod2019].
 The city created a new traffic violations agency in 2015, spurring its yearly ticketing numbers to jump from around 32,000 to over 52,000.
-This financial aspect of ticketing should make it distinct from arrests and incarceration: much like the coercion of labor under the Black Codes, contemporary fines and fees practices are blatantly an effort to extract wealth from Black Americans.
-Although 20th century political rhetoric centered public safety as the mission of policing [CITE], exploitative ticketing practices cannot be reconciled with such rhetoric.
-In other words, to the extent that mass incarceration could be justified using narratives of “colorblind racism” (i.e., there’s a lot of crime happening in Black communities, so that’s why there’s more policing in those areas), racist ticketing practices do not enjoy the same rhetorical convenience.
 
-Ticketing is by far the most common form of criminal legal contact; in 2018, more than 24 million people experienced police contact in the context of a traffic stop, whereas about 5.17 million people are currently disenfranchised as a result of a felony conviction [@Harrell2020; @Uggen2020].
-At the same time, the most egregious local ticketing increases occurred largely over the past two decades [@Singla2020], and increases have been concentrated largely in Black municipalities [@Sances2017].
-These facts have been extensively discussed in mainstream media and should be widely known among Black voters [@Eligon2019; @Ehrenfreund2014].
-We expect a larger share of more affluent Black voters to be affected by ticketing than other forms of criminalization---arrests and incarceration are most common among individuals experiencing poverty [@Looney2018].
-Because perceptions of “linked fate” and related critiques of policing are even more salient among members of the Black middle class [@Dawson1995], we expect Black middle class voters to be mobilized by egregious ticketing practices.
-In other words, we argue that ticketing should ensnare more Black voters who are more likely to politicize the issue.
-
-Finally, the rise of the Black Lives Matter movement in 2013 constitutes a significant development for the political socialization of Black Americans, and the movement began in municipalities that targeted Black residents with tickets.
-The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious.
-Furthermore, local Black Lives Matter activism can change police practices.
-One recent study found that census places that saw Black Lives Matter protests experienced a 15 to 20 percent decrease in police killings over the following five year period [@Campbell2021].
-It’s possible that Black Lives Matter facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis---the movement arose shortly after fines and fees became a more salient and widespread threat to Black Americans’ material security, and many early Black Lives Matter protests either occurred in municipalities with exploitative ticketing practices or directly followed traffic stops that escalated into police violence [@Holpuch2015; @LaFraniere2016].
-
-Today, fines and fees disproportionately affect Black people, and Black political mobilization appears to mitigate some of the most egregious ticketing practices [@Sances2017].
-Accordingly, we expect that Black voters’ political behavior in response to police ticketing will be distinct from the political behavior of white voters, and further that ticketing should mobilize Black voter turnout in cities that have recently ramped up ticketing.
+We argue that many of the factors leading to withdrawal associated with higher-level criminal legal contact should not apply to police stops.
+At the same time, we expect that the national BLM movement should have encouraged Black Americans stopped by the police to connect their experience to macro-level trends, and that this should encourage political behaviors such as voting.
+Simply put, we expect that police stops are far less demobilizing than higher-level contact, and that they may in fact be mobilizing for Black Americans in an era of increased awareness of racially disparate policing practices.
 
@@
 
-We mobilize three distinct approaches to ask whether ticketing and police stops structure voter turnout, and whether these effects are unique for Black Americans.
-We look at national survey data, municipal-level finance data, and individual-level administrative records in a major American county to explore these effects.
-Each approach offers advantages and drawbacks; taken together, however, they dramatically advance our understanding of the political consequences of the most routine types of contact with the criminal legal system.
+We leverage three distinct approaches to ask whether ticketing and police stops structure voter turnout, and whether these effects are unique for Black Americans.
+Our theoretical estimand [@Lundberg2021] is the effect of police ticketing on the political socialization of ticketed individuals, which we proxy using their voter turnout.
 
-## National Survey Data {-}
+Each approach offers advantages and drawbacks.
+Our individual-level analysis in Hillsborough County exploits unusually detailed public data, which allows for a precise causal analysis that cannot be conducted in counties that do not provide ticketing records with personally identifiable information or states that do not include self-reported race data in the voter file.
+The empirical estimand is the voter turnout gap between Hillsborough County residents who have recently been ticketed and residents who will be ticketed in a future period, conditional on similar turnout in past elections and similar demographic characteristics.
+In isolation, however, results from one county may not be generalizable to other U.S.
+counties.
 
-We begin by turning to the American National Election Studies 2020 Time Series data (ANES).
-The ANES has been fielded in every presidential election year since 1948 and is among the most widely-used tools for understanding American’s political beliefs and behaviors, including their relationship with the criminal legal system [@Walker2020].
-It is weighted to be nationally representative of all American adults.
-In both 2016 and 2020, the ANES added new survey questions about respondent’s encounters with the police and the criminal legal system.
-We focus in particular on two questions: *During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?*, and *Have you ever been arrested, or has that never happened to you?* We include the roughly 87 percent of respondents that answered both questions, giving us a sample size of 7,347 respondents, of whom just over 11% identified as Black.
+We include two supplementary analyses to test the generalizability of the results from Hillsborough County.
+First, we analyze change in municipal-level revenue from fees and fines and voter turnout, which allows us to expand our analysis outside of Hillsborough County to about nine thousand American municipalities.
+This test does not allow us to directly observe the causal mechanism we argue is at play (police stops influencing political socialization, which in turn drives individual voter turnout), and replaces individual ticketing events with less-precise budget data.
+Also, if interpreted in isolation, the municipal-level analysis would suffer from the ecological fallacy: it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
 
-We use the survey questions to test the effect of a police stop on voter turnout---and, specifically, whether the effect is different for Black respondents.
-We also test whether an arrest is associated in the 2020 ANES with a lower probability of voting as described in previous work.
-In addition to the respondent’s contact with the criminal legal system, we control for age; sex; income; party affiliation; and self-described ideology.
-Using the ANES, we test our first two hypotheses:
+Finally, data from the 2020 American National Election Studies allow us to observe how tickets and arrests differentially influence voting behavior at the individual level among a nationally representative sample, but survey data analysis is subject to the vulnerabilities detailed in our introduction (e.g.
+measurement bias).
+Nevertheless, it provides important national insight into the phenomena we observe locally in Hillsborough County.
 
-*Hypothesis 1*: Personal and proximal experience of police stops is demobilizing for non-Black respondents, and mobilizing for Black respondents, other things equal.
+Taken together, these approaches dramatically advance our understanding of the political consequences of the most routine types of contact with the criminal legal system.
 
-*Hypothesis 2*: Personal experience of an arrest is demobilizing for individuals of all races, other things equal.
+## Individual-Level Causal Effects of Ticketing {-}
 
-There is an important caveat to the use of the ANES survey---namely, while the police stop question asks whether the respondent *or anyone in their family* was stopped in the past year, the arrest question asks only about the individual respondent.
-While this may muddy the water between direct and proximal contact with the criminal legal system, we expect that the national survey data will give us some insight into the uniquely politicizing nature of police stops for Black Americans.
+First, we turn to individual-level data from Hillsborough County, Florida (home to Tampa). 
+Hillsborough County makes a unique set of data publicly available.
+The county clerk makes information available about every traffic stop in the county going back to 2003.
+This data includes the name and date of birth of the individual stopped; the date of the offense; the amount the individual paid for a ticket; and other information.
 
-## City-level relationship between voter turnout and fines and fees {-}
+To identify ticketed voters, we match the first and last names and dates of birth from the stop data against the Hillsborough County registered voter file.
+@Meredith2014 develops a test for assessing the prevalence of false-positives in administrative record matching.
+We present the results of that test in the Supplementary Information.
+We likely have a false-positive match of around 0.03 percent, a figure we consider too low to impact our results meaningfully.
 
-After an examination of the cross-sectional national survey data, we turn to our nationwide analysis of the relationship between municipal revenue raised from fees and fines, and turnout in the 2018 federal election.
+Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status [see @Nyhan2017].
+Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.^1^ We thus observe virtually all individuals who were registered to vote at any time during our period of study.
+Unique voter identification numbers allow us to avoid double-counting voters who are registered in multiple snapshots.
+We retain each voter’s earliest record, and geocode voters to their home census block groups.
+Because we argue that police contact is the driving force behind any turnout effect, we remove tickets issued by red-light cameras.
+
+By matching the police stop and voter records, we identify all voters who were ticketed between the 2012 and 2020 general elections (voters stopped between 2018 and 2020 elections serve only as controls).
+We collect self-reported information regarding the race of each voter from Florida’s public voter file rather than the police stop data.
+Voters are considered “treated” in the general election following their ticket.
+Treated voters are then matched to a control voter using a nearest-neighbor approach, with a genetic algorithm used to determine the best weight for each characteristic [@Sekhon2011].
+Control voters are individuals who are stopped in the two years following the post-treatment election of the treated voters.
+Put differently, if a voter is stopped between 2012 and 2014, their control voter must be an individual stopped between the 2014 and 2016 elections.
+A voter cannot both be a treated and control voter for the same election; therefore, someone ticketed between the 2012 and 2014 elections and again between the 2014 and 2016 elections cannot serve as a control for anyone ticketed between 2012 and 2014.
+We limit the target population to voters who are ticketed at some point in order to account for unobserved characteristics that motivate people who are ticketed at some point to turn out at higher rates than people who are never ticketed.
+
+We match voters on individual-level characteristics (race / ethnicity; gender; party affiliation; age; number of traffic stops prior to the treatment period) and block group-level characteristics from the 2012 5-year ACS estimates (median income; share of the population with some college; unemployment rate).
+We match exactly on the type of ticket (civil / criminal infraction; whether they paid a fine; whether they were stopped by the Tampa Police Department) to ensure that treated and control voters receive the same treatment.
+Finally, we match treated and control voters on their turnout in the three pre-treatment elections.
+
+We assume that after controlling for observable characteristics, past turnout, *and* the unobservable characteristics associated with receiving a ticket, the timing of the ticket is effectively random.
+In short, any turnout difference between the treated voters and their controls is the causal effect of a police stop on turnout.
+Our overall turnout effects are robust to much weaker assumptions: in the Supplementary Information, we demonstrate that our overall turnout results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
+
+Our analytical design thus incorporates two different causal approaches in order to improve the credibility of our identification assumptions.
+Leveraging pre-treatment turnout allows us to estimate a traditional difference-in-differences model, while the matching procedure improves the plausibility of the parallel trends assumption by reducing salient differences between the treated and control voters.
+For a more detailed discussion of how matching can improve upon traditional difference-in-difference approaches when using panel data, see @Imai2020.
+
+We then estimate the following equation:
+
+\begin{gather}
+\label{eq:1}
+v_{it}=\beta_0+\beta_1Treated_{i}+\beta_2Post Treatment_{t} + \nonumber \\
+\beta_3Treated_{i}\times Post Treatment_{t} + \\
+\beta_4Year_{t} + \delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
+\end{gather}
+
+Individual *i*'s turnout (*v*) in year *t* is a function of the year and whether they were stopped by the police.
+In the equation, *$\beta$~1~Treated~i~* measures the historical difference between treated voters and their controls.
+*$\beta$~2~Post Treatment~t~* measures whether turnout increased for controls in the first election following the treated voter’s stop, while *$\beta$~3~Treated~i~ × Post Treatment~t~* tests whether turnout changed differently for treated voters than their controls in the election following their police stop.
+*$\beta$~3~*, then, will capture the causal effect of a police stop on voter turnout; it is the unit-specific quantity measured in our empirical estimand [@Lundberg2021].
+*$\beta$~4~Year~t~* captures year fixed-effects depending on the timing of the police stop, and the matrix *$\delta$Z~i~* contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
+
+In some models, we also interact the treatment variable with a dummy indicating whether the voter is Black to determine race-specific treatment effects.
+
+## Voter turnout and municipal fines and fees collections {-}
+
+Next, we turn to our nationwide analysis of the relationship between municipal revenue raised from fees and fines and turnout.
 Our data come from two primary sources: the US Census Bureau’s Census of Governments Data (COG), and registered voter files from L2 Political.
@@
 **Census of Governments**: Every five years, the US Census Bureau collects data from governmental bodies around the country.
-We use two snapshots of the COG: one that covers the years 2008 -- 2012, and another that covers 2013 -- 2017.
+We use two waves of the COG: one that covers the years 2008 -- 2012, and another that covers 2013 -- 2017.
 The COG asks municipalities to report how much revenue they collect from “penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation...
@@
 L2 collects voter files from around the country and merges them with proprietary data that estimates other voter- and household-level characteristics such as race and education.
-L2 also geocodes voters’ residential addresses.
-
-We merge the geocoded voter files with “place” and “county subdivision” shapefiles published by the US Census Bureau.
-By aggregating individual-level records to the municipal level, we are able to estimate the number of registered voters and the number of ballots cast in every city in the country.
-Moreover, by using the racial estimates provided by L2 we can estimate the number of ballots cast by voters of each race in each city.
-Each voters’ race is modeled based on L2’s algorithms and not self-reported, surely leading to errors at the individual-voter level.
-We assume this does not present a problem when records are aggregated to the municipal level.
-
-We calculate turnout by dividing the number of ballots cast according to L2 by the 5-year estimate of each municipality’s citizen voting-age population (CVAP) from the US Census Bureau.
-These estimates are available for individual racial groups.
-Because our turnout numerator and denominators come from different sources there is slight measurement error: our estimate indicates, for instance, that roughly 1 percent of municipalities had Black turnout above 100 percent.
+The individual-level records are aggregated up to the municipality level to determine the number of ballots cast for members of each race; these estimates are divided by 5-year citizen voting age population (CVAP) estimates from the Census Bureau to calculate turnout.
+As we show in the Supplementary Information, the L2 racial estimates closely track the municipal-level racial estimates from the Census Bureau.
+Because our turnout numerator and denominators come from different sources, there is slight measurement error: our estimate indicates, for instance, that roughly 1 percent of municipalities had Black turnout above 100 percent.
 Where more votes were cast than the Census estimate for CVAP, we recode turnout as 100 percent.
@@
 Because this measure is highly right-skewed, we use the natural log of fees and fines per capita (plus 1, to account for municipalities that collected no fees and fines).
-We also control for other municipal and state characteristics: racial composition, population density, median income, collegiate education, median age, share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality’s revenue that comes from the state or federal government in the 2012 and 2017 COGs.
-We retain the 8,954 municipalities whose data is reported to the COG in both 2012 and 2017 and meet the other criteria noted above.
+We also control for other municipal and state characteristics: racial composition, population density, median income, collegiate education, median age, and share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality’s revenue that comes from the state or federal government in the 2012 and 2017 COGs.
+We retain the 8,954 municipalities whose data is reported to the COG in both 2012 and 2017 and meet the other criteria noted above; these constitute the target population.
 
@@
 We run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
-Our national two-way fixed effect model allows us to test our first two hypotheses:
 
-*Hypothesis 3*: Increased reliance on fines and fees revenue at the city level reduces voter turnout at the city level.
+## National Survey Data {-}
 
-*Hypothesis 4*: The effect of the city-level relationship between fines and voter turnout is stronger for Black voters, given the historical and explicit racial injustice narratives used to explain these practices.
+Next, we turn to the American National Election Studies 2020 Time Series data (ANES).
+The ANES has been fielded in every presidential election year since 1948 and is among the most widely-used tools for understanding American’s political beliefs and behaviors, including their relationship with the criminal legal system [@Walker2020].
+It is weighted to be nationally representative of all American adults.
+In both 2016 and 2020, the ANES added new survey questions about respondent’s encounters with the police and the criminal legal system.
+We focus in particular on two questions: *During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?*, and *Have you ever been arrested, or has that never happened to you?* We include the roughly 87 percent of respondents that answered both questions, giving us a sample size of 7,347 respondents, of whom just over 11% identified as Black.
 
-## Individual-Level Effects of Ticketing {-}
+We use these survey questions to make descriptive inferences about how stops and arrests affect the voting behavior of the general population.
+The first descriptive theoretical estimand is the gap between the voter turnout rate of individuals who were recently stopped by the police or who have ever been arrested, and another is whether stops or arrests uniquely influence the political behavior of Black Americans.
+In addition to the respondent’s contact with the criminal legal system, we control for age; sex; income; education; party affiliation; self-described ideology; and reported 2016 turnout.
 
-Our national, cross-sectional analyses offer novel insight into the political socialization of low-level police contact.
-They cannot, however, directly observe the causal mechanism we argue is at play: namely, that direct contact with the criminal legal system influences turnout.
-If interpreted in isolation, our national analysis would suffer from the ecological fallacy.
-In other words, it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
-Moreover, there are many other factors that could be at play.
-Increased fees and fines could be correlated with increased policing in general, for instance.
-We are also unable to isolate the individual-level effect of being ticketed on turnout using this setup.
-
-Additionally, the national analyses cannot distinguish personal contact from proximal contact (“having a loved one who is a custodial citizen without yourself having had contact” [@Walker2017]).
-Because existing research investigating the effect of proximal contact has produced mixed results [@Burch2014; @Lee2014; @Sugie2015; @White2019; @Walker2017; @Walker2020], we are unable to prove that personal police contact is the only dynamic driving effects observed in our national analysis.
-For that reason, we turn to individual-level data from Hillsborough County, Florida (home to Tampa).
-
-Hillsborough County is interesting for theoretical reasons: Tampa is in the top decile of municipalities in terms of fees and fines increase between the 2012 and 2017 COGs, and its population puts it in the top 1 percent of cities nationwide.
-It also has a relatively large Black population, allowing us to test for racial differences in the turnout effect of ticketing.
-
-Further, the Tampa Police Department was scrutinized by the Tampa Bay Times in 2015 for its relentless ticketing of Black bicyclists [@Zayas2015].
-This investigation catalyzed a U.S.
-Department of Justice investigation and report, requested by Tampa’s mayor and police chief.
-In other words, there is strong evidence suggesting both racist targeting of tickets and potential publicity to catalyze distinct Black voter responses to the abusive behavior during the same time frame as our national analysis.
-Ticketing has also been expressly politicized in Tampa: Jane Castor, who was elected mayor in 2019, was Tampa’s police chief until 2015 and publicly defended her department’s disproportionate ticketing of Black bicyclists before retracting her defense ahead of her mayoral campaign [@Carlton2018].
-Her opponent, banker and philanthropist David Straz, campaigned against red-light cameras and focused his outreach in Tampa’s Black communities [@Frago2019].
-
-Hillsborough County also makes a unique set of data publicly available.
-The county clerk makes information available about every traffic stop in the county going back to 2003.
-This data includes the name and date of birth of the individual stopped; the date of the offense; and the amount the individual paid for a ticket; and other information.
-
-To identify ticketed voters, we match the first and last names and dates of birth from court data against the Hillsborough County registered voter file.
-Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status [see @Nyhan2017].
-Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.^[Because such frequent snapshots are not available from L2, we here use the registered voter file made freely available by the state of Florida.] We thus observe virtually all individuals who were registered to vote at any time during our period of study.
-Unique voter identification numbers allow us to avoid double-counting voters who are registered in multiple snapshots.
-We retain each voter’s earliest record, and geocode voters to their home census block groups.
-Because we argue that police contact is the driving force behind any turnout effect, we remove tickets issued by red-light cameras.
-
-To improve the quality of the match between the two datasets, we remove all punctuation from all names and convert all names to lower-case.
-This means that a “Jonathan O’Shea” in one file would match a “jonathan oshea” in the other.
-@Meredith2014 develops a test for assessing the prevalence of false-positives in administrative record matching.
-We present the results of that test in the Supplementary Information.
-We likely have a false-positive match of around 0.03 percent, a figure we consider too low to impact our results meaningfully.
-
-By matching the police stop and voter records, we identify all voters who were ticketed between the 2012 and 2020 general elections (voters stopped between 2018 and 2020 elections serve only as controls).
-Voters are considered “treated” in the general election following their ticket.
-Treated voters are then matched to a control voter using a nearest-neighbor approach, with a genetic algorithm used to determine the best weight for each characteristic [@Sekhon2011].
-Control voters are individuals who are stopped in the two years following the post-treatment election of the treated voters.
-Put differently, if a voter is stopped between 2012 and 2014, their control voter must be an individual stopped between the 2014 and 2016 elections.
-A voter cannot both be a treated and control voter for the same election; therefore, someone ticketed between the 2012 and 2014 elections and again between the 2014 and 2016 elections cannot serve as a control for anyone ticketed between 2012 and 2014.
-
-We match voters on individual-level characteristics (race / ethnicity; gender; party affiliation; age; number of traffic stops prior to the treatment period) and block group-level characteristics from the 2012 5-year ACS estimates (median income; share of the population with some college; unemployment rate).
-We match exactly on the type of ticket (civil / criminal infraction; whether they paid a fine; whether they were stopped by the Tampa Police Department) to ensure that treated and control voters receive the same treatment.
-Finally, we exactly match treated and control voters on their turnout in the three pre-treatment elections.
-
-We assume that after controlling for observable characteristics, past turnout, *and* the unobservable characteristics associated with receiving a ticket, the timing of the ticket is effectively random.
-In short, any turnout difference between the treated voters and their controls is the causal effect of a police stop on turnout.
-It is important to note that our overall turnout effects are robust to much stricter assumptions.
-In the Supplementary Information we demonstrate that our primary reported results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
-
-Our analytical approach thus incorporates two different causal approaches.
-Leveraging pre-treatment turnout allows us to estimate a traditional difference-in-differences model.
-Difference-in-differences models assume that, in the absence of the treatment, any turnout gap between treated and control voters would have remained stable in the post-treatment period.
-While the validity of this assumption is commonly established by examining pre-treatment trends in turnout between the two groups, it can be improved upon by using the matching methodology described above.
-In the case at hand, we both establish that the turnout of treated voters was mirrored by that of their control voters prior to treatment, *and* that the observable characteristics of treated and control voters are similar---thus lending credence to the assumption that this gap would have remained constant absent treatment.
-Finally, by drawing controls from the population of individuals who were ticketed in subsequent years, we also indirectly control for any unobserved characteristics associated with receiving a ticket.
-For a more detailed discussion of how matching can improve upon traditional difference-in-difference approaches when using panel data, see @Imai2020.
-
-We then estimate the following equation:
-
-\begin{gather}
-\label{eq:1}
-v_{it}=\beta_0+\beta_1Treated_{i}+\beta_2Post Treatment_{t} + \nonumber \\
-\beta_3Treated_{i}\times Post Treatment_{t} + \\
-\delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
-\end{gather}
-
-Individual *i*'s turnout (*v*) in year *t* is a function of the year and whether they were stopped by the police.
-In the equation, *$\beta$~1~Treated~i~* measures the historical difference between treated voters and their controls.
-*$\beta$~2~Post Treatment~t~* measures whether turnout increased for controls in the first election following the treated voter’s stop, while *$\beta$~3~Treated~i~ × Post Treatment~t~* tests whether turnout changed differently for treated voters than their controls in the election following their police stop.
-*$\beta$~3~*, then, will capture the causal effect of a police stop on voter turnout.
-Finally, the matrix *$\delta$Z~i~* contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
-Equation 1 allows us to test Hypothesis 5:
-
-*Hypothesis 5*: Being ticketed reduces an individual’s likelihood of turning out in the subsequent election.
-
-We also estimate Equation 2, in which the treatment effect is interacted with whether a voter is Black (*$\beta$~4~Treated~i~ × Post Treatment~t~ × Black~i~*):
-
-\begin{gather}
-\label{eq:2}
-v_{it}=\beta_0+\beta_1Treated_{i}+\beta_2Post Treatment_{t} + \nonumber \\
-\beta_3Treated_{i}\times Post Treatment_{t} + \beta_4Treated_{i}\times Post Treatment_{t}\times Black_{i} +\\
-\delta{Y}_{i} + \delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
-\end{gather}
-
-where *$\delta$Y~it~* includes the dummy for Black interacted with the treatment and post treatment dummies. Equation 2 allows us to test Hypothesis 6:
-
-*Hypothesis 6*: The effect of being ticketed on an individual’s voter turnout is less negative / more positive if that individual is Black.
-
-<!-- Because Tampa holds off-year local elections, we are able to test whether ticketed voters target officials who are able to change local police practices.
-@Laniyonu2019 gives us reason to believe that the effect should be stronger for local elections.
-
-*Hypothesis 7*: Any potential mobilizing turnout effect for Black voters in Tampa is stronger for local (mayoral) elections, since those elections directly affect police practices. -->
+There is an important caveat to the use of the ANES survey---namely, while the police stop question asks whether the respondent *or anyone in their family* was stopped in the past year, the arrest question asks only about the individual respondent.
+While this may muddy the water between direct and proximal contact with the criminal legal system, we expect that the national survey data will give us some insight into the uniquely politicizing nature of police stops for Black Americans.
 
@@
 
-As discussed above, we begin by testing the relationship between police stops and turnout in the 2020 election, and then move to testing the relationship between fees and fines at the municipal level.
-While both tests give us insight into the political ramifications of low-level police contact, their cross-sectional nature cannot establish causality.
-To investigate causality, we also examine whether the turnout of individuals stopped by the police before an election was different than those stopped after the election in Hillsborough County, Florida.
-
-## National Survey Data {-}
-
-In this section we make use of the American National Election Studies 2020 Time Series Data (ANES).
-The test for this section is simple: we ask whether, after controlling for standard covariates, having personal or proximal contact with a police stop in the previous 12 months is associated with whether a respondent voted in the 2020 presidential election.
-We also ask whether this relationship was different for Black and non-Black respondents.
-We also use the ANES data to reconfirm prior literature demonstrating that higher-level contact with the criminal legal system is associated with lower turnout, as these relationships could have changed in the aftermath of the widespread protests following the police killing of George Floyd in 2020.
-
-Roughly 15 percent of non-Black respondents reported a police stop in the preceding 12 months, while the same was true for more than 22 percent of Black respondents.
-In Figure \ref{fig:anes} we present the results of our econometric models.
-In the left-hand panel, we show the predicted turnout of respondents who answered “yes” or “no” to the question *During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?* The right-hand panel, meanwhile, plots these relationships for respondents who answered “yes” or “no” to the question *Have you ever been arrested, or has that never happened to you?*.
-These are the predicted probabilities after controlling for respondents’ race / ethnicity; age; party; ideology; income; and education.
-The full regression table can be found in the Supplementary Information..
-
-```{r anes-cross, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:anes}Predicted Turnout, 2020", fig.pos = "!htpb", fig.align = "center"}
-load("temp/anes_plot.rdata")
-print(p2)
-```
-Figure \ref{fig:anes} demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (*p* = 0.006).
-The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (*p* = 0.52).
-Importantly, this effect is not a remnant of a white--nonwhite divide.
-As we show in the Supplementary Information, police stops were not differently related to turnout for Latinos than for non-Latinos; nor did they impact turnout differently for Asians than for non-Asians.
-The ANES results point, then, to the fact that police stops are uniquely associated with higher turnout for Black respondents.
-
-The second panel of Figure \ref{fig:anes} shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
-Importantly, the interaction between arrest status and the respondent’s race was not statistically significant.
-In other words, although police stops seem to be uniquely mobilizing for Black Americans, we fail to uncover evidence that arrests differentially structured subsequent Black- and non-Black turnout.
-
-These cross-sectional results cannot establish causality.
-It is possible that Black respondents who had been stopped by the police (or had family members who experienced a stop) differed from non-Black respondents with such contact in ways that cannot be captured by the survey data.
-However, our findings are consistent with a causal story that police stops are mobilizing for Black Americans---but that this is not the case for higher-level contact such as arrests.
-
-## Municipal-Level Results {-}
-
-Before testing the causal effect of fees and fines collections, we begin with a cross-sectional analysis of the relationship between fees and fines and turnout using ordinary least squares.
-Here, we regress municipality-level turnout in 2018 against fees and fines collections as reported in the 2017 COG, as well as a number of other covariates.
-In Figure \ref{fig:mef-2018} we present the marginal effect of fees and fines on municipal-level turnout.
-The plot shows the results from two separate models: one in which the dependent variable is Black turnout (as a share of CVAP), and a second in which the dependent variable is non-Black turnout.
-The figure also marks the interdecile range.
-The full regression table can be found in the Supplementary Information.
-
-```{r cross-18, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:mef-2018}Predicted Turnout, 2018", fig.pos = "H", fig.align = "center"}
-load("temp/mef_to.rdata")
-print(p2)
-```
-
-As Figure \ref{fig:mef-2018} makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 2.5 percentage points over the interdecile range, after controlling for the other covariates.
-The opposite is true for Black voters: over the same range, Black turnout *increases* by roughly 2.4 percentage points.
-Both relationships are statistically significant at the 95 confidence level.
-This does not prove that higher fees and fines increase Black turnout; cross-sectional regressions cannot establish causality.
-Nevertheless, Figure \ref{fig:mef-2018} is consistent with this story.
-
-We turn now to our two-way fixed effects model.
-As discussed above, we retain each municipality that reported their fees and fines data to the COG in both 2012 and 2017 (and met the other criteria discussed in the *Data and Design* section).
-The dependent variable in each model is calculated by dividing the number of ballots cast in 2014 and 2018 by the 5-year CVAP estimate from the same year.
-We run the two-way fixed effects on overall turnout, Black turnout, and non-Black turnout.
-The results of these models can be found in Table \ref{tab:twfe}.
-
-\begin{singlespace}
-\input{"../temp/2wfe_reg_clean.tex"}
-\end{singlespace}
-
-The results of the two-way fixed effects model are different than what we saw in the 2018 cross-sectional approach; namely, while Table \ref{tab:twfe} indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not significantly impact Black turnout.
-The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.06 percentage points.
-
-In Table \ref{tab:coarser}, we re-estimate the model from Table \ref{tab:twfe} but coarsen the data.
-Here, the dependent variable of interest is binary: we test whether turnout changed for municipalities who increased their per-capita fees and fines collections differently than municipalities where collections stayed the same or decreased.
-Municipalities that increased their per-capita fees and fines are considered “treated.”
-
-\begin{singlespace}
-\input{"../temp/coarser_reg_clean.tex"}
-\end{singlespace}
-
-The coefficient on *Treated × 2018* indicates that non-Black turnout dropped by about 0.5 percentage points in municipalities where fees and fines collections increased, relative to other municipalities.
-While this coefficient is slightly *positive* for Black voters, it is not statistically significantly different from 0.
-In other words, both Tables \ref{tab:twfe} and \ref{tab:coarser} indicate that increased fees and fines collections decrease non-Black turnout but have no impact on Black turnout.
+As discussed above, we begin by examining whether the turnout of individuals ticketed before an election was different from those ticketed after the election in Hillsborough County, Florida.
+Next, we test the relationship between fines and fees revenue reliance and voter turnout at the municipal level.
+We also test the relationship between police stops and turnout in the 2020 election using survey data.
 
@@
 
-Thus far, we have shown that voter turnout decreased in municipalities that increased fines and fees collections.
-We argue that this relationship is causal: increased fees and fines collections means that more residents have direct interactions with the criminal legal system.
-Based on prior literature, we assume there are indirect effects as well, as more residents know a family or community member who has been ticketed.
-While the national analysis gives us great breadth and an increased understanding of how this plays out across the country, municipal-level data leaves us unable to directly observe the causal mechanisms at play.
-
 To directly observe the effect of being stopped by the police on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
-As discussed above, we match individuals who were ticketed between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.^[Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
-The full sample is used in the actual matching process.]  Matching is done with replacement and ties are not broken.
-This means that some treated voters have multiple controls; the regression weights are calculated to allow for this possibility.
-In Table \ref{tab:balance} we present the results of the matching algorithm.
+As discussed above, we match individuals who were ticketed between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.^2^ Matching is done with replacement and ties are not broken.
+This means that some treated voters have multiple controls; the regression weights are calculated to account for this possibility.
+In Table 1 we present the results of the matching algorithm.
 As the table demonstrates, the selected control voters are very similar to the treated voters.
@@
 \begin{singlespace}
-```{r baltab-chunk, echo = F, warning = F}
-t <- readRDS("temp/balance_table_y.rds")
-j <- knitr::kable(t, booktabs = T, caption = "(\\#tab:balance) Balance Table", linesep = "",
-                  escape = F)  %>%
-  kable_styling(latex_options = c("hold_position"))
-
-j
-```
+\input{"../temp/balance_table.tex"}
 \end{singlespace}
 
-It is worth noting that voters who were stopped between 2012 and 2018 were far more likely to be Black and male than the general electorate, and live in Census block groups with moderately lower incomes.
-Unsurprisingly, they were also stopped at higher rates in the pre-treatment period than those never stopped between 2012 and 2018.
+It is worth noting that voters who were ticketed between 2012 and 2020 were far more likely to be Black and male than the general electorate, and live in Census block groups with moderately lower incomes.
 
-While Table \ref{tab:balance} indicates that our treatment voters and their matches are substantially similar to their matches, the validity of the difference-in-differences design requires that any turnout gap between treatment and control voters be comparable in the baseline period.
-In Figure \ref{fig:did1}, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped.
+In Figure 1, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped.
+In the top row, we present the turnout in 2008--2014 of the individuals stopped between 2012 and 2014 and their controls; the second row shows the 2010--2016 turnout for individuals stopped between 2014 and 2016 and their controls; and the third shows the treatment effect for those stopped in the 2 years prior to the 2018 midterms.
+Finally, in the bottom row, we present the overall turnout effects for these three elections.
 The first election following a treated voter’s stop is denoted as *t = 0* while the years in which *t* is less than zero are the periods prior to the stop.
-This means that for someone stopped in 2013 (and their controls), *t* is 0 in 2014, while *t* is equal to 0 in 2018 for an individual stopped between the 2016 and 2018 elections.
 
-```{r did1, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
+```{r did1, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "!htb", fig.align = "center"}
 p2 <- readRDS("temp/stopped_any_time_y.rds")
@@
 
-Figure \ref{fig:did1} makes a number of things immediately apparent.
-First, we can see that for both Black and non-Black voters the parallel trends assumption is satisfied.
-Of course, because we matched treated and control voters based on turnout prior to the ticket, this is unsurprising.
+Figure 1 makes a number of things immediately apparent.
+First, we can see that for both Black and non-Black voters the pre-treatment trends are identical.
+This, combined with the fact that treated and control voters mirror one another in terms of other characteristics, lends credibility to the parallel trends assumption.
+Secondly, Figure 1 provides preliminary visual evidence of the demobilizing effects of police stops in Hillsborough County.
+However, as the figure also makes clear, it seems that the negative effects are concentrated in the lower-salience midterm elections; there is little evidence of turnout effects in the 2016 presidential election.
 
-Table \ref{tab:dind-table} formalizes Figure \ref{fig:did1} into an ordinary least squares regression.
-Model 1 shows our overall causal effect, while Model 2 allows for the possibility that a ticket differentially mobilizes Black voters.
-The coefficients of note are *Treated × Post Treatment* and *Treated × Post Treatment × Black*.
+Table 2 formalizes the final row of Figure 1 into an ordinary least squares regression (the regression tables broken out for each year can be found in the Supplementary Information).
+Models 1 and 2 show our overall causal effect, while models 3 and 4 allow for the possibility that a ticket differentially mobilizes Black voters.
+In models 1 and 3, we include only the treatment, timing, and race dummies, while the full set of covariates used for the matching procedure are included in models 2 and 4.
+The empirical estimands are *Treated × Post Treatment* and *Treated × Post Treatment × Black*.
 In models 1 and 2, *Treated × Post Treatment* measures the overall treatment effect, and in models 3 and 4 it measures the treatment effect for non-Black voters.
@@
 
-As both Figure \ref{fig:did1} and Table \ref{tab:dind-table} make clear, police tickets meaningfully depressed turnout.
+As both Figure 1 and Table 2 make clear, police tickets meaningfully depressed turnout.
 In models 1 and 2, the estimated overall treatment effect is -1.5 percentage points.
-In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---nonBlack turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
-Although the treatment effect is still substantively quite large for Black individuals, the pattern follows our national analysis.
-It appears that, in Tampa and around the country, Black voters' turnout in federal elections is not as negatively impacted by police contact as that of non-Black individuals.
+In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---non-Black turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
+Although the treatment effect is still substantively quite large for Black individuals, Hillsborough County Black voters' turnout in federal elections was not as negatively impacted by police contact as that of non-Black individuals.
 
-<!-- As shown in model 5 and table XX, we find that being ticketed in the 90 days preceding a mayoral election in Tampa is demobilizing for Black voters, but not demobilizing for non-Black voters.
-Being ticketed decreased Black turnout by 0.5 percentage points.
--->
+## Municipal-Level Results {-}
+
+Before testing the causal effect of fees and fines collections on turnout, we begin with a cross-sectional analysis of the relationship using ordinary least squares.
+Here, we regress municipality-level turnout in 2018 against fees and fines collections as reported in the 2017 COG, as well as a number of other covariates.
+In Figure 2 we present the marginal effect of fees and fines on municipal-level turnout.
+The plot shows the results from two separate models: one in which the dependent variable is Black turnout (as a share of CVAP), and a second in which the dependent variable is non-Black turnout.
+The figure also marks the interdecile range.
+The full regression table can be found in the Supplementary Information.
+
+```{r cross-18, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:mef-2018}Predicted Turnout, 2018", fig.pos = "!htb", fig.align = "center"}
+load("temp/mef_to.rdata")
+print(p2)
+```
+
+As Figure 2 makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 1.5 percentage points over the interdecile range, after controlling for the other covariates.
+The opposite is true for Black voters: over the same range, Black turnout *increases* by roughly 2.4 percentage points.
+Both relationships are statistically significant at the 95 confidence level.
+This does not prove that higher fees and fines increase Black turnout; cross-sectional regressions cannot establish causality.
+Nevertheless, Figure 2 is consistent with this story.
+
+We turn now to our two-way fixed effects model.
+As discussed above, we retain each municipality that reported their fees and fines data to the COG in both 2012 and 2017 (and met the other criteria discussed in the *Data and Design* section).
+The dependent variable in each model is calculated by dividing the number of ballots cast in 2014 and 2018 by the 5-year CVAP estimate from the same year.
+We run the two-way fixed effects on overall turnout, Black turnout, and non-Black turnout.
+The results of these models can be found in Table 3.
+The average municipality included in this analysis raised $2.17 in fees and fines per resident in 2012, and the average municipality increased this per-capita figure by $0.47 between 2012 and 2017.
+Just over 10% of municipalities raised no revenue from fees and fines in either year.
+
+\begin{singlespace}
+\input{"../temp/2wfe_reg_clean.tex"}
+\end{singlespace}
+
+The results of the two-way fixed effects model are different from what we saw in the 2018 cross-sectional approach; namely, Table 3 indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not significantly impact Black turnout.
+The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.04 percentage points.
+
+## National Survey Data {-}
+
+In this section we make use of the American National Election Studies 2020 Time Series Data (ANES).
+The first test is simple: we ask whether, after controlling for standard covariates, having personal or proximal contact with a police stop in the previous 12 months is associated with whether a respondent voted in the 2020 presidential election.
+We also ask whether this relationship was different for Black and non-Black respondents.
+Finally, we use the ANES data to reconfirm prior literature demonstrating that higher-level contact with the criminal legal system is associated with lower turnout, as these relationships could have changed in the aftermath of the widespread protests following the police murder of George Floyd in 2020.
+
+Roughly 15 percent of non-Black respondents reported a police stop in the preceding 12 months, while the same was true for more than 22 percent of Black respondents.
+In Figure 3 we present the results of our econometric models.
+In the left-hand panel, we show the predicted turnout of respondents who answered “yes” or “no” to the question *During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?* The right-hand panel, meanwhile, plots these relationships for respondents who answered “yes” or “no” to the question *Have you ever been arrested, or has that never happened to you?*.
+These are the predicted probabilities after controlling for respondents’ race / ethnicity; age; party; ideology; income; education; and 2016 turnout.
+The full regression table can be found in the Supplementary Information..
+
+```{r anes-cross, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:anes}Predicted Turnout, 2020", fig.pos = "!htpb", fig.align = "center"}
+load("temp/anes_plot.rdata")
+print(p2)
+```
+
+Figure 3 demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (*p* = 0.005).
+The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (*p* = 0.27).
+Importantly, this effect is not a remnant of a white--nonwhite divide.
+As we show in the Supplementary Information, police stops were not differently related to turnout for Latinos than for non-Latinos; nor did they impact turnout differently for Asians than for non-Asians.
+The ANES results point, then, to the fact that police stops are uniquely associated with higher turnout for Black respondents.
+
+The second panel of Figure 3 shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
+Importantly, the interaction between arrest status and the respondent’s race was not statistically significant.
+In other words, although police stops seem to be uniquely mobilizing for Black Americans, we fail to uncover evidence that arrests differentially structured subsequent Black and non-Black turnout.
+
+This theoretical estimand is descriptive, and cross-sectional results cannot establish causality.
+It is possible that Black respondents who had been stopped by the police (or had family members who experienced a stop) differed from non-Black respondents with such contact in ways that cannot be captured by the survey data.
+However, our findings are consistent with a causal story that police stops are uniquely mobilizing for Black Americans---but this is not the case for higher-level contact, such as arrests.
 
@@
 
-While existing sociology and political science literature has examined the rise and collateral consequences of fines and fees as well as the effects of criminalization on political socialization, no study has investigated the causal relationship between ticketing and voter turnout.
+While existing sociological and political science literature has examined the rise and collateral consequences of fines and fees as well as the effects of criminalization on political socialization, no study has investigated the causal relationship between ticketing and voter turnout.
 Additionally, our study is among the first to use individual-level administrative data to investigate the relationship between criminalization and political participation.
 
-We first used survey data collected in the American National Election Studies 2016 and 2020 datasets to show how, unlike arrests, ticketing can mobilize Black voters.
-We found that Black people who reported personal or proximal police contact with a police stop in the last 12 months were 0.5 pp more likely to vote compared to Black people who did not report such contact.
-Non-Black respondents demonstrated no statistically significant result for police stops.
-Meanwhile, both Black and non-Black people who had been arrested at any point were less likely to vote, and we did not find significant differences between racial groups’ behaviors in response to arrests.
+Given how widespread police stops are and their relationship to racial injustice, their political implications demand close study.
+Accordingly, we investigate this question from a variety of perspectives, using multiple data sources and empirical approaches.
+What we find complicates our understanding of how lower-level police contact affects political participation.
+The national survey data and cross-sectional municipal-level analysis indicate that police contact is associated with higher turnout for Black Americans, and either unrelated or negatively related to turnout for others.
+Our causal models tell a slightly different story---they fail to uncover mobilizing effects for Black Americans.
+Nevertheless, our causal models *do* indicate that police stops are less demobilizing for Black individuals than for others.
+In this sense, our results all point in the same direction.
+Based on these three independent approaches, we conclude that the political consequences of police stops are unique for Black Americans---and that they are less demobilizing for Black Americans than others.
+Additionally, as @Walker2020a suggests, ticketed Black individuals may be politically mobilized for activities other than voting not observed in this study, such as contacting elected representatives or volunteering for campaigns.
 
-Next, we used a two-way fixed effects model to estimate the effect of increased fines and fees reliance at the city level on aggregate voter turnout in federal elections.
-We found that each 10 percent increase in fines and fees collected per resident is associated with a voter turnout decrease of about 0.06 percentage points, with no significant impact on Black turnout in particular---in other words, the demobilizing effect of ticketing increases at the city level is largely driven by non-Black voters.
+Our individual-level analysis based on Hillsborough County, Florida, advances our understanding of this dynamic while raising new questions.
+On the one hand, the causal results are highly robust, and the ticketing data allows us to identify the treatment fairly precisely.
+On the other hand, these are the only results in which police stops are associated with a *decrease* in turnout for Black individuals.
+This may be because this analysis tests the impact of direct contact with the police, rather than direct *or* proximal contact, as the ANES questions do.
+It may be because we can isolate the effect of a police stop from other, broader changes that may be correlated with increased fees and fines revenue in the municipal-level data.
+Or it may point to unique political circumstances surrounding race, policing, and political participation in Hillsborough County.
+We look forward to future scholarship that replicates and extends these Hillsborough County results.
+Nevertheless, that police stops are less demobilizing for Black Floridians in Hillsborough County---an effect that does not extend to other nonwhite residents---provides support for our general thesis that the political interpretation of these contacts with the criminal legal system are unique for Black Americans.
 
-In order to directly observe the causal mechanism, we then conducted an individual-level analysis of ticketing and voting behavior in Hillsborough County, Florida.
-Using a difference-in-differences design, we found that individuals who were ticketed in the 90-day period preceding a federal election were 1.7 percentage points less likely to vote compared to individuals who were ticketed following the election.
-The effect was smaller for Black individuals (1 percentage point less likely), which is consistent with our hypothesis that Black political responses to ticketing should be distinct from whites (and more mobilized by comparison).
+The difference between the cross-sectional and two-way fixed effects models using the municipality-level data is somewhat surprising.
+There are a few potential explanations for this mismatch.
+First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes in the two-way fixed effects models are smaller or not statistically significant.
+Along a similar vein, it is possible that a mobilizing effect of ticketing for Black voters in the city-level analysis is offset by higher-intensity forms of criminal legal contact, such as arrest and incarceration.
+The bulk of existing literature suggests that incarceration discourages political participation, and it is not unreasonable to assume that cities that ramp up ticketing of Black residents also ramp up arrest and incarceration of Black residents.
+If these phenomena coincide, that could explain why the city-level analysis produced no statistically significant effect for Black voters---the personally mobilizing effect of ticketing could be counterbalanced by the proximal chilling effect of incarceration, and because the city-level analysis is not as temporally sensitive, it is more difficult to isolate the effect of ticketing.
+At the same time, @Harris2020 indicates that when municipalities increase their fees and fines collections, relatively more *white* individuals are ticketed.
+@Shoub2020 demonstrates the corollary: when municipalities stop fewer motorists, the decrease is concentrated among white individuals.
+Existing research, then, indicates that a relatively constant share of the Black population is stopped by the police; changes in fees and fines collections largely impacts the white population.
+The overall changes in revenue we observe in our two-way fixed effects models might reflect changes largely for the white populations in these municipalities, while ticketing---and turnout---remain more or less constant for Black populations.
+We were unable to incorporate a race-specific measure of police stops or measures of local incarceration or policing trends due to a lack of consistent data nationwide.
 
-We were somewhat surprised by the differences that arose between our two sets of findings---our city-level analysis using a two-way fixed effects model did not produce statistically significant results for Black voters.
-We think there are a few potential explanations for this mismatch.
+Finally, Sances and You [-@Sances2017: 1091]---the paper that originally detailed the relationship between fees and fines collections and municipalities’ racial composition using the Census of Governments data---specifically notes that they did not exploit the panel setup of the COG because of “little variation within a city in terms of revenues from fines.” Instead, they present only the results of a cross-sectional study.
+Here, we present both the cross-sectional and panel results, acknowledging that each have limitations but that, taken together, they shed light on the unique politicization of fees and fines for Black Americans.
 
-First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes are smaller or not statistically significant.
-Along a similar vein, it’s possible that the effect size for Black voters in the city-level analysis is affected by higher-intensity forms of criminal legal contact, such as arrest and incarceration.
-The bulk of existing literature suggests that incarceration discourages political participation, and it’s not unreasonable to assume that cities that ramp up ticketing of Black residents also ramp up arrest and incarceration of Black residents.
-If these phenomena coincide, that could explain why the city-level analysis produced no statistically significant effect for Black voters---the personally mobilizing effect of ticketing could be counterbalanced by the proximal chilling effect of incarceration, and because the city-level analysis is not as temporally sensitive, it’s more difficult to isolate the effect of ticketing.
-
-That said, @Sances2017 specifically note that they didn't exploit the panel setup of the COG because of little variation between the 2007-2012 COG to the 2012-2017 one, and so they just stuck to cross sectional.
-The positive effect for Black turnout in Figure 2 is consistent with our Tampa analysis and doesn't totally contradict the TWFE.
-
-Our findings point to several implications for political sociology and political science scholarship.
+Our findings have several implications for political sociology and political science scholarship.
 While existing literature suggests that the most disruptive forms of criminal legal contact (i.e.
 criminal convictions and incarceration) consistently discourage voting [@Lerman2014; @Burch2011; @White2019a], research regarding police stops has produced more mixed results [@Laniyonu2019].
-We extend this theory to police ticketing, the most common form of police contact in America, and find that city-level increases in ticketing generally reduce turnout.
+We extend this theory to police ticketing, the most common form of police contact in America, and find that ticketing generally reduces turnout.
 For Black voters, however, our findings suggest that ticketing can be politically mobilizing.
@@
 
-**Limitations**: Because our individual-level analysis is limited to Hillsborough County, we don’t have a good idea of whether the city-level revenue reliance trend interacts with the individual experience of being ticketed.
+In this sense, our analysis points to a political contestation of criminal legal policy, a phenomenon that aligns with dozens of recent campaigns to reform local fines and fees practices (or abolish them entirely).^3^  We know that increased fines and fees result from political economy (i.e.
+austerity at the federal level), but our analysis suggests that this is a “two way street” wherein people who are harmed by policing practices can be politically socialized into resistance.
+
+**Limitations**: Because our individual-level administrative data analysis is limited to Hillsborough County where fines collections increased over the period, we do not have a good sense of how the city-level revenue reliance trend interacts with the individual experience of being ticketed in areas where fees and fines are constant or decreasing.
 Is ticketing more politically mobilizing for Black voters in cities that are palpably dialing up their revenue collection efforts?
-Future research could test this hypothesis in cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.
+Future research could test this hypothesis at the individual level within cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.
 
-Additionally, in our analysis of Hillsborough County voters, we don’t look at people who weren’t registered to vote in 2018.
-This means that there could be some proportion of ticketed Black motorists who are now less likely to register to vote in the first place, for example.
-In other words the mobilization effect in our findings only applies to people who were registered to vote---we are unable to make claims about whether being ticketed makes an individual more likely to register to vote.
+Additionally, in our analysis of Hillsborough County voters, we do not look at people who were not registered to vote in 2018.
+Because we cannot tell whether unregistered individuals who were stopped in Hillsborough County were unregistered because they were *ineligible* to do so (by virtue of living in a different county or being a non-citizen, for instance) or chose to eschew electoral politics, our analysis is necessarily limited to individuals who were registered to vote.
+This likely makes our results conservative: we cannot capture the lost participation of individuals who would have registered and voted if they were not stopped by the police.
 
-**Future research**: Future work should explore whether ticketing can be mobilizing for Black individuals under circumstances.
-We were unable to test whether what we're observing is just *decreased* demobilization, or whether some subgroups of the Black population were mobilized while others were demobilized.
-In other words, it could be the case that ticketing is demobilizing for all voters, but there is a subset of Black voters who are *mobilized* by this, though they aren't a large enough group to counteract the demobilization of other Black people.
+**Future research**: This work looks at the difference between the political behavior of Black and non-Black Americans.
+Future work should explore variation *within* the Black community.
+When is this sort of contact mobilizing?
+For whom?
+Can organizers build on this potential for broad-based political action?
+We were unable to test whether what we observed was simply *decreased* demobilization, or whether some subgroups of the Black population were mobilized while others were demobilized.
+Put differently: it could be the case that ticketing is demobilizing for most voters of all races, but that a subset of the Black population is affirmatively mobilized, leading to lower group-level demobilization.
+Scholars should also investigate the interactive effects of criminal legal contact, asking whether police stops result in different political behavior for formerly incarcerated individuals than individuals with no other contact with the system.
 
-Unlike previous studies using survey data, we are unable to tell whether individuals in Tampa have non-ticketing criminal legal exposure.
-Future research could test whether formerly incarcerated people respond to unjust ticketing by mobilizing or withdrawing from political participation.
+Finally, we are sensitive to the fact that although administrative data provides real-world evidence of actual behavior, such an approach limits our ability to understand the psychological processes in play.
+This means that although we demonstrate that police stops are demobilizing, future work must further investigate how stops are interpreted by individuals and translated into political behavior.
 
-<!--  [Laniyonu] - [he writes that block groups with higher Black pop and higher SQF density voted at higher rates for Thompson, the candidate who pledged not to implement SQF reform, but who was Black.
-The descriptive representation from Sances2017 kind of covers for this, tactically speaking - electing Black politicians should reduce fines and fees abuses.
-But in Tampa, the current mayor, Jane Castor, was the police chief until 2015 --- which overlaps with the treatment period in our analysis.
-One voter told the Tampa Bay Times that he voted against Castor as “payback” for the racist ticketing practices she oversaw, and the article notes that her opponent won five majority-Black precincts [@Frago2019].
-In 2015, Castor even released a statement as police chief supporting the racist ticketing, insisting that “Many individuals receiving bike citations are involved in criminal activity.” -->
+Although we have generated new evidence suggesting that police stops and related exploitative ticketing practices may mobilize Black voters, we emphasize that this finding does not redeem or justify such police practices.
+Black Americans already suffer from disproportionate police contact and the racial wealth gap, and racist revenue-motivated ticketing only increases the burden on Black communities nationwide.
+Policymakers should work to ensure that Black Americans no longer have to struggle to enjoy the same political power as whites---to that end, the current trend of voting rights restriction policies across the country is especially pernicious.
+Even if Black Americans understand the ballot box as one tool they can use to limit the state’s power to exploit and harm them, policymakers should still feel an obligation to support voting rights protections and stop disproportionate ticketing in Black communities.
+
+\newpage
+
+# Notes {-}
+
+^1^ Because such frequent snapshots are not available from L2, we here use the registered voter file made freely available by the state of Florida.
+
+^2^ Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights. The full sample is used in the actual matching process.
+
+^3^ See https://finesandfeesjusticecenter.org/clearinghouse.
 
@@
 
-<!-- 
-[stuff on Black MC]
-https://press.princeton.edu/books/paperback/9780691025438/behind-the-mule
-
-https://journals.sagepub.com/doi/abs/10.1177/0011128799045004006?casa_token=C1tIg2PtoRQAAAAA:jiOyqKAFal3XdvfUC7BI6ItWF4rJOFNuj-FhTScVU-vXfrpW1wduVWp-aXtGdzq8EnaDVC4sbTbj
-
-https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1745-9125.2002.tb00962.x?casa_token=CAPT_XZTho4AAAAA:EVzYhsgW-c44zwpabCYoP8QtZ3-6YNws9vjdBgjhau8f-ehG-GwkS6h0MdhfYncmV3t60_WUCykNUw
-
-https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1745-9125.2009.00159.x -->
+<div id="refs"></div>

### 2022-02-14 markdown/draft_paper.tex
pre 2022 edits

@@
 
-\title{Policing for Profit and the Mobilization of Black Voters}
+\title{Ticketing and Turnout: How Policing for Profit Shapes Democratic Participation}
 \author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
-\date{May 24, 2021}
+\date{October 01, 2021}
 
@@
 Despite this burgeoning literature, no research has directly investigated how police ticketing practices affect political participation.
-We use three approaches to answer this question: national survey data, a city-level analysis using Census of Governments data and the national voter file, and individual-level ticketing data from Hillsborough County, Florida between 2003 and 2019.
+We use three approaches to answer this question: we leverage individual-level administrative ticketing data from Hillsborough County, Florida between 2010 and 2020, a city-level analysis using Census of Governments data and the national voter file, and national survey data.
+We use a genetic matching algorithm and difference-in-differences to estimate that being ticketed decreases an individual's likelihood of voting in federal elections by 1.7 percentage points, but depressive effects are smaller for Black residents.
+Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 was associated with a roughly 0.04 percentage point turnout decrease but was not associated with any change in Black turnout.
 The survey data show that Black people who report that they or a family member were recently stopped by police are more likely to vote than those who reported no such contact.
-Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 is associated with a roughly 0.04 percentage point turnout decrease but was not associated with Black turnout.
-In Tampa, Florida, we estimate that being ticketed decreases an individual's likelihood of voting in federal elections by 1.7 percentage points, but depressive effects are smaller for Black residents.
 
@@
 It wasn't just a Ferguson problem, or even a Missouri problem.
-American cities' reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (\protect\hyperlink{ref-Singla2020}{Singla, Kirschner, and Stone 2020}; \protect\hyperlink{ref-Harris2017}{Harris et al.
-2017}).
-
-Work exploring how criminalization directly and indirectly influences political participation has exploded in recent years.
+American cities' reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (\protect\hyperlink{ref-Singla2020}{Singla, Kirschner, and Stone 2020}; \protect\hyperlink{ref-Harris2017}{A.
+Harris et al.
+2017}; \protect\hyperlink{ref-Harris2020}{A.
+P.
+Harris, Ash, and Fagan 2020}).
+
+Work exploring how criminalization directly and indirectly influences political participation has exploded in recent years following path-breaking work from political sociologists Chris Uggen and Jeff Manza (\protect\hyperlink{ref-Uggen2002}{Uggen and Manza 2002}; \protect\hyperlink{ref-Manza2006}{Manza and Uggen 2006}).
 Scholars have found that criminal legal contact (i.e.~arrest, conviction, incarceration) consistently discourages voting (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}; \protect\hyperlink{ref-Burch2011}{Burch 2011}; \protect\hyperlink{ref-White2019a}{White 2019b}).
 Such work has largely focused on the effects of highly disruptive contact with the criminal legal system such as incarceration and felony convictions (\protect\hyperlink{ref-Burch2014}{Burch 2014}; \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}).
-Building on recent theoretical work from \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020a}) and an analysis of the historical context of fees and fines collections in the United States, this paper is the first to explicitly theorize how local ticketing practices shape the political socialization of ticketed individuals.
+While ticketing involves potentially negative interactions with the state, it does not necessarily carry the disruptive consequences of a felony conviction and might thus politicize Americans in unique ways.
+Building on recent theoretical work from \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020b}) and an analysis of the historical context of fees and fines collections in the United States, this paper is the first to explicitly theorize how local ticketing practices shape the political socialization of ticketed individuals.
+We argue that ticketing depresses voter turnout overall, but also catalyzes a ``linked fate'' political analysis among Black voters that either causes increased turnout or mitigates the turnout reductions observed among non-Black individuals.
+
 Additionally, our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
-
-In addition to our theoretical contribution, the use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures political participation.
+The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures political participation.
 Past work looking at the individual-level effects of low-level contact has relied entirely on survey or qualitative data (e.g.
@@
 Research on legal cynicism has found that public perceptions of abusive police practices can reduce willingness to report crimes or cooperate with law enforcement (\protect\hyperlink{ref-Desmond2016}{Desmond, Papachristos, and Kirk 2016}; \protect\hyperlink{ref-Tyler2014}{Tyler, Fagan, and Geller 2014}).
+In short, the ``hidden curriculum'' (\protect\hyperlink{ref-Justice2014}{Justice and Meares 2014}; \protect\hyperlink{ref-Meares2017}{Meares 2017}) of the criminal legal system teaches Americans about their identities as citizens---even parts of their identities that have little to do with policing or incarceration.
+New evidence related to ticketing and legal estrangement has recently emerged: in a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government compared to residents who were not ticketed (\protect\hyperlink{ref-CarpenterII2019}{Carpenter II, Sweetland, and McDonald 2019}).
+
 Because police are the most visible agents of the state, perceptions of unfairness in policing can translate to a recognition of actual group-level structural exclusion from public institutions (\protect\hyperlink{ref-Bell2017}{Bell 2017}).
-New evidence related to ticketing and legal estrangement has recently emerged: in a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government compared to residents who were not ticketed (\protect\hyperlink{ref-CarpenterII2019}{Carpenter II, Sweetland, and McDonald 2019}).
-
-Sarah Brayne found related results in her analysis of survey data---as the intensity of criminal legal contact escalates (i.e.~stopped, arrested, convicted), people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions (\protect\hyperlink{ref-Brayne2014}{Brayne 2014}).
+Soss and Weaver explain how criminal legal contact shapes perceptions of government and political participation: ``interviewees have looked, not to City Hall, Congress, or political parties, but rather to their direct experiences with police, jails and prisons, welfare offices, courts, and reentry agencies as they sought to ground their explanations of how government works, what political life is like for them, and how they understand their own political identities'' (\protect\hyperlink{ref-Soss2017}{Soss and Weaver 2017}: 574).
+
+Sarah Brayne found related results in her analysis of survey data.
+As the intensity of criminal legal contact escalates (i.e.~stopped, arrested, convicted), people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions (\protect\hyperlink{ref-Brayne2014}{Brayne 2014}).
 She calls this phenomenon ``system avoidance,'' and while her analysis did not specifically assess voting behavior, her findings demonstrate how criminal legal contact can discourage Americans' participation in public institutions as well as how the effect may vary alongside the intensity of criminal legal intervention.
 Similarly, \protect\hyperlink{ref-Remster2018a}{Remster and Kramer} (\protect\hyperlink{ref-Remster2018a}{2018}) finds that men who return home from prison are more likely to avoid contact with their childrens' schools.
+Vesla Weaver and colleagues helpfully describe this form of self-preserving withdrawal from public institutions as a ``strategic retreat'' (\protect\hyperlink{ref-Weaver2020}{Weaver, Prowse, and Piston 2020}).
 
 In addition to influencing perceptions of government and participation in public institutions, recent scholarship indicates that criminalization influences political behavior.
-The ``hidden curriculum'' of the criminal legal system (\protect\hyperlink{ref-Justice2014}{Justice and Meares 2014}; \protect\hyperlink{ref-Meares2017}{Meares 2017}) teaches individuals about their position within the political system, and the criminal legal system consequently serves as a primary site of political socialization for convicted individuals and their families (e.g.
-\protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}).
-
 Using existing national survey data and extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
-Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a ``linked fate'' where ``one's individual opportunities are linked to the entire racial group'' (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014, 197}).
-Their interview data lead them to conclude that while criminal legal contact does increase perceptions of linked fate among Black respondents, ``a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing''---and interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}).
-
-Lerman and Weaver's finding has been corroborated by administrative data: Ariel White found that short jail sentences in Harris County, Texas reduced Black defendant turnout in subsequent elections by 13 percentage points---but the effect on white turnout was not statistically significant (\protect\hyperlink{ref-White2019}{White 2019a}).
+Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a ``linked fate'' where ``one's individual opportunities are linked to the entire racial group'' (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}: 197).
+Their interview data lead them to conclude that while criminal legal contact does increase perceptions of linked fate among Black respondents, ``a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing.'' Interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}).
+
+Lerman and Weaver's findings have been corroborated using administrative data: Ariel White found that short jail sentences in Harris County, Texas reduced Black defendant turnout in subsequent elections by 13 percentage points---but the effect on white turnout was not statistically significant (\protect\hyperlink{ref-White2019}{White 2019a}).
 Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level (\protect\hyperlink{ref-Burch2014}{Burch 2014}).
-
-Although most work documents a uniformly demobilizing effect from contact with the criminal legal system, recent work from Hannah Walker (\protect\hyperlink{ref-Walker2020}{2020b}, \protect\hyperlink{ref-Walker2020a}{2020a}) complicates this narrative by arguing that, when Black Americans understand their contact with the criminal legal system in the context of a narrative of racial injustice, such contact can actually prove mobilizing.
-She explains: ``experiences with punitive policies are subject to interpretation and, when understood through narratives of injustice, lead to wholly different participation outcomes than we usually predict'' (\protect\hyperlink{ref-Walker2020}{Walker 2020b, 132}).
-While she finds that this sense of injustice is especially likely to increase political participation in non-voting ways (such as attending a protest or signing a petition), the logic could extend to electoral participation as well given a strong narrative or relatively weak contact with the criminal legal system.
+These effects can also extend to family members, and the political consequences can be quite durable (\protect\hyperlink{ref-Morris2021}{Morris 2021}).
+
+Although most work documents how contact with the criminal legal system causes strategic retreat, recent work from Hannah Walker (\protect\hyperlink{ref-Walker2020}{2020a}, \protect\hyperlink{ref-Walker2020a}{2020b}) complicates this narrative.
+She argues that when Black Americans understand their contact with the criminal legal system in the context of a narrative of racial injustice, such contact can actually mobilize.
+She explains: ``experiences with punitive policies are subject to interpretation and, when understood through narratives of injustice, lead to wholly different participation outcomes than we usually predict'' (\protect\hyperlink{ref-Walker2020}{Walker 2020a}: 132).
+While she finds that this sense of injustice is especially likely to increase political participation in non-voting ways (such as attending a protest or signing a petition), the logic could extend to electoral participation as well given a relevant electoral context, strong injustice narrative, or relatively weak contact with the criminal legal system.
+Findings presented in \protect\hyperlink{ref-Laniyonu2019}{Laniyonu} (\protect\hyperlink{ref-Laniyonu2019}{2019}) provide support for this concept: concentrated Stop, Question, and Frisk (SQF) policing in New York City neighborhoods was associated with reduced turnout in federal midterm elections but increased turnout in presidential and mayoral primary elections.
+Laniyonu also uncovered an association regarding candidate choice---he demonstrates higher turnout for a candidate who opposed SQF policing and lower turnout for a candidate who supported it.
+In other words, low-level police contact mobilized voters to participate in a local election (which could plausibly affect police practices).
 
 Despite the growing body of high-quality scholarship on the democratic implications of the American criminal legal system, we still know remarkably little about the effects of the most routine sort of contact---police stops and tickets that do not result in an arrest.
-We leverage Walker's novel insights about the potentiality of a narrative of injustice to re-think how these sorts of contact with the state can structure political participation.
 
@@
 
-Fines and fees are situated in a distinct historical legacy of racist exploitation that may uniquely facilitate a collective ``sense of injustice'' among Black Americans---the sort of collective perception that \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020a}) argues could prove to be politically mobilizing.
+Fines and fees are situated in a distinct historical legacy of racist exploitation that may uniquely facilitate a collective ``sense of injustice'' among Black Americans---the sort of collective perception that \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020b}) argues could prove to be politically mobilizing.
 
 Cedric Robinson's articulation of racial capitalism offers a useful theoretical framework for interpreting the trajectory of American anti-Black political economy (\protect\hyperlink{ref-Robinson2000}{Robinson 2000}).
-Brittany Friedman theorizes fines and fees as a ``progression of racial capitalism penology,'' emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices (\protect\hyperlink{ref-Friedman2020}{Friedman 2020, 177}).
+Brittany Friedman theorizes fines and fees as a ``progression of racial capitalism penology,'' emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices (\protect\hyperlink{ref-Friedman2020}{Friedman 2020}: 177).
 Robinson argues that European industrial capitalism continued a longer political-economic trend of differentiating racial groups in order to dispossess them and exploit their labor.
@@
 The implementation of the Black Codes, convict leasing, and sharecropping systems marked a transition to a new stage of racial capitalism, wherein criminalization provided an easily-exploited labor supply that offset costs that the state incurred by coercing their labor (\protect\hyperlink{ref-Lichtenstein1996}{Lichtenstein 1996}; \protect\hyperlink{ref-Mancini1978}{Mancini 1978}).
-Contemporary fines and fees practices have been directly compared to sharecropping because both structures share ``a long-term pattern of financial exploitation based on race\ldots{} that limits the life-choices of the affected population'' (\protect\hyperlink{ref-Blessett2016}{Blessett and Box 2016, 113}).
+Contemporary fines and fees practices have been directly compared to sharecropping because both structures share ``a long-term pattern of financial exploitation based on race\ldots{} that limits the life-choices of the affected population'' (\protect\hyperlink{ref-Blessett2016}{Blessett and Box 2016}: 113).
 
 In the 20th century, residential segregation simultaneously fueled the racial wealth gap and ensured that criminalization was both spatially and racially concentrated (\protect\hyperlink{ref-Rothstein2017}{Rothstein 2017}; \protect\hyperlink{ref-Hinton2021}{Hinton and Cook 2021}).
-At the level of federal policy, racial threat and whites' attribution of criminality to Blackness (\protect\hyperlink{ref-Muhammad2010}{Muhammad 2010}) prompted a shift ``from the War on Poverty to the War on Crime'' wherein Black communities' demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration (\protect\hyperlink{ref-Hinton2017}{Hinton 2017}; \protect\hyperlink{ref-Vargas2017a}{Vargas and McHarris 2017}).
+At the level of federal policy, racial threat and whites' attribution of criminality to Blackness (\protect\hyperlink{ref-Muhammad2010}{Muhammad 2010}) prompted a shift from the War on Poverty to the War on Crime wherein Black communities' demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration (\protect\hyperlink{ref-Hinton2017}{Hinton 2017}; \protect\hyperlink{ref-Vargas2017}{Vargas and McHarris 2017}).
 
@@
 
-Black Americans can therefore situate exploitative ticketing practices in a longer historical legacy of collective disparate treatment and violence at the hands of the state.
-We argue that Black voters' recognition of discriminatory ticketing practices facilitates a ``linked fate'' political analysis that motivates voting behavior distinct from other forms of criminalization, such as criminal conviction or incarceration.
-We expect both ticketing and incarceration to spark a recognition of ``a sense of injustice'' among Black Americans, but we argue that ticketing should ultimately mobilize Black voters (unlike incarceration, which discourages Black voters more than whites (\protect\hyperlink{ref-White2019}{White 2019a})).
-
-Ticketing produces substantively different experiences than being arrested or incarcerated.
-While tickets can lead to driver's license suspensions or, in a smaller subset of cases, nonpayment incarceration, tickets are generally far less disruptive than criminal convictions and prison terms, and we argue that this difference should lead to different political behaviors.
-For example, one participant in \protect\hyperlink{ref-Lerman2014}{Lerman and Weaver} (\protect\hyperlink{ref-Lerman2014}{2014}) who had served five years of probation after a criminal conviction reported, ``I feel like if I contact a senator or governor, they'll probably want to put me in jail and leave me as a troublemaker\ldots{} That's how I actually feel: `I better stay below the radar 'cause this guy's tryin' to start trouble''' (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014, 210}).
-While formerly incarcerated people or people who have experienced criminal legal supervision may avoid voting due to the same type of fear of state surveillance and control that motivates their avoidance of medical or educational institutions (\protect\hyperlink{ref-Brayne2014}{Brayne 2014}), we argue that being ticketed should not produce the same chilling effect---ticketing should not prompt Black people to use political withdrawal as a self-preservation strategy.
-
-Additionally, we argue that ``policing for profit''---the experience of being ticketed while a municipality is palpably ramping up its fines and fees practices to collect revenue---is also substantively distinct from the experience of being arrested or incarcerated.
-In doing so, we extend Epp et al.'s theory of pretextual traffic stops politically socializing Black voters to the specific context of discriminatory police ticketing (\protect\hyperlink{ref-Epp2014}{Epp, Maynard-Moody, and Haider-Markel 2014}).
-Black Americans who experience disproportionate ticketing are likely aware that they are being targeted by police for reasons unrelated to traffic safety.
+\hypertarget{theory}{%
+\section*{Theory}\label{theory}}
+\addcontentsline{toc}{section}{Theory}
+
+As the preceding sections make clear, past work on the political ramifications of criminal legal contact has largely determined that such contact is demobilizing.
+Scholars have argued that all contact with the criminal legal system causes political withdrawal, and that the severity of the withdrawal varies according to the intensity of the contact.
+This finding may not hold true for lower-level criminal legal contact, however.
+We argue that police ticketing may be an exception to this rule for two reasons: (1) police stops are far less disruptive to Americans' lives than arrests or periods of incarceration, and (2), the injustice narrative framework (\protect\hyperlink{ref-Walker2020a}{Walker 2020b}) indicates that the explicit politicization of police stops by the Black Lives Matter movement in recent years should be mobilizing for Black Americans.
+
+Receiving a ticket is a substantively different experience than being arrested or incarcerated.
+People who have been convicted of a crime and incarcerated are relegated to an alternate political membership status that Reuben Jonathan Miller and Forrest Stuart call ``carceral citizenship,'' subjecting them to forms of supervision and sanction ``that are otherwise unavailable to {[}people{]} who have not been accused of a crime'' (\protect\hyperlink{ref-Miller2017}{R.
+J.
+Miller and Stuart 2017}: 536).
+The politically discouraging effects of criminalization are even stronger for people who are convicted of felonies, who lose their right to vote in all but two U.S.
+states.
+This ``civil death'' (\protect\hyperlink{ref-Ewald2002}{Ewald 2002}; \protect\hyperlink{ref-Miller2012}{B.
+L.
+Miller and Spillane 2012}) explicitly removes Americans from the electorate; the felony conviction becomes ``a durable constraint and marker of their citizenship'' (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}: 133).
+The experience of formal legal exclusion from voting forms a powerful piece of the ``hidden curriculum'' (\protect\hyperlink{ref-Meares2017}{Meares 2017}) that teaches convicted individuals about their identities as citizens.
+Finally, the financial and social costs following a period of incarceration (\protect\hyperlink{ref-Bushway2007}{Bushway, Stoll, and Weiman 2007}) can make it less likely that citizens invest the time and energy into registering to vote, learning where their polling place is, and determining which candidates they support.
+
+While tickets can lead to driver's license suspensions or, in a smaller subset of cases, nonpayment incarceration, tickets are generally far less disruptive than criminal convictions and prison terms.
+Ticketed drivers are not disenfranchised, and they are not subject to the same forms of supervision and sanction that affect people with criminal convictions.
+Accordingly, individuals who have \emph{not} been subjected to such intense supervision may be less likely to avoid state institutions compared to formerly incarcerated people pursuing a ``strategic retreat.'' (\protect\hyperlink{ref-Brayne2014}{Brayne 2014}), In short, if higher-intensity contact with the criminal legal system leads to political withdrawal because of carceral control, surveillance, and resultant lessons about citizenship, these same arguments are unlikely to apply to ticketed individuals.
+
+This is not to say that ticketing should be considered completely distinct from more intense forms of criminalization, but rather that a ticketed individual has not yet been relegated to ``carceral citizenship.'' .
+Walker's research gives us reason to believe that drivers who feel that they were unfairly targeted by the police---and link that unfair experience to broader social narratives---can be \emph{mobilized} by that experience.
+Moreover, given political organizing in recent years specifically about the racial injustices of discriminatory traffic stops, this injustice narrative is likely particularly accessible---and mobilizing---for Black Americans.
+
+The rise of the Black Lives Matter movement in 2013 constitutes a significant development for the political socialization of Black Americans, and many early Black Lives Matter protests either occurred in municipalities with exploitative ticketing practices or directly followed traffic stops that escalated into police violence (\protect\hyperlink{ref-Holpuch2015}{Holpuch 2015}; \protect\hyperlink{ref-LaFraniere2016}{LaFraniere and Smith 2016}).
+The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious.
+It is possible that Black Lives Matter facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis---the movement arose shortly after fines and fees became a more salient and widespread threat to Black Americans' material security, and the BLM movement helped to publicize these disparities.
+The injustice narrative framework proposed by \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020b}) explains how individuals connect their ``micro'' experience of criminal legal contact with the ``macro'' narrative of racially discriminatory policing.
+
+The financially exploitative nature of recent ticketing increases should be particularly fertile ground for robust injustice narratives.
 One Buffalo, New York resident who is a plaintiff in a lawsuit regarding racist ticketing practices told a local newspaper in 2019: ``In my mind, they weren't balancing the budgets for Black lives, but with Black lives'' (\protect\hyperlink{ref-McLeod2019}{McLeod 2019}).
 The city created a new traffic violations agency in 2015, spurring its yearly ticketing numbers to jump from around 32,000 to over 52,000.
-This financial aspect of ticketing should make it distinct from arrests and incarceration: much like the coercion of labor under the Black Codes, contemporary fines and fees practices are blatantly an effort to extract wealth from Black Americans.
-In other words, to the extent that mass incarceration could be justified using narratives of ``colorblind racism'' (i.e., high crime rates in Black communities results in more policing in those areas), racist ticketing practices do not enjoy the same rhetorical convenience.
-It may not be possible for revenue-motivated, racist ticketing to be reconciled with the idea that policing is primarily meant to improve public safety.
-
-Ticketing is by far the most common form of criminal legal contact; in 2018, more than 24 million people experienced police contact in the context of a traffic stop, whereas about 5.17 million people are currently disenfranchised as a result of a felony conviction (\protect\hyperlink{ref-Harrell2020}{Harrell and Davis 2020}; \protect\hyperlink{ref-Uggen2020}{Uggen et al.
-2020}).
-At the same time, the most egregious local ticketing increases occurred largely over the past two decades (\protect\hyperlink{ref-Singla2020}{Singla, Kirschner, and Stone 2020}), and increases have been concentrated largely in Black municipalities (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
-These facts have been extensively discussed in mainstream media and should be widely known among Black voters (\protect\hyperlink{ref-Eligon2019}{Eligon 2019}; \protect\hyperlink{ref-Ehrenfreund2014}{Ehrenfreund 2014}).
-We expect a larger share of more affluent Black voters to be affected by ticketing than other forms of criminalization---arrests and incarceration are most common among individuals experiencing poverty (\protect\hyperlink{ref-Looney2018}{Looney and Turner 2018}).
-Because perceptions of ``linked fate'' and related critiques of policing are even more salient among members of the Black middle class (\protect\hyperlink{ref-Dawson1995}{Dawson 1995}), we expect Black middle class voters to be mobilized by egregious ticketing practices.
-In other words, we argue that ticketing should ensnare more Black voters who are more likely to politicize the issue.
-
-Finally, the rise of the Black Lives Matter movement in 2013 constitutes a significant development for the political socialization of Black Americans, and the movement began in municipalities that targeted Black residents with tickets.
-The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious.
-Furthermore, local Black Lives Matter activism can change police practices.
-One recent study found that census places that saw Black Lives Matter protests experienced a 15 to 20 percent decrease in police killings over the following five year period (\protect\hyperlink{ref-Campbell2021}{Campbell 2021}).
-It's possible that Black Lives Matter facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis---the movement arose shortly after fines and fees became a more salient and widespread threat to Black Americans' material security, and many early Black Lives Matter protests either occurred in municipalities with exploitative ticketing practices or directly followed traffic stops that escalated into police violence (\protect\hyperlink{ref-Holpuch2015}{Holpuch 2015}; \protect\hyperlink{ref-LaFraniere2016}{LaFraniere and Smith 2016}).
-
-Today, fines and fees disproportionately affect Black people, and Black political mobilization appears to mitigate some of the most egregious ticketing practices (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
-As we have shown, contemporary fees and fines practices are just one iteration of a longer anti-Black project in the United States.
-Moreover, organizing in recent years by groups affiliated with the BLM movement have made this narrative easily accessible to citizens around the country.
-Based on the strength and accessibility of this narrative and the injustice framework proposed by \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020a}), we expect that Black voters' political behavior in response to police ticketing will be distinct from the political behavior of white voters, and further that ticketing should mobilize Black voter turnout in cities that have recently ramped up ticketing.
+
+We argue that many of the factors leading to withdrawal associated with higher-level criminal legal contact should not apply to police stops.
+At the same time, we expect that the national BLM movement should have encouraged Black Americans stopped by the police to connect their experience to macro-level trends, and that this should encourage political behaviors such as voting.
+Simply put, we expect that police stops are far less demobilizing than higher-level contact, and that they may in fact be mobilizing for Black Americans in an era of increased awareness of racially disparate policing practices.
 
@@
 
-We mobilize three distinct approaches to ask whether ticketing and police stops structure voter turnout, and whether these effects are unique for Black Americans.
-We look at national survey data, municipal-level finance data, and individual-level administrative records in a major American county to explore these effects.
-Each approach offers advantages and drawbacks; taken together, however, they dramatically advance our understanding of the political consequences of the most routine types of contact with the criminal legal system.
-
-\hypertarget{national-survey-data}{%
-\subsection*{National Survey Data}\label{national-survey-data}}
-\addcontentsline{toc}{subsection}{National Survey Data}
-
-We begin by turning to the American National Election Studies 2020 Time Series data (ANES).
-The ANES has been fielded in every presidential election year since 1948 and is among the most widely-used tools for understanding American's political beliefs and behaviors, including their relationship with the criminal legal system (\protect\hyperlink{ref-Walker2020}{Walker 2020b}).
-It is weighted to be nationally representative of all American adults.
-In both 2016 and 2020, the ANES added new survey questions about respondent's encounters with the police and the criminal legal system.
-We focus in particular on two questions: \emph{During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?}, and \emph{Have you ever been arrested, or has that never happened to you?} We include the roughly 87 percent of respondents that answered both questions, giving us a sample size of 7,347 respondents, of whom just over 11\% identified as Black.
-
-We use the survey questions to test the effect of a police stop on voter turnout---and, specifically, whether the effect is different for Black respondents.
-We also test whether an arrest is associated in the 2020 ANES with a lower probability of voting as described in previous work.
-In addition to the respondent's contact with the criminal legal system, we control for age; sex; income; education; party affiliation; self-described ideology; and reported 2016 turnout.
-Using the ANES, we test our first two hypotheses:
-
-\emph{Hypothesis 1}: Personal and proximal experience of police stops is demobilizing for non-Black respondents, and mobilizing for Black respondents, other things equal.
-
-\emph{Hypothesis 2}: Personal experience of an arrest is demobilizing for individuals of all races, other things equal.
-
-There is an important caveat to the use of the ANES survey---namely, while the police stop question asks whether the respondent \emph{or anyone in their family} was stopped in the past year, the arrest question asks only about the individual respondent.
-While this may muddy the water between direct and proximal contact with the criminal legal system, we expect that the national survey data will give us some insight into the uniquely politicizing nature of police stops for Black Americans.
-
-\hypertarget{city-level-relationship-between-voter-turnout-and-fines-and-fees}{%
-\subsection*{City-level relationship between voter turnout and fines and fees}\label{city-level-relationship-between-voter-turnout-and-fines-and-fees}}
-\addcontentsline{toc}{subsection}{City-level relationship between voter turnout and fines and fees}
-
-After an examination of the cross-sectional national survey data, we turn to our nationwide analysis of the relationship between municipal revenue raised from fees and fines, and turnout in the 2018 federal election.
-Our data come from two primary sources: the US Census Bureau's Census of Governments Data (COG), and registered voter files from L2 Political.
-
-\textbf{Census of Governments}: Every five years, the US Census Bureau collects data from governmental bodies around the country.
-We use two waves of the COG: one that covers the years 2008 -- 2012, and another that covers 2013 -- 2017.
-The COG asks municipalities to report how much revenue they collect from ``penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation\ldots{} and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).'' We divide these amounts by the population to estimate the per-capita fees and fines revenue raised in each municipality.
-This data has been used as a proxy for the amount of tickets issued at the local level in scholarly research (see, for instance, \protect\hyperlink{ref-Goldstein2020}{Goldstein, Sances, and You 2020}; \protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
-
-The COG data are useful to isolate ticketing practices because other fines and fees (e.g.~fines imposed at sentencing in state court, probation fees, conviction fees, public defender fees) are typically collected by county or state governments.
-The COG data only include local revenues, which means the share of fines revenue corresponds more directly to local police practices.
-Following the guidance of \protect\hyperlink{ref-Sances2017}{Sances and You} (\protect\hyperlink{ref-Sances2017}{2017}), we retain only municipalities with police and/or court systems, as these are the only municipalities capable of issuing tickets.
-We also only retain municipalities with populations of at least 2,500.
-
-\textbf{Registered Voter Files}: The COG data do not include estimates of turnout at the local level.
-To estimate local turnout, we leverage registered voter files provided by data vendor L2 Political.
-In Washington, DC, and every state in the country (with the exception of North Dakota) voters are required to register to vote prior to participating.
-These files are considered public record, and in most states contain information about each voter's age, residential address, political affiliation, and participation history.
-L2 collects voter files from around the country and merges them with proprietary data that estimates other voter- and household-level characteristics such as race and education.
-L2 also geocodes voters' residential addresses.
-
-We merge the geocoded voter files with ``place'' and ``county subdivision'' shapefiles published by the US Census Bureau.
-These divisions correspond to the governmental bodies who report to the COG.
-By aggregating individual-level records to the municipal level, we are able to estimate the number of registered voters and the number of ballots cast in every city in the country.
-Moreover, by using the racial estimates provided by L2 we can estimate the number of ballots cast by voters of each race in each city.
-While in a few states race is self-reported by voters, race is in most cases modeled by L2 using first, middle, and last name, as well as Census block demographic information.
-Although this is a commonly used way to determine voters' races (\protect\hyperlink{ref-Imai2016}{Imai and Khanna 2016}), it is subject to some error.
-We assume, however, that after controlling for other municipality-level characteristics, the errors in these predictions will be uncorrelated with fees and fines collections.
-Put differently, although we acknowledge that these estimates are imprecise, we expect that these errors are effectively random.
-As we show in the Supplemental Information, the estimated Black share of the electorate tracks very closely with the share of the citizen voting age population that is non-Hispanic Black.
-After accounting for state-level voter registration differentials, the mean absolute error between these two measures is 2.4\% and is unrelated to per-capita fines and fees after controlling for other covariates (\emph{p} = 0.92).
-The individual-level racial estimates, when aggregated to the municipal level, thus provide a reasonably unbiased picture of the municipal electorate.
-
-We calculate turnout by dividing the number of ballots cast according to L2 by the 5-year estimate of each municipality's citizen voting-age population (CVAP) from the US Census Bureau.
-These estimates are available for individual racial groups.
-Because our turnout numerator and denominators come from different sources there is slight measurement error: our estimate indicates, for instance, that roughly 1 percent of municipalities had Black turnout above 100 percent.
-Where more votes were cast than the Census estimate for CVAP, we recode turnout as 100 percent.
-Our results do not change if we instead simply remove these municipalities, or use unmodified turnout estimates.
-
-\textbf{Estimation Strategy}: We begin by merging each municipality's fees and fines per capita (that is, dollars per resident) from the 2012 COG to its turnout from the 2014 midterm election, and the 2017 COG to its 2018 turnout.
-Because this measure is highly right-skewed, we use the natural log of fees and fines per capita (plus 1, to account for municipalities that collected no fees and fines).
-We also control for other municipal and state characteristics: racial composition, population density, median income, collegiate education, median age, share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality's revenue that comes from the state or federal government in the 2012 and 2017 COGs.
-We retain the 8,954 municipalities whose data is reported to the COG in both 2012 and 2017 and meet the other criteria noted above.
-
-The 5-year cycle of the COG does not neatly line up with the general 4-year cycle typical of American elections.
-The timing of the COG and midterm elections mean that our analytical strategy is conservative.
-If municipalities shift their fees and fines collections dramatically over the 2013 -- 2017 period, this shift may influence their 2014 turnout.
-However, we assume that turnout in 2014 will still be influenced by the policing practices of the 2008 -- 2012 period, while 2018 turnout will be largely influenced by the practices of the 2013 -- 2017 period.
-
-We run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
-Our national two-way fixed effect model allows us to test our next hypotheses:
-
-\emph{Hypothesis 3}: Increased reliance on fines and fees revenue at the city level reduces voter turnout at the city level among non-Black residents.
-
-\emph{Hypothesis 4}: Increased reliance on fines and fees revenue at the city level increases voter turnout at the city level among Black residents.
-
-\hypertarget{individual-level-effects-of-ticketing}{%
-\subsection*{Individual-Level Effects of Ticketing}\label{individual-level-effects-of-ticketing}}
-\addcontentsline{toc}{subsection}{Individual-Level Effects of Ticketing}
-
-Our national analyses offer novel insight into the political socialization of low-level police contact.
-They cannot, however, directly observe the causal mechanism we argue is at play: namely, that direct contact with the criminal legal system influences turnout.
-If interpreted in isolation, our national analysis would suffer from the ecological fallacy.
-In other words, it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
-Moreover, there are many other factors that could be at play.
-Increased fees and fines could be correlated with increased policing in general, for instance.
-Similarly, respondents in the ANES who report contact with a police stop may differ from those who report no such contact, even after controlling for available characteristics in the survey responses.
-
-Additionally, the national analyses cannot distinguish personal contact from proximal contact (``having a loved one who is a custodial citizen without yourself having had contact'' (\protect\hyperlink{ref-Walker2017}{Walker and García-Castañon 2017})).
-Because existing research investigating the effect of proximal contact has produced mixed results (\protect\hyperlink{ref-Burch2014}{Burch 2014}; \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}; \protect\hyperlink{ref-Sugie2015}{Sugie 2015}; \protect\hyperlink{ref-White2019}{White 2019a}; \protect\hyperlink{ref-Walker2017}{Walker and García-Castañon 2017}; \protect\hyperlink{ref-Walker2020}{Walker 2020b}), we are unable to prove that personal police contact is the only dynamic driving effects observed in our national analysis.
-For that reason, we turn to individual-level data from Hillsborough County, Florida (home to Tampa).
-
-Hillsborough County is interesting for theoretical reasons: Tampa is in the top decile of municipalities in terms of fees and fines increase between the 2012 and 2017 COGs, and its population puts it in the top 1 percent of cities nationwide.
-It also has a relatively large Black population, allowing us to test for racial differences in the turnout effect of ticketing.
-
-Further, the Tampa Police Department was scrutinized by the Tampa Bay Times in 2015 for its relentless ticketing of Black bicyclists (\protect\hyperlink{ref-Zayas2015}{Zayas 2015}).
-This investigation catalyzed a U.S.
-Department of Justice investigation and report, requested by Tampa's mayor and police chief.
-In other words, there is strong evidence suggesting both racist targeting of tickets and potential publicity to catalyze distinct Black voter responses to the abusive behavior during the same time frame as our national analysis.
-Ticketing has also been expressly politicized in Tampa: Jane Castor, who was elected mayor in 2019, was Tampa's police chief until 2015 and publicly defended her department's disproportionate ticketing of Black bicyclists before retracting her defense ahead of her mayoral campaign (\protect\hyperlink{ref-Carlton2018}{Carlton 2018}).
-Her opponent, banker and philanthropist David Straz, campaigned against red-light cameras and focused his outreach in Tampa's Black communities (\protect\hyperlink{ref-Frago2019}{Frago 2019}).
-
-Hillsborough County also makes a unique set of data publicly available.
+We leverage three distinct approaches to ask whether ticketing and police stops structure voter turnout, and whether these effects are unique for Black Americans.
+Our theoretical estimand (\protect\hyperlink{ref-Lundberg2021}{Lundberg, Johnson, and Stewart 2021}) is the effect of police ticketing on the political socialization of ticketed individuals, which we proxy using their voter turnout.
+
+Each approach offers advantages and drawbacks.
+Our individual-level analysis in Hillsborough County exploits unusually detailed public data, which allows for a precise causal analysis that cannot be conducted in counties that do not provide ticketing records with personally identifiable information or states that do not include self-reported race data in the voter file.
+The empirical estimand is the voter turnout gap between Hillsborough County residents who have recently been ticketed and residents who will be ticketed in a future period, conditional on similar turnout in past elections and similar demographic characteristics.
+In isolation, however, results from one county may not be generalizable to other U.S.
+counties.
+
+We include two supplementary analyses to test the generalizability of the results from Hillsborough County.
+First, we analyze change in municipal-level revenue from fees and fines and voter turnout, which allows us to expand our analysis outside of Hillsborough County to about nine thousand American municipalities.
+This test does not allow us to directly observe the causal mechanism we argue is at play (police stops influencing political socialization, which in turn drives individual voter turnout), and replaces individual ticketing events with less-precise budget data.
+Also, if interpreted in isolation, the municipal-level analysis would suffer from the ecological fallacy: it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
+
+Finally, data from the 2020 American National Election Studies allow us to observe how tickets and arrests differentially influence voting behavior at the individual level among a nationally representative sample, but survey data analysis is subject to the vulnerabilities detailed in our introduction (e.g.~measurement bias).
+Nevertheless, it provides important national insight into the phenomena we observe locally in Hillsborough County.
+
+Taken together, these approaches dramatically advance our understanding of the political consequences of the most routine types of contact with the criminal legal system.
+
+\hypertarget{individual-level-causal-effects-of-ticketing}{%
+\subsection*{Individual-Level Causal Effects of Ticketing}\label{individual-level-causal-effects-of-ticketing}}
+\addcontentsline{toc}{subsection}{Individual-Level Causal Effects of Ticketing}
+
+First, we turn to individual-level data from Hillsborough County, Florida (home to Tampa).
+Hillsborough County makes a unique set of data publicly available.
 The county clerk makes information available about every traffic stop in the county going back to 2003.
-This data includes the name and date of birth of the individual stopped; the date of the offense; and the amount the individual paid for a ticket; and other information.
+This data includes the name and date of birth of the individual stopped; the date of the offense; the amount the individual paid for a ticket; and other information.
 
 To identify ticketed voters, we match the first and last names and dates of birth from the stop data against the Hillsborough County registered voter file.
+\protect\hyperlink{ref-Meredith2014}{Meredith and Morse} (\protect\hyperlink{ref-Meredith2014}{2014}) develops a test for assessing the prevalence of false-positives in administrative record matching.
+We present the results of that test in the Supplementary Information.
+We likely have a false-positive match of around 0.03 percent, a figure we consider too low to impact our results meaningfully.
+
 Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status (see \protect\hyperlink{ref-Nyhan2017}{Nyhan, Skovron, and Titiunik 2017}).
-Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.\footnote{Because such frequent snapshots are not available from L2, we here use the registered voter file made freely available by the state of Florida.} We thus observe virtually all individuals who were registered to vote at any time during our period of study.
+Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.\textsuperscript{1} We thus observe virtually all individuals who were registered to vote at any time during our period of study.
 Unique voter identification numbers allow us to avoid double-counting voters who are registered in multiple snapshots.
@@
 
-To improve the quality of the match between the two datasets, we remove all punctuation from all names and convert all names to lower-case.
-This means that a ``Jonathan O'Shea'' in one file would match a ``jonathan oshea'' in the other.
-\protect\hyperlink{ref-Meredith2014}{Meredith and Morse} (\protect\hyperlink{ref-Meredith2014}{2014}) develops a test for assessing the prevalence of false-positives in administrative record matching.
-We present the results of that test in the Supplementary Information.
-We likely have a false-positive match of around 0.03 percent, a figure we consider too low to impact our results meaningfully.
-
 By matching the police stop and voter records, we identify all voters who were ticketed between the 2012 and 2020 general elections (voters stopped between 2018 and 2020 elections serve only as controls).
+We collect self-reported information regarding the race of each voter from Florida's public voter file rather than the police stop data.
 Voters are considered ``treated'' in the general election following their ticket.
@@
 A voter cannot both be a treated and control voter for the same election; therefore, someone ticketed between the 2012 and 2014 elections and again between the 2014 and 2016 elections cannot serve as a control for anyone ticketed between 2012 and 2014.
+We limit the target population to voters who are ticketed at some point in order to account for unobserved characteristics that motivate people who are ticketed at some point to turn out at higher rates than people who are never ticketed.
 
@@
 We match exactly on the type of ticket (civil / criminal infraction; whether they paid a fine; whether they were stopped by the Tampa Police Department) to ensure that treated and control voters receive the same treatment.
-Finally, we exactly match treated and control voters on their turnout in the three pre-treatment elections.
+Finally, we match treated and control voters on their turnout in the three pre-treatment elections.
 
@@
 In short, any turnout difference between the treated voters and their controls is the causal effect of a police stop on turnout.
-It is important to note that our overall turnout effects are robust to much stricter assumptions.
-In the Supplementary Information we demonstrate that our overall turnout results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
-
-Our analytical approach thus incorporates two different causal approaches.
-Leveraging pre-treatment turnout allows us to estimate a traditional difference-in-differences model.
-Difference-in-differences models assume that, in the absence of the treatment, any turnout gap between treated and control voters would have remained stable in the post-treatment period.
-While the validity of this assumption is commonly established by examining pre-treatment trends in turnout between the two groups, it can be improved upon by using the matching methodology described above.
-In the case at hand, we both establish that the turnout of treated voters was mirrored by that of their control voters prior to treatment, \emph{and} that the observable characteristics of treated and control voters are similar---thus lending credence to the assumption that this gap would have remained constant absent treatment.
-Finally, by drawing controls from the population of individuals who were ticketed in subsequent years, we also indirectly control for any unobserved characteristics associated with receiving a ticket.
+Our overall turnout effects are robust to much weaker assumptions: in the Supplementary Information, we demonstrate that our overall turnout results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
+
+Our analytical design thus incorporates two different causal approaches in order to improve the credibility of our identification assumptions.
+Leveraging pre-treatment turnout allows us to estimate a traditional difference-in-differences model, while the matching procedure improves the plausibility of the parallel trends assumption by reducing salient differences between the treated and control voters.
 For a more detailed discussion of how matching can improve upon traditional difference-in-difference approaches when using panel data, see \protect\hyperlink{ref-Imai2020}{Imai, Kim, and Wang} (\protect\hyperlink{ref-Imai2020}{2020}).
@@
 \emph{\(\beta\)\textsubscript{2}Post Treatment\textsubscript{t}} measures whether turnout increased for controls in the first election following the treated voter's stop, while \emph{\(\beta\)\textsubscript{3}Treated\textsubscript{i} × Post Treatment\textsubscript{t}} tests whether turnout changed differently for treated voters than their controls in the election following their police stop.
-\emph{\(\beta\)\textsubscript{3}}, then, will capture the causal effect of a police stop on voter turnout.
+\emph{\(\beta\)\textsubscript{3}}, then, will capture the causal effect of a police stop on voter turnout; it is the unit-specific quantity measured in our empirical estimand (\protect\hyperlink{ref-Lundberg2021}{Lundberg, Johnson, and Stewart 2021}).
 \emph{\(\beta\)\textsubscript{4}Year\textsubscript{t}} captures year fixed-effects depending on the timing of the police stop, and the matrix \emph{\(\delta\)Z\textsubscript{i}} contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
-Equation 1 allows us to test Hypothesis 5:
-
-\emph{Hypothesis 5}: Being ticketed reduces an individual's likelihood of turning out in the subsequent election.
-
-We also estimate Equation 2, in which the treatment effect is interacted with whether a voter is Black (\emph{\(\beta\)\textsubscript{4}Treated\textsubscript{i} × Post Treatment\textsubscript{t} × Black\textsubscript{i}}):
-
-\begin{gather}
-\label{eq:2}
-v_{it}=\beta_0+\beta_1Treated_{i}+\beta_2Post Treatment_{t} + \nonumber \\
-\beta_3Treated_{i}\times Post Treatment_{t} + \beta_4Treated_{i}\times Post Treatment_{t}\times Black_{i} +\\
-\beta_5Year_{t} + \delta{Y}_{i} + \delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
-\end{gather}
-
-where \emph{\(\delta\)Y\textsubscript{it}} includes the dummy for Black interacted with the treatment and post treatment dummies. Equation 2 allows us to test Hypothesis 6:
-
-\emph{Hypothesis 6}: The effect of being ticketed on an individual's voter turnout is less negative / more positive if that individual is Black.
+
+In some models, we also interact the treatment variable with a dummy indicating whether the voter is Black to determine race-specific treatment effects.
+
+\hypertarget{voter-turnout-and-municipal-fines-and-fees-collections}{%
+\subsection*{Voter turnout and municipal fines and fees collections}\label{voter-turnout-and-municipal-fines-and-fees-collections}}
+\addcontentsline{toc}{subsection}{Voter turnout and municipal fines and fees collections}
+
+Next, we turn to our nationwide analysis of the relationship between municipal revenue raised from fees and fines and turnout.
+Our data come from two primary sources: the US Census Bureau's Census of Governments Data (COG), and registered voter files from L2 Political.
+
+\textbf{Census of Governments}: Every five years, the US Census Bureau collects data from governmental bodies around the country.
+We use two waves of the COG: one that covers the years 2008 -- 2012, and another that covers 2013 -- 2017.
+The COG asks municipalities to report how much revenue they collect from ``penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation\ldots{} and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).'' We divide these amounts by the population to estimate the per-capita fees and fines revenue raised in each municipality.
+This data has been used as a proxy for the amount of tickets issued at the local level in scholarly research (see, for instance, \protect\hyperlink{ref-Goldstein2020}{Goldstein, Sances, and You 2020}; \protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
+
+The COG data are useful to isolate ticketing practices because other fines and fees (e.g.~fines imposed at sentencing in state court, probation fees, conviction fees, public defender fees) are typically collected by county or state governments.
+The COG data only include local revenues, which means the share of fines revenue corresponds more directly to local police practices.
+Following the guidance of \protect\hyperlink{ref-Sances2017}{Sances and You} (\protect\hyperlink{ref-Sances2017}{2017}), we retain only municipalities with police and/or court systems, as these are the only municipalities capable of issuing tickets.
+We also only retain municipalities with populations of at least 2,500.
+
+\textbf{Registered Voter Files}: The COG data do not include estimates of turnout at the local level.
+To estimate local turnout, we leverage registered voter files provided by data vendor L2 Political.
+In Washington, DC, and every state in the country (with the exception of North Dakota) voters are required to register to vote prior to participating.
+These files are considered public record, and in most states contain information about each voter's age, residential address, political affiliation, and participation history.
+L2 collects voter files from around the country and merges them with proprietary data that estimates other voter- and household-level characteristics such as race and education.
+The individual-level records are aggregated up to the municipality level to determine the number of ballots cast for members of each race; these estimates are divided by 5-year citizen voting age population (CVAP) estimates from the Census Bureau to calculate turnout.
+As we show in the Supplementary Information, the L2 racial estimates closely track the municipal-level racial estimates from the Census Bureau.
+Because our turnout numerator and denominators come from different sources, there is slight measurement error: our estimate indicates, for instance, that roughly 1 percent of municipalities had Black turnout above 100 percent.
+Where more votes were cast than the Census estimate for CVAP, we recode turnout as 100 percent.
+Our results do not change if we instead simply remove these municipalities, or use unmodified turnout estimates.
+
+\textbf{Estimation Strategy}: We begin by merging each municipality's fees and fines per capita (that is, dollars per resident) from the 2012 COG to its turnout from the 2014 midterm election, and the 2017 COG to its 2018 turnout.
+Because this measure is highly right-skewed, we use the natural log of fees and fines per capita (plus 1, to account for municipalities that collected no fees and fines).
+We also control for other municipal and state characteristics: racial composition, population density, median income, collegiate education, median age, and share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality's revenue that comes from the state or federal government in the 2012 and 2017 COGs.
+We retain the 8,954 municipalities whose data is reported to the COG in both 2012 and 2017 and meet the other criteria noted above; these constitute the target population.
+
+The 5-year cycle of the COG does not neatly line up with the general 4-year cycle typical of American elections.
+The timing of the COG and midterm elections mean that our analytical strategy is conservative.
+If municipalities shift their fees and fines collections dramatically over the 2013 -- 2017 period, this shift may influence their 2014 turnout.
+However, we assume that turnout in 2014 will still be influenced by the policing practices of the 2008 -- 2012 period, while 2018 turnout will be largely influenced by the practices of the 2013 -- 2017 period.
+
+We run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
+
+\hypertarget{national-survey-data}{%
+\subsection*{National Survey Data}\label{national-survey-data}}
+\addcontentsline{toc}{subsection}{National Survey Data}
+
+Next, we turn to the American National Election Studies 2020 Time Series data (ANES).
+The ANES has been fielded in every presidential election year since 1948 and is among the most widely-used tools for understanding American's political beliefs and behaviors, including their relationship with the criminal legal system (\protect\hyperlink{ref-Walker2020}{Walker 2020a}).
+It is weighted to be nationally representative of all American adults.
+In both 2016 and 2020, the ANES added new survey questions about respondent's encounters with the police and the criminal legal system.
+We focus in particular on two questions: \emph{During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?}, and \emph{Have you ever been arrested, or has that never happened to you?} We include the roughly 87 percent of respondents that answered both questions, giving us a sample size of 7,347 respondents, of whom just over 11\% identified as Black.
+
+We use these survey questions to make descriptive inferences about how stops and arrests affect the voting behavior of the general population.
+The first descriptive theoretical estimand is the gap between the voter turnout rate of individuals who were recently stopped by the police or who have ever been arrested, and another is whether stops or arrests uniquely influence the political behavior of Black Americans.
+In addition to the respondent's contact with the criminal legal system, we control for age; sex; income; education; party affiliation; self-described ideology; and reported 2016 turnout.
+
+There is an important caveat to the use of the ANES survey---namely, while the police stop question asks whether the respondent \emph{or anyone in their family} was stopped in the past year, the arrest question asks only about the individual respondent.
+While this may muddy the water between direct and proximal contact with the criminal legal system, we expect that the national survey data will give us some insight into the uniquely politicizing nature of police stops for Black Americans.
 
@@
 
-As discussed above, we begin by testing the relationship between police stops and turnout in the 2020 election, and then move to testing the relationship between fees and fines at the municipal level.
-We also examine whether the turnout of individuals stopped by the police before an election was different than those stopped after the election in Hillsborough County, Florida.
+As discussed above, we begin by examining whether the turnout of individuals ticketed before an election was different from those ticketed after the election in Hillsborough County, Florida.
+Next, we test the relationship between fines and fees revenue reliance and voter turnout at the municipal level.
+We also test the relationship between police stops and turnout in the 2020 election using survey data.
+
+\hypertarget{individual-level-results}{%
+\subsection*{Individual-Level Results}\label{individual-level-results}}
+\addcontentsline{toc}{subsection}{Individual-Level Results}
+
+To directly observe the effect of being stopped by the police on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
+As discussed above, we match individuals who were ticketed between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.\textsuperscript{2} Matching is done with replacement and ties are not broken.
+This means that some treated voters have multiple controls; the regression weights are calculated to account for this possibility.
+In Table 1 we present the results of the matching algorithm.
+As the table demonstrates, the selected control voters are very similar to the treated voters.
+
+\begin{singlespace}
+\input{"../temp/balance_table.tex"}
+\end{singlespace}
+
+It is worth noting that voters who were ticketed between 2012 and 2020 were far more likely to be Black and male than the general electorate, and live in Census block groups with moderately lower incomes.
+
+In Figure 1, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped.
+In the top row, we present the turnout in 2008--2014 of the individuals stopped between 2012 and 2014 and their controls; the second row shows the 2010--2016 turnout for individuals stopped between 2014 and 2016 and their controls; and the third shows the treatment effect for those stopped in the 2 years prior to the 2018 midterms.
+Finally, in the bottom row, we present the overall turnout effects for these three elections.
+The first election following a treated voter's stop is denoted as \emph{t = 0} while the years in which \emph{t} is less than zero are the periods prior to the stop.
+
+\begin{figure}[!htb]
+
+{\centering \includegraphics{draft_paper_files/figure-latex/did1-1}
+
+}
+
+\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout}\label{fig:did1}
+\end{figure}
+
+Figure 1 makes a number of things immediately apparent.
+First, we can see that for both Black and non-Black voters the pre-treatment trends are identical.
+This, combined with the fact that treated and control voters mirror one another in terms of other characteristics, lends credibility to the parallel trends assumption.
+Secondly, Figure 1 provides preliminary visual evidence of the demobilizing effects of police stops in Hillsborough County.
+However, as the figure also makes clear, it seems that the negative effects are concentrated in the lower-salience midterm elections; there is little evidence of turnout effects in the 2016 presidential election.
+
+Table 2 formalizes the final row of Figure 1 into an ordinary least squares regression (the regression tables broken out for each year can be found in the Supplementary Information).
+Models 1 and 2 show our overall causal effect, while models 3 and 4 allow for the possibility that a ticket differentially mobilizes Black voters.
+In models 1 and 3, we include only the treatment, timing, and race dummies, while the full set of covariates used for the matching procedure are included in models 2 and 4.
+The empirical estimands are \emph{Treated × Post Treatment} and \emph{Treated × Post Treatment × Black}.
+In models 1 and 2, \emph{Treated × Post Treatment} measures the overall treatment effect, and in models 3 and 4 it measures the treatment effect for non-Black voters.
+\emph{Treated × Post Treatment × Black} measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
+
+\begin{singlespace}
+\input{"../temp/dind_reg_y.tex"}
+\end{singlespace}
+
+As both Figure 1 and Table 2 make clear, police tickets meaningfully depressed turnout.
+In models 1 and 2, the estimated overall treatment effect is -1.5 percentage points.
+In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---non-Black turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
+Although the treatment effect is still substantively quite large for Black individuals, Hillsborough County Black voters' turnout in federal elections was not as negatively impacted by police contact as that of non-Black individuals.
+
+\hypertarget{municipal-level-results}{%
+\subsection*{Municipal-Level Results}\label{municipal-level-results}}
+\addcontentsline{toc}{subsection}{Municipal-Level Results}
+
+Before testing the causal effect of fees and fines collections on turnout, we begin with a cross-sectional analysis of the relationship using ordinary least squares.
+Here, we regress municipality-level turnout in 2018 against fees and fines collections as reported in the 2017 COG, as well as a number of other covariates.
+In Figure 2 we present the marginal effect of fees and fines on municipal-level turnout.
+The plot shows the results from two separate models: one in which the dependent variable is Black turnout (as a share of CVAP), and a second in which the dependent variable is non-Black turnout.
+The figure also marks the interdecile range.
+The full regression table can be found in the Supplementary Information.
+
+\begin{figure}[!htb]
+
+{\centering \includegraphics{draft_paper_files/figure-latex/cross-18-1}
+
+}
+
+\caption{\label{fig:mef-2018}Predicted Turnout, 2018}\label{fig:cross-18}
+\end{figure}
+
+As Figure 2 makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 1.5 percentage points over the interdecile range, after controlling for the other covariates.
+The opposite is true for Black voters: over the same range, Black turnout \emph{increases} by roughly 2.4 percentage points.
+Both relationships are statistically significant at the 95 confidence level.
+This does not prove that higher fees and fines increase Black turnout; cross-sectional regressions cannot establish causality.
+Nevertheless, Figure 2 is consistent with this story.
+
+We turn now to our two-way fixed effects model.
+As discussed above, we retain each municipality that reported their fees and fines data to the COG in both 2012 and 2017 (and met the other criteria discussed in the \emph{Data and Design} section).
+The dependent variable in each model is calculated by dividing the number of ballots cast in 2014 and 2018 by the 5-year CVAP estimate from the same year.
+We run the two-way fixed effects on overall turnout, Black turnout, and non-Black turnout.
+The results of these models can be found in Table 3.
+The average municipality included in this analysis raised \$2.17 in fees and fines per resident in 2012, and the average municipality increased this per-capita figure by \$0.47 between 2012 and 2017.
+Just over 10\% of municipalities raised no revenue from fees and fines in either year.
+
+\begin{singlespace}
+\input{"../temp/2wfe_reg_clean.tex"}
+\end{singlespace}
+
+The results of the two-way fixed effects model are different from what we saw in the 2018 cross-sectional approach; namely, Table 3 indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not significantly impact Black turnout.
+The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.04 percentage points.
 
@@
 In this section we make use of the American National Election Studies 2020 Time Series Data (ANES).
-The test for this section is simple: we ask whether, after controlling for standard covariates, having personal or proximal contact with a police stop in the previous 12 months is associated with whether a respondent voted in the 2020 presidential election.
+The first test is simple: we ask whether, after controlling for standard covariates, having personal or proximal contact with a police stop in the previous 12 months is associated with whether a respondent voted in the 2020 presidential election.
 We also ask whether this relationship was different for Black and non-Black respondents.
@@
 Roughly 15 percent of non-Black respondents reported a police stop in the preceding 12 months, while the same was true for more than 22 percent of Black respondents.
-In Figure \ref{fig:anes} we present the results of our econometric models.
+In Figure 3 we present the results of our econometric models.
 In the left-hand panel, we show the predicted turnout of respondents who answered ``yes'' or ``no'' to the question \emph{During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?} The right-hand panel, meanwhile, plots these relationships for respondents who answered ``yes'' or ``no'' to the question \emph{Have you ever been arrested, or has that never happened to you?}.
-These are the predicted probabilities after controlling for respondents' race / ethnicity; age; party; ideology; income; 2016 turnout; and education.
+These are the predicted probabilities after controlling for respondents' race / ethnicity; age; party; ideology; income; education; and 2016 turnout.
 The full regression table can be found in the Supplementary Information..
@@
 
-Figure \ref{fig:anes} demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (\emph{p} = 0.005).
+Figure 3 demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (\emph{p} = 0.005).
 The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (\emph{p} = 0.27).
@@
 
-The second panel of Figure \ref{fig:anes} shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
+The second panel of Figure 3 shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
 Importantly, the interaction between arrest status and the respondent's race was not statistically significant.
-In other words, although police stops seem to be uniquely mobilizing for Black Americans, we fail to uncover evidence that arrests differentially structured subsequent Black- and non-Black turnout.
-
-These cross-sectional results cannot establish causality.
+In other words, although police stops seem to be uniquely mobilizing for Black Americans, we fail to uncover evidence that arrests differentially structured subsequent Black and non-Black turnout.
+
+This theoretical estimand is descriptive, and cross-sectional results cannot establish causality.
 It is possible that Black respondents who had been stopped by the police (or had family members who experienced a stop) differed from non-Black respondents with such contact in ways that cannot be captured by the survey data.
-However, our findings are consistent with a causal story that police stops are mobilizing for Black Americans---but that this is not the case for higher-level contact such as arrests.
-
-\hypertarget{municipal-level-results}{%
-\subsection*{Municipal-Level Results}\label{municipal-level-results}}
-\addcontentsline{toc}{subsection}{Municipal-Level Results}
-
-Before testing the causal effect of fees and fines collections on turnout, we begin with a cross-sectional analysis of the relationship using ordinary least squares.
-Here, we regress municipality-level turnout in 2018 against fees and fines collections as reported in the 2017 COG, as well as a number of other covariates.
-In Figure \ref{fig:mef-2018} we present the marginal effect of fees and fines on municipal-level turnout.
-The plot shows the results from two separate models: one in which the dependent variable is Black turnout (as a share of CVAP), and a second in which the dependent variable is non-Black turnout.
-The figure also marks the interdecile range.
-The full regression table can be found in the Supplementary Information.
-
-\begin{figure}[H]
-
-{\centering \includegraphics{draft_paper_files/figure-latex/cross-18-1}
-
-}
-
-\caption{\label{fig:mef-2018}Predicted Turnout, 2018}\label{fig:cross-18}
-\end{figure}
-
-As Figure \ref{fig:mef-2018} makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 1.5 percentage points over the interdecile range, after controlling for the other covariates.
-The opposite is true for Black voters: over the same range, Black turnout \emph{increases} by roughly 2.4 percentage points.
-Both relationships are statistically significant at the 95 confidence level.
-This does not prove that higher fees and fines increase Black turnout; cross-sectional regressions cannot establish causality.
-Nevertheless, Figure \ref{fig:mef-2018} is consistent with this story.
-
-We turn now to our two-way fixed effects model.
-As discussed above, we retain each municipality that reported their fees and fines data to the COG in both 2012 and 2017 (and met the other criteria discussed in the \emph{Data and Design} section).
-The dependent variable in each model is calculated by dividing the number of ballots cast in 2014 and 2018 by the 5-year CVAP estimate from the same year.
-We run the two-way fixed effects on overall turnout, Black turnout, and non-Black turnout.
-The results of these models can be found in Table \ref{tab:twfe}.
-The average municipality included in this analysis raised \$2.17 in fees and fines per resident in 2012, and the average municipality increased or decreased this per-capita figure by \$0.47 between 2012 and 2017.
-Just over 10\% of municipalities raised no revenue from fees and fines in either year.
-
-\begin{singlespace}
-\input{"../temp/2wfe_reg_clean.tex"}
-\end{singlespace}
-
-The results of the two-way fixed effects model are different than what we saw in the 2018 cross-sectional approach; namely, Table \ref{tab:twfe} indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not significantly impact Black turnout.
-The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.04 percentage points.
-
-\hypertarget{individual-level-results}{%
-\subsection*{Individual-Level Results}\label{individual-level-results}}
-\addcontentsline{toc}{subsection}{Individual-Level Results}
-
-Thus far, we have shown that Black individuals with police contact reported participating at higher rates in the 2020 election than those without such contact.
-We also demonstrated that voter turnout decreases in municipalities that increased fines and fees collections.
-We argue that this relationship is causal: increased fees and fines collections means that more residents have direct interactions with the criminal legal system.
-Based on prior literature, we assume there are indirect effects as well, as more residents know a family or community member who has been ticketed.
-While the national analyses give us great breadth and an increased understanding of how this plays out across the country, they leave us unable to directly observe the causal mechanisms at play.
-
-To directly observe the effect of being stopped by the police on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
-As discussed above, we match individuals who were ticketed between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.\footnote{Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
-The full sample is used in the actual matching process.} Matching is done with replacement and ties are not broken.
-This means that some treated voters have multiple controls; the regression weights are calculated to allow for this possibility.
-In Table \ref{tab:balance} we present the results of the matching algorithm.
-As the table demonstrates, the selected control voters are very similar to the treated voters.
-
-\begin{singlespace}
-\begin{table}[!h]
-
-\caption{\label{tab:baltab-chunk}\label{tab:balance} Balance Table}
-\centering
-\begin{tabular}[t]{llll}
-\toprule
-Variable & Treated Voters & Control Voters & Never Stopped\\
-\midrule
-\%White & 47.4\% & 47.6\% & 62.2\%\\
-\% Black & 24.4\% & 25.1\% & 13.1\%\\
-\% Latino & 19.0\% & 19.3\% & 16.0\%\\
-\% Asian & 2.1\% & 2.1\% & 2.7\%\\
-\% Male & 53.2\% & 53.0\% & 42.8\%\\
-\% Democrat & 42.5\% & 43.1\% & 37.9\%\\
-\% Republican & 23.7\% & 23.6\% & 31.3\%\\
-Age & 42.5 & 41.8 & 51.9\\
-Median Income & \$62,836 & \$62,497 & \$67,897\\
-\% with Some College & 73.9\% & 74.1\% & 76.5\%\\
-Unemployment Rate & 6.6\% & 6.6\% & 5.9\%\\
-Turnout\textsubscript{t=-3} & 31.7\% & 31.7\% & \\
-Turnout\textsubscript{t=-2} & 29.6\% & 29.6\% & \\
-Turnout\textsubscript{t=-1} & 44.6\% & 44.6\% & \\
-Stops in pre-period & 2.2 & 1.9 & \\
-Paid Money & 89.1\% & 89.1\% & \\
-Civil Stop & 82.6\% & 82.6\% & \\
-Stopped by Tampa PD & 47.0\% & 47.0\% & \\
-\bottomrule
-\end{tabular}
-\end{table}
-\end{singlespace}
-
-It is worth noting that voters who were stopped between 2012 and 2020 were far more likely to be Black and male than the general electorate, and live in Census block groups with moderately lower incomes.
-
-While Table \ref{tab:balance} indicates that our treatment voters and their matches are substantially similar to their matches, the validity of the difference-in-differences design requires that any turnout gap between treatment and control voters be comparable in the baseline period.
-In Figure \ref{fig:did1}, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped.
-The first election following a treated voter's stop is denoted as \emph{t = 0} while the years in which \emph{t} is less than zero are the periods prior to the stop.
-This means that for someone stopped in 2013 (and their controls), \emph{t} is 0 in 2014, while \emph{t} is equal to 0 in 2018 for an individual stopped between the 2016 and 2018 elections.
-
-\begin{figure}[H]
-
-{\centering \includegraphics{draft_paper_files/figure-latex/did1-1}
-
-}
-
-\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout}\label{fig:did1}
-\end{figure}
-
-Figure \ref{fig:did1} makes a number of things immediately apparent.
-First, we can see that for both Black and non-Black voters the parallel trends assumption is satisfied.
-Because we matched treated and control voters based on turnout prior to the ticket, this is by design.
-
-Table \ref{tab:dind-table} formalizes Figure \ref{fig:did1} into an ordinary least squares regression.
-Models 1 and 2 show our overall causal effect, while models 3 and 4 allow for the possibility that a ticket differentially mobilizes Black voters.
-In models 1 and 3, we include only the treatment, timing, and race dummies, while the full set of covariates used for the matching procedure are included in models 2 and 4.
-The coefficients of note are \emph{Treated × Post Treatment} and \emph{Treated × Post Treatment × Black}.
-In models 1 and 2, \emph{Treated × Post Treatment} measures the overall treatment effect, and in models 3 and 4 it measures the treatment effect for non-Black voters.
-\emph{Treated × Post Treatment × Black} measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
-
-\begin{singlespace}
-\input{"../temp/dind_reg_y.tex"}
-\end{singlespace}
-
-As both Figure \ref{fig:did1} and Table \ref{tab:dind-table} make clear, police tickets meaningfully depressed turnout.
-In models 1 and 2, the estimated overall treatment effect is -1.5 percentage points.
-In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---non-Black turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
-Although the treatment effect is still substantively quite large for Black individuals, the pattern follows our national analysis.
-It appears that, in Tampa and around the country, Black voters' turnout in federal elections is not as negatively impacted by police contact as that of non-Black individuals.
+However, our findings are consistent with a causal story that police stops are uniquely mobilizing for Black Americans---but this is not the case for higher-level contact, such as arrests.
 
@@
 Based on these three independent approaches, we conclude that the political consequences of police stops are unique for Black Americans---and that they are less demobilizing for Black Americans than others.
-
-The difference between the cross-sectional and two-way fixed effects models using the municipality-level data is somewhat surprising. There are a few potential explanations for this mismatch.
-
-First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes in the two-way fixed effects models are smaller or not statistically significant.
-Along a similar vein, it's possible that the effect size for Black voters in the city-level analysis is influenced by higher-intensity forms of criminal legal contact, such as arrest and incarceration.
-The bulk of existing literature suggests that incarceration discourages political participation, and it's not unreasonable to assume that cities that ramp up ticketing of Black residents also ramp up arrest and incarceration of Black residents.
-If these phenomena coincide, that could explain why the city-level analysis produced no statistically significant effect for Black voters---the personally mobilizing effect of ticketing could be counterbalanced by the proximal chilling effect of incarceration, and because the city-level analysis is not as temporally sensitive, it's more difficult to isolate the effect of ticketing.
-We were unable to incorporate a measure of local incarceration trends due to a lack of consistent data nationwide.
-
-Moreover, Sances and You (\protect\hyperlink{ref-Sances2017}{2017, 1091})---the paper that originally detailed the relationship between fees and fines collections and municipalities' racial composition using the Census of Governments data---specifically notes that they did not exploit the panel setup of the COG because of ``little variation within a city in terms of revenues from fines.'' Instead, they present only the results of a cross-sectional study.
-Here, we present both the cross-sectional and panel results, acknowledging that each have limitations but that, taken together, they shed light on the unique politicization of fees and fines for Black Americans.
+Additionally, as \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020b}) suggests, ticketed Black individuals may be politically mobilized for activities other than voting not observed in this study, such as contacting elected representatives or volunteering for campaigns.
 
@@
 
-In this sense, our analysis points to a political contestation of criminal legal policy, a phenomenon that aligns with dozens of recent campaigns to reform local fines and fees practices (or abolish them entirely).\footnote{See \url{https://finesandfeesjusticecenter.org/clearinghouse}.} We know that fines and fees result from political economy (i.e.~austerity at the federal level), but our analysis suggests that this is a ``two way street'' wherein people who are harmed by policing practices are politically socialized into resistance.
-
-\textbf{Limitations}: Because our individual-level analysis is limited to Hillsborough County, we don't have a good sense of how the city-level revenue reliance trend interacts with the individual experience of being ticketed.
+In this sense, our analysis points to a political contestation of criminal legal policy, a phenomenon that aligns with dozens of recent campaigns to reform local fines and fees practices (or abolish them entirely).\textsuperscript{3} We know that increased fines and fees result from political economy (i.e.~austerity at the federal level), but our analysis suggests that this is a ``two way street'' wherein people who are harmed by policing practices can be politically socialized into resistance.
+
+\textbf{Limitations}: Because our individual-level administrative data analysis is limited to Hillsborough County where fines collections increased over the period, we do not have a good sense of how the city-level revenue reliance trend interacts with the individual experience of being ticketed in areas where fees and fines are constant or decreasing.
 Is ticketing more politically mobilizing for Black voters in cities that are palpably dialing up their revenue collection efforts?
@@
 Policymakers should work to ensure that Black Americans no longer have to struggle to enjoy the same political power as whites---to that end, the current trend of voting rights restriction policies across the country is especially pernicious.
-Even if Black Americans understand the ballot box as one tool they can use to limit the state's power to exploit and harm them, policymakers should still feel an obligation to support voting rights and stop disproportionate ticketing in Black communities.
+Even if Black Americans understand the ballot box as one tool they can use to limit the state's power to exploit and harm them, policymakers should still feel an obligation to support voting rights protections and stop disproportionate ticketing in Black communities.
+
+\newpage
+
+\hypertarget{notes}{%
+\section*{Notes}\label{notes}}
+\addcontentsline{toc}{section}{Notes}
+
+\textsuperscript{1} Because such frequent snapshots are not available from L2, we here use the registered voter file made freely available by the state of Florida.
+
+\textsuperscript{2} Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
+The full sample is used in the actual matching process.
+
+\textsuperscript{3} See \url{https://finesandfeesjusticecenter.org/clearinghouse}.
 
@@
 
-\leavevmode\hypertarget{ref-Campbell2021}{}%
-Campbell, Travis.
-2021.
-{``Black {Lives Matter}'s {Effect} on {Police Lethal Use}-of-{Force}.''} SSRN Scholarly Paper ID 3767097.
-{Rochester, NY}: {Social Science Research Network}.
-\url{https://doi.org/10.2139/ssrn.3767097}.
-
-\leavevmode\hypertarget{ref-Carlton2018}{}%
-Carlton, Sue.
-2018.
-{``Carlton: {Jane Castor} Now Says Biking-While-Black Tickets Were Wrong.''} \emph{Tampa Bay Times}, April 12, 2018.
-\url{https://www.tampabay.com/news/politics/local/Carlton-Jane-Castor-now-says-biking-while-black-tickets-were-wrong_167233952/}.
+\leavevmode\hypertarget{ref-Bushway2007}{}%
+Bushway, Shawn D., Michael A.
+Stoll, and David Weiman.
+2007.
+\emph{Barriers to {Reentry}?: {The Labor Market} for {Released Prisoners} in {Post}-{Industrial America}}.
+{Russell Sage Foundation}.
+\url{http://books.google.com?id=YOeFAwAAQBAJ}.
+
+\leavevmode\hypertarget{ref-Butler2011}{}%
+Butler, Daniel M., and David E.
+Broockman.
+2011.
+{``Do {Politicians Racially Discriminate Against Constituents}?
+{A Field Experiment} on {State Legislators}.''} \emph{American Journal of Political Science} 55 (3): 463--77.
+\url{https://doi.org/10.1111/j.1540-5907.2011.00515.x}.
 
@@
 Colgan, Beth A. 2019. {``Wealth-{Based Penal Disenfranchisement}.''} \emph{Vanderbilt Law Review} 72 (January). \url{https://papers.ssrn.com/abstract=3312439}.
-
-\leavevmode\hypertarget{ref-Dawson1995}{}%
-Dawson, Michael C. 1995. \emph{Behind the Mule: Race and Class in {African}-{American} Politics}. 1st pbk printing. {Princeton, NJ}: {Princeton Univ. Press}.
 
@@
 
-\leavevmode\hypertarget{ref-Ehrenfreund2014}{}%
-Ehrenfreund, Max.
-2014.
-{``How Segregation Led to Speed Traps, Traffic Tickets and Distrust Outside {St}.
-{Louis}.''} \emph{Washington Post}, November 26, 2014.
-\url{https://www.washingtonpost.com/news/wonk/wp/2014/11/26/how-segregation-led-to-speed-traps-traffic-tickets-and-distrust-outside-st-louis/}.
-
-\leavevmode\hypertarget{ref-Eligon2019}{}%
-Eligon, John.
-2019.
-{``Stopped, {Ticketed}, {Fined}: {The Pitfalls} of {Driving While Black} in {Ferguson}.''} \emph{The New York Times: U.S.}, August 6, 2019.
-\url{https://www.nytimes.com/2019/08/06/us/black-drivers-traffic-stops.html}.
-
-\leavevmode\hypertarget{ref-Epp2014}{}%
-Epp, Charles R., Steven Maynard-Moody, and Donald P.
-Haider-Markel.
-2014.
-\emph{Pulled {Over}}.
-{The University of Chicago Press}.
-\url{https://press.uchicago.edu/ucp/books/book/chicago/P/bo17322831.html}.
-
-\leavevmode\hypertarget{ref-Frago2019}{}%
-Frago, Charlie.
-2019.
-{``Tampa Police Have {`Evolved'} on Biking While Black, Chief Says.''} \emph{Tampa Bay Times}, October 24, 2019.
-\url{https://www.tampabay.com/news/tampa/2019/10/24/tampa-police-have-evolved-on-biking-while-black-chief-says/}.
+\leavevmode\hypertarget{ref-Ewald2002}{}%
+Ewald, Alec C. 2002. {``'{Civil} Death': {The} Ideological Paradox of Criminal Disenfranchisement Law in the {United States}.''} \emph{Wisconsin Law Review} 2002 (5): 1045--1137.
 
@@
 
-\leavevmode\hypertarget{ref-Harrell2020}{}%
-Harrell, Erika, and Elizabeth Davis.
-2020.
-{``Contacts {Between Police} and the {Public}, 2018 - {Statistical Tables}.''} {Bureau of Justice Statistics}.
-\url{https://www.bjs.gov/index.cfm?ty=pbdetail\&iid=7167}.
+\leavevmode\hypertarget{ref-Gunderson2020}{}%
+Gunderson, Anna.
+2020.
+{``Representation, {Incorporation}, and {Corrections Spending}: {The Counterbalancing Effect} of {Black Political Incorporation}.''} \emph{Journal of Race, Ethnicity, and Politics} 5 (3): 573--603.
+\url{https://doi.org/10.1017/rep.2020.15}.
 
@@
 
+\leavevmode\hypertarget{ref-Harris2020}{}%
+Harris, Allison P., Elliott Ash, and Jeffrey Fagan.
+2020.
+{``Fiscal {Pressures} and {Discriminatory Policing}: {Evidence} from {Traffic Stops} in {Missouri}.''} \emph{Journal of Race, Ethnicity, and Politics} 5 (3): 450--80.
+\url{https://doi.org/10.1017/rep.2020.10}.
+
 \leavevmode\hypertarget{ref-Hinton2017}{}%
@@
 \url{http://www.theguardian.com/us-news/2015/apr/08/protesters-demand-justice-walter-scott-north-charleston}.
-
-\leavevmode\hypertarget{ref-Imai2016}{}%
-Imai, Kosuke, and Kabir Khanna.
-2016.
-{``Improving {Ecological Inference} by {Predicting Individual Ethnicity} from {Voter Registration Records}.''} \emph{Political Analysis} 24 (2): 263--72.
-\url{https://doi.org/10.1093/pan/mpw001}.
 
@@
 
-\leavevmode\hypertarget{ref-Looney2018}{}%
-Looney, Adam, and Nicholas Turner.
-2018.
-{``Work and Opportunity Before and After Incarceration.''} {The Brookings Institution}.
-\url{https://www.brookings.edu/wp-content/uploads/2018/03/es_20180314_looneyincarceration_final.pdf}.
+\leavevmode\hypertarget{ref-Lundberg2021}{}%
+Lundberg, Ian, Rebecca Johnson, and Brandon M.
+Stewart.
+2021.
+{``What {Is Your Estimand}?
+{Defining} the {Target Quantity Connects Statistical Evidence} to {Theory}.''} \emph{American Sociological Review} 86 (3): 532--65.
+\url{https://doi.org/10.1177/00031224211004187}.
 
@@
 
-\leavevmode\hypertarget{ref-Meredith2017}{}%
----------. 2017. {``Discretionary {Disenfranchisement}: {The Case} of {Legal Financial Obligations}.''} \emph{The Journal of Legal Studies} 46 (2): 309--38. \url{https://doi.org/10.1086/694323}.
+\leavevmode\hypertarget{ref-Miller2012}{}%
+Miller, Bryan Lee, and Joseph F.
+Spillane.
+2012.
+{``Civil Death: {An} Examination of Ex-Felon Disenfranchisement and Reintegration.''} \emph{Punishment \& Society} 14 (4): 402--28.
+\url{https://doi.org/10.1177/1462474512452513}.
+
+\leavevmode\hypertarget{ref-Miller2017}{}%
+Miller, Reuben Jonathan, and Forrest Stuart.
+2017.
+{``Carceral {Citizenship}: {Race}, {Rights} and {Responsibility} in the {Age} of {Mass Supervision}.''} \emph{Theoretical Criminology} 21 (4): 532--48.
+\url{https://doi.org/10.1177/1362480617731203}.
 
@@
 
-\leavevmode\hypertarget{ref-Vargas2017a}{}%
+\leavevmode\hypertarget{ref-Vargas2017}{}%
 Vargas, Robert, and Philip McHarris.
@@
 
+\leavevmode\hypertarget{ref-Walker2020}{}%
+---------. 2020a. \emph{Mobilized by Injustice: Criminal Justice Contact, Political Participation, and Race}. {NewYork}: {Oxford University Press 2020}.
+
 \leavevmode\hypertarget{ref-Walker2020a}{}%
----------. 2020a. \emph{Mobilized by Injustice: Criminal Justice Contact, Political Participation, and Race}. {NewYork}: {Oxford University Press 2020}.
-
-\leavevmode\hypertarget{ref-Walker2020}{}%
 ---------. 2020b. {``Targeted: {The Mobilizing Effect} of {Perceptions} of {Unfair Policing Practices}.''} \emph{The Journal of Politics} 82 (1): 119--34. \url{https://doi.org/10.1086/705684}.
-
-\leavevmode\hypertarget{ref-Walker2017}{}%
-Walker, Hannah L., and Marcela García-Castañon.
-2017.
-{``For {Love} and {Justice}: {The Mobilizing} of {Race}, {Gender}, and {Criminal Justice Contact}.''} \emph{Politics \& Gender} 13 (4): 541--68.
-\url{https://doi.org/10.1017/S1743923X17000198}.
 
@@
 
-\leavevmode\hypertarget{ref-Zayas2015}{}%
-Zayas, Alexandra.
-2015.
-{``How Riding Your Bike Can Land You in Trouble with the Cops --- If You're Black.''} \emph{Tampa Bay Times}, April 15, 2015.
-\url{https://www.tampabay.com/news/publicsafety/how-riding-your-bike-can-land-you-in-trouble-with-the-cops—if-youre-black/2225966/}.
-
 \end{CSLReferences}

### 2022-02-14 markdown/si.Rmd
pre 2022 edits

@@
 title: "Supplementary Information"
-output: word_document
+output:
+  bookdown::pdf_document2:
+    toc: no
+    fig_caption: yes
+    latex_engine: xelatex
+    keep_tex: true
 bibliography: "policing_turnout.bib"
@@
 
-```{r windows, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:rob-window}Estimated Treatment Effect for Different Treatment Windows", fig.pos = "H", fig.align = "center"}
+```{r windows, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:rob-window}Estimated Treatment Effect for Different Treatment Windows", fig.pos = "!htb", fig.align = "center"}
 p2 <- readRDS("temp/windows_rob.rds")

### 2022-02-14 markdown/si.tex
pre 2022 edits

@@
 
-{
-\setcounter{tocdepth}{2}
-\tableofcontents
-}
 \pagenumbering{gobble}
@@
 
-\begin{figure}[H]
+\begin{figure}[!htb]
 
@@
 In the body of this manuscript, we present only the overall treatment effects for the police stops in Hillsborough County, which are effectively averaged across all three years.
-Here, in Tables \ref{tab:dind-table-2014}--\ref{tab:dind-table-2018}, we present the results for each group of treated and control voters.
-In Table \ref{tab:dind-table-2014}, all treated voters were stopped between the 2012 and 2014 elections, and all controls were stopped between the 2014 and 2016 elections.
-In Table \ref{tab:dind-table-2016}, treated voters were stopped between 2014 and 2016, while controls were stopped between 2016 and 2018.
-Finally, Table \ref{tab:dind-table-2018} presents the treatment effect for voters stopped between 2016 and 2018, relative to their controls stopped between the 2018 and 2020 elections.
+Here, in Tables 2--4, we present the results for each group of treated and control voters.
+In Table 2, all treated voters were stopped between the 2012 and 2014 elections, and all controls were stopped between the 2014 and 2016 elections.
+In Table 3, treated voters were stopped between 2014 and 2016, while controls were stopped between 2016 and 2018.
+Finally, Table 4 presents the treatment effect for voters stopped between 2016 and 2018, relative to their controls stopped between the 2018 and 2020 elections.
 In every year, there is a statistically significant, negative treatment effect for non-Black voters.
@@
 
-In Table \ref{tab:mae} we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level and adjusted according to the CPS, relative to the Census Bureau's CVAP estimate.
+In Table 5 we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level and adjusted according to the CPS, relative to the Census Bureau's CVAP estimate.
 Because it seems possible that these errors vary by population size, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.
@@
 
-Table \ref{tab:mae} makes clear that the adjusted Black estimates of the electorate mirror the Black share of CVAP very closely: for no group of municipalities does the MAE exceed 3\%.
+Table 5 makes clear that the adjusted Black estimates of the electorate mirror the Black share of CVAP very closely: for no group of municipalities does the MAE exceed 3\%.
 This seems to indicate that the L2 racial estimates are quite good when aggregated to the municipal level.
 
-In Table \ref{tab:mae:reg}, we show that the difference between the adjusted estimate of the Black share of the electorate and the Black share of the CVAP is entirely unrelated to cities' per-capita fees and fines, after controlling for other characteristics.
+In Table 6, we show that the difference between the adjusted estimate of the Black share of the electorate and the Black share of the CVAP is entirely unrelated to cities' per-capita fees and fines, after controlling for other characteristics.
 Given the low MAE and the lack of relationship between the error and the fees and fines, we conclude that the municipal-level racial estimates from the individual-level records are reasonable and unbiased.
@@
 
-In Table \ref{tab:cog-cross-reg} we present the full results of the econometric used to test the cross-sectional relationship between per-capita fees and fines, and 2018 municipal turnout.
+In Table 7 we present the full results of the econometric used to test the cross-sectional relationship between per-capita fees and fines, and 2018 municipal turnout.
 The table shows that a doubling of the fees and fines collected per capita is associated with a 0.3 percentage point reduction in overall turnout.
@@
 
-Model 1 in Table \ref{tab:anes-reg} shows that Black individuals who had been stopped by the police (or had a family member stopped) in the preceding 12 months were 9 percentage points more likely to vote in 2020, other things equal; they were not related to turnout for non-Black respondents.
+Model 1 in Table 8 shows that Black individuals who had been stopped by the police (or had a family member stopped) in the preceding 12 months were 9 percentage points more likely to vote in 2020, other things equal; they were not related to turnout for non-Black respondents.
 Police stops are not, however, associated with different turnout effects for other non-white groups.

### 2022-02-14 code/00_initialize.R

@@ -2,8 +2,10 @@ library(splitstackshape)
 library(PanelMatch)
 library(rgdal)
 library(sqldf)
+library(fixest)
 library(Metrics)
 library(RSQLite)
+library(modelsummary)
 library(tidycensus)
 library(multcomp)
 library(miceadds)
@@ -20,7 +22,7 @@ library(tidyverse)
 library(kevostools)
 
 save <- c("db", "cleanup", "theme_bc", "save", "weighted.ttest.ci")
-
+options("modelsummary_format_numeric_latex" = "plain")
 
 cleanup <- function(...){
   save2 <- c(save, ...)

### 2022-02-14 code/04_anes.R

@@ -1,5 +1,5 @@
 
-anes_pre <- read.dta13("../regular_data/anes/anes_timeseries_2020_stata_20210324/anes_timeseries_2020_stata_20210324.dta")
+anes_pre <- fread("F:/regular_data/anes/anes_timeseries_2020_csv_20210719/anes_timeseries_2020_csv_20210719.csv")
 
 
 anes_pre <- anes_pre %>% 
@@ -12,14 +12,16 @@ anes_pre <- anes_pre %>%
          asian = V201549x == 4,
          party = ifelse(V201228 == 1 | V201230 == 3, "DEM",
                         ifelse(V201228 == 2 | V201230 == 1, "REP", "OTH")),
-         vote16 = as.integer(V201101 == 1 | V201102 == 1))
+         vote16 = as.integer(V201101 == 1 | V201102 == 1),
+         imp = V202500x)
 
 anes_pre$party <- factor(anes_pre$party, levels = c("DEM", "REP", "OTH"))
 
 income <- fread("../regular_data/anes/income_lu.csv")
 
 anes_pre <- left_join(anes_pre, income) %>% 
-  mutate(income = income / 10000)
+  mutate(income = income / 10000,
+         cd = paste(V203000, V203002))
 
 reg_d <- select(anes_pre, ideol, white, black, latino, party, V200002,
                 age, income, V200010b, to, asian, V201600, V201201,
@@ -28,7 +30,7 @@ reg_d <- select(anes_pre, ideol, white, black, latino, party, V200002,
                 fair_police = V202493x,
                 self_descrim = V202537,
                 linked_fate_black = V202507,
-                blm = V202174, vote16) %>% 
+                blm = V202174, vote16, cd, imp) %>% 
   filter(V202456 %in% c(1, 2),
          V202457 %in% c(1, 2)) %>% 
   mutate(stopped = V202456 == 1,
@@ -71,77 +73,42 @@ reg_d <- select(anes_pre, ideol, white, black, latino, party, V200002,
   mutate_at(vars(white, latino, asian, to, black, stopped, arrested), ~ ifelse(., 1, 0))
 
 
-m_stop <- lm(to ~ stopped*black + white + latino + asian + age + party + income + sex +
-               ideol + educ + vote16, filter(reg_d), weight = V200010b)
+m_stop <- feols(to ~ stopped*black + white + latino + asian + age + party + income + sex +
[…]

### 2022-02-14 code/hills/cam/04_match.R

@@ -12,7 +12,7 @@ require(snow)
 require(parallel)
 
 
-hills_pre_match <- readRDS("temp/hills_pre_match.rds")
+hills_pre_match <- readRDS("temp/hills_pre_match_cam.rds")
 
 ############## 2014
 
@@ -75,7 +75,7 @@ hills18 <- bind_rows(hills18_t, hills18_c) %>%
 ###########################################
 pre <- bind_rows(hills14, hills16, hills18)
 
-saveRDS(pre, "temp/real_pre_match_hills.rds")
+saveRDS(pre, "temp/real_pre_match_hills_cam.rds")
 
 ids <- pre %>%
   mutate(id = row_number()) %>%
@@ -87,7 +87,7 @@ X <- pre %>%
   mutate_at(vars(white, black, latino, asian, male, dem, rep, v1, v2, v3, paid), ~ ifelse(. == T, 1, 0)) %>% 
   select(first_tr_year, paid, civil, tampa_pd, v1, v2, v3, everything())
 
-genout <- readRDS("temp/genout_hills_yem.rds")
+genout <- readRDS("temp/genout_hills_yem_cam.rds")
 
 
 mout <- Matchby(Tr = pre$treated, X = X,
@@ -103,9 +103,9 @@ mout <- Matchby(Tr = pre$treated, X = X,
 
 
 
-save(mout, file = "./temp/mout_hills_y.RData")
+save(mout, file = "./temp/mout_hills_y_cam.RData")
 
-load("temp/mout_hills_y.RData")
+load("temp/mout_hills_y_cam.RData")
 
 matches <- data.table(voter = c(mout$index.control,
                                 mout$index.treated),
@@ -124,4 +124,4 @@ matches <- left_join(matches, ids, by = c("group" = "id")) %>%
   select(-group) %>%
   rename(group = voter_id)
 
-saveRDS(matches, "temp/matches_hills_yem.rds")
+saveRDS(matches, "temp/matches_hills_yem_cam.rds")

### 2022-02-14 code/hills/cam/05_regression.R

@@ -1,0 +1,278 @@
+
+#####
+hills_pre_match <- readRDS("temp/real_pre_match_hills_cam.rds") %>% 
+  ungroup()
+
+matches <- readRDS("temp/matches_hills_yem_cam.rds")
+
+matches <- left_join(matches, select(hills_pre_match, voter_id, first_tr_year),
+                     by = c("group" = "voter_id", "first_tr_year")) %>% 
+  mutate(fd = first_tr_year,
+         first_tr_year = ifelse(first_tr_year == 1, "2014-11-04",
+                                ifelse(first_tr_year == 2, "2016-11-08",
+                                       ifelse(first_tr_year == 3, "2018-11-06", "XX"))),
+         first_tr_year = as.Date(first_tr_year))
+
+hist <- readRDS("C:/Users/morrisk/Desktop/full_raw_coded_hills_w_bgs.rds") %>%
+  select(voter_id, starts_with("v1"), v08) %>%
+  pivot_longer(!starts_with("vo"), names_to = "year", values_to = "to")
+
+elec_dates <- fread("raw_data/election_dates.csv")
+
+hist <- left_join(hist, elec_dates) %>% 
+  select(-year) %>% 
+  rename(year = date) %>% 
+  mutate(year = as.Date(year, "%m/%d/%Y"))
+
+
+matches <- left_join(matches, hist %>% 
+                       filter(year(year) %% 2 == 0), by = c("voter" = "voter_id"))
+
+periods <- fread("raw_data/period_lu.csv") %>% 
+  mutate_at(vars(first_tr_year, year), as.Date, "%m/%d/%Y")
+
+matches <- left_join(matches, periods) %>% 
+  filter(period %in% c(-2.5, -1.5, -.5, .5, 1.5))
+
+matches <- left_join(matches,
+                     hills_pre_match %>%
+                       select(-GEOID, -amount_paid, -last_date),
+                     by = c("voter" = "voter_id", "fd" = "first_tr_year"))
+
+matches <- left_join(matches,
+                     hills_pre_match %>%
+                       select(voter_id, amount_paid, last_date, first_tr_year, black_t = black,
+                              dem_t = dem),
+                     by = c("group" = "voter_id", "fd" = "first_tr_year")) %>% 
+  mutate(post = period >= 0.5,
+         treated = voter == group)
+
+cleanup("matches")
+gc()
+
+##########################################################
[…]

### 2022-02-14 code/hills/cam/gm.R

@@ -12,7 +12,19 @@ require(snow)
 require(parallel)
 
 
-hills_pre_match <- readRDS("temp/hills_pre_match.rds")
+Sys.info()
+
+NodeFile = Sys.getenv("MY_HOSTFILE")
+
+print(NodeFile)
+
+readLines(NodeFile)
+
+cl<-makeCluster(c(readLines(NodeFile)), type="SOCK")
+cl
+
+
+hills_pre_match <- readRDS("temp/hills_pre_match_cam.rds")
 
 ############## 2014
 
@@ -75,53 +87,20 @@ hills18 <- bind_rows(hills18_t, hills18_c) %>%
 ###########################################
 pre <- bind_rows(hills14, hills16, hills18)
 
-saveRDS(pre, "temp/real_pre_match_hills.rds")
+samp <- pre %>% 
+  group_by(treated, first_tr_year) %>% 
+  sample_frac(0.05) %>% 
+  ungroup()
 
-ids <- pre %>%
-  mutate(id = row_number()) %>%
-  select(id, voter_id, first_tr_year)
-
-X <- pre %>%
+match_data <- samp %>% 
   select(-voter_id, -treated, -GEOID, -amount_paid, -last_date,
          -v08, -v16, -v10, -reg_date) %>% 
   mutate_at(vars(white, black, latino, asian, male, dem, rep, v1, v2, v3, paid), ~ ifelse(. == T, 1, 0)) %>% 
   select(first_tr_year, paid, civil, tampa_pd, v1, v2, v3, everything())
 
-genout <- readRDS("temp/genout_hills_yem.rds")
+genout <- GenMatch(Tr = samp$treated, X = match_data, replace = T, cluster = cl, pop.size = 1000,
+                   exact = c(rep(T, 7), rep(F, 14)))
+
+saveRDS(genout, "temp/genout_hills_yem_cam.rds")
 
 
-mout <- Matchby(Tr = pre$treated, X = X,
-                by = c(X$first_tr_year,
-                       X$white,
-                       X$black,
-                       X$latino,
-                       X$asian,
-                       X$male,
-                       X$dem,
-                       X$rep), estimand = "ATT", Weight.matrix = genout, M = 1,
-                exact = c(rep(T, 7), rep(F, 14)), ties = T)
-
-
-
-save(mout, file = "./temp/mout_hills_y.RData")
-
-load("temp/mout_hills_y.RData")
-
-matches <- data.table(voter = c(mout$index.control,
[…]

### 2022-02-14 code/hills/cam/process_cam.R

@@ -1,0 +1,249 @@
+hills_stops <- rbindlist(lapply(c(2003:2021), function(l){
+  print(l)
+  if(l != "J"){
+    if(!(file.exists(paste0("raw_data/hills_stops/civil_stops_", l, ".csv")))){
+      download.file(paste0("https://publicrec.hillsclerk.com/Traffic/Civil_Traffic_Name_Index_files/Civil_Traffic_Name_Index_", l, ".csv"),
+                    paste0("raw_data/hills_stops/civil_stops_", l, ".csv"))
+    }
+    
+    ja <- fread(paste0("raw_data/hills_stops/civil_stops_", l, ".csv"))
+    
+    colnames(ja) <- clean_names(ja)
+    
+    ja <- ja %>%
+      filter(grepl("cam", tolower(statute_description))) %>%
+      select(last_name, first_name, middle_name,
+             date_of_birth,
+             street = address_line_1,
+             city,
+             state,
+             zip = zip_code,
+             offense_date,
+             amount_paid,
+             law_enf_agency_name) %>%
+      mutate(civil = 1,
+             tampa_pd = grepl("tampa police", tolower(law_enf_agency_name)),
+             tampa_pd = ifelse(tampa_pd, T, law_enf_agency_name == "TPD")) %>%
+      select(-law_enf_agency_name)
+    
+    return(ja)
+  }
+}))
+
+hills_stops <- hills_stops %>%
+  mutate(amount_paid = ifelse(is.na(amount_paid), 0, amount_paid)) %>%
+  mutate(offense_date = as.Date(offense_date, "%m/%d/%Y"),
+         date_of_birth = as.Date(date_of_birth, "%m/%d/%Y")) %>%
+  mutate_at(vars(first_name,
+                 last_name), ~ gsub("[[:punct:]]| ", "", ifelse(. == "", NA, toupper(.))))
+
+saveRDS(hills_stops, "temp/hills_stops_cam.rds")
+
+hills_stops <- readRDS("temp/hills_stops_cam.rds")
+
+#########
+
+pre12 <- filter(hills_stops, offense_date <= "2012-11-06")[,
+                                                           .(stop_count = .N),
+                                                           .(first_name, last_name, date_of_birth, offense_date)]  # using data.table syntax for speed
+
+pre12 <-  pre12[,
+                .(stop_count = .N),
+                .(first_name, last_name, date_of_birth)]  # using data.table syntax for speed
+
[…]

### 2022-02-14 code/process14.R

@@ -12,17 +12,17 @@ for(f in files){
   }
   if(!file.exists(paste0("temp/", state, "_to_14_block.rds"))){
     l <- list.files(f2, full.names = T, pattern = "*.tab")
-    k <- read.csv.sql(l, sep = "\t",
-                      sql = "select LALVOTERID, Voters_FIPS,
-                             Residence_Addresses_AddressLine, 
-                             Residence_Addresses_ExtraAddressLine, 
-                             Residence_Addresses_City, 
-                             Residence_Addresses_State,
-                             Residence_Addresses_CensusTract,
-                             Residence_Addresses_CensusBlockGroup,
-                             Residence_Addresses_CensusBlock,
-                             EthnicGroups_EthnicGroup1Desc,
-                             [General_2014.11.04] from file") %>%
+    k <- fread(l, sep = "\t",
+                      select = c("LALVOTERID", "Voters_FIPS",
+                             "Residence_Addresses_AddressLine", 
+                             "Residence_Addresses_ExtraAddressLine", 
+                             "Residence_Addresses_City", 
+                             "Residence_Addresses_State",
+                             "Residence_Addresses_CensusTract",
+                             "Residence_Addresses_CensusBlockGroup",
+                             "Residence_Addresses_CensusBlock",
+                             "EthnicGroups_EthnicGroup1Desc",
+                             "General_2014-11-04")) %>%
       mutate(state = state)
     
     saveRDS(filter(k,
@@ -41,7 +41,7 @@ for(f in files){
 ##############################
 files <- list.files("temp", pattern = "*to_14_no_block.rds", full.names = T)
 
-db18 <- dbConnect(SQLite(), "E:/national_file.db")
+db18 <- dbConnect(SQLite(), "D:/national_file.db")
 
 for(f in files){
   s <- substring(f, 6, 7)

### 2022-04-19 markdown/draft_paper.Rmd
submissions

@@
 ---
-title: "Ticketing and Turnout: How Policing for Profit Shapes Democratic Participation"
+title: "Ticketing and Turnout: The Participatory Consequences of Low-Level Police Contact"
 
-author:
-- Jonathan Ben-Menachem^[PhD Student, Columbia University, Department of Sociology (jb4487@columbia.edu)]
-- Kevin Morris^[PhD Student, CUNY Graduate Center, Department of Sociology (kmorris@gradcenter.cuny.edu)]
+# author:
+# - Jonathan Ben-Menachem^[PhD Student, Columbia University, Department of Sociology (jb4487@columbia.edu)]
+# - Kevin Morris^[PhD Student, CUNY Graduate Center, Department of Sociology (kmorris@gradcenter.cuny.edu)]
+# thanks: Earlier versions of this work were presented at the 2021 American Sociological Association Annual Meeting, the 2021 American Political Science Association Annual Meeting, and the Justice Lab at Columbia University.
+We would like to thank Bruce Western, Joshua Whitford,  Gerard Torrats-Espinosa, Brittany Friedman, Brendan McQuade, Flavien Ganter, Hannah Pullen-Blasnik, Tim Ittner, LeShae Henderson, and Van Tran for their engagement with our paper in its earliest stages.
+Special thanks to Sam Donahue for identifying the Tampa dataset that became the core of our analysis and eyeballing many, many iterations of analysis results.
+And finally, we would like to thank Hannah Walker for deep, charitable feedback that pushed us not to undersell our own contribution
 date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
 abstract: |
-  The American criminal legal system is an important site of political socialization: sociologists show how the alienating effect of criminalization pushes people away from public institutions, and political scientists have measured the effects of policing and incarceration on political participation.
-Despite this burgeoning literature, no research has directly investigated how police ticketing practices affect political participation.
-We use three approaches to answer this question: we leverage individual-level administrative ticketing data from Hillsborough County, Florida between 2010 and 2020, a city-level analysis using Census of Governments data and the national voter file, and national survey data.
-We use a genetic matching algorithm and difference-in-differences to estimate that being ticketed decreases an individual’s likelihood of voting in federal elections by 1.7 percentage points, but depressive effects are smaller for Black residents.
-Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 was associated with a roughly 0.04 percentage point turnout decrease but was not associated with any change in Black turnout.
-The survey data show that Black people who report that they or a family member were recently stopped by police are more likely to vote than those who reported no such contact.
+  The American criminal legal system is an important site of political socialization: scholars have shown that criminal legal contact reduces turnout, and that criminalization pushes people away from public institutions more broadly.
+Despite this burgeoning literature, few analyses directly investigate the causal effect of *lower-level* police contact on voter turnout.
+We use two approaches to do so: we leverage both individual-level administrative ticketing data from Hillsborough County, Florida, and responses to the American National Election Studies.
+We estimate that a traffic stop decreases an individual’s likelihood of voting by 1.7 percentage points, but depressive effects are smaller for Black residents.
+The survey data, however, show that Black people who report that they or a family member were recently stopped by police are *more* likely to vote than those who reported no such contact.
+Taken together, our results indicate that low-level contact with police may have participatory consequences.
 
@@
   |
-  **Keywords**: voting, monetary sanctions, race, punishment, political participation
+  **Keywords**: voting, policing, race, punishment, political participation
 ---
@@
 
-Work exploring how criminalization directly and indirectly influences political participation has exploded in recent years following path-breaking work from political sociologists Chris Uggen and Jeff Manza [@Uggen2002; @Manza2006].
+Although scholars have examined the collateral consequences of this increased reliance on fines and fees [@Sances2017; @Pacewicz2020], comparatively few have explored the moment during which such revenue-raising actually occurs: namely, in the individual interactions between residents and the police via the issuance of a ticket.
+This “moment” of low-level contact has also been relatively understudied by scholars investigating the participatory consequences of contact with the criminal legal system.
+Work exploring how criminalization directly and indirectly influences political participation has exploded in recent years.
 Scholars have found that criminal legal contact (i.e.
@@
 While ticketing involves potentially negative interactions with the state, it does not necessarily carry the disruptive consequences of a felony conviction and might thus politicize Americans in unique ways.
-Building on recent theoretical work from @Walker2020a and an analysis of the historical context of fees and fines collections in the United States, this paper is the first to explicitly theorize how local ticketing practices shape the political socialization of ticketed individuals.
-We argue that ticketing depresses voter turnout overall, but also catalyzes a “linked fate” political analysis among Black voters that either causes increased turnout or mitigates the turnout reductions observed among non-Black individuals.
+Building on recent theoretical work from @Walker2020a, this paper theorizes how local police practices affect voting behavior among ticketed individuals and provides precisely estimated evidence of a causal effect.
 
-Additionally, our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
+Our project represents the first use of individual-level administrative data to identify the causal effect of traffic stops on voter behavior.
 The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures political participation.
-Past work looking at the individual-level effects of low-level contact has relied entirely on survey or qualitative data [e.g.
+Past work looking at the individual-level effects of low-level contact has relied on survey or qualitative data [e.g.
 @Walker2014; @Weaver2010].
@@
 As Weaver and Lerman [-@Weaver2010: 821] note, it may also introduce measurement bias.
-Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to police ticketing.
-The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of a quarter-million individuals ticketed over a 6 year period---a far larger pool than even the most robust surveys.
+Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to a traffic stop.
+The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of a quarter-million individuals stopped over a 6 year period---a far larger pool than even the most robust surveys.
 
-We use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were ticketed between the 2012 and 2018 elections.
-By matching individual voters who were ticketed to similar voters who were ticketed at later points and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout.
-We find that being ticketed reduces the chance that an individual will turn out in the subsequent election, but that this effect is smaller for Black voters.
+We use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were stopped between the 2012 and 2018 elections.
+By matching individual voters who were stopped to similar voters who were stopped at later points and running a difference-in-differences model, we estimate the causal effect of these stops on turnout.
+This borrows from the logic of regression discontinuities in time: conditional on observable characteristics *and* unobservable factors associated with being ticketed, the timing of the ticket on either side of election day is essentially as-if random.
+We find that being stopped reduces the chance that an individual will turn out in the subsequent election, but that this effect is smaller for Black voters.
 
-To test the generalizability of our findings in Hillsborough County, we leverage two different datasets that are national in scope.
-First, we join fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for thousands of municipalities around the country.
-While we find that increased fees and fines likely cause lower turnout among non-Black Americans, we find no effect of fees and fines on Black turnout.
+To test the generalizability of our findings in Hillsborough County, we conduct a novel analysis of 2020 national survey data regarding voters’ experience with police stops.
+We find that Black respondents who reported personal or proximal experience with police stops in the last 12 months are more likely to vote than Black people who did not, while we find no statistically significant relationship between stops and voting among non-Black respondents.
+While the survey data present some drawbacks relative to the individual-level administrative data, their national scope provides helpful corroboration for the unique turnout effects of traffic stops for Black Americans observed in Hillsborough County.
 
-Second, we conduct a novel analysis of 2020 national survey data regarding voters’ experience with police stops.
-We find that Black respondents who reported personal or proximal experience with police stops in the last 12 months are more likely to vote than Black people who did not, while we find no statistically significant relationship between stops and voting among non-Black respondents.
-While both the municipal-level and survey data present some drawbacks relative to the individual-level administrative data, their national scope provides helpful corroboration for the unique turnout effects of tickets for Black Americans observed in Hillsborough County.
+We demonstrate that police ticketing practices---the most widespread form of police contact in America---substantially reduce the turnout of non-Black American voters, but have a unique effect on Black voter turnout.
+Our findings complicate existing theories of how criminalization politically socializes Americans, and Black Americans in particular [@Weaver2010].
+Additionally, while many forms of criminalization have been found to contribute to a well-documented subjective experience of alienation or group-level exclusion among Black Americans [@Bell2017; @Stuart2016; @Desmond2016; @Zoorob2020; @Desmond2020; @Ang2021], our contribution emphasizes the need for further research regarding how different forms of criminalization affect group-level perceptions of government and resultant political behaviors.
+Our findings are relevant for interdisciplinary scholars of crime, race, politics, municipal finance, and policing.
 
-We demonstrate that police ticketing practices---the most widespread form of police contact in America---substantially reduce the turnout of non-Black American voters, but can mobilize Black voters.
-Our findings complicate existing theories of how criminalization politically socializes Americans, and Black Americans in particular [@Weaver2010].
-Additionally, while all forms of criminalization likely contribute to a subjective experience of alienation or group-level exclusion among Black Americans that is well-documented in sociological scholarship [@Bell2017; @Desmond2016], our contribution emphasizes the need for further research regarding how different forms of criminalization affect group-level perceptions of government and resultant political behaviors.
-Accordingly, we propose a new theory explaining how ticketing may uniquely catalyze Black political participation.
-Our findings are relevant for interdisciplinary scholars of crime, race, politics, political economy, social movements, and policing.
+# Criminal Legal System and Citizen Identity {-}
 
-# Literature Review {-}
+In recent years, scholars have paid more attention to the political implications of the American criminal legal system.
+Evolving in part out of a literature focused on street-level bureaucrats, researchers across the social sciences are asking how daily interactions with agents of the carceral state shape Americans’ relationships to themselves, their communities, and their state.
+As @Soss2017 argues, this “second face” of the state---“the activities of governing institutions and officials that exercise social control and encompass various modes of coercion, containment, repression, surveillance, regulation, predation, discipline, and violence” (567)---is the primary way through which many class-race subjugated communities develop their political knowledge.
+“[I]nterviewees have looked, not to City Hall, Congress, or political parties,” they write, “but rather to their direct experiences with police, jails and prisons, welfare offices, courts, and reentry agencies as they sought to ground their explanations of how government works, what political life is like for them, and how they understand their own political identities” [@Soss2017, 574].
 
-An emerging political science literature directly investigates the relationship between criminalization and political behavior.
-Additionally, sociologists have incorporated contemporary fines and fees practices into a broader empirical-historical theory of racialized punishment policy [@Harris2010; @Friedman2020].
-
-In order to theorize how fines and fees affect political behavior, we consider how criminalization directly shapes the electorate; the existing scholarly understanding of the influence of criminalization on political socialization; and how contemporary ticketing practices are tied to a longer legacy of racist exploitation and thus ripe for political mobilization around narratives of racial injustice.
-
-## Criminalization and political socialization {-}
-
-The American criminal legal system directly shapes the American electorate and excludes voters.
-Today, more than five million Americans are legally barred from voting due to a felony conviction, and one in every sixteen Black Americans of voting age is disenfranchised [@Uggen2020].
-Notably, fines and fees legally disenfranchise Americans as well: 48 states and the District of Columbia authorize some form of wealth-based penal disenfranchisement [@Colgan2019].
-Many states require payment of fees as a condition of criminal legal supervision or the payment of all legal financial obligations as a condition of completing a sentence, and failure to comply with supervision or sentence completion conditions can be a barrier to voting rights restoration.
-
-Beyond de jure disenfranchisement, the spatial and racial concentration of criminalization influences affected communities’ perceptions of government.
-Monica Bell calls this process “legal estrangement,” a conceptual framework meant to capture those perceptions and cultural attitudes (“legal cynicism”) as well as the historical-structural conditions that produced them [@Bell2017].
-Research on legal cynicism has found that public perceptions of abusive police practices can reduce willingness to report crimes or cooperate with law enforcement [@Desmond2016; @Tyler2014].
-In short, the “hidden curriculum” [@Justice2014; @Meares2017] of the criminal legal system teaches Americans about their identities as citizens---even parts of their identities that have little to do with policing or incarceration.
+Recent work has explored the production of this political knowledge in increasingly sophisticated ways, using both qualitative and quantitative approaches.
+@Lerman2014’s pathbreaking book *Arresting Citizenship* set the table for future research.
+Their project combined extensive interviews of individuals living in areas closely monitored by the criminal legal system with novel survey data to probe the political consequences of what they term the “carceral state.” Their work indicates that citizens nearly uniformly react negatively to police and carceral supervision---from low-level interactions to lengthy periods of incarceration, Americans subjected to the second face of the state apparently withdraw from political participation.
+They find that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) [@Weaver2010].
 New evidence related to ticketing and legal estrangement has recently emerged: in a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government compared to residents who were not ticketed [@CarpenterII2019].
 
-Because police are the most visible agents of the state, perceptions of unfairness in policing can translate to a recognition of actual group-level structural exclusion from public institutions [@Bell2017].
-Soss and Weaver explain how criminal legal contact shapes perceptions of government and political participation: “interviewees have looked, not to City Hall, Congress, or political parties, but rather to their direct experiences with police, jails and prisons, welfare offices, courts, and reentry agencies as they sought to ground their explanations of how government works, what political life is like for them, and how they understand their own political identities” [@Soss2017: 574].
-
-Sarah Brayne found related results in her analysis of survey data.
-As the intensity of criminal legal contact escalates (i.e.
-stopped, arrested, convicted), people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions [@Brayne2014].
+Sarah Brayne [-@Brayne2014] found related results in her analysis of survey data.
+As the intensity of criminal legal contact escalates , people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions.
 She calls this phenomenon “system avoidance,” and while her analysis did not specifically assess voting behavior, her findings demonstrate how criminal legal contact can discourage Americans’ participation in public institutions as well as how the effect may vary alongside the intensity of criminal legal intervention.
 Similarly, @Remster2018a finds that men who return home from prison are more likely to avoid contact with their childrens’ schools.
-Vesla Weaver and colleagues helpfully describe this form of self-preserving withdrawal from public institutions as a “strategic retreat” [@Weaver2020].
+Vesla Weaver and colleagues describe this form of self-preserving withdrawal from public institutions as a “strategic retreat” [@Weaver2020].
 
-In addition to influencing perceptions of government and participation in public institutions, recent scholarship indicates that criminalization influences political behavior.
-Using existing national survey data and extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) [@Weaver2010].
-Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a “linked fate” where “one’s individual opportunities are linked to the entire racial group” [@Lerman2014: 197].
-Their interview data lead them to conclude that while criminal legal contact does increase perceptions of linked fate among Black respondents, “a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing.” Interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation [@Lerman2014].
+These findings can be situated in a process that sociologist Monica Bell calls “legal estrangement,” which captures those perceptions and cultural attitudes (“legal cynicism”) as well as the historical-structural conditions that produced them [@Bell2017].
+Research on legal cynicism has found that public perceptions of abusive police practices can reduce willingness to report crimes or cooperate with law enforcement [@Tyler2014].
+The “hidden curriculum” [@Justice2014; @Meares2017] of the criminal legal system teaches Americans about their identities as citizens---even parts of their identities that have little to do with policing or incarceration.
 
-Lerman and Weaver’s findings have been corroborated using administrative data: Ariel White found that short jail sentences in Harris County, Texas reduced Black defendant turnout in subsequent elections by 13 percentage points---but the effect on white turnout was not statistically significant [@White2019].
-Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level [@Burch2014].
-These effects can also extend to family members, and the political consequences can be quite durable [@Morris2021].
+# Administrative Data and the Causal Effects of Criminalization {-}
 
-Although most work documents how contact with the criminal legal system causes strategic retreat, recent work from Hannah Walker [-@Walker2020; -@Walker2020a] complicates this narrative.
-She argues that when Black Americans understand their contact with the criminal legal system in the context of a narrative of racial injustice, such contact can actually mobilize.
-She explains: “experiences with punitive policies are subject to interpretation and, when understood through narratives of injustice, lead to wholly different participation outcomes than we usually predict” [@Walker2020: 132].
+Many scholars have turned to administrative data in recent years to explore the actual effects of contact with the criminal legal system on political participation in the voting booth.
+To be sure, administrative data have limitations: they are not ideally suited to probe the psychological, social, relational, and other mechanisms leading some citizens to vote and others to abstain.
+These limitations, however, are balanced by offering researchers precise estimates of actual---and not just reported---turnout.
+
+Traci Burch [-@Burch2011] was among the earliest scholars to match voter-file records with records detailing citizens’ contact with the criminal legal system.
+Her work complicated a previously dominant theory postulating that the turnout and party registration of formerly incarcerated individuals was largely driven by their sociodemographic characteristics but not their formal conviction or supervision [see, for instance, @Uggen2002].
+She argues that citizens who are convicted of felony offenses are less likely to vote, and less likely to register with a party, than citizens with similar sociodemographic characteristics without such a conviction.
+
+Other scholars have similarly matched corrections records with registered voter files to explore the effect of contact with the second face of the state.
+@White2019a finds that short periods of incarceration reduce Black, but not white, turnout.
+@Gerber2017 similarly finds relatively small effects of incarceration on turnout.
+Meredith and Morse [-@Meredith2014; -@Meredith2015] and @Gerber2015 explore the turnout effect of notifying formerly incarcerated citizens of the legal restoration of their voting rights, with mixed results, while @Morris2021a shows that restoring voting rights to individuals while they are still on parole increases post-supervision turnout.
+Other work has explored the “spillover” effects of such contact, finding that the political behavior of family members [@White2019] and neighbors [@Burch2014; @Morris2020] can be influenced by indirect contact with incarceration.
+@Morris2021 argues that these effects are durable, showing that citizens whose household members had been to prison were not disproportionately mobilized by a ballot initiative promising to end felony disenfranchisement.
+
+This burgeoning literature using administrative data has given scholars far greater insight into the participatory consequences of American incarceration.
+It is, however, virtually silent on the effects of *lower level* contact with the criminal legal system.
+Far more Americans have low-level contact with the police than will ever spend a night behind bars: just under 20 million Americans experience a traffic stop each year, whereas approximately five million Americans are arrested and jailed each year [@Harrell2020; @Jones2019].
+Despite the fact that so many more citizens are subjected to traffic stops, we know comparatively little about its political ramifications, a lack that is particularly glaring given how much we have learned in recent years about higher-level contact.
+
+The one project that has used administrative data to explore the political implications of low-level police contact is @Laniyonu2019, which explores the effects of the Stop, Question, and Frisk (SQF) program in New York City.
+@Laniyonu2019’s causal estimates rely on a cross-sectional matching model to compare voter turnout in precincts with *high* SQF activity to turnout in precincts with similar sociodemographic characteristics but *low* SQF activity, supplemented with cross-sectional analyses of all precincts in the city.
+His results paint a complicated picture: his causal estimates find that high levels of SQF increased turnout in the 2008 presidential election, but decreased it in the 2010 midterms.
+While @Laniyonu2019 marks an important step forward in the investigation of the consequences of policing for political behavior, it faces certain data and methodological limitations.
+Because the SQF data does not include identifying information about the individuals stopped, he cannot explore the turnout of New Yorkers who were actually subjected to SQF.
+Thus, as he notes in the conclusion, “the ability of the analysis to make causal claims is limited” (554) by the cross-sectional matching approach.
+
+In this project, we seek to extend our understanding of the political consequences of routine contact with the state’s second face.
+Combining an individual-level administrative panel dataset with national survey data gives us new insight into how traffic stops can shape citizens’ engagement with their democracy.
+
+# How Police Stops Might Structure Turnout {-}
+
+Much of the existing work on the turnout consequences of the criminal legal system points to a process of political learning or political socialization.
+@Lerman2014 finds that individuals in highly surveilled neighborhoods learn that the government does not care about them, and is uninterested in soliciting their participation.
+They note that more than half of individuals stopped by the police report agreeing with the statement “the leaders in government care very little about people like me,” compared with just a third of respondents with no police contact (150).
+The numbers, however, were far higher for individuals convicted of a crime, of whom three-quarters agreed with the statement.
+Learning about the criminal legal system takes place over a long period of time.
+Could isolated police stops that neither require sustained contact with the criminal legal system nor (generally) impose punishments as severe as incarceration politically socialize Americans to the same degree as incarceration?
+
+On one hand, it might seem unlikely that a single stop would produce much new knowledge about the state.
+For many Americans, a traffic stop amounts to little more than a slap on the wrist.
+To be sure, fines and fees can wreak havoc on the lives of some drivers.
+If a ticket leads to a suspended driver’s license, the initial stop can snowball into a much bigger life event that could jeopardize employment, or lead to shorter stints of incarceration for individuals apprehended driving on a suspended license.
+Searches conducted during traffic stops may also lead to arrest or incarceration if a police officer finds contraband in the vehicle.
+These comparatively less frequent cases might have consequences more akin to those associated with a brief period of incarceration that can also threaten employment.
+Nevertheless, the average traffic stop is certainly less disruptive than the average period of incarceration, perhaps producing less political knowledge and therefore impacting turnout less.
+
+On the other hand, a far larger set of Americans are stopped by the police than sent to jail or prison each year.
+According to the American National Election Study, a nationally-representative survey we use later in this study, the incomes and education levels for individuals stopped by the police are meaningfully higher than for individuals who report ever having been arrested.
+Motorists stopped by police are apparently systematically different compared to people who experience incarceration.
+Traffic stops might thus be the primary way some of these Americans learn about the criminal legal system.
+If these Americans have not already “learned” about the system from their neighborhoods or family members, the political consequences of such newly gleaned knowledge might be large.
+
+Traffic stops might provide early insights about the criminal legal system even for Americans who live in more heavily-policed areas.
+As @Gerber2017 notes in their study arguing that the participatory consequences of incarceration might be small, incarceration “is an outcome that often follows a long series of interactions with the criminal justice system” (1145).
+In other words, much of what the criminal legal system “teaches” might have already been learned by the time an individual is sent to prison.
+Someone who is stopped by the police, however, might have had fewer negative interactions with the state.
+Put differently, stopped individuals might have more to learn than incarcerated individuals with a long history of police contact, resulting in higher turnout effects.
+
+# Potential for Racially Disparate Effects {-}
+
+The potential for more “learning” from a police stop seems especially salient for Black Americans, particularly in recent years.
+National news over the 2010s was filled with the names of Black Americans who were killed during routine police stops.
+The Black Lives Matter movement gained national attention in the aftermath of the Ferguson uprising, an uprising sparked by the police killing of Michael Brown but also fueled by that city’s racial discriminatory ticketing practices.
+In the fall of 2021, *The New York Times* ran an extensive report exploring police killings that occur during traffic stops, providing more proof of their racially disparate nature [@Levenson2021].
+
+We expect that the participatory consequences of such a stop will be different for Black than non-Black Americans.
+First, traffic stops differ in meaningful ways for Black and non-Black Americans.
+As @Baumgartner2018 notes, Black Americans are more likely than whites to receive both “light” (i.e., a warning without a ticked) *and* “severe” (i.e., arrest) outcomes from a traffic stop.
+Although this may seem paradoxical at first, the authors explain: “while many might rejoice in getting a warning rather than a ticket, the racial differences consistently apparent in the data suggest another interpretation for black drivers: even the officer recognized that there was no infraction” [88].
+Black drivers are also more likely to be searched and arrested, but less likely to be found with contraband [@Baumgartner2018].
+Similarly, @Epp2014 argues that traffic stops are particularly instructive for Black Americans, as pretextual traffic stops politically socialize Black voters to the specific context of discriminatory police ticketing.
+
+The politicization of a police stop can occur differently for Black Americans through other avenues as well.
+The BLM movement has raised the salience of racially disparate policing across the country, as have the tragic stories of individuals like Philando Castile who was killed during a police stop.
+Routine interactions with the police are also more likely to turn deadly for Black Americans than for others [@Levenson2021].
+Thus, even if an individual police stop for a Black American is relatively unremarkable on its own, the background context that the interaction *could* have turned deadly is likely to result in some level of trauma for Black drivers.
+Recent work from Hannah Walker [-@Walker2020; -@Walker2020a] argues that this could lead to a *mobilizing* effect, if stopped drivers understand their contact with the criminal legal system in the context of a narrative of racial injustice, such contact can actually mobilize.
+She explains: “experiences with punitive policies are subject to interpretation and, when understood through narratives of injustice, lead to wholly different participation outcomes than we usually predict” [@Walker2020, 132].
 While she finds that this sense of injustice is especially likely to increase political participation in non-voting ways (such as attending a protest or signing a petition), the logic could extend to electoral participation as well given a relevant electoral context, strong injustice narrative, or relatively weak contact with the criminal legal system.
-Findings presented in @Laniyonu2019 provide support for this concept: concentrated Stop, Question, and Frisk (SQF) policing in New York City neighborhoods was associated with reduced turnout in federal midterm elections but increased turnout in presidential and mayoral primary elections.
-Laniyonu also uncovered an association regarding candidate choice—he demonstrates higher turnout for a candidate who opposed SQF policing and lower turnout for a candidate who supported it.
-In other words, low-level police contact mobilized voters to participate in a local election (which could plausibly affect police practices).
 
-Despite the growing body of high-quality scholarship on the democratic implications of the American criminal legal system, we still know remarkably little about the effects of the most routine sort of contact---police stops and tickets that do not result in an arrest.
+Given that police stops are more likely to be traumatic for Black motorists (because traffic stops come with a threat of escalation into racialized police violence, because they received harsher punishments, *or* because the stop itself was discriminatory) *and* that there exists a framework available for translating negative experiences with the criminal legal system into political action, we expect police stops to have unique participatory consequences for Black Americans.
 
-## Race and fines and fees practices {-}
-
-Fines and fees are situated in a distinct historical legacy of racist exploitation that may uniquely facilitate a collective “sense of injustice” among Black Americans---the sort of collective perception that @Walker2020a argues could prove to be politically mobilizing.
-
-Cedric Robinson’s articulation of racial capitalism offers a useful theoretical framework for interpreting the trajectory of American anti-Black political economy [@Robinson2000].
-Brittany Friedman theorizes fines and fees as a “progression of racial capitalism penology,” emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices [@Friedman2020: 177].
-Robinson argues that European industrial capitalism continued a longer political-economic trend of differentiating racial groups in order to dispossess them and exploit their labor.
-
-Following the Civil War and the rise of global industrial capitalism, slave patrols were replaced by more formal police forces [@EqualJusticeInitiative2017; @Hinton2021].
-The implementation of the Black Codes, convict leasing, and sharecropping systems marked a transition to a new stage of racial capitalism, wherein criminalization provided an easily-exploited labor supply that offset costs that the state incurred by coercing their labor [@Lichtenstein1996; @Mancini1978].
-Contemporary fines and fees practices have been directly compared to sharecropping because both structures share “a long-term pattern of financial exploitation based on race… that limits the life-choices of the affected population” [@Blessett2016: 113].
-
-In the 20th century, residential segregation simultaneously fueled the racial wealth gap and ensured that criminalization was both spatially and racially concentrated [@Rothstein2017; @Hinton2021].
-At the level of federal policy, racial threat and whites’ attribution of criminality to Blackness [@Muhammad2010] prompted a shift from the War on Poverty to the War on Crime wherein Black communities’ demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration [@Hinton2017; @Vargas2017].
-
-The 2008 financial crisis solidified the connection between fiscal austerity and policing, prompting a decline in tax revenues that devastated state and local governments---but law enforcement agencies were largely spared from cuts.
-At the local level, this means that police budgets today constitute about thirty percent of city budgets nationwide, and cities where residents have lower median incomes dedicate a larger proportion of spending to policing [@Friedman2020].
-Similarly, municipalities where a larger share of the population is Black raise more fines and fees revenue per-capita than less-Black municipalities [@Sances2017; @UnitedStatesCommissiononCivilRights2017].
-Although major urban centers collect high dollar amounts of fines and fees, some of the most egregious ticketing practices measured on a per-capita basis are concentrated in suburbs or smaller cities with municipal courts---Ferguson being a prominent example [@UnitedStatesDepartmentofJusticeCivilRightsDivision2015; @Mughan2020].
-In municipalities with substantial Black populations, then, people who are most heavily affected by criminalization are expected to foot the bill for their own mistreatment.
-@Sances2017, however, finds that the discriminatory imposition of tickets can be mitigated by descriptive representation (i.e.
-Black elected officials): The positive association between cities’ reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator [@Sances2017].
-This result aligns with recent research demonstrating that states with more Black legislators spend less on corrections budgets; that racial disparities in arrests are reduced in municipalities represented by a majority-nonwhite city council; and that descriptive representation can reduce racial disparities in the criminal legal system  [@Butler2011; @Gunderson2020; @Eckhouse2016].
-It thus seems that the ballot box can be a site from which Black Americans can secure some protections against the most egregious forms of revenue extraction.
-
-Racial capitalist political economy imposes fiscal constraints regardless of city officials’ identities or intentions.
-In their study of fines and fees reliance in Chicago suburbs, Josh Pacewicz and John Robinson, III show how the racialization of municipal opportunity structures prevents majority-Black suburban governments from acquiring sufficient revenue from “good” sources such as sales taxes or property taxes, catalyzing a reliance on fines and fees to fund government services [@Pacewicz2020].
-Pacewicz and Robinson III note that racialized municipal opportunity structures are tied to the political-historical processes of neoliberalism and fiscal austerity, an observation that aligns with recent scholarship detailing the origins of fees paid by incarcerated people [@Kirk2020].
-
-Today, fines and fees primarily target Black Americans: traffic stops and searches disproportionately affect Black motorists nationwide [@Pierson2020], and a host of local analyses confirm the national finding [@Dunn2009; @Goncalves2020; @Mughan2020].
-In criminal court proceedings, Black defendants tend to face more severe monetary sanctions [@Edwards2020; @Harris2011], and a 2020 Federal Reserve survey found that five percent of white respondents reported “unpaid legal expenses, fines, or court costs,” whereas twelve percent of Black respondents reported such debt [@BoardofGovernorsoftheFederalReserveSystem2020].
-
-Research regarding police stops and searches in response to local fiscal crises shows how decreasing local revenues affect racist police practices.
-One study of all U.S.
-city governments found that local fiscal stress was related to increased “revenue-generating arrests” (e.g.
-arrests involving civil asset forfeiture) and that Black and Hispanic people were arrested at higher rates [@Makowsky2009].
-A study of four million North Carolina traffic stops found that fiscal stress caused a decrease in the probability of white drivers being searched, but no decrease for Black drivers [@Shoub2020].
-This suggests that higher reliance on fines and fees results in government officials and police targeting individuals who hold less political power---whether those individuals are out-of-state motorists or members of local marginalized communities [@Makowsky2009].
-
-# Theory {-}
-
-As the preceding sections make clear, past work on the political ramifications of criminal legal contact has largely determined that such contact is demobilizing.
-Scholars have argued that all contact with the criminal legal system causes political withdrawal, and that the severity of the withdrawal varies according to the intensity of the contact.
-This finding may not hold true for lower-level criminal legal contact, however.
-We argue that police ticketing may be an exception to this rule for two reasons: (1) police stops are far less disruptive to Americans’ lives than arrests or periods of incarceration, and (2), the injustice narrative framework [@Walker2020a] indicates that the explicit politicization of police stops by the Black Lives Matter movement in recent years should be mobilizing for Black Americans.
-
-Receiving a ticket is a substantively different experience than being arrested or incarcerated.
-People who have been convicted of a crime and incarcerated are relegated to an alternate political membership status that Reuben Jonathan Miller and Forrest Stuart call “carceral citizenship,” subjecting them to forms of supervision and sanction “that are otherwise unavailable to [people] who have not been accused of a crime” [@Miller2017: 536].
-The politically discouraging effects of criminalization are even stronger for people who are convicted of felonies, who lose their right to vote in all but two U.S.
-states.
-This “civil death” [@Ewald2002; @Miller2012] explicitly removes Americans from the electorate; the felony conviction becomes “a durable constraint and marker of their citizenship” [@Lerman2014: 133].
-The experience of formal legal exclusion from voting forms a powerful piece of the “hidden curriculum” [@Meares2017] that teaches convicted individuals about their identities as citizens.
-Finally, the financial and social costs following a period of incarceration [@Bushway2007] can make it less likely that citizens invest the time and energy into registering to vote, learning where their polling place is, and determining which candidates they support.
-
-While tickets can lead to driver’s license suspensions or, in a smaller subset of cases, nonpayment incarceration, tickets are generally far less disruptive than criminal convictions and prison terms.
-Ticketed drivers are not disenfranchised, and they are not subject to the same forms of supervision and sanction that affect people with criminal convictions.
-Accordingly, individuals who have *not* been subjected to such intense supervision may be less likely to avoid state institutions compared to formerly incarcerated people pursuing a “strategic retreat.” [@Brayne2014], In short, if higher-intensity contact with the criminal legal system leads to political withdrawal because of carceral control, surveillance, and resultant lessons about citizenship, these same arguments are unlikely to apply to ticketed individuals.
-
-This is not to say that ticketing should be considered completely distinct from more intense forms of criminalization, but rather that a ticketed individual has not yet been relegated to “carceral citizenship.” .
-Walker’s research gives us reason to believe that drivers who feel that they were unfairly targeted by the police---and link that unfair experience to broader social narratives---can be *mobilized* by that experience.
-Moreover, given political organizing in recent years specifically about the racial injustices of discriminatory traffic stops, this injustice narrative is likely particularly accessible---and mobilizing---for Black Americans.
-
-The rise of the Black Lives Matter movement in 2013 constitutes a significant development for the political socialization of Black Americans, and many early Black Lives Matter protests either occurred in municipalities with exploitative ticketing practices or directly followed traffic stops that escalated into police violence [@Holpuch2015; @LaFraniere2016].
-The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious.
-It is possible that Black Lives Matter facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis---the movement arose shortly after fines and fees became a more salient and widespread threat to Black Americans’ material security, and the BLM movement helped to publicize these disparities.
-The injustice narrative framework proposed by @Walker2020a explains how individuals connect their “micro” experience of criminal legal contact with the “macro” narrative of racially discriminatory policing.
-
-The financially exploitative nature of recent ticketing increases should be particularly fertile ground for robust injustice narratives.
-One Buffalo, New York resident who is a plaintiff in a lawsuit regarding racist ticketing practices told a local newspaper in 2019: “In my mind, they weren’t balancing the budgets for Black lives, but with Black lives” [@McLeod2019].
-The city created a new traffic violations agency in 2015, spurring its yearly ticketing numbers to jump from around 32,000 to over 52,000.
-
-We argue that many of the factors leading to withdrawal associated with higher-level criminal legal contact should not apply to police stops.
-At the same time, we expect that the national BLM movement should have encouraged Black Americans stopped by the police to connect their experience to macro-level trends, and that this should encourage political behaviors such as voting.
-Simply put, we expect that police stops are far less demobilizing than higher-level contact, and that they may in fact be mobilizing for Black Americans in an era of increased awareness of racially disparate policing practices.
+At the same time, the average Black American already knows far more about the criminal legal system due to the extreme racial disparities in policing and incarceration.
+As one 2015 study observed, 44% of Black women (and 32% of Black men) have a family member in prison.
+These numbers compare with just 12% and 6% for white women and men, respectively [@Lee2015].
+Black Americans’ disproportionate contact with the criminal legal system is a firmly established fact at this point.
+This greater baseline exposure could mean that Black Americans have less to “learn” from a marginal police stop, resulting in smaller turnout effects.
 
@@
 
-We leverage three distinct approaches to ask whether ticketing and police stops structure voter turnout, and whether these effects are unique for Black Americans.
-Our theoretical estimand [@Lundberg2021] is the effect of police ticketing on the political socialization of ticketed individuals, which we proxy using their voter turnout.
+We leverage two distinct approaches to ask whether police traffic stops affect voter turnout, and whether these effects are unique for Black Americans.
 
@@
 
-We include two supplementary analyses to test the generalizability of the results from Hillsborough County.
-First, we analyze change in municipal-level revenue from fees and fines and voter turnout, which allows us to expand our analysis outside of Hillsborough County to about nine thousand American municipalities.
-This test does not allow us to directly observe the causal mechanism we argue is at play (police stops influencing political socialization, which in turn drives individual voter turnout), and replaces individual ticketing events with less-precise budget data.
-Also, if interpreted in isolation, the municipal-level analysis would suffer from the ecological fallacy: it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
-
-Finally, data from the 2020 American National Election Studies allow us to observe how tickets and arrests differentially influence voting behavior at the individual level among a nationally representative sample, but survey data analysis is subject to the vulnerabilities detailed in our introduction (e.g.
+Data from the 2020 American National Election Studies allow us to observe how tickets and arrests differentially influence voting behavior at the individual level among a nationally representative sample, but survey data analysis is subject to the vulnerabilities detailed in our introduction (e.g.
 measurement bias).
@@
 
-Taken together, these approaches dramatically advance our understanding of the political consequences of the most routine types of contact with the criminal legal system.
+Taken together, these approaches advance our understanding of the political consequences of the most routine types of contact with the criminal legal system.
 
-## Individual-Level Causal Effects of Ticketing {-}
+## Individual-Level Causal Effects of Traffic Stops {-}
 
@@
 @Meredith2014 develops a test for assessing the prevalence of false-positives in administrative record matching.
-We present the results of that test in the Supplementary Information.
+We present the results of that test in section 1 of the Supplementary Information (SI).
 We likely have a false-positive match of around 0.03 percent, a figure we consider too low to impact our results meaningfully.
@@
 Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status [see @Nyhan2017].
-Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.^1^ We thus observe virtually all individuals who were registered to vote at any time during our period of study.
+Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.^[Because such frequent snapshots are not available from L2, we here use the registered voter file made freely available by the state of Florida.] We thus observe virtually all individuals who were registered to vote at any time during our period of study.
 Unique voter identification numbers allow us to avoid double-counting voters who are registered in multiple snapshots.
@@
 
-By matching the police stop and voter records, we identify all voters who were ticketed between the 2012 and 2020 general elections (voters stopped between 2018 and 2020 elections serve only as controls).
+By matching the police stop and voter records, we identify all voters who were stopped between the 2012 and 2020 general elections (voters stopped between 2018 and 2020 elections serve only as controls).
 We collect self-reported information regarding the race of each voter from Florida’s public voter file rather than the police stop data.
-Voters are considered “treated” in the general election following their ticket.
+Voters are considered “treated” in the general election following their stop.
 Treated voters are then matched to a control voter using a nearest-neighbor approach, with a genetic algorithm used to determine the best weight for each characteristic [@Sekhon2011].
@@
 Put differently, if a voter is stopped between 2012 and 2014, their control voter must be an individual stopped between the 2014 and 2016 elections.
-A voter cannot both be a treated and control voter for the same election; therefore, someone ticketed between the 2012 and 2014 elections and again between the 2014 and 2016 elections cannot serve as a control for anyone ticketed between 2012 and 2014.
-We limit the target population to voters who are ticketed at some point in order to account for unobserved characteristics that motivate people who are ticketed at some point to turn out at higher rates than people who are never ticketed.
+A voter cannot both be a treated and control voter for the same election; therefore, someone stopped between the 2012 and 2014 elections and again between the 2014 and 2016 elections cannot serve as a control for anyone stopped between 2012 and 2014.
+We limit the target population to voters who are stopped at some point in order to account for unobserved characteristics that motivate people who are stopped at some point to turn out at higher rates than people who are never stopped.
 
@@
 
-We assume that after controlling for observable characteristics, past turnout, *and* the unobservable characteristics associated with receiving a ticket, the timing of the ticket is effectively random.
-In short, any turnout difference between the treated voters and their controls is the causal effect of a police stop on turnout.
-Our overall turnout effects are robust to much weaker assumptions: in the Supplementary Information, we demonstrate that our overall turnout results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
+We assume that after controlling for observable characteristics, past turnout, *and* the unobservable characteristics associated with experiencing a traffic stop, the timing of the stop is effectively random.
+This is conceptually similar to the regression discontinuity in time framework, and we assume that any turnout difference between the treated voters and their controls is the causal effect of a police stop on turnout.
+Our overall turnout effects are robust to much weaker assumptions: in section 2 of the SI, we demonstrate that our overall turnout results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
 
@@
 
-## Voter turnout and municipal fines and fees collections {-}
-
-Next, we turn to our nationwide analysis of the relationship between municipal revenue raised from fees and fines and turnout.
-Our data come from two primary sources: the US Census Bureau’s Census of Governments Data (COG), and registered voter files from L2 Political.
-
-**Census of Governments**: Every five years, the US Census Bureau collects data from governmental bodies around the country.
-We use two waves of the COG: one that covers the years 2008 -- 2012, and another that covers 2013 -- 2017.
-The COG asks municipalities to report how much revenue they collect from “penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation...
-and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).” We divide these amounts by the population to estimate the per-capita fees and fines revenue raised in each municipality.
-This data has been used as a proxy for the amount of tickets issued at the local level in scholarly research [see, for instance, @Goldstein2020; @Sances2017].
-
-The COG data are useful to isolate ticketing practices because other fines and fees (e.g.
-fines imposed at sentencing in state court, probation fees, conviction fees, public defender fees) are typically collected by county or state governments.
-The COG data only include local revenues, which means the share of fines revenue corresponds more directly to local police practices.
-Following the guidance of @Sances2017, we retain only municipalities with police and/or court systems, as these are the only municipalities capable of issuing tickets.
-We also only retain municipalities with populations of at least 2,500.
-
-**Registered Voter Files**: The COG data do not include estimates of turnout at the local level.
-To estimate local turnout, we leverage registered voter files provided by data vendor L2 Political.
-In Washington, DC, and every state in the country (with the exception of North Dakota) voters are required to register to vote prior to participating.
-These files are considered public record, and in most states contain information about each voter’s age, residential address, political affiliation, and participation history.
-L2 collects voter files from around the country and merges them with proprietary data that estimates other voter- and household-level characteristics such as race and education.
-The individual-level records are aggregated up to the municipality level to determine the number of ballots cast for members of each race; these estimates are divided by 5-year citizen voting age population (CVAP) estimates from the Census Bureau to calculate turnout.
-As we show in the Supplementary Information, the L2 racial estimates closely track the municipal-level racial estimates from the Census Bureau.
-Because our turnout numerator and denominators come from different sources, there is slight measurement error: our estimate indicates, for instance, that roughly 1 percent of municipalities had Black turnout above 100 percent.
-Where more votes were cast than the Census estimate for CVAP, we recode turnout as 100 percent.
-Our results do not change if we instead simply remove these municipalities, or use unmodified turnout estimates.
-
-**Estimation Strategy**: We begin by merging each municipality’s fees and fines per capita (that is, dollars per resident) from the 2012 COG to its turnout from the 2014 midterm election, and the 2017 COG to its 2018 turnout.
-Because this measure is highly right-skewed, we use the natural log of fees and fines per capita (plus 1, to account for municipalities that collected no fees and fines).
-We also control for other municipal and state characteristics: racial composition, population density, median income, collegiate education, median age, and share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality’s revenue that comes from the state or federal government in the 2012 and 2017 COGs.
-We retain the 8,954 municipalities whose data is reported to the COG in both 2012 and 2017 and meet the other criteria noted above; these constitute the target population.
-
-The 5-year cycle of the COG does not neatly line up with the general 4-year cycle typical of American elections.
-The timing of the COG and midterm elections mean that our analytical strategy is conservative.
-If municipalities shift their fees and fines collections dramatically over the 2013 -- 2017 period, this shift may influence their 2014 turnout.
-However, we assume that turnout in 2014 will still be influenced by the policing practices of the 2008 -- 2012 period, while 2018 turnout will be largely influenced by the practices of the 2013 -- 2017 period.
-
-We run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
-
 ## National Survey Data {-}
@@
 We use these survey questions to make descriptive inferences about how stops and arrests affect the voting behavior of the general population.
-The first descriptive theoretical estimand is the gap between the voter turnout rate of individuals who were recently stopped by the police or who have ever been arrested, and another is whether stops or arrests uniquely influence the political behavior of Black Americans.
+The first descriptive estimand is the gap between the voter turnout rate of individuals who were recently stopped by the police or who have ever been arrested, and another is whether stops or arrests uniquely influence the political behavior of Black Americans.
 In addition to the respondent’s contact with the criminal legal system, we control for age; sex; income; education; party affiliation; self-described ideology; and reported 2016 turnout.
@@
 
-As discussed above, we begin by examining whether the turnout of individuals ticketed before an election was different from those ticketed after the election in Hillsborough County, Florida.
-Next, we test the relationship between fines and fees revenue reliance and voter turnout at the municipal level.
+As discussed above, we begin by examining whether the turnout of individuals stopped before an election was different from those stopped after the election in Hillsborough County, Florida.
 We also test the relationship between police stops and turnout in the 2020 election using survey data.
@@
 
-To directly observe the effect of being stopped by the police on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
-As discussed above, we match individuals who were ticketed between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.^2^ Matching is done with replacement and ties are not broken.
+To observe the effect of being stopped by the police on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
+As discussed above, we match individuals who were stopped between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.^[Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
+The full sample is used in the actual matching process.] Matching is done with replacement and ties are not broken.
 This means that some treated voters have multiple controls; the regression weights are calculated to account for this possibility.
-In Table 1 we present the results of the matching algorithm.
+In Table \ref{tab:balance} we present the results of the matching algorithm.
 As the table demonstrates, the selected control voters are very similar to the treated voters.
@@
 
-It is worth noting that voters who were ticketed between 2012 and 2020 were far more likely to be Black and male than the general electorate, and live in Census block groups with moderately lower incomes.
+It is worth noting that voters who were stopped between 2012 and 2020 were far more likely to be Black and male than the general electorate, and live in Census block groups with moderately lower incomes.
 
-In Figure 1, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped.
+In Figure \ref{fig:did-1}, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped.
 In the top row, we present the turnout in 2008--2014 of the individuals stopped between 2012 and 2014 and their controls; the second row shows the 2010--2016 turnout for individuals stopped between 2014 and 2016 and their controls; and the third shows the treatment effect for those stopped in the 2 years prior to the 2018 midterms.
@@
 
-```{r did1, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "!htb", fig.align = "center"}
+```{r did1, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
 p2 <- readRDS("temp/stopped_any_time_y.rds")
@@
 
-Figure 1 makes a number of things immediately apparent.
+Figure \ref{fig:did-1} makes a number of things immediately apparent.
 First, we can see that for both Black and non-Black voters the pre-treatment trends are identical.
 This, combined with the fact that treated and control voters mirror one another in terms of other characteristics, lends credibility to the parallel trends assumption.
-Secondly, Figure 1 provides preliminary visual evidence of the demobilizing effects of police stops in Hillsborough County.
+Secondly, Figure \ref{fig:did-1} provides preliminary visual evidence of the demobilizing effects of police stops in Hillsborough County.
 However, as the figure also makes clear, it seems that the negative effects are concentrated in the lower-salience midterm elections; there is little evidence of turnout effects in the 2016 presidential election.
 
-Table 2 formalizes the final row of Figure 1 into an ordinary least squares regression (the regression tables broken out for each year can be found in the Supplementary Information).
+Table \ref{tab:dind-table} formalizes the final row of Figure \ref{fig:did-1} into an ordinary least squares regression (the regression tables broken out for each year and including the coefficients for the matching covariates can be found in section 3 of the SI).
 Models 1 and 2 show our overall causal effect, while models 3 and 4 allow for the possibility that a ticket differentially mobilizes Black voters.
@@
 The empirical estimands are *Treated × Post Treatment* and *Treated × Post Treatment × Black*.
-In models 1 and 2, *Treated × Post Treatment* measures the overall treatment effect, and in models 3 and 4 it measures the treatment effect for non-Black voters.
-*Treated × Post Treatment × Black* measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
+In models 1 and 2, the coefficient on *Treated × Post Treatment* measures the overall treatment effect, and in models 3 and 4 it measures the treatment effect for non-Black voters.
+The coefficient on *Treated × Post Treatment × Black* measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
 
 \begin{singlespace}
-\input{"../temp/dind_reg_y.tex"}
+\input{"../temp/small_two_matches_reg_y_overall.tex"}
 \end{singlespace}
 
-As both Figure 1 and Table 2 make clear, police tickets meaningfully depressed turnout.
+As both Figure \ref{fig:did-1} and Table \ref{tab:dind-table} make clear, traffic stops meaningfully depressed turnout.
 In models 1 and 2, the estimated overall treatment effect is -1.5 percentage points.
-In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---non-Black turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
+In models 3 and 4, we can see that a stop was less demobilizing for Black individuals than for others---non-Black turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
 Although the treatment effect is still substantively quite large for Black individuals, Hillsborough County Black voters' turnout in federal elections was not as negatively impacted by police contact as that of non-Black individuals.
-
-## Municipal-Level Results {-}
-
-Before testing the causal effect of fees and fines collections on turnout, we begin with a cross-sectional analysis of the relationship using ordinary least squares.
-Here, we regress municipality-level turnout in 2018 against fees and fines collections as reported in the 2017 COG, as well as a number of other covariates.
-In Figure 2 we present the marginal effect of fees and fines on municipal-level turnout.
-The plot shows the results from two separate models: one in which the dependent variable is Black turnout (as a share of CVAP), and a second in which the dependent variable is non-Black turnout.
-The figure also marks the interdecile range.
-The full regression table can be found in the Supplementary Information.
-
-```{r cross-18, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:mef-2018}Predicted Turnout, 2018", fig.pos = "!htb", fig.align = "center"}
-load("temp/mef_to.rdata")
-print(p2)
-```
-
-As Figure 2 makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 1.5 percentage points over the interdecile range, after controlling for the other covariates.
-The opposite is true for Black voters: over the same range, Black turnout *increases* by roughly 2.4 percentage points.
-Both relationships are statistically significant at the 95 confidence level.
-This does not prove that higher fees and fines increase Black turnout; cross-sectional regressions cannot establish causality.
-Nevertheless, Figure 2 is consistent with this story.
-
-We turn now to our two-way fixed effects model.
-As discussed above, we retain each municipality that reported their fees and fines data to the COG in both 2012 and 2017 (and met the other criteria discussed in the *Data and Design* section).
-The dependent variable in each model is calculated by dividing the number of ballots cast in 2014 and 2018 by the 5-year CVAP estimate from the same year.
-We run the two-way fixed effects on overall turnout, Black turnout, and non-Black turnout.
-The results of these models can be found in Table 3.
-The average municipality included in this analysis raised $2.17 in fees and fines per resident in 2012, and the average municipality increased this per-capita figure by $0.47 between 2012 and 2017.
-Just over 10% of municipalities raised no revenue from fees and fines in either year.
-
-\begin{singlespace}
-\input{"../temp/2wfe_reg_clean.tex"}
-\end{singlespace}
-
-The results of the two-way fixed effects model are different from what we saw in the 2018 cross-sectional approach; namely, Table 3 indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not significantly impact Black turnout.
-The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.04 percentage points.
+It is also clear that midterm turnout is more impacted by these stops---as we show in section 3 of the SI, the negative impact is statistically significant in all years for non-Black residents, but much smaller in 2016 (-0.6pp) than in 2014 (-1.9pp) or 2018 (-3.0pp),
 
@@
 Roughly 15 percent of non-Black respondents reported a police stop in the preceding 12 months, while the same was true for more than 22 percent of Black respondents.
-In Figure 3 we present the results of our econometric models.
+In Figure \ref{fig:anes} we present the results of our econometric models.
 In the left-hand panel, we show the predicted turnout of respondents who answered “yes” or “no” to the question *During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?* The right-hand panel, meanwhile, plots these relationships for respondents who answered “yes” or “no” to the question *Have you ever been arrested, or has that never happened to you?*.
 These are the predicted probabilities after controlling for respondents’ race / ethnicity; age; party; ideology; income; education; and 2016 turnout.
-The full regression table can be found in the Supplementary Information..
+The full regression table can be found in section XX of the SI.
 
@@
 
-Figure 3 demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (*p* = 0.005).
-The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (*p* = 0.27).
+Figure \ref{fig:anes} demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (*p* = 0.004).
+The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (*p* = 0.07).
 Importantly, this effect is not a remnant of a white--nonwhite divide.
-As we show in the Supplementary Information, police stops were not differently related to turnout for Latinos than for non-Latinos; nor did they impact turnout differently for Asians than for non-Asians.
+As we show in the SI, police stops were not differently related to turnout for Latinos than for non-Latinos; nor did they impact turnout differently for Asians than for non-Asians.
 The ANES results point, then, to the fact that police stops are uniquely associated with higher turnout for Black respondents.
 
-The second panel of Figure 3 shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
+The second panel of Figure \ref{fig:anes} shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
 Importantly, the interaction between arrest status and the respondent’s race was not statistically significant.
@@
 
-This theoretical estimand is descriptive, and cross-sectional results cannot establish causality.
+It is worth re-establishing that cross-sectional results cannot establish causality.
 It is possible that Black respondents who had been stopped by the police (or had family members who experienced a stop) differed from non-Black respondents with such contact in ways that cannot be captured by the survey data.
@@
 
-### Discussion {-}
+# Discussion {-}
 
-While existing sociological and political science literature has examined the rise and collateral consequences of fines and fees as well as the effects of criminalization on political socialization, no study has investigated the causal relationship between ticketing and voter turnout.
-Additionally, our study is among the first to use individual-level administrative data to investigate the relationship between criminalization and political participation.
+While existing sociological and political science literature has examined the rise and collateral consequences of criminalization on political socialization, no study has investigated the causal relationship between ticketing and voter turnout using individual-level administrative data.
 
 Given how widespread police stops are and their relationship to racial injustice, their political implications demand close study.
-Accordingly, we investigate this question from a variety of perspectives, using multiple data sources and empirical approaches.
+Accordingly, we investigate this question using two different data sources and analytic strategies.
 What we find complicates our understanding of how lower-level police contact affects political participation.
-The national survey data and cross-sectional municipal-level analysis indicate that police contact is associated with higher turnout for Black Americans, and either unrelated or negatively related to turnout for others.
-Our causal models tell a slightly different story---they fail to uncover mobilizing effects for Black Americans.
-Nevertheless, our causal models *do* indicate that police stops are less demobilizing for Black individuals than for others.
-In this sense, our results all point in the same direction.
-Based on these three independent approaches, we conclude that the political consequences of police stops are unique for Black Americans---and that they are less demobilizing for Black Americans than others.
+In the analysis of Hillsborough County police stops, we find that stops reduce the voter turnout of non-Black voters, with a smaller negative effect for Black voters.
+On the other hand, the descriptive analysis of national survey data indicates that police contact is associated with *higher* turnout for Black Americans, and *unrelated* to turnout for others.
+Despite this incongruence, both analyses indicate that police stops have different participatory effects for Black individuals than for others.
+In this sense, our results point in the same direction.
+We conclude that the political consequences of police stops are unique for Black Americans---and that they are less demobilizing for Black Americans than others.
 Additionally, as @Walker2020a suggests, ticketed Black individuals may be politically mobilized for activities other than voting not observed in this study, such as contacting elected representatives or volunteering for campaigns.
+To that end, it is also worth noting that our causal analysis tests the effect of personal police contact rather than proximal contact, which was the focus of @Walker2020a---it could be the case that mobilizing effects of low-level police contact come from proximal exposure rather than personal.
 
-Our individual-level analysis based on Hillsborough County, Florida, advances our understanding of this dynamic while raising new questions.
-On the one hand, the causal results are highly robust, and the ticketing data allows us to identify the treatment fairly precisely.
-On the other hand, these are the only results in which police stops are associated with a *decrease* in turnout for Black individuals.
-This may be because this analysis tests the impact of direct contact with the police, rather than direct *or* proximal contact, as the ANES questions do.
-It may be because we can isolate the effect of a police stop from other, broader changes that may be correlated with increased fees and fines revenue in the municipal-level data.
-Or it may point to unique political circumstances surrounding race, policing, and political participation in Hillsborough County.
-We look forward to future scholarship that replicates and extends these Hillsborough County results.
-Nevertheless, that police stops are less demobilizing for Black Floridians in Hillsborough County---an effect that does not extend to other nonwhite residents---provides support for our general thesis that the political interpretation of these contacts with the criminal legal system are unique for Black Americans.
-
-The difference between the cross-sectional and two-way fixed effects models using the municipality-level data is somewhat surprising.
-There are a few potential explanations for this mismatch.
-First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes in the two-way fixed effects models are smaller or not statistically significant.
-Along a similar vein, it is possible that a mobilizing effect of ticketing for Black voters in the city-level analysis is offset by higher-intensity forms of criminal legal contact, such as arrest and incarceration.
-The bulk of existing literature suggests that incarceration discourages political participation, and it is not unreasonable to assume that cities that ramp up ticketing of Black residents also ramp up arrest and incarceration of Black residents.
-If these phenomena coincide, that could explain why the city-level analysis produced no statistically significant effect for Black voters---the personally mobilizing effect of ticketing could be counterbalanced by the proximal chilling effect of incarceration, and because the city-level analysis is not as temporally sensitive, it is more difficult to isolate the effect of ticketing.
-At the same time, @Harris2020 indicates that when municipalities increase their fees and fines collections, relatively more *white* individuals are ticketed.
-@Shoub2020 demonstrates the corollary: when municipalities stop fewer motorists, the decrease is concentrated among white individuals.
-Existing research, then, indicates that a relatively constant share of the Black population is stopped by the police; changes in fees and fines collections largely impacts the white population.
-The overall changes in revenue we observe in our two-way fixed effects models might reflect changes largely for the white populations in these municipalities, while ticketing---and turnout---remain more or less constant for Black populations.
-We were unable to incorporate a race-specific measure of police stops or measures of local incarceration or policing trends due to a lack of consistent data nationwide.
-
-Finally, Sances and You [-@Sances2017: 1091]---the paper that originally detailed the relationship between fees and fines collections and municipalities’ racial composition using the Census of Governments data---specifically notes that they did not exploit the panel setup of the COG because of “little variation within a city in terms of revenues from fines.” Instead, they present only the results of a cross-sectional study.
-Here, we present both the cross-sectional and panel results, acknowledging that each have limitations but that, taken together, they shed light on the unique politicization of fees and fines for Black Americans.
-
-Our findings have several implications for political sociology and political science scholarship.
+Our findings have several implications for political science scholarship.
 While existing literature suggests that the most disruptive forms of criminal legal contact (i.e.
 criminal convictions and incarceration) consistently discourage voting [@Lerman2014; @Burch2011; @White2019a], research regarding police stops has produced more mixed results [@Laniyonu2019].
-We extend this theory to police ticketing, the most common form of police contact in America, and find that ticketing generally reduces turnout.
-For Black voters, however, our findings suggest that ticketing can be politically mobilizing.
+We extend this theory to police ticketing, the most common form of police contact in America, and find that police traffic stops generally reduce turnout.
+For Black voters, however, our findings suggest that traffic stops are less demobilizing, a sharp contrast with existing scholarship wherein more disruptive forms of criminalization discourage Black voters more than non-Black voters.
 Particularly following the rise of the Black Lives Matter movement in 2013, our findings constitute new evidence in support of our theory that ticketing is distinct from other forms of criminal legal contact and therefore catalyzes different political behaviors among Black voters, who are disproportionately affected by both ticketing and criminalization in general.
 
-In this sense, our analysis points to a political contestation of criminal legal policy, a phenomenon that aligns with dozens of recent campaigns to reform local fines and fees practices (or abolish them entirely).^3^  We know that increased fines and fees result from political economy (i.e.
-austerity at the federal level), but our analysis suggests that this is a “two way street” wherein people who are harmed by policing practices can be politically socialized into resistance.
+In this sense, our analysis could be consistent with a political contestation of criminal legal policy, a phenomenon that aligns with dozens of recent campaigns to reform local fines and fees practices (or abolish them entirely).^[See https://finesandfeesjusticecenter.org/clearinghouse.]  We know that increased fines and fees result from political economy (i.e.
+austerity at the federal level), but our analysis suggests that this could be a “two way street” wherein people who are harmed by policing practices can be politically socialized into resistance.
 
-**Limitations**: Because our individual-level administrative data analysis is limited to Hillsborough County where fines collections increased over the period, we do not have a good sense of how the city-level revenue reliance trend interacts with the individual experience of being ticketed in areas where fees and fines are constant or decreasing.
-Is ticketing more politically mobilizing for Black voters in cities that are palpably dialing up their revenue collection efforts?
-Future research could test this hypothesis at the individual level within cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.
-
-Additionally, in our analysis of Hillsborough County voters, we do not look at people who were not registered to vote in 2018.
+**Limitations**: In our analysis of Hillsborough County voters, we do not look at people who were not registered to vote in 2018.
 Because we cannot tell whether unregistered individuals who were stopped in Hillsborough County were unregistered because they were *ineligible* to do so (by virtue of living in a different county or being a non-citizen, for instance) or chose to eschew electoral politics, our analysis is necessarily limited to individuals who were registered to vote.
@@
 
-Finally, we are sensitive to the fact that although administrative data provides real-world evidence of actual behavior, such an approach limits our ability to understand the psychological processes in play.
+Finally, we are sensitive to the fact that although administrative data provides real-world evidence of actual behavior, such an approach limits our ability to understand the causal mechanisms in play.
 This means that although we demonstrate that police stops are demobilizing, future work must further investigate how stops are interpreted by individuals and translated into political behavior.
 
-Although we have generated new evidence suggesting that police stops and related exploitative ticketing practices may mobilize Black voters, we emphasize that this finding does not redeem or justify such police practices.
+Although we have contributed new evidence suggesting that police stops and related exploitative ticketing practices may not demobilize Black voters to the same extent as non-Black voters, we emphasize that this finding does not redeem or justify such police practices.
 Black Americans already suffer from disproportionate police contact and the racial wealth gap, and racist revenue-motivated ticketing only increases the burden on Black communities nationwide.
 Policymakers should work to ensure that Black Americans no longer have to struggle to enjoy the same political power as whites---to that end, the current trend of voting rights restriction policies across the country is especially pernicious.
-Even if Black Americans understand the ballot box as one tool they can use to limit the state’s power to exploit and harm them, policymakers should still feel an obligation to support voting rights protections and stop disproportionate ticketing in Black communities.
-
-\newpage
-
-# Notes {-}
-
-^1^ Because such frequent snapshots are not available from L2, we here use the registered voter file made freely available by the state of Florida.
-
-^2^ Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights. The full sample is used in the actual matching process.
-
-^3^ See https://finesandfeesjusticecenter.org/clearinghouse.
+Even if some Black Americans understand the ballot box as one tool they can use to limit the state’s power to exploit and harm them, policymakers should still feel an obligation to support voting rights protections and stop disproportionate ticketing in Black communities.
 
@@
 # References {-}
-
-<div id="refs"></div>

### 2022-04-19 markdown/draft_paper.tex
submissions

@@
 \hypersetup{
-  pdftitle={Ticketing and Turnout: How Policing for Profit Shapes Democratic Participation},
-  pdfauthor={Jonathan Ben-Menachem; Kevin Morris},
+  pdftitle={Ticketing and Turnout: The Participatory Consequences of Low-Level Police Contact},
   hidelinks,
@@
 
-\title{Ticketing and Turnout: How Policing for Profit Shapes Democratic Participation}
-\author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
-\date{October 01, 2021}
+\title{Ticketing and Turnout: The Participatory Consequences of Low-Level Police Contact}
+\author{}
+\date{\vspace{-2.5em}February 22, 2022}
 
@@
 \begin{abstract}
-The American criminal legal system is an important site of political socialization: sociologists show how the alienating effect of criminalization pushes people away from public institutions, and political scientists have measured the effects of policing and incarceration on political participation.
-Despite this burgeoning literature, no research has directly investigated how police ticketing practices affect political participation.
-We use three approaches to answer this question: we leverage individual-level administrative ticketing data from Hillsborough County, Florida between 2010 and 2020, a city-level analysis using Census of Governments data and the national voter file, and national survey data.
-We use a genetic matching algorithm and difference-in-differences to estimate that being ticketed decreases an individual's likelihood of voting in federal elections by 1.7 percentage points, but depressive effects are smaller for Black residents.
-Nationally, we estimate that each 10 percent increase in city fines and fees collections between 2012 and 2017 was associated with a roughly 0.04 percentage point turnout decrease but was not associated with any change in Black turnout.
-The survey data show that Black people who report that they or a family member were recently stopped by police are more likely to vote than those who reported no such contact.
+The American criminal legal system is an important site of political socialization: scholars have shown that criminal legal contact reduces turnout, and that criminalization pushes people away from public institutions more broadly.
+Despite this burgeoning literature, few analyses directly investigate the causal effect of \emph{lower-level} police contact on voter turnout.
+We use two approaches to do so: we leverage both individual-level administrative ticketing data from Hillsborough County, Florida, and responses to the American National Election Studies.
+We estimate that a traffic stop decreases an individual's likelihood of voting by 1.7 percentage points, but depressive effects are smaller for Black residents.
+The survey data, however, show that Black people who report that they or a family member were recently stopped by police are \emph{more} likely to vote than those who reported no such contact.
+Taken together, our results indicate that low-level contact with police may have participatory consequences.
 
@@
 
-\textbf{Keywords}: voting, monetary sanctions, race, punishment, political participation
+\textbf{Keywords}: voting, policing, race, punishment, political participation
 \end{abstract}
@@
 
-Work exploring how criminalization directly and indirectly influences political participation has exploded in recent years following path-breaking work from political sociologists Chris Uggen and Jeff Manza (\protect\hyperlink{ref-Uggen2002}{Uggen and Manza 2002}; \protect\hyperlink{ref-Manza2006}{Manza and Uggen 2006}).
+Although scholars have examined the collateral consequences of this increased reliance on fines and fees (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}; \protect\hyperlink{ref-Pacewicz2020}{Pacewicz and Robinson 2020}), comparatively few have explored the moment during which such revenue-raising actually occurs: namely, in the individual interactions between residents and the police via the issuance of a ticket.
+This ``moment'' of low-level contact has also been relatively understudied by scholars investigating the participatory consequences of contact with the criminal legal system.
+Work exploring how criminalization directly and indirectly influences political participation has exploded in recent years.
 Scholars have found that criminal legal contact (i.e.~arrest, conviction, incarceration) consistently discourages voting (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}; \protect\hyperlink{ref-Burch2011}{Burch 2011}; \protect\hyperlink{ref-White2019a}{White 2019b}).
@@
 While ticketing involves potentially negative interactions with the state, it does not necessarily carry the disruptive consequences of a felony conviction and might thus politicize Americans in unique ways.
-Building on recent theoretical work from \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020b}) and an analysis of the historical context of fees and fines collections in the United States, this paper is the first to explicitly theorize how local ticketing practices shape the political socialization of ticketed individuals.
-We argue that ticketing depresses voter turnout overall, but also catalyzes a ``linked fate'' political analysis among Black voters that either causes increased turnout or mitigates the turnout reductions observed among non-Black individuals.
+Building on recent theoretical work from \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020b}), this paper theorizes how local police practices affect voting behavior among ticketed individuals and provides precisely estimated evidence of a causal effect.
 
-Additionally, our project represents the first use of individual-level administrative data to identify the causal effect of ticketing on voter behavior.
+Our project represents the first use of individual-level administrative data to identify the causal effect of traffic stops on voter behavior.
 The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures political participation.
-Past work looking at the individual-level effects of low-level contact has relied entirely on survey or qualitative data (e.g.
+Past work looking at the individual-level effects of low-level contact has relied on survey or qualitative data (e.g.
 \protect\hyperlink{ref-Walker2014}{Walker 2014}; \protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
@@
 As Weaver and Lerman (\protect\hyperlink{ref-Weaver2010}{2010}: 821) note, it may also introduce measurement bias.
-Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to police ticketing.
-The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of a quarter-million individuals ticketed over a 6 year period---a far larger pool than even the most robust surveys.
+Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to a traffic stop.
+The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of a quarter-million individuals stopped over a 6 year period---a far larger pool than even the most robust surveys.
 
-We use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were ticketed between the 2012 and 2018 elections.
-By matching individual voters who were ticketed to similar voters who were ticketed at later points and running a difference-in-differences model, we estimate the causal effect of these tickets on turnout.
-We find that being ticketed reduces the chance that an individual will turn out in the subsequent election, but that this effect is smaller for Black voters.
+We use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were stopped between the 2012 and 2018 elections.
+By matching individual voters who were stopped to similar voters who were stopped at later points and running a difference-in-differences model, we estimate the causal effect of these stops on turnout.
+This borrows from the logic of regression discontinuities in time: conditional on observable characteristics \emph{and} unobservable factors associated with being ticketed, the timing of the ticket on either side of election day is essentially as-if random.
+We find that being stopped reduces the chance that an individual will turn out in the subsequent election, but that this effect is smaller for Black voters.
 
-To test the generalizability of our findings in Hillsborough County, we leverage two different datasets that are national in scope.
-First, we join fees and fines data from municipalities around the country in 2012 and 2017 with a novel dataset estimating racial turnout for thousands of municipalities around the country.
-While we find that increased fees and fines likely cause lower turnout among non-Black Americans, we find no effect of fees and fines on Black turnout.
+To test the generalizability of our findings in Hillsborough County, we conduct a novel analysis of 2020 national survey data regarding voters' experience with police stops.
+We find that Black respondents who reported personal or proximal experience with police stops in the last 12 months are more likely to vote than Black people who did not, while we find no statistically significant relationship between stops and voting among non-Black respondents.
+While the survey data present some drawbacks relative to the individual-level administrative data, their national scope provides helpful corroboration for the unique turnout effects of traffic stops for Black Americans observed in Hillsborough County.
 
-Second, we conduct a novel analysis of 2020 national survey data regarding voters' experience with police stops.
-We find that Black respondents who reported personal or proximal experience with police stops in the last 12 months are more likely to vote than Black people who did not, while we find no statistically significant relationship between stops and voting among non-Black respondents.
-While both the municipal-level and survey data present some drawbacks relative to the individual-level administrative data, their national scope provides helpful corroboration for the unique turnout effects of tickets for Black Americans observed in Hillsborough County.
+We demonstrate that police ticketing practices---the most widespread form of police contact in America---substantially reduce the turnout of non-Black American voters, but have a unique effect on Black voter turnout.
+Our findings complicate existing theories of how criminalization politically socializes Americans, and Black Americans in particular (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
+Additionally, while many forms of criminalization have been found to contribute to a well-documented subjective experience of alienation or group-level exclusion among Black Americans (\protect\hyperlink{ref-Bell2017}{Bell 2017}; \protect\hyperlink{ref-Stuart2016}{Stuart 2016}; \protect\hyperlink{ref-Desmond2016}{Desmond, Papachristos, and Kirk 2016}, \protect\hyperlink{ref-Desmond2020}{2020}; \protect\hyperlink{ref-Zoorob2020}{Zoorob 2020}; \protect\hyperlink{ref-Ang2021}{Ang et al.
+2021}), our contribution emphasizes the need for further research regarding how different forms of criminalization affect group-level perceptions of government and resultant political behaviors.
+Our findings are relevant for interdisciplinary scholars of crime, race, politics, municipal finance, and policing.
 
-We demonstrate that police ticketing practices---the most widespread form of police contact in America---substantially reduce the turnout of non-Black American voters, but can mobilize Black voters.
-Our findings complicate existing theories of how criminalization politically socializes Americans, and Black Americans in particular (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
-Additionally, while all forms of criminalization likely contribute to a subjective experience of alienation or group-level exclusion among Black Americans that is well-documented in sociological scholarship (\protect\hyperlink{ref-Bell2017}{Bell 2017}; \protect\hyperlink{ref-Desmond2016}{Desmond, Papachristos, and Kirk 2016}), our contribution emphasizes the need for further research regarding how different forms of criminalization affect group-level perceptions of government and resultant political behaviors.
-Accordingly, we propose a new theory explaining how ticketing may uniquely catalyze Black political participation.
-Our findings are relevant for interdisciplinary scholars of crime, race, politics, political economy, social movements, and policing.
+\hypertarget{criminal-legal-system-and-citizen-identity}{%
+\section*{Criminal Legal System and Citizen Identity}\label{criminal-legal-system-and-citizen-identity}}
+\addcontentsline{toc}{section}{Criminal Legal System and Citizen Identity}
 
-\hypertarget{literature-review}{%
-\section*{Literature Review}\label{literature-review}}
-\addcontentsline{toc}{section}{Literature Review}
+In recent years, scholars have paid more attention to the political implications of the American criminal legal system.
+Evolving in part out of a literature focused on street-level bureaucrats, researchers across the social sciences are asking how daily interactions with agents of the carceral state shape Americans' relationships to themselves, their communities, and their state.
+As \protect\hyperlink{ref-Soss2017}{Soss and Weaver} (\protect\hyperlink{ref-Soss2017}{2017}) argues, this ``second face'' of the state---``the activities of governing institutions and officials that exercise social control and encompass various modes of coercion, containment, repression, surveillance, regulation, predation, discipline, and violence'' (567)---is the primary way through which many class-race subjugated communities develop their political knowledge.
+``{[}I{]}nterviewees have looked, not to City Hall, Congress, or political parties,'' they write, ``but rather to their direct experiences with police, jails and prisons, welfare offices, courts, and reentry agencies as they sought to ground their explanations of how government works, what political life is like for them, and how they understand their own political identities'' (\protect\hyperlink{ref-Soss2017}{Soss and Weaver 2017, 574}).
 
-An emerging political science literature directly investigates the relationship between criminalization and political behavior.
-Additionally, sociologists have incorporated contemporary fines and fees practices into a broader empirical-historical theory of racialized punishment policy (\protect\hyperlink{ref-Harris2010}{A.
-Harris, Evans, and Beckett 2010}; \protect\hyperlink{ref-Friedman2020}{Friedman 2020}).
-
-In order to theorize how fines and fees affect political behavior, we consider how criminalization directly shapes the electorate; the existing scholarly understanding of the influence of criminalization on political socialization; and how contemporary ticketing practices are tied to a longer legacy of racist exploitation and thus ripe for political mobilization around narratives of racial injustice.
-
-\hypertarget{criminalization-and-political-socialization}{%
-\subsection*{Criminalization and political socialization}\label{criminalization-and-political-socialization}}
-\addcontentsline{toc}{subsection}{Criminalization and political socialization}
-
-The American criminal legal system directly shapes the American electorate and excludes voters.
-Today, more than five million Americans are legally barred from voting due to a felony conviction, and one in every sixteen Black Americans of voting age is disenfranchised (\protect\hyperlink{ref-Uggen2020}{Uggen et al.
-2020}).
-Notably, fines and fees legally disenfranchise Americans as well: 48 states and the District of Columbia authorize some form of wealth-based penal disenfranchisement (\protect\hyperlink{ref-Colgan2019}{Colgan 2019}).
-Many states require payment of fees as a condition of criminal legal supervision or the payment of all legal financial obligations as a condition of completing a sentence, and failure to comply with supervision or sentence completion conditions can be a barrier to voting rights restoration.
-
-Beyond de jure disenfranchisement, the spatial and racial concentration of criminalization influences affected communities' perceptions of government.
-Monica Bell calls this process ``legal estrangement,'' a conceptual framework meant to capture those perceptions and cultural attitudes (``legal cynicism'') as well as the historical-structural conditions that produced them (\protect\hyperlink{ref-Bell2017}{Bell 2017}).
-Research on legal cynicism has found that public perceptions of abusive police practices can reduce willingness to report crimes or cooperate with law enforcement (\protect\hyperlink{ref-Desmond2016}{Desmond, Papachristos, and Kirk 2016}; \protect\hyperlink{ref-Tyler2014}{Tyler, Fagan, and Geller 2014}).
-In short, the ``hidden curriculum'' (\protect\hyperlink{ref-Justice2014}{Justice and Meares 2014}; \protect\hyperlink{ref-Meares2017}{Meares 2017}) of the criminal legal system teaches Americans about their identities as citizens---even parts of their identities that have little to do with policing or incarceration.
+Recent work has explored the production of this political knowledge in increasingly sophisticated ways, using both qualitative and quantitative approaches.
+\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver} (\protect\hyperlink{ref-Lerman2014}{2014})'s pathbreaking book \emph{Arresting Citizenship} set the table for future research.
+Their project combined extensive interviews of individuals living in areas closely monitored by the criminal legal system with novel survey data to probe the political consequences of what they term the ``carceral state.'' Their work indicates that citizens nearly uniformly react negatively to police and carceral supervision---from low-level interactions to lengthy periods of incarceration, Americans subjected to the second face of the state apparently withdraw from political participation.
+They find that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
 New evidence related to ticketing and legal estrangement has recently emerged: in a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government compared to residents who were not ticketed (\protect\hyperlink{ref-CarpenterII2019}{Carpenter II, Sweetland, and McDonald 2019}).
 
-Because police are the most visible agents of the state, perceptions of unfairness in policing can translate to a recognition of actual group-level structural exclusion from public institutions (\protect\hyperlink{ref-Bell2017}{Bell 2017}).
-Soss and Weaver explain how criminal legal contact shapes perceptions of government and political participation: ``interviewees have looked, not to City Hall, Congress, or political parties, but rather to their direct experiences with police, jails and prisons, welfare offices, courts, and reentry agencies as they sought to ground their explanations of how government works, what political life is like for them, and how they understand their own political identities'' (\protect\hyperlink{ref-Soss2017}{Soss and Weaver 2017}: 574).
-
-Sarah Brayne found related results in her analysis of survey data.
-As the intensity of criminal legal contact escalates (i.e.~stopped, arrested, convicted), people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions (\protect\hyperlink{ref-Brayne2014}{Brayne 2014}).
+Sarah Brayne (\protect\hyperlink{ref-Brayne2014}{2014}) found related results in her analysis of survey data.
+As the intensity of criminal legal contact escalates , people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions.
 She calls this phenomenon ``system avoidance,'' and while her analysis did not specifically assess voting behavior, her findings demonstrate how criminal legal contact can discourage Americans' participation in public institutions as well as how the effect may vary alongside the intensity of criminal legal intervention.
 Similarly, \protect\hyperlink{ref-Remster2018a}{Remster and Kramer} (\protect\hyperlink{ref-Remster2018a}{2018}) finds that men who return home from prison are more likely to avoid contact with their childrens' schools.
-Vesla Weaver and colleagues helpfully describe this form of self-preserving withdrawal from public institutions as a ``strategic retreat'' (\protect\hyperlink{ref-Weaver2020}{Weaver, Prowse, and Piston 2020}).
+Vesla Weaver and colleagues describe this form of self-preserving withdrawal from public institutions as a ``strategic retreat'' (\protect\hyperlink{ref-Weaver2020}{Weaver, Prowse, and Piston 2020}).
 
-In addition to influencing perceptions of government and participation in public institutions, recent scholarship indicates that criminalization influences political behavior.
-Using existing national survey data and extended interviews, Vesla Weaver and Amy Lerman found that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
-Weaver and Lerman also investigate the potential role of criminal legal contact in facilitating a collective political consciousness among Black Americans, or the concept of a ``linked fate'' where ``one's individual opportunities are linked to the entire racial group'' (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}: 197).
-Their interview data lead them to conclude that while criminal legal contact does increase perceptions of linked fate among Black respondents, ``a custodial linked fate is not the building block of greater activism and a mobilized racial identity; instead, it is demobilizing.'' Interview respondents who had been incarcerated reported that withdrawal from public institutions and democratic participation constituted a form of self-preservation (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}).
+These findings can be situated in a process that sociologist Monica Bell calls ``legal estrangement,'' which captures those perceptions and cultural attitudes (``legal cynicism'') as well as the historical-structural conditions that produced them (\protect\hyperlink{ref-Bell2017}{Bell 2017}).
+Research on legal cynicism has found that public perceptions of abusive police practices can reduce willingness to report crimes or cooperate with law enforcement (\protect\hyperlink{ref-Tyler2014}{Tyler, Fagan, and Geller 2014}).
+The ``hidden curriculum'' (\protect\hyperlink{ref-Justice2014}{Justice and Meares 2014}; \protect\hyperlink{ref-Meares2017}{Meares 2017}) of the criminal legal system teaches Americans about their identities as citizens---even parts of their identities that have little to do with policing or incarceration.
 
-Lerman and Weaver's findings have been corroborated using administrative data: Ariel White found that short jail sentences in Harris County, Texas reduced Black defendant turnout in subsequent elections by 13 percentage points---but the effect on white turnout was not statistically significant (\protect\hyperlink{ref-White2019}{White 2019a}).
-Traci Burch found that North Carolina block groups with higher concentrations of people who had experienced incarceration or criminal legal supervision saw substantial reductions in voter turnout, and confirmed her findings at the individual level (\protect\hyperlink{ref-Burch2014}{Burch 2014}).
-These effects can also extend to family members, and the political consequences can be quite durable (\protect\hyperlink{ref-Morris2021}{Morris 2021}).
+\hypertarget{administrative-data-and-the-causal-effects-of-criminalization}{%
+\section*{Administrative Data and the Causal Effects of Criminalization}\label{administrative-data-and-the-causal-effects-of-criminalization}}
+\addcontentsline{toc}{section}{Administrative Data and the Causal Effects of Criminalization}
 
-Although most work documents how contact with the criminal legal system causes strategic retreat, recent work from Hannah Walker (\protect\hyperlink{ref-Walker2020}{2020a}, \protect\hyperlink{ref-Walker2020a}{2020b}) complicates this narrative.
-She argues that when Black Americans understand their contact with the criminal legal system in the context of a narrative of racial injustice, such contact can actually mobilize.
-She explains: ``experiences with punitive policies are subject to interpretation and, when understood through narratives of injustice, lead to wholly different participation outcomes than we usually predict'' (\protect\hyperlink{ref-Walker2020}{Walker 2020a}: 132).
+Many scholars have turned to administrative data in recent years to explore the actual effects of contact with the criminal legal system on political participation in the voting booth.
+To be sure, administrative data have limitations: they are not ideally suited to probe the psychological, social, relational, and other mechanisms leading some citizens to vote and others to abstain.
+These limitations, however, are balanced by offering researchers precise estimates of actual---and not just reported---turnout.
+
+Traci Burch (\protect\hyperlink{ref-Burch2011}{2011}) was among the earliest scholars to match voter-file records with records detailing citizens' contact with the criminal legal system.
+Her work complicated a previously dominant theory postulating that the turnout and party registration of formerly incarcerated individuals was largely driven by their sociodemographic characteristics but not their formal conviction or supervision (see, for instance, \protect\hyperlink{ref-Uggen2002}{Uggen and Manza 2002}).
+She argues that citizens who are convicted of felony offenses are less likely to vote, and less likely to register with a party, than citizens with similar sociodemographic characteristics without such a conviction.
+
+Other scholars have similarly matched corrections records with registered voter files to explore the effect of contact with the second face of the state.
+\protect\hyperlink{ref-White2019a}{White} (\protect\hyperlink{ref-White2019a}{2019b}) finds that short periods of incarceration reduce Black, but not white, turnout.
+\protect\hyperlink{ref-Gerber2017}{Gerber et al.} (\protect\hyperlink{ref-Gerber2017}{2017}) similarly finds relatively small effects of incarceration on turnout.
+Meredith and Morse (\protect\hyperlink{ref-Meredith2014}{2014}, \protect\hyperlink{ref-Meredith2015}{2015}) and \protect\hyperlink{ref-Gerber2015}{Gerber et al.} (\protect\hyperlink{ref-Gerber2015}{2015}) explore the turnout effect of notifying formerly incarcerated citizens of the legal restoration of their voting rights, with mixed results, while \protect\hyperlink{ref-Morris2021a}{Morris} (\protect\hyperlink{ref-Morris2021a}{2021a}) shows that restoring voting rights to individuals while they are still on parole increases post-supervision turnout.
+Other work has explored the ``spillover'' effects of such contact, finding that the political behavior of family members (\protect\hyperlink{ref-White2019}{White 2019a}) and neighbors (\protect\hyperlink{ref-Burch2014}{Burch 2014}; \protect\hyperlink{ref-Morris2020}{Morris 2020}) can be influenced by indirect contact with incarceration.
+\protect\hyperlink{ref-Morris2021}{Morris} (\protect\hyperlink{ref-Morris2021}{2021b}) argues that these effects are durable, showing that citizens whose household members had been to prison were not disproportionately mobilized by a ballot initiative promising to end felony disenfranchisement.
+
+This burgeoning literature using administrative data has given scholars far greater insight into the participatory consequences of American incarceration.
+It is, however, virtually silent on the effects of \emph{lower level} contact with the criminal legal system.
+Far more Americans have low-level contact with the police than will ever spend a night behind bars: just under 20 million Americans experience a traffic stop each year, whereas approximately five million Americans are arrested and jailed each year (\protect\hyperlink{ref-Harrell2020}{Harrell and Davis 2020}; \protect\hyperlink{ref-Jones2019}{Jones and Sawyer 2019}).
+Despite the fact that so many more citizens are subjected to traffic stops, we know comparatively little about its political ramifications, a lack that is particularly glaring given how much we have learned in recent years about higher-level contact.
+
+The one project that has used administrative data to explore the political implications of low-level police contact is \protect\hyperlink{ref-Laniyonu2019}{Laniyonu} (\protect\hyperlink{ref-Laniyonu2019}{2019}), which explores the effects of the Stop, Question, and Frisk (SQF) program in New York City.
+\protect\hyperlink{ref-Laniyonu2019}{Laniyonu} (\protect\hyperlink{ref-Laniyonu2019}{2019})'s causal estimates rely on a cross-sectional matching model to compare voter turnout in precincts with \emph{high} SQF activity to turnout in precincts with similar sociodemographic characteristics but \emph{low} SQF activity, supplemented with cross-sectional analyses of all precincts in the city.
+His results paint a complicated picture: his causal estimates find that high levels of SQF increased turnout in the 2008 presidential election, but decreased it in the 2010 midterms.
+While \protect\hyperlink{ref-Laniyonu2019}{Laniyonu} (\protect\hyperlink{ref-Laniyonu2019}{2019}) marks an important step forward in the investigation of the consequences of policing for political behavior, it faces certain data and methodological limitations.
+Because the SQF data does not include identifying information about the individuals stopped, he cannot explore the turnout of New Yorkers who were actually subjected to SQF.
+Thus, as he notes in the conclusion, ``the ability of the analysis to make causal claims is limited'' (554) by the cross-sectional matching approach.
+
+In this project, we seek to extend our understanding of the political consequences of routine contact with the state's second face.
+Combining an individual-level administrative panel dataset with national survey data gives us new insight into how traffic stops can shape citizens' engagement with their democracy.
+
+\hypertarget{how-police-stops-might-structure-turnout}{%
+\section*{How Police Stops Might Structure Turnout}\label{how-police-stops-might-structure-turnout}}
+\addcontentsline{toc}{section}{How Police Stops Might Structure Turnout}
+
+Much of the existing work on the turnout consequences of the criminal legal system points to a process of political learning or political socialization.
+\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver} (\protect\hyperlink{ref-Lerman2014}{2014}) finds that individuals in highly surveilled neighborhoods learn that the government does not care about them, and is uninterested in soliciting their participation.
+They note that more than half of individuals stopped by the police report agreeing with the statement ``the leaders in government care very little about people like me,'' compared with just a third of respondents with no police contact (150).
+The numbers, however, were far higher for individuals convicted of a crime, of whom three-quarters agreed with the statement.
+Learning about the criminal legal system takes place over a long period of time.
+Could isolated police stops that neither require sustained contact with the criminal legal system nor (generally) impose punishments as severe as incarceration politically socialize Americans to the same degree as incarceration?
+
+On one hand, it might seem unlikely that a single stop would produce much new knowledge about the state.
+For many Americans, a traffic stop amounts to little more than a slap on the wrist.
+To be sure, fines and fees can wreak havoc on the lives of some drivers.
+If a ticket leads to a suspended driver's license, the initial stop can snowball into a much bigger life event that could jeopardize employment, or lead to shorter stints of incarceration for individuals apprehended driving on a suspended license.
+Searches conducted during traffic stops may also lead to arrest or incarceration if a police officer finds contraband in the vehicle.
+These comparatively less frequent cases might have consequences more akin to those associated with a brief period of incarceration that can also threaten employment.
+Nevertheless, the average traffic stop is certainly less disruptive than the average period of incarceration, perhaps producing less political knowledge and therefore impacting turnout less.
+
+On the other hand, a far larger set of Americans are stopped by the police than sent to jail or prison each year.
+According to the American National Election Study, a nationally-representative survey we use later in this study, the incomes and education levels for individuals stopped by the police are meaningfully higher than for individuals who report ever having been arrested.
+Motorists stopped by police are apparently systematically different compared to people who experience incarceration.
+Traffic stops might thus be the primary way some of these Americans learn about the criminal legal system.
+If these Americans have not already ``learned'' about the system from their neighborhoods or family members, the political consequences of such newly gleaned knowledge might be large.
+
+Traffic stops might provide early insights about the criminal legal system even for Americans who live in more heavily-policed areas.
+As \protect\hyperlink{ref-Gerber2017}{Gerber et al.} (\protect\hyperlink{ref-Gerber2017}{2017}) notes in their study arguing that the participatory consequences of incarceration might be small, incarceration ``is an outcome that often follows a long series of interactions with the criminal justice system'' (1145).
+In other words, much of what the criminal legal system ``teaches'' might have already been learned by the time an individual is sent to prison.
+Someone who is stopped by the police, however, might have had fewer negative interactions with the state.
+Put differently, stopped individuals might have more to learn than incarcerated individuals with a long history of police contact, resulting in higher turnout effects.
+
+\hypertarget{potential-for-racially-disparate-effects}{%
+\section*{Potential for Racially Disparate Effects}\label{potential-for-racially-disparate-effects}}
+\addcontentsline{toc}{section}{Potential for Racially Disparate Effects}
+
+The potential for more ``learning'' from a police stop seems especially salient for Black Americans, particularly in recent years.
+National news over the 2010s was filled with the names of Black Americans who were killed during routine police stops.
+The Black Lives Matter movement gained national attention in the aftermath of the Ferguson uprising, an uprising sparked by the police killing of Michael Brown but also fueled by that city's racial discriminatory ticketing practices.
+In the fall of 2021, \emph{The New York Times} ran an extensive report exploring police killings that occur during traffic stops, providing more proof of their racially disparate nature (\protect\hyperlink{ref-Levenson2021}{Levenson 2021}).
+
+We expect that the participatory consequences of such a stop will be different for Black than non-Black Americans.
+First, traffic stops differ in meaningful ways for Black and non-Black Americans.
+As \protect\hyperlink{ref-Baumgartner2018}{Baumgartner, Epp, and Shoub} (\protect\hyperlink{ref-Baumgartner2018}{2018}) notes, Black Americans are more likely than whites to receive both ``light'' (i.e., a warning without a ticked) \emph{and} ``severe'' (i.e., arrest) outcomes from a traffic stop.
+Although this may seem paradoxical at first, the authors explain: ``while many might rejoice in getting a warning rather than a ticket, the racial differences consistently apparent in the data suggest another interpretation for black drivers: even the officer recognized that there was no infraction'' {[}88{]}.
+Black drivers are also more likely to be searched and arrested, but less likely to be found with contraband (\protect\hyperlink{ref-Baumgartner2018}{Baumgartner, Epp, and Shoub 2018}).
+Similarly, \protect\hyperlink{ref-Epp2014}{Epp, Maynard-Moody, and Haider-Markel} (\protect\hyperlink{ref-Epp2014}{2014}) argues that traffic stops are particularly instructive for Black Americans, as pretextual traffic stops politically socialize Black voters to the specific context of discriminatory police ticketing.
+
+The politicization of a police stop can occur differently for Black Americans through other avenues as well.
+The BLM movement has raised the salience of racially disparate policing across the country, as have the tragic stories of individuals like Philando Castile who was killed during a police stop.
+Routine interactions with the police are also more likely to turn deadly for Black Americans than for others (\protect\hyperlink{ref-Levenson2021}{Levenson 2021}).
+Thus, even if an individual police stop for a Black American is relatively unremarkable on its own, the background context that the interaction \emph{could} have turned deadly is likely to result in some level of trauma for Black drivers.
+Recent work from Hannah Walker (\protect\hyperlink{ref-Walker2020}{2020a}, \protect\hyperlink{ref-Walker2020a}{2020b}) argues that this could lead to a \emph{mobilizing} effect, if stopped drivers understand their contact with the criminal legal system in the context of a narrative of racial injustice, such contact can actually mobilize.
+She explains: ``experiences with punitive policies are subject to interpretation and, when understood through narratives of injustice, lead to wholly different participation outcomes than we usually predict'' (\protect\hyperlink{ref-Walker2020}{Walker 2020a, 132}).
 While she finds that this sense of injustice is especially likely to increase political participation in non-voting ways (such as attending a protest or signing a petition), the logic could extend to electoral participation as well given a relevant electoral context, strong injustice narrative, or relatively weak contact with the criminal legal system.
-Findings presented in \protect\hyperlink{ref-Laniyonu2019}{Laniyonu} (\protect\hyperlink{ref-Laniyonu2019}{2019}) provide support for this concept: concentrated Stop, Question, and Frisk (SQF) policing in New York City neighborhoods was associated with reduced turnout in federal midterm elections but increased turnout in presidential and mayoral primary elections.
-Laniyonu also uncovered an association regarding candidate choice---he demonstrates higher turnout for a candidate who opposed SQF policing and lower turnout for a candidate who supported it.
-In other words, low-level police contact mobilized voters to participate in a local election (which could plausibly affect police practices).
 
-Despite the growing body of high-quality scholarship on the democratic implications of the American criminal legal system, we still know remarkably little about the effects of the most routine sort of contact---police stops and tickets that do not result in an arrest.
+Given that police stops are more likely to be traumatic for Black motorists (because traffic stops come with a threat of escalation into racialized police violence, because they received harsher punishments, \emph{or} because the stop itself was discriminatory) \emph{and} that there exists a framework available for translating negative experiences with the criminal legal system into political action, we expect police stops to have unique participatory consequences for Black Americans.
 
-\hypertarget{race-and-fines-and-fees-practices}{%
-\subsection*{Race and fines and fees practices}\label{race-and-fines-and-fees-practices}}
-\addcontentsline{toc}{subsection}{Race and fines and fees practices}
-
-Fines and fees are situated in a distinct historical legacy of racist exploitation that may uniquely facilitate a collective ``sense of injustice'' among Black Americans---the sort of collective perception that \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020b}) argues could prove to be politically mobilizing.
-
-Cedric Robinson's articulation of racial capitalism offers a useful theoretical framework for interpreting the trajectory of American anti-Black political economy (\protect\hyperlink{ref-Robinson2000}{Robinson 2000}).
-Brittany Friedman theorizes fines and fees as a ``progression of racial capitalism penology,'' emphasizing the centrality of carceral immobility and financial capture in contemporary fines and fees practices (\protect\hyperlink{ref-Friedman2020}{Friedman 2020}: 177).
-Robinson argues that European industrial capitalism continued a longer political-economic trend of differentiating racial groups in order to dispossess them and exploit their labor.
-
-Following the Civil War and the rise of global industrial capitalism, slave patrols were replaced by more formal police forces (\protect\hyperlink{ref-EqualJusticeInitiative2017}{Initiative 2017}; \protect\hyperlink{ref-Hinton2021}{Hinton and Cook 2021}).
-The implementation of the Black Codes, convict leasing, and sharecropping systems marked a transition to a new stage of racial capitalism, wherein criminalization provided an easily-exploited labor supply that offset costs that the state incurred by coercing their labor (\protect\hyperlink{ref-Lichtenstein1996}{Lichtenstein 1996}; \protect\hyperlink{ref-Mancini1978}{Mancini 1978}).
-Contemporary fines and fees practices have been directly compared to sharecropping because both structures share ``a long-term pattern of financial exploitation based on race\ldots{} that limits the life-choices of the affected population'' (\protect\hyperlink{ref-Blessett2016}{Blessett and Box 2016}: 113).
-
-In the 20th century, residential segregation simultaneously fueled the racial wealth gap and ensured that criminalization was both spatially and racially concentrated (\protect\hyperlink{ref-Rothstein2017}{Rothstein 2017}; \protect\hyperlink{ref-Hinton2021}{Hinton and Cook 2021}).
-At the level of federal policy, racial threat and whites' attribution of criminality to Blackness (\protect\hyperlink{ref-Muhammad2010}{Muhammad 2010}) prompted a shift from the War on Poverty to the War on Crime wherein Black communities' demands for material security and safety were selectively amplified to promote increased and harsher policing and incarceration (\protect\hyperlink{ref-Hinton2017}{Hinton 2017}; \protect\hyperlink{ref-Vargas2017}{Vargas and McHarris 2017}).
-
-The 2008 financial crisis solidified the connection between fiscal austerity and policing, prompting a decline in tax revenues that devastated state and local governments---but law enforcement agencies were largely spared from cuts.
-At the local level, this means that police budgets today constitute about thirty percent of city budgets nationwide, and cities where residents have lower median incomes dedicate a larger proportion of spending to policing (\protect\hyperlink{ref-Friedman2020}{Friedman 2020}).
-Similarly, municipalities where a larger share of the population is Black raise more fines and fees revenue per-capita than less-Black municipalities (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}; \protect\hyperlink{ref-UnitedStatesCommissiononCivilRights2017}{United States Commission on Civil Rights 2017}).
-Although major urban centers collect high dollar amounts of fines and fees, some of the most egregious ticketing practices measured on a per-capita basis are concentrated in suburbs or smaller cities with municipal courts---Ferguson being a prominent example (\protect\hyperlink{ref-UnitedStatesDepartmentofJusticeCivilRightsDivision2015}{United States Department of Justice Civil Rights Division 2015}; \protect\hyperlink{ref-Mughan2020}{Mughan 2020}).
-In municipalities with substantial Black populations, then, people who are most heavily affected by criminalization are expected to foot the bill for their own mistreatment.
-\protect\hyperlink{ref-Sances2017}{Sances and You} (\protect\hyperlink{ref-Sances2017}{2017}), however, finds that the discriminatory imposition of tickets can be mitigated by descriptive representation (i.e.~Black elected officials): The positive association between cities' reliance on fines and fees and the proportion of Black residents is significantly diminished when Black communities are represented by at least one Black legislator (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
-This result aligns with recent research demonstrating that states with more Black legislators spend less on corrections budgets; that racial disparities in arrests are reduced in municipalities represented by a majority-nonwhite city council; and that descriptive representation can reduce racial disparities in the criminal legal system (\protect\hyperlink{ref-Butler2011}{Butler and Broockman 2011}; \protect\hyperlink{ref-Gunderson2020}{Gunderson 2020}; \protect\hyperlink{ref-Eckhouse2016}{Eckhouse 2016}).
-It thus seems that the ballot box can be a site from which Black Americans can secure some protections against the most egregious forms of revenue extraction.
-
-Racial capitalist political economy imposes fiscal constraints regardless of city officials' identities or intentions.
-In their study of fines and fees reliance in Chicago suburbs, Josh Pacewicz and John Robinson, III show how the racialization of municipal opportunity structures prevents majority-Black suburban governments from acquiring sufficient revenue from ``good'' sources such as sales taxes or property taxes, catalyzing a reliance on fines and fees to fund government services (\protect\hyperlink{ref-Pacewicz2020}{Pacewicz and Robinson 2020}).
-Pacewicz and Robinson III note that racialized municipal opportunity structures are tied to the political-historical processes of neoliberalism and fiscal austerity, an observation that aligns with recent scholarship detailing the origins of fees paid by incarcerated people (\protect\hyperlink{ref-Kirk2020}{Kirk, Fernandes, and Friedman 2020}).
-
-Today, fines and fees primarily target Black Americans: traffic stops and searches disproportionately affect Black motorists nationwide (\protect\hyperlink{ref-Pierson2020}{Pierson et al.
-2020}), and a host of local analyses confirm the national finding (\protect\hyperlink{ref-Dunn2009}{Dunn 2009}; \protect\hyperlink{ref-Goncalves2020}{Goncalves and Mello 2020}; \protect\hyperlink{ref-Mughan2020}{Mughan 2020}).
-In criminal court proceedings, Black defendants tend to face more severe monetary sanctions (\protect\hyperlink{ref-Edwards2020}{Edwards and Harris 2020}; \protect\hyperlink{ref-Harris2011}{A.
-Harris, Evans, and Beckett 2011}), and a 2020 Federal Reserve survey found that five percent of white respondents reported ``unpaid legal expenses, fines, or court costs,'' whereas twelve percent of Black respondents reported such debt (\protect\hyperlink{ref-BoardofGovernorsoftheFederalReserveSystem2020}{Governors of the Federal Reserve System 2020}).
-
-Research regarding police stops and searches in response to local fiscal crises shows how decreasing local revenues affect racist police practices.
-One study of all U.S.
-city governments found that local fiscal stress was related to increased ``revenue-generating arrests'' (e.g.~arrests involving civil asset forfeiture) and that Black and Hispanic people were arrested at higher rates (\protect\hyperlink{ref-Makowsky2009}{Makowsky and Stratmann 2009}).
-A study of four million North Carolina traffic stops found that fiscal stress caused a decrease in the probability of white drivers being searched, but no decrease for Black drivers (\protect\hyperlink{ref-Shoub2020}{Shoub et al.
-2020}).
-This suggests that higher reliance on fines and fees results in government officials and police targeting individuals who hold less political power---whether those individuals are out-of-state motorists or members of local marginalized communities (\protect\hyperlink{ref-Makowsky2009}{Makowsky and Stratmann 2009}).
-
-\hypertarget{theory}{%
-\section*{Theory}\label{theory}}
-\addcontentsline{toc}{section}{Theory}
-
-As the preceding sections make clear, past work on the political ramifications of criminal legal contact has largely determined that such contact is demobilizing.
-Scholars have argued that all contact with the criminal legal system causes political withdrawal, and that the severity of the withdrawal varies according to the intensity of the contact.
-This finding may not hold true for lower-level criminal legal contact, however.
-We argue that police ticketing may be an exception to this rule for two reasons: (1) police stops are far less disruptive to Americans' lives than arrests or periods of incarceration, and (2), the injustice narrative framework (\protect\hyperlink{ref-Walker2020a}{Walker 2020b}) indicates that the explicit politicization of police stops by the Black Lives Matter movement in recent years should be mobilizing for Black Americans.
-
-Receiving a ticket is a substantively different experience than being arrested or incarcerated.
-People who have been convicted of a crime and incarcerated are relegated to an alternate political membership status that Reuben Jonathan Miller and Forrest Stuart call ``carceral citizenship,'' subjecting them to forms of supervision and sanction ``that are otherwise unavailable to {[}people{]} who have not been accused of a crime'' (\protect\hyperlink{ref-Miller2017}{R.
-J.
-Miller and Stuart 2017}: 536).
-The politically discouraging effects of criminalization are even stronger for people who are convicted of felonies, who lose their right to vote in all but two U.S.
-states.
-This ``civil death'' (\protect\hyperlink{ref-Ewald2002}{Ewald 2002}; \protect\hyperlink{ref-Miller2012}{B.
-L.
-Miller and Spillane 2012}) explicitly removes Americans from the electorate; the felony conviction becomes ``a durable constraint and marker of their citizenship'' (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}: 133).
-The experience of formal legal exclusion from voting forms a powerful piece of the ``hidden curriculum'' (\protect\hyperlink{ref-Meares2017}{Meares 2017}) that teaches convicted individuals about their identities as citizens.
-Finally, the financial and social costs following a period of incarceration (\protect\hyperlink{ref-Bushway2007}{Bushway, Stoll, and Weiman 2007}) can make it less likely that citizens invest the time and energy into registering to vote, learning where their polling place is, and determining which candidates they support.
-
-While tickets can lead to driver's license suspensions or, in a smaller subset of cases, nonpayment incarceration, tickets are generally far less disruptive than criminal convictions and prison terms.
-Ticketed drivers are not disenfranchised, and they are not subject to the same forms of supervision and sanction that affect people with criminal convictions.
-Accordingly, individuals who have \emph{not} been subjected to such intense supervision may be less likely to avoid state institutions compared to formerly incarcerated people pursuing a ``strategic retreat.'' (\protect\hyperlink{ref-Brayne2014}{Brayne 2014}), In short, if higher-intensity contact with the criminal legal system leads to political withdrawal because of carceral control, surveillance, and resultant lessons about citizenship, these same arguments are unlikely to apply to ticketed individuals.
-
-This is not to say that ticketing should be considered completely distinct from more intense forms of criminalization, but rather that a ticketed individual has not yet been relegated to ``carceral citizenship.'' .
-Walker's research gives us reason to believe that drivers who feel that they were unfairly targeted by the police---and link that unfair experience to broader social narratives---can be \emph{mobilized} by that experience.
-Moreover, given political organizing in recent years specifically about the racial injustices of discriminatory traffic stops, this injustice narrative is likely particularly accessible---and mobilizing---for Black Americans.
-
-The rise of the Black Lives Matter movement in 2013 constitutes a significant development for the political socialization of Black Americans, and many early Black Lives Matter protests either occurred in municipalities with exploitative ticketing practices or directly followed traffic stops that escalated into police violence (\protect\hyperlink{ref-Holpuch2015}{Holpuch 2015}; \protect\hyperlink{ref-LaFraniere2016}{LaFraniere and Smith 2016}).
-The movement garnered national attention and momentum during the Ferguson protests in 2014, where racially discriminatory ticketing practices were particularly egregious.
-It is possible that Black Lives Matter facilitated a more robust and prevalent linked-fate political analysis among Black Americans during the time frame of our analysis---the movement arose shortly after fines and fees became a more salient and widespread threat to Black Americans' material security, and the BLM movement helped to publicize these disparities.
-The injustice narrative framework proposed by \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020b}) explains how individuals connect their ``micro'' experience of criminal legal contact with the ``macro'' narrative of racially discriminatory policing.
-
-The financially exploitative nature of recent ticketing increases should be particularly fertile ground for robust injustice narratives.
-One Buffalo, New York resident who is a plaintiff in a lawsuit regarding racist ticketing practices told a local newspaper in 2019: ``In my mind, they weren't balancing the budgets for Black lives, but with Black lives'' (\protect\hyperlink{ref-McLeod2019}{McLeod 2019}).
-The city created a new traffic violations agency in 2015, spurring its yearly ticketing numbers to jump from around 32,000 to over 52,000.
-
-We argue that many of the factors leading to withdrawal associated with higher-level criminal legal contact should not apply to police stops.
-At the same time, we expect that the national BLM movement should have encouraged Black Americans stopped by the police to connect their experience to macro-level trends, and that this should encourage political behaviors such as voting.
-Simply put, we expect that police stops are far less demobilizing than higher-level contact, and that they may in fact be mobilizing for Black Americans in an era of increased awareness of racially disparate policing practices.
+At the same time, the average Black American already knows far more about the criminal legal system due to the extreme racial disparities in policing and incarceration.
+As one 2015 study observed, 44\% of Black women (and 32\% of Black men) have a family member in prison.
+These numbers compare with just 12\% and 6\% for white women and men, respectively (\protect\hyperlink{ref-Lee2015}{Lee et al.
+2015}).
+Black Americans' disproportionate contact with the criminal legal system is a firmly established fact at this point.
+This greater baseline exposure could mean that Black Americans have less to ``learn'' from a marginal police stop, resulting in smaller turnout effects.
 
@@
 
-We leverage three distinct approaches to ask whether ticketing and police stops structure voter turnout, and whether these effects are unique for Black Americans.
-Our theoretical estimand (\protect\hyperlink{ref-Lundberg2021}{Lundberg, Johnson, and Stewart 2021}) is the effect of police ticketing on the political socialization of ticketed individuals, which we proxy using their voter turnout.
+We leverage two distinct approaches to ask whether police traffic stops affect voter turnout, and whether these effects are unique for Black Americans.
 
@@
 
-We include two supplementary analyses to test the generalizability of the results from Hillsborough County.
-First, we analyze change in municipal-level revenue from fees and fines and voter turnout, which allows us to expand our analysis outside of Hillsborough County to about nine thousand American municipalities.
-This test does not allow us to directly observe the causal mechanism we argue is at play (police stops influencing political socialization, which in turn drives individual voter turnout), and replaces individual ticketing events with less-precise budget data.
-Also, if interpreted in isolation, the municipal-level analysis would suffer from the ecological fallacy: it is possible that any observed relationship between fees and fines collections and municipal turnout is being driven by the behavior of voters other than those who are ticketed.
-
-Finally, data from the 2020 American National Election Studies allow us to observe how tickets and arrests differentially influence voting behavior at the individual level among a nationally representative sample, but survey data analysis is subject to the vulnerabilities detailed in our introduction (e.g.~measurement bias).
+Data from the 2020 American National Election Studies allow us to observe how tickets and arrests differentially influence voting behavior at the individual level among a nationally representative sample, but survey data analysis is subject to the vulnerabilities detailed in our introduction (e.g.~measurement bias).
 Nevertheless, it provides important national insight into the phenomena we observe locally in Hillsborough County.
 
-Taken together, these approaches dramatically advance our understanding of the political consequences of the most routine types of contact with the criminal legal system.
+Taken together, these approaches advance our understanding of the political consequences of the most routine types of contact with the criminal legal system.
 
-\hypertarget{individual-level-causal-effects-of-ticketing}{%
-\subsection*{Individual-Level Causal Effects of Ticketing}\label{individual-level-causal-effects-of-ticketing}}
-\addcontentsline{toc}{subsection}{Individual-Level Causal Effects of Ticketing}
+\hypertarget{individual-level-causal-effects-of-traffic-stops}{%
+\subsection*{Individual-Level Causal Effects of Traffic Stops}\label{individual-level-causal-effects-of-traffic-stops}}
+\addcontentsline{toc}{subsection}{Individual-Level Causal Effects of Traffic Stops}
 
@@
 \protect\hyperlink{ref-Meredith2014}{Meredith and Morse} (\protect\hyperlink{ref-Meredith2014}{2014}) develops a test for assessing the prevalence of false-positives in administrative record matching.
-We present the results of that test in the Supplementary Information.
+We present the results of that test in section 1 of the Supplementary Information (SI).
 We likely have a false-positive match of around 0.03 percent, a figure we consider too low to impact our results meaningfully.
@@
 Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status (see \protect\hyperlink{ref-Nyhan2017}{Nyhan, Skovron, and Titiunik 2017}).
-Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.\textsuperscript{1} We thus observe virtually all individuals who were registered to vote at any time during our period of study.
+Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.\footnote{Because such frequent snapshots are not available from L2, we here use the registered voter file made freely available by the state of Florida.} We thus observe virtually all individuals who were registered to vote at any time during our period of study.
 Unique voter identification numbers allow us to avoid double-counting voters who are registered in multiple snapshots.
@@
 
-By matching the police stop and voter records, we identify all voters who were ticketed between the 2012 and 2020 general elections (voters stopped between 2018 and 2020 elections serve only as controls).
+By matching the police stop and voter records, we identify all voters who were stopped between the 2012 and 2020 general elections (voters stopped between 2018 and 2020 elections serve only as controls).
 We collect self-reported information regarding the race of each voter from Florida's public voter file rather than the police stop data.
-Voters are considered ``treated'' in the general election following their ticket.
+Voters are considered ``treated'' in the general election following their stop.
 Treated voters are then matched to a control voter using a nearest-neighbor approach, with a genetic algorithm used to determine the best weight for each characteristic (\protect\hyperlink{ref-Sekhon2011}{Sekhon 2011}).
@@
 
-We assume that after controlling for observable characteristics, past turnout, \emph{and} the unobservable characteristics associated with receiving a ticket, the timing of the ticket is effectively random.
-In short, any turnout difference between the treated voters and their controls is the causal effect of a police stop on turnout.
-Our overall turnout effects are robust to much weaker assumptions: in the Supplementary Information, we demonstrate that our overall turnout results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
+We assume that after controlling for observable characteristics, past turnout, \emph{and} the unobservable characteristics associated with experiencing a traffic stop, the timing of the stop is effectively random.
+This is conceptually similar to the regression discontinuity in time framework, and we assume that any turnout difference between the treated voters and their controls is the causal effect of a police stop on turnout.
+Our overall turnout effects are robust to much weaker assumptions: in section 2 of the SI, we demonstrate that our overall turnout results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
 
@@
 
-\hypertarget{voter-turnout-and-municipal-fines-and-fees-collections}{%
-\subsection*{Voter turnout and municipal fines and fees collections}\label{voter-turnout-and-municipal-fines-and-fees-collections}}
-\addcontentsline{toc}{subsection}{Voter turnout and municipal fines and fees collections}
-
-Next, we turn to our nationwide analysis of the relationship between municipal revenue raised from fees and fines and turnout.
-Our data come from two primary sources: the US Census Bureau's Census of Governments Data (COG), and registered voter files from L2 Political.
-
-\textbf{Census of Governments}: Every five years, the US Census Bureau collects data from governmental bodies around the country.
-We use two waves of the COG: one that covers the years 2008 -- 2012, and another that covers 2013 -- 2017.
-The COG asks municipalities to report how much revenue they collect from ``penalties imposed for violation of law; civil penalties (e.g., for violating court orders); court fees if levied upon conviction of a crime or violation\ldots{} and forfeits of deposits held for performance guarantees or against loss or damage (such as forfeited bail and collateral).'' We divide these amounts by the population to estimate the per-capita fees and fines revenue raised in each municipality.
-This data has been used as a proxy for the amount of tickets issued at the local level in scholarly research (see, for instance, \protect\hyperlink{ref-Goldstein2020}{Goldstein, Sances, and You 2020}; \protect\hyperlink{ref-Sances2017}{Sances and You 2017}).
-
-The COG data are useful to isolate ticketing practices because other fines and fees (e.g.~fines imposed at sentencing in state court, probation fees, conviction fees, public defender fees) are typically collected by county or state governments.
-The COG data only include local revenues, which means the share of fines revenue corresponds more directly to local police practices.
-Following the guidance of \protect\hyperlink{ref-Sances2017}{Sances and You} (\protect\hyperlink{ref-Sances2017}{2017}), we retain only municipalities with police and/or court systems, as these are the only municipalities capable of issuing tickets.
-We also only retain municipalities with populations of at least 2,500.
-
-\textbf{Registered Voter Files}: The COG data do not include estimates of turnout at the local level.
-To estimate local turnout, we leverage registered voter files provided by data vendor L2 Political.
-In Washington, DC, and every state in the country (with the exception of North Dakota) voters are required to register to vote prior to participating.
-These files are considered public record, and in most states contain information about each voter's age, residential address, political affiliation, and participation history.
-L2 collects voter files from around the country and merges them with proprietary data that estimates other voter- and household-level characteristics such as race and education.
-The individual-level records are aggregated up to the municipality level to determine the number of ballots cast for members of each race; these estimates are divided by 5-year citizen voting age population (CVAP) estimates from the Census Bureau to calculate turnout.
-As we show in the Supplementary Information, the L2 racial estimates closely track the municipal-level racial estimates from the Census Bureau.
-Because our turnout numerator and denominators come from different sources, there is slight measurement error: our estimate indicates, for instance, that roughly 1 percent of municipalities had Black turnout above 100 percent.
-Where more votes were cast than the Census estimate for CVAP, we recode turnout as 100 percent.
-Our results do not change if we instead simply remove these municipalities, or use unmodified turnout estimates.
-
-\textbf{Estimation Strategy}: We begin by merging each municipality's fees and fines per capita (that is, dollars per resident) from the 2012 COG to its turnout from the 2014 midterm election, and the 2017 COG to its 2018 turnout.
-Because this measure is highly right-skewed, we use the natural log of fees and fines per capita (plus 1, to account for municipalities that collected no fees and fines).
-We also control for other municipal and state characteristics: racial composition, population density, median income, collegiate education, median age, and share of the population over 64 years of age from the 5-year American Community Survey ending in 2014 and 2018, and total municipal revenue, share of revenue that comes from taxes, and share of each municipality's revenue that comes from the state or federal government in the 2012 and 2017 COGs.
-We retain the 8,954 municipalities whose data is reported to the COG in both 2012 and 2017 and meet the other criteria noted above; these constitute the target population.
-
-The 5-year cycle of the COG does not neatly line up with the general 4-year cycle typical of American elections.
-The timing of the COG and midterm elections mean that our analytical strategy is conservative.
-If municipalities shift their fees and fines collections dramatically over the 2013 -- 2017 period, this shift may influence their 2014 turnout.
-However, we assume that turnout in 2014 will still be influenced by the policing practices of the 2008 -- 2012 period, while 2018 turnout will be largely influenced by the practices of the 2013 -- 2017 period.
-
-We run a two-way fixed effects model to explore whether changes in fees and fines collections from 2012 to 2017 were associated with changes in turnout, and whether these effects differed for Black and non-Black voters.
-
 \hypertarget{national-survey-data}{%
@@
 We use these survey questions to make descriptive inferences about how stops and arrests affect the voting behavior of the general population.
-The first descriptive theoretical estimand is the gap between the voter turnout rate of individuals who were recently stopped by the police or who have ever been arrested, and another is whether stops or arrests uniquely influence the political behavior of Black Americans.
+The first descriptive estimand is the gap between the voter turnout rate of individuals who were recently stopped by the police or who have ever been arrested, and another is whether stops or arrests uniquely influence the political behavior of Black Americans.
 In addition to the respondent's contact with the criminal legal system, we control for age; sex; income; education; party affiliation; self-described ideology; and reported 2016 turnout.
@@
 
-To directly observe the effect of being stopped by the police on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
-As discussed above, we match individuals who were ticketed between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.\textsuperscript{2} Matching is done with replacement and ties are not broken.
+To observe the effect of being stopped by the police on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
+As discussed above, we match individuals who were stopped between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.\footnote{Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
+The full sample is used in the actual matching process.} Matching is done with replacement and ties are not broken.
 This means that some treated voters have multiple controls; the regression weights are calculated to account for this possibility.
-In Table 1 we present the results of the matching algorithm.
+In Table \ref{tab:balance} we present the results of the matching algorithm.
 As the table demonstrates, the selected control voters are very similar to the treated voters.
@@
 
-\begin{figure}[!htb]
+\begin{figure}[H]
 
@@
 The empirical estimands are \emph{Treated × Post Treatment} and \emph{Treated × Post Treatment × Black}.
-In models 1 and 2, \emph{Treated × Post Treatment} measures the overall treatment effect, and in models 3 and 4 it measures the treatment effect for non-Black voters.
-\emph{Treated × Post Treatment × Black} measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
+In models 1 and 2, the coefficient on \emph{Treated × Post Treatment} measures the overall treatment effect, and in models 3 and 4 it measures the treatment effect for non-Black voters.
+The coefficient on \emph{Treated × Post Treatment × Black} measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
 
 \begin{singlespace}
-\input{"../temp/dind_reg_y.tex"}
+\input{"../temp/small_two_matches_reg_y_overall.tex"}
 \end{singlespace}
 
-As both Figure 1 and Table 2 make clear, police tickets meaningfully depressed turnout.
+As both Figure \ref{fig:did-1} and Table \ref{tab:dind-table} make clear, traffic stops meaningfully depressed turnout.
 In models 1 and 2, the estimated overall treatment effect is -1.5 percentage points.
-In models 3 and 4, we can see that a ticket was less demobilizing for Black individuals than for others---non-Black turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
+In models 3 and 4, we can see that a stop was less demobilizing for Black individuals than for others---non-Black turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
 Although the treatment effect is still substantively quite large for Black individuals, Hillsborough County Black voters' turnout in federal elections was not as negatively impacted by police contact as that of non-Black individuals.
-
-\hypertarget{municipal-level-results}{%
-\subsection*{Municipal-Level Results}\label{municipal-level-results}}
-\addcontentsline{toc}{subsection}{Municipal-Level Results}
-
-Before testing the causal effect of fees and fines collections on turnout, we begin with a cross-sectional analysis of the relationship using ordinary least squares.
-Here, we regress municipality-level turnout in 2018 against fees and fines collections as reported in the 2017 COG, as well as a number of other covariates.
-In Figure 2 we present the marginal effect of fees and fines on municipal-level turnout.
-The plot shows the results from two separate models: one in which the dependent variable is Black turnout (as a share of CVAP), and a second in which the dependent variable is non-Black turnout.
-The figure also marks the interdecile range.
-The full regression table can be found in the Supplementary Information.
-
-\begin{figure}[!htb]
-
-{\centering \includegraphics{draft_paper_files/figure-latex/cross-18-1}
-
-}
-
-\caption{\label{fig:mef-2018}Predicted Turnout, 2018}\label{fig:cross-18}
-\end{figure}
-
-As Figure 2 makes clear, turnout was lower for non-Black voters in municipalities with higher fees and fines collections per resident: it dropped by roughly 1.5 percentage points over the interdecile range, after controlling for the other covariates.
-The opposite is true for Black voters: over the same range, Black turnout \emph{increases} by roughly 2.4 percentage points.
-Both relationships are statistically significant at the 95 confidence level.
-This does not prove that higher fees and fines increase Black turnout; cross-sectional regressions cannot establish causality.
-Nevertheless, Figure 2 is consistent with this story.
-
-We turn now to our two-way fixed effects model.
-As discussed above, we retain each municipality that reported their fees and fines data to the COG in both 2012 and 2017 (and met the other criteria discussed in the \emph{Data and Design} section).
-The dependent variable in each model is calculated by dividing the number of ballots cast in 2014 and 2018 by the 5-year CVAP estimate from the same year.
-We run the two-way fixed effects on overall turnout, Black turnout, and non-Black turnout.
-The results of these models can be found in Table 3.
-The average municipality included in this analysis raised \$2.17 in fees and fines per resident in 2012, and the average municipality increased this per-capita figure by \$0.47 between 2012 and 2017.
-Just over 10\% of municipalities raised no revenue from fees and fines in either year.
-
-\begin{singlespace}
-\input{"../temp/2wfe_reg_clean.tex"}
-\end{singlespace}
-
-The results of the two-way fixed effects model are different from what we saw in the 2018 cross-sectional approach; namely, Table 3 indicates that higher fees and fines cause lower turnout among non-Black individuals, but do not significantly impact Black turnout.
-The estimated coefficient, however, is small: a 10 percent increase in fees and fines is associated with a decrease in turnout of about 0.04 percentage points.
+It is also clear that midterm turnout is more impacted by these stops---as we show in section 3 of the SI, the negative impact is statistically significant in all years for non-Black residents, but much smaller in 2016 (-0.6pp) than in 2014 (-1.9pp) or 2018 (-3.0pp),
 
@@
 Roughly 15 percent of non-Black respondents reported a police stop in the preceding 12 months, while the same was true for more than 22 percent of Black respondents.
-In Figure 3 we present the results of our econometric models.
+In Figure \ref{fig:anes} we present the results of our econometric models.
 In the left-hand panel, we show the predicted turnout of respondents who answered ``yes'' or ``no'' to the question \emph{During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?} The right-hand panel, meanwhile, plots these relationships for respondents who answered ``yes'' or ``no'' to the question \emph{Have you ever been arrested, or has that never happened to you?}.
 These are the predicted probabilities after controlling for respondents' race / ethnicity; age; party; ideology; income; education; and 2016 turnout.
-The full regression table can be found in the Supplementary Information..
+The full regression table can be found in section XX of the SI.
 
@@
 
-Figure 3 demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (\emph{p} = 0.005).
-The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (\emph{p} = 0.27).
+Figure \ref{fig:anes} demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (\emph{p} = 0.004).
+The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (\emph{p} = 0.07).
 Importantly, this effect is not a remnant of a white--nonwhite divide.
-As we show in the Supplementary Information, police stops were not differently related to turnout for Latinos than for non-Latinos; nor did they impact turnout differently for Asians than for non-Asians.
+As we show in the SI, police stops were not differently related to turnout for Latinos than for non-Latinos; nor did they impact turnout differently for Asians than for non-Asians.
 The ANES results point, then, to the fact that police stops are uniquely associated with higher turnout for Black respondents.
 
-The second panel of Figure 3 shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
+The second panel of Figure \ref{fig:anes} shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
 Importantly, the interaction between arrest status and the respondent's race was not statistically significant.
@@
 \hypertarget{discussion}{%
-\subsubsection*{Discussion}\label{discussion}}
-\addcontentsline{toc}{subsubsection}{Discussion}
+\section*{Discussion}\label{discussion}}
+\addcontentsline{toc}{section}{Discussion}
 
-While existing sociological and political science literature has examined the rise and collateral consequences of fines and fees as well as the effects of criminalization on political socialization, no study has investigated the causal relationship between ticketing and voter turnout.
-Additionally, our study is among the first to use individual-level administrative data to investigate the relationship between criminalization and political participation.
+While existing sociological and political science literature has examined the rise and collateral consequences of criminalization on political socialization, no study has investigated the causal relationship between ticketing and voter turnout using individual-level administrative data.
 
 Given how widespread police stops are and their relationship to racial injustice, their political implications demand close study.
-Accordingly, we investigate this question from a variety of perspectives, using multiple data sources and empirical approaches.
+Accordingly, we investigate this question using two different data sources and analytic strategies.
 What we find complicates our understanding of how lower-level police contact affects political participation.
-The national survey data and cross-sectional municipal-level analysis indicate that police contact is associated with higher turnout for Black Americans, and either unrelated or negatively related to turnout for others.
-Our causal models tell a slightly different story---they fail to uncover mobilizing effects for Black Americans.
-Nevertheless, our causal models \emph{do} indicate that police stops are less demobilizing for Black individuals than for others.
-In this sense, our results all point in the same direction.
-Based on these three independent approaches, we conclude that the political consequences of police stops are unique for Black Americans---and that they are less demobilizing for Black Americans than others.
+In the analysis of Hillsborough County police stops, we find that stops reduce the voter turnout of non-Black voters, with a smaller negative effect for Black voters.
+On the other hand, the descriptive analysis of national survey data indicates that police contact is associated with \emph{higher} turnout for Black Americans, and \emph{unrelated} to turnout for others.
+Despite this incongruence, both analyses indicate that police stops have different participatory effects for Black individuals than for others.
+In this sense, our results point in the same direction.
+We conclude that the political consequences of police stops are unique for Black Americans---and that they are less demobilizing for Black Americans than others.
 Additionally, as \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020b}) suggests, ticketed Black individuals may be politically mobilized for activities other than voting not observed in this study, such as contacting elected representatives or volunteering for campaigns.
+To that end, it is also worth noting that our causal analysis tests the effect of personal police contact rather than proximal contact, which was the focus of \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020b})---it could be the case that mobilizing effects of low-level police contact come from proximal exposure rather than personal.
 
-Our individual-level analysis based on Hillsborough County, Florida, advances our understanding of this dynamic while raising new questions.
-On the one hand, the causal results are highly robust, and the ticketing data allows us to identify the treatment fairly precisely.
-On the other hand, these are the only results in which police stops are associated with a \emph{decrease} in turnout for Black individuals.
-This may be because this analysis tests the impact of direct contact with the police, rather than direct \emph{or} proximal contact, as the ANES questions do.
-It may be because we can isolate the effect of a police stop from other, broader changes that may be correlated with increased fees and fines revenue in the municipal-level data.
-Or it may point to unique political circumstances surrounding race, policing, and political participation in Hillsborough County.
-We look forward to future scholarship that replicates and extends these Hillsborough County results.
-Nevertheless, that police stops are less demobilizing for Black Floridians in Hillsborough County---an effect that does not extend to other nonwhite residents---provides support for our general thesis that the political interpretation of these contacts with the criminal legal system are unique for Black Americans.
-
-The difference between the cross-sectional and two-way fixed effects models using the municipality-level data is somewhat surprising.
-There are a few potential explanations for this mismatch.
-First, compared to the individual-level analysis, our city-level analysis is much less sensitive to the temporal placement of treatment, which could explain why the city-level effect sizes in the two-way fixed effects models are smaller or not statistically significant.
-Along a similar vein, it is possible that a mobilizing effect of ticketing for Black voters in the city-level analysis is offset by higher-intensity forms of criminal legal contact, such as arrest and incarceration.
-The bulk of existing literature suggests that incarceration discourages political participation, and it is not unreasonable to assume that cities that ramp up ticketing of Black residents also ramp up arrest and incarceration of Black residents.
-If these phenomena coincide, that could explain why the city-level analysis produced no statistically significant effect for Black voters---the personally mobilizing effect of ticketing could be counterbalanced by the proximal chilling effect of incarceration, and because the city-level analysis is not as temporally sensitive, it is more difficult to isolate the effect of ticketing.
-At the same time, \protect\hyperlink{ref-Harris2020}{A.
-P.
-Harris, Ash, and Fagan} (\protect\hyperlink{ref-Harris2020}{2020}) indicates that when municipalities increase their fees and fines collections, relatively more \emph{white} individuals are ticketed.
-\protect\hyperlink{ref-Shoub2020}{Shoub et al.} (\protect\hyperlink{ref-Shoub2020}{2020}) demonstrates the corollary: when municipalities stop fewer motorists, the decrease is concentrated among white individuals.
-Existing research, then, indicates that a relatively constant share of the Black population is stopped by the police; changes in fees and fines collections largely impacts the white population.
-The overall changes in revenue we observe in our two-way fixed effects models might reflect changes largely for the white populations in these municipalities, while ticketing---and turnout---remain more or less constant for Black populations.
-We were unable to incorporate a race-specific measure of police stops or measures of local incarceration or policing trends due to a lack of consistent data nationwide.
-
-Finally, Sances and You (\protect\hyperlink{ref-Sances2017}{2017}: 1091)---the paper that originally detailed the relationship between fees and fines collections and municipalities' racial composition using the Census of Governments data---specifically notes that they did not exploit the panel setup of the COG because of ``little variation within a city in terms of revenues from fines.'' Instead, they present only the results of a cross-sectional study.
-Here, we present both the cross-sectional and panel results, acknowledging that each have limitations but that, taken together, they shed light on the unique politicization of fees and fines for Black Americans.
-
-Our findings have several implications for political sociology and political science scholarship.
+Our findings have several implications for political science scholarship.
 While existing literature suggests that the most disruptive forms of criminal legal contact (i.e.~criminal convictions and incarceration) consistently discourage voting (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}; \protect\hyperlink{ref-Burch2011}{Burch 2011}; \protect\hyperlink{ref-White2019a}{White 2019b}), research regarding police stops has produced more mixed results (\protect\hyperlink{ref-Laniyonu2019}{Laniyonu 2019}).
-We extend this theory to police ticketing, the most common form of police contact in America, and find that ticketing generally reduces turnout.
-For Black voters, however, our findings suggest that ticketing can be politically mobilizing.
+We extend this theory to police ticketing, the most common form of police contact in America, and find that police traffic stops generally reduce turnout.
+For Black voters, however, our findings suggest that traffic stops are less demobilizing, a sharp contrast with existing scholarship wherein more disruptive forms of criminalization discourage Black voters more than non-Black voters.
 Particularly following the rise of the Black Lives Matter movement in 2013, our findings constitute new evidence in support of our theory that ticketing is distinct from other forms of criminal legal contact and therefore catalyzes different political behaviors among Black voters, who are disproportionately affected by both ticketing and criminalization in general.
 
-In this sense, our analysis points to a political contestation of criminal legal policy, a phenomenon that aligns with dozens of recent campaigns to reform local fines and fees practices (or abolish them entirely).\textsuperscript{3} We know that increased fines and fees result from political economy (i.e.~austerity at the federal level), but our analysis suggests that this is a ``two way street'' wherein people who are harmed by policing practices can be politically socialized into resistance.
+In this sense, our analysis could be consistent with a political contestation of criminal legal policy, a phenomenon that aligns with dozens of recent campaigns to reform local fines and fees practices (or abolish them entirely).\footnote{See \url{https://finesandfeesjusticecenter.org/clearinghouse}.} We know that increased fines and fees result from political economy (i.e.~austerity at the federal level), but our analysis suggests that this could be a ``two way street'' wherein people who are harmed by policing practices can be politically socialized into resistance.
 
-\textbf{Limitations}: Because our individual-level administrative data analysis is limited to Hillsborough County where fines collections increased over the period, we do not have a good sense of how the city-level revenue reliance trend interacts with the individual experience of being ticketed in areas where fees and fines are constant or decreasing.
-Is ticketing more politically mobilizing for Black voters in cities that are palpably dialing up their revenue collection efforts?
-Future research could test this hypothesis at the individual level within cities that either maintained constant fines and fees revenue reliance over time or reduced revenue reliance.
-
-Additionally, in our analysis of Hillsborough County voters, we do not look at people who were not registered to vote in 2018.
+\textbf{Limitations}: In our analysis of Hillsborough County voters, we do not look at people who were not registered to vote in 2018.
 Because we cannot tell whether unregistered individuals who were stopped in Hillsborough County were unregistered because they were \emph{ineligible} to do so (by virtue of living in a different county or being a non-citizen, for instance) or chose to eschew electoral politics, our analysis is necessarily limited to individuals who were registered to vote.
@@
 
-Finally, we are sensitive to the fact that although administrative data provides real-world evidence of actual behavior, such an approach limits our ability to understand the psychological processes in play.
+Finally, we are sensitive to the fact that although administrative data provides real-world evidence of actual behavior, such an approach limits our ability to understand the causal mechanisms in play.
 This means that although we demonstrate that police stops are demobilizing, future work must further investigate how stops are interpreted by individuals and translated into political behavior.
 
-Although we have generated new evidence suggesting that police stops and related exploitative ticketing practices may mobilize Black voters, we emphasize that this finding does not redeem or justify such police practices.
+Although we have contributed new evidence suggesting that police stops and related exploitative ticketing practices may not demobilize Black voters to the same extent as non-Black voters, we emphasize that this finding does not redeem or justify such police practices.
 Black Americans already suffer from disproportionate police contact and the racial wealth gap, and racist revenue-motivated ticketing only increases the burden on Black communities nationwide.
 Policymakers should work to ensure that Black Americans no longer have to struggle to enjoy the same political power as whites---to that end, the current trend of voting rights restriction policies across the country is especially pernicious.
-Even if Black Americans understand the ballot box as one tool they can use to limit the state's power to exploit and harm them, policymakers should still feel an obligation to support voting rights protections and stop disproportionate ticketing in Black communities.
-
-\newpage
-
-\hypertarget{notes}{%
-\section*{Notes}\label{notes}}
-\addcontentsline{toc}{section}{Notes}
-
-\textsuperscript{1} Because such frequent snapshots are not available from L2, we here use the registered voter file made freely available by the state of Florida.
-
-\textsuperscript{2} Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
-The full sample is used in the actual matching process.
-
-\textsuperscript{3} See \url{https://finesandfeesjusticecenter.org/clearinghouse}.
+Even if some Black Americans understand the ballot box as one tool they can use to limit the state's power to exploit and harm them, policymakers should still feel an obligation to support voting rights protections and stop disproportionate ticketing in Black communities.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Ang2021}{}%
+Ang, Desmond, Panka Bencsik, Jesse Bruhn, and Ellora Derenoncourt. 2021. {``Police {Violence Reduces Civilian Cooperation} and {Engagement} with {Law Enforcement}.''} \emph{Working Paper.}, September.
+
+\leavevmode\hypertarget{ref-Baumgartner2018}{}%
+Baumgartner, Frank R, Derek A Epp, and Kelsey Shoub. 2018. \emph{Suspect Citizens: What 20 Million Traffic Stops Tell Us about Policing and Race}.
+
 \leavevmode\hypertarget{ref-Bell2017}{}%
-Bell, Monica C. 2017. {``Police {Reform} and the {Dismantling} of {Legal Estrangement}.''} \emph{The Yale Law Journal} 126 (7): 2054--150. \url{http://www.jstor.org/stable/45222555}.
-
-\leavevmode\hypertarget{ref-Blessett2016}{}%
-Blessett, Brandi, and Richard Box.
-2016.
-{``Sharecropper {Finance}: {Using} the {Justice System} as a {Public Revenue Source}.''} \emph{Public Integrity} 18 (January): 113--26.
-\url{https://doi.org/10.1080/10999922.2015.1111742}.
+Bell, Monica C. 2017. {``Police {Reform} and the {Dismantling} of {Legal Estrangement}.''} \emph{The Yale Law Journal} 126 (7): 2054--150.
 
@@
 
-\leavevmode\hypertarget{ref-Bushway2007}{}%
-Bushway, Shawn D., Michael A.
-Stoll, and David Weiman.
-2007.
-\emph{Barriers to {Reentry}?: {The Labor Market} for {Released Prisoners} in {Post}-{Industrial America}}.
-{Russell Sage Foundation}.
-\url{http://books.google.com?id=YOeFAwAAQBAJ}.
-
-\leavevmode\hypertarget{ref-Butler2011}{}%
-Butler, Daniel M., and David E.
-Broockman.
-2011.
-{``Do {Politicians Racially Discriminate Against Constituents}?
-{A Field Experiment} on {State Legislators}.''} \emph{American Journal of Political Science} 55 (3): 463--77.
-\url{https://doi.org/10.1111/j.1540-5907.2011.00515.x}.
-
 \leavevmode\hypertarget{ref-CarpenterII2019}{}%
@@
 {``The {Price} of {Taxation} by {Citation}: {Case Studies} of {Three Georgia Cities That Rely Heavily} on {Fines} and {Fees}.''} {Institute for Justice}.
-
-\leavevmode\hypertarget{ref-Colgan2019}{}%
-Colgan, Beth A. 2019. {``Wealth-{Based Penal Disenfranchisement}.''} \emph{Vanderbilt Law Review} 72 (January). \url{https://papers.ssrn.com/abstract=3312439}.
 
@@
 
-\leavevmode\hypertarget{ref-Dunn2009}{}%
-Dunn, Ronnie A.
-2009.
-{``Measuring {Racial Disparities} in {Traffic Ticketing Within Large Urban Jurisdictions}.''} \emph{Public Performance \& Management Review} 32 (4): 537--61.
-\url{https://doi.org/10.2753/PMR1530-9576320403}.
+\leavevmode\hypertarget{ref-Desmond2020}{}%
+---------. 2020. {``Evidence of the {Effect} of {Police Violence} on {Citizen Crime Reporting}.''} \emph{American Sociological Review} 85 (1): 184--90. \url{https://doi.org/10.1177/0003122419895979}.
 
-\leavevmode\hypertarget{ref-Eckhouse2016}{}%
-Eckhouse, Laurel. 2016. {``Descriptive {Representation} and {Political Power}: {Explaining Racial Inequalities} in {Policing}.''} \emph{(Unpublished Manuscript)}.
+\leavevmode\hypertarget{ref-Epp2014}{}%
+Epp, Charles R., Steven Maynard-Moody, and Donald P. Haider-Markel. 2014. \emph{Pulled {Over}}. {The University of Chicago Press}.
 
-\leavevmode\hypertarget{ref-Edwards2020}{}%
-Edwards, Frank, and Alexes Harris. 2020. {``An {Analysis} of {Court Imposed Monetary Sanctions} in {Seattle Municipal Courts}, 2000-2017.''} August. \url{https://doi.org/10.31235/osf.io/ajpqc}.
+\leavevmode\hypertarget{ref-Gerber2015}{}%
+Gerber, Alan S., Gregory A.
+Huber, Marc Meredith, Daniel R.
+Biggers, and David J.
+Hendry.
+2015.
+{``Can {Incarcerated Felons Be} ({Re})integrated into the {Political System}?
+{Results} from a {Field Experiment}.''} \emph{American Journal of Political Science} 59 (4): 912--26.
+\url{https://doi.org/10.1111/ajps.12166}.
 
-\leavevmode\hypertarget{ref-Ewald2002}{}%
-Ewald, Alec C. 2002. {``'{Civil} Death': {The} Ideological Paradox of Criminal Disenfranchisement Law in the {United States}.''} \emph{Wisconsin Law Review} 2002 (5): 1045--1137.
+\leavevmode\hypertarget{ref-Gerber2017}{}%
+---------.
+2017.
+{``Does {Incarceration Reduce Voting}?
+{Evidence} about the {Political Consequences} of {Spending Time} in {Prison}.''} \emph{The Journal of Politics} 79 (4): 1130--46.
+\url{https://doi.org/10.1086/692670}.
 
-\leavevmode\hypertarget{ref-Friedman2020}{}%
-Friedman, Brittany.
-2020.
-{``Carceral {Immobility} and {Financial Capture}: {A Framework} for the {Consequences} of {Racial Capitalism Penology} and {Monetary Sanctions}.''} \emph{UCLA Criminal Justice Law Review} 4 (1).
-\url{https://escholarship.org/uc/item/31r669wf}.
-
-\leavevmode\hypertarget{ref-Goldstein2020}{}%
-Goldstein, Rebecca, Michael W.
-Sances, and Hye Young You.
-2020.
-{``Exploitative {Revenues}, {Law Enforcement}, and the {Quality} of {Government Service}.''} \emph{Urban Affairs Review} 56 (1): 5--31.
-\url{https://doi.org/10.1177/1078087418791775}.
-
-\leavevmode\hypertarget{ref-Goncalves2020}{}%
-Goncalves, Felipe, and Steven Mello.
-2020.
-{``A {Few Bad Apples}?
-{Racial Bias} in {Policing}.''} SSRN Scholarly Paper ID 3627809.
-{Rochester, NY}: {Social Science Research Network}.
-\url{https://doi.org/10.2139/ssrn.3627809}.
-
-\leavevmode\hypertarget{ref-BoardofGovernorsoftheFederalReserveSystem2020}{}%
-Governors of the Federal Reserve System, Board of.
-2020.
-{``Report on the {Economic Well}-{Being} of {U}.{S}.
-{Households} in 2019, {Featuring Supplemental Data} from {April} 2020.''} {Federal Reserve System}.
-\url{https://www.federalreserve.gov/publications/report-economic-well-being-us-households.htm}.
-
-\leavevmode\hypertarget{ref-Gunderson2020}{}%
-Gunderson, Anna.
-2020.
-{``Representation, {Incorporation}, and {Corrections Spending}: {The Counterbalancing Effect} of {Black Political Incorporation}.''} \emph{Journal of Race, Ethnicity, and Politics} 5 (3): 573--603.
-\url{https://doi.org/10.1017/rep.2020.15}.
-
-\leavevmode\hypertarget{ref-Harris2010}{}%
-Harris, Alexes, Heather Evans, and Katherine Beckett.
-2010.
-{``Drawing {Blood} from {Stones}: {Legal Debt} and {Social Inequality} in the {Contemporary United States}.''} \emph{American Journal of Sociology} 115 (6): 1753--99.
-\url{https://doi.org/10.1086/651940}.
-
-\leavevmode\hypertarget{ref-Harris2011}{}%
----------.
-2011.
-{``Courtesy {Stigma} and {Monetary Sanctions}: {Toward} a {Socio}-{Cultural Theory} of {Punishment}.''} \emph{American Sociological Review} 76 (2): 234--64.
-\url{https://doi.org/10.1177/0003122411400054}.
+\leavevmode\hypertarget{ref-Harrell2020}{}%
+Harrell, Erika, and Elizabeth Davis. 2020. {``Contacts {Between Police} and the {Public}, 2018 - {Statistical Tables}.''} {Bureau of Justice Statistics}.
 
@@
 
-\leavevmode\hypertarget{ref-Hinton2017}{}%
-Hinton, Elizabeth. 2017. \emph{From the {War} on {Poverty} to the {War} on {Crime}: {The Making} of {Mass Incarceration} in {America}}. {Harvard University Press}.
-
-\leavevmode\hypertarget{ref-Hinton2021}{}%
-Hinton, Elizabeth, and DeAnza Cook.
-2021.
-{``The {Mass Criminalization} of {Black Americans}: {A Historical Overview}.''} \emph{Annual Review of Criminology} 4 (1): 261--86.
-\url{https://doi.org/10.1146/annurev-criminol-060520-033306}.
-
-\leavevmode\hypertarget{ref-Holpuch2015}{}%
-Holpuch, Amanda.
-2015.
-{``Walter {Scott}: Protesters Demand Justice -- and an End to Police Discrimination.''} \emph{The Guardian: US News}, April 8, 2015.
-\url{http://www.theguardian.com/us-news/2015/apr/08/protesters-demand-justice-walter-scott-north-charleston}.
-
 \leavevmode\hypertarget{ref-Imai2020}{}%
@@
 2020.
-{``Matching {Methods} for {Causal Inference} with {Time}-{Series Cross}-{Sectional Data}.''} \emph{Working Paper}.
+{``Matching {Methods} for {Causal Inference} with {Time-Series Cross-Sectional Data}.''} \emph{Working Paper}.
 \url{https://doi.org/Matching\%20Methods\%20for\%20Causal\%20Inference\%20with\%20Time-Series\%20Cross-Sectional\%20Data}.
 
-\leavevmode\hypertarget{ref-EqualJusticeInitiative2017}{}%
-Initiative, Equal Justice. 2017. {``Lynching in {America}: {Confronting} the {Legacy} of {Racial Terror}.''} \url{https://lynchinginamerica.eji.org/report/}.
+\leavevmode\hypertarget{ref-Jones2019}{}%
+Jones, Alexi, and Wendy Sawyer. 2019. {``Arrest, Release, Repeat: {How} Police and Jails Are Misused to Respond to Social Problems.''} {Prison Policy Initiative}.
 
@@
 
-\leavevmode\hypertarget{ref-Kirk2020}{}%
-Kirk, Gabriela, April Fernandes, and Brittany Friedman.
-2020.
-{``Who {Pays} for the {Welfare State}?
-{Austerity Politics} and the {Origin} of {Pay}-to-{Stay Fees} as {Revenue Generation}.''} \emph{Sociological Perspectives} 63 (6): 921--38.
-\url{https://doi.org/10.1177/0731121420967037}.
-
-\leavevmode\hypertarget{ref-LaFraniere2016}{}%
-LaFraniere, Sharon, and Mitch Smith.
-2016.
-{``Philando {Castile Was Pulled Over} 49 {Times} in 13 {Years}, {Often} for {Minor Infractions}.''} \emph{The New York Times: U.S.}, July 16, 2016.
-\url{https://www.nytimes.com/2016/07/17/us/before-philando-castiles-fatal-encounter-a-costly-trail-of-minor-traffic-stops.html}.
-
 \leavevmode\hypertarget{ref-Laniyonu2019}{}%
 Laniyonu, Ayobami. 2019. {``The {Political Consequences} of {Policing}: {Evidence} from {New York City}.''} \emph{Political Behavior} 41 (2): 527--58. \url{https://doi.org/10.1007/s11109-018-9461-9}.
+
+\leavevmode\hypertarget{ref-Lee2015}{}%
+Lee, Hedwig, Tyler McCormick, Margaret T.
+Hicken, and Christopher Wildeman.
+2015.
+{``Racial {Inequalities} in {Connectedness} to {Imprisoned Individuals} in the {United States}.''} \emph{Du Bois Review: Social Science Research on Race} 12 (2): 269--82.
+\url{https://doi.org/10.1017/S1742058X15000065}.
 
@@
 
-\leavevmode\hypertarget{ref-Lichtenstein1996}{}%
-Lichtenstein, Alexander C. 1996. \emph{Twice the {Work} of {Free Labor}}. {Verso}. \url{https://www.versobooks.com/books/738-twice-the-work-of-free-labor}.
+\leavevmode\hypertarget{ref-Levenson2021}{}%
+Levenson, Michael. 2021. {``Pulled {Over}: {What} to {Know About Deadly Police Traffic Stops}.''} \emph{The New York Times}, October.
 
@@
 
-\leavevmode\hypertarget{ref-Makowsky2009}{}%
-Makowsky, Michael D., and Thomas Stratmann.
-2009.
-{``Political {Economy} at {Any Speed}: {What Determines Traffic Citations}?''} \emph{The American Economic Review} 99 (1): 509--27.
-\url{http://www.jstor.org/stable/29730194}.
-
-\leavevmode\hypertarget{ref-Mancini1978}{}%
-Mancini, Matthew J. 1978. {``Race, {Economics}, and {The Abandonment} of {Convict Leasing}.''} \emph{The Journal of Negro History} 63 (4): 339--52. \url{https://doi.org/10.2307/2716851}.
-
-\leavevmode\hypertarget{ref-Manza2006}{}%
-Manza, Jeff, and Christopher Uggen. 2006. \emph{Locked Out: Felon Disenfranchisement and {American} Democracy}. Studies in Crime and Public Policy. {Oxford ; New York}: {Oxford University Press}.
-
 \leavevmode\hypertarget{ref-McCoy2015}{}%
-McCoy, Terrence.
-2015.
-{``Ferguson Shows How a Police Force Can Turn into a Plundering {`Collection Agency'}.''} \emph{Washington Post}, March 5, 2015.
-\url{https://www.washingtonpost.com/news/morning-mix/wp/2015/03/05/ferguson-shows-how-a-police-force-can-turn-into-a-plundering-collection-agency/}.
-
-\leavevmode\hypertarget{ref-McLeod2019}{}%
-McLeod, Marsha.
-2019.
-{``City {Hall} Cashing in on Traffic Tickets.''} {Investigative Post}.
-February 27, 2019.
-\url{https://www.investigativepost.org/2019/02/27/city-hall-cashing-in-on-traffic-tickets/}.
+McCoy, Terrence. 2015. {``Ferguson Shows How a Police Force Can Turn into a Plundering {`Collection Agency'}.''} \emph{Washington Post}, March.
 
@@
 2014.
-{``Do {Voting Rights Notification Laws Increase Ex}-{Felon Turnout}?''} \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 220--49.
+{``Do {Voting Rights Notification Laws Increase Ex-Felon Turnout}?''} \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 220--49.
 \url{https://doi.org/10.1177/0002716213502931}.
 
-\leavevmode\hypertarget{ref-Miller2012}{}%
-Miller, Bryan Lee, and Joseph F.
-Spillane.
-2012.
-{``Civil Death: {An} Examination of Ex-Felon Disenfranchisement and Reintegration.''} \emph{Punishment \& Society} 14 (4): 402--28.
-\url{https://doi.org/10.1177/1462474512452513}.
+\leavevmode\hypertarget{ref-Meredith2015}{}%
+---------.
+2015.
+{``The {Politics} of the {Restoration} of {Ex-Felon Voting Rights}: {The Case} of {Iowa}.''} \emph{Quarterly Journal of Political Science} 10 (1): 41--100.
+\url{https://doi.org/10.1561/100.00013026}.
 
-\leavevmode\hypertarget{ref-Miller2017}{}%
-Miller, Reuben Jonathan, and Forrest Stuart.
-2017.
-{``Carceral {Citizenship}: {Race}, {Rights} and {Responsibility} in the {Age} of {Mass Supervision}.''} \emph{Theoretical Criminology} 21 (4): 532--48.
-\url{https://doi.org/10.1177/1362480617731203}.
+\leavevmode\hypertarget{ref-Morris2020}{}%
+Morris, Kevin.
+2020.
+{``Neighborhoods and {Felony Disenfranchisement}: {The Case} of {New York City}.''} \emph{Urban Affairs Review}, May, 1078087420921522.
+\url{https://doi.org/10.1177/1078087420921522}.
+
+\leavevmode\hypertarget{ref-Morris2021a}{}%
+---------.
+2021a.
+{``Welcome {Home}{{Now Vote}}!
+{Voting Rights Restoration} and {Postsupervision Participation}.''} \emph{Social Science Quarterly} 102 (1): 140--53.
+\url{https://doi.org/10.1111/ssqu.12901}.
 
 \leavevmode\hypertarget{ref-Morris2021}{}%
-Morris, Kevin.
-2021.
+---------.
+2021b.
 {``Turnout and {Amendment Four}: {Mobilizing Eligible Voters Close} to {Formerly Incarcerated Floridians}.''} \emph{American Political Science Review}, April, 1--16.
 \url{https://doi.org/10.1017/S0003055421000253}.
-
-\leavevmode\hypertarget{ref-Mughan2020}{}%
-Mughan, Siân.
-2020.
-{``Municipal {Reliance} on {Fine} and {Fee Revenues}: {How Local Courts Contribute} to {Extractive Revenue Practices} in {U}.{S}.
-{Cities}.''} \emph{Public Budgeting \& Finance}, December.
-\url{https://doi.org/10.1111/pbaf.12277}.
-
-\leavevmode\hypertarget{ref-Muhammad2010}{}%
-Muhammad, Khalil Gibran.
-2010.
-\emph{The {Condemnation} of {Blackness} --- {Khalil Gibran Muhammad} \textbar{} {Harvard University Press}}.
-{Harvard University Press}.
-\url{https://www.hup.harvard.edu/catalog.php?isbn=9780674238145}.
 
@@
 2020.
-{``Pocketbook Policing: {How} Race Shapes Municipal Reliance on Punitive Fines and Fees in the {Chicago} Suburbs.''} \emph{Socio-Economic Review}, October.
+{``Pocketbook Policing: {How} Race Shapes Municipal Reliance on Punitive Fines and Fees in the {Chicago} Suburbs.''} \emph{Socio-Economic Review}, no.
+mwaa029 (October).
 \url{https://doi.org/10.1093/ser/mwaa029}.
-
-\leavevmode\hypertarget{ref-Pierson2020}{}%
-Pierson, Emma, Camelia Simoiu, Jan Overgoor, Sam Corbett-Davies, Daniel Jenson, Amy Shoemaker, Vignesh Ramachandran, et al.
-2020.
-{``A Large-Scale Analysis of Racial Disparities in Police Stops Across the {United States}.''} \emph{Nature Human Behaviour} 4 (7, 7): 736--45.
-\url{https://doi.org/10.1038/s41562-020-0858-1}.
 
@@
 \url{https://doi.org/10.1177/2378023118761434}.
-
-\leavevmode\hypertarget{ref-Robinson2000}{}%
-Robinson, Cedric J. 2000. \emph{Black {Marxism}: The {Making} of the {Black Radical Tradition}}. {University of North Carolina Press}. \url{https://uncpress.org/book/9780807848296/black-marxism/}.
-
-\leavevmode\hypertarget{ref-Rothstein2017}{}%
-Rothstein, Richard.
-2017.
-\emph{The Color of Law: A Forgotten History of How Our Government Segregated {America}}.
-First edition.
-{New York ; London}: {Liveright Publishing Corporation, a division of W.
-W.
-Norton \& Company}.
 
@@
 \leavevmode\hypertarget{ref-Sanders2017}{}%
-Sanders, Topher, and Benjamin Conarck.
-2017.
-{``Florida {Police Issue Hundreds} of {Bad Pedestrian Tickets Every Year Because They Don}'t {Seem} to {Know} the {Law}.''} \emph{ProPublica}, December 20, 2017.
-\url{https://www.propublica.org/article/florida-police-issue-hundreds-of-bad-pedestrian-tickets-every-year-because-they-dont-seem-to-know-the-law?token=CpfrqXaMuR8UnJ5-FryRkVwuKl3C98Ae}.
+Sanders, Topher, and Benjamin Conarck. 2017. {``Florida {Police Issue Hundreds} of {Bad Pedestrian Tickets Every Year Because They Don}'t {Seem} to {Know} the {Law}.''} \emph{ProPublica}, December.
 
@@
 \leavevmode\hypertarget{ref-Shaer2019}{}%
-Shaer, Matthew.
-2019.
-{``How {Cities Make Money} by {Fining} the {Poor}.''} \emph{The New York Times: Magazine}, January 8, 2019.
-\url{https://www.nytimes.com/2019/01/08/magazine/cities-fine-poor-jail.html}.
-
-\leavevmode\hypertarget{ref-Shoub2020}{}%
-Shoub, Kelsey, Leah Christiani, Frank R.
-Baumgartner, Derek A.
-Epp, and Kevin Roach.
-2020.
-{``Fines, {Fees}, {Forfeitures}, and {Disparities}: {A Link Between Municipal Reliance} on {Fines} and {Racial Disparities} in {Policing}.''} \emph{Policy Studies Journal}.
-\url{https://doi.org/10.1111/psj.12412}.
+Shaer, Matthew. 2019. {``How {Cities Make Money} by {Fining} the {Poor}.''} \emph{The New York Times}, January.
 
@@
 2017.
-{``Police {Are Our Government}: {Politics}, {Political Science}, and the {Policing} of {Race}--{Class Subjugated Communities}.''} \emph{Annual Review of Political Science} 20 (1): 565--91.
+{``Police {Are Our Government}: {Politics}, {Political Science}, and the {Policing} of {Race}{{Class Subjugated Communities}}.''} \emph{Annual Review of Political Science} 20 (1): 565--91.
 \url{https://doi.org/10.1146/annurev-polisci-060415-093825}.
+
+\leavevmode\hypertarget{ref-Stuart2016}{}%
+Stuart, Forrest.
+2016.
+{``Becoming {`{Copwise}'}: {Policing}, {Culture}, and the {Collateral Consequences} of {Street-Level Criminalization}.''} \emph{Law \& Society Review} 50 (2): 279--313.
+\url{https://doi.org/10.1111/lasr.12201}.
 
@@
 \url{https://doi.org/10.1111/jels.12055}.
-
-\leavevmode\hypertarget{ref-Uggen2020}{}%
-Uggen, Christopher, Ryan Larson, Sarah Shannon, and Arleth Pulido-Nava.
-2020.
-{``Locked {Out} 2020: {Estimates} of {People Denied Voting Rights Due} to a {Felony Conviction}.''} Research report.
-{The Sentencing Project}.
-\url{https://www.sentencingproject.org/wp-content/uploads/2020/10/Locked-Out-2020.pdf}.
 
@@
 
-\leavevmode\hypertarget{ref-UnitedStatesCommissiononCivilRights2017}{}%
-United States Commission on Civil Rights. 2017. {``Targeted {Fines} and {Fees Against Communities} of {Color}.''} \url{https://www.usccr.gov/pubs/2017/Statutory_Enforcement_Report2017.pdf}.
-
 \leavevmode\hypertarget{ref-UnitedStatesDepartmentofJusticeCivilRightsDivision2015}{}%
-United States Department of Justice Civil Rights Division.
-2015.
-{``Investigation of the {Ferguson Police Department}.''} \url{https://www.justice.gov/sites/default/files/opa/press-releases/attachments/2015/03/04/ferguson_police_department_report.pdf}.
-
-\leavevmode\hypertarget{ref-Vargas2017}{}%
-Vargas, Robert, and Philip McHarris.
-2017.
-{``Race and {State} in {City Police Spending Growth}: 1980 to 2010.''} \emph{Sociology of Race and Ethnicity} 3 (1): 96--112.
-\url{https://doi.org/10.1177/2332649216650692}.
+United States Department of Justice Civil Rights Division. 2015. {``Investigation of the {Ferguson Police Department}.''}
 
@@
 
+\leavevmode\hypertarget{ref-Zoorob2020}{}%
+Zoorob, Michael.
+2020.
+{``Do {Police Brutality Stories Reduce} 911 {Calls}?
+{Reassessing} an {Important Criminological Finding}.''} \emph{American Sociological Review} 85 (1): 176--83.
+\url{https://doi.org/10.1177/0003122419895254}.
+
 \end{CSLReferences}

### 2022-04-19 markdown/jop_note.Rmd
submissions

--- 2022-04-19 markdown/draft_paper.Rmd
@@
 abstract: |
-  The American criminal legal system is an important site of political socialization: scholars have shown that criminal legal contact reduces turnout, and that criminalization pushes people away from public institutions more broadly.
-Despite this burgeoning literature, few analyses directly investigate the causal effect of *lower-level* police contact on voter turnout.
-We use two approaches to do so: we leverage both individual-level administrative ticketing data from Hillsborough County, Florida, and responses to the American National Election Studies.
-We estimate that a traffic stop decreases an individual’s likelihood of voting by 1.7 percentage points, but depressive effects are smaller for Black residents.
-The survey data, however, show that Black people who report that they or a family member were recently stopped by police are *more* likely to vote than those who reported no such contact.
-Taken together, our results indicate that low-level contact with police may have participatory consequences.
-
-  |
-  |
-  **Keywords**: voting, policing, race, punishment, political participation
+  TJT
 ---
@@
 
-# Introduction {-}
-
-Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities’ alienation from government [@Sanders2017; @McCoy2015; @Shaer2019].
-After Michael Brown was killed by the Ferguson Police Department in 2014, a US Department of Justice investigation into the city’s police and courts demonstrated that the municipality was engaged in a practice that advocates now refer to as “policing for profit.” The city’s reliance on fines and fees to fund government functions grew from 13 to 23 percent of the total budget between fiscal years 2012 and 2015.
-From 2012 to 2014, the Department of Justice found that 85 percent of vehicle stops, 90 percent of citations, and 93 percent of arrests targeted Black people.
-By contrast, just two-thirds of Ferguson’s residents are Black [@UnitedStatesDepartmentofJusticeCivilRightsDivision2015].
-
-It wasn’t just a Ferguson problem, or even a Missouri problem.
-American cities’ reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services [@Singla2020; @Harris2017; @Harris2020].
-
-Although scholars have examined the collateral consequences of this increased reliance on fines and fees [@Sances2017; @Pacewicz2020], comparatively few have explored the moment during which such revenue-raising actually occurs: namely, in the individual interactions between residents and the police via the issuance of a ticket.
-This “moment” of low-level contact has also been relatively understudied by scholars investigating the participatory consequences of contact with the criminal legal system.
-Work exploring how criminalization directly and indirectly influences political participation has exploded in recent years.
-Scholars have found that criminal legal contact (i.e.
-arrest, conviction, incarceration) consistently discourages voting [@Weaver2010; @Burch2011; @White2019a].
-Such work has largely focused on the effects of highly disruptive contact with the criminal legal system such as incarceration and felony convictions [@Burch2014; @Lee2014].
-While ticketing involves potentially negative interactions with the state, it does not necessarily carry the disruptive consequences of a felony conviction and might thus politicize Americans in unique ways.
-Building on recent theoretical work from @Walker2020a, this paper theorizes how local police practices affect voting behavior among ticketed individuals and provides precisely estimated evidence of a causal effect.
-
-Our project represents the first use of individual-level administrative data to identify the causal effect of traffic stops on voter behavior.
-The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures political participation.
-Past work looking at the individual-level effects of low-level contact has relied on survey or qualitative data [e.g.
-@Walker2014; @Weaver2010].
-Existing research allows for the testing of specific psychological mechanisms and personal interpretations of criminal legal contact, but does not allow us to generalize more broadly.
-As Weaver and Lerman [-@Weaver2010: 821] note, it may also introduce measurement bias.
-Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to a traffic stop.
-The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of a quarter-million individuals stopped over a 6 year period---a far larger pool than even the most robust surveys.
-
-We use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were stopped between the 2012 and 2018 elections.
-By matching individual voters who were stopped to similar voters who were stopped at later points and running a difference-in-differences model, we estimate the causal effect of these stops on turnout.
-This borrows from the logic of regression discontinuities in time: conditional on observable characteristics *and* unobservable factors associated with being ticketed, the timing of the ticket on either side of election day is essentially as-if random.
-We find that being stopped reduces the chance that an individual will turn out in the subsequent election, but that this effect is smaller for Black voters.
-
-To test the generalizability of our findings in Hillsborough County, we conduct a novel analysis of 2020 national survey data regarding voters’ experience with police stops.
-We find that Black respondents who reported personal or proximal experience with police stops in the last 12 months are more likely to vote than Black people who did not, while we find no statistically significant relationship between stops and voting among non-Black respondents.
-While the survey data present some drawbacks relative to the individual-level administrative data, their national scope provides helpful corroboration for the unique turnout effects of traffic stops for Black Americans observed in Hillsborough County.
-
-We demonstrate that police ticketing practices---the most widespread form of police contact in America---substantially reduce the turnout of non-Black American voters, but have a unique effect on Black voter turnout.
-Our findings complicate existing theories of how criminalization politically socializes Americans, and Black Americans in particular [@Weaver2010].
-Additionally, while many forms of criminalization have been found to contribute to a well-documented subjective experience of alienation or group-level exclusion among Black Americans [@Bell2017; @Stuart2016; @Desmond2016; @Zoorob2020; @Desmond2020; @Ang2021], our contribution emphasizes the need for further research regarding how different forms of criminalization affect group-level perceptions of government and resultant political behaviors.
-Our findings are relevant for interdisciplinary scholars of crime, race, politics, municipal finance, and policing.
-
-# Criminal Legal System and Citizen Identity {-}
-
-In recent years, scholars have paid more attention to the political implications of the American criminal legal system.
-Evolving in part out of a literature focused on street-level bureaucrats, researchers across the social sciences are asking how daily interactions with agents of the carceral state shape Americans’ relationships to themselves, their communities, and their state.
-As @Soss2017 argues, this “second face” of the state---“the activities of governing institutions and officials that exercise social control and encompass various modes of coercion, containment, repression, surveillance, regulation, predation, discipline, and violence” (567)---is the primary way through which many class-race subjugated communities develop their political knowledge.
-“[I]nterviewees have looked, not to City Hall, Congress, or political parties,” they write, “but rather to their direct experiences with police, jails and prisons, welfare offices, courts, and reentry agencies as they sought to ground their explanations of how government works, what political life is like for them, and how they understand their own political identities” [@Soss2017, 574].
-
-Recent work has explored the production of this political knowledge in increasingly sophisticated ways, using both qualitative and quantitative approaches.
-@Lerman2014’s pathbreaking book *Arresting Citizenship* set the table for future research.
-Their project combined extensive interviews of individuals living in areas closely monitored by the criminal legal system with novel survey data to probe the political consequences of what they term the “carceral state.” Their work indicates that citizens nearly uniformly react negatively to police and carceral supervision---from low-level interactions to lengthy periods of incarceration, Americans subjected to the second face of the state apparently withdraw from political participation.
-They find that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) [@Weaver2010].
-New evidence related to ticketing and legal estrangement has recently emerged: in a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government compared to residents who were not ticketed [@CarpenterII2019].
-
-Sarah Brayne [-@Brayne2014] found related results in her analysis of survey data.
-As the intensity of criminal legal contact escalates , people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions.
-She calls this phenomenon “system avoidance,” and while her analysis did not specifically assess voting behavior, her findings demonstrate how criminal legal contact can discourage Americans’ participation in public institutions as well as how the effect may vary alongside the intensity of criminal legal intervention.
-Similarly, @Remster2018a finds that men who return home from prison are more likely to avoid contact with their childrens’ schools.
-Vesla Weaver and colleagues describe this form of self-preserving withdrawal from public institutions as a “strategic retreat” [@Weaver2020].
-
-These findings can be situated in a process that sociologist Monica Bell calls “legal estrangement,” which captures those perceptions and cultural attitudes (“legal cynicism”) as well as the historical-structural conditions that produced them [@Bell2017].
-Research on legal cynicism has found that public perceptions of abusive police practices can reduce willingness to report crimes or cooperate with law enforcement [@Tyler2014].
-The “hidden curriculum” [@Justice2014; @Meares2017] of the criminal legal system teaches Americans about their identities as citizens---even parts of their identities that have little to do with policing or incarceration.
-
-# Administrative Data and the Causal Effects of Criminalization {-}
-
-Many scholars have turned to administrative data in recent years to explore the actual effects of contact with the criminal legal system on political participation in the voting booth.
-To be sure, administrative data have limitations: they are not ideally suited to probe the psychological, social, relational, and other mechanisms leading some citizens to vote and others to abstain.
-These limitations, however, are balanced by offering researchers precise estimates of actual---and not just reported---turnout.
-
-Traci Burch [-@Burch2011] was among the earliest scholars to match voter-file records with records detailing citizens’ contact with the criminal legal system.
-Her work complicated a previously dominant theory postulating that the turnout and party registration of formerly incarcerated individuals was largely driven by their sociodemographic characteristics but not their formal conviction or supervision [see, for instance, @Uggen2002].
-She argues that citizens who are convicted of felony offenses are less likely to vote, and less likely to register with a party, than citizens with similar sociodemographic characteristics without such a conviction.
-
-Other scholars have similarly matched corrections records with registered voter files to explore the effect of contact with the second face of the state.
-@White2019a finds that short periods of incarceration reduce Black, but not white, turnout.
-@Gerber2017 similarly finds relatively small effects of incarceration on turnout.
-Meredith and Morse [-@Meredith2014; -@Meredith2015] and @Gerber2015 explore the turnout effect of notifying formerly incarcerated citizens of the legal restoration of their voting rights, with mixed results, while @Morris2021a shows that restoring voting rights to individuals while they are still on parole increases post-supervision turnout.
-Other work has explored the “spillover” effects of such contact, finding that the political behavior of family members [@White2019] and neighbors [@Burch2014; @Morris2020] can be influenced by indirect contact with incarceration.
-@Morris2021 argues that these effects are durable, showing that citizens whose household members had been to prison were not disproportionately mobilized by a ballot initiative promising to end felony disenfranchisement.
-
-This burgeoning literature using administrative data has given scholars far greater insight into the participatory consequences of American incarceration.
-It is, however, virtually silent on the effects of *lower level* contact with the criminal legal system.
-Far more Americans have low-level contact with the police than will ever spend a night behind bars: just under 20 million Americans experience a traffic stop each year, whereas approximately five million Americans are arrested and jailed each year [@Harrell2020; @Jones2019].
-Despite the fact that so many more citizens are subjected to traffic stops, we know comparatively little about its political ramifications, a lack that is particularly glaring given how much we have learned in recent years about higher-level contact.
-
-The one project that has used administrative data to explore the political implications of low-level police contact is @Laniyonu2019, which explores the effects of the Stop, Question, and Frisk (SQF) program in New York City.
-@Laniyonu2019’s causal estimates rely on a cross-sectional matching model to compare voter turnout in precincts with *high* SQF activity to turnout in precincts with similar sociodemographic characteristics but *low* SQF activity, supplemented with cross-sectional analyses of all precincts in the city.
-His results paint a complicated picture: his causal estimates find that high levels of SQF increased turnout in the 2008 presidential election, but decreased it in the 2010 midterms.
-While @Laniyonu2019 marks an important step forward in the investigation of the consequences of policing for political behavior, it faces certain data and methodological limitations.
-Because the SQF data does not include identifying information about the individuals stopped, he cannot explore the turnout of New Yorkers who were actually subjected to SQF.
-Thus, as he notes in the conclusion, “the ability of the analysis to make causal claims is limited” (554) by the cross-sectional matching approach.
-
-In this project, we seek to extend our understanding of the political consequences of routine contact with the state’s second face.
-Combining an individual-level administrative panel dataset with national survey data gives us new insight into how traffic stops can shape citizens’ engagement with their democracy.
-
-# How Police Stops Might Structure Turnout {-}
-
-Much of the existing work on the turnout consequences of the criminal legal system points to a process of political learning or political socialization.
-@Lerman2014 finds that individuals in highly surveilled neighborhoods learn that the government does not care about them, and is uninterested in soliciting their participation.
-They note that more than half of individuals stopped by the police report agreeing with the statement “the leaders in government care very little about people like me,” compared with just a third of respondents with no police contact (150).
-The numbers, however, were far higher for individuals convicted of a crime, of whom three-quarters agreed with the statement.
-Learning about the criminal legal system takes place over a long period of time.
-Could isolated police stops that neither require sustained contact with the criminal legal system nor (generally) impose punishments as severe as incarceration politically socialize Americans to the same degree as incarceration?
-
-On one hand, it might seem unlikely that a single stop would produce much new knowledge about the state.
-For many Americans, a traffic stop amounts to little more than a slap on the wrist.
-To be sure, fines and fees can wreak havoc on the lives of some drivers.
-If a ticket leads to a suspended driver’s license, the initial stop can snowball into a much bigger life event that could jeopardize employment, or lead to shorter stints of incarceration for individuals apprehended driving on a suspended license.
-Searches conducted during traffic stops may also lead to arrest or incarceration if a police officer finds contraband in the vehicle.
-These comparatively less frequent cases might have consequences more akin to those associated with a brief period of incarceration that can also threaten employment.
-Nevertheless, the average traffic stop is certainly less disruptive than the average period of incarceration, perhaps producing less political knowledge and therefore impacting turnout less.
-
-On the other hand, a far larger set of Americans are stopped by the police than sent to jail or prison each year.
-According to the American National Election Study, a nationally-representative survey we use later in this study, the incomes and education levels for individuals stopped by the police are meaningfully higher than for individuals who report ever having been arrested.
-Motorists stopped by police are apparently systematically different compared to people who experience incarceration.
-Traffic stops might thus be the primary way some of these Americans learn about the criminal legal system.
-If these Americans have not already “learned” about the system from their neighborhoods or family members, the political consequences of such newly gleaned knowledge might be large.
-
-Traffic stops might provide early insights about the criminal legal system even for Americans who live in more heavily-policed areas.
-As @Gerber2017 notes in their study arguing that the participatory consequences of incarceration might be small, incarceration “is an outcome that often follows a long series of interactions with the criminal justice system” (1145).
-In other words, much of what the criminal legal system “teaches” might have already been learned by the time an individual is sent to prison.
-Someone who is stopped by the police, however, might have had fewer negative interactions with the state.
-Put differently, stopped individuals might have more to learn than incarcerated individuals with a long history of police contact, resulting in higher turnout effects.
-
-# Potential for Racially Disparate Effects {-}
-
-The potential for more “learning” from a police stop seems especially salient for Black Americans, particularly in recent years.
-National news over the 2010s was filled with the names of Black Americans who were killed during routine police stops.
-The Black Lives Matter movement gained national attention in the aftermath of the Ferguson uprising, an uprising sparked by the police killing of Michael Brown but also fueled by that city’s racial discriminatory ticketing practices.
-In the fall of 2021, *The New York Times* ran an extensive report exploring police killings that occur during traffic stops, providing more proof of their racially disparate nature [@Levenson2021].
-
-We expect that the participatory consequences of such a stop will be different for Black than non-Black Americans.
-First, traffic stops differ in meaningful ways for Black and non-Black Americans.
-As @Baumgartner2018 notes, Black Americans are more likely than whites to receive both “light” (i.e., a warning without a ticked) *and* “severe” (i.e., arrest) outcomes from a traffic stop.
-Although this may seem paradoxical at first, the authors explain: “while many might rejoice in getting a warning rather than a ticket, the racial differences consistently apparent in the data suggest another interpretation for black drivers: even the officer recognized that there was no infraction” [88].
-Black drivers are also more likely to be searched and arrested, but less likely to be found with contraband [@Baumgartner2018].
-Similarly, @Epp2014 argues that traffic stops are particularly instructive for Black Americans, as pretextual traffic stops politically socialize Black voters to the specific context of discriminatory police ticketing.
-
-The politicization of a police stop can occur differently for Black Americans through other avenues as well.
-The BLM movement has raised the salience of racially disparate policing across the country, as have the tragic stories of individuals like Philando Castile who was killed during a police stop.
-Routine interactions with the police are also more likely to turn deadly for Black Americans than for others [@Levenson2021].
-Thus, even if an individual police stop for a Black American is relatively unremarkable on its own, the background context that the interaction *could* have turned deadly is likely to result in some level of trauma for Black drivers.
-Recent work from Hannah Walker [-@Walker2020; -@Walker2020a] argues that this could lead to a *mobilizing* effect, if stopped drivers understand their contact with the criminal legal system in the context of a narrative of racial injustice, such contact can actually mobilize.
-She explains: “experiences with punitive policies are subject to interpretation and, when understood through narratives of injustice, lead to wholly different participation outcomes than we usually predict” [@Walker2020, 132].
-While she finds that this sense of injustice is especially likely to increase political participation in non-voting ways (such as attending a protest or signing a petition), the logic could extend to electoral participation as well given a relevant electoral context, strong injustice narrative, or relatively weak contact with the criminal legal system.
-
-Given that police stops are more likely to be traumatic for Black motorists (because traffic stops come with a threat of escalation into racialized police violence, because they received harsher punishments, *or* because the stop itself was discriminatory) *and* that there exists a framework available for translating negative experiences with the criminal legal system into political action, we expect police stops to have unique participatory consequences for Black Americans.
-
-At the same time, the average Black American already knows far more about the criminal legal system due to the extreme racial disparities in policing and incarceration.
-As one 2015 study observed, 44% of Black women (and 32% of Black men) have a family member in prison.
-These numbers compare with just 12% and 6% for white women and men, respectively [@Lee2015].
-Black Americans’ disproportionate contact with the criminal legal system is a firmly established fact at this point.
-This greater baseline exposure could mean that Black Americans have less to “learn” from a marginal police stop, resulting in smaller turnout effects.
-
-# Data and Design {-}
-
-We leverage two distinct approaches to ask whether police traffic stops affect voter turnout, and whether these effects are unique for Black Americans.
-
-Each approach offers advantages and drawbacks.
-Our individual-level analysis in Hillsborough County exploits unusually detailed public data, which allows for a precise causal analysis that cannot be conducted in counties that do not provide ticketing records with personally identifiable information or states that do not include self-reported race data in the voter file.
-The empirical estimand is the voter turnout gap between Hillsborough County residents who have recently been ticketed and residents who will be ticketed in a future period, conditional on similar turnout in past elections and similar demographic characteristics.
-In isolation, however, results from one county may not be generalizable to other U.S.
-counties.
-
-Data from the 2020 American National Election Studies allow us to observe how tickets and arrests differentially influence voting behavior at the individual level among a nationally representative sample, but survey data analysis is subject to the vulnerabilities detailed in our introduction (e.g.
-measurement bias).
-Nevertheless, it provides important national insight into the phenomena we observe locally in Hillsborough County.
-
-Taken together, these approaches advance our understanding of the political consequences of the most routine types of contact with the criminal legal system.
-
-## Individual-Level Causal Effects of Traffic Stops {-}
-
-First, we turn to individual-level data from Hillsborough County, Florida (home to Tampa). 
-Hillsborough County makes a unique set of data publicly available.
-The county clerk makes information available about every traffic stop in the county going back to 2003.
-This data includes the name and date of birth of the individual stopped; the date of the offense; the amount the individual paid for a ticket; and other information.
-
-To identify ticketed voters, we match the first and last names and dates of birth from the stop data against the Hillsborough County registered voter file.
-@Meredith2014 develops a test for assessing the prevalence of false-positives in administrative record matching.
-We present the results of that test in section 1 of the Supplementary Information (SI).
-We likely have a false-positive match of around 0.03 percent, a figure we consider too low to impact our results meaningfully.
-
-Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status [see @Nyhan2017].
-Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.^[Because such frequent snapshots are not available from L2, we here use the registered voter file made freely available by the state of Florida.] We thus observe virtually all individuals who were registered to vote at any time during our period of study.
-Unique voter identification numbers allow us to avoid double-counting voters who are registered in multiple snapshots.
-We retain each voter’s earliest record, and geocode voters to their home census block groups.
-Because we argue that police contact is the driving force behind any turnout effect, we remove tickets issued by red-light cameras.
-
-By matching the police stop and voter records, we identify all voters who were stopped between the 2012 and 2020 general elections (voters stopped between 2018 and 2020 elections serve only as controls).
-We collect self-reported information regarding the race of each voter from Florida’s public voter file rather than the police stop data.
-Voters are considered “treated” in the general election following their stop.
-Treated voters are then matched to a control voter using a nearest-neighbor approach, with a genetic algorithm used to determine the best weight for each characteristic [@Sekhon2011].
-Control voters are individuals who are stopped in the two years following the post-treatment election of the treated voters.
-Put differently, if a voter is stopped between 2012 and 2014, their control voter must be an individual stopped between the 2014 and 2016 elections.
-A voter cannot both be a treated and control voter for the same election; therefore, someone stopped between the 2012 and 2014 elections and again between the 2014 and 2016 elections cannot serve as a control for anyone stopped between 2012 and 2014.
-We limit the target population to voters who are stopped at some point in order to account for unobserved characteristics that motivate people who are stopped at some point to turn out at higher rates than people who are never stopped.
-
-We match voters on individual-level characteristics (race / ethnicity; gender; party affiliation; age; number of traffic stops prior to the treatment period) and block group-level characteristics from the 2012 5-year ACS estimates (median income; share of the population with some college; unemployment rate).
-We match exactly on the type of ticket (civil / criminal infraction; whether they paid a fine; whether they were stopped by the Tampa Police Department) to ensure that treated and control voters receive the same treatment.
-Finally, we match treated and control voters on their turnout in the three pre-treatment elections.
-
-We assume that after controlling for observable characteristics, past turnout, *and* the unobservable characteristics associated with experiencing a traffic stop, the timing of the stop is effectively random.
-This is conceptually similar to the regression discontinuity in time framework, and we assume that any turnout difference between the treated voters and their controls is the causal effect of a police stop on turnout.
-Our overall turnout effects are robust to much weaker assumptions: in section 2 of the SI, we demonstrate that our overall turnout results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
-
-Our analytical design thus incorporates two different causal approaches in order to improve the credibility of our identification assumptions.
-Leveraging pre-treatment turnout allows us to estimate a traditional difference-in-differences model, while the matching procedure improves the plausibility of the parallel trends assumption by reducing salient differences between the treated and control voters.
-For a more detailed discussion of how matching can improve upon traditional difference-in-difference approaches when using panel data, see @Imai2020.
-
-We then estimate the following equation:
-
-\begin{gather}
-\label{eq:1}
-v_{it}=\beta_0+\beta_1Treated_{i}+\beta_2Post Treatment_{t} + \nonumber \\
-\beta_3Treated_{i}\times Post Treatment_{t} + \\
-\beta_4Year_{t} + \delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
-\end{gather}
-
-Individual *i*'s turnout (*v*) in year *t* is a function of the year and whether they were stopped by the police.
-In the equation, *$\beta$~1~Treated~i~* measures the historical difference between treated voters and their controls.
-*$\beta$~2~Post Treatment~t~* measures whether turnout increased for controls in the first election following the treated voter’s stop, while *$\beta$~3~Treated~i~ × Post Treatment~t~* tests whether turnout changed differently for treated voters than their controls in the election following their police stop.
-*$\beta$~3~*, then, will capture the causal effect of a police stop on voter turnout; it is the unit-specific quantity measured in our empirical estimand [@Lundberg2021].
-*$\beta$~4~Year~t~* captures year fixed-effects depending on the timing of the police stop, and the matrix *$\delta$Z~i~* contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
-
-In some models, we also interact the treatment variable with a dummy indicating whether the voter is Black to determine race-specific treatment effects.
-
-## National Survey Data {-}
-
-Next, we turn to the American National Election Studies 2020 Time Series data (ANES).
-The ANES has been fielded in every presidential election year since 1948 and is among the most widely-used tools for understanding American’s political beliefs and behaviors, including their relationship with the criminal legal system [@Walker2020].
-It is weighted to be nationally representative of all American adults.
-In both 2016 and 2020, the ANES added new survey questions about respondent’s encounters with the police and the criminal legal system.
-We focus in particular on two questions: *During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?*, and *Have you ever been arrested, or has that never happened to you?* We include the roughly 87 percent of respondents that answered both questions, giving us a sample size of 7,347 respondents, of whom just over 11% identified as Black.
-
-We use these survey questions to make descriptive inferences about how stops and arrests affect the voting behavior of the general population.
-The first descriptive estimand is the gap between the voter turnout rate of individuals who were recently stopped by the police or who have ever been arrested, and another is whether stops or arrests uniquely influence the political behavior of Black Americans.
-In addition to the respondent’s contact with the criminal legal system, we control for age; sex; income; education; party affiliation; self-described ideology; and reported 2016 turnout.
-
-There is an important caveat to the use of the ANES survey---namely, while the police stop question asks whether the respondent *or anyone in their family* was stopped in the past year, the arrest question asks only about the individual respondent.
-While this may muddy the water between direct and proximal contact with the criminal legal system, we expect that the national survey data will give us some insight into the uniquely politicizing nature of police stops for Black Americans.
-
-# Results {-}
-
-As discussed above, we begin by examining whether the turnout of individuals stopped before an election was different from those stopped after the election in Hillsborough County, Florida.
-We also test the relationship between police stops and turnout in the 2020 election using survey data.
-
-## Individual-Level Results {-}
-
-To observe the effect of being stopped by the police on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
-As discussed above, we match individuals who were stopped between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.^[Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
-The full sample is used in the actual matching process.] Matching is done with replacement and ties are not broken.
-This means that some treated voters have multiple controls; the regression weights are calculated to account for this possibility.
-In Table \ref{tab:balance} we present the results of the matching algorithm.
-As the table demonstrates, the selected control voters are very similar to the treated voters.
-
-\begin{singlespace}
-\input{"../temp/balance_table.tex"}
-\end{singlespace}
-
-It is worth noting that voters who were stopped between 2012 and 2020 were far more likely to be Black and male than the general electorate, and live in Census block groups with moderately lower incomes.
-
-In Figure \ref{fig:did-1}, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped.
-In the top row, we present the turnout in 2008--2014 of the individuals stopped between 2012 and 2014 and their controls; the second row shows the 2010--2016 turnout for individuals stopped between 2014 and 2016 and their controls; and the third shows the treatment effect for those stopped in the 2 years prior to the 2018 midterms.
-Finally, in the bottom row, we present the overall turnout effects for these three elections.
-The first election following a treated voter’s stop is denoted as *t = 0* while the years in which *t* is less than zero are the periods prior to the stop.
-
-```{r did1, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/stopped_any_time_y.rds")
+```{r cross-18, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:mef-2018}Predicted Turnout, 2018", fig.pos = "H", fig.align = "center"}
+load("temp/mef_to.rdata")
 print(p2)
@@
 
-Figure \ref{fig:did-1} makes a number of things immediately apparent.
-First, we can see that for both Black and non-Black voters the pre-treatment trends are identical.
-This, combined with the fact that treated and control voters mirror one another in terms of other characteristics, lends credibility to the parallel trends assumption.
-Secondly, Figure \ref{fig:did-1} provides preliminary visual evidence of the demobilizing effects of police stops in Hillsborough County.
-However, as the figure also makes clear, it seems that the negative effects are concentrated in the lower-salience midterm elections; there is little evidence of turnout effects in the 2016 presidential election.
-
-Table \ref{tab:dind-table} formalizes the final row of Figure \ref{fig:did-1} into an ordinary least squares regression (the regression tables broken out for each year and including the coefficients for the matching covariates can be found in section 3 of the SI).
-Models 1 and 2 show our overall causal effect, while models 3 and 4 allow for the possibility that a ticket differentially mobilizes Black voters.
-In models 1 and 3, we include only the treatment, timing, and race dummies, while the full set of covariates used for the matching procedure are included in models 2 and 4.
-The empirical estimands are *Treated × Post Treatment* and *Treated × Post Treatment × Black*.
-In models 1 and 2, the coefficient on *Treated × Post Treatment* measures the overall treatment effect, and in models 3 and 4 it measures the treatment effect for non-Black voters.
-The coefficient on *Treated × Post Treatment × Black* measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
-
 \begin{singlespace}
-\input{"../temp/small_two_matches_reg_y_overall.tex"}
+\input{"../temp/2wfe_reg_clean.tex"}
 \end{singlespace}
-
-As both Figure \ref{fig:did-1} and Table \ref{tab:dind-table} make clear, traffic stops meaningfully depressed turnout.
-In models 1 and 2, the estimated overall treatment effect is -1.5 percentage points.
-In models 3 and 4, we can see that a stop was less demobilizing for Black individuals than for others---non-Black turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
-Although the treatment effect is still substantively quite large for Black individuals, Hillsborough County Black voters' turnout in federal elections was not as negatively impacted by police contact as that of non-Black individuals.
-It is also clear that midterm turnout is more impacted by these stops---as we show in section 3 of the SI, the negative impact is statistically significant in all years for non-Black residents, but much smaller in 2016 (-0.6pp) than in 2014 (-1.9pp) or 2018 (-3.0pp),
-
-## National Survey Data {-}
-
-In this section we make use of the American National Election Studies 2020 Time Series Data (ANES).
-The first test is simple: we ask whether, after controlling for standard covariates, having personal or proximal contact with a police stop in the previous 12 months is associated with whether a respondent voted in the 2020 presidential election.
-We also ask whether this relationship was different for Black and non-Black respondents.
-Finally, we use the ANES data to reconfirm prior literature demonstrating that higher-level contact with the criminal legal system is associated with lower turnout, as these relationships could have changed in the aftermath of the widespread protests following the police murder of George Floyd in 2020.
-
-Roughly 15 percent of non-Black respondents reported a police stop in the preceding 12 months, while the same was true for more than 22 percent of Black respondents.
-In Figure \ref{fig:anes} we present the results of our econometric models.
-In the left-hand panel, we show the predicted turnout of respondents who answered “yes” or “no” to the question *During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?* The right-hand panel, meanwhile, plots these relationships for respondents who answered “yes” or “no” to the question *Have you ever been arrested, or has that never happened to you?*.
-These are the predicted probabilities after controlling for respondents’ race / ethnicity; age; party; ideology; income; education; and 2016 turnout.
-The full regression table can be found in section XX of the SI.
-
-```{r anes-cross, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:anes}Predicted Turnout, 2020", fig.pos = "!htpb", fig.align = "center"}
-load("temp/anes_plot.rdata")
-print(p2)
-```
-
-Figure \ref{fig:anes} demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (*p* = 0.004).
-The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (*p* = 0.07).
-Importantly, this effect is not a remnant of a white--nonwhite divide.
-As we show in the SI, police stops were not differently related to turnout for Latinos than for non-Latinos; nor did they impact turnout differently for Asians than for non-Asians.
-The ANES results point, then, to the fact that police stops are uniquely associated with higher turnout for Black respondents.
-
-The second panel of Figure \ref{fig:anes} shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
-Importantly, the interaction between arrest status and the respondent’s race was not statistically significant.
-In other words, although police stops seem to be uniquely mobilizing for Black Americans, we fail to uncover evidence that arrests differentially structured subsequent Black and non-Black turnout.
-
-It is worth re-establishing that cross-sectional results cannot establish causality.
-It is possible that Black respondents who had been stopped by the police (or had family members who experienced a stop) differed from non-Black respondents with such contact in ways that cannot be captured by the survey data.
-However, our findings are consistent with a causal story that police stops are uniquely mobilizing for Black Americans---but this is not the case for higher-level contact, such as arrests.
-
-# Discussion {-}
-
-While existing sociological and political science literature has examined the rise and collateral consequences of criminalization on political socialization, no study has investigated the causal relationship between ticketing and voter turnout using individual-level administrative data.
-
-Given how widespread police stops are and their relationship to racial injustice, their political implications demand close study.
-Accordingly, we investigate this question using two different data sources and analytic strategies.
-What we find complicates our understanding of how lower-level police contact affects political participation.
-In the analysis of Hillsborough County police stops, we find that stops reduce the voter turnout of non-Black voters, with a smaller negative effect for Black voters.
-On the other hand, the descriptive analysis of national survey data indicates that police contact is associated with *higher* turnout for Black Americans, and *unrelated* to turnout for others.
-Despite this incongruence, both analyses indicate that police stops have different participatory effects for Black individuals than for others.
-In this sense, our results point in the same direction.
-We conclude that the political consequences of police stops are unique for Black Americans---and that they are less demobilizing for Black Americans than others.
-Additionally, as @Walker2020a suggests, ticketed Black individuals may be politically mobilized for activities other than voting not observed in this study, such as contacting elected representatives or volunteering for campaigns.
-To that end, it is also worth noting that our causal analysis tests the effect of personal police contact rather than proximal contact, which was the focus of @Walker2020a---it could be the case that mobilizing effects of low-level police contact come from proximal exposure rather than personal.
-
-Our findings have several implications for political science scholarship.
-While existing literature suggests that the most disruptive forms of criminal legal contact (i.e.
-criminal convictions and incarceration) consistently discourage voting [@Lerman2014; @Burch2011; @White2019a], research regarding police stops has produced more mixed results [@Laniyonu2019].
-We extend this theory to police ticketing, the most common form of police contact in America, and find that police traffic stops generally reduce turnout.
-For Black voters, however, our findings suggest that traffic stops are less demobilizing, a sharp contrast with existing scholarship wherein more disruptive forms of criminalization discourage Black voters more than non-Black voters.
-Particularly following the rise of the Black Lives Matter movement in 2013, our findings constitute new evidence in support of our theory that ticketing is distinct from other forms of criminal legal contact and therefore catalyzes different political behaviors among Black voters, who are disproportionately affected by both ticketing and criminalization in general.
-
-In this sense, our analysis could be consistent with a political contestation of criminal legal policy, a phenomenon that aligns with dozens of recent campaigns to reform local fines and fees practices (or abolish them entirely).^[See https://finesandfeesjusticecenter.org/clearinghouse.]  We know that increased fines and fees result from political economy (i.e.
-austerity at the federal level), but our analysis suggests that this could be a “two way street” wherein people who are harmed by policing practices can be politically socialized into resistance.
-
-**Limitations**: In our analysis of Hillsborough County voters, we do not look at people who were not registered to vote in 2018.
-Because we cannot tell whether unregistered individuals who were stopped in Hillsborough County were unregistered because they were *ineligible* to do so (by virtue of living in a different county or being a non-citizen, for instance) or chose to eschew electoral politics, our analysis is necessarily limited to individuals who were registered to vote.
-This likely makes our results conservative: we cannot capture the lost participation of individuals who would have registered and voted if they were not stopped by the police.
-
-**Future research**: This work looks at the difference between the political behavior of Black and non-Black Americans.
-Future work should explore variation *within* the Black community.
-When is this sort of contact mobilizing?
-For whom?
-Can organizers build on this potential for broad-based political action?
-We were unable to test whether what we observed was simply *decreased* demobilization, or whether some subgroups of the Black population were mobilized while others were demobilized.
-Put differently: it could be the case that ticketing is demobilizing for most voters of all races, but that a subset of the Black population is affirmatively mobilized, leading to lower group-level demobilization.
-Scholars should also investigate the interactive effects of criminal legal contact, asking whether police stops result in different political behavior for formerly incarcerated individuals than individuals with no other contact with the system.
-
-Finally, we are sensitive to the fact that although administrative data provides real-world evidence of actual behavior, such an approach limits our ability to understand the causal mechanisms in play.
-This means that although we demonstrate that police stops are demobilizing, future work must further investigate how stops are interpreted by individuals and translated into political behavior.
-
-Although we have contributed new evidence suggesting that police stops and related exploitative ticketing practices may not demobilize Black voters to the same extent as non-Black voters, we emphasize that this finding does not redeem or justify such police practices.
-Black Americans already suffer from disproportionate police contact and the racial wealth gap, and racist revenue-motivated ticketing only increases the burden on Black communities nationwide.
-Policymakers should work to ensure that Black Americans no longer have to struggle to enjoy the same political power as whites---to that end, the current trend of voting rights restriction policies across the country is especially pernicious.
-Even if some Black Americans understand the ballot box as one tool they can use to limit the state’s power to exploit and harm them, policymakers should still feel an obligation to support voting rights protections and stop disproportionate ticketing in Black communities.
-
-\newpage
-
-# References {-}

### 2022-04-19 markdown/si.Rmd
submissions

@@
   bookdown::pdf_document2:
-    toc: no
+    toc: yes
     fig_caption: yes
@@
 \doublespacing
+\newpage
 
-# Administrative Matching Robustness Check {-}
+# Administrative Matching Robustness Check
 
@@
 
-# Sensitivity to Narrower Windows {-}
+# Sensitivity to Narrower Windows
 
@@
 Here, we re-run our matching process on a variety of different windows around the elections.
-In the most conservative approach, we force voters stopped in the month before an election to match with voters stopped in the month after the election; we then gradually relax this assumption by allowing voters stopped in the 2 months before the election to match to those stopped in the 2 months afterwards, etc.
+In the most conservative approach, we force voters stopped in the month before an election to match with voters stopped in the month after the election; we then gradually relax this assumption by allowing voters stopped in the 2 months before the election to match to those stopped in the 2 months afterwards, until reaching the two-years used in the manuscript.
 
@@
 As we expand the window, we gain more treated voters (and treated voters have a larger pool of potential controls).
-As such, the confidence interval shrinks, but the overall effect is clearly robust to very strict assumptions.
+As such, the confidence interval shrinks, but the treated and control voters are stopped at more distant temporal points from one another.
+The left-most side of the plot shows that the overall effect is robust to very strict assumptions.
 In each case, we are re-estimating our primary models in which the covariates used in the matching exercise are also included in the econometric model.
@@
 
-# Regression Tables for Individual Treatment Years {-}
+# Full Regression Tables for Administrative Test
 
@@
 In 2014 and 2016, the effect is significantly smaller for Black individuals, though in 2018 the treatment effect for Black and non-Black voters is statistically indistinguishable.
+
+In Table 5, we present the full regression table for the overall models, with all covariates included.
 
@@
 
-# Testing Robustness of L2 Racial Estimates {-}
-
-As discussed in the body of this manuscript, our municipality-level racial estimates are constructed by aggregating up from individual-level records provided by L2.
-Because L2 uses statistical modeling to infer voters' race---not self-reported information---there is potential room for error in these estimates.
-
-Because there are no precise estimates of the racial demographics of the registered electorate in each city, we compare the estimated Black share of each municipality to the Black share of the citizen voting age population (CVAP) in each municipality.
-This method is not without drawbacks: if different cities have different racial registration rates, they will not track perfectly.
-To mitigate some of this discrepancy, we adjust the Black share of the electorate in each municipality by the racial registration gap in that municipality's state, according to the Current Population Survey's (CPS) 2018 data.
-For example, according to the CPS, 27.0% of the citizen population in Alabama was Black in 2018, but just 26.4% of registered voters were Black.
-We therefore add 0.6% to the estimated Black share of the electorate in each municipality in Alabama, so that it might more closely mirror the Black share of CVAP.
-
-In Table 5 we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level and adjusted according to the CPS, relative to the Census Bureau's CVAP estimate.
-Because it seems possible that these errors vary by population size, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.
-
 \begin{singlespace}
-```{r mae-chunck, echo = F, warning = F}
-t <- readRDS("./temp/maes.rds") %>%
-  mutate_all(~ gsub("[%]", "\\\\%", .))
-j <- t %>%
-  mutate_all(linebreak) %>%
-  knitr::kable(booktabs = T, caption = "(\\#tab:mae) MAE of L2 Municipality Estimates, CVAP", linesep = "", escape = F,
-               col.names = linebreak(colnames(t)),
-               align = "c") %>%
-  kable_styling(latex_options = c("HOLD_position"),
-                position = "center")
-j
-```
+\input{"../temp/dind_reg_yoverall.tex"}
 \end{singlespace}
 
-Table 5 makes clear that the adjusted Black estimates of the electorate mirror the Black share of CVAP very closely: for no group of municipalities does the MAE exceed 3%.
-This seems to indicate that the L2 racial estimates are quite good when aggregated to the municipal level.
-
-In Table 6, we show that the difference between the adjusted estimate of the Black share of the electorate and the Black share of the CVAP is entirely unrelated to cities' per-capita fees and fines, after controlling for other characteristics.
-Given the low MAE and the lack of relationship between the error and the fees and fines, we conclude that the municipal-level racial estimates from the individual-level records are reasonable and unbiased.
-
-\begin{singlespace}
-\input{"../temp/mae_clean.tex"}
-\end{singlespace}
-
-# Regression Table for 2018 Cross-Sectional Municipality Model {-}
-
-In Table 7 we present the full results of the econometric used to test the cross-sectional relationship between per-capita fees and fines, and 2018 municipal turnout.
-The table shows that a doubling of the fees and fines collected per capita is associated with a 0.3 percentage point reduction in overall turnout.
-That same doubling, however, is associated with a 0.4 percentage point *increase* in the Black turnout.
-While these point estimates are quite small, it is worth keeping in mind that the range of fees and fines per capita is very wide.
-The interquartile ranges of fees and fines per capita stretches from \$1.96 to \$20.63---a more than ten-fold increase.
-
-\begin{singlespace}
-\input{"../temp/cog_cross_clean.tex"}
-\end{singlespace}
-
-# Regression Table for Survey Data {-}
+# Regression Table for Survey Data
 
@@
 
-Models 2, 3, and 4 test whether the relationship is different for other non-white groups. Finally, model 5 tests the relationship between turnout and a historical arrest.
+Models 2 and 3 whether the relationship is different for other non-white groups. Finally, model 4 tests the relationship between turnout and a historical arrest.
 
 \begin{singlespace}
-\input{"../temp/anes_clean.tex"}
+\input{"../temp/anes_raw.tex"}
 \end{singlespace}
 
-Model 1 in Table 8 shows that Black individuals who had been stopped by the police (or had a family member stopped) in the preceding 12 months were 9 percentage points more likely to vote in 2020, other things equal; they were not related to turnout for non-Black respondents.
+Model 1 in Table 6 shows that Black individuals who had been stopped by the police (or had a family member stopped) in the preceding 12 months were 9.6 percentage points more likely to vote in 2020, other things equal; they were not related to turnout for non-Black respondents.
 Police stops are not, however, associated with different turnout effects for other non-white groups.
-Moreover, as discussed in the body of the paper, historical arrests were uniformly associated with a decrease in turnout of 4 percentage points for Black and non-Black respondents alike.
+Moreover, as discussed in the body of the paper, historical arrests were uniformly associated with a decrease in turnout of 3 percentage points for Black and non-Black respondents alike.
 
 \newpage
-# References {-}
+# References

### 2022-04-19 markdown/si.tex
submissions

@@
 
+{
+\setcounter{tocdepth}{2}
+\tableofcontents
+}
 \pagenumbering{gobble}
@@
 \doublespacing
+\newpage
 
 \hypertarget{administrative-matching-robustness-check}{%
-\section*{Administrative Matching Robustness Check}\label{administrative-matching-robustness-check}}
-\addcontentsline{toc}{section}{Administrative Matching Robustness Check}
+\section{Administrative Matching Robustness Check}\label{administrative-matching-robustness-check}}
 
@@
 \hypertarget{sensitivity-to-narrower-windows}{%
-\section*{Sensitivity to Narrower Windows}\label{sensitivity-to-narrower-windows}}
-\addcontentsline{toc}{section}{Sensitivity to Narrower Windows}
+\section{Sensitivity to Narrower Windows}\label{sensitivity-to-narrower-windows}}
 
@@
 
-\hypertarget{regression-tables-for-individual-treatment-years}{%
-\section*{Regression Tables for Individual Treatment Years}\label{regression-tables-for-individual-treatment-years}}
-\addcontentsline{toc}{section}{Regression Tables for Individual Treatment Years}
+\hypertarget{full-regression-tables-for-administrative-test}{%
+\section{Full Regression Tables for Administrative Test}\label{full-regression-tables-for-administrative-test}}
 
@@
 
-\hypertarget{testing-robustness-of-l2-racial-estimates}{%
-\section*{Testing Robustness of L2 Racial Estimates}\label{testing-robustness-of-l2-racial-estimates}}
-\addcontentsline{toc}{section}{Testing Robustness of L2 Racial Estimates}
-
-As discussed in the body of this manuscript, our municipality-level racial estimates are constructed by aggregating up from individual-level records provided by L2.
-Because L2 uses statistical modeling to infer voters' race---not self-reported information---there is potential room for error in these estimates.
-
-Because there are no precise estimates of the racial demographics of the registered electorate in each city, we compare the estimated Black share of each municipality to the Black share of the citizen voting age population (CVAP) in each municipality.
-This method is not without drawbacks: if different cities have different racial registration rates, they will not track perfectly.
-To mitigate some of this discrepancy, we adjust the Black share of the electorate in each municipality by the racial registration gap in that municipality's state, according to the Current Population Survey's (CPS) 2018 data.
-For example, according to the CPS, 27.0\% of the citizen population in Alabama was Black in 2018, but just 26.4\% of registered voters were Black.
-We therefore add 0.6\% to the estimated Black share of the electorate in each municipality in Alabama, so that it might more closely mirror the Black share of CVAP.
-
-In Table 5 we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level and adjusted according to the CPS, relative to the Census Bureau's CVAP estimate.
-Because it seems possible that these errors vary by population size, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.
-
 \begin{singlespace}
-\begin{table}[H]
-
-\caption{\label{tab:mae-chunck}\label{tab:mae} MAE of L2 Municipality Estimates, CVAP}
-\centering
-\begin{tabular}[t]{ccccc}
-\toprule
-Bottom Quartile & Second Quartile & Third Quartile & Fourth Quartile & Overall\\
-\midrule
-2.40\% & 2.38\% & 2.24\% & 2.70\% & 2.42\%\\
-\bottomrule
-\end{tabular}
-\end{table}
-\end{singlespace}
-
-Table 5 makes clear that the adjusted Black estimates of the electorate mirror the Black share of CVAP very closely: for no group of municipalities does the MAE exceed 3\%.
-This seems to indicate that the L2 racial estimates are quite good when aggregated to the municipal level.
-
-In Table 6, we show that the difference between the adjusted estimate of the Black share of the electorate and the Black share of the CVAP is entirely unrelated to cities' per-capita fees and fines, after controlling for other characteristics.
-Given the low MAE and the lack of relationship between the error and the fees and fines, we conclude that the municipal-level racial estimates from the individual-level records are reasonable and unbiased.
-
-\begin{singlespace}
-\input{"../temp/mae_clean.tex"}
-\end{singlespace}
-
-\hypertarget{regression-table-for-2018-cross-sectional-municipality-model}{%
-\section*{Regression Table for 2018 Cross-Sectional Municipality Model}\label{regression-table-for-2018-cross-sectional-municipality-model}}
-\addcontentsline{toc}{section}{Regression Table for 2018 Cross-Sectional Municipality Model}
-
-In Table 7 we present the full results of the econometric used to test the cross-sectional relationship between per-capita fees and fines, and 2018 municipal turnout.
-The table shows that a doubling of the fees and fines collected per capita is associated with a 0.3 percentage point reduction in overall turnout.
-That same doubling, however, is associated with a 0.4 percentage point \emph{increase} in the Black turnout.
-While these point estimates are quite small, it is worth keeping in mind that the range of fees and fines per capita is very wide.
-The interquartile ranges of fees and fines per capita stretches from \$1.96 to \$20.63---a more than ten-fold increase.
-
-\begin{singlespace}
-\input{"../temp/cog_cross_clean.tex"}
+\input{"../temp/dind_reg_yoverall.tex"}
 \end{singlespace}
@@
 \hypertarget{regression-table-for-survey-data}{%
-\section*{Regression Table for Survey Data}\label{regression-table-for-survey-data}}
-\addcontentsline{toc}{section}{Regression Table for Survey Data}
+\section{Regression Table for Survey Data}\label{regression-table-for-survey-data}}
 
@@
 
-Models 2, 3, and 4 test whether the relationship is different for other non-white groups. Finally, model 5 tests the relationship between turnout and a historical arrest.
+Models 2 and 3 whether the relationship is different for other non-white groups. Finally, model 4 tests the relationship between turnout and a historical arrest.
 
 \begin{singlespace}
-\input{"../temp/anes_clean.tex"}
+\input{"../temp/anes_raw.tex"}
 \end{singlespace}
 
-Model 1 in Table 8 shows that Black individuals who had been stopped by the police (or had a family member stopped) in the preceding 12 months were 9 percentage points more likely to vote in 2020, other things equal; they were not related to turnout for non-Black respondents.
+Model 1 in Table 6 shows that Black individuals who had been stopped by the police (or had a family member stopped) in the preceding 12 months were 9.6 percentage points more likely to vote in 2020, other things equal; they were not related to turnout for non-Black respondents.
 Police stops are not, however, associated with different turnout effects for other non-white groups.
-Moreover, as discussed in the body of the paper, historical arrests were uniformly associated with a decrease in turnout of 4 percentage points for Black and non-Black respondents alike.
+Moreover, as discussed in the body of the paper, historical arrests were uniformly associated with a decrease in turnout of 3 percentage points for Black and non-Black respondents alike.
 
@@
 2014.
-{``Do {Voting Rights Notification Laws Increase Ex}-{Felon Turnout}?''} \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 220--49.
+{``Do {Voting Rights Notification Laws Increase Ex-Felon Turnout}?''} \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 220--49.
 \url{https://doi.org/10.1177/0002716213502931}.

### 2022-04-19 markdown/si_jop.Rmd
submissions

---
title: "Supplementary Information"
output:
  bookdown::pdf_document2:
    toc: no
    fig_caption: yes
    latex_engine: xelatex
    keep_tex: true
bibliography: "policing_turnout.bib"
link-citations: yes
fontsize: 12pt
always_allow_html: true
header-includes:
    - \usepackage{rotating}
    - \usepackage{setspace}
---
```{r setup, echo = F, message = F, warning = F}
knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf")
library(systemfit)
library(AER)
library(sandwich)
library(lmtest)
library(scales)
library(tidyverse)
library(extrafont)
library(kableExtra)
library(data.table)
library(stargazer)
loadfonts()
```
\pagenumbering{gobble}
\pagenumbering{arabic}
\doublespacing

# Testing Robustness of L2 Racial Estimates {-}

As discussed in the body of this manuscript, our municipality-level racial estimates are constructed by aggregating up from individual-level records provided by L2. Because L2 uses statistical modeling to infer voters' race---not self-reported information---there is potential room for error in these estimates.

Because there are no precise estimates of the racial demographics of the registered electorate in each city, we compare the estimated Black share of each municipality to the Black share of the citizen voting age population (CVAP) in each municipality. This method is not without drawbacks: if different cities have different racial registration rates, they will not track perfectly. To mitigate some of this discrepancy, we adjust the Black share of the electorate in each municipality by the racial registration gap in that municipality's state, according to the Current Population Survey's (CPS) 2018 data. For example, according to the CPS, 27.0% of the citizen population in Alabama was Black in 2018, but just 26.4% of registered voters were Black. We therefore add 0.6% to the estimated Black share of the electorate in each municipality in Alabama, so that it might more closely mirror the Black share of CVAP.

In Table \ref{tab:mae} we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level and adjusted according to the CPS, relative to the Census Bureau's CVAP estimate. Because it seems possible that these errors vary by population size, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.

\begin{singlespace}
```{r mae-chunck, echo = F, warning = F}
t <- readRDS("./temp/maes.rds") %>%
  mutate_all(~ gsub("[%]", "\\\\%", .))
j <- t %>%
  mutate_all(linebreak) %>%
  knitr::kable(booktabs = T, caption = "(\\#tab:mae) MAE of L2 Municipality Estimates, CVAP", linesep = "", escape = F,
               col.names = linebreak(colnames(t)),
               align = "c") %>%
  kable_styling(latex_options = c("HOLD_position"),
                position = "center")
j
```
\end{singlespace}

Table \ref{tab:mae} makes clear that the adjusted Black estimates of the electorate mirror the Black share of CVAP very closely: for no group of municipalities does the MAE exceed 3%. This seems to indicate that the L2 racial estimates are quite good when aggregated to the municipal level.

In Table \ref{tab:mae-reg}, we show that the difference between the adjusted estimate of the Black share of the electorate and the Black share of the CVAP is entirely unrelated to cities' per-capita fees and fines, after controlling for other characteristics. Given the low MAE and the lack of relationship between the error and the fees and fines, we conclude that the municipal-level racial estimates from the individual-level records are reasonable and unbiased.

\begin{singlespace}
\input{"../temp/mae_clean.tex"}
\end{singlespace}

# Regression Table for 2018 Cross-Sectional Municipality Model {-}

In Table \ref{tab:cog-cross-reg} we present the full results of the econometric used to test the cross-sectional relationship between per-capita fees and fines, and 2018 municipal turnout. The table shows that a doubling of the fees and fines collected per capita is associated with a 0.3 percentage point reduction in overall turnout. That same doubling, however, is associated with a 0.4 percentage point *increase* in the Black turnout. While these point estimates are quite small, it is worth keeping in mind that the range of fees and fines per capita is very wide. The interquartile ranges of fees and fines per capita stretches from \$1.96 to \$20.63---a more than ten-fold increase.

\begin{singlespace}
\input{"../temp/cog_cross_clean.tex"}
\end{singlespace}

# Full Regression Table for TWFE Model {-}

In Table \ref{tab:twfe} we present the full regression table for the two-way fixed effects models presented in the body of the manuscript.

\begin{singlespace}
\input{"../temp/2wfe_reg_clean.tex"}
\end{singlespace}

### 2022-04-19 markdown/si_jop.tex
submissions

--- 2021-07-23 markdown/si.tex
@@
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 \doublespacing
-
-\hypertarget{administrative-matching-robustness-check}{%
-\section*{Administrative Matching Robustness Check}\label{administrative-matching-robustness-check}}
-\addcontentsline{toc}{section}{Administrative Matching Robustness Check}
-
-Our models exploring the turnout effects of traffic stops in Hillsborough County, Florida, require that we merge administrative records using the identifiers in the data.
-This runs the risk of identifying false positives.
-To test the prevalence of false positives in our administrative matching procedure, we use the test developed by \protect\hyperlink{ref-Meredith2014}{Meredith and Morse} (\protect\hyperlink{ref-Meredith2014}{2014}).
-By systematically permuting the birth dates in one set of records, we can see whether false positive matches are a major concern.
-In Table \ref{tab:change-dobs} we begin by merging all names and dates of birth in the traffic stop data with the names and dates of birth in the Hillsborough County registered voter file.
-We then add and subtract 35 days from the birth dates in the traffic stop data.
-If there are no false positives, these records should match with no records from the registered voter file.
-
-\begin{singlespace}
-\begin{table}[H]
-
-\caption{\label{tab:shift-dobs-chunk}\label{tab:change-dobs} Results of Shifting Birthdates}
-\centering
-\begin{tabular}[t]{cc}
-\toprule
-Group & \makecell[c]{Number of Matches Between\\Traffic Stop and Voter File Records}\\
-\midrule
-Actual Birthdate & 263,152\\
-Birthdate + 35 Days & 78\\
-Birthdate - 35 Days & 60\\
-\bottomrule
-\end{tabular}
-\end{table}
-\end{singlespace}
-
-As the table makes clear, more than a quarter-million registered voters in Hillsborough County match at least one record in the traffic stop database when merging by first and last name, and date of birth.
-Once we permute the birth dates, however, the match rate drops dramatically---to 60 or 78, depending on how these dates of birth are permuted.
-This translates into a false positive rate of roughly 0.03 percent.
-We consider this rate of false positives too low to meaningfully impact our results.
-
-\hypertarget{sensitivity-to-narrower-windows}{%
-\section*{Sensitivity to Narrower Windows}\label{sensitivity-to-narrower-windows}}
-\addcontentsline{toc}{section}{Sensitivity to Narrower Windows}
-
-In the individual-level section of this manuscript, voters stopped in the 2 years prior to an election are considered treated, and we draw our controls from the voters stopped 2 years after the election.
-It is perhaps the case that this large window results in implausible matches; under this design, a treated voter stopped in December of 2012 could draw a control not stopped until October of 2016.
-Voters stopped nearly 4 years apart from one another might differ in meaningful ways that our matching models cannot capture.
-
-Here, we re-run our matching process on a variety of different windows around the elections.
-In the most conservative approach, we force voters stopped in the month before an election to match with voters stopped in the month after the election; we then gradually relax this assumption by allowing voters stopped in the 2 months before the election to match to those stopped in the 2 months afterwards, etc.
-
-Figure \ref{fig:rob-window} shows that our overall treatment effect is remarkably consistent regardless of the size of the window drawn around the election.
-As we expand the window, we gain more treated voters (and treated voters have a larger pool of potential controls).
-As such, the confidence interval shrinks, but the overall effect is clearly robust to very strict assumptions.
-In each case, we are re-estimating our primary models in which the covariates used in the matching exercise are also included in the econometric model.
-
-\begin{figure}[H]
-
-{\centering \includegraphics{si_files/figure-latex/windows-1}
-
-}
-
-\caption{\label{fig:rob-window}Estimated Treatment Effect for Different Treatment Windows}\label{fig:windows}
-\end{figure}
-
-\hypertarget{regression-tables-for-individual-treatment-years}{%
-\section*{Regression Tables for Individual Treatment Years}\label{regression-tables-for-individual-treatment-years}}
-\addcontentsline{toc}{section}{Regression Tables for Individual Treatment Years}
-
-In the body of this manuscript, we present only the overall treatment effects for the police stops in Hillsborough County, which are effectively averaged across all three years.
-Here, in Tables \ref{tab:dind-table-2014}--\ref{tab:dind-table-2018}, we present the results for each group of treated and control voters.
-In Table \ref{tab:dind-table-2014}, all treated voters were stopped between the 2012 and 2014 elections, and all controls were stopped between the 2014 and 2016 elections.
-In Table \ref{tab:dind-table-2016}, treated voters were stopped between 2014 and 2016, while controls were stopped between 2016 and 2018.
-Finally, Table \ref{tab:dind-table-2018} presents the treatment effect for voters stopped between 2016 and 2018, relative to their controls stopped between the 2018 and 2020 elections.
-In every year, there is a statistically significant, negative treatment effect for non-Black voters.
-In 2014 and 2016, the effect is significantly smaller for Black individuals, though in 2018 the treatment effect for Black and non-Black voters is statistically indistinguishable.
-
-\begin{singlespace}
-\input{"../temp/dind_reg_y2014-11-04.tex"}
-\end{singlespace}
-
-\begin{singlespace}
-\input{"../temp/dind_reg_y2016-11-08.tex"}
-\end{singlespace}
-
-\begin{singlespace}
-\input{"../temp/dind_reg_y2018-11-06.tex"}
-\end{singlespace}
 
@@
 
-In Table \ref{tab:mae:reg}, we show that the difference between the adjusted estimate of the Black share of the electorate and the Black share of the CVAP is entirely unrelated to cities' per-capita fees and fines, after controlling for other characteristics.
+In Table \ref{tab:mae-reg}, we show that the difference between the adjusted estimate of the Black share of the electorate and the Black share of the CVAP is entirely unrelated to cities' per-capita fees and fines, after controlling for other characteristics.
 Given the low MAE and the lack of relationship between the error and the fees and fines, we conclude that the municipal-level racial estimates from the individual-level records are reasonable and unbiased.
@@
 
-\hypertarget{regression-table-for-survey-data}{%
-\section*{Regression Table for Survey Data}\label{regression-table-for-survey-data}}
-\addcontentsline{toc}{section}{Regression Table for Survey Data}
+\hypertarget{full-regression-table-for-twfe-model}{%
+\section*{Full Regression Table for TWFE Model}\label{full-regression-table-for-twfe-model}}
+\addcontentsline{toc}{section}{Full Regression Table for TWFE Model}
 
-Here we present the regression table reported in the national survey data section of the manuscript.
-In model 1 we test whether personal or proximal contact with a police stop is differentially associated with turnout for Black and non-Black respondents.
-In this model, \emph{Stopped in Past 12 Months} captures the relationship between police stops and non-Black respondents; \emph{Stopped in Past 12 Months × Black} tests whether this relationship is different for Black respondents.
-
-Models 2, 3, and 4 test whether the relationship is different for other non-white groups. Finally, model 5 tests the relationship between turnout and a historical arrest.
+In Table \ref{tab:twfe} we present the full regression table for the two-way fixed effects models presented in the body of the manuscript.
 
 \begin{singlespace}
-\input{"../temp/anes_clean.tex"}
+\input{"../temp/2wfe_reg_clean.tex"}
 \end{singlespace}
 
-Model 1 in Table \ref{tab:anes-reg} shows that Black individuals who had been stopped by the police (or had a family member stopped) in the preceding 12 months were 9 percentage points more likely to vote in 2020, other things equal; they were not related to turnout for non-Black respondents.
-Police stops are not, however, associated with different turnout effects for other non-white groups.
-Moreover, as discussed in the body of the paper, historical arrests were uniformly associated with a decrease in turnout of 4 percentage points for Black and non-Black respondents alike.
-
-\newpage
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-Meredith2014}{}%
-Meredith, Marc, and Michael Morse.
-2014.
-{``Do {Voting Rights Notification Laws Increase Ex}-{Felon Turnout}?''} \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 220--49.
-\url{https://doi.org/10.1177/0002716213502931}.
-
-\end{CSLReferences}
-
 \end{document}

### 2022-04-19 code/02_2018_cross_sectional.R

@@ -92,70 +92,43 @@ saveRDS(full_set, "temp/full_set_for_mae.rds")
 
 covars <- gsub("\\n|            ", "", "lndper + nh_white + nh_black + latino + asian + lpd +
             median_income + some_college + median_age + share_over_64 +
-            state + total_revenue + share_taxes + share_s_fed")
+            total_revenue + share_taxes + share_s_fed | state")
 
 ms <- data.frame(m = c("vap_to_18_overall", "vap_to_18_black", "vap_to_18_nonblack"),
                  name = c("Overall Turnout", "Black Turnout", "Non-Black Turnout"))
 
 
 models <- lapply(ms$m, function(f){
-  lm(as.formula(paste0(f, " ~ ", covars)),
-     data = filter(full_set, !!sym(f) <= 1))
+  feols(as.formula(paste0(f, " ~ ", covars)),
+     data = filter(full_set, !!sym(f) <= 1), cluster = ~ state)
 })
 
-ses <- lapply(ms$m, function(f){
-  summary(lm.cluster(as.formula(paste0(f, " ~ ", covars)),
-                     data = filter(full_set, !!sym(f) <= 1),
-                     cluster = filter(full_set, !!sym(f) <= 1)$state))[,2]
-})
+names(models) <- ms$name
 
-
-stargazer(models, type = "text", omit = c("state"),
-          column.labels = ms$name,
-          dep.var.labels = "",
-          covariate.labels = c("Log((Dollars / Resident) + 1)",
-                               "% nonHispanic White",
-                               "% nonHispanic Black",
-                               "% Latinx",
-                               "% Asian",
-                               "Log(Population Density)",
-                               "Median Income (dollarsign10,000s)",
-                               "% with Some College",
-                               "Median Age",
-                               "Share over 64",
-                               "Log(Total Revenue)",
-                               "% of Rev from Taxes",
-                               "% of Rev from State / Fed Gov."),
-          se = ses,
-          add.lines = list(c("State fixed effects", "X", "X", "X")),
-          notes = "TO REPLACE",
-          omit.stat = c("F", "ser"),
-          out = "temp/cog_cross_raw.tex",
-          table.placement = "H",
-          title = "\\label{tab:cog-cross-reg} Fees and Fines and 2018 Turnout")
-
-
[…]

### 2022-04-19 code/03_2wayfe.R

@@ -139,47 +139,48 @@ models <- lapply(ms$m, function(f){
       effect = "twoways")
 })
 
-stargazer(models, type = "text",
-          covariate.labels = c("Log(Dollars / Resident)",
-                               "Share non-Hispanic White",
-                               "Share non-Hispanic Black",
-                               "Share Latinx",
-                               "Share Asian",
-                               "Log(Population Density)",
-                               "Median Income (dollarsign10,000s)",
-                               "Share with Some College",
-                               "Median Age",
-                               "Share over 64 Years Old",
-                               "Log(Total Revenue)",
-                               "Share of Revenue from Taxes",
-                               "Share of Revenue from State / Federal Government"),
-          column.labels = ms$name,
-          dep.var.labels = "",
-          notes = "TO REPLACE",
-          title = "\\label{tab:twfe} Two-Way Fixed Effects Models",
-          out = "temp/2wfe_reg.tex",
-          omit.stat = c("F", "ser"))
+names(models) <- ms$name
 
-j <- fread("./temp/2wfe_reg.tex", header = F, sep = "+")
 
-note.latex <- "\\multicolumn{3}{l}{\\scriptsize{\\parbox{.5\\linewidth}{\\vspace{2pt}$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$.}}}"
+modelsummary(models,
+             statistic = "std.error",
+             stars = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
+             coef_map = c("lndper" = "Log((Dollars / Resident) + 1)",
+                          "nh_white" = "Share non-Hispanic White",
+                          "nh_black" = "Share non-Hispanic Black",
+                          "latino" = "Share Latinx",
+                          "asian" = "Share Asian",
+                          "pop_dens" = "Log(Population Density)",
+                          "median_income" = "Median Income (\\$10,000s)",
+                          "some_college" = "Share with Some College",
+                          "median_age" = "Median Age",
+                          "share_over_64" = "Share over 64 Years Old",
+                          "total_revenue" = "Log(Total Revenue)",
+                          "share_taxes" = "Share of Revenue from Taxes",
[…]

### 2022-04-19 code/04_anes.R

@@ -73,42 +73,82 @@ reg_d <- select(anes_pre, ideol, white, black, latino, party, V200002,
   mutate_at(vars(white, latino, asian, to, black, stopped, arrested), ~ ifelse(., 1, 0))
 
 
-m_stop <- feols(to ~ stopped*black + white + latino + asian + age + party + income + sex +
-               ideol + vote16 + cd + educ, filter(reg_d), weight = reg_d$V200010b)
+m_stop <- lm(to ~ stopped*black + white + latino + asian + age + party + income + sex +
+               ideol + educ + vote16, filter(reg_d), weight = V200010b)
 
-m_stop2 <- feols(to ~ stopped*asian + white + latino + black + age + party + income + sex +
-                ideol + vote16 + cd + educ, filter(reg_d), weight = reg_d$V200010b)
+m_stop2 <- lm(to ~ stopped*asian + white + latino + black + age + party + income + sex +
+                ideol + educ + vote16, filter(reg_d), weight = V200010b)
 
-m_stop3 <- feols(to ~ stopped*latino + white + asian + black + age + party + income + sex +
-                ideol + vote16 + cd + educ, filter(reg_d), weight = reg_d$V200010b)
+m_stop3 <- lm(to ~ stopped*latino + white + asian + black + age + party + income + sex +
+                ideol + educ + vote16, filter(reg_d), weight = V200010b)
 
-m_arrest <- feols(to ~ arrested*black + white + asian + latino + age + party + income + sex +
-               ideol + vote16 + cd + educ, filter(reg_d), weight = reg_d$V200010b)
+m_stop4 <- lm(to ~ stopped*blm + age + party + income + sex +
+                ideol + educ + vote16, filter(reg_d, black == 1, blm >= 0), weight = V200010b)
 
-################################
-rows <- tribble(~term,          ~m_stop, ~m_arrest,
-                "Age", "$\\checkmark$", "$\\checkmark$", 
-                "Income", "$\\checkmark$", "$\\checkmark$", 
-                "2016 Turnout", "$\\checkmark$", "$\\checkmark$", 
-                "Race Fixed Effects", "$\\checkmark$", "$\\checkmark$", 
-                "Gender Fixed Effects", "$\\checkmark$", "$\\checkmark$", 
-                "Ideology Fixed Effects", "$\\checkmark$", "$\\checkmark$", 
-                "Party Fixed Effects", "$\\checkmark$", "$\\checkmark$", 
[…]

### 2022-04-19 code/hills/05_regression.R

@@ -88,7 +88,8 @@ p2 <- ggplot(data = ll) +
   labs(x = "t", y = "Turnout",
        linetype = "Treatment Group",
        shape = "Treatment Group",
-       caption = "Treatment occurs inside of yellow band.", ) +
+       caption = "Treatment occurs inside of yellow band.
+Full regression tables in section 3 of SI.", ) +
   coord_cartesian(ylim = c(0.05, 0.75))
 p2
 saveRDS(p2, "temp/stopped_any_time_y.rds")
@@ -124,54 +125,77 @@ for(gg in c("overall", "2014-11-04", "2016-11-08", "2018-11-06")){
   }
  
   models1 <- lapply(c(m1, m2, m3, m4), function(f){
-    m <- lm(f, data = dat1,
-            weight = dat1$weight)
+    m <- feols(f, data = dat1,
+            weight = ~ weight, cluster = "group")
   })
+
+  rows <- tribble(~term, ~m1,  ~m2, ~m3, ~m4,
+                  "Year Fixed Effects", "$\\checkmark$", "$\\checkmark$", "$\\checkmark$", "$\\checkmark$")
   
+  attr(rows, 'position') <- c(13)
   
-  ses_cl <- list(
-    summary(lm.cluster(formula = m1, data = dat1, weights = dat1$weight, cluster = dat1$group))[ , 2],
-    summary(lm.cluster(formula = m2, data = dat1, weights = dat1$weight, cluster = dat1$group))[ , 2],
-    summary(lm.cluster(formula = m3, data = dat1, weights = dat1$weight, cluster = dat1$group))[ , 2],
-    summary(lm.cluster(formula = m4, data = dat1, weights = dat1$weight, cluster = dat1$group))[ , 2]
-  )
+  modelsummary(models1,
+               statistic = "std.error",
+               stars = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
+               coef_map = c("treatedTRUE:postTRUE" = "Treated $\\times$ Post Treatment",
+                            "treatedTRUE:postTRUE:blackTRUE" = "Treated $\\times$ Post Treatment $\\times$ Black",
+                            "treatedTRUE" = "Treated",
+                            "postTRUE" = "Post Treatment",
+                            "blackTRUE" = "Black",
+                            "(Intercept)" = "Intercept"),
+               gof_omit = 'DF|Deviance|AIC|BIC|Within|Pseudo|Log|Std|FE',
+               title = tit,
[…]

### 2022-04-19 code/robust/maes.R

@@ -52,57 +52,32 @@ saveRDS(dat, "temp/maes.rds")
 
 test_set$er <- abs(test_set$share_electorate_black - test_set$cvap_share_black)
 
-m1a <- lm(er ~ lndper + nh_white + nh_black + latino + asian + lpd +
+m1a <- feols(er ~ lndper + nh_white + nh_black + latino + asian + lpd +
             median_income + some_college + median_age + share_over_64 +
-            state + total_revenue + share_taxes + share_s_fed, data = test_set)
+            total_revenue + share_taxes + share_s_fed | state, data = test_set,
+            cluster = ~ state)
 
-m1 <- summary(lm.cluster(er ~ lndper + nh_white + nh_black + latino + asian + lpd +
-                           median_income + some_college + median_age + share_over_64 +
-                           state + total_revenue + share_taxes + share_s_fed, data = test_set, cluster = test_set$state))[,2]
-
-
-stargazer(m1a, type = "text", omit = c("state"),
-          column.labels = "Error",
-          dep.var.labels = "",
-          covariate.labels = c("Log((Dollars / Resident) + 1)",
-                               "% nonHispanic White",
-                               "% nonHispanic Black",
-                               "% Latinx",
-                               "% Asian",
-                               "Log(Population Density)",
-                               "Median Income (dollarsign10,000s)",
-                               "% with Some College",
-                               "Median Age",
-                               "Share over 64",
-                               "Total Revenue",
-                               "% of Rev from Taxes",
-                               "% of Rev from State / Fed Gov."),
-          se = list(m1),
-          add.lines = list(c("State fixed effects", "X", "X", "X")),
-          notes = "TO REPLACE",
-          omit.stat = c("F", "ser"),
-          out = "temp/cog_rob_mae.tex",
-          table.placement = "H",
-          title = "\\label{tab:mae:reg} Absolute Value of Difference Between CVAP, Electorate Share Black")
-
-j <- fread("./temp/cog_rob_mae.tex", header = F, sep = "+") %>% 
-  mutate(V1 = gsub("[%]", "Share", V1))
-
[…]

### 2022-05-04 markdown/compile.Rmd
new models, etc

---
title: "Ticketing and Turnout: The Participatory Consequences of Low-Level Police Contact"

# author:
# - Jonathan Ben-Menachem^[PhD Student, Columbia University, Department of Sociology (jb4487@columbia.edu)]
# - Kevin Morris^[PhD Student, CUNY Graduate Center, Department of Sociology (kmorris@gradcenter.cuny.edu)]
# thanks: Earlier versions of this work were presented at the 2021 American Sociological Association Annual Meeting, the 2021 American Political Science Association Annual Meeting, and the Justice Lab at Columbia University. We would like to thank Bruce Western, Joshua Whitford,  Gerard Torrats-Espinosa, Brittany Friedman, Brendan McQuade, Flavien Ganter, Hannah Pullen-Blasnik, Tim Ittner, LeShae Henderson, and Van Tran for their engagement with our paper in its earliest stages. Special thanks to Sam Donahue for identifying the Tampa dataset that became the core of our analysis and eyeballing many, many iterations of analysis results. And finally, we would like to thank Hannah Walker for deep, charitable feedback that pushed us not to undersell our own contribution
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  bookdown::pdf_document2:
    toc: no
    fig_caption: yes
    latex_engine: xelatex
    keep_tex: true
bibliography: "policing_turnout.bib"
link-citations: yes
fontsize: 12pt
header-includes:
    - \usepackage{rotating}
    - \usepackage{setspace}
---

\pagenumbering{gobble}
\pagebreak
```{r setup, echo = F, message = F, warning = F}
knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf")
library(systemfit)
library(kevostools)
library(AER)
library(sandwich)
library(lmtest)
library(scales)
library(ggpubr)
library(tidyverse)
library(extrafont)
library(kableExtra)
library(data.table)
library(stargazer)
loadfonts()
```
\pagenumbering{arabic}
\doublespacing

```{r did-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/stopped_any_time.rds")
print(p2)
```

```{r did-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/stopped_any_time_no_prior.rds")
print(p2)
```

```{r did-no-matching, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout (no matching at all)", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/stopped_any_time_no_matching.rds")
print(p2)
```

Tables 1--4 are with prior turnout in the match. Tables 5--8 have no prior turnout. Table 9--12 have no matching at all
\begin{singlespace}
\input{"../temp/small_two_matches_reg_overall.tex"}
\input{"../temp/small_two_matches_reg_2014-11-04.tex"}
\input{"../temp/small_two_matches_reg_2016-11-08.tex"}
\input{"../temp/small_two_matches_reg_2018-11-06.tex"}

\input{"../temp/small_table_overall_no_prior.tex"}
\input{"../temp/small_table_2014-11-04_no_prior.tex"}
\input{"../temp/small_table_2016-11-08_no_prior.tex"}
\input{"../temp/small_table_2018-11-06_no_prior.tex"}

\input{"../temp/small_two_matches_reg_overall_no_matching.tex"}
\input{"../temp/small_two_matches_reg_2014-11-04_no_matching.tex"}
\input{"../temp/small_two_matches_reg_2016-11-08_no_matching.tex"}
\input{"../temp/small_two_matches_reg_2018-11-06_no_matching.tex"}
\end{singlespace}

```{r coef-plot-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/coef_plot.rds")
print(p2)
```

```{r coef-plot-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/coef_plot_no_prior.rds")
print(p2)
```

```{r event-study-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/event_study.rds")
print(p2)
```

```{r event-study-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/event_study_no_prior.rds")
print(p2)
```

```{r black-overall-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Overall", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/black_overall_effect.rds")
print(p2)
```

```{r black-overall-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Overall (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/black_overall_effect_no_prior.rds")
print(p2)
```

```{r black-relative-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Relative", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/black_relative_effect.rds")
print(p2)
```

```{r black-relative-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Relative (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/black_relative_effect_no_prior.rds")
print(p2)
```

```{r non-black-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Nonblack", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/non_black_effect.rds")
print(p2)
```

```{r non-black-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Nonblack (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/non_black_effect_no_prior.rds")
print(p2)
```

```{r overall-time-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Relative", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/overall_effect.rds")
print(p2)
```

```{r overall-time-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Relative (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/overall_effect_no_prior.rds")
print(p2)
```

### 2022-05-04 markdown/compile.tex
new models, etc

--- 2022-04-19 markdown/draft_paper.tex
@@
 \author{}
-\date{\vspace{-2.5em}February 22, 2022}
+\date{\vspace{-2.5em}May 04, 2022}
 
@@
 \maketitle
-\begin{abstract}
-The American criminal legal system is an important site of political socialization: scholars have shown that criminal legal contact reduces turnout, and that criminalization pushes people away from public institutions more broadly.
-Despite this burgeoning literature, few analyses directly investigate the causal effect of \emph{lower-level} police contact on voter turnout.
-We use two approaches to do so: we leverage both individual-level administrative ticketing data from Hillsborough County, Florida, and responses to the American National Election Studies.
-We estimate that a traffic stop decreases an individual's likelihood of voting by 1.7 percentage points, but depressive effects are smaller for Black residents.
-The survey data, however, show that Black people who report that they or a family member were recently stopped by police are \emph{more} likely to vote than those who reported no such contact.
-Taken together, our results indicate that low-level contact with police may have participatory consequences.
-
-\hfill\break
-
-\textbf{Keywords}: voting, policing, race, punishment, political participation
-\end{abstract}
 
@@
 
-\hypertarget{introduction}{%
-\section*{Introduction}\label{introduction}}
-\addcontentsline{toc}{section}{Introduction}
+\begin{figure}[H]
 
-Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities' alienation from government (\protect\hyperlink{ref-Sanders2017}{Sanders and Conarck 2017}; \protect\hyperlink{ref-McCoy2015}{McCoy 2015}; \protect\hyperlink{ref-Shaer2019}{Shaer 2019}).
-After Michael Brown was killed by the Ferguson Police Department in 2014, a US Department of Justice investigation into the city's police and courts demonstrated that the municipality was engaged in a practice that advocates now refer to as ``policing for profit.'' The city's reliance on fines and fees to fund government functions grew from 13 to 23 percent of the total budget between fiscal years 2012 and 2015.
-From 2012 to 2014, the Department of Justice found that 85 percent of vehicle stops, 90 percent of citations, and 93 percent of arrests targeted Black people.
-By contrast, just two-thirds of Ferguson's residents are Black (\protect\hyperlink{ref-UnitedStatesDepartmentofJusticeCivilRightsDivision2015}{United States Department of Justice Civil Rights Division 2015}).
+{\centering \includegraphics{compile_files/figure-latex/did-primary-1}
 
-It wasn't just a Ferguson problem, or even a Missouri problem.
-American cities' reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (\protect\hyperlink{ref-Singla2020}{Singla, Kirschner, and Stone 2020}; \protect\hyperlink{ref-Harris2017}{A.
-Harris et al.
-2017}; \protect\hyperlink{ref-Harris2020}{A.
-P.
-Harris, Ash, and Fagan 2020}).
+}
 
-Although scholars have examined the collateral consequences of this increased reliance on fines and fees (\protect\hyperlink{ref-Sances2017}{Sances and You 2017}; \protect\hyperlink{ref-Pacewicz2020}{Pacewicz and Robinson 2020}), comparatively few have explored the moment during which such revenue-raising actually occurs: namely, in the individual interactions between residents and the police via the issuance of a ticket.
-This ``moment'' of low-level contact has also been relatively understudied by scholars investigating the participatory consequences of contact with the criminal legal system.
-Work exploring how criminalization directly and indirectly influences political participation has exploded in recent years.
-Scholars have found that criminal legal contact (i.e.~arrest, conviction, incarceration) consistently discourages voting (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}; \protect\hyperlink{ref-Burch2011}{Burch 2011}; \protect\hyperlink{ref-White2019a}{White 2019b}).
-Such work has largely focused on the effects of highly disruptive contact with the criminal legal system such as incarceration and felony convictions (\protect\hyperlink{ref-Burch2014}{Burch 2014}; \protect\hyperlink{ref-Lee2014}{Lee, Porter, and Comfort 2014}).
-While ticketing involves potentially negative interactions with the state, it does not necessarily carry the disruptive consequences of a felony conviction and might thus politicize Americans in unique ways.
-Building on recent theoretical work from \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020b}), this paper theorizes how local police practices affect voting behavior among ticketed individuals and provides precisely estimated evidence of a causal effect.
-
-Our project represents the first use of individual-level administrative data to identify the causal effect of traffic stops on voter behavior.
-The use of administrative data marks an important step forward in our understanding of how low-level contact with the criminal legal system structures political participation.
-Past work looking at the individual-level effects of low-level contact has relied on survey or qualitative data (e.g.
-\protect\hyperlink{ref-Walker2014}{Walker 2014}; \protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
-Existing research allows for the testing of specific psychological mechanisms and personal interpretations of criminal legal contact, but does not allow us to generalize more broadly.
-As Weaver and Lerman (\protect\hyperlink{ref-Weaver2010}{2010}: 821) note, it may also introduce measurement bias.
-Our analysis investigates actual voting behavior following actual ticketing events, not reported voting behavior or reported exposure to a traffic stop.
-The administrative data therefore allow us both to sidestep reporting error and to observe the behavior of a quarter-million individuals stopped over a 6 year period---a far larger pool than even the most robust surveys.
-
-We use individual-level traffic stop data from Hillsborough County, Florida, to identify the turnout patterns of voters who were stopped between the 2012 and 2018 elections.
-By matching individual voters who were stopped to similar voters who were stopped at later points and running a difference-in-differences model, we estimate the causal effect of these stops on turnout.
-This borrows from the logic of regression discontinuities in time: conditional on observable characteristics \emph{and} unobservable factors associated with being ticketed, the timing of the ticket on either side of election day is essentially as-if random.
-We find that being stopped reduces the chance that an individual will turn out in the subsequent election, but that this effect is smaller for Black voters.
-
-To test the generalizability of our findings in Hillsborough County, we conduct a novel analysis of 2020 national survey data regarding voters' experience with police stops.
-We find that Black respondents who reported personal or proximal experience with police stops in the last 12 months are more likely to vote than Black people who did not, while we find no statistically significant relationship between stops and voting among non-Black respondents.
-While the survey data present some drawbacks relative to the individual-level administrative data, their national scope provides helpful corroboration for the unique turnout effects of traffic stops for Black Americans observed in Hillsborough County.
-
-We demonstrate that police ticketing practices---the most widespread form of police contact in America---substantially reduce the turnout of non-Black American voters, but have a unique effect on Black voter turnout.
-Our findings complicate existing theories of how criminalization politically socializes Americans, and Black Americans in particular (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
-Additionally, while many forms of criminalization have been found to contribute to a well-documented subjective experience of alienation or group-level exclusion among Black Americans (\protect\hyperlink{ref-Bell2017}{Bell 2017}; \protect\hyperlink{ref-Stuart2016}{Stuart 2016}; \protect\hyperlink{ref-Desmond2016}{Desmond, Papachristos, and Kirk 2016}, \protect\hyperlink{ref-Desmond2020}{2020}; \protect\hyperlink{ref-Zoorob2020}{Zoorob 2020}; \protect\hyperlink{ref-Ang2021}{Ang et al.
-2021}), our contribution emphasizes the need for further research regarding how different forms of criminalization affect group-level perceptions of government and resultant political behaviors.
-Our findings are relevant for interdisciplinary scholars of crime, race, politics, municipal finance, and policing.
-
-\hypertarget{criminal-legal-system-and-citizen-identity}{%
-\section*{Criminal Legal System and Citizen Identity}\label{criminal-legal-system-and-citizen-identity}}
-\addcontentsline{toc}{section}{Criminal Legal System and Citizen Identity}
-
-In recent years, scholars have paid more attention to the political implications of the American criminal legal system.
-Evolving in part out of a literature focused on street-level bureaucrats, researchers across the social sciences are asking how daily interactions with agents of the carceral state shape Americans' relationships to themselves, their communities, and their state.
-As \protect\hyperlink{ref-Soss2017}{Soss and Weaver} (\protect\hyperlink{ref-Soss2017}{2017}) argues, this ``second face'' of the state---``the activities of governing institutions and officials that exercise social control and encompass various modes of coercion, containment, repression, surveillance, regulation, predation, discipline, and violence'' (567)---is the primary way through which many class-race subjugated communities develop their political knowledge.
-``{[}I{]}nterviewees have looked, not to City Hall, Congress, or political parties,'' they write, ``but rather to their direct experiences with police, jails and prisons, welfare offices, courts, and reentry agencies as they sought to ground their explanations of how government works, what political life is like for them, and how they understand their own political identities'' (\protect\hyperlink{ref-Soss2017}{Soss and Weaver 2017, 574}).
-
-Recent work has explored the production of this political knowledge in increasingly sophisticated ways, using both qualitative and quantitative approaches.
-\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver} (\protect\hyperlink{ref-Lerman2014}{2014})'s pathbreaking book \emph{Arresting Citizenship} set the table for future research.
-Their project combined extensive interviews of individuals living in areas closely monitored by the criminal legal system with novel survey data to probe the political consequences of what they term the ``carceral state.'' Their work indicates that citizens nearly uniformly react negatively to police and carceral supervision---from low-level interactions to lengthy periods of incarceration, Americans subjected to the second face of the state apparently withdraw from political participation.
-They find that trust in government and willingness to vote decrease as individuals progress through increasingly intense levels of criminal legal contact (questioned by police, arrested, convicted, incarcerated) (\protect\hyperlink{ref-Weaver2010}{Weaver and Lerman 2010}).
-New evidence related to ticketing and legal estrangement has recently emerged: in a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government compared to residents who were not ticketed (\protect\hyperlink{ref-CarpenterII2019}{Carpenter II, Sweetland, and McDonald 2019}).
-
-Sarah Brayne (\protect\hyperlink{ref-Brayne2014}{2014}) found related results in her analysis of survey data.
-As the intensity of criminal legal contact escalates , people subjected to criminalization are increasingly likely to avoid institutions that they perceive as surveilling, such as financial or educational institutions.
-She calls this phenomenon ``system avoidance,'' and while her analysis did not specifically assess voting behavior, her findings demonstrate how criminal legal contact can discourage Americans' participation in public institutions as well as how the effect may vary alongside the intensity of criminal legal intervention.
-Similarly, \protect\hyperlink{ref-Remster2018a}{Remster and Kramer} (\protect\hyperlink{ref-Remster2018a}{2018}) finds that men who return home from prison are more likely to avoid contact with their childrens' schools.
-Vesla Weaver and colleagues describe this form of self-preserving withdrawal from public institutions as a ``strategic retreat'' (\protect\hyperlink{ref-Weaver2020}{Weaver, Prowse, and Piston 2020}).
-
-These findings can be situated in a process that sociologist Monica Bell calls ``legal estrangement,'' which captures those perceptions and cultural attitudes (``legal cynicism'') as well as the historical-structural conditions that produced them (\protect\hyperlink{ref-Bell2017}{Bell 2017}).
-Research on legal cynicism has found that public perceptions of abusive police practices can reduce willingness to report crimes or cooperate with law enforcement (\protect\hyperlink{ref-Tyler2014}{Tyler, Fagan, and Geller 2014}).
-The ``hidden curriculum'' (\protect\hyperlink{ref-Justice2014}{Justice and Meares 2014}; \protect\hyperlink{ref-Meares2017}{Meares 2017}) of the criminal legal system teaches Americans about their identities as citizens---even parts of their identities that have little to do with policing or incarceration.
-
-\hypertarget{administrative-data-and-the-causal-effects-of-criminalization}{%
-\section*{Administrative Data and the Causal Effects of Criminalization}\label{administrative-data-and-the-causal-effects-of-criminalization}}
-\addcontentsline{toc}{section}{Administrative Data and the Causal Effects of Criminalization}
-
-Many scholars have turned to administrative data in recent years to explore the actual effects of contact with the criminal legal system on political participation in the voting booth.
-To be sure, administrative data have limitations: they are not ideally suited to probe the psychological, social, relational, and other mechanisms leading some citizens to vote and others to abstain.
-These limitations, however, are balanced by offering researchers precise estimates of actual---and not just reported---turnout.
-
-Traci Burch (\protect\hyperlink{ref-Burch2011}{2011}) was among the earliest scholars to match voter-file records with records detailing citizens' contact with the criminal legal system.
-Her work complicated a previously dominant theory postulating that the turnout and party registration of formerly incarcerated individuals was largely driven by their sociodemographic characteristics but not their formal conviction or supervision (see, for instance, \protect\hyperlink{ref-Uggen2002}{Uggen and Manza 2002}).
-She argues that citizens who are convicted of felony offenses are less likely to vote, and less likely to register with a party, than citizens with similar sociodemographic characteristics without such a conviction.
-
-Other scholars have similarly matched corrections records with registered voter files to explore the effect of contact with the second face of the state.
-\protect\hyperlink{ref-White2019a}{White} (\protect\hyperlink{ref-White2019a}{2019b}) finds that short periods of incarceration reduce Black, but not white, turnout.
-\protect\hyperlink{ref-Gerber2017}{Gerber et al.} (\protect\hyperlink{ref-Gerber2017}{2017}) similarly finds relatively small effects of incarceration on turnout.
-Meredith and Morse (\protect\hyperlink{ref-Meredith2014}{2014}, \protect\hyperlink{ref-Meredith2015}{2015}) and \protect\hyperlink{ref-Gerber2015}{Gerber et al.} (\protect\hyperlink{ref-Gerber2015}{2015}) explore the turnout effect of notifying formerly incarcerated citizens of the legal restoration of their voting rights, with mixed results, while \protect\hyperlink{ref-Morris2021a}{Morris} (\protect\hyperlink{ref-Morris2021a}{2021a}) shows that restoring voting rights to individuals while they are still on parole increases post-supervision turnout.
-Other work has explored the ``spillover'' effects of such contact, finding that the political behavior of family members (\protect\hyperlink{ref-White2019}{White 2019a}) and neighbors (\protect\hyperlink{ref-Burch2014}{Burch 2014}; \protect\hyperlink{ref-Morris2020}{Morris 2020}) can be influenced by indirect contact with incarceration.
-\protect\hyperlink{ref-Morris2021}{Morris} (\protect\hyperlink{ref-Morris2021}{2021b}) argues that these effects are durable, showing that citizens whose household members had been to prison were not disproportionately mobilized by a ballot initiative promising to end felony disenfranchisement.
-
-This burgeoning literature using administrative data has given scholars far greater insight into the participatory consequences of American incarceration.
-It is, however, virtually silent on the effects of \emph{lower level} contact with the criminal legal system.
-Far more Americans have low-level contact with the police than will ever spend a night behind bars: just under 20 million Americans experience a traffic stop each year, whereas approximately five million Americans are arrested and jailed each year (\protect\hyperlink{ref-Harrell2020}{Harrell and Davis 2020}; \protect\hyperlink{ref-Jones2019}{Jones and Sawyer 2019}).
-Despite the fact that so many more citizens are subjected to traffic stops, we know comparatively little about its political ramifications, a lack that is particularly glaring given how much we have learned in recent years about higher-level contact.
-
-The one project that has used administrative data to explore the political implications of low-level police contact is \protect\hyperlink{ref-Laniyonu2019}{Laniyonu} (\protect\hyperlink{ref-Laniyonu2019}{2019}), which explores the effects of the Stop, Question, and Frisk (SQF) program in New York City.
-\protect\hyperlink{ref-Laniyonu2019}{Laniyonu} (\protect\hyperlink{ref-Laniyonu2019}{2019})'s causal estimates rely on a cross-sectional matching model to compare voter turnout in precincts with \emph{high} SQF activity to turnout in precincts with similar sociodemographic characteristics but \emph{low} SQF activity, supplemented with cross-sectional analyses of all precincts in the city.
-His results paint a complicated picture: his causal estimates find that high levels of SQF increased turnout in the 2008 presidential election, but decreased it in the 2010 midterms.
-While \protect\hyperlink{ref-Laniyonu2019}{Laniyonu} (\protect\hyperlink{ref-Laniyonu2019}{2019}) marks an important step forward in the investigation of the consequences of policing for political behavior, it faces certain data and methodological limitations.
-Because the SQF data does not include identifying information about the individuals stopped, he cannot explore the turnout of New Yorkers who were actually subjected to SQF.
-Thus, as he notes in the conclusion, ``the ability of the analysis to make causal claims is limited'' (554) by the cross-sectional matching approach.
-
-In this project, we seek to extend our understanding of the political consequences of routine contact with the state's second face.
-Combining an individual-level administrative panel dataset with national survey data gives us new insight into how traffic stops can shape citizens' engagement with their democracy.
-
-\hypertarget{how-police-stops-might-structure-turnout}{%
-\section*{How Police Stops Might Structure Turnout}\label{how-police-stops-might-structure-turnout}}
-\addcontentsline{toc}{section}{How Police Stops Might Structure Turnout}
-
-Much of the existing work on the turnout consequences of the criminal legal system points to a process of political learning or political socialization.
-\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver} (\protect\hyperlink{ref-Lerman2014}{2014}) finds that individuals in highly surveilled neighborhoods learn that the government does not care about them, and is uninterested in soliciting their participation.
-They note that more than half of individuals stopped by the police report agreeing with the statement ``the leaders in government care very little about people like me,'' compared with just a third of respondents with no police contact (150).
-The numbers, however, were far higher for individuals convicted of a crime, of whom three-quarters agreed with the statement.
-Learning about the criminal legal system takes place over a long period of time.
-Could isolated police stops that neither require sustained contact with the criminal legal system nor (generally) impose punishments as severe as incarceration politically socialize Americans to the same degree as incarceration?
-
-On one hand, it might seem unlikely that a single stop would produce much new knowledge about the state.
-For many Americans, a traffic stop amounts to little more than a slap on the wrist.
-To be sure, fines and fees can wreak havoc on the lives of some drivers.
-If a ticket leads to a suspended driver's license, the initial stop can snowball into a much bigger life event that could jeopardize employment, or lead to shorter stints of incarceration for individuals apprehended driving on a suspended license.
-Searches conducted during traffic stops may also lead to arrest or incarceration if a police officer finds contraband in the vehicle.
-These comparatively less frequent cases might have consequences more akin to those associated with a brief period of incarceration that can also threaten employment.
-Nevertheless, the average traffic stop is certainly less disruptive than the average period of incarceration, perhaps producing less political knowledge and therefore impacting turnout less.
-
-On the other hand, a far larger set of Americans are stopped by the police than sent to jail or prison each year.
-According to the American National Election Study, a nationally-representative survey we use later in this study, the incomes and education levels for individuals stopped by the police are meaningfully higher than for individuals who report ever having been arrested.
-Motorists stopped by police are apparently systematically different compared to people who experience incarceration.
-Traffic stops might thus be the primary way some of these Americans learn about the criminal legal system.
-If these Americans have not already ``learned'' about the system from their neighborhoods or family members, the political consequences of such newly gleaned knowledge might be large.
-
-Traffic stops might provide early insights about the criminal legal system even for Americans who live in more heavily-policed areas.
-As \protect\hyperlink{ref-Gerber2017}{Gerber et al.} (\protect\hyperlink{ref-Gerber2017}{2017}) notes in their study arguing that the participatory consequences of incarceration might be small, incarceration ``is an outcome that often follows a long series of interactions with the criminal justice system'' (1145).
-In other words, much of what the criminal legal system ``teaches'' might have already been learned by the time an individual is sent to prison.
-Someone who is stopped by the police, however, might have had fewer negative interactions with the state.
-Put differently, stopped individuals might have more to learn than incarcerated individuals with a long history of police contact, resulting in higher turnout effects.
-
-\hypertarget{potential-for-racially-disparate-effects}{%
-\section*{Potential for Racially Disparate Effects}\label{potential-for-racially-disparate-effects}}
-\addcontentsline{toc}{section}{Potential for Racially Disparate Effects}
-
-The potential for more ``learning'' from a police stop seems especially salient for Black Americans, particularly in recent years.
-National news over the 2010s was filled with the names of Black Americans who were killed during routine police stops.
-The Black Lives Matter movement gained national attention in the aftermath of the Ferguson uprising, an uprising sparked by the police killing of Michael Brown but also fueled by that city's racial discriminatory ticketing practices.
-In the fall of 2021, \emph{The New York Times} ran an extensive report exploring police killings that occur during traffic stops, providing more proof of their racially disparate nature (\protect\hyperlink{ref-Levenson2021}{Levenson 2021}).
-
-We expect that the participatory consequences of such a stop will be different for Black than non-Black Americans.
-First, traffic stops differ in meaningful ways for Black and non-Black Americans.
-As \protect\hyperlink{ref-Baumgartner2018}{Baumgartner, Epp, and Shoub} (\protect\hyperlink{ref-Baumgartner2018}{2018}) notes, Black Americans are more likely than whites to receive both ``light'' (i.e., a warning without a ticked) \emph{and} ``severe'' (i.e., arrest) outcomes from a traffic stop.
-Although this may seem paradoxical at first, the authors explain: ``while many might rejoice in getting a warning rather than a ticket, the racial differences consistently apparent in the data suggest another interpretation for black drivers: even the officer recognized that there was no infraction'' {[}88{]}.
-Black drivers are also more likely to be searched and arrested, but less likely to be found with contraband (\protect\hyperlink{ref-Baumgartner2018}{Baumgartner, Epp, and Shoub 2018}).
-Similarly, \protect\hyperlink{ref-Epp2014}{Epp, Maynard-Moody, and Haider-Markel} (\protect\hyperlink{ref-Epp2014}{2014}) argues that traffic stops are particularly instructive for Black Americans, as pretextual traffic stops politically socialize Black voters to the specific context of discriminatory police ticketing.
-
-The politicization of a police stop can occur differently for Black Americans through other avenues as well.
-The BLM movement has raised the salience of racially disparate policing across the country, as have the tragic stories of individuals like Philando Castile who was killed during a police stop.
-Routine interactions with the police are also more likely to turn deadly for Black Americans than for others (\protect\hyperlink{ref-Levenson2021}{Levenson 2021}).
-Thus, even if an individual police stop for a Black American is relatively unremarkable on its own, the background context that the interaction \emph{could} have turned deadly is likely to result in some level of trauma for Black drivers.
-Recent work from Hannah Walker (\protect\hyperlink{ref-Walker2020}{2020a}, \protect\hyperlink{ref-Walker2020a}{2020b}) argues that this could lead to a \emph{mobilizing} effect, if stopped drivers understand their contact with the criminal legal system in the context of a narrative of racial injustice, such contact can actually mobilize.
-She explains: ``experiences with punitive policies are subject to interpretation and, when understood through narratives of injustice, lead to wholly different participation outcomes than we usually predict'' (\protect\hyperlink{ref-Walker2020}{Walker 2020a, 132}).
-While she finds that this sense of injustice is especially likely to increase political participation in non-voting ways (such as attending a protest or signing a petition), the logic could extend to electoral participation as well given a relevant electoral context, strong injustice narrative, or relatively weak contact with the criminal legal system.
-
-Given that police stops are more likely to be traumatic for Black motorists (because traffic stops come with a threat of escalation into racialized police violence, because they received harsher punishments, \emph{or} because the stop itself was discriminatory) \emph{and} that there exists a framework available for translating negative experiences with the criminal legal system into political action, we expect police stops to have unique participatory consequences for Black Americans.
-
-At the same time, the average Black American already knows far more about the criminal legal system due to the extreme racial disparities in policing and incarceration.
-As one 2015 study observed, 44\% of Black women (and 32\% of Black men) have a family member in prison.
-These numbers compare with just 12\% and 6\% for white women and men, respectively (\protect\hyperlink{ref-Lee2015}{Lee et al.
-2015}).
-Black Americans' disproportionate contact with the criminal legal system is a firmly established fact at this point.
-This greater baseline exposure could mean that Black Americans have less to ``learn'' from a marginal police stop, resulting in smaller turnout effects.
-
-\hypertarget{data-and-design}{%
-\section*{Data and Design}\label{data-and-design}}
-\addcontentsline{toc}{section}{Data and Design}
-
-We leverage two distinct approaches to ask whether police traffic stops affect voter turnout, and whether these effects are unique for Black Americans.
-
-Each approach offers advantages and drawbacks.
-Our individual-level analysis in Hillsborough County exploits unusually detailed public data, which allows for a precise causal analysis that cannot be conducted in counties that do not provide ticketing records with personally identifiable information or states that do not include self-reported race data in the voter file.
-The empirical estimand is the voter turnout gap between Hillsborough County residents who have recently been ticketed and residents who will be ticketed in a future period, conditional on similar turnout in past elections and similar demographic characteristics.
-In isolation, however, results from one county may not be generalizable to other U.S.
-counties.
-
-Data from the 2020 American National Election Studies allow us to observe how tickets and arrests differentially influence voting behavior at the individual level among a nationally representative sample, but survey data analysis is subject to the vulnerabilities detailed in our introduction (e.g.~measurement bias).
-Nevertheless, it provides important national insight into the phenomena we observe locally in Hillsborough County.
-
-Taken together, these approaches advance our understanding of the political consequences of the most routine types of contact with the criminal legal system.
-
-\hypertarget{individual-level-causal-effects-of-traffic-stops}{%
-\subsection*{Individual-Level Causal Effects of Traffic Stops}\label{individual-level-causal-effects-of-traffic-stops}}
-\addcontentsline{toc}{subsection}{Individual-Level Causal Effects of Traffic Stops}
-
-First, we turn to individual-level data from Hillsborough County, Florida (home to Tampa).
-Hillsborough County makes a unique set of data publicly available.
-The county clerk makes information available about every traffic stop in the county going back to 2003.
-This data includes the name and date of birth of the individual stopped; the date of the offense; the amount the individual paid for a ticket; and other information.
-
-To identify ticketed voters, we match the first and last names and dates of birth from the stop data against the Hillsborough County registered voter file.
-\protect\hyperlink{ref-Meredith2014}{Meredith and Morse} (\protect\hyperlink{ref-Meredith2014}{2014}) develops a test for assessing the prevalence of false-positives in administrative record matching.
-We present the results of that test in section 1 of the Supplementary Information (SI).
-We likely have a false-positive match of around 0.03 percent, a figure we consider too low to impact our results meaningfully.
-
-Using a single post-treatment snapshot of the voter file can result in conditioning on a post-treatment status (see \protect\hyperlink{ref-Nyhan2017}{Nyhan, Skovron, and Titiunik 2017}).
-Instead, we collect snapshots of the voter file following each even-year general election between 2012 and 2018.\footnote{Because such frequent snapshots are not available from L2, we here use the registered voter file made freely available by the state of Florida.} We thus observe virtually all individuals who were registered to vote at any time during our period of study.
-Unique voter identification numbers allow us to avoid double-counting voters who are registered in multiple snapshots.
-We retain each voter's earliest record, and geocode voters to their home census block groups.
-Because we argue that police contact is the driving force behind any turnout effect, we remove tickets issued by red-light cameras.
-
-By matching the police stop and voter records, we identify all voters who were stopped between the 2012 and 2020 general elections (voters stopped between 2018 and 2020 elections serve only as controls).
-We collect self-reported information regarding the race of each voter from Florida's public voter file rather than the police stop data.
-Voters are considered ``treated'' in the general election following their stop.
-Treated voters are then matched to a control voter using a nearest-neighbor approach, with a genetic algorithm used to determine the best weight for each characteristic (\protect\hyperlink{ref-Sekhon2011}{Sekhon 2011}).
-Control voters are individuals who are stopped in the two years following the post-treatment election of the treated voters.
-Put differently, if a voter is stopped between 2012 and 2014, their control voter must be an individual stopped between the 2014 and 2016 elections.
-A voter cannot both be a treated and control voter for the same election; therefore, someone stopped between the 2012 and 2014 elections and again between the 2014 and 2016 elections cannot serve as a control for anyone stopped between 2012 and 2014.
-We limit the target population to voters who are stopped at some point in order to account for unobserved characteristics that motivate people who are stopped at some point to turn out at higher rates than people who are never stopped.
-
-We match voters on individual-level characteristics (race / ethnicity; gender; party affiliation; age; number of traffic stops prior to the treatment period) and block group-level characteristics from the 2012 5-year ACS estimates (median income; share of the population with some college; unemployment rate).
-We match exactly on the type of ticket (civil / criminal infraction; whether they paid a fine; whether they were stopped by the Tampa Police Department) to ensure that treated and control voters receive the same treatment.
-Finally, we match treated and control voters on their turnout in the three pre-treatment elections.
-
-We assume that after controlling for observable characteristics, past turnout, \emph{and} the unobservable characteristics associated with experiencing a traffic stop, the timing of the stop is effectively random.
-This is conceptually similar to the regression discontinuity in time framework, and we assume that any turnout difference between the treated voters and their controls is the causal effect of a police stop on turnout.
-Our overall turnout effects are robust to much weaker assumptions: in section 2 of the SI, we demonstrate that our overall turnout results hold even when we force voters stopped shortly before the election to match to voters stopped shortly afterwards.
-
-Our analytical design thus incorporates two different causal approaches in order to improve the credibility of our identification assumptions.
-Leveraging pre-treatment turnout allows us to estimate a traditional difference-in-differences model, while the matching procedure improves the plausibility of the parallel trends assumption by reducing salient differences between the treated and control voters.
-For a more detailed discussion of how matching can improve upon traditional difference-in-difference approaches when using panel data, see \protect\hyperlink{ref-Imai2020}{Imai, Kim, and Wang} (\protect\hyperlink{ref-Imai2020}{2020}).
-
-We then estimate the following equation:
-
-\begin{gather}
-\label{eq:1}
-v_{it}=\beta_0+\beta_1Treated_{i}+\beta_2Post Treatment_{t} + \nonumber \\
-\beta_3Treated_{i}\times Post Treatment_{t} + \\
-\beta_4Year_{t} + \delta{Z}_{i} + \mathcal{E}_{it}. \nonumber
-\end{gather}
-
-Individual \emph{i}'s turnout (\emph{v}) in year \emph{t} is a function of the year and whether they were stopped by the police.
-In the equation, \emph{\(\beta\)\textsubscript{1}Treated\textsubscript{i}} measures the historical difference between treated voters and their controls.
-\emph{\(\beta\)\textsubscript{2}Post Treatment\textsubscript{t}} measures whether turnout increased for controls in the first election following the treated voter's stop, while \emph{\(\beta\)\textsubscript{3}Treated\textsubscript{i} × Post Treatment\textsubscript{t}} tests whether turnout changed differently for treated voters than their controls in the election following their police stop.
-\emph{\(\beta\)\textsubscript{3}}, then, will capture the causal effect of a police stop on voter turnout; it is the unit-specific quantity measured in our empirical estimand (\protect\hyperlink{ref-Lundberg2021}{Lundberg, Johnson, and Stewart 2021}).
-\emph{\(\beta\)\textsubscript{4}Year\textsubscript{t}} captures year fixed-effects depending on the timing of the police stop, and the matrix \emph{\(\delta\)Z\textsubscript{i}} contains the individual- and neighborhood-level characteristics on which the match was performed, included in some of the models.
-
-In some models, we also interact the treatment variable with a dummy indicating whether the voter is Black to determine race-specific treatment effects.
-
-\hypertarget{national-survey-data}{%
-\subsection*{National Survey Data}\label{national-survey-data}}
-\addcontentsline{toc}{subsection}{National Survey Data}
-
-Next, we turn to the American National Election Studies 2020 Time Series data (ANES).
-The ANES has been fielded in every presidential election year since 1948 and is among the most widely-used tools for understanding American's political beliefs and behaviors, including their relationship with the criminal legal system (\protect\hyperlink{ref-Walker2020}{Walker 2020a}).
-It is weighted to be nationally representative of all American adults.
-In both 2016 and 2020, the ANES added new survey questions about respondent's encounters with the police and the criminal legal system.
-We focus in particular on two questions: \emph{During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?}, and \emph{Have you ever been arrested, or has that never happened to you?} We include the roughly 87 percent of respondents that answered both questions, giving us a sample size of 7,347 respondents, of whom just over 11\% identified as Black.
-
-We use these survey questions to make descriptive inferences about how stops and arrests affect the voting behavior of the general population.
-The first descriptive estimand is the gap between the voter turnout rate of individuals who were recently stopped by the police or who have ever been arrested, and another is whether stops or arrests uniquely influence the political behavior of Black Americans.
-In addition to the respondent's contact with the criminal legal system, we control for age; sex; income; education; party affiliation; self-described ideology; and reported 2016 turnout.
-
-There is an important caveat to the use of the ANES survey---namely, while the police stop question asks whether the respondent \emph{or anyone in their family} was stopped in the past year, the arrest question asks only about the individual respondent.
-While this may muddy the water between direct and proximal contact with the criminal legal system, we expect that the national survey data will give us some insight into the uniquely politicizing nature of police stops for Black Americans.
-
-\hypertarget{results}{%
-\section*{Results}\label{results}}
-\addcontentsline{toc}{section}{Results}
-
-As discussed above, we begin by examining whether the turnout of individuals stopped before an election was different from those stopped after the election in Hillsborough County, Florida.
-We also test the relationship between police stops and turnout in the 2020 election using survey data.
-
-\hypertarget{individual-level-results}{%
-\subsection*{Individual-Level Results}\label{individual-level-results}}
-\addcontentsline{toc}{subsection}{Individual-Level Results}
-
-To observe the effect of being stopped by the police on voter participation, we now turn to our individual-level analysis in Hillsborough County, Florida.
-As discussed above, we match individuals who were stopped between the 2012 and 2018 elections to individuals who were stopped following the subsequent general election.\footnote{Due to computing constraints, a 5 percent random sample stratified by treatment status is used to calculate the genetic weights.
-The full sample is used in the actual matching process.} Matching is done with replacement and ties are not broken.
-This means that some treated voters have multiple controls; the regression weights are calculated to account for this possibility.
-In Table \ref{tab:balance} we present the results of the matching algorithm.
-As the table demonstrates, the selected control voters are very similar to the treated voters.
-
-\begin{singlespace}
-\input{"../temp/balance_table.tex"}
-\end{singlespace}
-
-It is worth noting that voters who were stopped between 2012 and 2020 were far more likely to be Black and male than the general electorate, and live in Census block groups with moderately lower incomes.
-
-In Figure \ref{fig:did-1}, we plot the turnout of treated and control voters in the elections before and after the treated voter was stopped.
-In the top row, we present the turnout in 2008--2014 of the individuals stopped between 2012 and 2014 and their controls; the second row shows the 2010--2016 turnout for individuals stopped between 2014 and 2016 and their controls; and the third shows the treatment effect for those stopped in the 2 years prior to the 2018 midterms.
-Finally, in the bottom row, we present the overall turnout effects for these three elections.
-The first election following a treated voter's stop is denoted as \emph{t = 0} while the years in which \emph{t} is less than zero are the periods prior to the stop.
+\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout}\label{fig:did-primary}
+\end{figure}
 
@@
 
-{\centering \includegraphics{draft_paper_files/figure-latex/did1-1}
+{\centering \includegraphics{compile_files/figure-latex/did-no-prior-1}
 
@@
 
-\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout}\label{fig:did1}
+\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout (no prior turnout in match)}\label{fig:did-no-prior}
 \end{figure}
 
-Figure \ref{fig:did-1} makes a number of things immediately apparent.
-First, we can see that for both Black and non-Black voters the pre-treatment trends are identical.
-This, combined with the fact that treated and control voters mirror one another in terms of other characteristics, lends credibility to the parallel trends assumption.
-Secondly, Figure \ref{fig:did-1} provides preliminary visual evidence of the demobilizing effects of police stops in Hillsborough County.
-However, as the figure also makes clear, it seems that the negative effects are concentrated in the lower-salience midterm elections; there is little evidence of turnout effects in the 2016 presidential election.
+\begin{figure}[H]
 
-Table \ref{tab:dind-table} formalizes the final row of Figure \ref{fig:did-1} into an ordinary least squares regression (the regression tables broken out for each year and including the coefficients for the matching covariates can be found in section 3 of the SI).
-Models 1 and 2 show our overall causal effect, while models 3 and 4 allow for the possibility that a ticket differentially mobilizes Black voters.
-In models 1 and 3, we include only the treatment, timing, and race dummies, while the full set of covariates used for the matching procedure are included in models 2 and 4.
-The empirical estimands are \emph{Treated × Post Treatment} and \emph{Treated × Post Treatment × Black}.
-In models 1 and 2, the coefficient on \emph{Treated × Post Treatment} measures the overall treatment effect, and in models 3 and 4 it measures the treatment effect for non-Black voters.
-The coefficient on \emph{Treated × Post Treatment × Black} measures any effect for Black voters above-and-beyond the effect measured for non-Black voters.
-
-\begin{singlespace}
-\input{"../temp/small_two_matches_reg_y_overall.tex"}
-\end{singlespace}
-
-As both Figure \ref{fig:did-1} and Table \ref{tab:dind-table} make clear, traffic stops meaningfully depressed turnout.
-In models 1 and 2, the estimated overall treatment effect is -1.5 percentage points.
-In models 3 and 4, we can see that a stop was less demobilizing for Black individuals than for others---non-Black turnout was depressed by 1.7 percentage points, while the negative effect was just 1.2 points for Black individuals.
-Although the treatment effect is still substantively quite large for Black individuals, Hillsborough County Black voters' turnout in federal elections was not as negatively impacted by police contact as that of non-Black individuals.
-It is also clear that midterm turnout is more impacted by these stops---as we show in section 3 of the SI, the negative impact is statistically significant in all years for non-Black residents, but much smaller in 2016 (-0.6pp) than in 2014 (-1.9pp) or 2018 (-3.0pp),
-
-\hypertarget{national-survey-data-1}{%
-\subsection*{National Survey Data}\label{national-survey-data-1}}
-\addcontentsline{toc}{subsection}{National Survey Data}
-
-In this section we make use of the American National Election Studies 2020 Time Series Data (ANES).
-The first test is simple: we ask whether, after controlling for standard covariates, having personal or proximal contact with a police stop in the previous 12 months is associated with whether a respondent voted in the 2020 presidential election.
-We also ask whether this relationship was different for Black and non-Black respondents.
-Finally, we use the ANES data to reconfirm prior literature demonstrating that higher-level contact with the criminal legal system is associated with lower turnout, as these relationships could have changed in the aftermath of the widespread protests following the police murder of George Floyd in 2020.
-
-Roughly 15 percent of non-Black respondents reported a police stop in the preceding 12 months, while the same was true for more than 22 percent of Black respondents.
-In Figure \ref{fig:anes} we present the results of our econometric models.
-In the left-hand panel, we show the predicted turnout of respondents who answered ``yes'' or ``no'' to the question \emph{During the past 12 months, were you or any of your family members stopped or questioned by a police officer, or did this not happen in the past 12 months?} The right-hand panel, meanwhile, plots these relationships for respondents who answered ``yes'' or ``no'' to the question \emph{Have you ever been arrested, or has that never happened to you?}.
-These are the predicted probabilities after controlling for respondents' race / ethnicity; age; party; ideology; income; education; and 2016 turnout.
-The full regression table can be found in section XX of the SI.
-
-\begin{figure}[!htpb]
-
-{\centering \includegraphics{draft_paper_files/figure-latex/anes-cross-1}
+{\centering \includegraphics{compile_files/figure-latex/did-no-matching-1}
 
@@
 
-\caption{\label{fig:anes}Predicted Turnout, 2020}\label{fig:anes-cross}
+\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout (no matching at all)}\label{fig:did-no-matching}
 \end{figure}
 
-Figure \ref{fig:anes} demonstrates that Black voters who were stopped by the police, or had a family member stopped by the police, were substantially more likely to vote in 2020 than Black individuals with neither direct nor proximal contact with a police stop (\emph{p} = 0.004).
-The same was not true for non-Black respondents, for whom contact with a police stop was not statistically associated with turnout in 2020 (\emph{p} = 0.07).
-Importantly, this effect is not a remnant of a white--nonwhite divide.
-As we show in the SI, police stops were not differently related to turnout for Latinos than for non-Latinos; nor did they impact turnout differently for Asians than for non-Asians.
-The ANES results point, then, to the fact that police stops are uniquely associated with higher turnout for Black respondents.
+Tables 1--4 are with prior turnout in the match. Tables 5--8 have no prior turnout. Table 9--12 have no matching at all
 
-The second panel of Figure \ref{fig:anes} shows that, as expected, respondents who had been arrested at some point turned out at lower rates, after controlling for relevant characteristics.
-Importantly, the interaction between arrest status and the respondent's race was not statistically significant.
-In other words, although police stops seem to be uniquely mobilizing for Black Americans, we fail to uncover evidence that arrests differentially structured subsequent Black and non-Black turnout.
+\begin{singlespace}
+\input{"../temp/small_two_matches_reg_overall.tex"}
+\input{"../temp/small_two_matches_reg_2014-11-04.tex"}
+\input{"../temp/small_two_matches_reg_2016-11-08.tex"}
+\input{"../temp/small_two_matches_reg_2018-11-06.tex"}
 
-It is worth re-establishing that cross-sectional results cannot establish causality.
-It is possible that Black respondents who had been stopped by the police (or had family members who experienced a stop) differed from non-Black respondents with such contact in ways that cannot be captured by the survey data.
-However, our findings are consistent with a causal story that police stops are uniquely mobilizing for Black Americans---but this is not the case for higher-level contact, such as arrests.
+\input{"../temp/small_table_overall_no_prior.tex"}
+\input{"../temp/small_table_2014-11-04_no_prior.tex"}
+\input{"../temp/small_table_2016-11-08_no_prior.tex"}
+\input{"../temp/small_table_2018-11-06_no_prior.tex"}
 
-\hypertarget{discussion}{%
-\section*{Discussion}\label{discussion}}
-\addcontentsline{toc}{section}{Discussion}
+\input{"../temp/small_two_matches_reg_overall_no_matching.tex"}
+\input{"../temp/small_two_matches_reg_2014-11-04_no_matching.tex"}
+\input{"../temp/small_two_matches_reg_2016-11-08_no_matching.tex"}
+\input{"../temp/small_two_matches_reg_2018-11-06_no_matching.tex"}
+\end{singlespace}
 
-While existing sociological and political science literature has examined the rise and collateral consequences of criminalization on political socialization, no study has investigated the causal relationship between ticketing and voter turnout using individual-level administrative data.
+\begin{figure}[H]
 
-Given how widespread police stops are and their relationship to racial injustice, their political implications demand close study.
-Accordingly, we investigate this question using two different data sources and analytic strategies.
-What we find complicates our understanding of how lower-level police contact affects political participation.
-In the analysis of Hillsborough County police stops, we find that stops reduce the voter turnout of non-Black voters, with a smaller negative effect for Black voters.
-On the other hand, the descriptive analysis of national survey data indicates that police contact is associated with \emph{higher} turnout for Black Americans, and \emph{unrelated} to turnout for others.
-Despite this incongruence, both analyses indicate that police stops have different participatory effects for Black individuals than for others.
-In this sense, our results point in the same direction.
-We conclude that the political consequences of police stops are unique for Black Americans---and that they are less demobilizing for Black Americans than others.
-Additionally, as \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020b}) suggests, ticketed Black individuals may be politically mobilized for activities other than voting not observed in this study, such as contacting elected representatives or volunteering for campaigns.
-To that end, it is also worth noting that our causal analysis tests the effect of personal police contact rather than proximal contact, which was the focus of \protect\hyperlink{ref-Walker2020a}{Walker} (\protect\hyperlink{ref-Walker2020a}{2020b})---it could be the case that mobilizing effects of low-level police contact come from proximal exposure rather than personal.
+{\centering \includegraphics{compile_files/figure-latex/coef-plot-primary-1}
 
-Our findings have several implications for political science scholarship.
-While existing literature suggests that the most disruptive forms of criminal legal contact (i.e.~criminal convictions and incarceration) consistently discourage voting (\protect\hyperlink{ref-Lerman2014}{Lerman and Weaver 2014}; \protect\hyperlink{ref-Burch2011}{Burch 2011}; \protect\hyperlink{ref-White2019a}{White 2019b}), research regarding police stops has produced more mixed results (\protect\hyperlink{ref-Laniyonu2019}{Laniyonu 2019}).
-We extend this theory to police ticketing, the most common form of police contact in America, and find that police traffic stops generally reduce turnout.
-For Black voters, however, our findings suggest that traffic stops are less demobilizing, a sharp contrast with existing scholarship wherein more disruptive forms of criminalization discourage Black voters more than non-Black voters.
-Particularly following the rise of the Black Lives Matter movement in 2013, our findings constitute new evidence in support of our theory that ticketing is distinct from other forms of criminal legal contact and therefore catalyzes different political behaviors among Black voters, who are disproportionately affected by both ticketing and criminalization in general.
+}
 
-In this sense, our analysis could be consistent with a political contestation of criminal legal policy, a phenomenon that aligns with dozens of recent campaigns to reform local fines and fees practices (or abolish them entirely).\footnote{See \url{https://finesandfeesjusticecenter.org/clearinghouse}.} We know that increased fines and fees result from political economy (i.e.~austerity at the federal level), but our analysis suggests that this could be a ``two way street'' wherein people who are harmed by policing practices can be politically socialized into resistance.
+\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout}\label{fig:coef-plot-primary}
+\end{figure}
 
-\textbf{Limitations}: In our analysis of Hillsborough County voters, we do not look at people who were not registered to vote in 2018.
-Because we cannot tell whether unregistered individuals who were stopped in Hillsborough County were unregistered because they were \emph{ineligible} to do so (by virtue of living in a different county or being a non-citizen, for instance) or chose to eschew electoral politics, our analysis is necessarily limited to individuals who were registered to vote.
-This likely makes our results conservative: we cannot capture the lost participation of individuals who would have registered and voted if they were not stopped by the police.
+\begin{figure}[H]
 
-\textbf{Future research}: This work looks at the difference between the political behavior of Black and non-Black Americans.
-Future work should explore variation \emph{within} the Black community.
-When is this sort of contact mobilizing?
-For whom?
-Can organizers build on this potential for broad-based political action?
-We were unable to test whether what we observed was simply \emph{decreased} demobilization, or whether some subgroups of the Black population were mobilized while others were demobilized.
-Put differently: it could be the case that ticketing is demobilizing for most voters of all races, but that a subset of the Black population is affirmatively mobilized, leading to lower group-level demobilization.
-Scholars should also investigate the interactive effects of criminal legal contact, asking whether police stops result in different political behavior for formerly incarcerated individuals than individuals with no other contact with the system.
+{\centering \includegraphics{compile_files/figure-latex/coef-plot-no-prior-1}
 
-Finally, we are sensitive to the fact that although administrative data provides real-world evidence of actual behavior, such an approach limits our ability to understand the causal mechanisms in play.
-This means that although we demonstrate that police stops are demobilizing, future work must further investigate how stops are interpreted by individuals and translated into political behavior.
+}
 
-Although we have contributed new evidence suggesting that police stops and related exploitative ticketing practices may not demobilize Black voters to the same extent as non-Black voters, we emphasize that this finding does not redeem or justify such police practices.
-Black Americans already suffer from disproportionate police contact and the racial wealth gap, and racist revenue-motivated ticketing only increases the burden on Black communities nationwide.
-Policymakers should work to ensure that Black Americans no longer have to struggle to enjoy the same political power as whites---to that end, the current trend of voting rights restriction policies across the country is especially pernicious.
-Even if some Black Americans understand the ballot box as one tool they can use to limit the state's power to exploit and harm them, policymakers should still feel an obligation to support voting rights protections and stop disproportionate ticketing in Black communities.
+\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout (no prior turnout in match)}\label{fig:coef-plot-no-prior}
+\end{figure}
 
-\newpage
+\begin{figure}[H]
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
+{\centering \includegraphics{compile_files/figure-latex/event-study-primary-1}
 
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-Ang2021}{}%
-Ang, Desmond, Panka Bencsik, Jesse Bruhn, and Ellora Derenoncourt. 2021. {``Police {Violence Reduces Civilian Cooperation} and {Engagement} with {Law Enforcement}.''} \emph{Working Paper.}, September.
+}
 
-\leavevmode\hypertarget{ref-Baumgartner2018}{}%
-Baumgartner, Frank R, Derek A Epp, and Kelsey Shoub. 2018. \emph{Suspect Citizens: What 20 Million Traffic Stops Tell Us about Policing and Race}.
+\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout}\label{fig:event-study-primary}
+\end{figure}
 
-\leavevmode\hypertarget{ref-Bell2017}{}%
-Bell, Monica C. 2017. {``Police {Reform} and the {Dismantling} of {Legal Estrangement}.''} \emph{The Yale Law Journal} 126 (7): 2054--150.
+\begin{figure}[H]
 
-\leavevmode\hypertarget{ref-Brayne2014}{}%
-Brayne, Sarah.
-2014.
-{``Surveillance and {System Avoidance}: {Criminal Justice Contact} and {Institutional Attachment}.''} \emph{American Sociological Review} 79 (3): 367--91.
-\url{https://doi.org/10.1177/0003122414530398}.
+{\centering \includegraphics{compile_files/figure-latex/event-study-no-prior-1}
 
-\leavevmode\hypertarget{ref-Burch2011}{}%
-Burch, Traci R.
-2011.
-{``Turnout and {Party Registration} Among {Criminal Offenders} in the 2008 {General Election}.''} \emph{Law \& Society Review} 45 (3): 699--730.
-\url{https://doi.org/10.1111/j.1540-5893.2011.00448.x}.
+}
 
-\leavevmode\hypertarget{ref-Burch2014}{}%
----------.
-2014.
-{``Effects of {Imprisonment} and {Community Supervision} on {Neighborhood Political Participation} in {North Carolina}.''} \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 184--201.
-\url{https://doi.org/10.1177/0002716213503093}.
+\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout (no prior turnout in match)}\label{fig:event-study-no-prior}
+\end{figure}
 
-\leavevmode\hypertarget{ref-CarpenterII2019}{}%
-Carpenter II, Dick M, Kyle Sweetland, and Jennifer McDonald.
-2019.
-{``The {Price} of {Taxation} by {Citation}: {Case Studies} of {Three Georgia Cities That Rely Heavily} on {Fines} and {Fees}.''} {Institute for Justice}.
+\begin{figure}[H]
 
-\leavevmode\hypertarget{ref-Desmond2016}{}%
-Desmond, Matthew, Andrew V.
-Papachristos, and David S.
-Kirk.
-2016.
-{``Police {Violence} and {Citizen Crime Reporting} in the {Black Community}.''} \emph{American Sociological Review} 81 (5): 857--76.
-\url{https://doi.org/10.1177/0003122416663494}.
+{\centering \includegraphics{compile_files/figure-latex/black-overall-primary-1}
 
-\leavevmode\hypertarget{ref-Desmond2020}{}%
----------. 2020. {``Evidence of the {Effect} of {Police Violence} on {Citizen Crime Reporting}.''} \emph{American Sociological Review} 85 (1): 184--90. \url{https://doi.org/10.1177/0003122419895979}.
+}
 
-\leavevmode\hypertarget{ref-Epp2014}{}%
-Epp, Charles R., Steven Maynard-Moody, and Donald P. Haider-Markel. 2014. \emph{Pulled {Over}}. {The University of Chicago Press}.
+\caption{\label{fig:did-1}Black Overall}\label{fig:black-overall-primary}
+\end{figure}
 
-\leavevmode\hypertarget{ref-Gerber2015}{}%
-Gerber, Alan S., Gregory A.
-Huber, Marc Meredith, Daniel R.
-Biggers, and David J.
-Hendry.
-2015.
-{``Can {Incarcerated Felons Be} ({Re})integrated into the {Political System}?
-{Results} from a {Field Experiment}.''} \emph{American Journal of Political Science} 59 (4): 912--26.
-\url{https://doi.org/10.1111/ajps.12166}.
+\begin{figure}[H]
 
-\leavevmode\hypertarget{ref-Gerber2017}{}%
----------.
-2017.
-{``Does {Incarceration Reduce Voting}?
-{Evidence} about the {Political Consequences} of {Spending Time} in {Prison}.''} \emph{The Journal of Politics} 79 (4): 1130--46.
-\url{https://doi.org/10.1086/692670}.
+{\centering \includegraphics{compile_files/figure-latex/black-overall-no-prior-1}
 
-\leavevmode\hypertarget{ref-Harrell2020}{}%
-Harrell, Erika, and Elizabeth Davis. 2020. {``Contacts {Between Police} and the {Public}, 2018 - {Statistical Tables}.''} {Bureau of Justice Statistics}.
+}
 
-\leavevmode\hypertarget{ref-Harris2017}{}%
-Harris, Alexes, Beth Huebner, Karin Martin, Mary Pattillo, Becky Pettit, Sarah Shannon, Bryan Sykes, Chris Uggen, and April Fernandes.
-2017.
-{``Monetary {Sanctions} in the {Criminal Justice System}.''}
+\caption{\label{fig:did-1}Black Overall (no prior turnout in match)}\label{fig:black-overall-no-prior}
+\end{figure}
 
-\leavevmode\hypertarget{ref-Harris2020}{}%
-Harris, Allison P., Elliott Ash, and Jeffrey Fagan.
-2020.
-{``Fiscal {Pressures} and {Discriminatory Policing}: {Evidence} from {Traffic Stops} in {Missouri}.''} \emph{Journal of Race, Ethnicity, and Politics} 5 (3): 450--80.
-\url{https://doi.org/10.1017/rep.2020.10}.
+\begin{figure}[H]
 
-\leavevmode\hypertarget{ref-Imai2020}{}%
-Imai, Kosuke, In Song Kim, and Erik Wang.
-2020.
-{``Matching {Methods} for {Causal Inference} with {Time-Series Cross-Sectional Data}.''} \emph{Working Paper}.
-\url{https://doi.org/Matching\%20Methods\%20for\%20Causal\%20Inference\%20with\%20Time-Series\%20Cross-Sectional\%20Data}.
+{\centering \includegraphics{compile_files/figure-latex/black-relative-primary-1}
 
-\leavevmode\hypertarget{ref-Jones2019}{}%
-Jones, Alexi, and Wendy Sawyer. 2019. {``Arrest, Release, Repeat: {How} Police and Jails Are Misused to Respond to Social Problems.''} {Prison Policy Initiative}.
+}
 
-\leavevmode\hypertarget{ref-Justice2014}{}%
-Justice, Benjamin, and Tracey L.
-Meares.
-2014.
-{``How the {Criminal Justice System Educates Citizens}.''} \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 159--77.
-\url{https://doi.org/10.1177/0002716213502929}.
+\caption{\label{fig:did-1}Black Relative}\label{fig:black-relative-primary}
+\end{figure}
 
-\leavevmode\hypertarget{ref-Laniyonu2019}{}%
-Laniyonu, Ayobami. 2019. {``The {Political Consequences} of {Policing}: {Evidence} from {New York City}.''} \emph{Political Behavior} 41 (2): 527--58. \url{https://doi.org/10.1007/s11109-018-9461-9}.
+\begin{figure}[H]
 
-\leavevmode\hypertarget{ref-Lee2015}{}%
-Lee, Hedwig, Tyler McCormick, Margaret T.
-Hicken, and Christopher Wildeman.
-2015.
-{``Racial {Inequalities} in {Connectedness} to {Imprisoned Individuals} in the {United States}.''} \emph{Du Bois Review: Social Science Research on Race} 12 (2): 269--82.
-\url{https://doi.org/10.1017/S1742058X15000065}.
+{\centering \includegraphics{compile_files/figure-latex/black-relative-no-prior-1}
 
-\leavevmode\hypertarget{ref-Lee2014}{}%
-Lee, Hedwig, Lauren C.
-Porter, and Megan Comfort.
-2014.
-{``Consequences of {Family Member Incarceration}: {Impacts} on {Civic Participation} and {Perceptions} of the {Legitimacy} and {Fairness} of {Government}.''} \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 44--73.
-\url{https://doi.org/10.1177/0002716213502920}.
+}
 
-\leavevmode\hypertarget{ref-Lerman2014}{}%
-Lerman, Amy E., and Vesla M.
-Weaver.
-2014.
-\emph{Arresting Citizenship: The Democratic Consequences of {American} Crime Control}.
-Chicago Studies in {American} Politics.
-{Chicago ; London}: {The University of Chicago Press}.
+\caption{\label{fig:did-1}Black Relative (no prior turnout in match)}\label{fig:black-relative-no-prior}
+\end{figure}
 
-\leavevmode\hypertarget{ref-Levenson2021}{}%
-Levenson, Michael. 2021. {``Pulled {Over}: {What} to {Know About Deadly Police Traffic Stops}.''} \emph{The New York Times}, October.
+\begin{figure}[H]
 
-\leavevmode\hypertarget{ref-Lundberg2021}{}%
-Lundberg, Ian, Rebecca Johnson, and Brandon M.
-Stewart.
-2021.
-{``What {Is Your Estimand}?
-{Defining} the {Target Quantity Connects Statistical Evidence} to {Theory}.''} \emph{American Sociological Review} 86 (3): 532--65.
-\url{https://doi.org/10.1177/00031224211004187}.
+{\centering \includegraphics{compile_files/figure-latex/non-black-primary-1}
 
-\leavevmode\hypertarget{ref-McCoy2015}{}%
-McCoy, Terrence. 2015. {``Ferguson Shows How a Police Force Can Turn into a Plundering {`Collection Agency'}.''} \emph{Washington Post}, March.
+}
 
-\leavevmode\hypertarget{ref-Meares2017}{}%
-Meares, Tracey. 2017. {``Policing and {Procedural Justice}: {Shaping Citizens}' {Identities} to {Increase Democratic Participation}.''} \emph{Northwestern University Law Review} 111 (6): 1525--36.
+\caption{\label{fig:did-1}Nonblack}\label{fig:non-black-primary}
+\end{figure}
 
-\leavevmode\hypertarget{ref-Meredith2014}{}%
-Meredith, Marc, and Michael Morse.
-2014.
-{``Do {Voting Rights Notification Laws Increase Ex-Felon Turnout}?''} \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 220--49.
-\url{https://doi.org/10.1177/0002716213502931}.
+\begin{figure}[H]
 
-\leavevmode\hypertarget{ref-Meredith2015}{}%
----------.
-2015.
-{``The {Politics} of the {Restoration} of {Ex-Felon Voting Rights}: {The Case} of {Iowa}.''} \emph{Quarterly Journal of Political Science} 10 (1): 41--100.
-\url{https://doi.org/10.1561/100.00013026}.
+{\centering \includegraphics{compile_files/figure-latex/non-black-no-prior-1}
 
-\leavevmode\hypertarget{ref-Morris2020}{}%
-Morris, Kevin.
-2020.
-{``Neighborhoods and {Felony Disenfranchisement}: {The Case} of {New York City}.''} \emph{Urban Affairs Review}, May, 1078087420921522.
-\url{https://doi.org/10.1177/1078087420921522}.
+}
 
-\leavevmode\hypertarget{ref-Morris2021a}{}%
----------.
-2021a.
-{``Welcome {Home}{{Now Vote}}!
-{Voting Rights Restoration} and {Postsupervision Participation}.''} \emph{Social Science Quarterly} 102 (1): 140--53.
-\url{https://doi.org/10.1111/ssqu.12901}.
+\caption{\label{fig:did-1}Nonblack (no prior turnout in match)}\label{fig:non-black-no-prior}
+\end{figure}
 
-\leavevmode\hypertarget{ref-Morris2021}{}%
----------.
-2021b.
-{``Turnout and {Amendment Four}: {Mobilizing Eligible Voters Close} to {Formerly Incarcerated Floridians}.''} \emph{American Political Science Review}, April, 1--16.
-\url{https://doi.org/10.1017/S0003055421000253}.
+\begin{figure}[H]
 
-\leavevmode\hypertarget{ref-Nyhan2017}{}%
-Nyhan, Brendan, Christopher Skovron, and Rocío Titiunik.
-2017.
-{``Differential {Registration Bias} in {Voter File Data}: {A Sensitivity Analysis Approach}.''} \emph{American Journal of Political Science} 61 (3): 744--60.
-\url{https://doi.org/10.1111/ajps.12288}.
+{\centering \includegraphics{compile_files/figure-latex/overall-time-primary-1}
 
-\leavevmode\hypertarget{ref-Pacewicz2020}{}%
-Pacewicz, Josh, and John N.
-Robinson III.
-2020.
-{``Pocketbook Policing: {How} Race Shapes Municipal Reliance on Punitive Fines and Fees in the {Chicago} Suburbs.''} \emph{Socio-Economic Review}, no.
-mwaa029 (October).
-\url{https://doi.org/10.1093/ser/mwaa029}.
+}
 
-\leavevmode\hypertarget{ref-Remster2018a}{}%
-Remster, Brianna, and Rory Kramer.
-2018.
-{``Race, {Space}, and {Surveillance}: {Understanding} the {Relationship} Between {Criminal Justice Contact} and {Institutional Involvement}.''} \emph{Socius} 4 (January).
-\url{https://doi.org/10.1177/2378023118761434}.
+\caption{\label{fig:did-1}Black Relative}\label{fig:overall-time-primary}
+\end{figure}
 
-\leavevmode\hypertarget{ref-Sances2017}{}%
-Sances, Michael W., and Hye Young You.
-2017.
-{``Who {Pays} for {Government}?
-{Descriptive Representation} and {Exploitative Revenue Sources}.''} \emph{The Journal of Politics} 79 (3): 1090--94.
-\url{https://doi.org/10.1086/691354}.
+\begin{figure}[H]
 
-\leavevmode\hypertarget{ref-Sanders2017}{}%
-Sanders, Topher, and Benjamin Conarck. 2017. {``Florida {Police Issue Hundreds} of {Bad Pedestrian Tickets Every Year Because They Don}'t {Seem} to {Know} the {Law}.''} \emph{ProPublica}, December.
+{\centering \includegraphics{compile_files/figure-latex/overall-time-no-prior-1}
 
-\leavevmode\hypertarget{ref-Sekhon2011}{}%
-Sekhon, Jasjeet S.
-2011.
-{``Multivariate and {Propensity Score Matching Software} with {Automated Balance Optimization}: {The Matching} Package for {R}.''} \emph{Journal of Statistical Software} 42 (7): 1--52.
-\url{https://doi.org/10.18637/jss.v042.i07}.
+}
 
-\leavevmode\hypertarget{ref-Shaer2019}{}%
-Shaer, Matthew. 2019. {``How {Cities Make Money} by {Fining} the {Poor}.''} \emph{The New York Times}, January.
-
-\leavevmode\hypertarget{ref-Singla2020}{}%
-Singla, Akheil, Charlotte Kirschner, and Samuel B.
-Stone.
-2020.
-{``Race, {Representation}, and {Revenue}: {Reliance} on {Fines} and {Forfeitures} in {City Governments}.''} \emph{Urban Affairs Review} 56 (4): 1132--67.
-\url{https://doi.org/10.1177/1078087419834632}.
-
-\leavevmode\hypertarget{ref-Soss2017}{}%
-Soss, Joe, and Vesla Weaver.
-2017.
-{``Police {Are Our Government}: {Politics}, {Political Science}, and the {Policing} of {Race}{{Class Subjugated Communities}}.''} \emph{Annual Review of Political Science} 20 (1): 565--91.
-\url{https://doi.org/10.1146/annurev-polisci-060415-093825}.
-
-\leavevmode\hypertarget{ref-Stuart2016}{}%
-Stuart, Forrest.
-2016.
-{``Becoming {`{Copwise}'}: {Policing}, {Culture}, and the {Collateral Consequences} of {Street-Level Criminalization}.''} \emph{Law \& Society Review} 50 (2): 279--313.
-\url{https://doi.org/10.1111/lasr.12201}.
-
-\leavevmode\hypertarget{ref-Tyler2014}{}%
-Tyler, Tom R., Jeffrey Fagan, and Amanda Geller.
-2014.
-{``Street {Stops} and {Police Legitimacy}: {Teachable Moments} in {Young Urban Men}'s {Legal Socialization}.''} \emph{Journal of Empirical Legal Studies} 11 (4): 751--85.
-\url{https://doi.org/10.1111/jels.12055}.
-
-\leavevmode\hypertarget{ref-Uggen2002}{}%
-Uggen, Christopher, and Jeff Manza.
-2002.
-{``Democratic {Contraction}?
-{Political Consequences} of {Felon Disenfranchisement} in the {United States}.''} \emph{American Sociological Review} 67 (6): 777--803.
-\url{https://doi.org/10.2307/3088970}.
-
-\leavevmode\hypertarget{ref-UnitedStatesDepartmentofJusticeCivilRightsDivision2015}{}%
-United States Department of Justice Civil Rights Division. 2015. {``Investigation of the {Ferguson Police Department}.''}
-
-\leavevmode\hypertarget{ref-Walker2014}{}%
-Walker, Hannah L.
-2014.
-{``Extending the {Effects} of the {Carceral State}: {Proximal Contact}, {Political Participation}, and {Race}.''} \emph{Political Research Quarterly}, July.
-\url{https://doi.org/10.1177/1065912914542522}.
-
-\leavevmode\hypertarget{ref-Walker2020}{}%
----------. 2020a. \emph{Mobilized by Injustice: Criminal Justice Contact, Political Participation, and Race}. {NewYork}: {Oxford University Press 2020}.
-
-\leavevmode\hypertarget{ref-Walker2020a}{}%
----------. 2020b. {``Targeted: {The Mobilizing Effect} of {Perceptions} of {Unfair Policing Practices}.''} \emph{The Journal of Politics} 82 (1): 119--34. \url{https://doi.org/10.1086/705684}.
-
-\leavevmode\hypertarget{ref-Weaver2010}{}%
-Weaver, Vesla M., and Amy E.
-Lerman.
-2010.
-{``Political {Consequences} of the {Carceral State}.''} \emph{American Political Science Review} 104 (4): 817--33.
-\url{https://doi.org/10.1017/S0003055410000456}.
-
-\leavevmode\hypertarget{ref-Weaver2020}{}%
-Weaver, Vesla M., Gwen Prowse, and Spencer Piston.
-2020.
-{``Withdrawing and {Drawing In}: {Political Discourse} in {Policed Communities}.''} \emph{Journal of Race, Ethnicity, and Politics} 5 (3): 604--47.
-\url{https://doi.org/10.1017/rep.2019.50}.
-
-\leavevmode\hypertarget{ref-White2019}{}%
-White, Ariel.
-2019a.
-{``Family {Matters}?
-{Voting Behavior} in {Households} with {Criminal Justice Contact}.''} \emph{American Political Science Review} 113 (2): 607--13.
-\url{https://doi.org/10.1017/S0003055418000862}.
-
-\leavevmode\hypertarget{ref-White2019a}{}%
----------.
-2019b.
-{``Misdemeanor {Disenfranchisement}?
-{The Demobilizing Effects} of {Brief Jail Spells} on {Potential Voters}.''} \emph{American Political Science Review} 113 (2): 311--24.
-\url{https://doi.org/10.1017/S000305541800093X}.
-
-\leavevmode\hypertarget{ref-Zoorob2020}{}%
-Zoorob, Michael.
-2020.
-{``Do {Police Brutality Stories Reduce} 911 {Calls}?
-{Reassessing} an {Important Criminological Finding}.''} \emph{American Sociological Review} 85 (1): 176--83.
-\url{https://doi.org/10.1177/0003122419895254}.
-
-\end{CSLReferences}
+\caption{\label{fig:did-1}Black Relative (no prior turnout in match)}\label{fig:overall-time-no-prior}
+\end{figure}
 

### 2022-05-04 code/00_initialize.R

@@ -29,4 +29,5 @@ options("modelsummary_format_numeric_latex" = "plain")
 cleanup <- function(...){
   save2 <- c(save, ...)
   rm(list=ls(envir = .GlobalEnv)[! ls(envir = .GlobalEnv) %in% save2], envir = .GlobalEnv)
+  gc()
 }

### 2022-05-04 code/02_hills/02_download_hills_stops.R

@@ -1,68 +1,66 @@
-# hills_stops <- rbindlist(lapply(c(2003:2021), function(l){
-#   print(l)
-#   if(l != "J"){
-#   if(!(file.exists(paste0("raw_data/hills_stops/civil_stops_", l, ".csv")))){
-#     download.file(paste0("https://publicrec.hillsclerk.com/Traffic/Civil_Traffic_Name_Index_files/Civil_Traffic_Name_Index_", l, ".csv"),
-#                   paste0("raw_data/hills_stops/civil_stops_", l, ".csv"))
-#   }
-# 
-#   ja <- fread(paste0("raw_data/hills_stops/civil_stops_", l, ".csv"))
-# 
-#   colnames(ja) <- clean_names(ja)
-# 
-#   ja <- ja %>%
-#     filter(!grepl("cam", tolower(statute_description))) %>%
-#     select(last_name, first_name, middle_name,
-#            date_of_birth,
-#            street = address_line_1,
-#            city,
-#            state,
-#            zip = zip_code,
-#            offense_date,
-#            amount_paid,
-#            law_enf_agency_name) %>%
-#     mutate(civil = 1,
-#            tampa_pd = grepl("tampa police", tolower(law_enf_agency_name)),
-#            tampa_pd = ifelse(tampa_pd, T, law_enf_agency_name == "TPD")) %>%
-#     select(-law_enf_agency_name)
-# 
-#   return(ja)
-#   }
-# }))
-# 
-# hills_stops_cr <- rbindlist(lapply(c(2003:2021), function(l){
-#   print(l)
-#   if(l != "J"){
-#     if(!(file.exists(paste0("raw_data/hills_stops/crim_stops_", l, ".csv")))){
-#       download.file(paste0("https://publicrec.hillsclerk.com/Traffic/Criminal_Traffic_Name_Index_files/Criminal_Traffic_Name_Index_", l, ".csv"),
-#                     paste0("raw_data/hills_stops/crim_stops_", l, ".csv"))
-#     }
-# 
-#     ja <- fread(paste0("raw_data/hills_stops/crim_stops_", l, ".csv"))
-# 
-#     colnames(ja) <- clean_names(ja)
-# 
-#     ja <- ja %>%
-#       select(last_name, first_name, middle_name,
-#              date_of_birth,
-#              offense_date, amount_paid,
-#              law_enf_agency_name) %>%
[…]

### 2022-05-04 code/02_hills/03_genmatch_weights.R

@@ -101,6 +101,6 @@ match_data <- samp %>%
 genout <- GenMatch(Tr = samp$treated, X = match_data, replace = T, cluster = cl, pop.size = 1000,
                    exact = c(rep(T, 7), rep(F, 14)))
 
-saveRDS(genout, "temp/genout_hills_yem.rds")
+saveRDS(genout, "temp/genout_hills.rds")
 
 

### 2022-05-04 code/02_hills/04_match.R

@@ -87,7 +87,7 @@ X <- pre %>%
   mutate_at(vars(white, black, latino, asian, male, dem, rep, v1, v2, v3, paid), ~ ifelse(. == T, 1, 0)) %>% 
   select(first_tr_year, paid, civil, tampa_pd, v1, v2, v3, everything())
 
-genout <- readRDS("temp/genout_hills_yem.rds")
+genout <- readRDS("temp/genout_hills.rds")
 
 
 mout <- Matchby(Tr = pre$treated, X = X,
@@ -103,9 +103,9 @@ mout <- Matchby(Tr = pre$treated, X = X,
 
 
 
-save(mout, file = "./temp/mout_hills_y.RData")
+save(mout, file = "./temp/mout_hills.RData")
 
-load("temp/mout_hills_y.RData")
+load("temp/mout_hills.RData")
 
 matches <- data.table(voter = c(mout$index.control,
                                 mout$index.treated),
@@ -124,4 +124,4 @@ matches <- left_join(matches, ids, by = c("group" = "id")) %>%
   select(-group) %>%
   rename(group = voter_id)
 
-saveRDS(matches, "temp/matches_hills_yem.rds")
+saveRDS(matches, "temp/matches_hills.rds")

### 2022-05-04 code/02_hills/07_coefplot.R

@@ -1,0 +1,168 @@
+
+matches <- readRDS("temp/full_reg_data.rds")
+m1 <- to ~ treated * post + as.factor(year)
+m2 <- to ~ treated * post + as.factor(year) +
+  white + black + latino + asian + male +
+  dem + rep + age + reg_date + pre_stops + v1 + v2 + v3 +
+  median_income + some_college + unem + civil + paid + tampa_pd
+
+for(gg in c("overall", "2014-11-04", "2016-11-08", "2018-11-06")){
+  
+  if(gg == "overall"){
+    dat1 <- filter(matches, period <= 0.5)
+  }else{
+    dat1 <- dplyr::filter(matches, period <= 0.5, first_tr_year == gg)
+  }
+  
+  c1 <- confint(
+    feols(m1, dat1, weights = ~ weight, cluster = ~ group)
+  )
+  c1$term <- rownames(c1)
+  c1 <- c1 %>% 
+    mutate(model = 1,
+           year = gg,
+           t = "Overall")
+  
+  c2 <- confint(
+    feols(m2, dat1, weights = ~ weight, cluster = ~ group)
+  )
+  c2$term <- rownames(c2)
+  c2 <- c2 %>% 
+    mutate(model = 2,
+           year = gg,
+           t = "Overall")
+  ######
+  c3 <- confint(
+    feols(m1, filter(dat1, !black), weights = ~ weight, cluster = ~ group)
+  )
+  c3$term <- rownames(c3)
+  c3 <- c3 %>% 
+    mutate(model = 3,
+           year = gg,
+           t = "Non-Black")
+  
+  c4 <- confint(
+    feols(m1, filter(dat1, black), weights = ~ weight, cluster = ~ group)
+  )
+  c4$term <- rownames(c4)
+  c4 <- c4 %>% 
+    mutate(model = 3,
+           year = gg,
+           t = "Black")
+  ######
+  c5 <- confint(
+    feols(m2, filter(dat1, !black), weights = ~ weight, cluster = ~ group)
+  )
+  c5$term <- rownames(c5)
+  c5 <- c5 %>% 
+    mutate(model = 4,
+           year = gg,
+           t = "Non-Black")
+  
+  c6 <- confint(
+    feols(m2, filter(dat1, black), weights = ~ weight, cluster = ~ group)
+  )
+  c6$term <- rownames(c6)
+  c6 <- c6 %>% 
+    mutate(model = 4,
[…]

### 2022-05-04 code/02_hills/07_make_prox.R

@@ -1,68 +1,0 @@
-
-stopped <- readRDS("temp/hills_pre_match.rds")
-
-voters <- readRDS("temp/full_raw_coded_hills_w_bgs.rds") %>% 
-  filter(count == 1) %>% 
-  ungroup() %>% 
-  mutate_at(vars(street, city), tolower) %>% 
-  group_by(city, street) %>% 
-  mutate(count = n()) %>% 
-  filter(count <= 5) %>% 
-  ungroup() %>% 
-  select(-count)
-
-
-stopped <- left_join(stopped, select(voters, voter_id, street, city))
-
-
-ads <- stopped %>% 
-  mutate_at(vars(street, city), tolower) %>% 
-  group_by(first_tr_year, street, city) %>% 
-  tally() %>% 
-  select(-n)
-
-
-voters2 <- left_join(voters,
-                    ads)
-
-prox14 <- filter(voters2, first_tr_year == "2014-11-04",
-                 !(voter_id %in% filter(stopped, first_tr_year == "2014-11-04")$voter_id))
-
-prox16 <- filter(voters2, first_tr_year == "2016-11-08",
-                 !(voter_id %in% filter(stopped, first_tr_year == "2016-11-08")$voter_id))
-
-prox18 <- filter(voters2, first_tr_year == "2018-11-06",
-                 !(voter_id %in% filter(stopped, first_tr_year == "2018-11-06")$voter_id))
-
-prox20 <- filter(voters2, first_tr_year == "2020-11-03",
-                 !(voter_id %in% filter(stopped, first_tr_year == "2020-11-03")$voter_id))
-
-proximals <- bind_rows(prox14, prox16, prox18, prox20) %>% 
-  mutate(white = race == 5,
-         black = race == 3,
-         latino = race == 4,
-         asian = race == 2,
-         male = gender == "M",
-         dem = party_affiliation == "DEM",
-         rep = party_affiliation == "REP",
-         reg_date = as.Date(registration_date, "%m/%d/%Y")) %>% 
-  select(voter_id, GEOID,
-         white, black, latino, asian, male, dem, rep, age, 
-         reg_date, name_first, name_last, birth_date,
-         v08, v10, v12, v14, v16, v18, latitude, longitude, first_tr_year)
-
-#######################
-
-census <- readRDS("../regular_data/census_bgs_18.rds")
-
-proximals <- left_join(proximals, census %>% 
[…]

### 2022-05-04 code/02_hills/10_reg_prox.R

@@ -1,86 +1,0 @@
-
-#####
-hills_pre_match <- readRDS("temp/real_pre_match_hills_prox.rds") %>% 
-  ungroup()
-
-matches <- readRDS("temp/matches_hills_yem_prox.rds")
-
-matches <- left_join(matches, select(hills_pre_match, voter_id, first_tr_year),
-                     by = c("group" = "voter_id", "first_tr_year")) %>% 
-  mutate(fd = first_tr_year,
-         first_tr_year = ifelse(first_tr_year == 1, "2014-11-04",
-                                ifelse(first_tr_year == 2, "2016-11-08",
-                                       ifelse(first_tr_year == 3, "2018-11-06", "XX"))),
-         first_tr_year = as.Date(first_tr_year))
-
-hist <- readRDS("temp/full_raw_coded_hills_w_bgs.rds") %>%
-  select(voter_id, starts_with("v1"), v08) %>%
-  pivot_longer(!starts_with("vo"), names_to = "year", values_to = "to")
-
-elec_dates <- fread("raw_data/election_dates.csv")
-
-hist <- left_join(hist, elec_dates) %>% 
-  select(-year) %>% 
-  rename(year = date) %>% 
-  mutate(year = as.Date(year, "%m/%d/%Y"))
-
-
-matches <- left_join(matches, hist %>% 
-                       filter(year(year) %% 2 == 0), by = c("voter" = "voter_id"))
-
-periods <- fread("raw_data/period_lu.csv") %>% 
-  mutate_at(vars(first_tr_year, year), as.Date, "%m/%d/%Y")
-
-matches <- left_join(matches, periods) %>% 
-  filter(period %in% c(-2.5, -1.5, -.5, .5, 1.5))
-
-matches <- left_join(matches,
-                     hills_pre_match %>%
-                       select(-GEOID),
-                     by = c("voter" = "voter_id", "fd" = "first_tr_year"))
-
-matches <- left_join(matches,
-                     hills_pre_match %>%
-                       select(voter_id, first_tr_year, black_t = black,
-                              dem_t = dem),
-                     by = c("group" = "voter_id", "fd" = "first_tr_year")) %>% 
-  mutate(post = period >= 0.5,
-         treated = voter == group)
-
-cleanup("matches")
-gc()
-
-##########################################################
-ll <- matches %>%
-  filter(period <= 0.5) %>% 
-  group_by(treated, period, black_t) %>%
-  summarize(to = weighted.mean(to, weight)) %>% 
[…]

### 2022-05-04 code/02_hills/rob_other/coef_plot.R

@@ -1,0 +1,166 @@
+
+matches <- readRDS("temp/full_reg_data_no_matching.rds")
+m1 <- to ~ treated * post + as.factor(year)
+m2 <- to ~ treated * post + as.factor(year) +
+  white + black + latino + asian + male +
+  dem + rep + age + reg_date + pre_stops + v1 + v2 + v3 +
+  median_income + some_college + unem + civil + paid + tampa_pd
+
+for(gg in c("overall", "2014-11-04", "2016-11-08", "2018-11-06")){
+  
+  if(gg == "overall"){
+    dat1 <- filter(matches, period <= 0.5)
+  }else{
+    dat1 <- dplyr::filter(matches, period <= 0.5, first_tr_year == gg)
+  }
+  
+  c1 <- confint(
+    feols(m1, dat1, weights = ~ weight, cluster = ~ group)
+  )
+  c1$term <- rownames(c1)
+  c1 <- c1 %>% 
+    mutate(model = 1,
+           year = gg,
+           t = "Overall")
+  
+  c2 <- confint(
+    feols(m2, dat1, weights = ~ weight, cluster = ~ group)
+  )
+  c2$term <- rownames(c2)
+  c2 <- c2 %>% 
+    mutate(model = 2,
+           year = gg,
+           t = "Overall")
+  ######
+  c3 <- confint(
+    feols(m1, filter(dat1, !black), weights = ~ weight, cluster = ~ group)
+  )
+  c3$term <- rownames(c3)
+  c3 <- c3 %>% 
+    mutate(model = 3,
+           year = gg,
+           t = "Non-Black")
+  
+  c4 <- confint(
+    feols(m1, filter(dat1, black), weights = ~ weight, cluster = ~ group)
+  )
+  c4$term <- rownames(c4)
+  c4 <- c4 %>% 
+    mutate(model = 3,
+           year = gg,
+           t = "Black")
+  ######
+  c5 <- confint(
+    feols(m2, filter(dat1, !black), weights = ~ weight, cluster = ~ group)
+  )
+  c5$term <- rownames(c5)
+  c5 <- c5 %>% 
+    mutate(model = 4,
+           year = gg,
+           t = "Non-Black")
+  
+  c6 <- confint(
+    feols(m2, filter(dat1, black), weights = ~ weight, cluster = ~ group)
+  )
+  c6$term <- rownames(c6)
+  c6 <- c6 %>% 
[…]

### 2022-05-04 code/02_hills/rob_other/no_matching.R

@@ -1,12 +1,10 @@
 
 #####
-hills_pre_match <- readRDS("temp/real_pre_match_hills.rds") %>% 
+matches <- readRDS("temp/real_pre_match_hills.rds") %>% 
   ungroup()
 
-matches <- readRDS("temp/matches_hills.rds")
 
-matches <- left_join(matches, select(hills_pre_match, voter_id, first_tr_year),
-                     by = c("group" = "voter_id", "first_tr_year")) %>% 
+matches <- matches %>% 
   mutate(fd = first_tr_year,
          first_tr_year = ifelse(first_tr_year == 1, "2014-11-04",
                                 ifelse(first_tr_year == 2, "2016-11-08",
@@ -26,7 +24,7 @@ hist <- left_join(hist, elec_dates) %>%
 
 
 matches <- left_join(matches, hist %>% 
-                       filter(year(year) %% 2 == 0), by = c("voter" = "voter_id"))
+                       filter(year(year) %% 2 == 0), by = c("voter_id" = "voter_id"))
 
 periods <- fread("raw_data/period_lu.csv") %>% 
   mutate_at(vars(first_tr_year, year), as.Date, "%m/%d/%Y")
@@ -34,19 +32,9 @@ periods <- fread("raw_data/period_lu.csv") %>%
 matches <- left_join(matches, periods) %>% 
   filter(period %in% c(-2.5, -1.5, -.5, .5, 1.5))
 
-matches <- left_join(matches,
-                     hills_pre_match %>%
-                       select(-GEOID, -amount_paid, -last_date),
-                     by = c("voter" = "voter_id", "fd" = "first_tr_year"))
-
-matches <- left_join(matches,
-                     hills_pre_match %>%
-                       select(voter_id, amount_paid, last_date, first_tr_year, black_t = black,
-                              dem_t = dem),
-                     by = c("group" = "voter_id", "fd" = "first_tr_year")) %>% 
-  mutate(post = period >= 0.5,
-         treated = voter == group)
-
+matches <- matches %>% 
+  mutate(post = period >= 0.5)
+matches$weight <- 1
 cleanup("matches")
 gc()
 
@@ -54,10 +42,10 @@ gc()
 ll <- bind_rows(mutate(matches, first_tr_year = as.character(first_tr_year)),
                 mutate(matches, first_tr_year = "Overall")) %>%
   filter(period <= 0.5) %>% 
[…]

### 2022-05-04 code/02_hills/robust_cameras/01_merge_tickets_vf.R

@@ -170,40 +170,6 @@ joined <- left_join(hills_voters, hills_stops_ll,
   mutate(age = 2020 - year(birth_date)) %>% 
   filter(!is.na(pre_stops))
 
-
-####################### test permuting birth dates to check for false positives
-
-stops_names_dobs <- select(hills_stops_ll, first_name,
-                           last_name, date_of_birth) %>% 
-  distinct()
-
-j1 <- inner_join(hills_voters,
-                 stops_names_dobs,
-                 by = c("name_first" = "first_name",
-                        "name_last" = "last_name",
-                        "birth_date" = "date_of_birth"))
-
-joined2 <- inner_join(hills_voters,
-                      stops_names_dobs %>%
-                        mutate(date_of_birth = date_of_birth + 35),
-                      by = c("name_first" = "first_name",
-                             "name_last" = "last_name",
-                             "birth_date" = "date_of_birth"))
-
-joined3 <- inner_join(hills_voters,
-                      stops_names_dobs %>%
-                        mutate(date_of_birth = date_of_birth - 35),
-                      by = c("name_first" = "first_name",
-                             "name_last" = "last_name",
-                             "birth_date" = "date_of_birth"))
-
-test <- data.table(group = c("Actual Birthdate", "Birthdate + 35 Days", "Birthdate - 35 Days"),
-                   values = c(nrow(j1),
-                              nrow(joined2),
-                              nrow(joined3))) %>% 
-  mutate(values = comma(values))
-
-saveRDS(test, "temp/plus_minus_35_cam.rds")
 ######################################
 
 joined <- joined %>% 

### 2022-05-04 code/02_hills/robust_cameras/02_gen.R

@@ -24,16 +24,19 @@ cl<-makeCluster(c(readLines(NodeFile)), type="SOCK")
 cl
 
 
-hills_pre_match <- readRDS("temp/hills_pre_match_proximal.rds")
+hills_pre_match <- readRDS("temp/hills_pre_match_cam.rds")
 
 ############## 2014
 
 hills14_t <- filter(hills_pre_match, first_tr_year == "2014-11-04") %>% 
-  mutate(treated = 1)
+  mutate(treated = 1) %>% 
+  select(-pre_stops_c)
 
 hills14_c <- filter(hills_pre_match, first_tr_year == "2016-11-08",
                     !(voter_id %in% hills14_t$voter_id)) %>% 
-  mutate(treated = 0)
+  mutate(treated = 0) %>% 
+  select(-pre_stops) %>% 
+  rename(pre_stops = pre_stops_c)
 
 
 hills14 <- bind_rows(hills14_t, hills14_c) %>%  
@@ -46,11 +49,14 @@ hills14 <- bind_rows(hills14_t, hills14_c) %>%
 ############## 2016
 
 hills16_t <- filter(hills_pre_match, first_tr_year == "2016-11-08") %>% 
-  mutate(treated = 1)
+  mutate(treated = 1) %>% 
+  select(-pre_stops_c)
 
 hills16_c <- filter(hills_pre_match, first_tr_year == "2018-11-06",
                     !(voter_id %in% hills16_t$voter_id)) %>% 
-  mutate(treated = 0)
+  mutate(treated = 0) %>% 
+  select(-pre_stops) %>% 
+  rename(pre_stops = pre_stops_c)
 
 
 hills16 <- bind_rows(hills16_t, hills16_c) %>%  
@@ -62,11 +68,15 @@ hills16 <- bind_rows(hills16_t, hills16_c) %>%
 ############## 2018
 
 hills18_t <- filter(hills_pre_match, first_tr_year == "2018-11-06") %>% 
-  mutate(treated = 1)
+  mutate(treated = 1) %>% 
+  select(-pre_stops_c)
 
 hills18_c <- filter(hills_pre_match, first_tr_year == "2020-11-03",
                     !(voter_id %in% hills18_t$voter_id)) %>% 
-  mutate(treated = 0)
+  mutate(treated = 0) %>% 
+  select(-pre_stops) %>% 
+  rename(pre_stops = pre_stops_c)
+
 
[…]

### 2022-05-04 code/02_hills/robust_cameras/03_match_cam.R

@@ -12,16 +12,19 @@ require(snow)
 require(parallel)
 
 
-hills_pre_match <- readRDS("temp/hills_pre_match_proximal.rds")
+hills_pre_match <- readRDS("temp/hills_pre_match_cam.rds")
 
 ############## 2014
 
 hills14_t <- filter(hills_pre_match, first_tr_year == "2014-11-04") %>% 
-  mutate(treated = 1)
+  mutate(treated = 1) %>% 
+  select(-pre_stops_c)
 
 hills14_c <- filter(hills_pre_match, first_tr_year == "2016-11-08",
                     !(voter_id %in% hills14_t$voter_id)) %>% 
-  mutate(treated = 0)
+  mutate(treated = 0) %>% 
+  select(-pre_stops) %>% 
+  rename(pre_stops = pre_stops_c)
 
 
 hills14 <- bind_rows(hills14_t, hills14_c) %>%  
@@ -34,11 +37,14 @@ hills14 <- bind_rows(hills14_t, hills14_c) %>%
 ############## 2016
 
 hills16_t <- filter(hills_pre_match, first_tr_year == "2016-11-08") %>% 
-  mutate(treated = 1)
+  mutate(treated = 1) %>% 
+  select(-pre_stops_c)
 
 hills16_c <- filter(hills_pre_match, first_tr_year == "2018-11-06",
                     !(voter_id %in% hills16_t$voter_id)) %>% 
-  mutate(treated = 0)
+  mutate(treated = 0) %>% 
+  select(-pre_stops) %>% 
+  rename(pre_stops = pre_stops_c)
 
 
 hills16 <- bind_rows(hills16_t, hills16_c) %>%  
@@ -50,11 +56,15 @@ hills16 <- bind_rows(hills16_t, hills16_c) %>%
 ############## 2018
 
 hills18_t <- filter(hills_pre_match, first_tr_year == "2018-11-06") %>% 
-  mutate(treated = 1)
+  mutate(treated = 1) %>% 
+  select(-pre_stops_c)
 
 hills18_c <- filter(hills_pre_match, first_tr_year == "2020-11-03",
                     !(voter_id %in% hills18_t$voter_id)) %>% 
-  mutate(treated = 0)
+  mutate(treated = 0) %>% 
+  select(-pre_stops) %>% 
+  rename(pre_stops = pre_stops_c)
+
 
 hills18 <- bind_rows(hills18_t, hills18_c) %>%  
   mutate(first_tr_year = 3) %>% 
[…]

### 2022-05-04 code/02_hills/robust_cameras/04_reg_cam.R

@@ -3,7 +3,7 @@
 hills_pre_match <- readRDS("temp/real_pre_match_hills_cam.rds") %>% 
   ungroup()
 
-matches <- readRDS("temp/matches_hills_yem_cam.rds")
+matches <- readRDS("temp/matches_hills_cam.rds")
 
 matches <- left_join(matches, select(hills_pre_match, voter_id, first_tr_year),
                      by = c("group" = "voter_id", "first_tr_year")) %>% 
@@ -13,7 +13,7 @@ matches <- left_join(matches, select(hills_pre_match, voter_id, first_tr_year),
                                        ifelse(first_tr_year == 3, "2018-11-06", "XX"))),
          first_tr_year = as.Date(first_tr_year))
 
-hist <- readRDS("C:/Users/morrisk/Desktop/full_raw_coded_hills_w_bgs.rds") %>%
+hist <- readRDS("temp/full_raw_coded_hills_w_bgs.rds") %>%
   select(voter_id, starts_with("v1"), v08) %>%
   pivot_longer(!starts_with("vo"), names_to = "year", values_to = "to")
 
@@ -88,10 +88,11 @@ p2 <- ggplot(data = ll) +
   labs(x = "t", y = "Turnout",
        linetype = "Treatment Group",
        shape = "Treatment Group",
-       caption = "Treatment occurs inside of yellow band.", ) +
+       caption = "Treatment occurs inside of yellow band.
+Full regression tables in section 3 of SI.", ) +
   coord_cartesian(ylim = c(0.05, 0.75))
 p2
-saveRDS(p2, "temp/stopped_any_time_y.rds")
+saveRDS(p2, "temp/stopped_any_time_cam.rds")
 
 #####################
 
@@ -122,62 +123,85 @@ for(gg in c("overall", "2014-11-04", "2016-11-08", "2018-11-06")){
     tit = paste0("\\label{tab:dind-table-", substring(gg, 1, 4), "}Treatment Effect for Voters Stopped before ", substring(gg, 1, 4), " Election")
     ooo = c(1, 2, 7, 23, 24, 22, 25)
   }
- 
+  
   models1 <- lapply(c(m1, m2, m3, m4), function(f){
-    m <- lm(f, data = dat1,
-            weight = dat1$weight)
+    m <- feols(f, data = dat1,
+               weight = ~ weight, cluster = "group")
   })
   
[…]

### 2022-05-04 code/02_hills/robust_no_prior_match/01_gen_no_turnout.R

@@ -24,7 +24,7 @@ cl<-makeCluster(c(readLines(NodeFile)), type="SOCK")
 cl
 
 
-hills_pre_match <- readRDS("temp/hills_pre_match_cam.rds")
+hills_pre_match <- readRDS("temp/hills_pre_match.rds")
 
 ############## 2014
 
@@ -94,13 +94,13 @@ samp <- pre %>%
 
 match_data <- samp %>% 
   select(-voter_id, -treated, -GEOID, -amount_paid, -last_date,
-         -v08, -v16, -v10, -reg_date) %>% 
-  mutate_at(vars(white, black, latino, asian, male, dem, rep, v1, v2, v3, paid), ~ ifelse(. == T, 1, 0)) %>% 
-  select(first_tr_year, paid, civil, tampa_pd, v1, v2, v3, everything())
+         -v08, -v16, -v10, -reg_date, -v1, -v2, -v3) %>% 
+  mutate_at(vars(white, black, latino, asian, male, dem, rep, paid), ~ ifelse(. == T, 1, 0)) %>% 
+  select(first_tr_year, paid, civil, tampa_pd, everything())
 
 genout <- GenMatch(Tr = samp$treated, X = match_data, replace = T, cluster = cl, pop.size = 1000,
-                   exact = c(rep(T, 7), rep(F, 14)))
+                   exact = c(rep(T, 4), rep(F, 14)))
 
-saveRDS(genout, "temp/genout_hills_yem_cam.rds")
+saveRDS(genout, "temp/genout_hills_no_prior.rds")
 
 

### 2022-05-04 code/02_hills/robust_no_prior_match/01_genmatch_neverstopped.R

@@ -1,95 +1,0 @@
-
-## needs to be run on nyu hpc or its way too slow
-## set seed for reproducibility. this is a random 5-digit number: floor(runif(1, min = 10000, max = 99999))
-## on nyu hpc with 50 processors, 50gb RAM: Total run time : 66 hours 14 minutes and 25 seconds
-set.seed(45251)
-
-library(Matching)
-library(data.table)
-library(scales)
-library(kableExtra)
-library(tidyverse)
-require(snow)
-require(parallel)
-
-
-Sys.info()
-
-NodeFile = Sys.getenv("MY_HOSTFILE")
-
-print(NodeFile)
-
-readLines(NodeFile)
-
-cl<-makeCluster(c(readLines(NodeFile)), type="SOCK")
-cl
-
-
-hills_pre_match <- readRDS("temp/hills_pre_match.rds") %>% 
-  mutate(tract = as.numeric(substring(GEOID, 1, 11)))
-############## 2014
-
-hills14 <- hills_pre_match  %>% 
-  filter(fd <= "2014-11-04" |
-           fd > "2018-11-06") %>% 
-  mutate(treated = fd <= "2014-11-04") %>% 
-  select(-v14, -v16, -pre, -tract)
-
-samp <- hills14 %>% 
-  group_by(treated) %>% 
-  sample_frac(0.05) %>% 
-  ungroup()
-
-match_data <- samp %>% 
-  select(-voter_id, -treated, -GEOID, -fd, -max_amount) %>% 
-  mutate_at(vars(white, black, latino, asian, male, dem, rep), ~ ifelse(. == T, 1, 0)) %>% 
-  mutate(reg_date = as.integer(reg_date))
-
-genout <- GenMatch(Tr = samp$treated, X = match_data, replace = T, cluster = cl, pop.size = 1000)
-
-saveRDS(genout, "temp/genout_hills_14.rds")
-############## 2016
-
-hills16 <- hills_pre_match %>% 
-  filter(fd > "2014-11-04",
-         fd <= "2016-11-08" |
-           fd > "2018-11-06") %>% 
-  mutate(treated = fd <= "2016-11-08") %>% 
-  select(-v16, -pre, -tract)
-
-samp <- hills16 %>% 
-  group_by(treated) %>% 
-  sample_frac(0.05) %>% 
-  ungroup()
-
-match_data <- samp %>% 
[…]

### 2022-05-04 code/02_hills/robust_no_prior_match/02_match_no_turnout.R

@@ -12,7 +12,7 @@ require(snow)
 require(parallel)
 
 
-hills_pre_match <- readRDS("temp/hills_pre_match_cam.rds")
+hills_pre_match <- readRDS("temp/hills_pre_match.rds")
 
 ############## 2014
 
@@ -75,19 +75,17 @@ hills18 <- bind_rows(hills18_t, hills18_c) %>%
 ###########################################
 pre <- bind_rows(hills14, hills16, hills18)
 
-saveRDS(pre, "temp/real_pre_match_hills_cam.rds")
-
 ids <- pre %>%
   mutate(id = row_number()) %>%
   select(id, voter_id, first_tr_year)
 
 X <- pre %>%
   select(-voter_id, -treated, -GEOID, -amount_paid, -last_date,
-         -v08, -v16, -v10, -reg_date) %>% 
-  mutate_at(vars(white, black, latino, asian, male, dem, rep, v1, v2, v3, paid), ~ ifelse(. == T, 1, 0)) %>% 
-  select(first_tr_year, paid, civil, tampa_pd, v1, v2, v3, everything())
+         -v08, -v16, -v10, -reg_date, -v1, -v2, -v3) %>% 
+  mutate_at(vars(white, black, latino, asian, male, dem, rep, paid), ~ ifelse(. == T, 1, 0)) %>% 
+  select(first_tr_year, paid, civil, tampa_pd, everything())
 
-genout <- readRDS("temp/genout_hills_yem_cam.rds")
+genout <- readRDS("temp/genout_hills_no_prior.rds")
 
 
 mout <- Matchby(Tr = pre$treated, X = X,
@@ -99,13 +97,13 @@ mout <- Matchby(Tr = pre$treated, X = X,
                        X$male,
                        X$dem,
                        X$rep), estimand = "ATT", Weight.matrix = genout, M = 1,
-                exact = c(rep(T, 7), rep(F, 14)), ties = T)
+                exact = c(rep(T, 4), rep(F, 14)), ties = T)
 
 
 
-save(mout, file = "./temp/mout_hills_y_cam.RData")
+save(mout, file = "./temp/mout_hills_no_prior.RData")
 
-load("temp/mout_hills_y_cam.RData")
+load("temp/mout_hills_no_prior.RData")
 
 matches <- data.table(voter = c(mout$index.control,
                                 mout$index.treated),
[…]

### 2022-05-04 code/02_hills/robust_no_prior_match/03_matchneverstopped.R

@@ -1,481 +1,0 @@
-library(Matching)
-library(data.table)
-library(scales)
-library(kableExtra)
-library(tidyverse)
-require(snow)
-require(parallel)
-
-
-
-#####
-hills_pre_match <- readRDS("temp/hills_pre_match.rds") %>% 
-  ungroup()
-
-#################################################################
-########## 2014 #################################################
-#################################################################
-#################################################################
-hills14 <- hills_pre_match  %>%
-  filter(fd <= "2014-11-04" |
-           fd > "2018-11-06") %>%
-  mutate(treated = fd <= "2014-11-04") %>%
-  select(-v14, -v16, -pre)
-
-pot_con_14 <- filter(hills14, !treated) %>%
-  mutate(first_tr_year = as.Date("2014-11-04"))
-
-# ids <- hills14 %>%
-#   mutate(id = row_number()) %>%
-#   select(id, voter_id)
-# 
-# X <- hills14 %>%
-#   select(-voter_id, -treated, -GEOID, -fd, -max_amount) %>%
-#   mutate_at(vars(white, black, latino, asian, male, dem, rep), ~ ifelse(. == T, 1, 0)) %>%
-#   mutate(reg_date = as.integer(reg_date))
-# 
-# 
-# genout <- readRDS("temp/genout_hills_14.rds")
-# 
-# mout <- Matchby(Tr = hills14$treated, X = X,
-#                 by = c(X$white,
-#                        X$black,
-#                        X$latino,
-#                        X$asian,
-#                        X$male,
-#                        X$dem,
-#                        X$rep), estimand = "ATT", Weight.matrix = genout, M = 2, ties = T)
-# 
-# save(mout, file = "./temp/mout_hills_14.RData")
-# 
-# load("temp/mout_hills_14.RData")
-# 
-# matches <- data.table(voter = c(mout$index.control,
-#                                 mout$index.treated),
-#                       group = rep(mout$index.treated, 2),
-#                       weight = rep(mout$weights, 2)) %>%
-#   group_by(voter, group) %>%
-#   summarize(weight = sum(weight)) %>%
-#   ungroup()
-# 
-# 
-# matches <- left_join(matches, ids, by = c("voter" = "id")) %>%
-#   select(-voter) %>%
-#   rename(voter = voter_id)
-# 
-# matches <- left_join(matches, ids, by = c("group" = "id")) %>%
-#   select(-group) %>%
-#   rename(group = voter_id) %>%
[…]

### 2022-05-04 code/02_hills/robust_no_prior_match/03_reg_no_prior.R

@@ -1,9 +1,9 @@
 
 #####
-hills_pre_match <- readRDS("temp/real_pre_match_hills.rds") %>% 
+hills_pre_match <- readRDS("temp/real_pre_match_hills_no_prior.rds") %>% 
   ungroup()
 
-matches <- readRDS("temp/matches_hills.rds")
+matches <- readRDS("temp/matches_hills_no_prior.rds")
 
 matches <- left_join(matches, select(hills_pre_match, voter_id, first_tr_year),
                      by = c("group" = "voter_id", "first_tr_year")) %>% 
@@ -48,7 +48,6 @@ matches <- left_join(matches,
          treated = voter == group)
 
 cleanup("matches")
-gc()
 
 ##########################################################
 ll <- bind_rows(mutate(matches, first_tr_year = as.character(first_tr_year)),
@@ -92,26 +91,26 @@ p2 <- ggplot(data = ll) +
 Full regression tables in section 3 of SI.", ) +
   coord_cartesian(ylim = c(0.05, 0.75))
 p2
-saveRDS(p2, "temp/stopped_any_time.rds")
+saveRDS(p2, "temp/stopped_any_time_no_prior.rds")
 
 #####################
 
-m1 <- to ~ treated * post + as.factor(year)
+m1 <- to ~ treated * post + as.factor(year) | voter
 
 m2 <- to ~ treated * post + as.factor(year) +
   white + black + latino + asian + male +
   dem + rep + age + reg_date + pre_stops + v1 + v2 + v3 +
-  median_income + some_college + unem + civil + paid + tampa_pd
+  median_income + some_college + unem + civil + paid + tampa_pd | voter
 
-m3 <- to ~ treated * post * black + as.factor(year)
+m3 <- to ~ treated * post * black + as.factor(year) | voter
 
 m4 <- to ~ treated * post * black + as.factor(year) +
   white + black + latino + asian + male +
   dem + rep + age + reg_date + pre_stops + v1 + v2 + v3 +
-  median_income + some_college + unem + civil + paid + tampa_pd
+  median_income + some_college + unem + civil + paid + tampa_pd | voter
 
 matches$first_tr_year <- as.character(matches$first_tr_year)
-saveRDS(matches, "temp/full_reg_data.rds")
+saveRDS(matches, "temp/full_reg_data_no_prior.rds")
 for(gg in c("overall", "2014-11-04", "2016-11-08", "2018-11-06")){
   
   if(gg == "overall"){
[…]

### 2022-05-04 code/02_hills/robust_no_prior_match/03_rob_original_stopped_post_election.R

@@ -1,76 +1,0 @@
-
-
-hills_pre_match <- readRDS("temp/hills_pre_match.rds") %>% 
-  ungroup()
-
-matches_wide <- rbindlist(lapply(c(
-  "temp/matches_hills_14_rob.rds",
-  "temp/matches_hills_16_rob.rds",
-  "temp/matches_hills_18_rob.rds"), readRDS))
-
-hist <- readRDS("temp/full_raw_coded_hills_w_bgs.rds") %>%
-  select(voter_id, starts_with("v1")) %>%
-  pivot_longer(starts_with("v1"), names_to = "year", values_to = "to")
-
-elec_dates <- fread("raw_data/election_dates.csv")
-
-hist <- left_join(hist, elec_dates) %>% 
-  select(-year) %>% 
-  rename(year = date) %>% 
-  mutate(year = as.Date(year))
-
-
-matches <- left_join(matches_wide, hist %>% 
-                       filter(year(year) %% 2 == 0), by = c("voter" = "voter_id"))
-
-periods <- fread("raw_data/period_lu.csv") %>% 
-  mutate_at(vars(first_tr_year, year), as.Date)
-
-matches <- left_join(matches, periods)
-
-matches <- left_join(matches,
-                     hills_pre_match %>%
-                       select(-GEOID, -fd, -max_amount),
-                     by = c("voter" = "voter_id"))
-
-matches <- left_join(matches,
-                     hills_pre_match %>%
-                       select(voter_id, max_amount, fd, black_t = black),
-                     by = c("group" = "voter_id")) %>% 
-  mutate(post = period >= 0.5,
-         treated = voter == group)
-
-ll <- matches %>%
-  filter(period <= 1.5) %>% 
-  group_by(treated, period, black_t) %>%
-  summarize(to = weighted.mean(to, weight)) %>% 
-  mutate(treated = ifelse(treated, "Treated", "Control"),
-         black = ifelse(black_t, "Black Voters", "Non-Black Voters"))
-
-
-ll$treated <- factor(ll$treated, levels = c("Treated", "Control"))
-
-p1 <- ggplot(data = ll) + 
-  facet_grid(~ black) +
-  geom_rect(aes(xmin = 0.5+.125, xmax = 0.5, ymin = 0, ymax = Inf),
-            alpha = 0.03, color = "black", fill = "yellow") +
-  geom_line(data =ll, aes(x = period, y = to, linetype = treated)) +
[…]

### 2022-05-04 code/02_hills/robust_no_prior_match/04_rob_windows.R

@@ -4,59 +4,58 @@ library(lubridate)
 library(data.table)
 
 lapply(c(1:23), function(i){
-  if(!file.exists(paste0("temp/matches_rob_", i, ".rds"))){
-    pre <- readRDS("temp/real_pre_match_hills.rds") %>% 
-      filter(((last_date >= (ymd(as.Date("2014-11-04")) %m+% months(-i))) &
-                (last_date <= ymd(as.Date("2014-11-04")) %m+% months(i)) & (first_tr_year == 1)) |
-               ((last_date >= (ymd(as.Date("2016-11-08")) %m+% months(-i))) &
-                  (last_date <= ymd(as.Date("2016-11-08")) %m+% months(i)) & (first_tr_year == 2)) |
-               ((last_date >= (ymd(as.Date("2018-11-06")) %m+% months(-i))) &
-                  (last_date <= ymd(as.Date("2018-11-06")) %m+% months(i)) & (first_tr_year == 3)))
-    
-    
-    ids <- pre %>%
-      mutate(id = row_number()) %>%
-      select(id, voter_id, first_tr_year)
-    
-    X <- pre %>%
-      select(-voter_id, -treated, -GEOID, -amount_paid, -last_date,
-             -v08, -v16, -v10, -reg_date) %>% 
-      mutate_at(vars(white, black, latino, asian, male, dem, rep, v1, v2, v3, paid), ~ ifelse(. == T, 1, 0)) %>% 
-      select(first_tr_year, paid, civil, tampa_pd, v1, v2, v3, everything())
-    
-    genout <- readRDS("temp/genout_hills.rds")
-    
-    
-    mout <- Matchby(Tr = pre$treated, X = X,
-                    by = c(X$first_tr_year,
-                           X$white,
-                           X$black,
-                           X$latino,
-                           X$asian,
-                           X$male,
-                           X$dem,
-                           X$rep), estimand = "ATT", Weight.matrix = genout, M = 1,
-                    exact = c(rep(T, 7), rep(F, 14)), ties = T)
-    
-    matches <- data.table(voter = c(mout$index.control,
-                                    mout$index.treated),
-                          group = rep(mout$index.treated, 2),
-                          weight = rep(mout$weights, 2)) %>%
-      group_by(voter, group) %>%
-      summarize(weight = sum(weight)) %>%
[…]

### 2022-05-04 code/02_hills/robust_no_prior_match/05_coef_plot_es.R

@@ -1,0 +1,168 @@
+
+matches <- readRDS("temp/full_reg_data_no_prior.rds")
+m1 <- to ~ treated * post + as.factor(year)
+m2 <- to ~ treated * post + as.factor(year) +
+  white + black + latino + asian + male +
+  dem + rep + age + reg_date + pre_stops + v1 + v2 + v3 +
+  median_income + some_college + unem + civil + paid + tampa_pd
+
+for(gg in c("overall", "2014-11-04", "2016-11-08", "2018-11-06")){
+  
+  if(gg == "overall"){
+    dat1 <- filter(matches, period <= 0.5)
+  }else{
+    dat1 <- dplyr::filter(matches, period <= 0.5, first_tr_year == gg)
+  }
+  
+  c1 <- confint(
+    feols(m1, dat1, weights = ~ weight, cluster = ~ group)
+  )
+  c1$term <- rownames(c1)
+  c1 <- c1 %>% 
+    mutate(model = 1,
+           year = gg,
+           t = "Overall")
+  
+  c2 <- confint(
+    feols(m2, dat1, weights = ~ weight, cluster = ~ group)
+  )
+  c2$term <- rownames(c2)
+  c2 <- c2 %>% 
+    mutate(model = 2,
+           year = gg,
+           t = "Overall")
+  ######
+  c3 <- confint(
+    feols(m1, filter(dat1, !black), weights = ~ weight, cluster = ~ group)
+  )
+  c3$term <- rownames(c3)
+  c3 <- c3 %>% 
+    mutate(model = 3,
+           year = gg,
+           t = "Non-Black")
+  
+  c4 <- confint(
+    feols(m1, filter(dat1, black), weights = ~ weight, cluster = ~ group)
+  )
+  c4$term <- rownames(c4)
+  c4 <- c4 %>% 
+    mutate(model = 3,
+           year = gg,
+           t = "Black")
+  ######
+  c5 <- confint(
+    feols(m2, filter(dat1, !black), weights = ~ weight, cluster = ~ group)
+  )
+  c5$term <- rownames(c5)
+  c5 <- c5 %>% 
+    mutate(model = 4,
+           year = gg,
+           t = "Non-Black")
+  
+  c6 <- confint(
+    feols(m2, filter(dat1, black), weights = ~ weight, cluster = ~ group)
+  )
+  c6$term <- rownames(c6)
+  c6 <- c6 %>% 
[…]

### 2022-08-30 markdown/compile.Rmd
compile

@@
 ```{r setup, echo = F, message = F, warning = F}
-knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf")
+library(ragg)
 library(systemfit)
-library(kevostools)
-library(AER)
-library(sandwich)
-library(lmtest)
-library(scales)
 library(ggpubr)
 library(tidyverse)
-library(extrafont)
 library(kableExtra)
 library(data.table)
-library(stargazer)
-loadfonts()
+ragg_png = function(..., res = 300) {
+  ragg::agg_png(..., res = res, units = "in")
+}
+knitr::opts_chunk$set(dev = "ragg_png", dpi = 800)
+knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf")
 ```
@@
 p2 <- readRDS("temp/stopped_any_time.rds")
-print(p2)
-```
-
-```{r did-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/stopped_any_time_no_prior.rds")
-print(p2)
+p2
 ```
@@
 p2 <- readRDS("temp/stopped_any_time_no_matching.rds")
+print(p2)
+```
+
+```{r did-different-approaches, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 6, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout (no matching at all)", fig.pos = "H", fig.align = "center"}
+p2 <- readRDS("temp/ts.rds")
 print(p2)
@@
 
-```{r coef-plot-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/coef_plot_no_prior.rds")
-print(p2)
-```
-
-```{r event-study-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
+```{r event-study-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 4, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
 p2 <- readRDS("temp/event_study.rds")
@@
 
-```{r black-overall-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Overall", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/black_overall_effect.rds")
+```{r windows, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:did-1}Black Relative", fig.pos = "H", fig.align = "center"}
+p2 <- readRDS("temp/window_plot_good.rds")
 print(p2)
 ```
-
-```{r black-overall-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Overall (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/black_overall_effect_no_prior.rds")
-print(p2)
-```
-
-```{r black-relative-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Relative", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/black_relative_effect.rds")
-print(p2)
-```
-
-```{r black-relative-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Relative (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/black_relative_effect_no_prior.rds")
-print(p2)
-```
-
-```{r non-black-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Nonblack", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/non_black_effect.rds")
-print(p2)
-```
-
-```{r non-black-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Nonblack (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/non_black_effect_no_prior.rds")
-print(p2)
-```
-
-```{r overall-time-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Relative", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/overall_effect.rds")
-print(p2)
-```
-
-```{r overall-time-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Relative (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/overall_effect_no_prior.rds")
-print(p2)
-```

### 2022-08-30 markdown/compile.tex
compile

@@
 \usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \usepackage{xcolor}
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
@@
 \author{}
-\date{\vspace{-2.5em}May 04, 2022}
+\date{\vspace{-2.5em}June 16, 2022}
 
@@
 
-{\centering \includegraphics{compile_files/figure-latex/did-no-prior-1}
-
-}
-
-\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout (no prior turnout in match)}\label{fig:did-no-prior}
-\end{figure}
-
-\begin{figure}[H]
-
 {\centering \includegraphics{compile_files/figure-latex/did-no-matching-1}
@@
 \caption{\label{fig:did-1}Effect of Being Ticketed on Turnout (no matching at all)}\label{fig:did-no-matching}
+\end{figure}
+
+\begin{figure}[H]
+
+{\centering \includegraphics{compile_files/figure-latex/did-different-approaches-1}
+
+}
+
+\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout (no matching at all)}\label{fig:did-different-approaches}
 \end{figure}
@@
 
-{\centering \includegraphics{compile_files/figure-latex/coef-plot-no-prior-1}
-
-}
-
-\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout (no prior turnout in match)}\label{fig:coef-plot-no-prior}
-\end{figure}
-
-\begin{figure}[H]
-
 {\centering \includegraphics{compile_files/figure-latex/event-study-primary-1}
@@
 
-{\centering \includegraphics{compile_files/figure-latex/black-overall-primary-1}
+{\centering \includegraphics{compile_files/figure-latex/windows-1}
 
@@
 
-\caption{\label{fig:did-1}Black Overall}\label{fig:black-overall-primary}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics{compile_files/figure-latex/black-overall-no-prior-1}
-
-}
-
-\caption{\label{fig:did-1}Black Overall (no prior turnout in match)}\label{fig:black-overall-no-prior}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics{compile_files/figure-latex/black-relative-primary-1}
-
-}
-
-\caption{\label{fig:did-1}Black Relative}\label{fig:black-relative-primary}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics{compile_files/figure-latex/black-relative-no-prior-1}
-
-}
-
-\caption{\label{fig:did-1}Black Relative (no prior turnout in match)}\label{fig:black-relative-no-prior}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics{compile_files/figure-latex/non-black-primary-1}
-
-}
-
-\caption{\label{fig:did-1}Nonblack}\label{fig:non-black-primary}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics{compile_files/figure-latex/non-black-no-prior-1}
-
-}
-
-\caption{\label{fig:did-1}Nonblack (no prior turnout in match)}\label{fig:non-black-no-prior}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics{compile_files/figure-latex/overall-time-primary-1}
-
-}
-
-\caption{\label{fig:did-1}Black Relative}\label{fig:overall-time-primary}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics{compile_files/figure-latex/overall-time-no-prior-1}
-
-}
-
-\caption{\label{fig:did-1}Black Relative (no prior turnout in match)}\label{fig:overall-time-no-prior}
+\caption{\label{fig:did-1}Black Relative}\label{fig:windows}
 \end{figure}

### 2022-08-30 markdown/si.Rmd
compile

@@
 j
+
+knitr::kable(table, booktabs = T, caption = "\\label{tab:change-dobs} Results of Shifting Birthdates", linesep = "", align=rep('c', ncol(table)), format = "latex",
+               col.names = linebreak(c("Group", "Number of Matches Between Traffic Stop and Voter File Records"))) %>%
+  kable_styling(font_size = 10,
+                latex_options = c("HOLD_position")) %>%
+  column_spec(c(1), width = "5cm") %>% 
+  column_spec(c(2), width = "6cm") %>% 
+  save_kable(paste0("./temp/shift_tab.tex"))
+
 ```
@@
 We consider this rate of false positives too low to meaningfully impact our results.
-
-# Sensitivity to Narrower Windows
-
-In the individual-level section of this manuscript, voters stopped in the 2 years prior to an election are considered treated, and we draw our controls from the voters stopped 2 years after the election.
-It is perhaps the case that this large window results in implausible matches; under this design, a treated voter stopped in December of 2012 could draw a control not stopped until October of 2016.
-Voters stopped nearly 4 years apart from one another might differ in meaningful ways that our matching models cannot capture.
-
-Here, we re-run our matching process on a variety of different windows around the elections.
-In the most conservative approach, we force voters stopped in the month before an election to match with voters stopped in the month after the election; we then gradually relax this assumption by allowing voters stopped in the 2 months before the election to match to those stopped in the 2 months afterwards, until reaching the two-years used in the manuscript.
-
-Figure 1 shows that our overall treatment effect is remarkably consistent regardless of the size of the window drawn around the election.
-As we expand the window, we gain more treated voters (and treated voters have a larger pool of potential controls).
-As such, the confidence interval shrinks, but the treated and control voters are stopped at more distant temporal points from one another.
-The left-most side of the plot shows that the overall effect is robust to very strict assumptions.
-In each case, we are re-estimating our primary models in which the covariates used in the matching exercise are also included in the econometric model.
-
-```{r windows, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:rob-window}Estimated Treatment Effect for Different Treatment Windows", fig.pos = "!htb", fig.align = "center"}
-p2 <- readRDS("temp/windows_rob.rds")
-print(p2)
-```
 

### 2022-08-30 markdown/si.tex
compile

@@
 \setcounter{secnumdepth}{5}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 \usepackage{rotating}
@@
 \usepackage{xcolor}
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 \pagenumbering{gobble}
-\pagenumbering{arabic}
+\pagebreak
+
 \doublespacing
-\newpage
 
@@
 This runs the risk of identifying false positives.
-To test the prevalence of false positives in our administrative matching procedure, we use the test developed by \protect\hyperlink{ref-Meredith2014}{Meredith and Morse} (\protect\hyperlink{ref-Meredith2014}{2014}).
+To test the prevalence of false positives in our administrative matching procedure, we use the test developed by Meredith and Morse (\protect\hyperlink{ref-Meredith2014}{2014}).
 By systematically permuting the birth dates in one set of records, we can see whether false positive matches are a major concern.
@@
 \midrule
-Actual Birthdate & 263,152\\
+Actual Birthdate & 263,149\\
 Birthdate + 35 Days & 78\\
@@
 We consider this rate of false positives too low to meaningfully impact our results.
-
-\hypertarget{sensitivity-to-narrower-windows}{%
-\section{Sensitivity to Narrower Windows}\label{sensitivity-to-narrower-windows}}
-
-In the individual-level section of this manuscript, voters stopped in the 2 years prior to an election are considered treated, and we draw our controls from the voters stopped 2 years after the election.
-It is perhaps the case that this large window results in implausible matches; under this design, a treated voter stopped in December of 2012 could draw a control not stopped until October of 2016.
-Voters stopped nearly 4 years apart from one another might differ in meaningful ways that our matching models cannot capture.
-
-Here, we re-run our matching process on a variety of different windows around the elections.
-In the most conservative approach, we force voters stopped in the month before an election to match with voters stopped in the month after the election; we then gradually relax this assumption by allowing voters stopped in the 2 months before the election to match to those stopped in the 2 months afterwards, until reaching the two-years used in the manuscript.
-
-Figure 1 shows that our overall treatment effect is remarkably consistent regardless of the size of the window drawn around the election.
-As we expand the window, we gain more treated voters (and treated voters have a larger pool of potential controls).
-As such, the confidence interval shrinks, but the treated and control voters are stopped at more distant temporal points from one another.
-The left-most side of the plot shows that the overall effect is robust to very strict assumptions.
-In each case, we are re-estimating our primary models in which the covariates used in the matching exercise are also included in the econometric model.
-
-\begin{figure}[!htb]
-
-{\centering \includegraphics{si_files/figure-latex/windows-1}
-
-}
-
-\caption{\label{fig:rob-window}Estimated Treatment Effect for Different Treatment Windows}\label{fig:windows}
-\end{figure}
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-Meredith2014}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Meredith2014}{}}%
 Meredith, Marc, and Michael Morse.

### 2022-08-30 markdown/compile.Rmd
compile

@@
 
-# author:
-# - Jonathan Ben-Menachem^[PhD Student, Columbia University, Department of Sociology (jb4487@columbia.edu)]
-# - Kevin Morris^[PhD Student, CUNY Graduate Center, Department of Sociology (kmorris@gradcenter.cuny.edu)]
-# thanks: Earlier versions of this work were presented at the 2021 American Sociological Association Annual Meeting, the 2021 American Political Science Association Annual Meeting, and the Justice Lab at Columbia University.
-We would like to thank Bruce Western, Joshua Whitford,  Gerard Torrats-Espinosa, Brittany Friedman, Brendan McQuade, Flavien Ganter, Hannah Pullen-Blasnik, Tim Ittner, LeShae Henderson, and Van Tran for their engagement with our paper in its earliest stages.
-Special thanks to Sam Donahue for identifying the Tampa dataset that became the core of our analysis and eyeballing many, many iterations of analysis results.
-And finally, we would like to thank Hannah Walker for deep, charitable feedback that pushed us not to undersell our own contribution
 date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
 
-```{r did-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/stopped_any_time.rds")
-p2
-```
-
-```{r did-no-matching, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout (no matching at all)", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/stopped_any_time_no_matching.rds")
-print(p2)
-```
-
 ```{r did-different-approaches, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 6, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout (no matching at all)", fig.pos = "H", fig.align = "center"}
@@
 
-Tables 1--4 are with prior turnout in the match. Tables 5--8 have no prior turnout. Table 9--12 have no matching at all
-\begin{singlespace}
-\input{"../temp/small_two_matches_reg_overall.tex"}
-\input{"../temp/small_two_matches_reg_2014-11-04.tex"}
-\input{"../temp/small_two_matches_reg_2016-11-08.tex"}
-\input{"../temp/small_two_matches_reg_2018-11-06.tex"}
-
-\input{"../temp/small_table_overall_no_prior.tex"}
-\input{"../temp/small_table_2014-11-04_no_prior.tex"}
-\input{"../temp/small_table_2016-11-08_no_prior.tex"}
-\input{"../temp/small_table_2018-11-06_no_prior.tex"}
-
-\input{"../temp/small_two_matches_reg_overall_no_matching.tex"}
-\input{"../temp/small_two_matches_reg_2014-11-04_no_matching.tex"}
-\input{"../temp/small_two_matches_reg_2016-11-08_no_matching.tex"}
-\input{"../temp/small_two_matches_reg_2018-11-06_no_matching.tex"}
-\end{singlespace}
-
 ```{r coef-plot-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
 p2 <- readRDS("temp/coef_plot.rds")
+print(p2)
+```
+
+```{r windows, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:did-1}Black Relative", fig.pos = "H", fig.align = "center"}
+p2 <- readRDS("temp/window_plot_good.rds")
 print(p2)
@@
 ```
-
-```{r event-study-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/event_study_no_prior.rds")
-print(p2)
-```
-
-```{r windows, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:did-1}Black Relative", fig.pos = "H", fig.align = "center"}
-p2 <- readRDS("temp/window_plot_good.rds")
-print(p2)
-```

### 2022-08-30 markdown/compile.tex
compile

@@
 \author{}
-\date{\vspace{-2.5em}June 16, 2022}
+\date{\vspace{-2.5em}August 30, 2022}
 
@@
 
-{\centering \includegraphics{compile_files/figure-latex/did-primary-1}
-
-}
-
-\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout}\label{fig:did-primary}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics{compile_files/figure-latex/did-no-matching-1}
-
-}
-
-\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout (no matching at all)}\label{fig:did-no-matching}
-\end{figure}
-
-\begin{figure}[H]
-
 {\centering \includegraphics{compile_files/figure-latex/did-different-approaches-1}
@@
 \end{figure}
-
-Tables 1--4 are with prior turnout in the match. Tables 5--8 have no prior turnout. Table 9--12 have no matching at all
-
-\begin{singlespace}
-\input{"../temp/small_two_matches_reg_overall.tex"}
-\input{"../temp/small_two_matches_reg_2014-11-04.tex"}
-\input{"../temp/small_two_matches_reg_2016-11-08.tex"}
-\input{"../temp/small_two_matches_reg_2018-11-06.tex"}
-
-\input{"../temp/small_table_overall_no_prior.tex"}
-\input{"../temp/small_table_2014-11-04_no_prior.tex"}
-\input{"../temp/small_table_2016-11-08_no_prior.tex"}
-\input{"../temp/small_table_2018-11-06_no_prior.tex"}
-
-\input{"../temp/small_two_matches_reg_overall_no_matching.tex"}
-\input{"../temp/small_two_matches_reg_2014-11-04_no_matching.tex"}
-\input{"../temp/small_two_matches_reg_2016-11-08_no_matching.tex"}
-\input{"../temp/small_two_matches_reg_2018-11-06_no_matching.tex"}
-\end{singlespace}
 
@@
 
+{\centering \includegraphics{compile_files/figure-latex/windows-1}
+
+}
+
+\caption{\label{fig:did-1}Black Relative}\label{fig:windows}
+\end{figure}
+
+\begin{figure}[H]
+
 {\centering \includegraphics{compile_files/figure-latex/event-study-primary-1}
@@
 
-\begin{figure}[H]
-
-{\centering \includegraphics{compile_files/figure-latex/event-study-no-prior-1}
-
-}
-
-\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout (no prior turnout in match)}\label{fig:event-study-no-prior}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics{compile_files/figure-latex/windows-1}
-
-}
-
-\caption{\label{fig:did-1}Black Relative}\label{fig:windows}
-\end{figure}
-
 \end{document}
